
  \begin{itemize}
 \item[] \textit{Asystasia} 十萬錯屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Asystasia+gangetica+subsp.+gangetica}{\textit{A. gangetica} (L.) T.Anderson subsp. \textit{gangetica}}  \index{Asystasia@\textit{Asystasia}!gangetica@\textit{gangetica}!subsp. gangetica@subsp. \textit{gangetica}} 赤道櫻草\index{赤道櫻草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Asystasia+gangetica+subsp.+micrantha}{\textit{A. gangetica} (L.) T.Anderson subsp. \textit{micrantha} (Nees) Ensermu}  \index{Asystasia@\textit{Asystasia}!gangetica@\textit{gangetica}!subsp. micrantha@subsp. \textit{micrantha}} 小花寬葉馬偕花\index{小花寬葉馬偕花} NA $^n$
  \end{itemize}
 \item[] \textit{Asystasiella} 擬馬偕花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Asystasiella+neesiana}{\textit{A. neesiana} (Wall.) Lindau}  \index{Asystasiella@\textit{Asystasiella}!neesiana@\textit{neesiana}} 尼氏擬馬偕花\index{尼氏擬馬偕花} VU
  \end{itemize}
 \item[] \textit{Avicennia} 海茄苳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Avicennia+marina}{\textit{A. marina} (Forssk.) Vierh.}  \index{Avicennia@\textit{Avicennia}!marina@\textit{marina}} 海茄冬\index{海茄冬} LC
  \end{itemize}
 \item[] \textit{Blechum} 賽山藍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blechum+pyramidatum}{\textit{B. pyramidatum} (Lam.) Urb.}  \index{Blechum@\textit{Blechum}!pyramidatum@\textit{pyramidatum}} 賽山藍\index{賽山藍} NA $^n$
  \end{itemize}
 \item[] \textit{Codonacanthus} 針刺草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Codonacanthus+pauciflorus}{\textit{C. pauciflorus} (Nees) Nees}  \index{Codonacanthus@\textit{Codonacanthus}!pauciflorus@\textit{pauciflorus}} 針刺草\index{針刺草} LC
  \end{itemize}
 \item[] \textit{Dicliptera} 華九頭獅子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dicliptera+chinensis}{\textit{D. chinensis} (L.) Juss.}  \index{Dicliptera@\textit{Dicliptera}!chinensis@\textit{chinensis}} 華九頭獅子草\index{華九頭獅子草} LC
  \end{itemize}
 \item[] \textit{Dipteracanthus} 楠草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dipteracanthus+repens}{\textit{D. repens} (L.) Hassk.}  \index{Dipteracanthus@\textit{Dipteracanthus}!repens@\textit{repens}} 蘆利草\index{蘆利草} LC
  \end{itemize}
 \item[] \textit{Hemigraphis} 半插花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemigraphis+cumingiana}{\textit{H. cumingiana} (Nees) Fern.-Vill.}  \index{Hemigraphis@\textit{Hemigraphis}!cumingiana@\textit{cumingiana}} 直立半插花\index{直立半插花} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemigraphis+primulifolia}{\textit{H. primulifolia} (Nees) Fern.-Vill.}  \index{Hemigraphis@\textit{Hemigraphis}!primulifolia@\textit{primulifolia}} 恆春半插花\index{恆春半插花} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemigraphis+reptans}{\textit{H. reptans} (G.Forst.) T.Anderson ex Hemsl.}  \index{Hemigraphis@\textit{Hemigraphis}!reptans@\textit{reptans}} 匍匐半插花\index{匍匐半插花} VU
  \end{itemize}
 \item[] \textit{Hygrophila} 水蓑衣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+corymbosa}{\textit{H. corymbosa} (Blume) Lindau}  \index{Hygrophila@\textit{Hygrophila}!corymbosa@\textit{corymbosa}} 繖花水蓑衣\index{繖花水蓑衣} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+difformis}{\textit{H. difformis} (L.f.) Blume}  \index{Hygrophila@\textit{Hygrophila}!difformis@\textit{difformis}} 異葉水蓑衣\index{異葉水蓑衣} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+guianensis}{\textit{H. guianensis} Nees}  \index{Hygrophila@\textit{Hygrophila}!guianensis@\textit{guianensis}} 蓋亞那水蓑衣\index{蓋亞那水蓑衣} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+lancea}{\textit{H. lancea} (Thunb.) Miq.}  \index{Hygrophila@\textit{Hygrophila}!lancea@\textit{lancea}} 水蓑衣\index{水蓑衣} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+pogonocalyx}{\textit{H. pogonocalyx} Hayata}  \index{Hygrophila@\textit{Hygrophila}!pogonocalyx@\textit{pogonocalyx}} 大安水蓑衣\index{大安水蓑衣}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+polysperma}{\textit{H. polysperma} T.Anderson}  \index{Hygrophila@\textit{Hygrophila}!polysperma@\textit{polysperma}} 小獅子草\index{小獅子草} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+salicifolia}{\textit{H. salicifolia} (Vahl) Nees}  \index{Hygrophila@\textit{Hygrophila}!salicifolia@\textit{salicifolia}} 柳葉水蓑衣\index{柳葉水蓑衣} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hygrophila+stricta}{\textit{H. stricta} (Nees) Lindau}  \index{Hygrophila@\textit{Hygrophila}!stricta@\textit{stricta}} 刻脈水蓑衣\index{刻脈水蓑衣} NA $^n$
  \end{itemize}
 \item[] \textit{Hypoestes} 槍刀菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypoestes+cumingiana}{\textit{H. cumingiana} Benth. \& Hook.}  \index{Hypoestes@\textit{Hypoestes}!cumingiana@\textit{cumingiana}} 槍刀菜\index{槍刀菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypoestes+purpurea}{\textit{H. purpurea} R.Br.}  \index{Hypoestes@\textit{Hypoestes}!purpurea@\textit{purpurea}} 六角英\index{六角英} LC
  \end{itemize}
 \item[] \textit{Justicia} 爵床屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+comata}{\textit{J. comata} (L.) Lam.}  \index{Justicia@\textit{Justicia}!comata@\textit{comata}} 穗花爵床\index{穗花爵床} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+gendarussa}{\textit{J. gendarussa} Brum.f.}  \index{Justicia@\textit{Justicia}!gendarussa@\textit{gendarussa}} 尖尾鳳\index{尖尾鳳} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+procumbens+var.+hayatae}{\textit{J. procumbens} L. var. \textit{hayatae} (Yamam.) Ohwi}  \index{Justicia@\textit{Justicia}!procumbens@\textit{procumbens}!var. hayatae@var. \textit{hayatae}} 早田氏爵床\index{早田氏爵床}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+procumbens+var.+hirsuta}{\textit{J. procumbens} L. var. \textit{hirsuta} Yamam.}  \index{Justicia@\textit{Justicia}!procumbens@\textit{procumbens}!var. hirsuta@var. \textit{hirsuta}} 密毛爵床\index{密毛爵床}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+procumbens+var.+linearifolia}{\textit{J. procumbens} L. var. \textit{linearifolia} Yamam.}  \index{Justicia@\textit{Justicia}!procumbens@\textit{procumbens}!var. linearifolia@var. \textit{linearifolia}} 狹葉爵床\index{狹葉爵床}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+procumbens+var.+procumbens}{\textit{J. procumbens} L. var. \textit{procumbens}}  \index{Justicia@\textit{Justicia}!procumbens@\textit{procumbens}!var. procumbens@var. \textit{procumbens}} 爵床\index{爵床} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Justicia+quadrifaria}{\textit{J. quadrifaria} (Nees) T.Anderson}  \index{Justicia@\textit{Justicia}!quadrifaria@\textit{quadrifaria}} 花蓮爵床\index{花蓮爵床} VU
  \end{itemize}
 \item[] \textit{Kudoacanthus} 銀脈爵床屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kudoacanthus+albonervosa}{\textit{K. albonervosa} Hosok.}  \index{Kudoacanthus@\textit{Kudoacanthus}!albonervosa@\textit{albonervosa}} 銀脈爵床\index{銀脈爵床}\# VU
  \end{itemize}
 \item[] \textit{Lepidagathis} 鱗球花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidagathis+formosensis}{\textit{L. formosensis} C.B.Clarke ex Hayata}  \index{Lepidagathis@\textit{Lepidagathis}!formosensis@\textit{formosensis}} 臺灣鱗球花\index{臺灣鱗球花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidagathis+inaequalis}{\textit{L. inaequalis} C.B.Clarke ex Elmer}  \index{Lepidagathis@\textit{Lepidagathis}!inaequalis@\textit{inaequalis}} 卵葉鱗球花\index{卵葉鱗球花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidagathis+secunda}{\textit{L. secunda} (Blanco) Nees}  \index{Lepidagathis@\textit{Lepidagathis}!secunda@\textit{secunda}} 小琉球鱗球花\index{小琉球鱗球花} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidagathis+stenophylla}{\textit{L. stenophylla} C.B.Clarke ex Hayata}  \index{Lepidagathis@\textit{Lepidagathis}!stenophylla@\textit{stenophylla}} 柳葉鱗球花\index{柳葉鱗球花}\# NT
  \end{itemize}
 \item[] \textit{Nelsonia} 瘤子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nelsonia+canescens}{\textit{N. canescens} (Lam.) Spreng.}  \index{Nelsonia@\textit{Nelsonia}!canescens@\textit{canescens}} 瘤子草\index{瘤子草} NA $^n$
  \end{itemize}
 \item[] \textit{Peristrophe} 九頭獅子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristrophe+japonica}{\textit{P. japonica} (Thunb.) Bremek.}  \index{Peristrophe@\textit{Peristrophe}!japonica@\textit{japonica}} 九頭獅子草\index{九頭獅子草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristrophe+roxburghiana}{\textit{P. roxburghiana} (Schult.) Bremek.}  \index{Peristrophe@\textit{Peristrophe}!roxburghiana@\textit{roxburghiana}} 長花九頭獅子草\index{長花九頭獅子草} LC
  \end{itemize}
 \item[] \textit{Ruellia} 蘆利草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ruellia+brittoniana}{\textit{R. brittoniana} Leonard}  \index{Ruellia@\textit{Ruellia}!brittoniana@\textit{brittoniana}} 紫花蘆利草\index{紫花蘆利草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ruellia+prostrata}{\textit{R. prostrata} Poir.}  \index{Ruellia@\textit{Ruellia}!prostrata@\textit{prostrata}} 匐蘆利草\index{匐蘆利草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ruellia+squarrosa}{\textit{R. squarrosa} (Fenzl) Schaffnit}  \index{Ruellia@\textit{Ruellia}!squarrosa@\textit{squarrosa}} 蔓枝蘆利草\index{蔓枝蘆利草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ruellia+tuberosa}{\textit{R. tuberosa} L.}  \index{Ruellia@\textit{Ruellia}!tuberosa@\textit{tuberosa}} 塊根蘆利草\index{塊根蘆利草} NA $^n$
  \end{itemize}
 \item[] \textit{Rungia} 明萼草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rungia+chinensis}{\textit{R. chinensis} Benth.}  \index{Rungia@\textit{Rungia}!chinensis@\textit{chinensis}} 明萼草\index{明萼草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rungia+taiwanensis}{\textit{R. taiwanensis} T.Yamaz.}  \index{Rungia@\textit{Rungia}!taiwanensis@\textit{taiwanensis}} 臺灣明萼草\index{臺灣明萼草}\# LC
  \end{itemize}
 \item[] \textit{Staurogyne} 哈哼花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Staurogyne+concinnula}{\textit{S. concinnula} (Hance) Kuntze}  \index{Staurogyne@\textit{Staurogyne}!concinnula@\textit{concinnula}} 哈哼花\index{哈哼花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Staurogyne+debilis}{\textit{S. debilis} (T.Anderson) C.B.Clarke ex Mill.}  \index{Staurogyne@\textit{Staurogyne}!debilis@\textit{debilis}} 菲律賓哈哼花\index{菲律賓哈哼花} VU
  \end{itemize}
 \item[] \textit{Strobilanthes} 馬藍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+cusia}{\textit{S. cusia} (Ness) Kuntze}  \index{Strobilanthes@\textit{Strobilanthes}!cusia@\textit{cusia}} 馬藍\index{馬藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+flexicaulis}{\textit{S. flexicaulis} Hayata}  \index{Strobilanthes@\textit{Strobilanthes}!flexicaulis@\textit{flexicaulis}} 曲莖馬藍\index{曲莖馬藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+formosana}{\textit{S. formosana} S.Moore}  \index{Strobilanthes@\textit{Strobilanthes}!formosana@\textit{formosana}} 臺灣馬藍\index{臺灣馬藍}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+lanyuensis}{\textit{S. lanyuensis} Seok, C.F.Hsieh \& J.Murata}  \index{Strobilanthes@\textit{Strobilanthes}!lanyuensis@\textit{lanyuensis}} 蘭嶼馬藍\index{蘭嶼馬藍} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+longespicatus}{\textit{S. longespicatus} Hayata}  \index{Strobilanthes@\textit{Strobilanthes}!longespicatus@\textit{longespicatus}} 長穗馬藍\index{長穗馬藍}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+penstemonoides}{\textit{S. penstemonoides} T.Anderson}  \index{Strobilanthes@\textit{Strobilanthes}!penstemonoides@\textit{penstemonoides}} 腺萼馬藍\index{腺萼馬藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+rankanensis}{\textit{S. rankanensis} Hayata}  \index{Strobilanthes@\textit{Strobilanthes}!rankanensis@\textit{rankanensis}} 蘭崁馬藍\index{蘭崁馬藍}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Strobilanthes+wallichii}{\textit{S. wallichii} Nees}  \index{Strobilanthes@\textit{Strobilanthes}!wallichii@\textit{wallichii}} 翅柄馬藍\index{翅柄馬藍} LC
  \end{itemize}
 \item[] \textit{Thunbergia} 鄧伯花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thunbergia+alata}{\textit{T. alata} Bojer ex Sims}  \index{Thunbergia@\textit{Thunbergia}!alata@\textit{alata}} 黑眼花\index{黑眼花} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thunbergia+fragrans}{\textit{T. fragrans} Roxb.}  \index{Thunbergia@\textit{Thunbergia}!fragrans@\textit{fragrans}} 碗花草\index{碗花草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thunbergia+grandiflora}{\textit{T. grandiflora} Roxb.}  \index{Thunbergia@\textit{Thunbergia}!grandiflora@\textit{grandiflora}} 大鄧伯花\index{大鄧伯花} NA $^n$
  \end{itemize}
  \end{itemize}
