
  \begin{itemize}
 \item[] \textit{Actinidia} 獼猴桃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinidia+arguta}{\textit{A. arguta} (Siebold \& Zucc.) Planch. ex Miq.}  \index{Actinidia@\textit{Actinidia}!arguta@\textbf{\textit{arguta}}}  \index{Actinidia@\textit{Actinidia}!tetramera@\textit{tetramera}{\\\noindent(= \textit{Actinidia arguta})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=軟棗獼猴桃&T2_new_value=true&fr=y}}{軟棗獼猴桃(四萼獼猴桃)} \index{軟棗獼猴桃@{\Song{軟棗獼猴桃}}} \index{四萼獼猴桃@{\Song{四萼獼猴桃(=軟棗獼猴桃)}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinidia+callosa+var.+discolor}{\textit{A. callosa} Lindl. var. \textit{discolor} C.F.Liang}  \index{Actinidia@\textit{Actinidia}!callosa@\textit{callosa}!var. discolor@var. \textit{discolor}}  \index{Actinidia@\textit{Actinidia}!rubricaulis@\textit{rubricaulis}{\\\noindent(= \textit{Actinidia callosa} var. \textit{discolor})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅莖獼猴桃&T2_new_value=true&fr=y}}{紅莖獼猴桃}\index{紅莖獼猴桃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinidia+chinensis+var.+setosa}{\textit{A. chinensis} Planch. var. \textit{setosa} H.L.Li}  \index{Actinidia@\textit{Actinidia}!chinensis@\textit{chinensis}!var. setosa@var. \textit{setosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣羊桃&T2_new_value=true&fr=y}}{臺灣羊桃}\index{臺灣羊桃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinidia+latifolia}{\textit{A. latifolia} (Gardn. \& Champ.) Merr.}  \index{Actinidia@\textit{Actinidia}!latifolia@\textit{latifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉獼猴桃&T2_new_value=true&fr=y}}{闊葉獼猴桃}\index{闊葉獼猴桃} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinidia+rufa}{\textit{A. rufa} (Siebold \& Zucc.) Planch. ex Miq.}  \index{Actinidia@\textit{Actinidia}!rufa@\textit{rufa}}  \index{Actinidia@\textit{Actinidia}!callosa@\textit{callosa}{\\\noindent(= \textit{Actinidia rufa})}}   \index{Actinidia@\textit{Actinidia}!callosa@\textit{callosa}!var. ephippioidea@var. \textit{ephippioidea}{\\\noindent(=\textit{Actinidia rufa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺齒獼猴桃&T2_new_value=true&fr=y}}{腺齒獼猴桃(硬齒獼猴桃、駝齒獼猴桃)} \index{腺齒獼猴桃} \index{硬齒獼猴桃@{硬齒獼猴桃(=腺齒獼猴桃)}} \index{駝齒獼猴桃@{駝齒獼猴桃(=腺齒獼猴桃)}} LC
  \end{itemize}
 \item[] \textit{Saurauia} 水冬瓜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saurauia+tristyla+var.+oldhamii}{\textit{S. tristyla} DC. var. \textit{oldhamii} (Hemsl.) Finet \& Gagnep.}  \index{Saurauia@\textit{Saurauia}!tristyla@\textit{tristyla}!var. oldhamii@var. \textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水冬瓜&T2_new_value=true&fr=y}}{水冬瓜}\index{水冬瓜} LC
  \end{itemize}
  \end{itemize}
