
  \begin{itemize}
 \item[] \textit{Sambucus} 接骨木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sambucus+chinensis}{\textit{S. chinensis} Lindl.}  \index{Sambucus@\textit{Sambucus}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冇骨消&T2_new_value=true&fr=y}}{冇骨消}\index{冇骨消} LC
  \end{itemize}
 \item[] \textit{Viburnum} 莢蒾屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+aboricolum}{\textit{V. aboricolum} Hayata}  \index{Viburnum@\textit{Viburnum}!aboricolum@\textit{aboricolum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=著生珊瑚樹&T2_new_value=true&fr=y}}{著生珊瑚樹}\index{著生珊瑚樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+betulifolium}{\textit{V. betulifolium} Batal.}  \index{Viburnum@\textit{Viburnum}!betulifolium@\textit{betulifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樺葉莢蒾&T2_new_value=true&fr=y}}{樺葉莢蒾}\index{樺葉莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+erosum}{\textit{V. erosum} Thunb.}  \index{Viburnum@\textit{Viburnum}!erosum@\textit{erosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=松田氏莢蒾&T2_new_value=true&fr=y}}{松田氏莢蒾}\index{松田氏莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+foetidum+var.+rectangulatum}{\textit{V. foetidum} Wall. var. \textit{rectangulatum} (Graebn.) Rehder}  \index{Viburnum@\textit{Viburnum}!foetidum@\textit{foetidum}!var. rectangulatum@var. \textit{rectangulatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉莢蒾&T2_new_value=true&fr=y}}{狹葉莢蒾}\index{狹葉莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+formosanum}{\textit{V. formosanum} Hayata}  \index{Viburnum@\textit{Viburnum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅子莢蒾&T2_new_value=true&fr=y}}{紅子莢蒾}\index{紅子莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+integrifolium}{\textit{V. integrifolium} Hayata}  \index{Viburnum@\textit{Viburnum}!integrifolium@\textit{integrifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山糯米樹&T2_new_value=true&fr=y}}{玉山糯米樹}\index{玉山糯米樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+japonicum}{\textit{V. japonicum} (Thunb.) Spreng.}  \index{Viburnum@\textit{Viburnum}!japonicum@\textit{japonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本莢蒾&T2_new_value=true&fr=y}}{日本莢蒾}\index{日本莢蒾} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+luzonicum}{\textit{V. luzonicum} Rolfe}  \index{Viburnum@\textit{Viburnum}!luzonicum@\textit{luzonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=呂宋莢蒾&T2_new_value=true&fr=y}}{呂宋莢蒾}\index{呂宋莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+odoratissimum}{\textit{V. odoratissimum} Ker}  \index{Viburnum@\textit{Viburnum}!odoratissimum@\textit{odoratissimum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=珊瑚樹&T2_new_value=true&fr=y}}{珊瑚樹}\index{珊瑚樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+parvifolium}{\textit{V. parvifolium} Hayata}  \index{Viburnum@\textit{Viburnum}!parvifolium@\textit{parvifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉莢蒾&T2_new_value=true&fr=y}}{小葉莢蒾}\index{小葉莢蒾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+plicatum+var.+formosanum}{\textit{V. plicatum} Thunb. var. \textit{formosanum} Y.C.Liu ＆ C.H.Ou}  \index{Viburnum@\textit{Viburnum}!plicatum@\textit{plicatum}!var. formosanum@var. \textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蝴蝶戲珠花&T2_new_value=true&fr=y}}{臺灣蝴蝶戲珠花}\index{臺灣蝴蝶戲珠花}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+propinquum}{\textit{V. propinquum} Hemsl.}  \index{Viburnum@\textit{Viburnum}!propinquum@\textit{propinquum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山莢蒾&T2_new_value=true&fr=y}}{高山莢蒾}\index{高山莢蒾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+sphaerocarpum}{\textit{V. sphaerocarpum} Y.C.Liu \& C.H.Ou}  \index{Viburnum@\textit{Viburnum}!sphaerocarpum@\textit{sphaerocarpum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球果莢蒾&T2_new_value=true&fr=y}}{球果莢蒾}\index{球果莢蒾} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+sympodiale}{\textit{V. sympodiale} Graebn.}  \index{Viburnum@\textit{Viburnum}!sympodiale@\textit{sympodiale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假繡球&T2_new_value=true&fr=y}}{假繡球}\index{假繡球} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+taitoense}{\textit{V. taitoense} Hayata}  \index{Viburnum@\textit{Viburnum}!taitoense@\textit{taitoense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東莢蒾&T2_new_value=true&fr=y}}{臺東莢蒾}\index{臺東莢蒾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Viburnum+urceolatum}{\textit{V. urceolatum} Siebold \& Zucc.}  \index{Viburnum@\textit{Viburnum}!urceolatum@\textit{urceolatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=壺花莢蒾&T2_new_value=true&fr=y}}{壺花莢蒾}\index{壺花莢蒾} LC
  \end{itemize}
  \end{itemize}
