
  \begin{itemize}
 \item[] \textit{Achyranthes} 牛膝屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Achyranthes+aspera+var.+indica}{\textit{A. aspera} L. var. \textit{indica} L.}  \index{Achyranthes@\textit{Achyranthes}!aspera@\textit{aspera}!var. indica@var. \textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度牛膝&T2_new_value=true&fr=y}}{印度牛膝}\index{印度牛膝} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Achyranthes+aspera+var.+rubro-fusca}{\textit{A. aspera} L. var. \textit{rubro-fusca} Hook.f.}  \index{Achyranthes@\textit{Achyranthes}!aspera@\textit{aspera}!var. rubro-fusca@var. \textit{rubro-fusca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣牛膝&T2_new_value=true&fr=y}}{臺灣牛膝}\index{臺灣牛膝} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Achyranthes+bidentata+var.+bidentata}{\textit{A. bidentata} Blume var. \textit{bidentata}}  \index{Achyranthes@\textit{Achyranthes}!bidentata@\textit{bidentata}!var. bidentata@var. \textit{bidentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牛膝&T2_new_value=true&fr=y}}{牛膝}\index{牛膝} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Achyranthes+bidentata+var.+japonica}{\textit{A. bidentata} Blume var. \textit{japonica} Miq.}  \index{Achyranthes@\textit{Achyranthes}!bidentata@\textit{bidentata}!var. japonica@var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本牛膝&T2_new_value=true&fr=y}}{日本牛膝}\index{日本牛膝} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Achyranthes+longifolia}{\textit{A. longifolia} (Makino) Makino}  \index{Achyranthes@\textit{Achyranthes}!longifolia@\textit{longifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柳葉牛膝&T2_new_value=true&fr=y}}{柳葉牛膝}\index{柳葉牛膝} LC
  \end{itemize}
 \item[] \textit{Aerva} 絹毛莧屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aerva+sanguinolenta}{\textit{A. sanguinolenta} Blume}  \index{Aerva@\textit{Aerva}!sanguinolenta@\textit{sanguinolenta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絹毛莧&T2_new_value=true&fr=y}}{絹毛莧}\index{絹毛莧} LC
  \end{itemize}
 \item[] \textit{Alternanthera} 蓮子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alternanthera+bettzickiana}{\textit{A. bettzickiana} (Regel) G.Nicholson}  \index{Alternanthera@\textit{Alternanthera}!bettzickiana@\textit{bettzickiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛蓮子草&T2_new_value=true&fr=y}}{毛蓮子草}\index{毛蓮子草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alternanthera+paronychioides}{\textit{A. paronychioides} A.St.-Hil.}  \index{Alternanthera@\textit{Alternanthera}!paronychioides@\textit{paronychioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匙葉蓮子草&T2_new_value=true&fr=y}}{匙葉蓮子草}\index{匙葉蓮子草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alternanthera+philoxeroides}{\textit{A. philoxeroides} (Mart.) Griseb.}  \index{Alternanthera@\textit{Alternanthera}!philoxeroides@\textit{philoxeroides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=空心蓮子草&T2_new_value=true&fr=y}}{空心蓮子草}\index{空心蓮子草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alternanthera+reineckii}{\textit{A. reineckii} Briquet}  \index{Alternanthera@\textit{Alternanthera}!reineckii@\textit{reineckii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瑞氏蓮子草&T2_new_value=true&fr=y}}{瑞氏蓮子草}\index{瑞氏蓮子草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alternanthera+sessilis}{\textit{A. sessilis} (L.) R.Br.}  \index{Alternanthera@\textit{Alternanthera}!sessilis@\textit{sessilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓮子草&T2_new_value=true&fr=y}}{蓮子草}\index{蓮子草} LC
  \end{itemize}
 \item[] \textit{Amaranthus} 莧屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+caudatus}{\textit{A. caudatus} L.}  \index{Amaranthus@\textit{Amaranthus}!caudatus@\textit{caudatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾穗莧&T2_new_value=true&fr=y}}{尾穗莧}\index{尾穗莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+dubius}{\textit{A. dubius} Mart. ex Thell.}  \index{Amaranthus@\textit{Amaranthus}!dubius@\textit{dubius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假刺莧&T2_new_value=true&fr=y}}{假刺莧}\index{假刺莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+hybridus}{\textit{A. hybridus} L.}  \index{Amaranthus@\textit{Amaranthus}!hybridus@\textit{hybridus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠穗莧&T2_new_value=true&fr=y}}{綠穗莧}\index{綠穗莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+lividus}{\textit{A. lividus} L.}  \index{Amaranthus@\textit{Amaranthus}!lividus@\textit{lividus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹葉野莧菜&T2_new_value=true&fr=y}}{凹葉野莧菜}\index{凹葉野莧菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+patulus}{\textit{A. patulus} Bertol.}  \index{Amaranthus@\textit{Amaranthus}!patulus@\textit{patulus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=青莧&T2_new_value=true&fr=y}}{青莧}\index{青莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+retroflexus}{\textit{A. retroflexus} L.}  \index{Amaranthus@\textit{Amaranthus}!retroflexus@\textit{retroflexus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=反刺莧&T2_new_value=true&fr=y}}{反刺莧}\index{反刺莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+spinosus}{\textit{A. spinosus} L.}  \index{Amaranthus@\textit{Amaranthus}!spinosus@\textit{spinosus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺莧&T2_new_value=true&fr=y}}{刺莧}\index{刺莧} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amaranthus+viridis}{\textit{A. viridis} L.}  \index{Amaranthus@\textit{Amaranthus}!viridis@\textit{viridis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野莧菜&T2_new_value=true&fr=y}}{野莧菜}\index{野莧菜} NA$^n$
  \end{itemize}
 \item[] \textit{Atriplex} 濱藜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Atriplex+maximowicziana}{\textit{A. maximowicziana} Makino}  \index{Atriplex@\textit{Atriplex}!maximowicziana@\textit{maximowicziana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬氏濱藜&T2_new_value=true&fr=y}}{馬氏濱藜}\index{馬氏濱藜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Atriplex+nummularia}{\textit{A. nummularia} Lindl.}  \index{Atriplex@\textit{Atriplex}!nummularia@\textit{nummularia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣濱藜&T2_new_value=true&fr=y}}{臺灣濱藜}\index{臺灣濱藜} DD
  \end{itemize}
 \item[] \textit{Celosia} 青葙屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celosia+argentea}{\textit{C. argentea} L.}  \index{Celosia@\textit{Celosia}!argentea@\textit{argentea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=青葙&T2_new_value=true&fr=y}}{青葙}\index{青葙} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celosia+taitoensis}{\textit{C. taitoensis} Hayata}  \index{Celosia@\textit{Celosia}!taitoensis@\textit{taitoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東青葙&T2_new_value=true&fr=y}}{臺東青葙}\index{臺東青葙}\# DD
  \end{itemize}
 \item[] \textit{Chenopodium} 藜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+acuminatum+subsp.+virgatum}{\textit{C. acuminatum} Willd. subsp. \textit{virgatum} (Thunb.) Kitam.}  \index{Chenopodium@\textit{Chenopodium}!acuminatum@\textit{acuminatum}!subsp. virgatum@subsp. \textit{virgatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉藜&T2_new_value=true&fr=y}}{變葉藜}\index{變葉藜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+album}{\textit{C. album} L.}  \index{Chenopodium@\textit{Chenopodium}!album@\textit{album}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藜&T2_new_value=true&fr=y}}{藜}\index{藜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+ambrosioides}{\textit{C. ambrosioides} L.}  \index{Chenopodium@\textit{Chenopodium}!ambrosioides@\textit{ambrosioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭杏&T2_new_value=true&fr=y}}{臭杏}\index{臭杏} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+formosanum}{\textit{C. formosanum} Koidz.}  \index{Chenopodium@\textit{Chenopodium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣藜&T2_new_value=true&fr=y}}{臺灣藜}\index{臺灣藜}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+glaucum}{\textit{C. glaucum} L.}  \index{Chenopodium@\textit{Chenopodium}!glaucum@\textit{glaucum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰綠藜&T2_new_value=true&fr=y}}{灰綠藜}\index{灰綠藜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chenopodium+serotinum}{\textit{C. serotinum} L.}  \index{Chenopodium@\textit{Chenopodium}!serotinum@\textit{serotinum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉藜&T2_new_value=true&fr=y}}{小葉藜}\index{小葉藜} LC
  \end{itemize}
 \item[] \textit{Cyathula} 川牛膝屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyathula+prostrata}{\textit{C. prostrata} (L.) Blume}  \index{Cyathula@\textit{Cyathula}!prostrata@\textit{prostrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假川牛膝&T2_new_value=true&fr=y}}{假川牛膝}\index{假川牛膝} LC
  \end{itemize}
 \item[] \textit{Deeringia} 漿果莧屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deeringia+amaranthoides}{\textit{D. amaranthoides} (Lam.) Merr.}  \index{Deeringia@\textit{Deeringia}!amaranthoides@\textit{amaranthoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=漿果莧&T2_new_value=true&fr=y}}{漿果莧}\index{漿果莧} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deeringia+polysperma}{\textit{D. polysperma} (Roxb.) Miq.}  \index{Deeringia@\textit{Deeringia}!polysperma@\textit{polysperma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多子漿果莧&T2_new_value=true&fr=y}}{多子漿果莧}\index{多子漿果莧} LC
  \end{itemize}
 \item[] \textit{Digera} 瘤果莧屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Digera+muricata}{\textit{D. muricata} (L.) Mart.}  \index{Digera@\textit{Digera}!muricata@\textit{muricata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瘤果莧&T2_new_value=true&fr=y}}{瘤果莧}\index{瘤果莧} NA$^n$
  \end{itemize}
 \item[] \textit{Gomphrena} 千日紅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gomphrena+celosioides}{\textit{G. celosioides} Mart.}  \index{Gomphrena@\textit{Gomphrena}!celosioides@\textit{celosioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假千日紅&T2_new_value=true&fr=y}}{假千日紅}\index{假千日紅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gomphrena+serrata}{\textit{G. serrata} L.}  \index{Gomphrena@\textit{Gomphrena}!serrata@\textit{serrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短穗假千日紅&T2_new_value=true&fr=y}}{短穗假千日紅}\index{短穗假千日紅} NA$^n$
  \end{itemize}
 \item[] \textit{Philoxerus} 安旱草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Philoxerus+wrightii}{\textit{P. wrightii} Hook.f.}  \index{Philoxerus@\textit{Philoxerus}!wrightii@\textbf{\textit{wrightii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=安旱草&T2_new_value=true&fr=y}}{安旱草}\index{安旱草@{\Song{安旱草}}} VU
  \end{itemize}
 \item[] \textit{Pupalia} 小花鉤牛膝屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pupalia+micrantha}{\textit{P. micrantha} Hauman}  \index{Pupalia@\textit{Pupalia}!micrantha@\textit{micrantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花鉤牛膝&T2_new_value=true&fr=y}}{小花鉤牛膝}\index{小花鉤牛膝} NA$^n$
  \end{itemize}
 \item[] \textit{Suaeda} 鹼蓬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Suaeda+maritima}{\textit{S. maritima} (L.) Dum.}  \index{Suaeda@\textit{Suaeda}!maritima@\textit{maritima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裸花鹼蓬&T2_new_value=true&fr=y}}{裸花鹼蓬}\index{裸花鹼蓬} LC
  \end{itemize}
  \end{itemize}
