
  \begin{itemize}
 \item[] \textit{Buchanania} 山羨子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Buchanania+arborescens}{\textit{B. arborescens} Blume}  \index{Buchanania@\textit{Buchanania}!arborescens@\textit{arborescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山檨子&T2_new_value=true&fr=y}}{山檨子}\index{山檨子} NT
  \end{itemize}
 \item[] \textit{Mangifera} 芒果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mangifera+indica}{\textit{M. indica} L.}  \index{Mangifera@\textit{Mangifera}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=檬果&T2_new_value=true&fr=y}}{檬果}\index{檬果} NA$^n$
  \end{itemize}
 \item[] \textit{Pistacia} 黃連木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pistacia+chinensis}{\textit{P. chinensis} Bunge}  \index{Pistacia@\textit{Pistacia}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃連木&T2_new_value=true&fr=y}}{黃連木}\index{黃連木} LC
  \end{itemize}
 \item[] \textit{Rhus} 漆樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+ambigua}{\textit{R. ambigua} Lav. ex Dippel}  \index{Rhus@\textit{Rhus}!ambigua@\textit{ambigua}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣藤漆&T2_new_value=true&fr=y}}{臺灣藤漆}\index{臺灣藤漆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+hypoleuca}{\textit{R. hypoleuca} Champ. ex Benth.}  \index{Rhus@\textit{Rhus}!hypoleuca@\textbf{\textit{hypoleuca}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白漆&T2_new_value=true&fr=y}}{裏白漆}\index{裏白漆@{\Song{裏白漆}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+javanica+var.+roxburghiana}{\textit{R. javanica} L. var. \textit{roxburghiana} (DC.) Rehder \& E.H.Wils.}  \index{Rhus@\textit{Rhus}!javanica@\textit{javanica}!var. roxburghiana@var. \textit{roxburghiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羅氏鹽膚木&T2_new_value=true&fr=y}}{羅氏鹽膚木}\index{羅氏鹽膚木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+succedanea+var.+dumoutieri}{\textit{R. succedanea} L. var. \textit{dumoutieri} Kudo \& Matsura}  \index{Rhus@\textit{Rhus}!succedanea@\textit{succedanea}!var. dumoutieri@var. \textit{dumoutieri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=安南漆&T2_new_value=true&fr=y}}{安南漆}\index{安南漆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+succedanea+var.+succedanea}{\textit{R. succedanea} L. var. \textit{succedanea}}  \index{Rhus@\textit{Rhus}!succedanea@\textit{succedanea}!var. succedanea@var. \textit{succedanea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木蠟樹&T2_new_value=true&fr=y}}{木蠟樹}\index{木蠟樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhus+sylvestris}{\textit{R. sylvestris} Siebold \& Zucc.}  \index{Rhus@\textit{Rhus}!sylvestris@\textit{sylvestris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野漆樹&T2_new_value=true&fr=y}}{野漆樹}\index{野漆樹} NT
  \end{itemize}
 \item[] \textit{Schinus} 巴西胡椒木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schinus+terebinthifolia}{\textit{S. terebinthifolia} Raddi}  \index{Schinus@\textit{Schinus}!terebinthifolia@\textit{terebinthifolia}}  \index{Schinus@\textit{Schinus}!terebinthifolius@\textit{terebinthifolius}{\\\noindent(= \textit{Schinus terebinthifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巴西胡椒木&T2_new_value=true&fr=y}}{巴西胡椒木}\index{巴西胡椒木} NA$^n$
  \end{itemize}
 \item[] \textit{Semecarpus} 大果漆樹
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Semecarpus+cuneiformis}{\textit{S. cuneiformis} Blanco}  \index{Semecarpus@\textit{Semecarpus}!cuneiformis@\textbf{\textit{cuneiformis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍葉大果漆&T2_new_value=true&fr=y}}{鈍葉大果漆}\index{鈍葉大果漆@{\Song{鈍葉大果漆}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Semecarpus+gigantifolia}{\textit{S. gigantifolia} Vidal}  \index{Semecarpus@\textit{Semecarpus}!gigantifolia@\textit{gigantifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東漆樹&T2_new_value=true&fr=y}}{臺東漆樹}\index{臺東漆樹} NT
  \end{itemize}
  \end{itemize}
