
  \begin{itemize}
 \item[] \textit{Angelica} 當歸屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+dahurica+var.+formosana}{\textit{A. dahurica} (Hoffm.) Benth. \& Hook.f. ex Franch. \& Sav. var. \textit{formosana} (H.Boissieu) K.Y.Yen. et al.}  \index{Angelica@\textit{Angelica}!dahurica@\textit{dahurica}!var. formosana@var. \textit{formosana}} 野當歸\index{野當歸}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+hirsutiflora}{\textit{A. hirsutiflora} T.S.Liu, C.Y.Chao \& T.I.Chuang}  \index{Angelica@\textit{Angelica}!hirsutiflora@\textit{hirsutiflora}} 濱當歸\index{濱當歸}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+morii}{\textit{A. morii} Hayata}  \index{Angelica@\textit{Angelica}!morii@\textit{morii}} 森氏當歸\index{森氏當歸}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+morrisonicola+var.+morrisonicola}{\textit{A. morrisonicola} Hayata var. \textit{morrisonicola}}  \index{Angelica@\textit{Angelica}!morrisonicola@\textit{morrisonicola}!var. morrisonicola@var. \textit{morrisonicola}} 玉山當歸\index{玉山當歸}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+morrisonicola+var.+nanhutashanensis}{\textit{A. morrisonicola} Hayata var. \textit{nanhutashanensis} T.S.Liu, C.Y.Chao \& T.I.Chuang}  \index{Angelica@\textit{Angelica}!morrisonicola@\textit{morrisonicola}!var. nanhutashanensis@var. \textit{nanhutashanensis}} 南湖當歸\index{南湖當歸}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Angelica+tarokoensis}{\textit{A. tarokoensis} Hayata}  \index{Angelica@\textit{Angelica}!tarokoensis@\textit{tarokoensis}} 太魯閣當歸\index{太魯閣當歸}\# EN
  \end{itemize}
 \item[] \textit{Apium} 芹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Apium+leptophyllum}{\textit{A. leptophyllum} (Pers.) F.Muell ex Benth.}  \index{Apium@\textit{Apium}!leptophyllum@\textit{leptophyllum}} 薄葉芹菜\index{薄葉芹菜} NA $^n$
  \end{itemize}
 \item[] \textit{Bupleurum} 柴胡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bupleurum+kaoi}{\textit{B. kaoi} T.S.Liu, C.Y.Chao \& T.I.Chuang}  \index{Bupleurum@\textit{Bupleurum}!kaoi@\textit{kaoi}} 高氏柴胡\index{高氏柴胡}\# EN
  \end{itemize}
 \item[] \textit{Centella} 雷公根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Centella+asiatica}{\textit{C. asiatica} (L.) Urb.}  \index{Centella@\textit{Centella}!asiatica@\textit{asiatica}} 雷公根\index{雷公根} LC
  \end{itemize}
 \item[] \textit{Chaerophyllum} 細葉芹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chaerophyllum+involucratum}{\textit{C. involucratum} (Hayata) K.F.Chung}  \index{Chaerophyllum@\textit{Chaerophyllum}!involucratum@\textit{involucratum}}  \index{Oreomyrrhis@\textit{Oreomyrrhis}!involucrata@\textit{involucrata}{\\\noindent(= \textit{Chaerophyllum involucratum})}} 山薰香\index{山薰香}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chaerophyllum+nanhuense}{\textit{C. nanhuense} (Chih H.Chen \& J.C.Wang) K.F.Chung}  \index{Chaerophyllum@\textit{Chaerophyllum}!nanhuense@\textit{nanhuense}}  \index{Oreomyrrhis@\textit{Oreomyrrhis}!nanhuensis@\textit{nanhuensis}{\\\noindent(= \textit{Chaerophyllum nanhuense})}} 南湖山薰香\index{南湖山薰香}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chaerophyllum+taiwanianum}{\textit{C. taiwanianum} (Masam.) K.F.Chung}  \index{Chaerophyllum@\textit{Chaerophyllum}!taiwanianum@\textit{taiwanianum}}  \index{Oreomyrrhis@\textit{Oreomyrrhis}!taiwaniana@\textit{taiwaniana}{\\\noindent(= \textit{Chaerophyllum taiwanianum})}} 臺灣山薰香\index{臺灣山薰香}\# VU
  \end{itemize}
 \item[] \textit{Cnidium} 芎窮屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cnidium+monnieri+var.+formosanum}{\textit{C. monnieri} (L.) Gusson var. \textit{formosanum} (Yabe) Kitag.}  \index{Cnidium@\textit{Cnidium}!monnieri@\textit{monnieri}!var. formosanum@var. \textit{formosanum}} 臺灣芎窮\index{臺灣芎窮}\# LC
  \end{itemize}
 \item[] \textit{Conioselinum} 彎柱芎屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conioselinum+morrisonense}{\textit{C. morrisonense} Hayata}  \index{Conioselinum@\textit{Conioselinum}!morrisonense@\textit{morrisonense}} 玉山彎柱芎\index{玉山彎柱芎}\# LC
  \end{itemize}
 \item[] \textit{Cryptotaenia} 鴨兒芹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptotaenia+japonica}{\textit{C. japonica} Hassk.}  \index{Cryptotaenia@\textit{Cryptotaenia}!japonica@\textit{japonica}} 鴨兒芹\index{鴨兒芹} LC
  \end{itemize}
 \item[] \textit{Eryngium} 刺芹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eryngium+foetidum}{\textit{E. foetidum} L.}  \index{Eryngium@\textit{Eryngium}!foetidum@\textit{foetidum}} 刺芫荽\index{刺芫荽} NA $^n$
  \end{itemize}
 \item[] \textit{Foeniculum} 茴香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Foeniculum+vulgare}{\textit{F. vulgare} Mill.}  \index{Foeniculum@\textit{Foeniculum}!vulgare@\textit{vulgare}} 茴香\index{茴香} NA $^n$
  \end{itemize}
 \item[] \textit{Glehnia} 濱防風屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glehnia+littoralis}{\textit{G. littoralis} F.Schmidt ex Miq.}  \index{Glehnia@\textit{Glehnia}!littoralis@\textit{littoralis}} 濱防風\index{濱防風} LC
  \end{itemize}
 \item[] \textit{Oenanthe} 水芹菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenanthe+javanica}{\textit{O. javanica} (Blume) DC.}  \index{Oenanthe@\textit{Oenanthe}!javanica@\textit{javanica}} 水芹菜\index{水芹菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenanthe+pterocaulon}{\textit{O. pterocaulon} T.S.Liu, C.Y.Chao \& T.I.Chuang}  \index{Oenanthe@\textit{Oenanthe}!pterocaulon@\textit{pterocaulon}} 翼莖水芹菜\index{翼莖水芹菜}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenanthe+thomsonii}{\textit{O. thomsonii} C.B.Clarke}  \index{Oenanthe@\textit{Oenanthe}!thomsonii@\textit{thomsonii}} 多裂葉水芹菜\index{多裂葉水芹菜} LC
  \end{itemize}
 \item[] \textit{Osmorhiza} 臭根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osmorhiza+aristata}{\textit{O. aristata} (Thunb.) Makino \& Yabe}  \index{Osmorhiza@\textit{Osmorhiza}!aristata@\textit{aristata}} 臭根\index{臭根} LC
  \end{itemize}
 \item[] \textit{Peucedanum} 前胡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peucedanum+formosanum}{\textit{P. formosanum} Hayata}  \index{Peucedanum@\textit{Peucedanum}!formosanum@\textit{formosanum}} 臺灣前胡\index{臺灣前胡}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peucedanum+japonicum}{\textit{P. japonicum} Thunb.}  \index{Peucedanum@\textit{Peucedanum}!japonicum@\textit{japonicum}} 日本前胡\index{日本前胡} LC
  \end{itemize}
 \item[] \textit{Pimpinella} 茴芹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pimpinella+diversifolia}{\textit{P. diversifolia} DC.}  \index{Pimpinella@\textit{Pimpinella}!diversifolia@\textit{diversifolia}} 三葉茴香\index{三葉茴香} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pimpinella+niitakayamensis}{\textit{P. niitakayamensis} Hayata}  \index{Pimpinella@\textit{Pimpinella}!niitakayamensis@\textit{niitakayamensis}} 玉山茴香\index{玉山茴香}\# LC
  \end{itemize}
 \item[] \textit{Sanicula} 山芹菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sanicula+lamelligera}{\textit{S. lamelligera} Hance}  \index{Sanicula@\textit{Sanicula}!lamelligera@\textit{lamelligera}} 三葉山芹菜\index{三葉山芹菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sanicula+petagnioides}{\textit{S. petagnioides} Hayata}  \index{Sanicula@\textit{Sanicula}!petagnioides@\textit{petagnioides}} 五葉山芹菜\index{五葉山芹菜}\# LC
  \end{itemize}
 \item[] \textit{Sium} 零餘子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sium+suave}{\textit{S. suave} Walt.}  \index{Sium@\textit{Sium}!suave@\textit{suave}} 細葉零餘子\index{細葉零餘子} CR
  \end{itemize}
 \item[] \textit{Torilis} 竊衣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torilis+japonica}{\textit{T. japonica} (Houtt.) DC.}  \index{Torilis@\textit{Torilis}!japonica@\textit{japonica}} 竊衣\index{竊衣} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torilis+scabra}{\textit{T. scabra} (Thunb.) DC.}  \index{Torilis@\textit{Torilis}!scabra@\textit{scabra}} 紫花竊衣\index{紫花竊衣} LC
  \end{itemize}
  \end{itemize}
