
  \begin{itemize}
 \item[] \textit{Alstonia} 雞骨常山屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alstonia+scholaris}{\textit{A. scholaris} (L.) R.Br.}  \index{Alstonia@\textit{Alstonia}!scholaris@\textit{scholaris}} 黑板樹\index{黑板樹} NA $^n$
  \end{itemize}
 \item[] \textit{Alyxia} 念珠藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alyxia+sibuyanensis}{\textit{A. sibuyanensis} Elmer}  \index{Alyxia@\textit{Alyxia}!sibuyanensis@\textit{sibuyanensis}} 蘭嶼念珠藤\index{蘭嶼念珠藤} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alyxia+sinensis}{\textit{A. sinensis} Champ. ex Benth.}  \index{Alyxia@\textit{Alyxia}!sinensis@\textit{sinensis}} 中國念珠藤\index{中國念珠藤} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alyxia+taiwanensis}{\textit{A. taiwanensis} S.Y.Lu \& Yuen P.Yang}  \index{Alyxia@\textit{Alyxia}!taiwanensis@\textit{taiwanensis}} 臺灣念珠藤\index{臺灣念珠藤}\# NT
  \end{itemize}
 \item[] \textit{Anodendron} 錦蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anodendron+affine}{\textit{A. affine} (Hook. \& Arn.) Druce}  \index{Anodendron@\textit{Anodendron}!affine@\textit{affine}} 小錦蘭\index{小錦蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anodendron+benthamiana}{\textit{A. benthamiana} Hemsl.}  \index{Anodendron@\textit{Anodendron}!benthamiana@\textit{benthamiana}} 大錦蘭\index{大錦蘭}\# LC
  \end{itemize}
 \item[] \textit{Asclepias} 尖尾鳳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Asclepias+curassavica}{\textit{A. curassavica} L.}  \index{Asclepias@\textit{Asclepias}!curassavica@\textit{curassavica}} 馬利筋\index{馬利筋} NA $^n$
  \end{itemize}
 \item[] \textit{Catharanthus} 長春花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Catharanthus+roseus}{\textit{C. roseus} (L.) G.Don}  \index{Catharanthus@\textit{Catharanthus}!roseus@\textit{roseus}} 長春花\index{長春花} NA $^n$
  \end{itemize}
 \item[] \textit{Cerbera} 海檬果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerbera+manghas}{\textit{C. manghas} L.}  \index{Cerbera@\textit{Cerbera}!manghas@\textit{manghas}} 海檬果\index{海檬果} LC
  \end{itemize}
 \item[] \textit{Cryptolepis} 隱鱗藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptolepis+sinensis}{\textit{C. sinensis} (Lour.) Merr.}  \index{Cryptolepis@\textit{Cryptolepis}!sinensis@\textit{sinensis}} 隱鱗藤\index{隱鱗藤} LC
  \end{itemize}
 \item[] \textit{Cynanchum} 牛皮消屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynanchum+atratum}{\textit{C. atratum} Bunge}  \index{Cynanchum@\textit{Cynanchum}!atratum@\textit{atratum}} 牛皮消\index{牛皮消} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynanchum+boudieri}{\textit{C. boudieri} H.Lév. \& Vaniot}  \index{Cynanchum@\textit{Cynanchum}!boudieri@\textit{boudieri}} 薄葉牛皮消\index{薄葉牛皮消} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynanchum+formosanum}{\textit{C. formosanum} (Maxim.) Hemsl. ex Forbes \& Hemsl.}  \index{Cynanchum@\textit{Cynanchum}!formosanum@\textit{formosanum}} 臺灣牛皮消\index{臺灣牛皮消}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynanchum+lanhsuense}{\textit{C. lanhsuense} T.Yamaz.}  \index{Cynanchum@\textit{Cynanchum}!lanhsuense@\textit{lanhsuense}} 蘭嶼牛皮消\index{蘭嶼牛皮消}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynanchum+mooreanum}{\textit{C. mooreanum} Hemsl.}  \index{Cynanchum@\textit{Cynanchum}!mooreanum@\textit{mooreanum}} 毛白前\index{毛白前} NT
  \end{itemize}
 \item[] \textit{Dischidia} 風不動屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dischidia+formosana}{\textit{D. formosana} Maxim.}  \index{Dischidia@\textit{Dischidia}!formosana@\textit{formosana}} 風不動\index{風不動}\# LC
  \end{itemize}
 \item[] \textit{Dregea} 華他卡藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dregea+volubilis}{\textit{D. volubilis} (L.f.) Benth.}  \index{Dregea@\textit{Dregea}!volubilis@\textit{volubilis}} 華他卡藤\index{華他卡藤} LC
  \end{itemize}
 \item[] \textit{Ecdysanthera} 酸藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ecdysanthera+rosea}{\textit{E. rosea} Hook. \& Arn.}  \index{Ecdysanthera@\textit{Ecdysanthera}!rosea@\textit{rosea}} 酸藤\index{酸藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ecdysanthera+utilis}{\textit{E. utilis} Hayata \& Kawak.}  \index{Ecdysanthera@\textit{Ecdysanthera}!utilis@\textit{utilis}} 乳藤\index{乳藤} LC
  \end{itemize}
 \item[] \textit{Gymnema} 武靴藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gymnema+sylvestre}{\textit{G. sylvestre} (Retz.) Schultes}  \index{Gymnema@\textit{Gymnema}!sylvestre@\textit{sylvestre}} 武靴藤\index{武靴藤} LC
  \end{itemize}
 \item[] \textit{Heterostemma} 布朗藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Heterostemma+brownii}{\textit{H. brownii} Hayata}  \index{Heterostemma@\textit{Heterostemma}!brownii@\textit{brownii}} 布朗藤\index{布朗藤}\# LC
  \end{itemize}
 \item[] \textit{Holarrhena} 止瀉木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Holarrhena+pubescens}{\textit{H. pubescens} Wall. ex G.Don}  \index{Holarrhena@\textit{Holarrhena}!pubescens@\textit{pubescens}} 止瀉木\index{止瀉木} DD
  \end{itemize}
 \item[] \textit{Hoya} 毬蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hoya+carnosa}{\textit{H. carnosa} (L.f.) R.Br.}  \index{Hoya@\textit{Hoya}!carnosa@\textit{carnosa}} 毬蘭\index{毬蘭} LC
  \end{itemize}
 \item[] \textit{Jasminanthes} 舌瓣花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Jasminanthes+mucronata}{\textit{J. mucronata} (Blanco) W.D.Stevens \& P.T.Li}  \index{Jasminanthes@\textit{Jasminanthes}!mucronata@\textit{mucronata}} 舌瓣花\index{舌瓣花} VU
  \end{itemize}
 \item[] \textit{Marsdenia} 牛彌菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Marsdenia+formosana}{\textit{M. formosana} Masam.}  \index{Marsdenia@\textit{Marsdenia}!formosana@\textit{formosana}} 臺灣牛彌菜\index{臺灣牛彌菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Marsdenia+tinctoria}{\textit{M. tinctoria} R.Br.}  \index{Marsdenia@\textit{Marsdenia}!tinctoria@\textit{tinctoria}} 絨毛芙蓉蘭\index{絨毛芙蓉蘭} LC
  \end{itemize}
 \item[] \textit{Melodinus} 山橙屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melodinus+angustifolius}{\textit{M. angustifolius} Hayata}  \index{Melodinus@\textit{Melodinus}!angustifolius@\textit{angustifolius}} 山橙\index{山橙}\# DD
  \end{itemize}
 \item[] \textit{Parsonia} 同心結屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parsonia+laevigata}{\textit{P. laevigata} (Moon) Alston}  \index{Parsonia@\textit{Parsonia}!laevigata@\textit{laevigata}} 爬森藤\index{爬森藤} LC
  \end{itemize}
 \item[] \textit{Rauvolfia} 蘿芙木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rauvolfia+tetraphylla}{\textit{R. tetraphylla} L.}  \index{Rauvolfia@\textit{Rauvolfia}!tetraphylla@\textit{tetraphylla}} 四葉蘿芙木\index{四葉蘿芙木} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rauvolfia+verticillata}{\textit{R. verticillata} (Lour.) Baill.}  \index{Rauvolfia@\textit{Rauvolfia}!verticillata@\textit{verticillata}} 蘿芙木\index{蘿芙木} LC
  \end{itemize}
 \item[] \textit{Tabernaemontana} 馬蹄花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tabernaemontana+pandacaqui}{\textit{T. pandacaqui} Poir.}  \index{Tabernaemontana@\textit{Tabernaemontana}!pandacaqui@\textit{pandacaqui}} 南洋馬蹄花\index{南洋馬蹄花} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tabernaemontana+subglobosa}{\textit{T. subglobosa} Merr.}  \index{Tabernaemontana@\textit{Tabernaemontana}!subglobosa@\textit{subglobosa}} 蘭嶼馬蹄花\index{蘭嶼馬蹄花} NT
  \end{itemize}
 \item[] \textit{Telosma} 夜香花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Telosma+pallida}{\textit{T. pallida} (Roxb.) Craib}  \index{Telosma@\textit{Telosma}!pallida@\textit{pallida}} 夜香花\index{夜香花} CR
  \end{itemize}
 \item[] \textit{Trachelospermum} 絡石屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trachelospermum+formosanum}{\textit{T. formosanum} Y.C.Liu \& C.H.Ou}  \index{Trachelospermum@\textit{Trachelospermum}!formosanum@\textit{formosanum}} 臺灣絡石\index{臺灣絡石}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trachelospermum+gracilipes}{\textit{T. gracilipes} Hook.f.}  \index{Trachelospermum@\textit{Trachelospermum}!gracilipes@\textit{gracilipes}} 細梗絡石\index{細梗絡石} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trachelospermum+jasminoides}{\textit{T. jasminoides} (Lindl.) Lemaire}  \index{Trachelospermum@\textit{Trachelospermum}!jasminoides@\textit{jasminoides}} 絡石\index{絡石} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trachelospermum+lanyuense}{\textit{T. lanyuense} C.E.Chang}  \index{Trachelospermum@\textit{Trachelospermum}!lanyuense@\textit{lanyuense}} 蘭嶼絡石\index{蘭嶼絡石}\# LC
  \end{itemize}
 \item[] \textit{Tylophora} 歐蔓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+lanyuensis}{\textit{T. lanyuensis} Y.C.Liu \& F.Y.Lu}  \index{Tylophora@\textit{Tylophora}!lanyuensis@\textit{lanyuensis}} 蘭嶼鷗蔓\index{蘭嶼鷗蔓}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+lui}{\textit{T. lui} Y.H.Tseng \& C.T.Chao}  \index{Tylophora@\textit{Tylophora}!lui@\textit{lui}} 呂氏鷗蔓\index{呂氏鷗蔓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+oshimae}{\textit{T. oshimae} Hayata}  \index{Tylophora@\textit{Tylophora}!oshimae@\textit{oshimae}} 疏花鷗蔓\index{疏花鷗蔓}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+ovata}{\textit{T. ovata} (Lindl.) Hook. ex Steud.}  \index{Tylophora@\textit{Tylophora}!ovata@\textit{ovata}} 鷗蔓\index{鷗蔓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+sui}{\textit{T. sui} Y.H.Tseng \& C.T.Chao}  \index{Tylophora@\textit{Tylophora}!sui@\textit{sui}} 蘇氏鷗蔓\index{蘇氏鷗蔓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tylophora+taiwanensis}{\textit{T. taiwanensis} Hatus.}  \index{Tylophora@\textit{Tylophora}!taiwanensis@\textit{taiwanensis}} 臺灣鷗蔓\index{臺灣鷗蔓}\# NT
  \end{itemize}
  \end{itemize}
