
  \begin{itemize}
 \item[] \textit{Ilex} 冬青屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+arisanensis}{\textit{I. arisanensis} Yamam.}  \index{Ilex@\textit{Ilex}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山冬青&T2_new_value=true&fr=y}}{阿里山冬青}\index{阿里山冬青}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+asprella}{\textit{I. asprella} (Hook. \& Arn.) Champ.}  \index{Ilex@\textit{Ilex}!asprella@\textit{asprella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=燈稱花&T2_new_value=true&fr=y}}{燈稱花}\index{燈稱花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+bioritsensis}{\textit{I. bioritsensis} Hayata}  \index{Ilex@\textit{Ilex}!bioritsensis@\textit{bioritsensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苗栗冬青&T2_new_value=true&fr=y}}{苗栗冬青}\index{苗栗冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+cochinchinensis}{\textit{I. cochinchinensis} (Lour.) Loes.}  \index{Ilex@\textit{Ilex}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=革葉冬青&T2_new_value=true&fr=y}}{革葉冬青}\index{革葉冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+crenata}{\textit{I. crenata} Thunb.}  \index{Ilex@\textit{Ilex}!crenata@\textit{crenata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假黃楊&T2_new_value=true&fr=y}}{假黃楊}\index{假黃楊} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+ficoidea}{\textit{I. ficoidea} Hemsl.}  \index{Ilex@\textit{Ilex}!ficoidea@\textit{ficoidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣糊樗&T2_new_value=true&fr=y}}{臺灣糊樗}\index{臺灣糊樗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+formosana}{\textit{I. formosana} Maxim.}  \index{Ilex@\textit{Ilex}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=糊樗&T2_new_value=true&fr=y}}{糊樗}\index{糊樗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+goshiensis}{\textit{I. goshiensis} Hayata}  \index{Ilex@\textit{Ilex}!goshiensis@\textit{goshiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉冬青&T2_new_value=true&fr=y}}{圓葉冬青}\index{圓葉冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+hayataiana}{\textit{I. hayataiana} Loes.}  \index{Ilex@\textit{Ilex}!hayataiana@\textit{hayataiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏冬青&T2_new_value=true&fr=y}}{早田氏冬青}\index{早田氏冬青}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+integra}{\textit{I. integra} Thunb.}  \index{Ilex@\textit{Ilex}!integra@\textbf{\textit{integra}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全緣葉冬青&T2_new_value=true&fr=y}}{全緣葉冬青}\index{全緣葉冬青@{\Song{全緣葉冬青}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+kusanoi}{\textit{I. kusanoi} Hayata}  \index{Ilex@\textit{Ilex}!kusanoi@\textit{kusanoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=草野氏冬青&T2_new_value=true&fr=y}}{草野氏冬青}\index{草野氏冬青} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+lonicerifolia+var.+lonicerifolia}{\textit{I. lonicerifolia} Hayata var. \textit{lonicerifolia}}  \index{Ilex@\textit{Ilex}!lonicerifolia@\textit{lonicerifolia}!var. lonicerifolia@var. \textit{lonicerifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=忍冬葉冬青&T2_new_value=true&fr=y}}{忍冬葉冬青}\index{忍冬葉冬青}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+lonicerifolia+var.+matsudai}{\textit{I. lonicerifolia} Hayata var. \textit{matsudai} Yamam.}  \index{Ilex@\textit{Ilex}!lonicerifolia@\textit{lonicerifolia}!var. matsudai@var. \textit{matsudai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=松田氏冬青&T2_new_value=true&fr=y}}{松田氏冬青}\index{松田氏冬青}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+maximowicziana}{\textit{I. maximowicziana} Loes.}  \index{Ilex@\textit{Ilex}!maximowicziana@\textit{maximowicziana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=倒卵葉冬青&T2_new_value=true&fr=y}}{倒卵葉冬青}\index{倒卵葉冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+micrococca}{\textit{I. micrococca} Maxim.}  \index{Ilex@\textit{Ilex}!micrococca@\textit{micrococca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=朱紅水木&T2_new_value=true&fr=y}}{朱紅水木}\index{朱紅水木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+pedunculosa}{\textit{I. pedunculosa} Miq.}  \index{Ilex@\textit{Ilex}!pedunculosa@\textit{pedunculosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刻脈冬青&T2_new_value=true&fr=y}}{刻脈冬青}\index{刻脈冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+pubescens}{\textit{I. pubescens} Hook. \& Arn.}  \index{Ilex@\textit{Ilex}!pubescens@\textit{pubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密毛假黃楊&T2_new_value=true&fr=y}}{密毛假黃楊}\index{密毛假黃楊} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+rarasanensis}{\textit{I. rarasanensis} Sasaki}  \index{Ilex@\textit{Ilex}!rarasanensis@\textit{rarasanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=拉拉山冬青&T2_new_value=true&fr=y}}{拉拉山冬青}\index{拉拉山冬青}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+rotunda}{\textit{I. rotunda} Thunb.}  \index{Ilex@\textit{Ilex}!rotunda@\textit{rotunda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐵冬青&T2_new_value=true&fr=y}}{鐵冬青}\index{鐵冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+sugerokii+var.+brevipedunculata}{\textit{I. sugerokii} Maxim. var. \textit{brevipedunculata} (Maxim.) S.Y.Hu}  \index{Ilex@\textit{Ilex}!sugerokii@\textit{sugerokii}!var. brevipedunculata@var. \textit{brevipedunculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太平山冬青&T2_new_value=true&fr=y}}{太平山冬青}\index{太平山冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+suzukii}{\textit{I. suzukii} S.Y.Hu}  \index{Ilex@\textit{Ilex}!suzukii@\textit{suzukii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈴木氏冬青&T2_new_value=true&fr=y}}{鈴木氏冬青}\index{鈴木氏冬青}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+taiwanensis}{\textit{I. taiwanensis} Hayata}  \index{Ilex@\textit{Ilex}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長梗花冬青&T2_new_value=true&fr=y}}{長梗花冬青}\index{長梗花冬青} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+tugitakayamensis}{\textit{I. tugitakayamensis} Sasaki}  \index{Ilex@\textit{Ilex}!tugitakayamensis@\textit{tugitakayamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪山冬青&T2_new_value=true&fr=y}}{雪山冬青}\index{雪山冬青}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+uraiensis}{\textit{I. uraiensis} Mori \& Yamam.}  \index{Ilex@\textit{Ilex}!uraiensis@\textit{uraiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來冬青&T2_new_value=true&fr=y}}{烏來冬青}\index{烏來冬青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ilex+yunnanensis+var.+parvifolia}{\textit{I. yunnanensis} Franch. var. \textit{parvifolia} (Hayata) S.Y.Hu}  \index{Ilex@\textit{Ilex}!yunnanensis@\textit{yunnanensis}!var. parvifolia@var. \textit{parvifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雲南冬青&T2_new_value=true&fr=y}}{雲南冬青}\index{雲南冬青}\# LC
  \end{itemize}
  \end{itemize}
