
  \begin{itemize}
 \item[] \textit{Alocasia} 海芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alocasia+cucullata}{\textit{A. cucullata} (Lour.) Schott}  \index{Alocasia@\textit{Alocasia}!cucullata@\textit{cucullata}} 臺灣姑婆芋\index{臺灣姑婆芋} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alocasia+macrorrhizos}{\textit{A. macrorrhizos} (L) G.Don}  \index{Alocasia@\textit{Alocasia}!macrorrhizos@\textit{macrorrhizos}} 海芋\index{海芋} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alocasia+odora}{\textit{A. odora} (Lodd.) Spach.}  \index{Alocasia@\textit{Alocasia}!odora@\textit{odora}} 姑婆芋\index{姑婆芋} LC
  \end{itemize}
 \item[] \textit{Amorphophallus} 蒟蒻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amorphophallus+henryi}{\textit{A. henryi} N.E.Br.}  \index{Amorphophallus@\textit{Amorphophallus}!henryi@\textit{henryi}} 臺灣魔芋\index{臺灣魔芋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amorphophallus+hirtus}{\textit{A. hirtus} N.E.Br.}  \index{Amorphophallus@\textit{Amorphophallus}!hirtus@\textit{hirtus}} 密毛魔芋\index{密毛魔芋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amorphophallus+kiusianus}{\textit{A. kiusianus} (Makino) Makino}  \index{Amorphophallus@\textit{Amorphophallus}!kiusianus@\textit{kiusianus}} 東亞魔芋\index{東亞魔芋} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amorphophallus+paeoniifolius}{\textit{A. paeoniifolius} (Dennst.) Nicolson}  \index{Amorphophallus@\textit{Amorphophallus}!paeoniifolius@\textit{paeoniifolius}} 疣柄魔芋\index{疣柄魔芋} EN
  \end{itemize}
 \item[] \textit{Arisaema} 天南星屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+consanguineum}{\textit{A. consanguineum} Schott}  \index{Arisaema@\textit{Arisaema}!consanguineum@\textit{consanguineum}} 長行天南星\index{長行天南星} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+formosanum}{\textit{A. formosanum} (Hayata) Hayata}  \index{Arisaema@\textit{Arisaema}!formosanum@\textit{formosanum}} 臺灣天南星\index{臺灣天南星}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+grapsospadix}{\textit{A. grapsospadix} Hayata}  \index{Arisaema@\textit{Arisaema}!grapsospadix@\textit{grapsospadix}} 毛筆天南星\index{毛筆天南星}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+heterophyllum}{\textit{A. heterophyllum} Blume}  \index{Arisaema@\textit{Arisaema}!heterophyllum@\textit{heterophyllum}} 羽葉天南星\index{羽葉天南星} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+ilanense}{\textit{A. ilanense} J.C.Wang}  \index{Arisaema@\textit{Arisaema}!ilanense@\textit{ilanense}} 宜蘭天南星\index{宜蘭天南星}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+matsudae}{\textit{A. matsudae} Hayata}  \index{Arisaema@\textit{Arisaema}!matsudae@\textit{matsudae}} 線花天南星\index{線花天南星}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+nanjenense}{\textit{A. nanjenense} T.C.Huang ＆ M.J.Wu}  \index{Arisaema@\textit{Arisaema}!nanjenense@\textit{nanjenense}} 南仁山天南星\index{南仁山天南星}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+ringens}{\textit{A. ringens} (Thunb.) Schott}  \index{Arisaema@\textit{Arisaema}!ringens@\textit{ringens}} 申跋\index{申跋} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+taiwanense+var.+brevipedunculatum}{\textit{A. taiwanense} J.Murata var. \textit{brevipedunculatum} J.Murata}  \index{Arisaema@\textit{Arisaema}!taiwanense@\textit{taiwanense}!var. brevipedunculatum@var. \textit{brevipedunculatum}} 短梗天南星\index{短梗天南星}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+taiwanense+var.+taiwanense}{\textit{A. taiwanense} J.Murata var. \textit{taiwanense}}  \index{Arisaema@\textit{Arisaema}!taiwanense@\textit{taiwanense}!var. taiwanense@var. \textit{taiwanense}} 蓬萊天南星\index{蓬萊天南星}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arisaema+thunbergii+subsp.+autumnale}{\textit{A. thunbergii} Blume subsp. \textit{autumnale} J.C.Wang, J.Murata ＆ H.Ohashi}  \index{Arisaema@\textit{Arisaema}!thunbergii@\textit{thunbergii}!subsp. autumnale@subsp. \textit{autumnale}} 東臺天南星\index{東臺天南星}\# NT
  \end{itemize}
 \item[] \textit{Colocasia} 芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colocasia+esculenta+var.+antiquorum}{\textit{C. esculenta} (L.) Schott var. \textit{antiquorum} (Schott) Hubb. \& Rehder}  \index{Colocasia@\textit{Colocasia}!esculenta@\textit{esculenta}!var. antiquorum@var. \textit{antiquorum}} 檳榔芋\index{檳榔芋} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colocasia+esculenta+var.+esculenta}{\textit{C. esculenta} (L.) Schott var. \textit{esculenta}}  \index{Colocasia@\textit{Colocasia}!esculenta@\textit{esculenta}!var. esculenta@var. \textit{esculenta}} 芋\index{芋} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colocasia+formosana}{\textit{C. formosana} Hayata}  \index{Colocasia@\textit{Colocasia}!formosana@\textit{formosana}} 臺灣青芋\index{臺灣青芋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colocasia+gigantea}{\textit{C. gigantea} (Blume) Hook.f.}  \index{Colocasia@\textit{Colocasia}!gigantea@\textit{gigantea}} 大野芋\index{大野芋} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colocasia+tonoimo}{\textit{C. tonoimo} Nakai}  \index{Colocasia@\textit{Colocasia}!tonoimo@\textit{tonoimo}} 紫芋\index{紫芋} NA$^n$
  \end{itemize}
 \item[] \textit{Epipremnum} 拎樹藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipremnum+aureum}{\textit{E. aureum} (Linden \& André) G.S.Bunting}  \index{Epipremnum@\textit{Epipremnum}!aureum@\textit{aureum}} 黃金葛\index{黃金葛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipremnum+formosanum}{\textit{E. formosanum} Hayata}  \index{Epipremnum@\textit{Epipremnum}!formosanum@\textit{formosanum}} 臺灣拎樹藤\index{臺灣拎樹藤}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipremnum+pinnatum}{\textit{E. pinnatum} (L.) Engl. ex Engl. \& Kraus}  \index{Epipremnum@\textit{Epipremnum}!pinnatum@\textit{pinnatum}} 拎樹藤\index{拎樹藤} LC
  \end{itemize}
 \item[] \textit{Homalomena} 扁葉芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Homalomena+kelungensis}{\textit{H. kelungensis} Hayata}  \index{Homalomena@\textit{Homalomena}!kelungensis@\textit{kelungensis}} 基隆扁葉芋\index{基隆扁葉芋}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Homalomena+philippinensis}{\textit{H. philippinensis} Engl. ex Engl. \& Kraus}  \index{Homalomena@\textit{Homalomena}!philippinensis@\textit{philippinensis}} 菲律賓扁葉芋\index{菲律賓扁葉芋} NT
  \end{itemize}
 \item[] \textit{Landoltia} 疏根萍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Landoltia+punctata}{\textit{L. punctata} (G.Mey.) Les \& D.J.Crawford}  \index{Landoltia@\textit{Landoltia}!punctata@\textit{punctata}}  \index{Spirodela@\textit{Spirodela}!punctata@\textit{punctata}{\\\noindent(= \textit{Landoltia punctata})}} 紫萍\index{紫萍} LC
  \end{itemize}
 \item[] \textit{Lemna} 青萍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lemna+aequinoctialis}{\textit{L. aequinoctialis} Welwitsch}  \index{Lemna@\textit{Lemna}!aequinoctialis@\textit{aequinoctialis}} 青萍\index{青萍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lemna+trisulca}{\textit{L. trisulca} L.}  \index{Lemna@\textit{Lemna}!trisulca@\textit{trisulca}} 品藻\index{品藻} CR
  \end{itemize}
 \item[] \textit{Pinellia} 半夏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinellia+ternata}{\textit{P. ternata} (Thunb.) Breit.}  \index{Pinellia@\textit{Pinellia}!ternata@\textit{ternata}} 半夏\index{半夏} LC
  \end{itemize}
 \item[] \textit{Pistia} 大薸屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pistia+stratiotes}{\textit{P. stratiotes} L.}  \index{Pistia@\textit{Pistia}!stratiotes@\textit{stratiotes}} 大萍\index{大萍} NA$^n$
  \end{itemize}
 \item[] \textit{Pothoidium} 假柚葉藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pothoidium+lobbianum}{\textit{P. lobbianum} Schott}  \index{Pothoidium@\textit{Pothoidium}!lobbianum@\textit{lobbianum}} 假柚葉藤\index{假柚葉藤} NT
  \end{itemize}
 \item[] \textit{Pothos} 柚葉藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pothos+chinensis}{\textit{P. chinensis} (Raf.) Merr.}  \index{Pothos@\textit{Pothos}!chinensis@\textit{chinensis}} 柚葉藤\index{柚葉藤} LC
  \end{itemize}
 \item[] \textit{Remusatia} 目賊芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Remusatia+vivipara}{\textit{R. vivipara} (Lodd.) Schott}  \index{Remusatia@\textit{Remusatia}!vivipara@\textit{vivipara}} 臺灣目賊芋\index{臺灣目賊芋} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Remusatia+yunnanensis}{\textit{R. yunnanensis} (H.Li \& A.Hay) A.Hay }  \index{Remusatia@\textit{Remusatia}!yunnanensis@\textit{yunnanensis}} 雲南岩芋\index{雲南岩芋} VU
  \end{itemize}
 \item[] \textit{Rhaphidophora} 利牟芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhaphidophora+hongkongensis}{\textit{R. hongkongensis} Schott}  \index{Rhaphidophora@\textit{Rhaphidophora}!hongkongensis@\textit{hongkongensis}} 香港針房藤\index{香港針房藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhaphidophora+liukiuensis}{\textit{R. liukiuensis} Hatus.}  \index{Rhaphidophora@\textit{Rhaphidophora}!liukiuensis@\textit{liukiuensis}} 針房藤\index{針房藤} VU
  \end{itemize}
 \item[] \textit{Schismatoglottis} 落檐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schismatoglottis+kotoensis}{\textit{S. kotoensis} (Hayata) T.C.Huang, J.L.Hsiao \& H.Y.Yeh}  \index{Schismatoglottis@\textit{Schismatoglottis}!kotoensis@\textit{kotoensis}} 蘭嶼芋\index{蘭嶼芋}\# VU
  \end{itemize}
 \item[] \textit{Spirodela} 浮萍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spirodela+polyrhiza}{\textit{S. polyrhiza} (L.) Schleid.}  \index{Spirodela@\textit{Spirodela}!polyrhiza@\textit{polyrhiza}} 水萍\index{水萍} LC
  \end{itemize}
 \item[] \textit{Syngonium} 合果芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syngonium+podophyllum}{\textit{S. podophyllum} Schott}  \index{Syngonium@\textit{Syngonium}!podophyllum@\textit{podophyllum}} 合果芋\index{合果芋} NA$^n$
  \end{itemize}
 \item[] \textit{Typhonium} 土半夏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Typhonium+blumei}{\textit{T. blumei} Nicolson \& Sivadasan}  \index{Typhonium@\textit{Typhonium}!blumei@\textit{blumei}} 土半夏\index{土半夏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Typhonium+roxburghii}{\textit{T. roxburghii} Schott}  \index{Typhonium@\textit{Typhonium}!roxburghii@\textit{roxburghii}} 金慈姑\index{金慈姑} NA$^n$
  \end{itemize}
 \item[] \textit{Wolffia} 無根萍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wolffia+arrhiza}{\textit{W. arrhiza} (L.) Wimmer}  \index{Wolffia@\textit{Wolffia}!arrhiza@\textit{arrhiza}} 無根萍\index{無根萍} LC
  \end{itemize}
 \item[] \textit{Xanthosoma} 千年芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Xanthosoma+sagittifolium}{\textit{X. sagittifolium} (L.) Schott}  \index{Xanthosoma@\textit{Xanthosoma}!sagittifolium@\textit{sagittifolium}} 千年芋\index{千年芋} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Xanthosoma+violaceum}{\textit{X. violaceum} Schott}  \index{Xanthosoma@\textit{Xanthosoma}!violaceum@\textit{violaceum}} 紫柄千年芋\index{紫柄千年芋} NA$^n$
  \end{itemize}
  \end{itemize}
