
  \begin{itemize}
 \item[] \textit{Aralia} 刺楤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aralia+armata}{\textit{A. armata} (Wall.) Seem.}  \index{Aralia@\textit{Aralia}!armata@\textit{armata}} 虎刺楤木\index{虎刺楤木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aralia+bipinnata}{\textit{A. bipinnata} Blanco}  \index{Aralia@\textit{Aralia}!bipinnata@\textit{bipinnata}} 裏白楤木\index{裏白楤木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aralia+cordata}{\textit{A. cordata} Thunb.}  \index{Aralia@\textit{Aralia}!cordata@\textit{cordata}} 食用土當歸\index{食用土當歸} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aralia+decaisneana}{\textit{A. decaisneana} Hance}  \index{Aralia@\textit{Aralia}!decaisneana@\textit{decaisneana}} 鵲不踏\index{鵲不踏} LC
  \end{itemize}
 \item[] \textit{Dendropanax} 樹參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendropanax+dentiger}{\textit{D. dentiger} (Harms ex Diels) Merr.}  \index{Dendropanax@\textit{Dendropanax}!dentiger@\textit{dentiger}} 臺灣樹參\index{臺灣樹參} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendropanax+trifidus}{\textit{D. trifidus} (Thunb.) Makino}  \index{Dendropanax@\textit{Dendropanax}!trifidus@\textit{trifidus}} 三菱果樹參\index{三菱果樹參} EN
  \end{itemize}
 \item[] \textit{Eleutherococcus} 三葉五加屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleutherococcus+trifoliatus+var.+setosus}{\textit{E. trifoliatus} (L.) S.Y.Hu var. \textit{setosus} (H.L.Li) H.Ohashi}  \index{Eleutherococcus@\textit{Eleutherococcus}!trifoliatus@\textit{trifoliatus}!var. setosus@var. \textit{setosus}} 毛脈三葉五加\index{毛脈三葉五加} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleutherococcus+trifoliatus+var.+trifoliatus}{\textit{E. trifoliatus} (L.) S.Y.Hu var. \textit{trifoliatus}}  \index{Eleutherococcus@\textit{Eleutherococcus}!trifoliatus@\textit{trifoliatus}!var. trifoliatus@var. \textit{trifoliatus}} 三葉五加\index{三葉五加} LC
  \end{itemize}
 \item[] \textit{Fatsia} 八角金盤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fatsia+polycarpa}{\textit{F. polycarpa} Hayata}  \index{Fatsia@\textit{Fatsia}!polycarpa@\textit{polycarpa}} 臺灣八角金盤\index{臺灣八角金盤}\# LC
  \end{itemize}
 \item[] \textit{Hedera} 常春藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedera+rhombea+var.+formosana}{\textit{H. rhombea} (Miq.) Bean var. \textit{formosana} (Nakai)) H.L.Li}  \index{Hedera@\textit{Hedera}!rhombea@\textit{rhombea}!var. formosana@var. \textit{formosana}} 臺灣常春藤\index{臺灣常春藤}\# LC
  \end{itemize}
 \item[] \textit{Hydrocotyle} 天胡荽屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+batrachium}{\textit{H. batrachium} Hance}  \index{Hydrocotyle@\textit{Hydrocotyle}!batrachium@\textit{batrachium}} 臺灣天胡荽\index{臺灣天胡荽} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+benguetensis}{\textit{H. benguetensis} Elm.}  \index{Hydrocotyle@\textit{Hydrocotyle}!benguetensis@\textit{benguetensis}} 菲島天胡荽\index{菲島天胡荽} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+dichondroides}{\textit{H. dichondroides} Makino}  \index{Hydrocotyle@\textit{Hydrocotyle}!dichondroides@\textit{dichondroides}} 毛天胡荽\index{毛天胡荽} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+keelungensis}{\textit{H. keelungensis} T.S.Liu, C.Y.Chao \& T.I.Chuang}  \index{Hydrocotyle@\textit{Hydrocotyle}!keelungensis@\textit{keelungensis}} 基隆天胡荽\index{基隆天胡荽} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+leucocephala}{\textit{H. leucocephala} Cham. \& Schltdl.}  \index{Hydrocotyle@\textit{Hydrocotyle}!leucocephala@\textit{leucocephala}} 白頭天胡荽\index{白頭天胡荽} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+nepalensis}{\textit{H. nepalensis} Hook.}  \index{Hydrocotyle@\textit{Hydrocotyle}!nepalensis@\textit{nepalensis}} 乞食碗\index{乞食碗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+setulosa}{\textit{H. setulosa} Hayata}  \index{Hydrocotyle@\textit{Hydrocotyle}!setulosa@\textit{setulosa}} 阿里山天胡荽\index{阿里山天胡荽}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+sibthorpioides}{\textit{H. sibthorpioides} Lam.}  \index{Hydrocotyle@\textit{Hydrocotyle}!sibthorpioides@\textit{sibthorpioides}} 天胡荽\index{天胡荽} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocotyle+verticillata}{\textit{H. verticillata} Thunb.}  \index{Hydrocotyle@\textit{Hydrocotyle}!verticillata@\textit{verticillata}} 銅錢草\index{銅錢草} NA$^c$
  \end{itemize}
 \item[] \textit{Osmoxylon} 蘭嶼八角金盤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osmoxylon+pectinatum}{\textit{O. pectinatum} (Merr.) Philipson}  \index{Osmoxylon@\textit{Osmoxylon}!pectinatum@\textit{pectinatum}} 蘭嶼八角金盤\index{蘭嶼八角金盤} NT
  \end{itemize}
 \item[] \textit{Pentapanax} 五葉參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pentapanax+castanopsisicola}{\textit{P. castanopsisicola} Hayata}  \index{Pentapanax@\textit{Pentapanax}!castanopsisicola@\textit{castanopsisicola}} 臺灣五葉參\index{臺灣五葉參}\# NT
  \end{itemize}
 \item[] \textit{Schefflera} 鵝掌柴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schefflera+arboricola}{\textit{S. arboricola} (Hayata) Kaneh.}  \index{Schefflera@\textit{Schefflera}!arboricola@\textit{arboricola}} 鵝掌蘗\index{鵝掌蘗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schefflera+octophylla}{\textit{S. octophylla} (Lour.) Harms}  \index{Schefflera@\textit{Schefflera}!octophylla@\textit{octophylla}} 鵝掌柴\index{鵝掌柴} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schefflera+odorata}{\textit{S. odorata} (Blanco) Merr. \& Rolfe}  \index{Schefflera@\textit{Schefflera}!odorata@\textit{odorata}} 鵝掌藤\index{鵝掌藤} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schefflera+taiwaniana}{\textit{S. taiwaniana} (Nakai) Kanehira}  \index{Schefflera@\textit{Schefflera}!taiwaniana@\textit{taiwaniana}} 臺灣鵝掌柴\index{臺灣鵝掌柴}\# LC
  \end{itemize}
 \item[] \textit{Sinopanax} 華參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sinopanax+formosana}{\textit{S. formosana} (Hayata) H.L.Li}  \index{Sinopanax@\textit{Sinopanax}!formosana@\textit{formosana}} 華參\index{華參}\# VU
  \end{itemize}
 \item[] \textit{Tetrapanax} 通脫木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrapanax+papyriferus}{\textit{T. papyriferus} (Hook.) K.Koch}  \index{Tetrapanax@\textit{Tetrapanax}!papyriferus@\textit{papyriferus}} 通脫木\index{通脫木} LC
  \end{itemize}
  \end{itemize}
