
  \begin{itemize}
 \item[] \textit{Arenga} 山棕屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arenga+tremula}{\textit{A. tremula} (Blanco) Becc.}  \index{Arenga@\textit{Arenga}!tremula@\textit{tremula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山棕&T2_new_value=true&fr=y}}{山棕}\index{山棕} LC
  \end{itemize}
 \item[] \textit{Calamus} 省藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calamus+beccarii}{\textit{C. beccarii} A.J.Hend.}  \index{Calamus@\textit{Calamus}!beccarii@\textit{beccarii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=土藤&T2_new_value=true&fr=y}}{土藤}\index{土藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calamus+formosanus}{\textit{C. formosanus} Becc.}  \index{Calamus@\textit{Calamus}!formosanus@\textit{formosanus}}  \index{Calamus@\textit{Calamus}!quiquesetinervius@\textit{quiquesetinervius}{\\\noindent(= \textit{Calamus formosanus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃藤&T2_new_value=true&fr=y}}{黃藤}\index{黃藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calamus+siphonospathus+var.+sublaevis}{\textit{C. siphonospathus} Mart. var. \textit{sublaevis} Becc.}  \index{Calamus@\textit{Calamus}!siphonospathus@\textit{siphonospathus}!var. sublaevis@var. \textit{sublaevis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼省藤&T2_new_value=true&fr=y}}{蘭嶼省藤}\index{蘭嶼省藤} NT
  \end{itemize}
 \item[] \textit{Livistona} 蒲葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Livistona+chinensis+var.+subglobosa}{\textit{L. chinensis} R.Br. var. \textit{subglobosa} (Mart.) Becc.}  \index{Livistona@\textit{Livistona}!chinensis@\textit{chinensis}!var. subglobosa@\textbf{var. \textit{subglobosa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蒲葵&T2_new_value=true&fr=y}}{蒲葵}\index{蒲葵@{\Song{蒲葵}}} VU
  \end{itemize}
 \item[] \textit{Phoenix} 海棗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phoenix+hanceana}{\textit{P. hanceana} Naudin}  \index{Phoenix@\textit{Phoenix}!hanceana@\textit{hanceana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣海棗&T2_new_value=true&fr=y}}{臺灣海棗}\index{臺灣海棗} LC
  \end{itemize}
 \item[] \textit{Pinanga} 山檳榔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinanga+tashiroi}{\textit{P. tashiroi} Hayata}  \index{Pinanga@\textit{Pinanga}!tashiroi@\textbf{\textit{tashiroi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山檳榔&T2_new_value=true&fr=y}}{山檳榔}\index{山檳榔@{\Song{山檳榔}}}\# EN
  \end{itemize}
  \end{itemize}
