
  \begin{itemize}
 \item[] \textit{Agave} 龍舌蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agave+americana}{\textit{A. americana} L.}  \index{Agave@\textit{Agave}!americana@\textit{americana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=龍舌蘭&T2_new_value=true&fr=y}}{龍舌蘭}\index{龍舌蘭} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agave+fourcroydes}{\textit{A. fourcroydes} Lem.}  \index{Agave@\textit{Agave}!fourcroydes@\textit{fourcroydes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃條龍舌蘭&T2_new_value=true&fr=y}}{黃條龍舌蘭}\index{黃條龍舌蘭} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agave+gigantean}{\textit{A. gigantean} L.}  \index{Agave@\textit{Agave}!gigantean@\textit{gigantean}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大龍舌蘭&T2_new_value=true&fr=y}}{大龍舌蘭}\index{大龍舌蘭} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agave+sisalana}{\textit{A. sisalana} Perr. ex Enghlm.}  \index{Agave@\textit{Agave}!sisalana@\textit{sisalana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓊麻&T2_new_value=true&fr=y}}{瓊麻}\index{瓊麻} NA$^n$
  \end{itemize}
 \item[] \textit{Asparagus} 天門冬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Asparagus+cochinchinensis}{\textit{A. cochinchinensis} (Lour.) Merr.}  \index{Asparagus@\textit{Asparagus}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天門冬&T2_new_value=true&fr=y}}{天門冬}\index{天門冬} LC
  \end{itemize}
 \item[] \textit{Aspidistra} 蜘蛛抱蛋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aspidistra+daibuensis}{\textit{A. daibuensis} Hayata}  \index{Aspidistra@\textit{Aspidistra}!daibuensis@\textit{daibuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大武蜘蛛抱蛋&T2_new_value=true&fr=y}}{大武蜘蛛抱蛋}\index{大武蜘蛛抱蛋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aspidistra+elatior+var.+attenuata}{\textit{A. elatior} Blume var. \textit{attenuata} (Hayata) S.S.Ying}  \index{Aspidistra@\textit{Aspidistra}!elatior@\textit{elatior}!var. attenuata@var. \textit{attenuata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蜘蛛抱蛋&T2_new_value=true&fr=y}}{臺灣蜘蛛抱蛋}\index{臺灣蜘蛛抱蛋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aspidistra+mushaensis}{\textit{A. mushaensis} Hayata}  \index{Aspidistra@\textit{Aspidistra}!mushaensis@\textbf{\textit{mushaensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=霧社蜘蛛抱蛋&T2_new_value=true&fr=y}}{霧社蜘蛛抱蛋}\index{霧社蜘蛛抱蛋@{\Song{霧社蜘蛛抱蛋}}}\# VU
  \end{itemize}
 \item[] \textit{Barnardia} 棉棗兒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Barnardia+japonica}{\textit{B. japonica} (Thunb.) Schult. \& Schult.f.}  \index{Barnardia@\textit{Barnardia}!japonica@\textbf{\textit{japonica}}}  \index{Scilla@\textit{Scilla}!sinensis@\textit{sinensis}{\\\noindent(= \textit{Barnardia japonica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綿棗兒&T2_new_value=true&fr=y}}{綿棗兒}\index{綿棗兒@{\Song{綿棗兒}}} VU
  \end{itemize}
 \item[] \textit{Disporopsis} 假寶鐸花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Disporopsis+fuscopicota+var.+arisanensis}{\textit{D. fuscopicota} Hance var. \textit{arisanensis} (Hayata) S.S.Ying}  \index{Disporopsis@\textit{Disporopsis}!fuscopicota@\textit{fuscopicota}!var. arisanensis@var. \textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山假寶鐸花&T2_new_value=true&fr=y}}{阿里山假寶鐸花}\index{阿里山假寶鐸花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Disporopsis+taiwanensis}{\textit{D. taiwanensis} S.S.Ying}  \index{Disporopsis@\textit{Disporopsis}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣假寶鐸花&T2_new_value=true&fr=y}}{臺灣假寶鐸花}\index{臺灣假寶鐸花}\# LC
  \end{itemize}
 \item[] \textit{Dracaena} 龍血樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dracaena+angustifolia}{\textit{D. angustifolia} Roxb.}  \index{Dracaena@\textit{Dracaena}!angustifolia@\textbf{\textit{angustifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=番仔林投&T2_new_value=true&fr=y}}{番仔林投}\index{番仔林投@{\Song{番仔林投}}} VU
  \end{itemize}
 \item[] \textit{Heteropolygonatum} 異黃精屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Heteropolygonatum+altelobatum}{\textit{H. altelobatum} (Hayata) Y.H.Tseng, H.Y.Tzeng \& C.T.Chao}  \index{Heteropolygonatum@\textit{Heteropolygonatum}!altelobatum@\textit{altelobatum}}  \index{Polygonatum@\textit{Polygonatum}!altelobatum@\textit{altelobatum}{\\\noindent(= \textit{Heteropolygonatum altelobatum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃精&T2_new_value=true&fr=y}}{臺灣黃精}\index{臺灣黃精}\# LC
  \end{itemize}
 \item[] \textit{Liriope} 麥門冬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liriope+minor+var.+angustissima}{\textit{L. minor} (Maxim.) Makino var. \textit{angustissima} (Ohwi) S.S.Ying}  \index{Liriope@\textit{Liriope}!minor@\textit{minor}!var. angustissima@var. \textit{angustissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉麥門冬&T2_new_value=true&fr=y}}{細葉麥門冬}\index{細葉麥門冬}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liriope+platyphylla}{\textit{L. platyphylla} F.T.Wang \& T.Tang}  \index{Liriope@\textit{Liriope}!platyphylla@\textit{platyphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉麥門冬&T2_new_value=true&fr=y}}{闊葉麥門冬}\index{闊葉麥門冬} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liriope+spicata}{\textit{L. spicata} (Thunb.) Lour.}  \index{Liriope@\textit{Liriope}!spicata@\textit{spicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=麥門冬&T2_new_value=true&fr=y}}{麥門冬}\index{麥門冬} LC
  \end{itemize}
 \item[] \textit{Maianthemum} 舞鶴草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maianthemum+formosanum}{\textit{M. formosanum} (Hayata) LaFrankie}  \index{Maianthemum@\textit{Maianthemum}!formosanum@\textit{formosanum}}  \index{Smilacina@\textit{Smilacina}!japonica@\textit{japonica}{\\\noindent(= \textit{Maianthemum formosanum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鹿藥&T2_new_value=true&fr=y}}{鹿藥}\index{鹿藥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maianthemum+harae}{\textit{M. harae} Y.H.Tseng \& C.T.Chao}  \index{Maianthemum@\textit{Maianthemum}!harae@\textit{harae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=原氏鹿藥&T2_new_value=true&fr=y}}{原氏鹿藥}\index{原氏鹿藥} LC
  \end{itemize}
 \item[] \textit{Ophiopogon} 沿階草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiopogon+intermedius}{\textit{O. intermedius} D.Don}  \index{Ophiopogon@\textit{Ophiopogon}!intermedius@\textit{intermedius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=間型沿階草&T2_new_value=true&fr=y}}{間型沿階草}\index{間型沿階草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiopogon+reversus}{\textit{O. reversus} C.C.Huang}  \index{Ophiopogon@\textit{Ophiopogon}!reversus@\textit{reversus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高節沿階草&T2_new_value=true&fr=y}}{高節沿階草}\index{高節沿階草} LC
  \end{itemize}
 \item[] \textit{Peliosanthes} 球子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peliosanthes+teta+var.+humilis}{\textit{P. teta} Andrews var. \textit{humilis} (Andrews) M.J.Lai}  \index{Peliosanthes@\textit{Peliosanthes}!teta@\textit{teta}!var. humilis@var. \textit{humilis}}  \index{Peliosanthes@\textit{Peliosanthes}!macrostegia@\textit{macrostegia}{\\\noindent(= \textit{Peliosanthes teta} var. \textit{humilis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=矮球子草&T2_new_value=true&fr=y}}{矮球子草}\index{矮球子草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peliosanthes+teta+var.+kaoi}{\textit{P. teta} Andrews var. \textit{kaoi} (Ohwi) S.S.Ying}  \index{Peliosanthes@\textit{Peliosanthes}!teta@\textit{teta}!var. kaoi@var. \textit{kaoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高氏球子草&T2_new_value=true&fr=y}}{高氏球子草}\index{高氏球子草}\# LC
  \end{itemize}
 \item[] \textit{Polygonatum} 黃精屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polygonatum+chingshuishanianum}{\textit{P. chingshuishanianum} S.S.Ying}  \index{Polygonatum@\textit{Polygonatum}!chingshuishanianum@\textit{chingshuishanianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水山黃精&T2_new_value=true&fr=y}}{清水山黃精}\index{清水山黃精}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polygonatum+odoratum+var.+pluriflorum}{\textit{P. odoratum} (Miller) Druce var. \textit{pluriflorum} (Miq.) Ohwi}  \index{Polygonatum@\textit{Polygonatum}!odoratum@\textit{odoratum}!var. pluriflorum@var. \textit{pluriflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=萎蕤&T2_new_value=true&fr=y}}{萎蕤}\index{萎蕤} LC
  \end{itemize}
 \item[] \textit{Rohdea} 萬年青屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rohdea+japonica+var.+watanabei}{\textit{R. japonica} (Thunb.) Roth. var. \textit{watanabei} (Hayata) S.S.Ying}  \index{Rohdea@\textit{Rohdea}!japonica@\textit{japonica}!var. watanabei@\textbf{var. \textit{watanabei}}}  \index{Campylandra@\textit{Campylandra}!chinensis@\textit{chinensis}{\\\noindent(= \textit{Rohdea japonica} var. \textit{watanabei})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=萬年青&T2_new_value=true&fr=y}}{萬年青}\index{萬年青@{\Song{萬年青}}}\# VU
  \end{itemize}
 \item[] \textit{Thysanotus} 異蕊草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thysanotus+chinensis}{\textit{T. chinensis} Benth.}  \index{Thysanotus@\textit{Thysanotus}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=異蕊草&T2_new_value=true&fr=y}}{異蕊草}\index{異蕊草@{\Song{異蕊草}}} CR
  \end{itemize}
  \end{itemize}
