
  \begin{itemize}
 \item[] \textit{Asplenium} 鐵角蕨屬
                                
  \begin{itemize}
        \item[] \textit{A. adiantumnigrum} L. \index{Asplenium@\textit{Asplenium}!adiantumnigrum@\textit{adiantumnigrum}} 深山鐵角蕨 \index{深山鐵角蕨}  LC
        \item[] \textit{A. antiquum} Makino \index{Asplenium@\textit{Asplenium}!antiquum@\textit{antiquum}} 山蘇花 \index{山蘇花}  LC
        \item[] \textit{A. australasicum} (J.Sm.) Hook. \index{Asplenium@\textit{Asplenium}!australasicum@\textit{australasicum}} 南洋山蘇花 \index{南洋山蘇花}  LC
        \item[] \textit{A. boreale} (Ohwi ex Sa.Kurata) T.Nakaike \index{Asplenium@\textit{Asplenium}!boreale@\textit{boreale}} 北方倒掛鐵角蕨 \index{北方倒掛鐵角蕨}  VU
        \item[] \textit{A. bullatum} Wall. ex Mett. \index{Asplenium@\textit{Asplenium}!bullatum@\textit{bullatum}} 大鐵角蕨 \index{大鐵角蕨}  NT
        \item[] \textit{A. capillipes} Makino \index{Asplenium@\textit{Asplenium}!capillipes@\textit{capillipes}} 姬鐵角蕨 \index{姬鐵角蕨}  LC
        \item[] \textit{A. crinicaule} Hance \index{Asplenium@\textit{Asplenium}!crinicaule@\textit{crinicaule}} 毛軸鐵角蕨 \index{毛軸鐵角蕨}  CR
        \item[] \textit{A. cuneatiforme} H.Christ \index{Asplenium@\textit{Asplenium}!cuneatiforme@\textit{cuneatiforme}} 大蓬萊鐵角蕨 \index{大蓬萊鐵角蕨} \# LC
        \item[] \textit{A. ensiforme} Wall. ex Hook. \& Grev. \index{Asplenium@\textit{Asplenium}!ensiforme@\textit{ensiforme}} 劍葉鐵角蕨 \index{劍葉鐵角蕨}  LC
        \item[] \textit{A. formosae} H.Christ \index{Asplenium@\textit{Asplenium}!formosae@\textit{formosae}} 南海鐵角蕨 \index{南海鐵角蕨}  LC
        \item[] \textit{A. griffithianum} Hook. \index{Asplenium@\textit{Asplenium}!griffithianum@\textit{griffithianum}} 叢葉鐵角蕨 \index{叢葉鐵角蕨}  LC
        \item[] \textit{A. incisum} Thunb. \index{Asplenium@\textit{Asplenium}!incisum@\textit{incisum}} 縮羽鐵角蕨 \index{縮羽鐵角蕨}  LC
        \item[] \textit{A. laciniatum} D.Don \index{Asplenium@\textit{Asplenium}!laciniatum@\textit{laciniatum}} 鱗柄鐵角蕨 \index{鱗柄鐵角蕨}  LC
        \item[] \textit{A. lobulatum} Mett. ex Kuhn \index{Asplenium@\textit{Asplenium}!lobulatum@\textit{lobulatum}} 裂葉鐵角蕨 \index{裂葉鐵角蕨}  LC
        \item[] \textit{A. neolaserpitiifolium} Tardieu \& Ching \index{Asplenium@\textit{Asplenium}!neolaserpitiifolium@\textit{neolaserpitiifolium}} 大黑柄鐵角蕨 \index{大黑柄鐵角蕨}  LC
        \item[] \textit{A. nidus} L. \index{Asplenium@\textit{Asplenium}!nidus@\textit{nidus}} 臺灣山蘇花 \index{臺灣山蘇花}  LC
        \item[] \textit{A. normale} D.Don \index{Asplenium@\textit{Asplenium}!normale@\textit{normale}} 生芽鐵角蕨 \index{生芽鐵角蕨}  LC
        \item[] \textit{A. obscurum} Blume \index{Asplenium@\textit{Asplenium}!obscurum@\textit{obscurum}} 綠柄剪葉鐵角蕨 \index{綠柄剪葉鐵角蕨}  NT
        \item[] \textit{A. oldhamii} Hance \index{Asplenium@\textit{Asplenium}!oldhamii@\textit{oldhamii}} 俄氏鐵角蕨 \index{俄氏鐵角蕨}  LC
        \item[] \textit{A. pekinense} Hance \index{Asplenium@\textit{Asplenium}!pekinense@\textit{pekinense}} 北京鐵角蕨 \index{北京鐵角蕨}  DD
        \item[] \textit{A. pifongiae} L.Y.Kuo, F.W.Li \& Y.H.Chang \index{Asplenium@\textit{Asplenium}!pifongiae@\textit{pifongiae}} 碧鳳鐵角蕨 \index{碧鳳鐵角蕨}  EN
        \item[] \textit{A. polyodon} G.Forst. \index{Asplenium@\textit{Asplenium}!polyodon@\textit{polyodon}} 革葉鐵角蕨 \index{革葉鐵角蕨}  LC
        \item[] \textit{A. prolongatum} Hook. \index{Asplenium@\textit{Asplenium}!prolongatum@\textit{prolongatum}} 長生鐵角蕨 \index{長生鐵角蕨}  LC
        \item[] \textit{A. pseudolaserpitiifolium} Ching ex Tardieu \& Ching \index{Asplenium@\textit{Asplenium}!pseudolaserpitiifolium@\textit{pseudolaserpitiifolium}} 黑鱗鐵角蕨 \index{黑鱗鐵角蕨}  DD
        \item[] \textit{A. pulcherrimum} (Baker) Ching \index{Asplenium@\textit{Asplenium}!pulcherrimum@\textit{pulcherrimum}} 細葉鐵角蕨 \index{細葉鐵角蕨}  NT
        \item[] \textit{A. ritoense} Hayata \index{Asplenium@\textit{Asplenium}!ritoense@\textit{ritoense}} 尖葉鐵角蕨 \index{尖葉鐵角蕨}  LC
        \item[] \textit{A. ruta-muraria} L. \index{Asplenium@\textit{Asplenium}!ruta-muraria@\textit{ruta-muraria}} 銀杏葉鐵角蕨 \index{銀杏葉鐵角蕨}  VU
        \item[] \textit{A. scolopendrium} L. \index{Asplenium@\textit{Asplenium}!scolopendrium@\textit{scolopendrium}} 對開蕨 \index{對開蕨}  VU*
        \item[] \textit{A. septentrionale} (L.) Hoffm. \index{Asplenium@\textit{Asplenium}!septentrionale@\textit{septentrionale}} 線葉鐵角蕨 \index{線葉鐵角蕨}  NT
        \item[] \textit{A. serricula} Fée \index{Asplenium@\textit{Asplenium}!serricula@\textit{serricula}} 蘭嶼鐵角蕨 \index{蘭嶼鐵角蕨}  NT
        \item[] \textit{A. steerei} Harr. \index{Asplenium@\textit{Asplenium}!steerei@\textit{steerei}} 劍羽鐵角蕨 \index{劍羽鐵角蕨}  VU
        \item[] \textit{A. tenerum} G.Forst. \index{Asplenium@\textit{Asplenium}!tenerum@\textit{tenerum}} 鈍齒鐵角蕨 \index{鈍齒鐵角蕨}  NT
        \item[] \textit{A. tenuicaule} Hayata \index{Asplenium@\textit{Asplenium}!tenuicaule@\textit{tenuicaule}} 小葉鐵角蕨 \index{小葉鐵角蕨}  LC
        \item[] \textit{A. tenuifolium} D.Don \index{Asplenium@\textit{Asplenium}!tenuifolium@\textit{tenuifolium}} 薄葉鐵角蕨 \index{薄葉鐵角蕨}  LC
        \item[] \textit{A. trichomanes} L. \index{Asplenium@\textit{Asplenium}!trichomanes@\textit{trichomanes}} 鐵角蕨 \index{鐵角蕨}  LC
        \item[] \textit{A. tripteropus} Nakai \index{Asplenium@\textit{Asplenium}!tripteropus@\textit{tripteropus}} 三翅鐵角蕨 \index{三翅鐵角蕨}  LC
        \item[] \textit{A. viride} Hudson \index{Asplenium@\textit{Asplenium}!viride@\textit{viride}} 綠柄鐵角蕨 \index{綠柄鐵角蕨}  LC
        \item[] \textit{A. wilfordii} Mett. ex Kuhn \index{Asplenium@\textit{Asplenium}!wilfordii@\textit{wilfordii}} 威氏鐵角蕨 \index{威氏鐵角蕨}  LC
        \item[] \textit{A. wrightii} Eaton ex Hook. \index{Asplenium@\textit{Asplenium}!wrightii@\textit{wrightii}} 萊氏鐵角蕨 \index{萊氏鐵角蕨}  LC
        \item[] \textit{A. yoshinagae} subsp. \textit{indicum} (Sledge) Fraser-Jenk. \index{Asplenium@\textit{Asplenium}!yoshinagae@\textit{yoshinagae}!subsp. indicum@subsp. \textit{indicum}}
                                        斜葉鐵角蕨 \index{斜葉鐵角蕨}  LC
        \item[] \textit{A. yunnanense} Franch. \index{Asplenium@\textit{Asplenium}!yunnanense@\textit{yunnanense}} 雲南鐵角蕨 \index{雲南鐵角蕨}  DD
        \item[] \textit{A. ×} shikokianum \textit{} Makino \index{Asplenium@\textit{Asplenium}!×@\textit{×}!shikokianum @shikokianum \textit{}}
                                        四國鐵角蕨 \index{四國鐵角蕨}  NA
        \item[] \textit{A. ×} wangii \textit{} C.M.Kuo \index{Asplenium@\textit{Asplenium}!×@\textit{×}!wangii @wangii \textit{}}
                                        王氏鐵角蕨 \index{王氏鐵角蕨}  NA
  \end{itemize}
 \item[] \textit{Hymenasplenium} 膜葉鐵角蕨屬
                                
  \begin{itemize}
        \item[] \textit{H. apogamum} (N.Murak. \& Hatan.) Nakaike \index{Hymenasplenium@\textit{Hymenasplenium}!apogamum@\textit{apogamum}} 無配鐵角蕨 \index{無配鐵角蕨}  LC
        \item[] \textit{H. cataractarum} (Rosenst.) N.Murakami \index{Hymenasplenium@\textit{Hymenasplenium}!cataractarum@\textit{cataractarum}} 湍生鐵角蕨 \index{湍生鐵角蕨}  LC
        \item[] \textit{H. cheilosorum} (Kunze ex Mett.) Tagawa \index{Hymenasplenium@\textit{Hymenasplenium}!cheilosorum@\textit{cheilosorum}} 薄葉孔雀鐵角蕨 \index{薄葉孔雀鐵角蕨}  LC
        \item[] \textit{H. excisum} (C.Presl) S.Linds. \index{Hymenasplenium@\textit{Hymenasplenium}!excisum@\textit{excisum}} 剪葉鐵角蕨 \index{剪葉鐵角蕨}  LC
        \item[] \textit{H. filipes} (Copel.) Sugimoto \index{Hymenasplenium@\textit{Hymenasplenium}!filipes@\textit{filipes}} 複齒鐵角蕨 \index{複齒鐵角蕨}  LC
        \item[] \textit{H. obliquissimum} (Hayata) Sugimoto \index{Hymenasplenium@\textit{Hymenasplenium}!obliquissimum@\textit{obliquissimum}} 蔭濕膜葉鐵角蕨 \index{蔭濕膜葉鐵角蕨}  LC
        \item[] \textit{H. subnormale} (Copel.) Nakaike \index{Hymenasplenium@\textit{Hymenasplenium}!subnormale@\textit{subnormale}} 小鐵角蕨 \index{小鐵角蕨}  DD
        \item[] \textit{H. unilaterale} (Lam.) Hayata \index{Hymenasplenium@\textit{Hymenasplenium}!unilaterale@\textit{unilaterale}} 單邊鐵角蕨 \index{單邊鐵角蕨}  LC
  \end{itemize}
  \end{itemize}
