
  \begin{itemize}
 \item[] \textit{Acmella} 金鈕扣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acmella+brachyglossa}{\textit{A. brachyglossa} Cass.}  \index{Acmella@\textit{Acmella}!brachyglossa@\textit{brachyglossa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短舌花金鈕釦&T2_new_value=true&fr=y}}{短舌花金鈕釦}\index{短舌花金鈕釦} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acmella+ciliata}{\textit{A. ciliata} (Kunth) Cass.}  \index{Acmella@\textit{Acmella}!ciliata@\textit{ciliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天文草&T2_new_value=true&fr=y}}{天文草}\index{天文草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acmella+oleracea}{\textit{A. oleracea} (L.) R.K.Jansen}  \index{Acmella@\textit{Acmella}!oleracea@\textit{oleracea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度金鈕釦&T2_new_value=true&fr=y}}{印度金鈕釦}\index{印度金鈕釦} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acmella+paniculata}{\textit{A. paniculata} (Wall. ex DC.) R.K.Jansen}  \index{Acmella@\textit{Acmella}!paniculata@\textbf{\textit{paniculata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金鈕釦&T2_new_value=true&fr=y}}{金鈕釦}\index{金鈕釦@{\Song{金鈕釦}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acmella+uliginosa}{\textit{A. uliginosa} (Swartz) Cassini}  \index{Acmella@\textit{Acmella}!uliginosa@\textit{uliginosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=沼生金鈕釦&T2_new_value=true&fr=y}}{沼生金鈕釦}\index{沼生金鈕釦} NA$^n$
  \end{itemize}
 \item[] \textit{Adenostemma} 下田菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adenostemma+lavenia+var.+lavenia}{\textit{A. lavenia} (L.) Kuntze var. \textit{lavenia}}  \index{Adenostemma@\textit{Adenostemma}!lavenia@\textit{lavenia}!var. lavenia@var. \textit{lavenia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=下田菊&T2_new_value=true&fr=y}}{下田菊}\index{下田菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adenostemma+lavenia+var.+parviflorum}{\textit{A. lavenia} (L.) Kuntze var. \textit{parviflorum} (Blume) Hochr.}  \index{Adenostemma@\textit{Adenostemma}!lavenia@\textit{lavenia}!var. parviflorum@var. \textit{parviflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花下田菊&T2_new_value=true&fr=y}}{小花下田菊}\index{小花下田菊} LC
  \end{itemize}
 \item[] \textit{Ageratina} 假藿香薊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ageratina+adenophora}{\textit{A. adenophora} (Spreng.) R.M.King \& H.Rob.}  \index{Ageratina@\textit{Ageratina}!adenophora@\textit{adenophora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假藿香薊&T2_new_value=true&fr=y}}{假藿香薊}\index{假藿香薊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ageratina+riparia}{\textit{A. riparia} (Regel) R.M.King \& H.Rob.}  \index{Ageratina@\textit{Ageratina}!riparia@\textit{riparia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澤假藿香薊&T2_new_value=true&fr=y}}{澤假藿香薊}\index{澤假藿香薊} NA$^n$
  \end{itemize}
 \item[] \textit{Ageratum} 藿香薊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ageratum+conyzoides}{\textit{A. conyzoides} L.}  \index{Ageratum@\textit{Ageratum}!conyzoides@\textit{conyzoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藿香薊&T2_new_value=true&fr=y}}{藿香薊}\index{藿香薊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ageratum+houstonianum}{\textit{A. houstonianum} Mill.}  \index{Ageratum@\textit{Ageratum}!houstonianum@\textit{houstonianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花藿香薊&T2_new_value=true&fr=y}}{紫花藿香薊}\index{紫花藿香薊} NA$^n$
  \end{itemize}
 \item[] \textit{Ainsliaea} 鬼督郵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ainsliaea+fragrans}{\textit{A. fragrans} Champ.}  \index{Ainsliaea@\textit{Ainsliaea}!fragrans@\textit{fragrans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香鬼督郵&T2_new_value=true&fr=y}}{香鬼督郵}\index{香鬼督郵} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ainsliaea+latifolia+subsp.+henryi}{\textit{A. latifolia} (D.Don) Sch.Bip. subsp. \textit{henryi} (Diels) H.Koyama}  \index{Ainsliaea@\textit{Ainsliaea}!latifolia@\textit{latifolia}!subsp. henryi@subsp. \textit{henryi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鬼督郵&T2_new_value=true&fr=y}}{臺灣鬼督郵}\index{臺灣鬼督郵} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ainsliaea+macroclinidioides}{\textit{A. macroclinidioides} Hayata}  \index{Ainsliaea@\textit{Ainsliaea}!macroclinidioides@\textit{macroclinidioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山鬼督郵&T2_new_value=true&fr=y}}{阿里山鬼督郵}\index{阿里山鬼督郵} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ainsliaea+secundiflora}{\textit{A. secundiflora} Hayata}  \index{Ainsliaea@\textit{Ainsliaea}!secundiflora@\textbf{\textit{secundiflora}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中原氏鬼督郵&T2_new_value=true&fr=y}}{中原氏鬼督郵}\index{中原氏鬼督郵@{\Song{中原氏鬼督郵}}}\# VU
  \end{itemize}
 \item[] \textit{Ambrosia} 豬草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ambrosia+artemisiifolia}{\textit{A. artemisiifolia} L.}  \index{Ambrosia@\textit{Ambrosia}!artemisiifolia@\textit{artemisiifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豬草&T2_new_value=true&fr=y}}{豬草}\index{豬草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ambrosia+psilostachya}{\textit{A. psilostachya} DC.}  \index{Ambrosia@\textit{Ambrosia}!psilostachya@\textit{psilostachya}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裸穗豬草&T2_new_value=true&fr=y}}{裸穗豬草}\index{裸穗豬草} NA$^n$
  \end{itemize}
 \item[] \textit{Anaphalis} 籟簫屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anaphalis+horaimontana}{\textit{A. horaimontana} Masam.}  \index{Anaphalis@\textit{Anaphalis}!horaimontana@\textit{horaimontana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊籟簫&T2_new_value=true&fr=y}}{蓬萊籟簫}\index{蓬萊籟簫}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anaphalis+morrisonicola}{\textit{A. morrisonicola} Hayata}  \index{Anaphalis@\textit{Anaphalis}!morrisonicola@\textit{morrisonicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山抱莖籟簫&T2_new_value=true&fr=y}}{玉山抱莖籟簫}\index{玉山抱莖籟簫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anaphalis+nepalensis}{\textit{A. nepalensis} (Spreng.) Hand.-Mazz.}  \index{Anaphalis@\textit{Anaphalis}!nepalensis@\textit{nepalensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尼泊爾籟簫&T2_new_value=true&fr=y}}{尼泊爾籟簫}\index{尼泊爾籟簫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anaphalis+royleana}{\textit{A. royleana} DC.}  \index{Anaphalis@\textit{Anaphalis}!royleana@\textit{royleana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高籟簫&T2_new_value=true&fr=y}}{能高籟簫}\index{能高籟簫} LC
  \end{itemize}
 \item[] \textit{Argyranthemum} 木茼蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argyranthemum+frutescens}{\textit{A. frutescens} (L.) Sch.Bip.}  \index{Argyranthemum@\textit{Argyranthemum}!frutescens@\textit{frutescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬茼蒿&T2_new_value=true&fr=y}}{蓬茼蒿}\index{蓬茼蒿} NA$^n$
  \end{itemize}
 \item[] \textit{Artemisia} 蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+annua}{\textit{A. annua} L.}  \index{Artemisia@\textit{Artemisia}!annua@\textit{annua}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花蒿&T2_new_value=true&fr=y}}{黃花蒿}\index{黃花蒿} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+anomala}{\textit{A. anomala} S.Moore}  \index{Artemisia@\textit{Artemisia}!anomala@\textit{anomala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=珍珠蒿&T2_new_value=true&fr=y}}{珍珠蒿}\index{珍珠蒿} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+capillaris}{\textit{A. capillaris} Thunb.}  \index{Artemisia@\textit{Artemisia}!capillaris@\textit{capillaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茵陳蒿&T2_new_value=true&fr=y}}{茵陳蒿}\index{茵陳蒿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+chingii}{\textit{A. chingii} Pamp.}  \index{Artemisia@\textit{Artemisia}!chingii@\textit{chingii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南毛蒿&T2_new_value=true&fr=y}}{南毛蒿}\index{南毛蒿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+fukudo}{\textit{A. fukudo} Makino}  \index{Artemisia@\textit{Artemisia}!fukudo@\textit{fukudo}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱艾&T2_new_value=true&fr=y}}{濱艾}\index{濱艾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+indica}{\textit{A. indica} Willd.}  \index{Artemisia@\textit{Artemisia}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=艾&T2_new_value=true&fr=y}}{艾}\index{艾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+japonica}{\textit{A. japonica} Thunb.}  \index{Artemisia@\textit{Artemisia}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牡蒿&T2_new_value=true&fr=y}}{牡蒿}\index{牡蒿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+kawakamii}{\textit{A. kawakamii} Hayata}  \index{Artemisia@\textit{Artemisia}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山艾&T2_new_value=true&fr=y}}{山艾}\index{山艾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+lancea}{\textit{A. lancea} Van.}  \index{Artemisia@\textit{Artemisia}!lancea@\textit{lancea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小艾&T2_new_value=true&fr=y}}{小艾}\index{小艾} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+morrisonensis}{\textit{A. morrisonensis} Hayata}  \index{Artemisia@\textit{Artemisia}!morrisonensis@\textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉山艾&T2_new_value=true&fr=y}}{細葉山艾}\index{細葉山艾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+niitakayamensis}{\textit{A. niitakayamensis} Hayata}  \index{Artemisia@\textit{Artemisia}!niitakayamensis@\textit{niitakayamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山艾&T2_new_value=true&fr=y}}{玉山艾}\index{玉山艾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+oligocarpa}{\textit{A. oligocarpa} Hayata}  \index{Artemisia@\textit{Artemisia}!oligocarpa@\textit{oligocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山艾&T2_new_value=true&fr=y}}{高山艾}\index{高山艾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+simulans}{\textit{A. simulans} Pamp.}  \index{Artemisia@\textit{Artemisia}!simulans@\textit{simulans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中南蒿&T2_new_value=true&fr=y}}{中南蒿}\index{中南蒿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+somai+var.+batakensis}{\textit{A. somai} Hayata var. \textit{batakensis} (Hayata) Kitam.}  \index{Artemisia@\textit{Artemisia}!somai@\textit{somai}!var. batakensis@var. \textit{batakensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣艾&T2_new_value=true&fr=y}}{太魯閣艾}\index{太魯閣艾}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+somai+var.+somai}{\textit{A. somai} Hayata var. \textit{somai}}  \index{Artemisia@\textit{Artemisia}!somai@\textit{somai}!var. somai@var. \textit{somai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=相馬氏艾&T2_new_value=true&fr=y}}{相馬氏艾}\index{相馬氏艾}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Artemisia+tsugitakaensis}{\textit{A. tsugitakaensis} (Kitam.) Ling \& Y.R.Ling}  \index{Artemisia@\textit{Artemisia}!tsugitakaensis@\textit{tsugitakaensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪山艾&T2_new_value=true&fr=y}}{雪山艾}\index{雪山艾}\# LC
  \end{itemize}
 \item[] \textit{Aster} 紫菀屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+ageratoides}{\textit{A. ageratoides} Turcz.}  \index{Aster@\textit{Aster}!ageratoides@\textit{ageratoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山白蘭&T2_new_value=true&fr=y}}{山白蘭}\index{山白蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+altaicus}{\textit{A. altaicus} Willd.}  \index{Aster@\textit{Aster}!altaicus@\textbf{\textit{altaicus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東鐵桿蒿&T2_new_value=true&fr=y}}{臺東鐵桿蒿}\index{臺東鐵桿蒿@{\Song{臺東鐵桿蒿}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+chingshuiensis}{\textit{A. chingshuiensis} Y.C.Liu \& C.H.Ou}  \index{Aster@\textit{Aster}!chingshuiensis@\textbf{\textit{chingshuiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水馬蘭&T2_new_value=true&fr=y}}{清水馬蘭}\index{清水馬蘭@{\Song{清水馬蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+formosanus}{\textit{A. formosanus} Hayata}  \index{Aster@\textit{Aster}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山白蘭&T2_new_value=true&fr=y}}{臺灣山白蘭}\index{臺灣山白蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+hispidus}{\textit{A. hispidus} Thunb.}  \index{Aster@\textit{Aster}!hispidus@\textit{hispidus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狗娃花&T2_new_value=true&fr=y}}{狗娃花}\index{狗娃花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+indicus}{\textit{A. indicus} L.}  \index{Aster@\textit{Aster}!indicus@\textit{indicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞兒腸&T2_new_value=true&fr=y}}{雞兒腸}\index{雞兒腸} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+itsunboshi}{\textit{A. itsunboshi} Kitam.}  \index{Aster@\textit{Aster}!itsunboshi@\textit{itsunboshi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大武山紫菀&T2_new_value=true&fr=y}}{大武山紫菀}\index{大武山紫菀}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+lasiocladus}{\textit{A. lasiocladus} Hayata}  \index{Aster@\textit{Aster}!lasiocladus@\textit{lasiocladus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絨山白蘭&T2_new_value=true&fr=y}}{絨山白蘭}\index{絨山白蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+morrisonensis}{\textit{A. morrisonensis} Hayata}  \index{Aster@\textit{Aster}!morrisonensis@\textbf{\textit{morrisonensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山鐵桿蒿&T2_new_value=true&fr=y}}{玉山鐵桿蒿}\index{玉山鐵桿蒿@{\Song{玉山鐵桿蒿}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+oldhamii}{\textit{A. oldhamii} Hemsl.}  \index{Aster@\textit{Aster}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣狗娃花&T2_new_value=true&fr=y}}{臺灣狗娃花}\index{臺灣狗娃花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+ovalifolius}{\textit{A. ovalifolius} Kitam.}  \index{Aster@\textit{Aster}!ovalifolius@\textbf{\textit{ovalifolius}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣紺菊&T2_new_value=true&fr=y}}{臺灣紺菊}\index{臺灣紺菊@{\Song{臺灣紺菊}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+shimadai}{\textit{A. shimadai} (Kitam.) Nemoto}  \index{Aster@\textit{Aster}!shimadai@\textbf{\textit{shimadai}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=島田氏雞兒腸&T2_new_value=true&fr=y}}{島田氏雞兒腸}\index{島田氏雞兒腸@{\Song{島田氏雞兒腸}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+subulatus+var.+sandwicensis}{\textit{A. subulatus} (Michx.) Hort. ex Michx. var. \textit{sandwicensis} (A.Gray) A.G.Jones}  \index{Aster@\textit{Aster}!subulatus@\textit{subulatus}!var. sandwicensis@var. \textit{sandwicensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澤掃帚菊&T2_new_value=true&fr=y}}{澤掃帚菊}\index{澤掃帚菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+subulatus+var.+subulatus}{\textit{A. subulatus} (Michx.) Hort. ex Michx. var. \textit{subulatus}}  \index{Aster@\textit{Aster}!subulatus@\textit{subulatus}!var. subulatus@var. \textit{subulatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掃帚菊&T2_new_value=true&fr=y}}{掃帚菊}\index{掃帚菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+taiwanensis}{\textit{A. taiwanensis} Kitam.}  \index{Aster@\textit{Aster}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣馬蘭&T2_new_value=true&fr=y}}{臺灣馬蘭}\index{臺灣馬蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+takasagomontanus}{\textit{A. takasagomontanus} Sasaki}  \index{Aster@\textit{Aster}!takasagomontanus@\textit{takasagomontanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪山馬蘭&T2_new_value=true&fr=y}}{雪山馬蘭}\index{雪山馬蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aster+taoyuenensis}{\textit{A. taoyuenensis} S.S.Ying}  \index{Aster@\textit{Aster}!taoyuenensis@\textbf{\textit{taoyuenensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桃園馬蘭&T2_new_value=true&fr=y}}{桃園馬蘭}\index{桃園馬蘭@{\Song{桃園馬蘭}}}\# EN
  \end{itemize}
 \item[] \textit{Austroeupatorium} 假澤蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Austroeupatorium+inulifolium}{\textit{A. inulifolium} (Kunth) R.M.King \& H.Rob.}  \index{Austroeupatorium@\textit{Austroeupatorium}!inulifolium@\textit{inulifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假澤蘭&T2_new_value=true&fr=y}}{假澤蘭}\index{假澤蘭} NA$^n$
  \end{itemize}
 \item[] \textit{Bellis} 雛菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bellis+perennis}{\textit{B. perennis} L.}  \index{Bellis@\textit{Bellis}!perennis@\textit{perennis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雛菊&T2_new_value=true&fr=y}}{雛菊}\index{雛菊} NA$^n$
  \end{itemize}
 \item[] \textit{Bidens} 鬼針屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+bipinnata}{\textit{B. bipinnata} L.}  \index{Bidens@\textit{Bidens}!bipinnata@\textit{bipinnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼針&T2_new_value=true&fr=y}}{鬼針}\index{鬼針} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+biternata}{\textit{B. biternata} (Lour.) Merr. \& Sherff}  \index{Bidens@\textit{Bidens}!biternata@\textit{biternata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼針舅&T2_new_value=true&fr=y}}{鬼針舅}\index{鬼針舅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+pilosa+var.+minor}{\textit{B. pilosa} L. var. \textit{minor} (Blume) Sherff}  \index{Bidens@\textit{Bidens}!pilosa@\textit{pilosa}!var. minor@var. \textit{minor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小白花鬼針&T2_new_value=true&fr=y}}{小白花鬼針}\index{小白花鬼針} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+pilosa+var.+pilosa}{\textit{B. pilosa} L. var. \textit{pilosa}}  \index{Bidens@\textit{Bidens}!pilosa@\textit{pilosa}!var. pilosa@var. \textit{pilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花鬼針&T2_new_value=true&fr=y}}{白花鬼針}\index{白花鬼針} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+pilosa+var.+radiata}{\textit{B. pilosa} L. var. \textit{radiata} (Sch.Bip.) Sherff}  \index{Bidens@\textit{Bidens}!pilosa@\textit{pilosa}!var. radiata@var. \textit{radiata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花咸豐草&T2_new_value=true&fr=y}}{大花咸豐草}\index{大花咸豐草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bidens+tripartita}{\textit{B. tripartita} L.}  \index{Bidens@\textit{Bidens}!tripartita@\textbf{\textit{tripartita}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狼把草&T2_new_value=true&fr=y}}{狼把草}\index{狼把草@{\Song{狼把草}}} VU
  \end{itemize}
 \item[] \textit{Blumea} 艾納香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+aromatica}{\textit{B. aromatica} DC.}  \index{Blumea@\textit{Blumea}!aromatica@\textit{aromatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉艾納香&T2_new_value=true&fr=y}}{薄葉艾納香}\index{薄葉艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+balsamifera}{\textit{B. balsamifera} (L.) DC.}  \index{Blumea@\textit{Blumea}!balsamifera@\textit{balsamifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=艾納香&T2_new_value=true&fr=y}}{艾納香}\index{艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+conspicua}{\textit{B. conspicua} Hayata}  \index{Blumea@\textit{Blumea}!conspicua@\textbf{\textit{conspicua}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花艾納香&T2_new_value=true&fr=y}}{大花艾納香}\index{大花艾納香@{\Song{大花艾納香}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+formosana}{\textit{B. formosana} Kitam.}  \index{Blumea@\textit{Blumea}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白艾納香&T2_new_value=true&fr=y}}{裏白艾納香}\index{裏白艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+hieracifolia}{\textit{B. hieracifolia} (D.Don) DC.}  \index{Blumea@\textit{Blumea}!hieracifolia@\textit{hieracifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛將軍&T2_new_value=true&fr=y}}{毛將軍}\index{毛將軍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+lacera}{\textit{B. lacera} (Burm.f.) DC.}  \index{Blumea@\textit{Blumea}!lacera@\textit{lacera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=生毛將軍&T2_new_value=true&fr=y}}{生毛將軍}\index{生毛將軍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+laciniata}{\textit{B. laciniata} (Roxb.) DC.}  \index{Blumea@\textit{Blumea}!laciniata@\textit{laciniata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂葉艾納香&T2_new_value=true&fr=y}}{裂葉艾納香}\index{裂葉艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+lanceolaria}{\textit{B. lanceolaria} (Roxb.) Druce}  \index{Blumea@\textit{Blumea}!lanceolaria@\textit{lanceolaria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=走馬胎&T2_new_value=true&fr=y}}{走馬胎}\index{走馬胎} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+linearis}{\textit{B. linearis} C.I Peng \& W.P.Leu}  \index{Blumea@\textit{Blumea}!linearis@\textbf{\textit{linearis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉艾納香&T2_new_value=true&fr=y}}{狹葉艾納香}\index{狹葉艾納香@{\Song{狹葉艾納香}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+mollis}{\textit{B. mollis} (D.Don) Merr.}  \index{Blumea@\textit{Blumea}!mollis@\textit{mollis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柔毛艾納香&T2_new_value=true&fr=y}}{柔毛艾納香}\index{柔毛艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+oblongifolia}{\textit{B. oblongifolia} Kitam.}  \index{Blumea@\textit{Blumea}!oblongifolia@\textbf{\textit{oblongifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣艾納香&T2_new_value=true&fr=y}}{臺灣艾納香}\index{臺灣艾納香@{\Song{臺灣艾納香}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+riparia+var.+megacephala}{\textit{B. riparia} (Blume) DC. var. \textit{megacephala} Randeria}  \index{Blumea@\textit{Blumea}!riparia@\textit{riparia}!var. megacephala@var. \textit{megacephala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大頭艾納香&T2_new_value=true&fr=y}}{大頭艾納香}\index{大頭艾納香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blumea+viscosa}{\textit{B. viscosa} (Mill.) V.M.Badillo}  \index{Blumea@\textit{Blumea}!viscosa@\textit{viscosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛假蓬舅&T2_new_value=true&fr=y}}{毛假蓬舅}\index{毛假蓬舅} NA$^n$
  \end{itemize}
 \item[] \textit{Calyptocarpus} 金腰箭舅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calyptocarpus+vialis}{\textit{C. vialis} Less.}  \index{Calyptocarpus@\textit{Calyptocarpus}!vialis@\textit{vialis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金腰箭舅&T2_new_value=true&fr=y}}{金腰箭舅}\index{金腰箭舅} NA$^n$
  \end{itemize}
 \item[] \textit{Carpesium} 天名精屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carpesium+abrotanoides}{\textit{C. abrotanoides} L.}  \index{Carpesium@\textit{Carpesium}!abrotanoides@\textbf{\textit{abrotanoides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天名精&T2_new_value=true&fr=y}}{天名精}\index{天名精@{\Song{天名精}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carpesium+cernuum}{\textit{C. cernuum} L.}  \index{Carpesium@\textit{Carpesium}!cernuum@\textbf{\textit{cernuum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杓兒菜&T2_new_value=true&fr=y}}{杓兒菜}\index{杓兒菜@{\Song{杓兒菜}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carpesium+divaricatum}{\textit{C. divaricatum} Siebold \& Zucc.}  \index{Carpesium@\textit{Carpesium}!divaricatum@\textit{divaricatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=煙管草&T2_new_value=true&fr=y}}{煙管草}\index{煙管草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carpesium+minus}{\textit{C. minus} Hemsl.}  \index{Carpesium@\textit{Carpesium}!minus@\textit{minus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細川氏天名精&T2_new_value=true&fr=y}}{細川氏天名精}\index{細川氏天名精} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carpesium+nepalense}{\textit{C. nepalense} Less.}  \index{Carpesium@\textit{Carpesium}!nepalense@\textit{nepalense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃金珠&T2_new_value=true&fr=y}}{黃金珠}\index{黃金珠} LC
  \end{itemize}
 \item[] \textit{Centipeda} 石胡荽屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Centipeda+minima}{\textit{C. minima} (L.) A.Br. \& Asch.}  \index{Centipeda@\textit{Centipeda}!minima@\textit{minima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石胡荽&T2_new_value=true&fr=y}}{石胡荽}\index{石胡荽} LC
  \end{itemize}
 \item[] \textit{Centratherum} 鈕扣花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Centratherum+punctatum+subsp.+fruticosum}{\textit{C. punctatum} Cass. subsp. \textit{fruticosum} (Vidal) Kirkman}  \index{Centratherum@\textit{Centratherum}!punctatum@\textit{punctatum}!subsp. fruticosum@subsp. \textit{fruticosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲律賓鈕釦花&T2_new_value=true&fr=y}}{菲律賓鈕釦花}\index{菲律賓鈕釦花} NA$^n$
  \end{itemize}
 \item[] \textit{Chromolaena} 香澤蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chromolaena+odorata}{\textit{C. odorata} (L.) R.M.King \& H.Rob.}  \index{Chromolaena@\textit{Chromolaena}!odorata@\textit{odorata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香澤蘭&T2_new_value=true&fr=y}}{香澤蘭}\index{香澤蘭} NA$^n$
  \end{itemize}
 \item[] \textit{Cichorium} 菊苣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cichorium+intybus}{\textit{C. intybus} L.}  \index{Cichorium@\textit{Cichorium}!intybus@\textit{intybus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菊苣&T2_new_value=true&fr=y}}{菊苣}\index{菊苣} NA$^n$
  \end{itemize}
 \item[] \textit{Cirsium} 薊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+arisanense}{\textit{C. arisanense} Kitam.}  \index{Cirsium@\textit{Cirsium}!arisanense@\textit{arisanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山薊&T2_new_value=true&fr=y}}{阿里山薊}\index{阿里山薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+brevicaule}{\textit{C. brevicaule} A.Gray}  \index{Cirsium@\textit{Cirsium}!brevicaule@\textit{brevicaule}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞觴刺&T2_new_value=true&fr=y}}{雞觴刺}\index{雞觴刺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+ferum}{\textit{C. ferum} Kitam.}  \index{Cirsium@\textit{Cirsium}!ferum@\textit{ferum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鱗毛薊&T2_new_value=true&fr=y}}{鱗毛薊}\index{鱗毛薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+hosokawae}{\textit{C. hosokawae} Kitam.}  \index{Cirsium@\textit{Cirsium}!hosokawae@\textit{hosokawae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細川氏薊&T2_new_value=true&fr=y}}{細川氏薊}\index{細川氏薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+japonicum+var.+australe}{\textit{C. japonicum} DC. var. \textit{australe} Kitam.}  \index{Cirsium@\textit{Cirsium}!japonicum@\textit{japonicum}!var. australe@var. \textit{australe}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南國小薊&T2_new_value=true&fr=y}}{南國小薊}\index{南國小薊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+japonicum+var.+takaoense}{\textit{C. japonicum} DC. var. \textit{takaoense} Kitam.}  \index{Cirsium@\textit{Cirsium}!japonicum@\textit{japonicum}!var. takaoense@var. \textit{takaoense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花小薊&T2_new_value=true&fr=y}}{白花小薊}\index{白花小薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+kawakamii}{\textit{C. kawakamii} Hayata}  \index{Cirsium@\textit{Cirsium}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山薊&T2_new_value=true&fr=y}}{玉山薊}\index{玉山薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+lineare}{\textit{C. lineare} (Thunb.) Sch.Bip.}  \index{Cirsium@\textit{Cirsium}!lineare@\textbf{\textit{lineare}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華薊&T2_new_value=true&fr=y}}{華薊}\index{華薊@{\Song{華薊}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+morii}{\textit{C. morii} Hayata}  \index{Cirsium@\textit{Cirsium}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏薊&T2_new_value=true&fr=y}}{森氏薊}\index{森氏薊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cirsium+suzukii}{\textit{C. suzukii} Kitam.}  \index{Cirsium@\textit{Cirsium}!suzukii@\textit{suzukii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈴木氏薊&T2_new_value=true&fr=y}}{鈴木氏薊}\index{鈴木氏薊}\# LC
  \end{itemize}
 \item[] \textit{Clibadium} 蘇利南野菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clibadium+surinamense}{\textit{C. surinamense} L.}  \index{Clibadium@\textit{Clibadium}!surinamense@\textit{surinamense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘇利南野菊&T2_new_value=true&fr=y}}{蘇利南野菊}\index{蘇利南野菊} NA$^n$
  \end{itemize}
 \item[] \textit{Conyza} 假蓬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+aegyptiaca}{\textit{C. aegyptiaca} (L.) Aiton}  \index{Conyza@\textit{Conyza}!aegyptiaca@\textbf{\textit{aegyptiaca}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=埃及假蓬&T2_new_value=true&fr=y}}{埃及假蓬}\index{埃及假蓬@{\Song{埃及假蓬}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+bonariensis}{\textit{C. bonariensis} (L.) Cronq.}  \index{Conyza@\textit{Conyza}!bonariensis@\textit{bonariensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=美洲假蓬&T2_new_value=true&fr=y}}{美洲假蓬}\index{美洲假蓬} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+canadensis+var.+canadensis}{\textit{C. canadensis} (L.) Cronq. var. \textit{canadensis}}  \index{Conyza@\textit{Conyza}!canadensis@\textit{canadensis}!var. canadensis@var. \textit{canadensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=加拿大蓬&T2_new_value=true&fr=y}}{加拿大蓬}\index{加拿大蓬} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+canadensis+var.+pusilla}{\textit{C. canadensis} (L.) Cronq. var. \textit{pusilla} (Nutt.) Cronq.}  \index{Conyza@\textit{Conyza}!canadensis@\textit{canadensis}!var. pusilla@var. \textit{pusilla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光莖飛蓬&T2_new_value=true&fr=y}}{光莖飛蓬}\index{光莖飛蓬} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+japonica}{\textit{C. japonica} (Thunb.) Less.}  \index{Conyza@\textit{Conyza}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本假蓬&T2_new_value=true&fr=y}}{日本假蓬}\index{日本假蓬} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+leucantha}{\textit{C. leucantha} (D.Don) Ludlow \& P.H.Raven}  \index{Conyza@\textit{Conyza}!leucantha@\textit{leucantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粘毛假蓬&T2_new_value=true&fr=y}}{粘毛假蓬}\index{粘毛假蓬} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conyza+sumatrensis}{\textit{C. sumatrensis} (Retz.) Walker}  \index{Conyza@\textit{Conyza}!sumatrensis@\textit{sumatrensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野茼蒿&T2_new_value=true&fr=y}}{野茼蒿}\index{野茼蒿} NA$^n$
  \end{itemize}
 \item[] \textit{Coreopsis} 金雞菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coreopsis+tinctoria}{\textit{C. tinctoria} Nutt.}  \index{Coreopsis@\textit{Coreopsis}!tinctoria@\textit{tinctoria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=波斯菊&T2_new_value=true&fr=y}}{波斯菊}\index{波斯菊} NA$^n$
  \end{itemize}
 \item[] \textit{Cosmos} 秋英屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cosmos+bipinnatus}{\textit{C. bipinnatus} Cav.}  \index{Cosmos@\textit{Cosmos}!bipinnatus@\textit{bipinnatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大波斯菊&T2_new_value=true&fr=y}}{大波斯菊}\index{大波斯菊} NA$^n$
  \end{itemize}
 \item[] \textit{Cotula} 山莞荽屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotula+australis}{\textit{C. australis} (Sieber ex Spreng.) Hook.f.}  \index{Cotula@\textit{Cotula}!australis@\textit{australis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南方山芫荽&T2_new_value=true&fr=y}}{南方山芫荽}\index{南方山芫荽} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotula+hemisphaerica}{\textit{C. hemisphaerica} Wall. ex Benth. \& Hook.}  \index{Cotula@\textit{Cotula}!hemisphaerica@\textbf{\textit{hemisphaerica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山芫荽&T2_new_value=true&fr=y}}{山芫荽}\index{山芫荽@{\Song{山芫荽}}} EN
  \end{itemize}
 \item[] \textit{Crassocephalum} 昭和草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crassocephalum+crepidioides}{\textit{C. crepidioides} (Benth.) S.Moore}  \index{Crassocephalum@\textit{Crassocephalum}!crepidioides@\textit{crepidioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=昭和草&T2_new_value=true&fr=y}}{昭和草}\index{昭和草} NA$^n$
  \end{itemize}
 \item[] \textit{Crepidiastrum} 假黃鵪菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidiastrum+lanceolatum}{\textit{C. lanceolatum} (Houtt.) Nakai}  \index{Crepidiastrum@\textit{Crepidiastrum}!lanceolatum@\textit{lanceolatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉假黃鵪菜&T2_new_value=true&fr=y}}{細葉假黃鵪菜}\index{細葉假黃鵪菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidiastrum+taiwanianum}{\textit{C. taiwanianum} Nakai}  \index{Crepidiastrum@\textit{Crepidiastrum}!taiwanianum@\textit{taiwanianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣假黃鵪菜&T2_new_value=true&fr=y}}{臺灣假黃鵪菜}\index{臺灣假黃鵪菜}\# NT
  \end{itemize}
 \item[] \textit{Crossostephium} 蘄艾屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crossostephium+chinense}{\textit{C. chinense} (L.) Makino}  \index{Crossostephium@\textit{Crossostephium}!chinense@\textbf{\textit{chinense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘄艾&T2_new_value=true&fr=y}}{蘄艾}\index{蘄艾@{\Song{蘄艾}}} VU
  \end{itemize}
 \item[] \textit{Dendranthema} 菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendranthema+arisanense}{\textit{D. arisanense} (Hayata) Y.Ling \& C.Shih}  \index{Dendranthema@\textit{Dendranthema}!arisanense@\textit{arisanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山油菊&T2_new_value=true&fr=y}}{阿里山油菊}\index{阿里山油菊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendranthema+horaimontana}{\textit{D. horaimontana} (Masam.) S.S.Ying}  \index{Dendranthema@\textit{Dendranthema}!horaimontana@\textbf{\textit{horaimontana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊油菊&T2_new_value=true&fr=y}}{蓬萊油菊}\index{蓬萊油菊@{\Song{蓬萊油菊}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendranthema+indicum}{\textit{D. indicum} (L.) Des Moul.}  \index{Dendranthema@\textit{Dendranthema}!indicum@\textit{indicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=油菊&T2_new_value=true&fr=y}}{油菊}\index{油菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendranthema+lavandulifolium+var.+tomentellum}{\textit{D. lavandulifolium} (Fisch. ex Trautv.) Y.Ling \& C.Shih var. \textit{tomentellum} (Hand.-Mazz.) Y.Ling \& C.Shih}  \index{Dendranthema@\textit{Dendranthema}!lavandulifolium@\textit{lavandulifolium}!var. tomentellum@\textbf{var. \textit{tomentellum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=新竹油菊&T2_new_value=true&fr=y}}{新竹油菊}\index{新竹油菊@{\Song{新竹油菊}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendranthema+morii}{\textit{D. morii} (Hayata) Kitam.}  \index{Dendranthema@\textit{Dendranthema}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏菊&T2_new_value=true&fr=y}}{森氏菊}\index{森氏菊}\# NT
  \end{itemize}
 \item[] \textit{Dichrocephala} 魚眼草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dichrocephala+integrifolia}{\textit{D. integrifolia} (L.f.) Kuntze}  \index{Dichrocephala@\textit{Dichrocephala}!integrifolia@\textit{integrifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茯苓菜&T2_new_value=true&fr=y}}{茯苓菜}\index{茯苓菜} LC
  \end{itemize}
 \item[] \textit{Echinops} 漏盧屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Echinops+grijsii}{\textit{E. grijsii} Hance}  \index{Echinops@\textit{Echinops}!grijsii@\textbf{\textit{grijsii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=漏盧&T2_new_value=true&fr=y}}{漏盧}\index{漏盧@{\Song{漏盧}}} CR
  \end{itemize}
 \item[] \textit{Eclipta} 鱧腸屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eclipta+prostrata}{\textit{E. prostrata} (L.) L.}  \index{Eclipta@\textit{Eclipta}!prostrata@\textit{prostrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鱧腸&T2_new_value=true&fr=y}}{鱧腸}\index{鱧腸} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eclipta+zippeliana}{\textit{E. zippeliana} Blume}  \index{Eclipta@\textit{Eclipta}!zippeliana@\textit{zippeliana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛鱧腸&T2_new_value=true&fr=y}}{毛鱧腸}\index{毛鱧腸} NA$^n$
  \end{itemize}
 \item[] \textit{Elephantopus} 地膽草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elephantopus+mollis}{\textit{E. mollis} Kunth}  \index{Elephantopus@\textit{Elephantopus}!mollis@\textit{mollis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=地膽草&T2_new_value=true&fr=y}}{地膽草}\index{地膽草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elephantopus+scaber}{\textit{E. scaber} L.}  \index{Elephantopus@\textit{Elephantopus}!scaber@\textit{scaber}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=燈豎朽&T2_new_value=true&fr=y}}{燈豎朽}\index{燈豎朽} LC
  \end{itemize}
 \item[] \textit{Eleutheranthera} 離葯金腰箭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleutheranthera+ruderalis}{\textit{E. ruderalis} (Swartz) Sch.Bip.}  \index{Eleutheranthera@\textit{Eleutheranthera}!ruderalis@\textit{ruderalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=離葯金腰箭&T2_new_value=true&fr=y}}{離葯金腰箭}\index{離葯金腰箭} NA$^n$
  \end{itemize}
 \item[] \textit{Emilia} 紫背草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Emilia+fosbergii}{\textit{E. fosbergii} Nicolson}  \index{Emilia@\textit{Emilia}!fosbergii@\textit{fosbergii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=纓絨花&T2_new_value=true&fr=y}}{纓絨花}\index{纓絨花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Emilia+praetermissa}{\textit{E. praetermissa} Milne-Redh.}  \index{Emilia@\textit{Emilia}!praetermissa@\textit{praetermissa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粉黃纓絨花&T2_new_value=true&fr=y}}{粉黃纓絨花}\index{粉黃纓絨花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Emilia+sonchifolia+var.+javanica}{\textit{E. sonchifolia} (L.) DC. var. \textit{javanica} (Burm.f.) Mattfeld}  \index{Emilia@\textit{Emilia}!sonchifolia@\textit{sonchifolia}!var. javanica@var. \textit{javanica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫背草&T2_new_value=true&fr=y}}{紫背草}\index{紫背草} LC
  \end{itemize}
 \item[] \textit{Epaltes} 鵝不食草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epaltes+australis}{\textit{E. australis} Less.}  \index{Epaltes@\textit{Epaltes}!australis@\textbf{\textit{australis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝不食草&T2_new_value=true&fr=y}}{鵝不食草}\index{鵝不食草@{\Song{鵝不食草}}} EN
  \end{itemize}
 \item[] \textit{Erechtites} 饑荒草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erechtites+hieraciifolius+var.+cacalioides}{\textit{E. hieraciifolius} (L.) Raf. ex DC. var. \textit{cacalioides} (Fisch. ex Spreng.) Griseb.}  \index{Erechtites@\textit{Erechtites}!hieraciifolius@\textit{hieraciifolius}!var. cacalioides@var. \textit{cacalioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛饑荒草&T2_new_value=true&fr=y}}{粗毛饑荒草}\index{粗毛饑荒草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erechtites+hieraciifolius+var.+hieraciifolius}{\textit{E. hieraciifolius} (L.) Raf. ex DC. var. \textit{hieraciifolius}}  \index{Erechtites@\textit{Erechtites}!hieraciifolius@\textit{hieraciifolius}!var. hieraciifolius@var. \textit{hieraciifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=饑荒草&T2_new_value=true&fr=y}}{饑荒草}\index{饑荒草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erechtites+valerianifolia}{\textit{E. valerianifolia} (Link ex Wolf) Less. ex DC.}  \index{Erechtites@\textit{Erechtites}!valerianifolia@\textit{valerianifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=飛機草&T2_new_value=true&fr=y}}{飛機草}\index{飛機草} NA$^n$
  \end{itemize}
 \item[] \textit{Erigeron} 飛蓬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erigeron+annuus}{\textit{E. annuus} (L.) Pers.}  \index{Erigeron@\textit{Erigeron}!annuus@\textit{annuus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白頂飛蓬&T2_new_value=true&fr=y}}{白頂飛蓬}\index{白頂飛蓬} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erigeron+bellioides}{\textit{E. bellioides} DC.}  \index{Erigeron@\textit{Erigeron}!bellioides@\textit{bellioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=類雛菊飛蓬&T2_new_value=true&fr=y}}{類雛菊飛蓬}\index{類雛菊飛蓬} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erigeron+morrisonensis+var.+fukuyamae}{\textit{E. morrisonensis} Hayata var. \textit{fukuyamae} (Kitam.) Kitam.}  \index{Erigeron@\textit{Erigeron}!morrisonensis@\textit{morrisonensis}!var. fukuyamae@var. \textit{fukuyamae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=福山氏飛蓬&T2_new_value=true&fr=y}}{福山氏飛蓬}\index{福山氏飛蓬}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erigeron+morrisonensis+var.+morrisonensis}{\textit{E. morrisonensis} Hayata var. \textit{morrisonensis}}  \index{Erigeron@\textit{Erigeron}!morrisonensis@\textit{morrisonensis}!var. morrisonensis@var. \textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山飛蓬&T2_new_value=true&fr=y}}{玉山飛蓬}\index{玉山飛蓬}\# LC
  \end{itemize}
 \item[] \textit{Eupatorium} 澤蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+amabile}{\textit{E. amabile} Kitam.}  \index{Eupatorium@\textit{Eupatorium}!amabile@\textit{amabile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺葉澤蘭&T2_new_value=true&fr=y}}{腺葉澤蘭}\index{腺葉澤蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+chinense+var.+tozanense}{\textit{E. chinense} L. var. \textit{tozanense} (Hayata) Kitam.}  \index{Eupatorium@\textit{Eupatorium}!chinense@\textit{chinense}!var. tozanense@var. \textit{tozanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=塔山澤蘭&T2_new_value=true&fr=y}}{塔山澤蘭}\index{塔山澤蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+clematideum+var.+clematideum}{\textit{E. clematideum} (Wall. ex DC.) Sch.Bip. var. \textit{clematideum}}  \index{Eupatorium@\textit{Eupatorium}!clematideum@\textit{clematideum}!var. clematideum@var. \textit{clematideum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田代氏澤蘭&T2_new_value=true&fr=y}}{田代氏澤蘭}\index{田代氏澤蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+clematideum+var.+gracillimum}{\textit{E. clematideum} (Wall. ex DC.) Sch.Bip. var. \textit{gracillimum} (Hayata) C.I Peng \& S.W.Chung}  \index{Eupatorium@\textit{Eupatorium}!clematideum@\textit{clematideum}!var. gracillimum@\textbf{var. \textit{gracillimum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛澤蘭&T2_new_value=true&fr=y}}{高士佛澤蘭}\index{高士佛澤蘭@{\Song{高士佛澤蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+formosanum}{\textit{E. formosanum} Hayata}  \index{Eupatorium@\textit{Eupatorium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣澤蘭&T2_new_value=true&fr=y}}{臺灣澤蘭}\index{臺灣澤蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+hualienense}{\textit{E. hualienense} C.H.Ou, S.W.Chung \& C.I Peng}  \index{Eupatorium@\textit{Eupatorium}!hualienense@\textit{hualienense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=花蓮澤蘭&T2_new_value=true&fr=y}}{花蓮澤蘭}\index{花蓮澤蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+kiirunense}{\textit{E. kiirunense} (Kitam.) C.H.Ou \& S.W.Chung}  \index{Eupatorium@\textit{Eupatorium}!kiirunense@\textit{kiirunense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基隆澤蘭&T2_new_value=true&fr=y}}{基隆澤蘭}\index{基隆澤蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+lindleyanum}{\textit{E. lindleyanum} DC.}  \index{Eupatorium@\textit{Eupatorium}!lindleyanum@\textbf{\textit{lindleyanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=林氏澤蘭&T2_new_value=true&fr=y}}{林氏澤蘭}\index{林氏澤蘭@{\Song{林氏澤蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eupatorium+shimadaiKitam.}{\textit{E. shimadaiKitam.} }  \index{Eupatorium@\textit{Eupatorium}!shimadaiKitam.@\textit{shimadaiKitam.}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=島田氏澤蘭&T2_new_value=true&fr=y}}{島田氏澤蘭}\index{島田氏澤蘭}\# LC
  \end{itemize}
 \item[] \textit{Farfugium} 山菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Farfugium+japonicum+var.+formosanum}{\textit{F. japonicum} (L.) Kitam. var. \textit{formosanum} (Hayata) Kitam.}  \index{Farfugium@\textit{Farfugium}!japonicum@\textit{japonicum}!var. formosanum@var. \textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山菊&T2_new_value=true&fr=y}}{臺灣山菊}\index{臺灣山菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Farfugium+japonicum+var.+japonicum}{\textit{F. japonicum} (L.) Kitam. var. \textit{japonicum}}  \index{Farfugium@\textit{Farfugium}!japonicum@\textit{japonicum}!var. japonicum@var. \textit{japonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山菊&T2_new_value=true&fr=y}}{山菊}\index{山菊} NT
  \end{itemize}
 \item[] \textit{Flaveria} 黃頂菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flaveria+bidentis}{\textit{F. bidentis} (L.) Kuntze}  \index{Flaveria@\textit{Flaveria}!bidentis@\textit{bidentis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃頂菊&T2_new_value=true&fr=y}}{黃頂菊}\index{黃頂菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flaveria+linearis}{\textit{F. linearis} Lag.}  \index{Flaveria@\textit{Flaveria}!linearis@\textit{linearis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=線葉黃頂菊&T2_new_value=true&fr=y}}{線葉黃頂菊}\index{線葉黃頂菊} NA$^n$
  \end{itemize}
 \item[] \textit{Gaillardia} 天人菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gaillardia+pulchella}{\textit{G. pulchella} Foug.}  \index{Gaillardia@\textit{Gaillardia}!pulchella@\textit{pulchella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天人菊&T2_new_value=true&fr=y}}{天人菊}\index{天人菊} NA$^n$
  \end{itemize}
 \item[] \textit{Galinsoga} 小米菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galinsoga+parviflora}{\textit{G. parviflora} Cav.}  \index{Galinsoga@\textit{Galinsoga}!parviflora@\textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小米菊&T2_new_value=true&fr=y}}{小米菊}\index{小米菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galinsoga+quadriradiata}{\textit{G. quadriradiata} Ruiz \& Pav.}  \index{Galinsoga@\textit{Galinsoga}!quadriradiata@\textit{quadriradiata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛小米菊&T2_new_value=true&fr=y}}{粗毛小米菊}\index{粗毛小米菊} NA$^n$
  \end{itemize}
 \item[] \textit{Gerbera} 大丁草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gerbera+anandria}{\textit{G. anandria} (L.) Sch.Bip}  \index{Gerbera@\textit{Gerbera}!anandria@\textbf{\textit{anandria}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大丁草&T2_new_value=true&fr=y}}{大丁草}\index{大丁草@{\Song{大丁草}}} CR
  \end{itemize}
 \item[] \textit{Glossocardia} 香茹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glossocardia+bidens}{\textit{G. bidens} (Retz.) Veldkamp}  \index{Glossocardia@\textit{Glossocardia}!bidens@\textbf{\textit{bidens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香茹&T2_new_value=true&fr=y}}{香茹}\index{香茹@{\Song{香茹}}} VU
  \end{itemize}
 \item[] \textit{Gnaphalium} 鼠麴草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+adnatum}{\textit{G. adnatum} Wall. ex DC.}  \index{Gnaphalium@\textit{Gnaphalium}!adnatum@\textit{adnatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅面番&T2_new_value=true&fr=y}}{紅面番}\index{紅面番} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+calviceps}{\textit{G. calviceps} Fernald}  \index{Gnaphalium@\textit{Gnaphalium}!calviceps@\textit{calviceps}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=直莖鼠麴草&T2_new_value=true&fr=y}}{直莖鼠麴草}\index{直莖鼠麴草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+hypoleucum+var.+amoyense}{\textit{G. hypoleucum} DC. var. \textit{amoyense} (Hance) Hand.-Mazz.}  \index{Gnaphalium@\textit{Gnaphalium}!hypoleucum@\textit{hypoleucum}!var. amoyense@var. \textit{amoyense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假秋鼠麴草&T2_new_value=true&fr=y}}{假秋鼠麴草}\index{假秋鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+hypoleucum+var.+hypoleucum}{\textit{G. hypoleucum} DC. var. \textit{hypoleucum}}  \index{Gnaphalium@\textit{Gnaphalium}!hypoleucum@\textit{hypoleucum}!var. hypoleucum@var. \textit{hypoleucum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=秋鼠麴草&T2_new_value=true&fr=y}}{秋鼠麴草}\index{秋鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+involucratum+var.+ramosum}{\textit{G. involucratum} Forst. var. \textit{ramosum} DC.}  \index{Gnaphalium@\textit{Gnaphalium}!involucratum@\textit{involucratum}!var. ramosum@var. \textit{ramosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=分枝鼠麴草&T2_new_value=true&fr=y}}{分枝鼠麴草}\index{分枝鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+involucratum+var.+simplex}{\textit{G. involucratum} Forst. var. \textit{simplex} DC.}  \index{Gnaphalium@\textit{Gnaphalium}!involucratum@\textit{involucratum}!var. simplex@var. \textit{simplex}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉鼠麴草&T2_new_value=true&fr=y}}{細葉鼠麴草}\index{細葉鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+japonicum}{\textit{G. japonicum} Thunb.}  \index{Gnaphalium@\textit{Gnaphalium}!japonicum@\textit{japonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=父子草&T2_new_value=true&fr=y}}{父子草}\index{父子草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+luteoalbum+subsp.+affine}{\textit{G. luteoalbum} L. subsp. \textit{affine} (D.Don) Koster}  \index{Gnaphalium@\textit{Gnaphalium}!luteoalbum@\textit{luteoalbum}!subsp. affine@subsp. \textit{affine}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鼠麴草&T2_new_value=true&fr=y}}{鼠麴草}\index{鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+luteoalbum+subsp.+luteoalbum}{\textit{G. luteoalbum} L. subsp. \textit{luteoalbum}}  \index{Gnaphalium@\textit{Gnaphalium}!luteoalbum@\textit{luteoalbum}!subsp. luteoalbum@subsp. \textit{luteoalbum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絲綿草&T2_new_value=true&fr=y}}{絲綿草}\index{絲綿草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+pensylvanicum}{\textit{G. pensylvanicum} Willd.}  \index{Gnaphalium@\textit{Gnaphalium}!pensylvanicum@\textit{pensylvanicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匙葉鼠麴草&T2_new_value=true&fr=y}}{匙葉鼠麴草}\index{匙葉鼠麴草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+polycaulon}{\textit{G. polycaulon} Pers.}  \index{Gnaphalium@\textit{Gnaphalium}!polycaulon@\textit{polycaulon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多莖鼠麴草&T2_new_value=true&fr=y}}{多莖鼠麴草}\index{多莖鼠麴草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+purpureum}{\textit{G. purpureum} L.}  \index{Gnaphalium@\textit{Gnaphalium}!purpureum@\textit{purpureum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鼠麴舅&T2_new_value=true&fr=y}}{鼠麴舅}\index{鼠麴舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gnaphalium+spicatum}{\textit{G. spicatum} Lam.}  \index{Gnaphalium@\textit{Gnaphalium}!spicatum@\textit{spicatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白鼠麴草&T2_new_value=true&fr=y}}{裏白鼠麴草}\index{裏白鼠麴草} NA$^n$
  \end{itemize}
 \item[] \textit{Grangea} 線球菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Grangea+maderaspatana}{\textit{G. maderaspatana} (L.) Poir.}  \index{Grangea@\textit{Grangea}!maderaspatana@\textit{maderaspatana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=線球菊&T2_new_value=true&fr=y}}{線球菊}\index{線球菊} NA$^n$
  \end{itemize}
 \item[] \textit{Guizotia} 小油菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Guizotia+abyssinica}{\textit{G. abyssinica} (L.f.) Cass.}  \index{Guizotia@\textit{Guizotia}!abyssinica@\textit{abyssinica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小油菊&T2_new_value=true&fr=y}}{小油菊}\index{小油菊} NA$^n$
  \end{itemize}
 \item[] \textit{Gymnocoronis} 光冠水菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gymnocoronis+spilanthoides}{\textit{G. spilanthoides} (D.Don ex Hook. \& Arn.) DC.}  \index{Gymnocoronis@\textit{Gymnocoronis}!spilanthoides@\textit{spilanthoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光冠水菊&T2_new_value=true&fr=y}}{光冠水菊}\index{光冠水菊} NA$^n$
  \end{itemize}
 \item[] \textit{Gynura} 三七草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gynura+bicolor}{\textit{G. bicolor} (Roxb. \& Willd.) DC.}  \index{Gynura@\textit{Gynura}!bicolor@\textit{bicolor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅鳳菜&T2_new_value=true&fr=y}}{紅鳳菜}\index{紅鳳菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gynura+divaricata+subsp.+formosana}{\textit{G. divaricata} (L.) DC. subsp. \textit{formosana} (Kitam.) F.G.Davies}  \index{Gynura@\textit{Gynura}!divaricata@\textit{divaricata}!subsp. formosana@subsp. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白鳳菜&T2_new_value=true&fr=y}}{白鳳菜}\index{白鳳菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gynura+elliptica}{\textit{G. elliptica} Yabe \& Hayata}  \index{Gynura@\textit{Gynura}!elliptica@\textbf{\textit{elliptica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼木耳菜&T2_new_value=true&fr=y}}{蘭嶼木耳菜}\index{蘭嶼木耳菜@{\Song{蘭嶼木耳菜}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gynura+japonica}{\textit{G. japonica} (Thunb.) Juel}  \index{Gynura@\textit{Gynura}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花三七草&T2_new_value=true&fr=y}}{黃花三七草}\index{黃花三七草} LC
  \end{itemize}
 \item[] \textit{Helianthus} 向日葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Helianthus+debilis+subsp.+cucumerifolius}{\textit{H. debilis} Nuttall subsp. \textit{cucumerifolius} (Torrey \& A.Gray) Heiser}  \index{Helianthus@\textit{Helianthus}!debilis@\textit{debilis}!subsp. cucumerifolius@subsp. \textit{cucumerifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓜葉向日葵&T2_new_value=true&fr=y}}{瓜葉向日葵}\index{瓜葉向日葵} NA$^n$
  \end{itemize}
 \item[] \textit{Hemistepta} 泥胡菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemistepta+lyrata}{\textit{H. lyrata} (Bunge) Bunge}  \index{Hemistepta@\textit{Hemistepta}!lyrata@\textit{lyrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泥胡菜&T2_new_value=true&fr=y}}{泥胡菜}\index{泥胡菜} LC
  \end{itemize}
 \item[] \textit{Hieracium} 山柳菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hieracium+morii}{\textit{H. morii} Hayata}  \index{Hieracium@\textit{Hieracium}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏山柳菊&T2_new_value=true&fr=y}}{森氏山柳菊}\index{森氏山柳菊}\# LC
  \end{itemize}
 \item[] \textit{Hypochaeris} 貓兒菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypochaeris+chillensis}{\textit{H. chillensis} (Kunth) Britton}  \index{Hypochaeris@\textit{Hypochaeris}!chillensis@\textit{chillensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=智利貓兒菊&T2_new_value=true&fr=y}}{智利貓兒菊}\index{智利貓兒菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypochaeris+glabra}{\textit{H. glabra} L.}  \index{Hypochaeris@\textit{Hypochaeris}!glabra@\textit{glabra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光貓兒菊&T2_new_value=true&fr=y}}{光貓兒菊}\index{光貓兒菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypochaeris+microcephala+var.+albiflora}{\textit{H. microcephala} (Sch. Bip.) Cabrera var. \textit{albiflora} (Kuntze) Cabrera}  \index{Hypochaeris@\textit{Hypochaeris}!microcephala@\textit{microcephala}!var. albiflora@var. \textit{albiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花貓兒菊&T2_new_value=true&fr=y}}{白花貓兒菊}\index{白花貓兒菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypochaeris+radicata}{\textit{H. radicata} L.}  \index{Hypochaeris@\textit{Hypochaeris}!radicata@\textit{radicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貓兒菊&T2_new_value=true&fr=y}}{貓兒菊}\index{貓兒菊} NA$^n$
  \end{itemize}
 \item[] \textit{Ixeridium} 小苦蕒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeridium+laevigatum}{\textit{I. laevigatum} (Blume) J.H.Pak \& Kawano}  \index{Ixeridium@\textit{Ixeridium}!laevigatum@\textit{laevigatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刀傷草&T2_new_value=true&fr=y}}{刀傷草}\index{刀傷草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeridium+transnokoense}{\textit{I. transnokoense} (Y. Sasaki) J.H.Pak \& Kawano}  \index{Ixeridium@\textit{Ixeridium}!transnokoense@\textit{transnokoense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高刀傷草&T2_new_value=true&fr=y}}{能高刀傷草}\index{能高刀傷草}\# LC
  \end{itemize}
 \item[] \textit{Ixeris} 苦蕒菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+chinensis}{\textit{I. chinensis} (Thunb.) Nakai}  \index{Ixeris@\textit{Ixeris}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=兔仔菜&T2_new_value=true&fr=y}}{兔仔菜}\index{兔仔菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+debilis}{\textit{I. debilis} (Thunb.) A.Gray}  \index{Ixeris@\textit{Ixeris}!debilis@\textit{debilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉剪刀股&T2_new_value=true&fr=y}}{細葉剪刀股}\index{細葉剪刀股} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+polycephala}{\textit{I. polycephala} Cass.}  \index{Ixeris@\textit{Ixeris}!polycephala@\textit{polycephala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多頭苦菜&T2_new_value=true&fr=y}}{多頭苦菜}\index{多頭苦菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+repens}{\textit{I. repens} (L.) A.Gray}  \index{Ixeris@\textit{Ixeris}!repens@\textit{repens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱剪刀股&T2_new_value=true&fr=y}}{濱剪刀股}\index{濱剪刀股} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+stolonifera}{\textit{I. stolonifera} A.Gray}  \index{Ixeris@\textit{Ixeris}!stolonifera@\textit{stolonifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓苦藚&T2_new_value=true&fr=y}}{蔓苦藚}\index{蔓苦藚} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixeris+tamagawaensis}{\textit{I. tamagawaensis} (Makino) Kitam.}  \index{Ixeris@\textit{Ixeris}!tamagawaensis@\textit{tamagawaensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澤苦菜&T2_new_value=true&fr=y}}{澤苦菜}\index{澤苦菜} LC
  \end{itemize}
 \item[] \textit{Kalimeris} 馬蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kalimeris+hispida}{\textit{K. hispida} (Thunb.) Nees}  \index{Kalimeris@\textit{Kalimeris}!hispida@\textit{hispida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱狗娃花&T2_new_value=true&fr=y}}{濱狗娃花}\index{濱狗娃花} NA$^n$
  \end{itemize}
 \item[] \textit{Lactuca} 萵苣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lactuca+serriola}{\textit{L. serriola} L.}  \index{Lactuca@\textit{Lactuca}!serriola@\textit{serriola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺萵苣&T2_new_value=true&fr=y}}{刺萵苣}\index{刺萵苣} NA$^n$
  \end{itemize}
 \item[] \textit{Lagenophora} 瓶頭草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lagenophora+lanata}{\textit{L. lanata} A.Cunn.}  \index{Lagenophora@\textit{Lagenophora}!lanata@\textbf{\textit{lanata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓶頭草&T2_new_value=true&fr=y}}{瓶頭草}\index{瓶頭草@{\Song{瓶頭草}}} EN
  \end{itemize}
 \item[] \textit{Laggera} 六角草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Laggera+alata}{\textit{L. alata} (D.Don) Sch.Bip. ex Oliv.}  \index{Laggera@\textit{Laggera}!alata@\textbf{\textit{alata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=六角草&T2_new_value=true&fr=y}}{六角草}\index{六角草@{\Song{六角草}}} VU
  \end{itemize}
 \item[] \textit{Lapsanastrum} 稻槎菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lapsanastrum+apogonoides}{\textit{L. apogonoides} (Maxim.) J.H.Pak \& K.Bremer}  \index{Lapsanastrum@\textit{Lapsanastrum}!apogonoides@\textbf{\textit{apogonoides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=稻槎菜&T2_new_value=true&fr=y}}{稻槎菜}\index{稻槎菜@{\Song{稻槎菜}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lapsanastrum+takasei}{\textit{L. takasei} (Sasaki) J.H.Pak \& K.Bremer}  \index{Lapsanastrum@\textit{Lapsanastrum}!takasei@\textit{takasei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣稻槎菜&T2_new_value=true&fr=y}}{臺灣稻槎菜}\index{臺灣稻槎菜}\# LC
  \end{itemize}
 \item[] \textit{Leontopodium} 薄雪草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leontopodium+microphyllum}{\textit{L. microphyllum} Hayata}  \index{Leontopodium@\textit{Leontopodium}!microphyllum@\textit{microphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山薄雪草&T2_new_value=true&fr=y}}{玉山薄雪草}\index{玉山薄雪草}\# LC
  \end{itemize}
 \item[] \textit{Leucanthemum} 濱菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leucanthemum+vulgare}{\textit{L. vulgare} H.J.Lam.}  \index{Leucanthemum@\textit{Leucanthemum}!vulgare@\textit{vulgare}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=法國菊&T2_new_value=true&fr=y}}{法國菊}\index{法國菊} NA$^n$
  \end{itemize}
 \item[] \textit{Ligularia} 橐吾屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ligularia+japonica}{\textit{L. japonica} (Thunb.) Less.}  \index{Ligularia@\textit{Ligularia}!japonica@\textbf{\textit{japonica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大吳風草&T2_new_value=true&fr=y}}{大吳風草}\index{大吳風草@{\Song{大吳風草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ligularia+kojimae}{\textit{L. kojimae} Kitam.}  \index{Ligularia@\textit{Ligularia}!kojimae@\textbf{\textit{kojimae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山橐吾&T2_new_value=true&fr=y}}{高山橐吾}\index{高山橐吾@{\Song{高山橐吾}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ligularia+stenocephala}{\textit{L. stenocephala} (Maxim.) Matsum. \& Koidz.}  \index{Ligularia@\textit{Ligularia}!stenocephala@\textit{stenocephala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=戟葉橐吾&T2_new_value=true&fr=y}}{戟葉橐吾}\index{戟葉橐吾} LC
  \end{itemize}
 \item[] \textit{Matricaria} 野菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Matricaria+matricarioides}{\textit{M. matricarioides} (Less.) Porter}  \index{Matricaria@\textit{Matricaria}!matricarioides@\textit{matricarioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=同花母菊&T2_new_value=true&fr=y}}{同花母菊}\index{同花母菊} NA$^n$
  \end{itemize}
 \item[] \textit{Microglossa} 小舌菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microglossa+pyrifolia}{\textit{M. pyrifolia} (Lam.) Kuntze}  \index{Microglossa@\textit{Microglossa}!pyrifolia@\textit{pyrifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小舌菊&T2_new_value=true&fr=y}}{小舌菊}\index{小舌菊} LC
  \end{itemize}
 \item[] \textit{Mikania} 蔓澤蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mikania+cordata}{\textit{M. cordata} (Burm.f.) B.L.Rob.}  \index{Mikania@\textit{Mikania}!cordata@\textit{cordata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓澤蘭&T2_new_value=true&fr=y}}{蔓澤蘭}\index{蔓澤蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mikania+micrantha}{\textit{M. micrantha} Kunth}  \index{Mikania@\textit{Mikania}!micrantha@\textit{micrantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花蔓澤蘭&T2_new_value=true&fr=y}}{小花蔓澤蘭}\index{小花蔓澤蘭} NA$^n$
  \end{itemize}
 \item[] \textit{Myriactis} 矮菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Myriactis+humilis}{\textit{M. humilis} Merr.}  \index{Myriactis@\textit{Myriactis}!humilis@\textit{humilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=矮菊&T2_new_value=true&fr=y}}{矮菊}\index{矮菊} LC
  \end{itemize}
 \item[] \textit{Nemosenecio} 羽葉千里光屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nemosenecio+formosanus}{\textit{N. formosanus} (Kitam.) B.Nord.}  \index{Nemosenecio@\textit{Nemosenecio}!formosanus@\textbf{\textit{formosanus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣劉寄奴&T2_new_value=true&fr=y}}{臺灣劉寄奴}\index{臺灣劉寄奴@{\Song{臺灣劉寄奴}}}\# VU
  \end{itemize}
 \item[] \textit{Notoseris} 紫菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Notoseris+formosana}{\textit{N. formosana} (Kitam.) C.Shih}  \index{Notoseris@\textit{Notoseris}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣福王草&T2_new_value=true&fr=y}}{臺灣福王草}\index{臺灣福王草}\# LC
  \end{itemize}
 \item[] \textit{Paraprenanthes} 假福王草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraprenanthes+sororia}{\textit{P. sororia} (Miq.) C.Shih}  \index{Paraprenanthes@\textit{Paraprenanthes}!sororia@\textit{sororia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山苦藚&T2_new_value=true&fr=y}}{山苦藚}\index{山苦藚} LC
  \end{itemize}
 \item[] \textit{Parasenecio} 蟹甲草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parasenecio+hwangshanica}{\textit{P. hwangshanica} (Ling) C.I Peng \& S.W.Chung}  \index{Parasenecio@\textit{Parasenecio}!hwangshanica@\textbf{\textit{hwangshanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃山蟹甲草&T2_new_value=true&fr=y}}{黃山蟹甲草}\index{黃山蟹甲草@{\Song{黃山蟹甲草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parasenecio+monantha}{\textit{P. monantha} (Diels) C.I Peng \& S.W.Chung}  \index{Parasenecio@\textit{Parasenecio}!monantha@\textbf{\textit{monantha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山蟹甲草&T2_new_value=true&fr=y}}{玉山蟹甲草}\index{玉山蟹甲草@{\Song{玉山蟹甲草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parasenecio+nokoensis}{\textit{P. nokoensis} (Masam. \& Suzuki) C.I Peng \& S.W.Chung}  \index{Parasenecio@\textit{Parasenecio}!nokoensis@\textbf{\textit{nokoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高蟹甲草&T2_new_value=true&fr=y}}{能高蟹甲草}\index{能高蟹甲草@{\Song{能高蟹甲草}}}\# EN
  \end{itemize}
 \item[] \textit{Parthenium} 銀膠菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parthenium+hysterophorus}{\textit{P. hysterophorus} L.}  \index{Parthenium@\textit{Parthenium}!hysterophorus@\textit{hysterophorus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀膠菊&T2_new_value=true&fr=y}}{銀膠菊}\index{銀膠菊} NA$^n$
  \end{itemize}
 \item[] \textit{Pectis} 香檬菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pectis+prostrata}{\textit{P. prostrata} Cavanilles}  \index{Pectis@\textit{Pectis}!prostrata@\textit{prostrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=伏生香檬菊&T2_new_value=true&fr=y}}{伏生香檬菊}\index{伏生香檬菊} NA$^n$
  \end{itemize}
 \item[] \textit{Pertya} 高野帚屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pertya+simozawai}{\textit{P. simozawai} Masam.}  \index{Pertya@\textit{Pertya}!simozawai@\textbf{\textit{simozawai}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=半高野帚&T2_new_value=true&fr=y}}{半高野帚}\index{半高野帚@{\Song{半高野帚}}}\# EN
  \end{itemize}
 \item[] \textit{Petasites} 款冬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Petasites+formosanus}{\textit{P. formosanus} Kitam.}  \index{Petasites@\textit{Petasites}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣款冬&T2_new_value=true&fr=y}}{臺灣款冬}\index{臺灣款冬}\# LC
  \end{itemize}
 \item[] \textit{Picris} 毛蓮菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Picris+hieracioides+subsp.+morrisonensis}{\textit{P. hieracioides} L. subsp. \textit{morrisonensis} (Hayata) Kitam.}  \index{Picris@\textit{Picris}!hieracioides@\textit{hieracioides}!subsp. morrisonensis@subsp. \textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山毛蓮菜&T2_new_value=true&fr=y}}{玉山毛蓮菜}\index{玉山毛蓮菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Picris+hieracioides+subsp.+ohwiana}{\textit{P. hieracioides} L. subsp. \textit{ohwiana} (Kitam.) Kitam.}  \index{Picris@\textit{Picris}!hieracioides@\textit{hieracioides}!subsp. ohwiana@subsp. \textit{ohwiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山毛蓮菜&T2_new_value=true&fr=y}}{高山毛蓮菜}\index{高山毛蓮菜}\# LC
  \end{itemize}
 \item[] \textit{Pluchea} 闊苞菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pluchea+carolinensis}{\textit{P. carolinensis} (Jacq.) G.Don}  \index{Pluchea@\textit{Pluchea}!carolinensis@\textit{carolinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=美洲闊苞菊&T2_new_value=true&fr=y}}{美洲闊苞菊}\index{美洲闊苞菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pluchea+indica}{\textit{P. indica} (L.) Less.}  \index{Pluchea@\textit{Pluchea}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鯽魚膽&T2_new_value=true&fr=y}}{鯽魚膽}\index{鯽魚膽} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pluchea+pteropoda}{\textit{P. pteropoda} Hemsl.}  \index{Pluchea@\textit{Pluchea}!pteropoda@\textbf{\textit{pteropoda}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光梗闊苞菊&T2_new_value=true&fr=y}}{光梗闊苞菊}\index{光梗闊苞菊@{\Song{光梗闊苞菊}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pluchea+sagittalis}{\textit{P. sagittalis} (Lam.) Cabera}  \index{Pluchea@\textit{Pluchea}!sagittalis@\textit{sagittalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼莖闊苞菊&T2_new_value=true&fr=y}}{翼莖闊苞菊}\index{翼莖闊苞菊} NA$^n$
  \end{itemize}
 \item[] \textit{Praxelis} 貓腥草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Praxelis+clematidea}{\textit{P. clematidea} (Griseb.) R.M.King \& H.Rob.}  \index{Praxelis@\textit{Praxelis}!clematidea@\textit{clematidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貓腥草&T2_new_value=true&fr=y}}{貓腥草}\index{貓腥草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Praxelis+pauciflora}{\textit{P. pauciflora} (Kunth) R.M.King \& H.Rob. }  \index{Praxelis@\textit{Praxelis}!pauciflora@\textit{pauciflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鋸葉貓腥草&T2_new_value=true&fr=y}}{鋸葉貓腥草}\index{鋸葉貓腥草} NA$^n$
  \end{itemize}
 \item[] \textit{Pseudelephantopus} 假地膽草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pseudelephantopus+spicatus}{\textit{P. spicatus} (Juss.) C.F.Baker}  \index{Pseudelephantopus@\textit{Pseudelephantopus}!spicatus@\textit{spicatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假地膽草&T2_new_value=true&fr=y}}{假地膽草}\index{假地膽草} NA$^n$
  \end{itemize}
 \item[] \textit{Pterocypsela} 翅果菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pterocypsela+formosana}{\textit{P. formosana} (Maxim.) C.Shih}  \index{Pterocypsela@\textit{Pterocypsela}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山苦藚&T2_new_value=true&fr=y}}{臺灣山苦藚}\index{臺灣山苦藚} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pterocypsela+indica}{\textit{P. indica} (L.) C.Shih}  \index{Pterocypsela@\textit{Pterocypsela}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝仔草&T2_new_value=true&fr=y}}{鵝仔草}\index{鵝仔草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pterocypsela+×mansuensis}{\textit{P. ×mansuensis} (Hayata) C.I Peng}  \index{Pterocypsela@\textit{Pterocypsela}!×mansuensis@\textit{×mansuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春山苦藚&T2_new_value=true&fr=y}}{恆春山苦藚}\index{恆春山苦藚} NA$^h$
  \end{itemize}
 \item[] \textit{Rhynchospermum} 秋分草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospermum+verticillatum}{\textit{R. verticillatum} Reinw.}  \index{Rhynchospermum@\textit{Rhynchospermum}!verticillatum@\textit{verticillatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=秋分草&T2_new_value=true&fr=y}}{秋分草}\index{秋分草} LC
  \end{itemize}
 \item[] \textit{Saussurea} 青木香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saussurea+deltoidea}{\textit{S. deltoidea} (DC.) C.B.Clarke}  \index{Saussurea@\textit{Saussurea}!deltoidea@\textit{deltoidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣青木香&T2_new_value=true&fr=y}}{臺灣青木香}\index{臺灣青木香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saussurea+glandulosa}{\textit{S. glandulosa} Kitam.}  \index{Saussurea@\textit{Saussurea}!glandulosa@\textbf{\textit{glandulosa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山青木香&T2_new_value=true&fr=y}}{高山青木香}\index{高山青木香@{\Song{高山青木香}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saussurea+japonica}{\textit{S. japonica} (Thunb.) DC.}  \index{Saussurea@\textit{Saussurea}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鳳毛菊&T2_new_value=true&fr=y}}{鳳毛菊}\index{鳳毛菊} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saussurea+kanzanensis}{\textit{S. kanzanensis} Kitam.}  \index{Saussurea@\textit{Saussurea}!kanzanensis@\textbf{\textit{kanzanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山青木香&T2_new_value=true&fr=y}}{關山青木香}\index{關山青木香@{\Song{關山青木香}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saussurea+kiraisiensis}{\textit{S. kiraisiensis} Masam.}  \index{Saussurea@\textit{Saussurea}!kiraisiensis@\textbf{\textit{kiraisiensis}}}  \index{Saussurea@\textit{Saussurea}!kiraisanensis@\textit{kiraisanensis}{\\\noindent(= \textit{Saussurea kiraisiensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奇萊青木香&T2_new_value=true&fr=y}}{奇萊青木香}\index{奇萊青木香@{\Song{奇萊青木香}}}\# VU
  \end{itemize}
 \item[] \textit{Senecio} 黃菀屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+crataegifolius}{\textit{S. crataegifolius} Hayata}  \index{Senecio@\textit{Senecio}!crataegifolius@\textbf{\textit{crataegifolius}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小蔓黃菀&T2_new_value=true&fr=y}}{小蔓黃菀}\index{小蔓黃菀@{\Song{小蔓黃菀}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+inaequidens}{\textit{S. inaequidens} DC.}  \index{Senecio@\textit{Senecio}!inaequidens@\textit{inaequidens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=窄葉黃菀&T2_new_value=true&fr=y}}{窄葉黃菀}\index{窄葉黃菀} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+kuanshanensis}{\textit{S. kuanshanensis} C.I Peng \& S.W.Chung}  \index{Senecio@\textit{Senecio}!kuanshanensis@\textbf{\textit{kuanshanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山千里光&T2_new_value=true&fr=y}}{關山千里光}\index{關山千里光@{\Song{關山千里光}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+morrisonensis}{\textit{S. morrisonensis} Hayata}  \index{Senecio@\textit{Senecio}!morrisonensis@\textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山黃菀&T2_new_value=true&fr=y}}{玉山黃菀}\index{玉山黃菀}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+nemorensis+var.+dentatus}{\textit{S. nemorensis} L. var. \textit{dentatus} (Kitam.) H.Koyama}  \index{Senecio@\textit{Senecio}!nemorensis@\textit{nemorensis}!var. dentatus@var. \textit{dentatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃菀&T2_new_value=true&fr=y}}{黃菀}\index{黃菀}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+scandens+var.+incisus}{\textit{S. scandens} Buch.-Ham. ex D.Don var. \textit{incisus} Franch.}  \index{Senecio@\textit{Senecio}!scandens@\textit{scandens}!var. incisus@var. \textit{incisus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂葉蔓黃菀&T2_new_value=true&fr=y}}{裂葉蔓黃菀}\index{裂葉蔓黃菀} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+scandens+var.+scandens}{\textit{S. scandens} Buch.-Ham. ex D.Don var. \textit{scandens}}  \index{Senecio@\textit{Senecio}!scandens@\textit{scandens}!var. scandens@var. \textit{scandens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓黃菀&T2_new_value=true&fr=y}}{蔓黃菀}\index{蔓黃菀} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+taitungensis}{\textit{S. taitungensis} S.S.Ying}  \index{Senecio@\textit{Senecio}!taitungensis@\textit{taitungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東黃菀&T2_new_value=true&fr=y}}{臺東黃菀}\index{臺東黃菀}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+tarokoensis}{\textit{S. tarokoensis} C.I Peng}  \index{Senecio@\textit{Senecio}!tarokoensis@\textbf{\textit{tarokoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣千里光&T2_new_value=true&fr=y}}{太魯閣千里光}\index{太魯閣千里光@{\Song{太魯閣千里光}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senecio+vulgaris}{\textit{S. vulgaris} L.}  \index{Senecio@\textit{Senecio}!vulgaris@\textit{vulgaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=歐洲黃菀&T2_new_value=true&fr=y}}{歐洲黃菀}\index{歐洲黃菀} NA$^n$
  \end{itemize}
 \item[] \textit{Sigesbeckia} 豨薟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sigesbeckia+orientalis}{\textit{S. orientalis} L.}  \index{Sigesbeckia@\textit{Sigesbeckia}!orientalis@\textit{orientalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豨薟&T2_new_value=true&fr=y}}{豨薟}\index{豨薟} NA$^n$
  \end{itemize}
 \item[] \textit{Solidago} 一枝黃花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solidago+altissima}{\textit{S. altissima} L.}  \index{Solidago@\textit{Solidago}!altissima@\textit{altissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=北美一枝黃花&T2_new_value=true&fr=y}}{北美一枝黃花}\index{北美一枝黃花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solidago+virgaurea+var.+leiocarpa}{\textit{S. virgaurea} L. var. \textit{leiocarpa} (Benth.) A.Gray}  \index{Solidago@\textit{Solidago}!virgaurea@\textit{virgaurea}!var. leiocarpa@var. \textit{leiocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=一枝黃花&T2_new_value=true&fr=y}}{一枝黃花}\index{一枝黃花} LC
  \end{itemize}
 \item[] \textit{Soliva} 假吐金菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Soliva+anthemifolia}{\textit{S. anthemifolia} (Juss.) R.Br. ex Less.}  \index{Soliva@\textit{Soliva}!anthemifolia@\textit{anthemifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假吐金菊&T2_new_value=true&fr=y}}{假吐金菊}\index{假吐金菊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Soliva+pterosperma}{\textit{S. pterosperma} (Juss.) Less.}  \index{Soliva@\textit{Soliva}!pterosperma@\textit{pterosperma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翅果假吐金菊&T2_new_value=true&fr=y}}{翅果假吐金菊}\index{翅果假吐金菊} NA$^n$
  \end{itemize}
 \item[] \textit{Sonchus} 苦苣菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sonchus+arvensis}{\textit{S. arvensis} L.}  \index{Sonchus@\textit{Sonchus}!arvensis@\textit{arvensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦苣菜&T2_new_value=true&fr=y}}{苦苣菜}\index{苦苣菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sonchus+asper}{\textit{S. asper} (L.) Hill}  \index{Sonchus@\textit{Sonchus}!asper@\textit{asper}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼苦苣菜&T2_new_value=true&fr=y}}{鬼苦苣菜}\index{鬼苦苣菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sonchus+oleraceus}{\textit{S. oleraceus} L.}  \index{Sonchus@\textit{Sonchus}!oleraceus@\textit{oleraceus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦滇菜&T2_new_value=true&fr=y}}{苦滇菜}\index{苦滇菜} NA$^n$
  \end{itemize}
 \item[] \textit{Sphaeranthus} 戴星草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sphaeranthus+africanus}{\textit{S. africanus} L.}  \index{Sphaeranthus@\textit{Sphaeranthus}!africanus@\textbf{\textit{africanus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=戴星草&T2_new_value=true&fr=y}}{戴星草}\index{戴星草@{\Song{戴星草}}} VU
  \end{itemize}
 \item[] \textit{Synedrella} 金腰箭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Synedrella+nodiflora}{\textit{S. nodiflora} (L.) Gaertn.}  \index{Synedrella@\textit{Synedrella}!nodiflora@\textit{nodiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金腰箭&T2_new_value=true&fr=y}}{金腰箭}\index{金腰箭} NA$^n$
  \end{itemize}
 \item[] \textit{Syneilesis} 破傘菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syneilesis+intermedia}{\textit{S. intermedia} (Hayata) Kitam.}  \index{Syneilesis@\textit{Syneilesis}!intermedia@\textbf{\textit{intermedia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣破傘菊&T2_new_value=true&fr=y}}{臺灣破傘菊}\index{臺灣破傘菊@{\Song{臺灣破傘菊}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syneilesis+subglabrata}{\textit{S. subglabrata} (Yamam. \& Sasaki) Kitam.}  \index{Syneilesis@\textit{Syneilesis}!subglabrata@\textit{subglabrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山破傘菊&T2_new_value=true&fr=y}}{高山破傘菊}\index{高山破傘菊}\# NT
  \end{itemize}
 \item[] \textit{Tagetes} 孔雀草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tagetes+minuta}{\textit{T. minuta} L.}  \index{Tagetes@\textit{Tagetes}!minuta@\textit{minuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印加孔雀草&T2_new_value=true&fr=y}}{印加孔雀草}\index{印加孔雀草} NA$^n$
  \end{itemize}
 \item[] \textit{Taraxacum} 蒲公英屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taraxacum+formosanum}{\textit{T. formosanum} Kitam.}  \index{Taraxacum@\textit{Taraxacum}!formosanum@\textbf{\textit{formosanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蒲公英&T2_new_value=true&fr=y}}{臺灣蒲公英}\index{臺灣蒲公英@{\Song{臺灣蒲公英}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taraxacum+officinale}{\textit{T. officinale} Weber}  \index{Taraxacum@\textit{Taraxacum}!officinale@\textit{officinale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=西洋蒲公英&T2_new_value=true&fr=y}}{西洋蒲公英}\index{西洋蒲公英} NA$^n$
  \end{itemize}
 \item[] \textit{Tephroseris} 狗舌草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephroseris+kirilowii}{\textit{T. kirilowii} (Turcz. ex DC.) Holub}  \index{Tephroseris@\textit{Tephroseris}!kirilowii@\textit{kirilowii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狗舌草&T2_new_value=true&fr=y}}{狗舌草}\index{狗舌草} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephroseris+taitoensis}{\textit{T. taitoensis} (Hayata) Holub}  \index{Tephroseris@\textit{Tephroseris}!taitoensis@\textit{taitoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣狗舌草&T2_new_value=true&fr=y}}{臺灣狗舌草}\index{臺灣狗舌草}\# DD
  \end{itemize}
 \item[] \textit{Tithonia} 腫柄菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tithonia+diversifolia}{\textit{T. diversifolia} (Hemsl.) A.Gray}  \index{Tithonia@\textit{Tithonia}!diversifolia@\textit{diversifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=王爺葵&T2_new_value=true&fr=y}}{王爺葵}\index{王爺葵} NA$^n$
  \end{itemize}
 \item[] \textit{Tridax} 長柄菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tridax+procumbens}{\textit{T. procumbens} L.}  \index{Tridax@\textit{Tridax}!procumbens@\textit{procumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長柄菊&T2_new_value=true&fr=y}}{長柄菊}\index{長柄菊} NA$^n$
  \end{itemize}
 \item[] \textit{Vernonia} 斑鳩菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+cinerea+var.+cinerea}{\textit{V. cinerea} (L.) Less. var. \textit{cinerea}}  \index{Vernonia@\textit{Vernonia}!cinerea@\textit{cinerea}!var. cinerea@var. \textit{cinerea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=一枝香&T2_new_value=true&fr=y}}{一枝香}\index{一枝香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+cinerea+var.+parviflora}{\textit{V. cinerea} (L.) Less. var. \textit{parviflora} (Reinw.) DC.}  \index{Vernonia@\textit{Vernonia}!cinerea@\textit{cinerea}!var. parviflora@var. \textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花斑鳩菊&T2_new_value=true&fr=y}}{小花斑鳩菊}\index{小花斑鳩菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+elliptica}{\textit{V. elliptica} DC.}  \index{Vernonia@\textit{Vernonia}!elliptica@\textit{elliptica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光耀藤&T2_new_value=true&fr=y}}{光耀藤}\index{光耀藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+gratiosa}{\textit{V. gratiosa} Hance}  \index{Vernonia@\textit{Vernonia}!gratiosa@\textit{gratiosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=過山龍&T2_new_value=true&fr=y}}{過山龍}\index{過山龍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+maritima}{\textit{V. maritima} Merr.}  \index{Vernonia@\textit{Vernonia}!maritima@\textbf{\textit{maritima}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱斑鳩菊&T2_new_value=true&fr=y}}{濱斑鳩菊}\index{濱斑鳩菊@{\Song{濱斑鳩菊}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernonia+patula}{\textit{V. patula} (Dryand.) Merr.}  \index{Vernonia@\textit{Vernonia}!patula@\textit{patula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=嶺南野菊&T2_new_value=true&fr=y}}{嶺南野菊}\index{嶺南野菊} LC
  \end{itemize}
 \item[] \textit{Wedelia} 蟛蜞菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+biflora+var.+biflora}{\textit{W. biflora} (L.) DC. var. \textit{biflora}}  \index{Wedelia@\textit{Wedelia}!biflora@\textit{biflora}!var. biflora@var. \textit{biflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙花蟛蜞菊&T2_new_value=true&fr=y}}{雙花蟛蜞菊}\index{雙花蟛蜞菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+biflora+var.+ryukyuensis}{\textit{W. biflora} (L.) DC. var. \textit{ryukyuensis} H.Koyama}  \index{Wedelia@\textit{Wedelia}!biflora@\textit{biflora}!var. ryukyuensis@var. \textit{ryukyuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球蟛蜞菊&T2_new_value=true&fr=y}}{琉球蟛蜞菊}\index{琉球蟛蜞菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+chinensis}{\textit{W. chinensis} (Osbeck) Merr.}  \index{Wedelia@\textit{Wedelia}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蟛蜞菊&T2_new_value=true&fr=y}}{蟛蜞菊}\index{蟛蜞菊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+montana}{\textit{W. montana} (Blume) Boerl.}  \index{Wedelia@\textit{Wedelia}!montana@\textit{montana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山蟛蜞菊&T2_new_value=true&fr=y}}{山蟛蜞菊}\index{山蟛蜞菊} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+prostrata+var.+prostrata}{\textit{W. prostrata} (Hook. \& Arn.) Hemsl. var. \textit{prostrata}}  \index{Wedelia@\textit{Wedelia}!prostrata@\textit{prostrata}!var. prostrata@var. \textit{prostrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天蓬草舅&T2_new_value=true&fr=y}}{天蓬草舅}\index{天蓬草舅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+prostrata+var.+robusta}{\textit{W. prostrata} (Hook. \& Arn.) Hemsl. var. \textit{robusta} Makino}  \index{Wedelia@\textit{Wedelia}!prostrata@\textit{prostrata}!var. robusta@var. \textit{robusta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大天蓬草舅&T2_new_value=true&fr=y}}{大天蓬草舅}\index{大天蓬草舅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wedelia+trilobata}{\textit{W. trilobata} (L.) Hitchc.}  \index{Wedelia@\textit{Wedelia}!trilobata@\textit{trilobata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南美蟛蜞菊&T2_new_value=true&fr=y}}{南美蟛蜞菊}\index{南美蟛蜞菊} NA$^n$
  \end{itemize}
 \item[] \textit{Xanthium} 蒼耳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Xanthium+strumarium}{\textit{X. strumarium} L.}  \index{Xanthium@\textit{Xanthium}!strumarium@\textit{strumarium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蒼耳&T2_new_value=true&fr=y}}{蒼耳}\index{蒼耳} NA$^n$
  \end{itemize}
 \item[] \textit{Youngia} 黃鵪菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Youngia+japonica+subsp.+formosana}{\textit{Y. japonica} (L.) DC. subsp. \textit{formosana} (Hayata) Kitam.}  \index{Youngia@\textit{Youngia}!japonica@\textit{japonica}!subsp. formosana@subsp. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃鵪菜&T2_new_value=true&fr=y}}{臺灣黃鵪菜}\index{臺灣黃鵪菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Youngia+japonica+subsp.+japonica}{\textit{Y. japonica} (L.) DC. subsp. \textit{japonica}}  \index{Youngia@\textit{Youngia}!japonica@\textit{japonica}!subsp. japonica@subsp. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃鵪菜&T2_new_value=true&fr=y}}{黃鵪菜}\index{黃鵪菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Youngia+japonica+subsp.+longiflora}{\textit{Y. japonica} (L.) DC. subsp. \textit{longiflora} Babc. \& Stebbins}  \index{Youngia@\textit{Youngia}!japonica@\textit{japonica}!subsp. longiflora@subsp. \textit{longiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花黃鵪菜&T2_new_value=true&fr=y}}{大花黃鵪菜}\index{大花黃鵪菜} LC
  \end{itemize}
  \end{itemize}
