
  \begin{itemize}
 \item[    ] \textit{Anisocampium} 安蕨屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anisocampium+cumingianum}{\textit{A. cumingianum} C.Presl}  \index{Anisocampium@\textit{Anisocampium}!cumingianum@\textit{cumingianum}} 安蕨 \index{安蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anisocampium+niponicum}{\textit{A. niponicum} (Mett.) Yea C.Liu, W.L.Chiou \& M.Kato}  \index{Anisocampium@\textit{Anisocampium}!niponicum@\textit{niponicum}} 日本蹄蓋蕨 \index{日本蹄蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anisocampium+sheareri}{\textit{A. sheareri} (Baker) Ching}  \index{Anisocampium@\textit{Anisocampium}!sheareri@\textit{sheareri}} 華東安蕨 \index{華東安蕨}  NA 
  \end{itemize}
 \item[    ] \textit{Athyrium} 蹄蓋蕨屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+anisopterum}{\textit{A. anisopterum} H.Christ}  \index{Athyrium@\textit{Athyrium}!anisopterum@\textit{anisopterum}} 宿蹄蓋蕨 \index{宿蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+arisanense}{\textit{A. arisanense} (Hayata) Tagawa}  \index{Athyrium@\textit{Athyrium}!arisanense@\textit{arisanense}} 阿里山蹄蓋蕨 \index{阿里山蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+atkinsonii}{\textit{A. atkinsonii} Bedd.}  \index{Athyrium@\textit{Athyrium}!atkinsonii@\textit{atkinsonii}} 亞德氏蹄蓋蕨 \index{亞德氏蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+auriculatum}{\textit{A. auriculatum} Seriz.}  \index{Athyrium@\textit{Athyrium}!auriculatum@\textit{auriculatum}} 耳垂蹄蓋蕨 \index{耳垂蹄蓋蕨} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+cryptogrammoides}{\textit{A. cryptogrammoides} Hayata}  \index{Athyrium@\textit{Athyrium}!cryptogrammoides@\textit{cryptogrammoides}} 合歡山蹄蓋蕨 \index{合歡山蹄蓋蕨} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+delavayi+var.+subrigescens}{\textit{A. delavayi} Christ var. \textit{subrigescens} (Hayata) Yea C.Liu, W.L.Chiou \& H.Y.Liu}  \index{Athyrium@\textit{Athyrium}!delavayi@\textit{delavayi}!var. subrigescens@var. \textit{subrigescens}}
                                        姬蹄蓋蕨 \index{姬蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+drepanopterum}{\textit{A. drepanopterum} (Kunze) A.Br. ex Milde}  \index{Athyrium@\textit{Athyrium}!drepanopterum@\textit{drepanopterum}} 細裂蹄蓋蕨 \index{細裂蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+epirachis}{\textit{A. epirachis} (H.Christ) Ching}  \index{Athyrium@\textit{Athyrium}!epirachis@\textit{epirachis}} 軸果蹄蓋蕨 \index{軸果蹄蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+erythropodum}{\textit{A. erythropodum} Hayata}  \index{Athyrium@\textit{Athyrium}!erythropodum@\textit{erythropodum}} 紅柄蹄蓋蕨 \index{紅柄蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+foliolosum}{\textit{A. foliolosum} (Wall.) T.Moore ex R.Sim}  \index{Athyrium@\textit{Athyrium}!foliolosum@\textit{foliolosum}} 薄葉蹄蓋蕨 \index{薄葉蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+iseanum+var.+angustisectum}{\textit{A. iseanum} Rosenst. var. \textit{angustisectum} Tagawa}  \index{Athyrium@\textit{Athyrium}!iseanum@\textit{iseanum}!var. angustisectum@var. \textit{angustisectum}}
                                        細葉蹄蓋蕨 \index{細葉蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+leiopodum}{\textit{A. leiopodum} (Hayata) Tagawa}  \index{Athyrium@\textit{Athyrium}!leiopodum@\textit{leiopodum}} 小葉蹄蓋蕨 \index{小葉蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+minimum}{\textit{A. minimum} Ching}  \index{Athyrium@\textit{Athyrium}!minimum@\textit{minimum}} 七星山蹄蓋蕨 \index{七星山蹄蓋蕨} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+mupinense}{\textit{A. mupinense} Christ}  \index{Athyrium@\textit{Athyrium}!mupinense@\textit{mupinense}} 細裂蹄蓋蕨 \index{細裂蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+nakanoi}{\textit{A. nakanoi} Makino}  \index{Athyrium@\textit{Athyrium}!nakanoi@\textit{nakanoi}} 紅苞蹄蓋蕨 \index{紅苞蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+oppositipinnum+var.+oppositipinnum}{\textit{A. oppositipinnum} Hayata var. \textit{oppositipinnum}}  \index{Athyrium@\textit{Athyrium}!oppositipinnum@\textit{oppositipinnum}!var. oppositipinnum@var. \textit{oppositipinnum}}
                                        對生蹄蓋蕨 \index{對生蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+oppositipinnum+var.+pubescens}{\textit{A. oppositipinnum} Hayata var. \textit{pubescens} (Tagawa) Tagawa}  \index{Athyrium@\textit{Athyrium}!oppositipinnum@\textit{oppositipinnum}!var. pubescens@var. \textit{pubescens}}
                                        逆羽蹄蓋蕨 \index{逆羽蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+otophorum}{\textit{A. otophorum} (Miq.) Koidz.}  \index{Athyrium@\textit{Athyrium}!otophorum@\textit{otophorum}} 光蹄蓋蕨 \index{光蹄蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+palustre}{\textit{A. palustre} Seriz.}  \index{Athyrium@\textit{Athyrium}!palustre@\textit{palustre}} 沼生蹄蓋蕨 \index{沼生蹄蓋蕨}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+pubicostatum}{\textit{A. pubicostatum} Ching \& Z.Y.Liu}  \index{Athyrium@\textit{Athyrium}!pubicostatum@\textit{pubicostatum}} 假軸果蹄蓋蕨 \index{假軸果蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+puncticaule}{\textit{A. puncticaule} (Blume) T.Moore}  \index{Athyrium@\textit{Athyrium}!puncticaule@\textit{puncticaule}} 密腺蹄蓋蕨 \index{密腺蹄蓋蕨}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+reflexipinnum}{\textit{A. reflexipinnum} Hayata}  \index{Athyrium@\textit{Athyrium}!reflexipinnum@\textit{reflexipinnum}} 逆葉蹄蓋蕨 \index{逆葉蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+silvicola}{\textit{A. silvicola} Tagawa}  \index{Athyrium@\textit{Athyrium}!silvicola@\textit{silvicola}} 高山蹄蓋蕨 \index{高山蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+strigillosum}{\textit{A. strigillosum} (T.Moore ex E.J.Lowe) Salomon}  \index{Athyrium@\textit{Athyrium}!strigillosum@\textit{strigillosum}} 生芽蹄蓋蕨 \index{生芽蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+subrigescens}{\textit{A. subrigescens} (Hayata) Hayata ex H.Ito}  \index{Athyrium@\textit{Athyrium}!subrigescens@\textit{subrigescens}} 溪谷蹄蓋蕨 \index{溪谷蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+tozanense}{\textit{A. tozanense} (Hayata) Hayata}  \index{Athyrium@\textit{Athyrium}!tozanense@\textit{tozanense}} 蓬萊蹄蓋蕨 \index{蓬萊蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+tripinnatum}{\textit{A. tripinnatum} Tagawa}  \index{Athyrium@\textit{Athyrium}!tripinnatum@\textit{tripinnatum}} 三回蹄蓋蕨 \index{三回蹄蓋蕨} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+vidalii}{\textit{A. vidalii} (Franch. \& Sav.) Nakai}  \index{Athyrium@\textit{Athyrium}!vidalii@\textit{vidalii}} 山蹄蓋蕨 \index{山蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+×hohuanshanense}{\textit{A. ×hohuanshanense} Yoshik.}  \index{Athyrium@\textit{Athyrium}!×hohuanshanense@\textit{×hohuanshanense}} 尖阿蹄蓋蕨 \index{尖阿蹄蓋蕨} \# NA (H)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+×pseudocryptogrammoides}{\textit{A. ×pseudocryptogrammoides} Yoshik.}  \index{Athyrium@\textit{Athyrium}!×pseudocryptogrammoides@\textit{×pseudocryptogrammoides}} 擬合歡蹄蓋蕨 \index{擬合歡蹄蓋蕨}  NA (H)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Athyrium+×purpurascens}{\textit{A. ×purpurascens} (Tagawa) Sa.Kurata}  \index{Athyrium@\textit{Athyrium}!×purpurascens@\textit{×purpurascens}} 紫柄蹄蓋蕨 \index{紫柄蹄蓋蕨}  NA (H)
  \end{itemize}
 \item[    ] \textit{Cornopteris} 角蕨屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cornopteris+banajaoensis}{\textit{C. banajaoensis} (C.Chr.) K.Iwats. \& M.G.Price}  \index{Cornopteris@\textit{Cornopteris}!banajaoensis@\textit{banajaoensis}} 大葉貞蕨 \index{大葉貞蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cornopteris+decurrenti-alata+var.+decurrenti-alata}{\textit{C. decurrenti-alata} (Hook.) Nakai var. \textit{decurrenti-alata}}  \index{Cornopteris@\textit{Cornopteris}!decurrenti-alata@\textit{decurrenti-alata}!var. decurrenti-alata@var. \textit{decurrenti-alata}}
                                        貞蕨 \index{貞蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cornopteris+decurrenti-alata+var.+pilosella}{\textit{C. decurrenti-alata} (Hook.) Nakai var. \textit{pilosella} H.Ito}  \index{Cornopteris@\textit{Cornopteris}!decurrenti-alata@\textit{decurrenti-alata}!var. pilosella@var. \textit{pilosella}}
                                        毛葉貞蕨 \index{毛葉貞蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cornopteris+opaca}{\textit{C. opaca} (D.Don) Tagawa}  \index{Cornopteris@\textit{Cornopteris}!opaca@\textit{opaca}} 黑葉貞蕨 \index{黑葉貞蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cornopteris+philippinensis}{\textit{C. philippinensis} M.Kato}  \index{Cornopteris@\textit{Cornopteris}!philippinensis@\textit{philippinensis}} 菲律賓貞蕨 \index{菲律賓貞蕨}  DD
  \end{itemize}
 \item[    ] \textit{Deparia} 假鱗毛蕨屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+allantodioides}{\textit{D. allantodioides} (Bedd.) M.Kato}  \index{Deparia@\textit{Deparia}!allantodioides@\textit{allantodioides}} 亞蹄蓋蕨 \index{亞蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+boryana}{\textit{D. boryana} (Willd.) M.Kato}  \index{Deparia@\textit{Deparia}!boryana@\textit{boryana}} 南洋假鱗毛蕨 \index{南洋假鱗毛蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+formosana}{\textit{D. formosana} (Rosenst.) R.Sano}  \index{Deparia@\textit{Deparia}!formosana@\textit{formosana}} 假腸蕨 \index{假腸蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+lancea}{\textit{D. lancea} (Thunb.) Fraser-Jenk.}  \index{Deparia@\textit{Deparia}!lancea@\textit{lancea}} 單葉假蹄蓋蕨 \index{單葉假蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+longipes}{\textit{D. longipes} (Ching) Shinohara}  \index{Deparia@\textit{Deparia}!longipes@\textit{longipes}} 昆明假蹄蓋蕨 \index{昆明假蹄蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+petersenii}{\textit{D. petersenii} (Kunze) M.Kato}  \index{Deparia@\textit{Deparia}!petersenii@\textit{petersenii}} 假蹄蓋蕨 \index{假蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+subfluvialis}{\textit{D. subfluvialis} (Hayata) M.Kato}  \index{Deparia@\textit{Deparia}!subfluvialis@\textit{subfluvialis}} 波氏蹄蓋蕨 \index{波氏蹄蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+tomitaroana}{\textit{D. tomitaroana} (Masam.) R.Sano}  \index{Deparia@\textit{Deparia}!tomitaroana@\textit{tomitaroana}} 羽裂假蹄蓋蕨 \index{羽裂假蹄蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deparia+unifurcata}{\textit{D. unifurcata} (Baker) M.Kato}  \index{Deparia@\textit{Deparia}!unifurcata@\textit{unifurcata}} 東亞假鱗毛蕨 \index{東亞假鱗毛蕨}  VU
  \end{itemize}
 \item[    ] \textit{Diplazium} 雙蓋蕨屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+agyokuense}{\textit{D. agyokuense} Tagawa}  \index{Diplazium@\textit{Diplazium}!agyokuense@\textit{agyokuense}} 阿玉雙蓋蕨 \index{阿玉雙蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+amamianum}{\textit{D. amamianum} Tagawa}  \index{Diplazium@\textit{Diplazium}!amamianum@\textit{amamianum}} 奄美雙蓋蕨 \index{奄美雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+asperum}{\textit{D. asperum} Blume}  \index{Diplazium@\textit{Diplazium}!asperum@\textit{asperum}} 粗柄雙蓋蕨 \index{粗柄雙蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+chinense}{\textit{D. chinense} (Baker) C.Chr.}  \index{Diplazium@\textit{Diplazium}!chinense@\textit{chinense}} 中華雙蓋蕨 \index{中華雙蓋蕨}  EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+chioui}{\textit{D. chioui} T.C.Hsu}  \index{Diplazium@\textit{Diplazium}!chioui@\textit{chioui}} 邱氏雙蓋蕨 \index{邱氏雙蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+conterminum}{\textit{D. conterminum} Christ}  \index{Diplazium@\textit{Diplazium}!conterminum@\textit{conterminum}} 邊生雙蓋蕨 \index{邊生雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+crassiusculum}{\textit{D. crassiusculum} Ching}  \index{Diplazium@\textit{Diplazium}!crassiusculum@\textit{crassiusculum}} 厚葉雙蓋蕨 \index{厚葉雙蓋蕨}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+dilatatum}{\textit{D. dilatatum} Blume}  \index{Diplazium@\textit{Diplazium}!dilatatum@\textit{dilatatum}} 廣葉鋸齒雙蓋蕨 \index{廣葉鋸齒雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+doederleinii}{\textit{D. doederleinii} (Luerss.) Makino}  \index{Diplazium@\textit{Diplazium}!doederleinii@\textit{doederleinii}} 德氏雙蓋蕨 \index{德氏雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+donianum+var.+aphanoneuron}{\textit{D. donianum} (Mett.) Tardieu var. \textit{aphanoneuron} (Ohwi) Tagawa}  \index{Diplazium@\textit{Diplazium}!donianum@\textit{donianum}!var. aphanoneuron@var. \textit{aphanoneuron}}
                                        隱脈細柄雙蓋蕨 \index{隱脈細柄雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+donianum+var.+donianum}{\textit{D. donianum} (Mett.) Tardieu var. \textit{donianum}}  \index{Diplazium@\textit{Diplazium}!donianum@\textit{donianum}!var. donianum@var. \textit{donianum}}
                                        細柄雙蓋蕨 \index{細柄雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+esculentum+var.+esculentum}{\textit{D. esculentum} (Retz.) Sw. var. \textit{esculentum}}  \index{Diplazium@\textit{Diplazium}!esculentum@\textit{esculentum}!var. esculentum@var. \textit{esculentum}}
                                        過溝菜蕨 \index{過溝菜蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+esculentum+var.+pubescens}{\textit{D. esculentum} (Retz.) Sw. var. \textit{pubescens} (Link) Tardieu \& C.Chr }  \index{Diplazium@\textit{Diplazium}!esculentum@\textit{esculentum}!var. pubescens@var. \textit{pubescens}}
                                        毛軸過溝菜蕨 \index{毛軸過溝菜蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+incomptum}{\textit{D. incomptum} Tagawa}  \index{Diplazium@\textit{Diplazium}!incomptum@\textit{incomptum}} 翅柄雙蓋蕨 \index{翅柄雙蓋蕨}  EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+kappanensis}{\textit{D. kappanensis} Hayata}  \index{Diplazium@\textit{Diplazium}!kappanensis@\textit{kappanensis}} 角板山雙蓋蕨 \index{角板山雙蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+kawakamii}{\textit{D. kawakamii} Hayata}  \index{Diplazium@\textit{Diplazium}!kawakamii@\textit{kawakamii}} 川上氏雙蓋蕨 \index{川上氏雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+ketagalaniorum}{\textit{D. ketagalaniorum} T.C.Hsu}  \index{Diplazium@\textit{Diplazium}!ketagalaniorum@\textit{ketagalaniorum}} 凱達格蘭雙蓋蕨 \index{凱達格蘭雙蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+kuoi}{\textit{D. kuoi} T.C.Hsu}  \index{Diplazium@\textit{Diplazium}!kuoi@\textit{kuoi}} 郭氏雙蓋蕨 \index{郭氏雙蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+laxifrons}{\textit{D. laxifrons} Rosenst.}  \index{Diplazium@\textit{Diplazium}!laxifrons@\textit{laxifrons}} 疏葉雙蓋蕨 \index{疏葉雙蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+lobatum}{\textit{D. lobatum} (Tagawa) Tagawa}  \index{Diplazium@\textit{Diplazium}!lobatum@\textit{lobatum}} 裂葉雙蓋蕨 \index{裂葉雙蓋蕨}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+maonense}{\textit{D. maonense} Ching}  \index{Diplazium@\textit{Diplazium}!maonense@\textit{maonense}} 馬鞍山雙蓋蕨 \index{馬鞍山雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+megaphyllum}{\textit{D. megaphyllum} (Baker) H.Christ}  \index{Diplazium@\textit{Diplazium}!megaphyllum@\textit{megaphyllum}} 大葉雙蓋蕨 \index{大葉雙蓋蕨}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+mettenianum}{\textit{D. mettenianum} (Miq.) C.Chr.}  \index{Diplazium@\textit{Diplazium}!mettenianum@\textit{mettenianum}} 深山雙蓋蕨 \index{深山雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+okinawaensis}{\textit{D. okinawaensis} Tagawa}  \index{Diplazium@\textit{Diplazium}!okinawaensis@\textit{okinawaensis}} 琉球雙蓋蕨 \index{琉球雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+okudairae}{\textit{D. okudairae} Makino}  \index{Diplazium@\textit{Diplazium}!okudairae@\textit{okudairae}} 假耳羽雙蓋蕨 \index{假耳羽雙蓋蕨}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+petri}{\textit{D. petri} Tardieu}  \index{Diplazium@\textit{Diplazium}!petri@\textit{petri}} 廣葉深山雙蓋蕨 \index{廣葉深山雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+phaeolepis}{\textit{D. phaeolepis} Tagawa}  \index{Diplazium@\textit{Diplazium}!phaeolepis@\textit{phaeolepis}} 褐鱗雙蓋蕨 \index{褐鱗雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+proliferum}{\textit{D. proliferum} (Lam.) Thouars}  \index{Diplazium@\textit{Diplazium}!proliferum@\textit{proliferum}} 多生菜蕨 \index{多生菜蕨}  NA DD-P
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+pullingeri}{\textit{D. pullingeri} (Baker) J.Sm.}  \index{Diplazium@\textit{Diplazium}!pullingeri@\textit{pullingeri}} 樸氏雙蓋蕨 \index{樸氏雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+squamigerum}{\textit{D. squamigerum} (Mett.) Hope}  \index{Diplazium@\textit{Diplazium}!squamigerum@\textit{squamigerum}} 長苞雙蓋蕨 \index{長苞雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+taiwanense}{\textit{D. taiwanense} Tagawa}  \index{Diplazium@\textit{Diplazium}!taiwanense@\textit{taiwanense}} 臺灣雙蓋蕨 \index{臺灣雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+virescens}{\textit{D. virescens} Kunze}  \index{Diplazium@\textit{Diplazium}!virescens@\textit{virescens}} 刺柄雙蓋蕨 \index{刺柄雙蓋蕨}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+viridissimum}{\textit{D. viridissimum} Christ}  \index{Diplazium@\textit{Diplazium}!viridissimum@\textit{viridissimum}} 擬德氏雙蓋蕨 \index{擬德氏雙蓋蕨} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplazium+wichurae}{\textit{D. wichurae} (Mett.) Diels}  \index{Diplazium@\textit{Diplazium}!wichurae@\textit{wichurae}} 鋸齒雙蓋蕨 \index{鋸齒雙蓋蕨}  LC
  \end{itemize}
  \end{itemize}
