
  \begin{itemize}
 \item[] \textit{Bothriospermum}\index{Bothriospermum@\textit{Bothriospermum}} 細纍子草屬
                                
  \begin{itemize}
        \item[] \textit{B. zeylanicum} (J. Jacq.) Druce \index{Bothriospermum@\textit{Bothriospermum}!zeylanicum@\textit{zeylanicum}} 細纍子草 \index{細纍子草}  LC
  \end{itemize}
 \item[] \textit{Cynoglossum}\index{Cynoglossum@\textit{Cynoglossum}} 琉璃草屬
                                
  \begin{itemize}
        \item[] \textit{C. alpestre} Ohwi \index{Cynoglossum@\textit{Cynoglossum}!alpestre@\textit{alpestre}} 高山倒提壺 \index{高山倒提壺} \# NT
        \item[] \textit{C. furcatum} Wall. \index{Cynoglossum@\textit{Cynoglossum}!furcatum@\textit{furcatum}} 琉璃草 \index{琉璃草}  LC
        \item[] \textit{C. lanceolatum} Forssk. \index{Cynoglossum@\textit{Cynoglossum}!lanceolatum@\textit{lanceolatum}} 小花倒提壺 \index{小花倒提壺}  LC
  \end{itemize}
 \item[] \textit{Lithospermum}\index{Lithospermum@\textit{Lithospermum}} 紫草屬
                                
  \begin{itemize}
        \item[] \textit{L. zollingeri} DC. \index{Lithospermum@\textit{Lithospermum}!zollingeri@\textit{zollingeri}} 梓木草 \index{梓木草}  VU
  \end{itemize}
 \item[] \textit{Myosotis}\index{Myosotis@\textit{Myosotis}} 勿忘草屬
                                
  \begin{itemize}
        \item[] \textit{M. arvensis} (L.) Hill \index{Myosotis@\textit{Myosotis}!arvensis@\textit{arvensis}} 野勿忘草 \index{野勿忘草}  NA
  \end{itemize}
 \item[] \textit{Symphytum}\index{Symphytum@\textit{Symphytum}} 聚合草屬
                                
  \begin{itemize}
        \item[] \textit{S. officinale} L. \index{Symphytum@\textit{Symphytum}!officinale@\textit{officinale}} 康復力 \index{康復力}  NA
  \end{itemize}
 \item[] \textit{Thyrocarpus}\index{Thyrocarpus@\textit{Thyrocarpus}} 盾果草屬
                                
  \begin{itemize}
        \item[] \textit{T. sampsonii} Hance \index{Thyrocarpus@\textit{Thyrocarpus}!sampsonii@\textit{sampsonii}} 盾果草 \index{盾果草}  LC
  \end{itemize}
 \item[] \textit{Trichodesma}\index{Trichodesma@\textit{Trichodesma}} 碧果草屬
                                
  \begin{itemize}
        \item[] \textit{T. calycosum} Collett \& Hemsl. \index{Trichodesma@\textit{Trichodesma}!calycosum@\textit{calycosum}} 假酸漿 \index{假酸漿}  LC
        \item[] \textit{T. indicum} (L.) Lehm. \index{Trichodesma@\textit{Trichodesma}!indicum@\textit{indicum}} 印度碧果草 \index{印度碧果草}  NA
        \item[] \textit{T. zeylanicum} (Burm.f.) R.Br. \index{Trichodesma@\textit{Trichodesma}!zeylanicum@\textit{zeylanicum}} 斯里蘭卡碧果草 \index{斯里蘭卡碧果草}  NA
  \end{itemize}
 \item[] \textit{Trigonotis}\index{Trigonotis@\textit{Trigonotis}} 附地草屬
                                
  \begin{itemize}
        \item[] \textit{T. formosana} Hayata \index{Trigonotis@\textit{Trigonotis}!formosana@\textit{formosana}} 臺灣附地草 \index{臺灣附地草} \# LC
        \item[] \textit{T. formosana} var. \textit{elevatovenosa} (Hayata) S. D. Shen \& J. C. Wang \index{Trigonotis@\textit{Trigonotis}!formosana@\textit{formosana}!var. elevatovenosa@var. \textit{elevatovenosa}} 臺北附地草 \index{臺北附地草} \# LC
        \item[] \textit{T. nankotaizanensis} (Sasaki) Masam. \& Ohwi ex Masam. \index{Trigonotis@\textit{Trigonotis}!nankotaizanensis@\textit{nankotaizanensis}} 南湖附地草 \index{南湖附地草} \# NT
        \item[] \textit{T. peduncularis} (Trev.) Benth. ex Baker \& S. Moore \index{Trigonotis@\textit{Trigonotis}!peduncularis@\textit{peduncularis}} 附地菜 \index{附地菜}  NA
  \end{itemize}
  \end{itemize}
