
  \begin{itemize}
 \item[] \textit{Arabidopsis} 擬南芥屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arabidopsis+halleri+var.+gemmifera}{\textit{A. halleri} (L.) O'Kane \& Al-Shehbaz var. \textit{gemmifera} (Matsum.) O'Kane \& Al-Shehbaz}  \index{Arabidopsis@\textit{Arabidopsis}!halleri@\textit{halleri}!var. gemmifera@\textbf{var. \textit{gemmifera}}}  \index{Arabis@\textit{Arabis}!gemmifera@\textit{gemmifera}{\\\noindent(= \textit{Arabidopsis halleri} var. \textit{gemmifera})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葉芽筷子芥&T2_new_value=true&fr=y}}{葉芽筷子芥}\index{葉芽筷子芥@{\Song{葉芽筷子芥}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arabidopsis+lyrata+subsp.+kamchatica}{\textit{A. lyrata} (L.) O'Kane \& Al-Shehbaz subsp. \textit{kamchatica} (Fisch. ex DC.) Hultén}  \index{Arabidopsis@\textit{Arabidopsis}!lyrata@\textit{lyrata}!subsp. kamchatica@subsp. \textit{kamchatica}}  \index{Arabis@\textit{Arabis}!lyrata@\textit{lyrata}!subsp. kamtschatica@subsp. \textit{kamtschatica}{\\\noindent(=\textit{Arabidopsis lyrata} subsp. \textit{kamchatica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山筷子芥&T2_new_value=true&fr=y}}{玉山筷子芥}\index{玉山筷子芥} LC
  \end{itemize}
 \item[] \textit{Arabis} 筷子芥屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arabis+alpina+var.+formosana}{\textit{A. alpina} (L.) var. \textit{formosana} Masam. ex S.F.Huang}  \index{Arabis@\textit{Arabis}!alpina@\textit{alpina}!var. formosana@var. \textit{formosana}}  \index{Arabis@\textit{Arabis}!formosana@\textit{formosana}{\\\noindent(= \textit{Arabis alpina} var. \textit{formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣筷子芥&T2_new_value=true&fr=y}}{臺灣筷子芥}\index{臺灣筷子芥}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arabis+serrata}{\textit{A. serrata} Franch. \& Sav.}  \index{Arabis@\textit{Arabis}!serrata@\textit{serrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=齒葉南芥&T2_new_value=true&fr=y}}{齒葉南芥}\index{齒葉南芥} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arabis+stelleris+var.+japonica}{\textit{A. stelleris} DC. var. \textit{japonica} (A.Gray) F.Schmidt}  \index{Arabis@\textit{Arabis}!stelleris@\textit{stelleris}!var. japonica@\textbf{var. \textit{japonica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基隆筷子芥&T2_new_value=true&fr=y}}{基隆筷子芥}\index{基隆筷子芥@{\Song{基隆筷子芥}}} VU
  \end{itemize}
 \item[] \textit{Barbarea} 山芥屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Barbarea+orthoceras}{\textit{B. orthoceras} Ledeb.}  \index{Barbarea@\textit{Barbarea}!orthoceras@\textit{orthoceras}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山芥菜&T2_new_value=true&fr=y}}{山芥菜}\index{山芥菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Barbarea+taiwaniana}{\textit{B. taiwaniana} Ohwi}  \index{Barbarea@\textit{Barbarea}!taiwaniana@\textbf{\textit{taiwaniana}}}  \index{Barbarea@\textit{Barbarea}!arisanense@\textit{arisanense}{\\\noindent(= \textit{Barbarea taiwaniana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山芥菜&T2_new_value=true&fr=y}}{臺灣山芥菜(高山山芥)} \index{臺灣山芥菜@{\Song{臺灣山芥菜}}} \index{高山山芥@{\Song{高山山芥(=臺灣山芥菜)}}}\# EN
  \end{itemize}
 \item[] \textit{Capsella} 薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Capsella+bursa-pastoris}{\textit{C. bursa-pastoris} (L.) Medic.}  \index{Capsella@\textit{Capsella}!bursa-pastoris@\textit{bursa-pastoris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薺&T2_new_value=true&fr=y}}{薺}\index{薺} NA$^n$
  \end{itemize}
 \item[] \textit{Cardamine} 碎米薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+agyokumontana}{\textit{C. agyokumontana} Hayata}  \index{Cardamine@\textit{Cardamine}!agyokumontana@\textit{agyokumontana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿玉碎米薺&T2_new_value=true&fr=y}}{阿玉碎米薺}\index{阿玉碎米薺}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+circaeoides}{\textit{C. circaeoides} Hook.f. \& Thomson}  \index{Cardamine@\textit{Cardamine}!circaeoides@\textit{circaeoides}}  \index{Cardamine@\textit{Cardamine}!reniformis@\textit{reniformis}{\\\noindent(= \textit{Cardamine circaeoides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腎葉碎米薺&T2_new_value=true&fr=y}}{腎葉碎米薺}\index{腎葉碎米薺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+flexuosa}{\textit{C. flexuosa} With.}  \index{Cardamine@\textit{Cardamine}!flexuosa@\textit{flexuosa}}  \index{Barbarea@\textit{Barbarea}!arisanense@\textit{arisanense}{\\\noindent(= \textit{Cardamine flexuosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔊菜&T2_new_value=true&fr=y}}{蔊菜(高山山芥)} \index{蔊菜} \index{高山山芥@{高山山芥(=蔊菜)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+impatiens}{\textit{C. impatiens} L.}  \index{Cardamine@\textit{Cardamine}!impatiens@\textit{impatiens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水花菜&T2_new_value=true&fr=y}}{水花菜}\index{水花菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+nipponica}{\textit{C. nipponica} Franch. \& Sav.}  \index{Cardamine@\textit{Cardamine}!nipponica@\textit{nipponica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本蔊菜&T2_new_value=true&fr=y}}{日本蔊菜}\index{日本蔊菜} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardamine+scutata+var.+rotundiloba}{\textit{C. scutata} Thunb. var. \textit{rotundiloba} (Hayata) T.S.Liu \& S.S.Ying}  \index{Cardamine@\textit{Cardamine}!scutata@\textit{scutata}!var. rotundiloba@var. \textit{rotundiloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣碎米薺&T2_new_value=true&fr=y}}{臺灣碎米薺}\index{臺灣碎米薺}\# LC
  \end{itemize}
 \item[] \textit{Coronopus} 濱芥屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coronopus+didymus}{\textit{C. didymus} (L.) Sm.}  \index{Coronopus@\textit{Coronopus}!didymus@\textit{didymus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭濱芥&T2_new_value=true&fr=y}}{臭濱芥}\index{臭濱芥} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coronopus+integrifolius}{\textit{C. integrifolius} (DC.) Prantl}  \index{Coronopus@\textit{Coronopus}!integrifolius@\textit{integrifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱芥&T2_new_value=true&fr=y}}{濱芥}\index{濱芥} NA$^n$
  \end{itemize}
 \item[] \textit{Draba} 山薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Draba+sekiyana}{\textit{D. sekiyana} Ohwi}  \index{Draba@\textit{Draba}!sekiyana@\textbf{\textit{sekiyana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山薺&T2_new_value=true&fr=y}}{臺灣山薺}\index{臺灣山薺@{\Song{臺灣山薺}}}\# EN
  \end{itemize}
 \item[] \textit{Eutrema} 山葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eutrema+japonica}{\textit{E. japonica} (Miq.) Koidz.}  \index{Eutrema@\textit{Eutrema}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山葵&T2_new_value=true&fr=y}}{山葵}\index{山葵} NA$^n$
  \end{itemize}
 \item[] \textit{Lepidium} 獨行菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidium+bonariense}{\textit{L. bonariense} L.}  \index{Lepidium@\textit{Lepidium}!bonariense@\textit{bonariense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南美獨行菜&T2_new_value=true&fr=y}}{南美獨行菜}\index{南美獨行菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepidium+virginicum}{\textit{L. virginicum} L.}  \index{Lepidium@\textit{Lepidium}!virginicum@\textit{virginicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=獨行菜&T2_new_value=true&fr=y}}{獨行菜}\index{獨行菜} NA$^n$
  \end{itemize}
 \item[] \textit{Nasturtium} 豆瓣菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nasturtium+officinale}{\textit{N. officinale} R.Br.}  \index{Nasturtium@\textit{Nasturtium}!officinale@\textit{officinale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水芥菜&T2_new_value=true&fr=y}}{水芥菜}\index{水芥菜} NA$^n$
  \end{itemize}
 \item[] \textit{Neslia} 球果薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neslia+paniculata}{\textit{N. paniculata} (L.) Desv.}  \index{Neslia@\textit{Neslia}!paniculata@\textit{paniculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球果薺&T2_new_value=true&fr=y}}{球果薺}\index{球果薺} NA$^n$
  \end{itemize}
 \item[] \textit{Raphanus} 萊服屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Raphanus+raphanistrum+subsp.+sativus}{\textit{R. raphanistrum} L. subsp. \textit{sativus} (L.) Domin}  \index{Raphanus@\textit{Raphanus}!raphanistrum@\textit{raphanistrum}!subsp. sativus@subsp. \textit{sativus}}  \index{Raphanus@\textit{Raphanus}!sativus@\textit{sativus}{\\\noindent(= \textit{Raphanus raphanistrum} subsp. \textit{sativus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱萊菔&T2_new_value=true&fr=y}}{濱萊菔}\index{濱萊菔} LC
  \end{itemize}
 \item[] \textit{Rapistrum} 皺果薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rapistrum+rugosum}{\textit{R. rugosum} (L.) All.}  \index{Rapistrum@\textit{Rapistrum}!rugosum@\textit{rugosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=皺果薺&T2_new_value=true&fr=y}}{皺果薺}\index{皺果薺} NA$^n$
  \end{itemize}
 \item[] \textit{Rorippa} 葶藶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+austriaca}{\textit{R. austriaca} (Crantz) Besser}  \index{Rorippa@\textit{Rorippa}!austriaca@\textit{austriaca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奧地利葶藶&T2_new_value=true&fr=y}}{奧地利葶藶}\index{奧地利葶藶} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+cantoniensis}{\textit{R. cantoniensis} (Lour.) Ohwi}  \index{Rorippa@\textit{Rorippa}!cantoniensis@\textit{cantoniensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=廣東葶藶&T2_new_value=true&fr=y}}{廣東葶藶}\index{廣東葶藶} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+dubia}{\textit{R. dubia} (Pers.) H.Hara}  \index{Rorippa@\textit{Rorippa}!dubia@\textit{dubia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葶藶&T2_new_value=true&fr=y}}{小葶藶}\index{小葶藶} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+globosa}{\textit{R. globosa} (Turcz. ex Fisch. \& C.A.Mey) Hayek}  \index{Rorippa@\textit{Rorippa}!globosa@\textit{globosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=風花菜&T2_new_value=true&fr=y}}{風花菜}\index{風花菜} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+indica}{\textit{R. indica} (L.) Hiern}  \index{Rorippa@\textit{Rorippa}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葶藶&T2_new_value=true&fr=y}}{葶藶}\index{葶藶} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+palustris}{\textit{R. palustris} (L.) Besser}  \index{Rorippa@\textit{Rorippa}!palustris@\textit{palustris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濕生葶藶&T2_new_value=true&fr=y}}{濕生葶藶}\index{濕生葶藶} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rorippa+sylvestris}{\textit{R. sylvestris} (L.) Besser}  \index{Rorippa@\textit{Rorippa}!sylvestris@\textit{sylvestris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=歐亞葶藶&T2_new_value=true&fr=y}}{歐亞葶藶}\index{歐亞葶藶} NA$^n$
  \end{itemize}
 \item[] \textit{Sisymbrium} 抪娘蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sisymbrium+irio}{\textit{S. irio} L.}  \index{Sisymbrium@\textit{Sisymbrium}!irio@\textit{irio}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=抪娘蒿&T2_new_value=true&fr=y}}{抪娘蒿}\index{抪娘蒿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sisymbrium+orientale}{\textit{S. orientale} L.}  \index{Sisymbrium@\textit{Sisymbrium}!orientale@\textit{orientale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=戟葉抪娘蒿&T2_new_value=true&fr=y}}{戟葉抪娘蒿}\index{戟葉抪娘蒿} NA$^n$
  \end{itemize}
 \item[] \textit{Thlaspi} 菥蓂屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thlaspi+arvense}{\textit{T. arvense} L.}  \index{Thlaspi@\textit{Thlaspi}!arvense@\textit{arvense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹果菥蓂&T2_new_value=true&fr=y}}{凹果菥蓂}\index{凹果菥蓂} NA$^n$
  \end{itemize}
 \item[] \textit{Yinshania} 假山葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Yinshania+rivulorum}{\textit{Y. rivulorum} (Dunn) Al-Shehbaz, G.Yang, L.L.Lu \& T.Y.Cheo}  \index{Yinshania@\textit{Yinshania}!rivulorum@\textit{rivulorum}}  \index{Cochlearia@\textit{Cochlearia}!formosana@\textit{formosana}{\\\noindent(= \textit{Yinshania rivulorum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣假山葵&T2_new_value=true&fr=y}}{臺灣假山葵}\index{臺灣假山葵} NT
  \end{itemize}
  \end{itemize}
