
  \begin{itemize}
 \item[] \textit{Buxus} 黃楊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Buxus+liukiuensis}{\textit{B. liukiuensis} Makino}  \index{Buxus@\textit{Buxus}!liukiuensis@\textit{liukiuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球黃楊&T2_new_value=true&fr=y}}{琉球黃楊}\index{琉球黃楊} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Buxus+microphylla+subsp.+sinica}{\textit{B. microphylla} Siebold \& Zucc. subsp. \textit{sinica} (Rehder \& E.H.Wils.) Hatus.}  \index{Buxus@\textit{Buxus}!microphylla@\textit{microphylla}!subsp. sinica@subsp. \textit{sinica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃楊&T2_new_value=true&fr=y}}{黃楊}\index{黃楊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Buxus+microphylla+subsp.+sinica+var.+tarokoensis}{\textit{B. microphylla} Siebold subsp. \textit{sinica} (Rehder \& E.H.Wils.) Hatus. var. \textit{tarokoensis} S.Y.Lu \& Yuen P.Yang}  \index{Buxus@\textit{Buxus}!microphylla@\textit{microphylla}!subsp. sinica var. tarokoensis@\textbf{subsp. \textit{sinica} var. \textit{tarokoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣黃楊&T2_new_value=true&fr=y}}{太魯閣黃楊}\index{太魯閣黃楊@{\Song{太魯閣黃楊}}}\# VU
  \end{itemize}
 \item[] \textit{Pachysandra} 三角咪屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pachysandra+axillaris}{\textit{P. axillaris} Franch.}  \index{Pachysandra@\textit{Pachysandra}!axillaris@\textit{axillaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三角咪草&T2_new_value=true&fr=y}}{三角咪草}\index{三角咪草} DD
  \end{itemize}
 \item[] \textit{Sarcococca} 野扇花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sarcococca+saligna}{\textit{S. saligna} (D.Don) Müll.Arg.}  \index{Sarcococca@\textit{Sarcococca}!saligna@\textit{saligna}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柳狀野扇花&T2_new_value=true&fr=y}}{柳狀野扇花}\index{柳狀野扇花} NT
  \end{itemize}
  \end{itemize}
