
  \begin{itemize}
 \item[] \textit{Adenophora} 沙參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adenophora+morrisonensis+subsp.+Morrisonensis}{\textit{A. morrisonensis} Hayata subsp. \textit{Morrisonensis} }  \index{Adenophora@\textit{Adenophora}!morrisonensis@\textit{morrisonensis}!subsp. Morrisonensis@subsp. \textit{Morrisonensis}} 玉山沙參\index{玉山沙參}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adenophora+morrisonensis+subsp.+uehatae}{\textit{A. morrisonensis} Hayata subsp. \textit{uehatae} (Yamam.) Lammers}  \index{Adenophora@\textit{Adenophora}!morrisonensis@\textit{morrisonensis}!subsp. uehatae@subsp. \textit{uehatae}} 高山沙參\index{高山沙參}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adenophora+triphylla}{\textit{A. triphylla} (Thunb.) A.DC.}  \index{Adenophora@\textit{Adenophora}!triphylla@\textit{triphylla}} 輪葉沙參\index{輪葉沙參} LC
  \end{itemize}
 \item[] \textit{Campanula} 桔梗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Campanula+dimorphantha}{\textit{C. dimorphantha} Schweinf.}  \index{Campanula@\textit{Campanula}!dimorphantha@\textit{dimorphantha}} 桔梗\index{桔梗} NT
  \end{itemize}
 \item[] \textit{Codonopsis} 山奶草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Codonopsis+javanica+subsp.+japonica}{\textit{C. javanica} (Blume) Miq. subsp. \textit{japonica} (Maxim. ex Makino) Lammers}  \index{Codonopsis@\textit{Codonopsis}!javanica@\textit{javanica}!subsp. japonica@subsp. \textit{japonica}} 金錢豹\index{金錢豹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Codonopsis+kawakamii}{\textit{C. kawakamii} Hayata}  \index{Codonopsis@\textit{Codonopsis}!kawakamii@\textit{kawakamii}} 玉山山奶草\index{玉山山奶草}\# LC
  \end{itemize}
 \item[] \textit{Cyclocodon} 土黨參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyclocodon+lancifolius}{\textit{C. lancifolius} (Roxb.) Kurz}  \index{Cyclocodon@\textit{Cyclocodon}!lancifolius@\textit{lancifolius}} 臺灣土黨參\index{臺灣土黨參} LC
  \end{itemize}
 \item[] \textit{Hippobroma} 馬醉草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hippobroma+longiflora}{\textit{H. longiflora} (L.) G.Don}  \index{Hippobroma@\textit{Hippobroma}!longiflora@\textit{longiflora}} 馬醉草\index{馬醉草} NA$^n$
  \end{itemize}
 \item[] \textit{Lobelia} 山梗菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+alsinoides+subsp.+hancei}{\textit{L. alsinoides} Lam. subsp. \textit{hancei} (H.Hara) Lammers}  \index{Lobelia@\textit{Lobelia}!alsinoides@\textit{alsinoides}!subsp. hancei@subsp. \textit{hancei}} 短柄半邊蓮\index{短柄半邊蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+chinensis}{\textit{L. chinensis} Lour.}  \index{Lobelia@\textit{Lobelia}!chinensis@\textit{chinensis}} 半邊蓮\index{半邊蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+cliffortiana}{\textit{L. cliffortiana} L.}  \index{Lobelia@\textit{Lobelia}!cliffortiana@\textit{cliffortiana}} 克氏半邊蓮\index{克氏半邊蓮} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+nummularia}{\textit{L. nummularia} Lam.}  \index{Lobelia@\textit{Lobelia}!nummularia@\textit{nummularia}} 普剌特草\index{普剌特草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+seguinii}{\textit{L. seguinii} H.Lév. \& Vaniot}  \index{Lobelia@\textit{Lobelia}!seguinii@\textit{seguinii}} 大本山梗菜\index{大本山梗菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lobelia+zeylanica}{\textit{L. zeylanica} L.}  \index{Lobelia@\textit{Lobelia}!zeylanica@\textit{zeylanica}} 圓葉山梗菜\index{圓葉山梗菜} LC
  \end{itemize}
 \item[] \textit{Peracarpa} 山桔梗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peracarpa+carnosa}{\textit{P. carnosa} (Wall.) Hook.f. \& Thomson}  \index{Peracarpa@\textit{Peracarpa}!carnosa@\textit{carnosa}} 山桔梗\index{山桔梗} LC
  \end{itemize}
 \item[] \textit{Triodanis} 異檐花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triodanis+biflora}{\textit{T. biflora} (Ruiz \& Pav.) Greene}  \index{Triodanis@\textit{Triodanis}!biflora@\textit{biflora}} 卵葉異檐花\index{卵葉異檐花} NA$^n$
  \end{itemize}
 \item[] \textit{Wahlenbergia} 蘭花參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wahlenbergia+marginata}{\textit{W. marginata} (Thunb.) A.DC.}  \index{Wahlenbergia@\textit{Wahlenbergia}!marginata@\textit{marginata}} 細葉蘭花參\index{細葉蘭花參} LC
  \end{itemize}
  \end{itemize}
