
  \begin{itemize}
 \item[] \textit{Abelia} 六道木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abelia+chinensis+var.+ionandra}{\textit{A. chinensis} R.Br. var. \textit{ionandra} (Hayata) Masam.}  \index{Abelia@\textit{Abelia}!chinensis@\textit{chinensis}!var. ionandra@\textbf{var. \textit{ionandra}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣糯米條&T2_new_value=true&fr=y}}{臺灣糯米條}\index{臺灣糯米條@{\Song{臺灣糯米條}}}\# VU
  \end{itemize}
 \item[] \textit{Lonicera} 忍冬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+acuminata}{\textit{L. acuminata} Wall.}  \index{Lonicera@\textit{Lonicera}!acuminata@\textit{acuminata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山忍冬&T2_new_value=true&fr=y}}{阿里山忍冬}\index{阿里山忍冬} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+apodantha}{\textit{L. apodantha} Ohwi}  \index{Lonicera@\textit{Lonicera}!apodantha@\textit{apodantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無梗忍冬&T2_new_value=true&fr=y}}{無梗忍冬}\index{無梗忍冬}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+hypoglauca}{\textit{L. hypoglauca} Miq.}  \index{Lonicera@\textit{Lonicera}!hypoglauca@\textit{hypoglauca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白忍冬&T2_new_value=true&fr=y}}{裏白忍冬}\index{裏白忍冬} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+japonica}{\textit{L. japonica} Thunb.}  \index{Lonicera@\textit{Lonicera}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=忍冬&T2_new_value=true&fr=y}}{忍冬}\index{忍冬} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+kawakamii}{\textit{L. kawakamii} (Hayata) Masam.}  \index{Lonicera@\textit{Lonicera}!kawakamii@\textbf{\textit{kawakamii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=川上氏忍冬&T2_new_value=true&fr=y}}{川上氏忍冬}\index{川上氏忍冬@{\Song{川上氏忍冬}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+macrantha}{\textit{L. macrantha} (D.Don) Spreng.}  \index{Lonicera@\textit{Lonicera}!macrantha@\textbf{\textit{macrantha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花忍冬&T2_new_value=true&fr=y}}{大花忍冬}\index{大花忍冬@{\Song{大花忍冬}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lonicera+oiwakensis}{\textit{L. oiwakensis} Hayata}  \index{Lonicera@\textit{Lonicera}!oiwakensis@\textbf{\textit{oiwakensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=追分忍冬&T2_new_value=true&fr=y}}{追分忍冬}\index{追分忍冬@{\Song{追分忍冬}}}\# VU
  \end{itemize}
 \item[] \textit{Patrinia} 敗醬屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Patrinia+formosana}{\textit{P. formosana} Kitam.}  \index{Patrinia@\textit{Patrinia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣敗醬&T2_new_value=true&fr=y}}{臺灣敗醬}\index{臺灣敗醬}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Patrinia+glabrifolia}{\textit{P. glabrifolia} Yamam. \& Sasaki}  \index{Patrinia@\textit{Patrinia}!glabrifolia@\textit{glabrifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=禿敗醬&T2_new_value=true&fr=y}}{禿敗醬}\index{禿敗醬}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Patrinia+scabiosifolia}{\textit{P. scabiosifolia} Fisch. ex Trevir.}  \index{Patrinia@\textit{Patrinia}!scabiosifolia@\textit{scabiosifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花龍芽草&T2_new_value=true&fr=y}}{黃花龍芽草}\index{黃花龍芽草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Patrinia+villosa}{\textit{P. villosa} (Thunb.) Juss. ex DC.}  \index{Patrinia@\textit{Patrinia}!villosa@\textit{villosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛敗醬&T2_new_value=true&fr=y}}{毛敗醬}\index{毛敗醬} LC
  \end{itemize}
 \item[] \textit{Scabiosa} 山蘿蔔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scabiosa+lacerifolia}{\textit{S. lacerifolia} Hayata}  \index{Scabiosa@\textit{Scabiosa}!lacerifolia@\textit{lacerifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山山蘿蔔&T2_new_value=true&fr=y}}{玉山山蘿蔔}\index{玉山山蘿蔔}\# LC
  \end{itemize}
 \item[] \textit{Triplostegia} 小纈草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triplostegia+glandulifera}{\textit{T. glandulifera} Wall. ex DC.}  \index{Triplostegia@\textit{Triplostegia}!glandulifera@\textit{glandulifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三萼花草&T2_new_value=true&fr=y}}{三萼花草}\index{三萼花草} LC
  \end{itemize}
 \item[] \textit{Valeriana} 纈草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Valeriana+fauriei}{\textit{V. fauriei} Briq.}  \index{Valeriana@\textit{Valeriana}!fauriei@\textit{fauriei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=纈草&T2_new_value=true&fr=y}}{纈草}\index{纈草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Valeriana+flaccidissima}{\textit{V. flaccidissima} Maxim.}  \index{Valeriana@\textit{Valeriana}!flaccidissima@\textit{flaccidissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=嫩莖纈草&T2_new_value=true&fr=y}}{嫩莖纈草}\index{嫩莖纈草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Valeriana+kawakamii}{\textit{V. kawakamii} Hayata}  \index{Valeriana@\textit{Valeriana}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山纈草&T2_new_value=true&fr=y}}{高山纈草}\index{高山纈草}\# LC
  \end{itemize}
  \end{itemize}
