
  \begin{itemize}
 \item[] \textit{Arenaria} 無心菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arenaria+serpyllifolia}{\textit{A. serpyllifolia} L.}  \index{Arenaria@\textit{Arenaria}!serpyllifolia@\textit{serpyllifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無心菜&T2_new_value=true&fr=y}}{無心菜}\index{無心菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arenaria+subpilosa}{\textit{A. subpilosa} (Hayata) Ohwi}  \index{Arenaria@\textit{Arenaria}!subpilosa@\textit{subpilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亞毛無心菜&T2_new_value=true&fr=y}}{亞毛無心菜}\index{亞毛無心菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arenaria+takasagomontana}{\textit{A. takasagomontana} (Masam.) S.S.Ying}  \index{Arenaria@\textit{Arenaria}!takasagomontana@\textit{takasagomontana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山無心菜&T2_new_value=true&fr=y}}{高山無心菜}\index{高山無心菜}\# LC
  \end{itemize}
 \item[] \textit{Cerastium} 卷耳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerastium+fontanum+var.+angustifolium}{\textit{C. fontanum} Baumg. var. \textit{angustifolium} (M.Mizush.) H.Hara}  \index{Cerastium@\textit{Cerastium}!fontanum@\textit{fontanum}!var. angustifolium@var. \textit{angustifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山卷耳&T2_new_value=true&fr=y}}{玉山卷耳}\index{玉山卷耳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerastium+formosanum}{\textit{C. formosanum} Ohwi}  \index{Cerastium@\textit{Cerastium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣卷耳&T2_new_value=true&fr=y}}{臺灣卷耳}\index{臺灣卷耳}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerastium+glomeratum}{\textit{C. glomeratum} Thuill.}  \index{Cerastium@\textit{Cerastium}!glomeratum@\textit{glomeratum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球序卷耳&T2_new_value=true&fr=y}}{球序卷耳}\index{球序卷耳} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerastium+holosteoides+var.+hallaisanense}{\textit{C. holosteoides} Fr. var. \textit{hallaisanense} (Nakai) Mizush.}  \index{Cerastium@\textit{Cerastium}!holosteoides@\textit{holosteoides}!var. hallaisanense@var. \textit{hallaisanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=卷耳&T2_new_value=true&fr=y}}{卷耳}\index{卷耳} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cerastium+parvipetalum}{\textit{C. parvipetalum} Hosok.}  \index{Cerastium@\textit{Cerastium}!parvipetalum@\textit{parvipetalum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小瓣卷耳&T2_new_value=true&fr=y}}{小瓣卷耳}\index{小瓣卷耳}\# LC
  \end{itemize}
 \item[] \textit{Cucubalus} 狗筋蔓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cucubalus+baccifer}{\textit{C. baccifer} L.}  \index{Cucubalus@\textit{Cucubalus}!baccifer@\textit{baccifer}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狗筋蔓&T2_new_value=true&fr=y}}{狗筋蔓}\index{狗筋蔓} LC
  \end{itemize}
 \item[] \textit{Dianthus} 石竹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dianthus+palinensis}{\textit{D. palinensis} S.S.Ying}  \index{Dianthus@\textit{Dianthus}!palinensis@\textbf{\textit{palinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巴陵石竹&T2_new_value=true&fr=y}}{巴陵石竹}\index{巴陵石竹@{\Song{巴陵石竹}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dianthus+pygmaeus}{\textit{D. pygmaeus} Hayata}  \index{Dianthus@\textit{Dianthus}!pygmaeus@\textbf{\textit{pygmaeus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山石竹&T2_new_value=true&fr=y}}{玉山石竹}\index{玉山石竹@{\Song{玉山石竹}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dianthus+pygmaeus+ f. +albiflorus}{\textit{D. pygmaeus} Hayata  f.  \textit{albiflorus} (S.S.Ying) S.S.Ying}  \index{Dianthus@\textit{Dianthus}!pygmaeus@\textit{pygmaeus}!f. albiflorus@f. \textit{albiflorus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花玉山石竹&T2_new_value=true&fr=y}}{白花玉山石竹}\index{白花玉山石竹}\# NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dianthus+superbus+var.+longicalycinus}{\textit{D. superbus} L. var. \textit{longicalycinus} (Maxim.) Will.}  \index{Dianthus@\textit{Dianthus}!superbus@\textit{superbus}!var. longicalycinus@var. \textit{longicalycinus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長萼瞿麥&T2_new_value=true&fr=y}}{長萼瞿麥}\index{長萼瞿麥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dianthus+superbus+var.+taiwanensis}{\textit{D. superbus} L. var. \textit{taiwanensis} (Masam.) T.S.Liu \& S.S.Ying}  \index{Dianthus@\textit{Dianthus}!superbus@\textit{superbus}!var. taiwanensis@var. \textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣瞿麥&T2_new_value=true&fr=y}}{臺灣瞿麥}\index{臺灣瞿麥}\# LC
  \end{itemize}
 \item[] \textit{Drymaria} 荷蓮豆草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Drymaria+cordata}{\textit{D. cordata} (L.) Willd. ex Schult.}  \index{Drymaria@\textit{Drymaria}!cordata@\textit{cordata}}  \index{Drymaria@\textit{Drymaria}!diandra@\textit{diandra}{\\\noindent(= \textit{Drymaria cordata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=荷蓮豆草&T2_new_value=true&fr=y}}{荷蓮豆草(菁芳草)} \index{荷蓮豆草} \index{菁芳草@{菁芳草(=荷蓮豆草)}} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Drymaria+villosa}{\textit{D. villosa} Cham. \& Schltdl.}  \index{Drymaria@\textit{Drymaria}!villosa@\textit{villosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛荷蓮豆草&T2_new_value=true&fr=y}}{毛荷蓮豆草}\index{毛荷蓮豆草} NA$^n$
  \end{itemize}
 \item[] \textit{Moehringia} 種阜草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Moehringia+trinervia}{\textit{M. trinervia} (L.) Clairv.}  \index{Moehringia@\textit{Moehringia}!trinervia@\textit{trinervia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三脈種阜草&T2_new_value=true&fr=y}}{三脈種阜草}\index{三脈種阜草} LC
  \end{itemize}
 \item[] \textit{Polycarpaea} 白鼓釘屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polycarpaea+corymbosa}{\textit{P. corymbosa} (L.) Lam.}  \index{Polycarpaea@\textit{Polycarpaea}!corymbosa@\textit{corymbosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白鼓釘&T2_new_value=true&fr=y}}{白鼓釘}\index{白鼓釘} DD
  \end{itemize}
 \item[] \textit{Polycarpon} 多莢草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polycarpon+tetraphyllum}{\textit{P. tetraphyllum} (L.) L.}  \index{Polycarpon@\textit{Polycarpon}!tetraphyllum@\textit{tetraphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=四葉多莢草&T2_new_value=true&fr=y}}{四葉多莢草}\index{四葉多莢草} NA$^n$
  \end{itemize}
 \item[] \textit{Sagina} 瓜槌草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sagina+japonica}{\textit{S. japonica} (Sw. ex Steud.) Ohwi}  \index{Sagina@\textit{Sagina}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓜槌草&T2_new_value=true&fr=y}}{瓜槌草}\index{瓜槌草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sagina+maxima}{\textit{S. maxima} A.Gray}  \index{Sagina@\textit{Sagina}!maxima@\textit{maxima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大瓜槌草&T2_new_value=true&fr=y}}{大瓜槌草}\index{大瓜槌草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sagina+procumbens}{\textit{S. procumbens} L.}  \index{Sagina@\textit{Sagina}!procumbens@\textit{procumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=仰臥漆姑草&T2_new_value=true&fr=y}}{仰臥漆姑草}\index{仰臥漆姑草} NA$^n$
  \end{itemize}
 \item[] \textit{Silene} 蠅子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+fortunei+var.+fortunei}{\textit{S. fortunei} Vis. var. \textit{fortunei}}  \index{Silene@\textit{Silene}!fortunei@\textit{fortunei}!var. fortunei@var. \textit{fortunei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蠅子草&T2_new_value=true&fr=y}}{蠅子草}\index{蠅子草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+fortunei+var.+kiruninsularis}{\textit{S. fortunei} Vis. var. \textit{kiruninsularis} (Masam.) S.S.Ying}  \index{Silene@\textit{Silene}!fortunei@\textit{fortunei}!var. kiruninsularis@\textbf{var. \textit{kiruninsularis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基隆蠅子草&T2_new_value=true&fr=y}}{基隆蠅子草}\index{基隆蠅子草@{\Song{基隆蠅子草}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+gallica}{\textit{S. gallica} L.}  \index{Silene@\textit{Silene}!gallica@\textit{gallica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匙葉麥瓶草&T2_new_value=true&fr=y}}{匙葉麥瓶草}\index{匙葉麥瓶草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+glabella}{\textit{S. glabella} (Ohwi) S.S.Ying}  \index{Silene@\textit{Silene}!glabella@\textbf{\textit{glabella}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖大山蠅子草&T2_new_value=true&fr=y}}{南湖大山蠅子草}\index{南湖大山蠅子草@{\Song{南湖大山蠅子草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+morii}{\textit{S. morii} Hayata}  \index{Silene@\textit{Silene}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蠅子草&T2_new_value=true&fr=y}}{臺灣蠅子草}\index{臺灣蠅子草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Silene+morrisonmontana}{\textit{S. morrisonmontana} (Hayata) Ohwi \& H.Ohashi}  \index{Silene@\textit{Silene}!morrisonmontana@\textbf{\textit{morrisonmontana}}}  \index{Silene@\textit{Silene}!transalpina@\textit{transalpina}{\\\noindent(= \textit{Silene morrisonmontana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山蠅子草&T2_new_value=true&fr=y}}{玉山蠅子草}\index{玉山蠅子草@{\Song{玉山蠅子草}}}\# VU
  \end{itemize}
 \item[] \textit{Spergula} 大爪草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spergula+arvensis}{\textit{S. arvensis} L.}  \index{Spergula@\textit{Spergula}!arvensis@\textit{arvensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大爪草&T2_new_value=true&fr=y}}{大爪草}\index{大爪草} NA$^n$
  \end{itemize}
 \item[] \textit{Spergularia} 牛漆姑草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spergularia+marina}{\textit{S. marina} (L.) Griseb.}  \index{Spergularia@\textit{Spergularia}!marina@\textit{marina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬漆姑&T2_new_value=true&fr=y}}{擬漆姑}\index{擬漆姑} NT
  \end{itemize}
 \item[] \textit{Stellaria} 繁縷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+alsine+var.+undulata}{\textit{S. alsine} Grimm. var. \textit{undulata} (Thunb.) Ohwi}  \index{Stellaria@\textit{Stellaria}!alsine@\textit{alsine}!var. undulata@var. \textit{undulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天蓬草&T2_new_value=true&fr=y}}{天蓬草}\index{天蓬草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+aquatica}{\textit{S. aquatica} (L.) Scop.}  \index{Stellaria@\textit{Stellaria}!aquatica@\textit{aquatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝兒腸&T2_new_value=true&fr=y}}{鵝兒腸}\index{鵝兒腸} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+arisanensis}{\textit{S. arisanensis} (Hayata) Hayata}  \index{Stellaria@\textit{Stellaria}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山繁縷&T2_new_value=true&fr=y}}{阿里山繁縷}\index{阿里山繁縷}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+media}{\textit{S. media} (L.) Vill.}  \index{Stellaria@\textit{Stellaria}!media@\textit{media}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繁縷&T2_new_value=true&fr=y}}{繁縷}\index{繁縷} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+reticulivena}{\textit{S. reticulivena} Hayata}  \index{Stellaria@\textit{Stellaria}!reticulivena@\textit{reticulivena}}  \index{Stellaria@\textit{Stellaria}!media@\textit{media}!var. micrantha@var. \textit{micrantha}{\\\noindent(=\textit{Stellaria reticulivena})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈繁縷&T2_new_value=true&fr=y}}{網脈繁縷}\index{網脈繁縷}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stellaria+saxatilis}{\textit{S. saxatilis} Buch.-Ham. ex D.Don}  \index{Stellaria@\textit{Stellaria}!saxatilis@\textit{saxatilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花繁縷&T2_new_value=true&fr=y}}{疏花繁縷}\index{疏花繁縷} LC
  \end{itemize}
  \end{itemize}
