
  \begin{itemize}
 \item[] \textit{Celastrus} 南蛇藤屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celastrus+hindsii}{\textit{C. hindsii} Benth.}  \index{Celastrus@\textit{Celastrus}!hindsii@\textit{hindsii}} 南華南蛇藤 \index{南華南蛇藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celastrus+kusanoi}{\textit{C. kusanoi} Hayata}  \index{Celastrus@\textit{Celastrus}!kusanoi@\textit{kusanoi}} 大葉南蛇藤 \index{大葉南蛇藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celastrus+paniculatus}{\textit{C. paniculatus} Willd.}  \index{Celastrus@\textit{Celastrus}!paniculatus@\textit{paniculatus}} 多花滇南蛇藤 \index{多花滇南蛇藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Celastrus+punctatus}{\textit{C. punctatus} Thunb.}  \index{Celastrus@\textit{Celastrus}!punctatus@\textit{punctatus}} 光果南蛇藤 \index{光果南蛇藤}  LC
  \end{itemize}
 \item[] \textit{Euonymus} 衛矛屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+carnosus}{\textit{E. carnosus} Hemsl.}  \index{Euonymus@\textit{Euonymus}!carnosus@\textit{carnosus}} 厚葉衛矛 \index{厚葉衛矛}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+cochinchinensis}{\textit{E. cochinchinensis} Pierre}  \index{Euonymus@\textit{Euonymus}!cochinchinensis@\textit{cochinchinensis}} 交趾衛矛 \index{交趾衛矛}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+huangii}{\textit{E. huangii} H.Y.Liu \& Yuen P.Yang}  \index{Euonymus@\textit{Euonymus}!huangii@\textit{huangii}} 黃氏衛矛 \index{黃氏衛矛} \# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+japonicus}{\textit{E. japonicus} Thunb.}  \index{Euonymus@\textit{Euonymus}!japonicus@\textit{japonicus}} 日本衛矛 \index{日本衛矛}  CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+laxiflorus}{\textit{E. laxiflorus} Champ. ex Benth.}  \index{Euonymus@\textit{Euonymus}!laxiflorus@\textit{laxiflorus}} 大丁黃 \index{大丁黃}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+oxyphyllus}{\textit{E. oxyphyllus} Miq.}  \index{Euonymus@\textit{Euonymus}!oxyphyllus@\textit{oxyphyllus}} 垂絲衛矛 \index{垂絲衛矛}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+pallidifolia}{\textit{E. pallidifolia} Hayata}  \index{Euonymus@\textit{Euonymus}!pallidifolia@\textit{pallidifolia}} 淡綠葉衛矛 \index{淡綠葉衛矛} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+spraguei}{\textit{E. spraguei} Hayata}  \index{Euonymus@\textit{Euonymus}!spraguei@\textit{spraguei}} 刺果衛矛 \index{刺果衛矛} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+tashiroi}{\textit{E. tashiroi} Maxim.}  \index{Euonymus@\textit{Euonymus}!tashiroi@\textit{tashiroi}} 菱葉衛矛 \index{菱葉衛矛}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euonymus+trichocarpus}{\textit{E. trichocarpus} Hayata}  \index{Euonymus@\textit{Euonymus}!trichocarpus@\textit{trichocarpus}} 卵葉刺果衛矛 \index{卵葉刺果衛矛} \# DD
  \end{itemize}
 \item[] \textit{Maytenus} 美登木屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maytenus+diversifolia}{\textit{M. diversifolia} (Maxim.) D.Hou}  \index{Maytenus@\textit{Maytenus}!diversifolia@\textit{diversifolia}} 北仲 \index{北仲}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maytenus+emarginata}{\textit{M. emarginata} (Willd.) D.Hou}  \index{Maytenus@\textit{Maytenus}!emarginata@\textit{emarginata}} 蘭嶼裸實 \index{蘭嶼裸實}  NT
  \end{itemize}
 \item[] \textit{Microtropis} 假衛矛屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microtropis+fokienensis}{\textit{M. fokienensis} Dunn}  \index{Microtropis@\textit{Microtropis}!fokienensis@\textit{fokienensis}} 福建賽衛矛 \index{福建賽衛矛}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microtropis+japonica}{\textit{M. japonica} (Franch. \& Sav.) Hallier f.}  \index{Microtropis@\textit{Microtropis}!japonica@\textit{japonica}} 日本賽衛矛 \index{日本賽衛矛}  LC
  \end{itemize}
 \item[] \textit{Parnassia} 梅花草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parnassia+palustris}{\textit{P. palustris} L.}  \index{Parnassia@\textit{Parnassia}!palustris@\textit{palustris}} 梅花草 \index{梅花草}  LC
  \end{itemize}
 \item[] \textit{Tripterygium} 雷公藤屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tripterygium+wilfordii}{\textit{T. wilfordii} Hook.f.}  \index{Tripterygium@\textit{Tripterygium}!wilfordii@\textit{wilfordii}} 雷公藤 \index{雷公藤}  NT
  \end{itemize}
  \end{itemize}
