
  \begin{itemize}
 \item[] \textit{Amischotolype}\index{Amischotolype@\textit{Amischotolype}} 穿鞘花屬
                                
  \begin{itemize}
        \item[] \textit{A. hispida} (Less. \& A. Rich.) D. Y. Hong \index{Amischotolype@\textit{Amischotolype}!hispida@\textit{hispida}} 穿鞘花 \index{穿鞘花}  LC
  \end{itemize}
 \item[] \textit{Belosynapsis}\index{Belosynapsis@\textit{Belosynapsis}} 假紫萬年青屬
                                
  \begin{itemize}
        \item[] \textit{B. ciliata} (Blume) R. S. Rao \index{Belosynapsis@\textit{Belosynapsis}!ciliata@\textit{ciliata}} 毛葉鴨舌疝 \index{毛葉鴨舌疝}  LC
        \item[] \textit{B. kawakamii} (Hayata) C.-I Peng \& Y. J. Chen. \index{Belosynapsis@\textit{Belosynapsis}!kawakamii@\textit{kawakamii}} 川上氏鴨舌疝 \index{川上氏鴨舌疝} \# NT
  \end{itemize}
 \item[] \textit{Callisia}\index{Callisia@\textit{Callisia}} 大葉錦竹草屬
                                
  \begin{itemize}
        \item[] \textit{C. fragrans} (Lindl.) Woodson \index{Callisia@\textit{Callisia}!fragrans@\textit{fragrans}} 大葉錦竹草 \index{大葉錦竹草}  NA
        \item[] \textit{C. repens} (Jacq.) L. \index{Callisia@\textit{Callisia}!repens@\textit{repens}} 鋪地錦竹草
 \index{鋪地錦竹草
}  NA
  \end{itemize}
 \item[] \textit{Commelina}\index{Commelina@\textit{Commelina}} 鴨跖草屬
                                
  \begin{itemize}
        \item[] \textit{C. auriculata} Blume \index{Commelina@\textit{Commelina}!auriculata@\textit{auriculata}} 耳葉鴨跖草 \index{耳葉鴨跖草}  LC
        \item[] \textit{C. benghalensis} L. \index{Commelina@\textit{Commelina}!benghalensis@\textit{benghalensis}} 圓葉鴨跖草 \index{圓葉鴨跖草}  LC
        \item[] \textit{C. communis} L. \index{Commelina@\textit{Commelina}!communis@\textit{communis}} 鴨跖草 \index{鴨跖草}  LC
        \item[] \textit{C. diffusa} Burm. f. \index{Commelina@\textit{Commelina}!diffusa@\textit{diffusa}} 竹仔菜 \index{竹仔菜}  LC
        \item[] \textit{C. paludosa} Blume \index{Commelina@\textit{Commelina}!paludosa@\textit{paludosa}} 大葉鴨跖草 \index{大葉鴨跖草}  LC
  \end{itemize}
 \item[] \textit{Cyanotis}\index{Cyanotis@\textit{Cyanotis}} 鴨舌疝屬
                                
  \begin{itemize}
        \item[] \textit{C. arachnoidea} C. B. Clarke \index{Cyanotis@\textit{Cyanotis}!arachnoidea@\textit{arachnoidea}} 蛛絲毛藍耳草 \index{蛛絲毛藍耳草}  LC
        \item[] \textit{C. axillaris} (L.) Sweet \index{Cyanotis@\textit{Cyanotis}!axillaris@\textit{axillaris}} 鞘苞花 \index{鞘苞花}  VU
  \end{itemize}
 \item[] \textit{Floscopa}\index{Floscopa@\textit{Floscopa}} 蔓襄荷屬
                                
  \begin{itemize}
        \item[] \textit{F. scandens} Lour. \index{Floscopa@\textit{Floscopa}!scandens@\textit{scandens}} 蔓蘘荷 \index{蔓蘘荷}  NT
  \end{itemize}
 \item[] \textit{Gibasis}\index{Gibasis@\textit{Gibasis}} 細梗鴨跖草屬
                                
  \begin{itemize}
        \item[] \textit{G. pellucida} (Martens \& Galeotti) D.R.Hunt \index{Gibasis@\textit{Gibasis}!pellucida@\textit{pellucida}} 細梗鴨跖草 \index{細梗鴨跖草}  NA
  \end{itemize}
 \item[] \textit{Murdannia}\index{Murdannia@\textit{Murdannia}} 水竹葉屬
                                
  \begin{itemize}
        \item[] \textit{M. edulis} (Stokes) Faden \index{Murdannia@\textit{Murdannia}!edulis@\textit{edulis}} 葶花水竹葉 \index{葶花水竹葉}  LC
        \item[] \textit{M. keisak} (Hassk.) Hand.-Mazz. \index{Murdannia@\textit{Murdannia}!keisak@\textit{keisak}} 水竹葉 \index{水竹葉}  LC
        \item[] \textit{M. loriformis} (Hassk.) R. S. Rao \& Kammathy \index{Murdannia@\textit{Murdannia}!loriformis@\textit{loriformis}} 牛軛草 \index{牛軛草}  LC
        \item[] \textit{M. spirata} (L.) Brückn. \index{Murdannia@\textit{Murdannia}!spirata@\textit{spirata}} 矮水竹葉 \index{矮水竹葉}  VU
  \end{itemize}
 \item[] \textit{Pollia}\index{Pollia@\textit{Pollia}} 杜若屬
                                
  \begin{itemize}
        \item[] \textit{P. japonica} Thunb. \index{Pollia@\textit{Pollia}!japonica@\textit{japonica}} 杜若 \index{杜若}  LC
        \item[] \textit{P. miranda} (H. Lév.) H. Hara \index{Pollia@\textit{Pollia}!miranda@\textit{miranda}} 小杜若 \index{小杜若}  LC
        \item[] \textit{P. secundiflora} (Blume) Bakh. f. \index{Pollia@\textit{Pollia}!secundiflora@\textit{secundiflora}} 叢林杜若 \index{叢林杜若}  LC
  \end{itemize}
 \item[] \textit{Rhopalephora}\index{Rhopalephora@\textit{Rhopalephora}} 毛果竹葉菜屬
                                
  \begin{itemize}
        \item[] \textit{R. scaberrima} (Blume) Faden \index{Rhopalephora@\textit{Rhopalephora}!scaberrima@\textit{scaberrima}} 毛果竹葉菜 \index{毛果竹葉菜}  LC
  \end{itemize}
 \item[] \textit{Tradescantia}\index{Tradescantia@\textit{Tradescantia}} 巴西水竹草屬
                                
  \begin{itemize}
        \item[] \textit{T. fluminensis} Vell. \index{Tradescantia@\textit{Tradescantia}!fluminensis@\textit{fluminensis}} 巴西水竹葉 \index{巴西水竹葉}  NA
        \item[] \textit{T. pallida} (Rose) D. R. Hunt \index{Tradescantia@\textit{Tradescantia}!pallida@\textit{pallida}} 紫錦草 \index{紫錦草}  NA
        \item[] \textit{T. zebrina} var. \textit{zebrina}  \index{Tradescantia@\textit{Tradescantia}!zebrina@\textit{zebrina}!var. zebrina@var. \textit{zebrina}} 吊竹草 \index{吊竹草}  NA
  \end{itemize}
  \end{itemize}
