
  \begin{itemize}
 \item[] \textit{Argyreia} 朝顏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argyreia+akoensis}{\textit{A. akoensis} S.Z.Yang, P.H.Chen \& G.W.Staples}  \index{Argyreia@\textit{Argyreia}!akoensis@\textbf{\textit{akoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東朝顏&T2_new_value=true&fr=y}}{屏東朝顏}\index{屏東朝顏@{\Song{屏東朝顏}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argyreia+formosana}{\textit{A. formosana} Ishigami ex T.Yamaz.}  \index{Argyreia@\textit{Argyreia}!formosana@\textbf{\textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍葉朝顏&T2_new_value=true&fr=y}}{鈍葉朝顏}\index{鈍葉朝顏@{\Song{鈍葉朝顏}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argyreia+nervosa}{\textit{A. nervosa} (Burm.f.) Boj.}  \index{Argyreia@\textit{Argyreia}!nervosa@\textit{nervosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=脈葉朝顏&T2_new_value=true&fr=y}}{脈葉朝顏}\index{脈葉朝顏} NA$^n$
  \end{itemize}
 \item[] \textit{Calystegia} 濱旋花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calystegia+soldanella}{\textit{C. soldanella} (L.) R.Br.}  \index{Calystegia@\textit{Calystegia}!soldanella@\textit{soldanella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱旋花&T2_new_value=true&fr=y}}{濱旋花}\index{濱旋花} NT
  \end{itemize}
 \item[] \textit{Cuscuta} 菟絲子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuscuta+australis}{\textit{C. australis} R.Br.}  \index{Cuscuta@\textit{Cuscuta}!australis@\textit{australis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菟絲子&T2_new_value=true&fr=y}}{菟絲子}\index{菟絲子} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuscuta+campestris}{\textit{C. campestris} Yunck.}  \index{Cuscuta@\textit{Cuscuta}!campestris@\textit{campestris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=平原菟絲子&T2_new_value=true&fr=y}}{平原菟絲子}\index{平原菟絲子} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuscuta+chinensis}{\textit{C. chinensis} Lam.}  \index{Cuscuta@\textit{Cuscuta}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中國菟絲子&T2_new_value=true&fr=y}}{中國菟絲子}\index{中國菟絲子@{\Song{中國菟絲子}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuscuta+japonica+var.+formosana}{\textit{C. japonica} Choisy var. \textit{formosana} (Hayata) Yunck.}  \index{Cuscuta@\textit{Cuscuta}!japonica@\textit{japonica}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣菟絲子&T2_new_value=true&fr=y}}{臺灣菟絲子}\index{臺灣菟絲子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuscuta+japonica+var.+japonica}{\textit{C. japonica} Choisy var. \textit{japonica}}  \index{Cuscuta@\textit{Cuscuta}!japonica@\textit{japonica}!var. japonica@var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本菟絲子&T2_new_value=true&fr=y}}{日本菟絲子}\index{日本菟絲子} DD
  \end{itemize}
 \item[] \textit{Dichondra} 馬蹄金屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dichondra+micrantha}{\textit{D. micrantha} Urb.}  \index{Dichondra@\textit{Dichondra}!micrantha@\textit{micrantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬蹄金&T2_new_value=true&fr=y}}{馬蹄金}\index{馬蹄金} LC
  \end{itemize}
 \item[] \textit{Erycibe} 伊立基藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erycibe+henryi}{\textit{E. henryi} Prain}  \index{Erycibe@\textit{Erycibe}!henryi@\textit{henryi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亨利氏伊立基藤&T2_new_value=true&fr=y}}{亨利氏伊立基藤}\index{亨利氏伊立基藤} LC
  \end{itemize}
 \item[] \textit{Evolvulus} 土丁桂屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Evolvulus+alsinoides}{\textit{E. alsinoides} (L.) L.}  \index{Evolvulus@\textit{Evolvulus}!alsinoides@\textit{alsinoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=土丁桂&T2_new_value=true&fr=y}}{土丁桂}\index{土丁桂} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Evolvulus+nummularius}{\textit{E. nummularius} (L.) L.}  \index{Evolvulus@\textit{Evolvulus}!nummularius@\textit{nummularius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短梗土丁桂&T2_new_value=true&fr=y}}{短梗土丁桂}\index{短梗土丁桂} NA$^n$
  \end{itemize}
 \item[] \textit{Hewittia} 吊鐘藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hewittia+malabarica}{\textit{H. malabarica} (L.) Suresh}  \index{Hewittia@\textit{Hewittia}!malabarica@\textit{malabarica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=吊鐘藤&T2_new_value=true&fr=y}}{吊鐘藤}\index{吊鐘藤} LC
  \end{itemize}
 \item[] \textit{Ipomoea} 牽牛花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+alba}{\textit{I. alba} L.}  \index{Ipomoea@\textit{Ipomoea}!alba@\textit{alba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天茄兒&T2_new_value=true&fr=y}}{天茄兒}\index{天茄兒} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+aquatica}{\textit{I. aquatica} Forssk.}  \index{Ipomoea@\textit{Ipomoea}!aquatica@\textit{aquatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=甕菜&T2_new_value=true&fr=y}}{甕菜}\index{甕菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+batatas}{\textit{I. batatas} (L.) Lam.}  \index{Ipomoea@\textit{Ipomoea}!batatas@\textit{batatas}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=甘薯&T2_new_value=true&fr=y}}{甘薯}\index{甘薯} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+biflora}{\textit{I. biflora} (L.) Persoon}  \index{Ipomoea@\textit{Ipomoea}!biflora@\textit{biflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花牽牛&T2_new_value=true&fr=y}}{白花牽牛}\index{白花牽牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+cairica}{\textit{I. cairica} (L.) Sweet}  \index{Ipomoea@\textit{Ipomoea}!cairica@\textit{cairica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=番仔藤&T2_new_value=true&fr=y}}{番仔藤}\index{番仔藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+carnea+subsp.+fistulosa}{\textit{I. carnea} Jacq. subsp. \textit{fistulosa} (Mart. ex Choisy) D.F.Austin}  \index{Ipomoea@\textit{Ipomoea}!carnea@\textit{carnea}!subsp. fistulosa@subsp. \textit{fistulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樹牽牛&T2_new_value=true&fr=y}}{樹牽牛}\index{樹牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+eriocarpa}{\textit{I. eriocarpa} R.Br.}  \index{Ipomoea@\textit{Ipomoea}!eriocarpa@\textit{eriocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果薯&T2_new_value=true&fr=y}}{毛果薯}\index{毛果薯} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+hederacea}{\textit{I. hederacea} (L.) Jacq.}  \index{Ipomoea@\textit{Ipomoea}!hederacea@\textit{hederacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=碗仔花&T2_new_value=true&fr=y}}{碗仔花}\index{碗仔花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+hederifolia}{\textit{I. hederifolia} L.}  \index{Ipomoea@\textit{Ipomoea}!hederifolia@\textit{hederifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=心葉蔦蘿&T2_new_value=true&fr=y}}{心葉蔦蘿}\index{心葉蔦蘿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+imperati}{\textit{I. imperati} (Vahl) Griseb.}  \index{Ipomoea@\textit{Ipomoea}!imperati@\textbf{\textit{imperati}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉牽牛&T2_new_value=true&fr=y}}{厚葉牽牛}\index{厚葉牽牛@{\Song{厚葉牽牛}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+indica}{\textit{I. indica} (Burm.f.) Merr.}  \index{Ipomoea@\textit{Ipomoea}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳葉牽牛&T2_new_value=true&fr=y}}{銳葉牽牛}\index{銳葉牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+littoralis}{\textit{I. littoralis} Blume}  \index{Ipomoea@\textit{Ipomoea}!littoralis@\textit{littoralis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海牽牛&T2_new_value=true&fr=y}}{海牽牛}\index{海牽牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+mauritiana}{\textit{I. mauritiana} Jacq.}  \index{Ipomoea@\textit{Ipomoea}!mauritiana@\textit{mauritiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉牽牛&T2_new_value=true&fr=y}}{掌葉牽牛}\index{掌葉牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+nil}{\textit{I. nil} (L.) Roth.}  \index{Ipomoea@\textit{Ipomoea}!nil@\textit{nil}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牽牛花&T2_new_value=true&fr=y}}{牽牛花}\index{牽牛花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+obscura}{\textit{I. obscura} (L.) Ker Gawl.}  \index{Ipomoea@\textit{Ipomoea}!obscura@\textit{obscura}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野牽牛&T2_new_value=true&fr=y}}{野牽牛}\index{野牽牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+pes-caprae+subsp.+brasiliensis}{\textit{I. pes-caprae} (L.) R.Br. subsp. \textit{brasiliensis} (L.) Oostst.}  \index{Ipomoea@\textit{Ipomoea}!pes-caprae@\textit{pes-caprae}!subsp. brasiliensis@subsp. \textit{brasiliensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬鞍藤&T2_new_value=true&fr=y}}{馬鞍藤}\index{馬鞍藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+pes-tigridis}{\textit{I. pes-tigridis} L.}  \index{Ipomoea@\textit{Ipomoea}!pes-tigridis@\textit{pes-tigridis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=九爪藤&T2_new_value=true&fr=y}}{九爪藤}\index{九爪藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+polymorpha}{\textit{I. polymorpha} Roem. \& Schult.}  \index{Ipomoea@\textit{Ipomoea}!polymorpha@\textbf{\textit{polymorpha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉立牽牛&T2_new_value=true&fr=y}}{變葉立牽牛}\index{變葉立牽牛@{\Song{變葉立牽牛}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+purpurea}{\textit{I. purpurea} (L.) Roth.}  \index{Ipomoea@\textit{Ipomoea}!purpurea@\textit{purpurea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花牽牛&T2_new_value=true&fr=y}}{紫花牽牛}\index{紫花牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+quamoclit}{\textit{I. quamoclit} L.}  \index{Ipomoea@\textit{Ipomoea}!quamoclit@\textit{quamoclit}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔦蘿&T2_new_value=true&fr=y}}{蔦蘿}\index{蔦蘿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+sumatrana}{\textit{I. sumatrana} (Blume) Oostst.}  \index{Ipomoea@\textit{Ipomoea}!sumatrana@\textbf{\textit{sumatrana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘇門答臘牽牛&T2_new_value=true&fr=y}}{蘇門答臘牽牛}\index{蘇門答臘牽牛@{\Song{蘇門答臘牽牛}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+trifida}{\textit{I. trifida} (Kunth) G.Don}  \index{Ipomoea@\textit{Ipomoea}!trifida@\textit{trifida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大星牽牛&T2_new_value=true&fr=y}}{大星牽牛}\index{大星牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+triloba}{\textit{I. triloba} L.}  \index{Ipomoea@\textit{Ipomoea}!triloba@\textit{triloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花野牽牛&T2_new_value=true&fr=y}}{紅花野牽牛}\index{紅花野牽牛} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+violacea}{\textit{I. violacea} L.}  \index{Ipomoea@\textit{Ipomoea}!violacea@\textit{violacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓萼天茄兒&T2_new_value=true&fr=y}}{圓萼天茄兒}\index{圓萼天茄兒} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ipomoea+wrightii}{\textit{I. wrightii} A.Gray}  \index{Ipomoea@\textit{Ipomoea}!wrightii@\textit{wrightii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=槭葉小牽牛&T2_new_value=true&fr=y}}{槭葉小牽牛}\index{槭葉小牽牛} NA$^n$
  \end{itemize}
 \item[] \textit{Jacquemontia} 娥房藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Jacquemontia+paniculata}{\textit{J. paniculata} (Burm.f.) Hallier f.}  \index{Jacquemontia@\textit{Jacquemontia}!paniculata@\textit{paniculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=娥房藤&T2_new_value=true&fr=y}}{娥房藤}\index{娥房藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Jacquemontia+polyantha}{\textit{J. polyantha} (Schltdl. \& Cham.) Hallier f.}  \index{Jacquemontia@\textit{Jacquemontia}!polyantha@\textit{polyantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多花娥房藤&T2_new_value=true&fr=y}}{多花娥房藤}\index{多花娥房藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Jacquemontia+tamnifolia}{\textit{J. tamnifolia} (L.) Griseb.}  \index{Jacquemontia@\textit{Jacquemontia}!tamnifolia@\textit{tamnifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長梗毛娥房藤&T2_new_value=true&fr=y}}{長梗毛娥房藤}\index{長梗毛娥房藤} NA$^n$
  \end{itemize}
 \item[] \textit{Lepistemon} 鮮蕊藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepistemon+binectariferum+var.+trichocarpum}{\textit{L. binectariferum} (Wall.) Kuntze var. \textit{trichocarpum} (Gagnep.) Ooststr.}  \index{Lepistemon@\textit{Lepistemon}!binectariferum@\textit{binectariferum}!var. trichocarpum@var. \textit{trichocarpum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鮮蕊藤&T2_new_value=true&fr=y}}{鮮蕊藤}\index{鮮蕊藤} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lepistemon+intermedius}{\textit{L. intermedius} Hallier f.}  \index{Lepistemon@\textit{Lepistemon}!intermedius@\textbf{\textit{intermedius}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光滑鮮蕊藤&T2_new_value=true&fr=y}}{光滑鮮蕊藤}\index{光滑鮮蕊藤@{\Song{光滑鮮蕊藤}}} CR
  \end{itemize}
 \item[] \textit{Merremia} 菜欒藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+cissoides}{\textit{M. cissoides} (Lam.) Hallier f.}  \index{Merremia@\textit{Merremia}!cissoides@\textit{cissoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓生菜欒藤&T2_new_value=true&fr=y}}{蔓生菜欒藤}\index{蔓生菜欒藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+gemella}{\textit{M. gemella} (Burm.f.) Hallier f.}  \index{Merremia@\textit{Merremia}!gemella@\textit{gemella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菜欒藤&T2_new_value=true&fr=y}}{菜欒藤}\index{菜欒藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+hederacea}{\textit{M. hederacea} (Burm.f.) Hallier f.}  \index{Merremia@\textit{Merremia}!hederacea@\textit{hederacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=卵葉菜欒藤&T2_new_value=true&fr=y}}{卵葉菜欒藤}\index{卵葉菜欒藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+hirta}{\textit{M. hirta} (L.) Merr.}  \index{Merremia@\textit{Merremia}!hirta@\textbf{\textit{hirta}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉姬旋花&T2_new_value=true&fr=y}}{變葉姬旋花}\index{變葉姬旋花@{\Song{變葉姬旋花}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+quinata}{\textit{M. quinata} (R.Br.) Oostst.}  \index{Merremia@\textit{Merremia}!quinata@\textit{quinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉姬旋花&T2_new_value=true&fr=y}}{掌葉姬旋花}\index{掌葉姬旋花} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+similis}{\textit{M. similis} Elmer}  \index{Merremia@\textit{Merremia}!similis@\textbf{\textit{similis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花姬旋花&T2_new_value=true&fr=y}}{紅花姬旋花}\index{紅花姬旋花@{\Song{紅花姬旋花}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+tuberosa}{\textit{M. tuberosa} (L.) Rendle}  \index{Merremia@\textit{Merremia}!tuberosa@\textit{tuberosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=姬旋花&T2_new_value=true&fr=y}}{姬旋花}\index{姬旋花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Merremia+vitifolia}{\textit{M. vitifolia} (Burm.f.) Hallier f.}  \index{Merremia@\textit{Merremia}!vitifolia@\textbf{\textit{vitifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉菜欒藤&T2_new_value=true&fr=y}}{掌葉菜欒藤}\index{掌葉菜欒藤@{\Song{掌葉菜欒藤}}} EN
  \end{itemize}
 \item[] \textit{Operculina} 盒果藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Operculina+turpethum}{\textit{O. turpethum} (L.) S.Manso}  \index{Operculina@\textit{Operculina}!turpethum@\textit{turpethum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=盒果藤&T2_new_value=true&fr=y}}{盒果藤}\index{盒果藤} LC
  \end{itemize}
 \item[] \textit{Stictocardia} 大萼旋花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stictocardia+tiliifolia}{\textit{S. tiliifolia} (Desr.) Hallier f.}  \index{Stictocardia@\textit{Stictocardia}!tiliifolia@\textit{tiliifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大萼旋花&T2_new_value=true&fr=y}}{大萼旋花}\index{大萼旋花} LC
  \end{itemize}
 \item[] \textit{Xenostegia} 戟葉菜欒藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Xenostegia+tridentata}{\textit{X. tridentata} (L.) D.F.Austin \& Staples}  \index{Xenostegia@\textit{Xenostegia}!tridentata@\textit{tridentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=戟葉菜欒藤&T2_new_value=true&fr=y}}{戟葉菜欒藤}\index{戟葉菜欒藤} LC
  \end{itemize}
  \end{itemize}
