
  \begin{itemize}
 \item[] \textit{Bryophyllum} 落地生根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bryophyllum+delagoense}{\textit{B. delagoense} (Eckl. \& Zeyh.) Druce}  \index{Bryophyllum@\textit{Bryophyllum}!delagoense@\textit{delagoense}} 洋吊鐘\index{洋吊鐘} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bryophyllum+pinnatum}{\textit{B. pinnatum} (Lam.) Kurz}  \index{Bryophyllum@\textit{Bryophyllum}!pinnatum@\textit{pinnatum}} 落地生根\index{落地生根} NA $^n$
  \end{itemize}
 \item[] \textit{Hylotelephium} 八寶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylotelephium+subcapitatum}{\textit{H. subcapitatum} (Hayata) H.Ohba}  \index{Hylotelephium@\textit{Hylotelephium}!subcapitatum@\textit{subcapitatum}} 穗花八寶\index{穗花八寶}\# LC
  \end{itemize}
 \item[] \textit{Kalanchoe} 燈籠草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kalanchoe+garambiensis}{\textit{K. garambiensis} Kudo}  \index{Kalanchoe@\textit{Kalanchoe}!garambiensis@\textit{garambiensis}} 鵝鑾鼻燈籠草\index{鵝鑾鼻燈籠草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kalanchoe+gracilis}{\textit{K. gracilis} Hance}  \index{Kalanchoe@\textit{Kalanchoe}!gracilis@\textit{gracilis}} 小燈籠草\index{小燈籠草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kalanchoe+spathulata}{\textit{K. spathulata} (Poir.) DC.}  \index{Kalanchoe@\textit{Kalanchoe}!spathulata@\textit{spathulata}} 倒吊蓮\index{倒吊蓮} LC
  \end{itemize}
 \item[] \textit{Sedum} 佛甲草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+actinocarpum}{\textit{S. actinocarpum} Yamam.}  \index{Sedum@\textit{Sedum}!actinocarpum@\textit{actinocarpum}} 星果佛甲草\index{星果佛甲草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+bulbiferum}{\textit{S. bulbiferum} Makino}  \index{Sedum@\textit{Sedum}!bulbiferum@\textit{bulbiferum}} 珠芽佛甲草\index{珠芽佛甲草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+cryptomerioides}{\textit{S. cryptomerioides} Bart. \& Yamam.}  \index{Sedum@\textit{Sedum}!cryptomerioides@\textit{cryptomerioides}} 杉葉佛甲草\index{杉葉佛甲草}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+drymarioides}{\textit{S. drymarioides} Hance}  \index{Sedum@\textit{Sedum}!drymarioides@\textit{drymarioides}} 大葉火焰草\index{大葉火焰草} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+emarginatum}{\textit{S. emarginatum} Migo}  \index{Sedum@\textit{Sedum}!emarginatum@\textit{emarginatum}} 凹葉景天\index{凹葉景天} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+erythrospermum}{\textit{S. erythrospermum} Hayata}  \index{Sedum@\textit{Sedum}!erythrospermum@\textit{erythrospermum}} 紅子佛甲草\index{紅子佛甲草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+formosanum}{\textit{S. formosanum} N.E.Br.}  \index{Sedum@\textit{Sedum}!formosanum@\textit{formosanum}} 臺灣佛甲草\index{臺灣佛甲草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+mexicanum}{\textit{S. mexicanum} Britt.}  \index{Sedum@\textit{Sedum}!mexicanum@\textit{mexicanum}} 松葉佛甲草\index{松葉佛甲草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+microsepalum}{\textit{S. microsepalum} Hayata}  \index{Sedum@\textit{Sedum}!microsepalum@\textit{microsepalum}} 小萼佛甲草\index{小萼佛甲草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+morrisonense}{\textit{S. morrisonense} Hayata}  \index{Sedum@\textit{Sedum}!morrisonense@\textit{morrisonense}} 玉山佛甲草\index{玉山佛甲草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+nokoense}{\textit{S. nokoense} Yamam.}  \index{Sedum@\textit{Sedum}!nokoense@\textit{nokoense}} 能高佛甲草\index{能高佛甲草}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+parvisepalum}{\textit{S. parvisepalum} Yamam.}  \index{Sedum@\textit{Sedum}!parvisepalum@\textit{parvisepalum}} 尖萼佛甲草\index{尖萼佛甲草}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+sarmentosum}{\textit{S. sarmentosum} Bunge}  \index{Sedum@\textit{Sedum}!sarmentosum@\textit{sarmentosum}} 垂盆草\index{垂盆草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+sekiteiense}{\textit{S. sekiteiense} Yamam.}  \index{Sedum@\textit{Sedum}!sekiteiense@\textit{sekiteiense}} 石碇佛甲草\index{石碇佛甲草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+stellariaefolium}{\textit{S. stellariaefolium} Franch.}  \index{Sedum@\textit{Sedum}!stellariaefolium@\textit{stellariaefolium}} 火焰草\index{火焰草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sedum+uniflorum}{\textit{S. uniflorum} Hook. \& Arn.}  \index{Sedum@\textit{Sedum}!uniflorum@\textit{uniflorum}} 疏花佛甲草\index{疏花佛甲草} NT
  \end{itemize}
  \end{itemize}
