
  \begin{itemize}
 \item[] \textit{Actinostemma}\index{Actinostemma@\textit{Actinostemma}} 合子草屬
                                
  \begin{itemize}
        \item[] \textit{A. tenerum} Griff. \index{Actinostemma@\textit{Actinostemma}!tenerum@\textit{tenerum}} 合子草 \index{合子草}  LC
  \end{itemize}
 \item[] \textit{Coccinia}\index{Coccinia@\textit{Coccinia}} 紅瓜屬
                                
  \begin{itemize}
        \item[] \textit{C. grandis} (L.) Voigt \index{Coccinia@\textit{Coccinia}!grandis@\textit{grandis}} 紅瓜 \index{紅瓜}  NA
  \end{itemize}
 \item[] \textit{Diplocyclos}\index{Diplocyclos@\textit{Diplocyclos}} 雙輪瓜屬
                                
  \begin{itemize}
        \item[] \textit{D. palmatus} (L.) C.Jeffrey \index{Diplocyclos@\textit{Diplocyclos}!palmatus@\textit{palmatus}} 雙輪瓜 \index{雙輪瓜}  LC
  \end{itemize}
 \item[] \textit{Gymnopetalum}\index{Gymnopetalum@\textit{Gymnopetalum}} 裸瓣瓜屬
                                
  \begin{itemize}
        \item[] \textit{G. chinense} (Lour.) Merr. \index{Gymnopetalum@\textit{Gymnopetalum}!chinense@\textit{chinense}} 裸瓣瓜 \index{裸瓣瓜}  LC
  \end{itemize}
 \item[] \textit{Gynostemma}\index{Gynostemma@\textit{Gynostemma}} 絞股藍屬
                                
  \begin{itemize}
        \item[] \textit{G. pentaphyllum} (Thunb.) Makino \index{Gynostemma@\textit{Gynostemma}!pentaphyllum@\textit{pentaphyllum}} 絞股藍 \index{絞股藍}  LC
  \end{itemize}
 \item[] \textit{Melothria}\index{Melothria@\textit{Melothria}} 垂瓜果屬
                                
  \begin{itemize}
        \item[] \textit{M. pendula} L. \index{Melothria@\textit{Melothria}!pendula@\textit{pendula}} 垂果瓜 \index{垂果瓜}  NA
  \end{itemize}
 \item[] \textit{Momordica}\index{Momordica@\textit{Momordica}} 苦瓜屬
                                
  \begin{itemize}
        \item[] \textit{M. charantia} L. \index{Momordica@\textit{Momordica}!charantia@\textit{charantia}} 苦瓜 \index{苦瓜}  NA
        \item[] \textit{M. cochinchinensis} (Lour.) Spreng. \index{Momordica@\textit{Momordica}!cochinchinensis@\textit{cochinchinensis}} 木虌子 \index{木虌子}  LC
  \end{itemize}
 \item[] \textit{Mukia}\index{Mukia@\textit{Mukia}} 紅紐子屬
                                
  \begin{itemize}
        \item[] \textit{M. maderaspatana} (L.) M.J.Roem. \index{Mukia@\textit{Mukia}!maderaspatana@\textit{maderaspatana}} 天花 \index{天花}  LC
  \end{itemize}
 \item[] \textit{Neoalsomitra}\index{Neoalsomitra@\textit{Neoalsomitra}} 穿山龍屬
                                
  \begin{itemize}
        \item[] \textit{N. integrifolia} (Cogn.) Hutch. \index{Neoalsomitra@\textit{Neoalsomitra}!integrifolia@\textit{integrifolia}} 穿山龍 \index{穿山龍}  LC
  \end{itemize}
 \item[] \textit{Sechium}\index{Sechium@\textit{Sechium}} 佛手瓜屬
                                
  \begin{itemize}
        \item[] \textit{S. edule} (Jacq.) Sw. \index{Sechium@\textit{Sechium}!edule@\textit{edule}} 佛手瓜 \index{佛手瓜}  NA
  \end{itemize}
 \item[] \textit{Sicyos}\index{Sicyos@\textit{Sicyos}} 刺果瓜屬
                                
  \begin{itemize}
        \item[] \textit{S. angulatus} L. \index{Sicyos@\textit{Sicyos}!angulatus@\textit{angulatus}} 刺果瓜 \index{刺果瓜}  NA
  \end{itemize}
 \item[] \textit{Siraitia}\index{Siraitia@\textit{Siraitia}} 羅漢果屬
                                
  \begin{itemize}
        \item[] \textit{S. taiwaniana} (Hayata) C.Jeffrey ex A.M.Lu \& Z.Y.Zhang \index{Siraitia@\textit{Siraitia}!taiwaniana@\textit{taiwaniana}} 臺灣羅漢果 \index{臺灣羅漢果} \# VU
  \end{itemize}
 \item[] \textit{Solena}\index{Solena@\textit{Solena}} 茅瓜屬
                                
  \begin{itemize}
        \item[] \textit{S. amplexicaulis} (Lam.) Gandhi \index{Solena@\textit{Solena}!amplexicaulis@\textit{amplexicaulis}} 茅瓜 \index{茅瓜}  LC
  \end{itemize}
 \item[] \textit{Thladiantha}\index{Thladiantha@\textit{Thladiantha}} 青牛膽屬
                                
  \begin{itemize}
        \item[] \textit{T. nudiflora} Hemsl. ex Forbes \& Hemsl. \index{Thladiantha@\textit{Thladiantha}!nudiflora@\textit{nudiflora}} 青牛膽 \index{青牛膽}  LC
        \item[] \textit{T. punctata} Hayata \index{Thladiantha@\textit{Thladiantha}!punctata@\textit{punctata}} 斑花青牛膽 \index{斑花青牛膽}  LC
  \end{itemize}
 \item[] \textit{Trichosanthes}\index{Trichosanthes@\textit{Trichosanthes}} 括樓屬
                                
  \begin{itemize}
        \item[] \textit{T. cucumeroides} (Ser.) Maxim. ex Franch. \& Sav. \index{Trichosanthes@\textit{Trichosanthes}!cucumeroides@\textit{cucumeroides}} 王瓜 \index{王瓜}  LC
        \item[] \textit{T. homophylla} Hayata \index{Trichosanthes@\textit{Trichosanthes}!homophylla@\textit{homophylla}} 芋葉括樓 \index{芋葉括樓} \# LC
        \item[] \textit{T. laceribracteata} Hayata \index{Trichosanthes@\textit{Trichosanthes}!laceribracteata@\textit{laceribracteata}} 槭葉括樓 \index{槭葉括樓}  LC
        \item[] \textit{T. ovigera} Blume \index{Trichosanthes@\textit{Trichosanthes}!ovigera@\textit{ovigera}} 全緣括樓 \index{全緣括樓}  LC
        \item[] \textit{T. quinquangulata} A.Gray \index{Trichosanthes@\textit{Trichosanthes}!quinquangulata@\textit{quinquangulata}} 蘭嶼括樓 \index{蘭嶼括樓}  VU
        \item[] \textit{T. rosthornii} Harms \index{Trichosanthes@\textit{Trichosanthes}!rosthornii@\textit{rosthornii}} 中華括樓 \index{中華括樓}  LC
  \end{itemize}
 \item[] \textit{Zehneria}\index{Zehneria@\textit{Zehneria}} 馬㼎兒屬
                                
  \begin{itemize}
        \item[] \textit{Z. japonica} (Thunb.) H.Y.Liu \index{Zehneria@\textit{Zehneria}!japonica@\textit{japonica}} 馬瓝兒 \index{馬瓝兒}  LC
        \item[] \textit{Z. mucronata} (Blume) Miq. \index{Zehneria@\textit{Zehneria}!mucronata@\textit{mucronata}} 黑果馬瓝兒 \index{黑果馬瓝兒}  LC
  \end{itemize}
  \end{itemize}
