
  \begin{itemize}
 \item[] \textit{Calocedrus} 肖楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calocedrus+macrolepis+var.+formosana}{\textit{C. macrolepis} Kurz var. \textit{formosana} (Florin) W.C.Cheng \& L.K.Fu}  \index{Calocedrus@\textit{Calocedrus}!macrolepis@\textit{macrolepis}!var. formosana@var. \textit{formosana}} 臺灣肖楠\index{臺灣肖楠}\# VU
  \end{itemize}
 \item[] \textit{Chamaecyparis} 扁柏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecyparis+formosensis}{\textit{C. formosensis} Mastum.}  \index{Chamaecyparis@\textit{Chamaecyparis}!formosensis@\textit{formosensis}} 紅檜\index{紅檜}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecyparis+obtusa+var.+formosana}{\textit{C. obtusa} Siebold \& Zucc. var. \textit{formosana} (Hayata) Rehder}  \index{Chamaecyparis@\textit{Chamaecyparis}!obtusa@\textit{obtusa}!var. formosana@var. \textit{formosana}} 臺灣扁柏\index{臺灣扁柏}\# NT
  \end{itemize}
 \item[] \textit{Cunninghamia} 杉木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cunninghamia+konishii}{\textit{C. konishii} Hayata}  \index{Cunninghamia@\textit{Cunninghamia}!konishii@\textit{konishii}} 巒大杉\index{巒大杉}\# VU
  \end{itemize}
 \item[] \textit{Juniperus} 刺柏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Juniperus+chinensis+var.+taiwanensis}{\textit{J. chinensis} L. var. \textit{taiwanensis} R.P.Adams \& C.F.Hsieh}  \index{Juniperus@\textit{Juniperus}!chinensis@\textit{chinensis}!var. taiwanensis@var. \textit{taiwanensis}} 清水圓柏\index{清水圓柏}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Juniperus+formosana+var.+concolor}{\textit{J. formosana} Hayata var. \textit{concolor} Hayata}  \index{Juniperus@\textit{Juniperus}!formosana@\textit{formosana}!var. concolor@var. \textit{concolor}} 綠背刺柏\index{綠背刺柏}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Juniperus+formosana+var.+formosana}{\textit{J. formosana} Hayata var. \textit{formosana}}  \index{Juniperus@\textit{Juniperus}!formosana@\textit{formosana}!var. formosana@var. \textit{formosana}} 刺柏\index{刺柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Juniperus+squamata}{\textit{J. squamata} Buch.-Ham. ex Lamb.}  \index{Juniperus@\textit{Juniperus}!squamata@\textit{squamata}} 香青\index{香青} LC
  \end{itemize}
 \item[] \textit{Taiwania} 臺灣杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taiwania+cryptomerioides}{\textit{T. cryptomerioides} Hayata}  \index{Taiwania@\textit{Taiwania}!cryptomerioides@\textit{cryptomerioides}} 臺灣杉\index{臺灣杉}\# EN
  \end{itemize}
  \end{itemize}
