
  \begin{itemize}
 \item[] \textit{Actinoscirpus} 大藨草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Actinoscirpus+grossus}{\textit{A. grossus} (L.f.) Goetgh. \& D.A.Simpson}  \index{Actinoscirpus@\textit{Actinoscirpus}!grossus@\textit{grossus}} 大藨草\index{大藨草} RE
  \end{itemize}
 \item[] \textit{Bolboschoenus} 塊莖藨草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolboschoenus+maritimus+subsp.+affinis}{\textit{B. maritimus} (L.) Palla subsp. \textit{affinis} (Roth) T.Koyama}  \index{Bolboschoenus@\textit{Bolboschoenus}!maritimus@\textit{maritimus}!subsp. affinis@subsp. \textit{affinis}} 多穗藨草\index{多穗藨草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolboschoenus+planiculmis}{\textit{B. planiculmis} (F.Schmidt) T.V.Egorova}  \index{Bolboschoenus@\textit{Bolboschoenus}!planiculmis@\textit{planiculmis}} 扁稈藨草\index{扁稈藨草} EN
  \end{itemize}
 \item[] \textit{Bulbostylis} 球柱草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbostylis+barbata}{\textit{B. barbata} (Rottb.) C.B.Clarke}  \index{Bulbostylis@\textit{Bulbostylis}!barbata@\textit{barbata}} 毛球柱草\index{毛球柱草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbostylis+densa}{\textit{B. densa} (Wall.) Hand.-Mazz.}  \index{Bulbostylis@\textit{Bulbostylis}!densa@\textit{densa}} 球柱草\index{球柱草} LC
  \end{itemize}
 \item[] \textit{Carex} 薹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+alliiformis}{\textit{C. alliiformis} C.B.Clarke}  \index{Carex@\textit{Carex}!alliiformis@\textit{alliiformis}} 林下薹\index{林下薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+alopecuroides}{\textit{C. alopecuroides} D.Don ex Tilloch \& Taylor}  \index{Carex@\textit{Carex}!alopecuroides@\textit{alopecuroides}} 高山日本薹\index{高山日本薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+alterniflora}{\textit{C. alterniflora} Franch.}  \index{Carex@\textit{Carex}!alterniflora@\textit{alterniflora}} 宜蘭宿柱薹\index{宜蘭宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+arisanensis}{\textit{C. arisanensis} Hayata}  \index{Carex@\textit{Carex}!arisanensis@\textit{arisanensis}} 阿里山疏花薹\index{阿里山疏花薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+atrata}{\textit{C. atrata} L.}  \index{Carex@\textit{Carex}!atrata@\textit{atrata}} 南湖扁果薹\index{南湖扁果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+baccans}{\textit{C. baccans} Nees}  \index{Carex@\textit{Carex}!baccans@\textit{baccans}} 紅果薹\index{紅果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+bilateralis}{\textit{C. bilateralis} Hayata}  \index{Carex@\textit{Carex}!bilateralis@\textit{bilateralis}} 短葉二柱薹\index{短葉二柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+brachyanthera}{\textit{C. brachyanthera} Ohwi}  \index{Carex@\textit{Carex}!brachyanthera@\textit{brachyanthera}} 垂穗薹\index{垂穗薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+breviculmis}{\textit{C. breviculmis} R.Br.}  \index{Carex@\textit{Carex}!breviculmis@\textit{breviculmis}} 短莖宿柱薹\index{短莖宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+brevicuspis}{\textit{C. brevicuspis} C.B.Clarke}  \index{Carex@\textit{Carex}!brevicuspis@\textit{brevicuspis}} 大山宿柱薹\index{大山宿柱薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+breviscapa}{\textit{C. breviscapa} C.B.Clarke}  \index{Carex@\textit{Carex}!breviscapa@\textit{breviscapa}} 寬果宿柱薹\index{寬果宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+brownii}{\textit{C. brownii} Turkerman}  \index{Carex@\textit{Carex}!brownii@\textit{brownii}} 布朗薹\index{布朗薹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+brunnea}{\textit{C. brunnea} Thunb.}  \index{Carex@\textit{Carex}!brunnea@\textit{brunnea}} 束草\index{束草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+capillacea}{\textit{C. capillacea} Boott}  \index{Carex@\textit{Carex}!capillacea@\textit{capillacea}} 單穗薹\index{單穗薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+chrysolepis}{\textit{C. chrysolepis} Franch. \& Sav.}  \index{Carex@\textit{Carex}!chrysolepis@\textit{chrysolepis}} 黃花薹\index{黃花薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+cruciata}{\textit{C. cruciata} Wahl.}  \index{Carex@\textit{Carex}!cruciata@\textit{cruciata}} 煙火薹\index{煙火薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+cryptostachys}{\textit{C. cryptostachys} Brongn.}  \index{Carex@\textit{Carex}!cryptostachys@\textit{cryptostachys}} 多序宿柱薹\index{多序宿柱薹} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+daibuensis}{\textit{C. daibuensis} Hayata}  \index{Carex@\textit{Carex}!daibuensis@\textit{daibuensis}}  \index{Crex@\textit{Crex}!transalpina@\textit{transalpina}{\\\noindent(= \textit{Carex daibuensis})}} 大武宿柱薹\index{大武宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+daxinensis}{\textit{C. daxinensis} Y.Y.Zhou \& X.F.Jin}  \index{Carex@\textit{Carex}!daxinensis@\textit{daxinensis}} 恆春薹\index{恆春薹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+dimorpholepis}{\textit{C. dimorpholepis} Steud.}  \index{Carex@\textit{Carex}!dimorpholepis@\textit{dimorpholepis}} 二型鱗薹\index{二型鱗薹} NA $^v$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+dolichostachya}{\textit{C. dolichostachya} Hayata}  \index{Carex@\textit{Carex}!dolichostachya@\textit{dolichostachya}} 長穗宿柱薹\index{長穗宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+doniana}{\textit{C. doniana} Spreng.}  \index{Carex@\textit{Carex}!doniana@\textit{doniana}} 大穗日本薹\index{大穗日本薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+echinata}{\textit{C. echinata} Murray}  \index{Carex@\textit{Carex}!echinata@\textit{echinata}} 刺苞薹\index{刺苞薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+fernaldiana}{\textit{C. fernaldiana} H.Lév. \& Vaniot}  \index{Carex@\textit{Carex}!fernaldiana@\textit{fernaldiana}} 線葉宿柱薹\index{線葉宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+filicina}{\textit{C. filicina} Nees}  \index{Carex@\textit{Carex}!filicina@\textit{filicina}} 紅鞘薹\index{紅鞘薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+finitima}{\textit{C. finitima} Boott}  \index{Carex@\textit{Carex}!finitima@\textit{finitima}} 長柱薹\index{長柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+formosensis}{\textit{C. formosensis} H.Lév. \& Vaniot}  \index{Carex@\textit{Carex}!formosensis@\textit{formosensis}} 寶島宿柱薹\index{寶島宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+fulvorubescens}{\textit{C. fulvorubescens} Hayata}  \index{Carex@\textit{Carex}!fulvorubescens@\textit{fulvorubescens}} 茶色扁果薹\index{茶色扁果薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+gentilis+var.+nakaharae}{\textit{C. gentilis} Franch. var. \textit{nakaharae} (Hayata) T.Koyama}  \index{Carex@\textit{Carex}!gentilis@\textit{gentilis}!var. nakaharae@var. \textit{nakaharae}} 中原氏二柱薹\index{中原氏二柱薹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+grallatoria+var.+heteroclita}{\textit{C. grallatoria} Maxim. var. \textit{heteroclita} (Franch.) Kuk.}  \index{Carex@\textit{Carex}!grallatoria@\textit{grallatoria}!var. heteroclita@var. \textit{heteroclita}} 異型菱果薹\index{異型菱果薹} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+hoozanensis}{\textit{C. hoozanensis} Hayata}  \index{Carex@\textit{Carex}!hoozanensis@\textit{hoozanensis}} 鳳凰宿柱薹\index{鳳凰宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+jisaburo-ohwiana}{\textit{C. jisaburo-ohwiana} T.Koyama}  \index{Carex@\textit{Carex}!jisaburo-ohwiana@\textit{jisaburo-ohwiana}}  \index{Carex@\textit{Carex}!caucasica@\textit{caucasica}{\\\noindent(= \textit{Carex jisaburo-ohwiana})}} 大井氏扁果薹\index{大井氏扁果薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+kiotensis}{\textit{C. kiotensis} Franch. \& Sav.}  \index{Carex@\textit{Carex}!kiotensis@\textit{kiotensis}} 班囊果薹\index{班囊果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+kobomugi}{\textit{C. kobomugi} Ohwi}  \index{Carex@\textit{Carex}!kobomugi@\textit{kobomugi}} 海米\index{海米} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+laticeps}{\textit{C. laticeps} C.B.Clarke ex Franch.}  \index{Carex@\textit{Carex}!laticeps@\textit{laticeps}} 彎喙薹\index{彎喙薹} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+ligulata}{\textit{C. ligulata} Nees}  \index{Carex@\textit{Carex}!ligulata@\textit{ligulata}} 具舌薹\index{具舌薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+liui}{\textit{C. liui} T.Koyama and T.I.Chuang}  \index{Carex@\textit{Carex}!liui@\textit{liui}} 劉氏薹\index{劉氏薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+longistipes}{\textit{C. longistipes} Hayata}  \index{Carex@\textit{Carex}!longistipes@\textit{longistipes}} 長梗扁果薹\index{長梗扁果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+macrandrolepis}{\textit{C. macrandrolepis} H.Lév.}  \index{Carex@\textit{Carex}!macrandrolepis@\textit{macrandrolepis}} 和平菱果薹\index{和平菱果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+maculata}{\textit{C. maculata} Boott}  \index{Carex@\textit{Carex}!maculata@\textit{maculata}} 寬囊果薹\index{寬囊果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+makinoensis}{\textit{C. makinoensis} Franch.}  \index{Carex@\textit{Carex}!makinoensis@\textit{makinoensis}} 牧野氏薹\index{牧野氏薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+manca+subsp.+takasagoana}{\textit{C. manca} Boott subsp. \textit{takasagoana} (Akiyama) T.Koyama}  \index{Carex@\textit{Carex}!manca@\textit{manca}!subsp. takasagoana@subsp. \textit{takasagoana}} 夢佳宿柱薹\index{夢佳宿柱薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+metallica}{\textit{C. metallica} H.Lév.}  \index{Carex@\textit{Carex}!metallica@\textit{metallica}} 寬穗薹\index{寬穗薹} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+mitrata+var.+aristata}{\textit{C. mitrata} Franch. var. \textit{aristata} Ohwi}  \index{Carex@\textit{Carex}!mitrata@\textit{mitrata}!var. aristata@var. \textit{aristata}} 具芒宿柱薹\index{具芒宿柱薹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+mollicula}{\textit{C. mollicula} Boott}  \index{Carex@\textit{Carex}!mollicula@\textit{mollicula}} 柔果薹\index{柔果薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+morii}{\textit{C. morii} Hayata}  \index{Carex@\textit{Carex}!morii@\textit{morii}} 森氏薹\index{森氏薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+morrisonicola}{\textit{C. morrisonicola} Hayata}  \index{Carex@\textit{Carex}!morrisonicola@\textit{morrisonicola}} 玉山宿柱薹\index{玉山宿柱薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+nemostachys}{\textit{C. nemostachys} Steud.}  \index{Carex@\textit{Carex}!nemostachys@\textit{nemostachys}} 毛囊果薹\index{毛囊果薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+nubigena}{\textit{C. nubigena} D.Don ex Tilloch \& Taylor}  \index{Carex@\textit{Carex}!nubigena@\textit{nubigena}} 聚生穗序薹\index{聚生穗序薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+orthostemon}{\textit{C. orthostemon} Hayata}  \index{Carex@\textit{Carex}!orthostemon@\textit{orthostemon}} 直蕊宿柱薹\index{直蕊宿柱薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+oxyandra}{\textit{C. oxyandra} (Franch. \& Sav.) Kudo}  \index{Carex@\textit{Carex}!oxyandra@\textit{oxyandra}} 南投薹\index{南投薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+perakensis}{\textit{C. perakensis} C.B.Clarke}  \index{Carex@\textit{Carex}!perakensis@\textit{perakensis}} 黃穗薹\index{黃穗薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+phacota}{\textit{C. phacota} Spreng.}  \index{Carex@\textit{Carex}!phacota@\textit{phacota}} 七星班囊果薹\index{七星班囊果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+pumila}{\textit{C. pumila} Thunb.}  \index{Carex@\textit{Carex}!pumila@\textit{pumila}} 小海米\index{小海米} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+purpureotincta}{\textit{C. purpureotincta} Ohwi}  \index{Carex@\textit{Carex}!purpureotincta@\textit{purpureotincta}} 太魯閣薹\index{太魯閣薹}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+rafflesiana}{\textit{C. rafflesiana} Boott}  \index{Carex@\textit{Carex}!rafflesiana@\textit{rafflesiana}} 紅頭薹\index{紅頭薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+rhynchachaenium}{\textit{C. rhynchachaenium} C.B.Clarke ex Merr.}  \index{Carex@\textit{Carex}!rhynchachaenium@\textit{rhynchachaenium}} 初島氏宿柱薹\index{初島氏宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+rochebrunei}{\textit{C. rochebrunei} Franch. \& Sav.}  \index{Carex@\textit{Carex}!rochebrunei@\textit{rochebrunei}} 高山穗序薹\index{高山穗序薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+satzumensis}{\textit{C. satzumensis} Franch. \& Sav.}  \index{Carex@\textit{Carex}!satzumensis@\textit{satzumensis}} 油薹\index{油薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+scabrifolia}{\textit{C. scabrifolia} Steud.}  \index{Carex@\textit{Carex}!scabrifolia@\textit{scabrifolia}} 鹼簣\index{鹼簣} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+scaposa}{\textit{C. scaposa} C.B.Clarke}  \index{Carex@\textit{Carex}!scaposa@\textit{scaposa}} 花葶薹草\index{花葶薹草} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+sclerocarpa}{\textit{C. sclerocarpa} Franch.}  \index{Carex@\textit{Carex}!sclerocarpa@\textit{sclerocarpa}} 太平山薹\index{太平山薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+sociata}{\textit{C. sociata} Boott}  \index{Carex@\textit{Carex}!sociata@\textit{sociata}} 中國宿柱薹\index{中國宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+subfilicinoides}{\textit{C. subfilicinoides} Kük.}  \index{Carex@\textit{Carex}!subfilicinoides@\textit{subfilicinoides}} 亞紅鞘薹\index{亞紅鞘薹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+taihokuensis}{\textit{C. taihokuensis} Hayata}  \index{Carex@\textit{Carex}!taihokuensis@\textit{taihokuensis}} 銳果薹\index{銳果薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+taiwanensis}{\textit{C. taiwanensis} (Ohwi) Akiyama}  \index{Carex@\textit{Carex}!taiwanensis@\textit{taiwanensis}} 臺灣疏花薹\index{臺灣疏花薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+tristachya+var.+pocilliformis}{\textit{C. tristachya} Thunb. var. \textit{pocilliformis} (Boott) Kük.}  \index{Carex@\textit{Carex}!tristachya@\textit{tristachya}!var. pocilliformis@var. \textit{pocilliformis}} 抱鱗宿柱薹\index{抱鱗宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+truncatigluma}{\textit{C. truncatigluma} C.B.Clarke}  \index{Carex@\textit{Carex}!truncatigluma@\textit{truncatigluma}}  \index{Carex@\textit{Carex}!gracilispica@\textit{gracilispica}{\\\noindent(= \textit{Carex truncatigluma})}} 細穗宿柱薹\index{細穗宿柱薹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+tsushimensis}{\textit{C. tsushimensis} (Ohwi) Ohwi}  \index{Carex@\textit{Carex}!tsushimensis@\textit{tsushimensis}} 長芒宿柱薹\index{長芒宿柱薹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+urelytra}{\textit{C. urelytra} Ohwi}  \index{Carex@\textit{Carex}!urelytra@\textit{urelytra}} 扁果薹\index{扁果薹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Carex+wahuensis}{\textit{C. wahuensis} C.A.Mey.}  \index{Carex@\textit{Carex}!wahuensis@\textit{wahuensis}} 布氏宿柱薹\index{布氏宿柱薹} LC
  \end{itemize}
 \item[] \textit{Cladium} 克拉莎屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cladium+jamaicense}{\textit{C. jamaicense} Crantz}  \index{Cladium@\textit{Cladium}!jamaicense@\textit{jamaicense}} 克拉莎\index{克拉莎} EN
  \end{itemize}
 \item[] \textit{Cyperus} 莎草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+albescens}{\textit{C. albescens} (Steud.) Larridon \& Govaerts}  \index{Cyperus@\textit{Cyperus}!albescens@\textit{albescens}}  \index{Lipocarpha@\textit{Lipocarpha}!chinensis@\textit{chinensis}{\\\noindent(= \textit{Cyperus albescens})}} 華湖瓜草\index{華湖瓜草} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+alternifolius}{\textit{C. alternifolius} L.}  \index{Cyperus@\textit{Cyperus}!alternifolius@\textit{alternifolius}} 光桿輪傘莎草\index{光桿輪傘莎草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+amuricus}{\textit{C. amuricus} Maxim.}  \index{Cyperus@\textit{Cyperus}!amuricus@\textit{amuricus}} 阿穆爾莎草\index{阿穆爾莎草} NA $^v$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+aromaticus}{\textit{C. aromaticus} (Ridl.) Mattf. \& Kuek.}  \index{Cyperus@\textit{Cyperus}!aromaticus@\textit{aromaticus}}  \index{Kyllinga@\textit{Kyllinga}!polyphylla@\textit{polyphylla}{\\\noindent(= \textit{Cyperus aromaticus})}} 多葉水蜈蚣\index{多葉水蜈蚣} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+brevifolius}{\textit{C. brevifolius} (Rottb.) Endl. ex Hassk.}  \index{Cyperus@\textit{Cyperus}!brevifolius@\textit{brevifolius}}  \index{Kyllinga@\textit{Kyllinga}!brevifolius@\textit{brevifolius}{\\\noindent(= \textit{Cyperus brevifolius})}} 短葉水蜈蚣\index{短葉水蜈蚣} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+compactus}{\textit{C. compactus} Retz.}  \index{Cyperus@\textit{Cyperus}!compactus@\textit{compactus}}  \index{Cyperus@\textit{Cyperus}!compactus@\textit{compactus}{\\\noindent(= \textit{Cyperus compactus})}} 密穗磚子苗\index{密穗磚子苗} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+compressus}{\textit{C. compressus} L.}  \index{Cyperus@\textit{Cyperus}!compressus@\textit{compressus}} 沙田草\index{沙田草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+cuspidatus}{\textit{C. cuspidatus} Kunth}  \index{Cyperus@\textit{Cyperus}!cuspidatus@\textit{cuspidatus}} 長尖莎草\index{長尖莎草} NA $^v$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+cylindrocephalus}{\textit{C. cylindrocephalus} T.C.Hsu}  \index{Cyperus@\textit{Cyperus}!cylindrocephalus@\textit{cylindrocephalus}}  \index{Kyllinga@\textit{Kyllinga}!sesquiflora@\textit{sesquiflora}!subsp. cylindrica@subsp. \textit{cylindrica}{\\\noindent(=\textit{Cyperus cylindrocephalus})}} 圓筒穗水蜈蚣\index{圓筒穗水蜈蚣} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+cyperinus}{\textit{C. cyperinus} (Retz.) Valck.Sur.}  \index{Cyperus@\textit{Cyperus}!cyperinus@\textit{cyperinus}}  \index{Mariscus@\textit{Mariscus}!cyperinus@\textit{cyperinus}{\\\noindent(= \textit{Cyperus cyperinus})}} 莎草磚子苗\index{莎草磚子苗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+difformis}{\textit{C. difformis} L.}  \index{Cyperus@\textit{Cyperus}!difformis@\textit{difformis}} 異花莎草\index{異花莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+diffusus}{\textit{C. diffusus} Vahl}  \index{Cyperus@\textit{Cyperus}!diffusus@\textit{diffusus}} 多脈莎草\index{多脈莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+digitatus}{\textit{C. digitatus} Roxb.}  \index{Cyperus@\textit{Cyperus}!digitatus@\textit{digitatus}} 恆春莎草\index{恆春莎草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+distans}{\textit{C. distans} L.f.}  \index{Cyperus@\textit{Cyperus}!distans@\textit{distans}} 疏穗莎草\index{疏穗莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+eragrostis}{\textit{C. eragrostis} Lam.}  \index{Cyperus@\textit{Cyperus}!eragrostis@\textit{eragrostis}} 頭穗莎草\index{頭穗莎草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+esculentus}{\textit{C. esculentus} L.}  \index{Cyperus@\textit{Cyperus}!esculentus@\textit{esculentus}} 黃土香\index{黃土香} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+exaltatus}{\textit{C. exaltatus} Retz.}  \index{Cyperus@\textit{Cyperus}!exaltatus@\textit{exaltatus}} 無翅莎草\index{無翅莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+haspan}{\textit{C. haspan} L.}  \index{Cyperus@\textit{Cyperus}!haspan@\textit{haspan}} 畦畔莎草\index{畦畔莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+imbricatus+subsp.+elongatus}{\textit{C. imbricatus} Retz. subsp. \textit{elongatus} (Bockeler) T.Koyama}  \index{Cyperus@\textit{Cyperus}!imbricatus@\textit{imbricatus}!subsp. elongatus@subsp. \textit{elongatus}} 士林莎草\index{士林莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+imbricatus+subsp.+imbricatus}{\textit{C. imbricatus} Retz. subsp. \textit{imbricatus}}  \index{Cyperus@\textit{Cyperus}!imbricatus@\textit{imbricatus}!subsp. imbricatus@subsp. \textit{imbricatus}} 覆瓦狀莎草\index{覆瓦狀莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+involucratus}{\textit{C. involucratus} Rottb.}  \index{Cyperus@\textit{Cyperus}!involucratus@\textit{involucratus}}  \index{Cyperus@\textit{Cyperus}!alternifolius@\textit{alternifolius}!subsp. flabelliformis@subsp. \textit{flabelliformis}{\\\noindent(=\textit{Cyperus involucratus})}} 輪傘莎草(風車草) \index{輪傘莎草} \index{風車草@{風車草(=輪傘莎草)}} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+iria}{\textit{C. iria} L.}  \index{Cyperus@\textit{Cyperus}!iria@\textit{iria}} 碎米莎草\index{碎米莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+javanicus}{\textit{C. javanicus} Houtt.}  \index{Cyperus@\textit{Cyperus}!javanicus@\textit{javanicus}}  \index{Mariscus@\textit{Mariscus}!javanicus@\textit{javanicus}{\\\noindent(= \textit{Cyperus javanicus})}} 羽狀穗磚子苗\index{羽狀穗磚子苗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+leptocarpus}{\textit{C. leptocarpus} (F.Muell.) Bauters}  \index{Cyperus@\textit{Cyperus}!leptocarpus@\textit{leptocarpus}}  \index{Lipocarpha@\textit{Lipocarpha}!microcephala@\textit{microcephala}{\\\noindent(= \textit{Cyperus leptocarpus})}} 銀穗湖瓜草\index{銀穗湖瓜草} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+malaccensis+subsp.+malaccensis}{\textit{C. malaccensis} Lam. subsp. \textit{malaccensis}}  \index{Cyperus@\textit{Cyperus}!malaccensis@\textit{malaccensis}!subsp. malaccensis@subsp. \textit{malaccensis}} 茳茳鹹草\index{茳茳鹹草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+malaccensis+subsp.+monophyllus}{\textit{C. malaccensis} Lam. subsp. \textit{monophyllus} (Vahl) T.Koyama}  \index{Cyperus@\textit{Cyperus}!malaccensis@\textit{malaccensis}!subsp. monophyllus@subsp. \textit{monophyllus}} 單葉鹹草\index{單葉鹹草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+michelianus}{\textit{C. michelianus} (L.) Link}  \index{Cyperus@\textit{Cyperus}!michelianus@\textit{michelianus}} 旋鱗莎草\index{旋鱗莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+mindorensis}{\textit{C. mindorensis} (Steud.) Huygh.}  \index{Cyperus@\textit{Cyperus}!mindorensis@\textit{mindorensis}}  \index{Kyllinga@\textit{Kyllinga}!nemoralis@\textit{nemoralis}{\\\noindent(= \textit{Cyperus mindorensis})}} 單穗水蜈蚣\index{單穗水蜈蚣} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+nipponicus}{\textit{C. nipponicus} Franch. \& Sav.}  \index{Cyperus@\textit{Cyperus}!nipponicus@\textit{nipponicus}} 白鱗莎草\index{白鱗莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+nutans+subsp.+subprolixus}{\textit{C. nutans} Vahl subsp. \textit{subprolixus} (Kük.) T.Koyama}  \index{Cyperus@\textit{Cyperus}!nutans@\textit{nutans}!subsp. subprolixus@subsp. \textit{subprolixus}} 點頭莎草\index{點頭莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+odoratus}{\textit{C. odoratus} L.}  \index{Cyperus@\textit{Cyperus}!odoratus@\textit{odoratus}}  \index{Torulinium@\textit{Torulinium}!odoratum@\textit{odoratum}{\\\noindent(= \textit{Cyperus odoratus})}} 斷節莎\index{斷節莎} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+pedunculatus}{\textit{C. pedunculatus} (R.Br.) J.Kern}  \index{Cyperus@\textit{Cyperus}!pedunculatus@\textit{pedunculatus}}  \index{Remirea@\textit{Remirea}!maritima@\textit{maritima}{\\\noindent(= \textit{Cyperus pedunculatus})}} 海濱莎\index{海濱莎} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+pilosus}{\textit{C. pilosus} Vahl}  \index{Cyperus@\textit{Cyperus}!pilosus@\textit{pilosus}} 毛軸莎草\index{毛軸莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+platystylis}{\textit{C. platystylis} R.Br.}  \index{Cyperus@\textit{Cyperus}!platystylis@\textit{platystylis}} 寬柱莎草\index{寬柱莎草} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+polystachyos}{\textit{C. polystachyos} Rottb.}  \index{Cyperus@\textit{Cyperus}!polystachyos@\textit{polystachyos}}  \index{Pycerus@\textit{Pycerus}!polystachyos@\textit{polystachyos}{\\\noindent(= \textit{Cyperus polystachyos})}} 多枝扁莎\index{多枝扁莎} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+procerus}{\textit{C. procerus} Rottb.}  \index{Cyperus@\textit{Cyperus}!procerus@\textit{procerus}} 擬毛軸莎草\index{擬毛軸莎草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+prolifer}{\textit{C. prolifer} Lam.}  \index{Cyperus@\textit{Cyperus}!prolifer@\textit{prolifer}} 紙莎草\index{紙莎草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+pumilus}{\textit{C. pumilus} L.}  \index{Cyperus@\textit{Cyperus}!pumilus@\textit{pumilus}}  \index{Pycreus@\textit{Pycreus}!pumilus@\textit{pumilus}{\\\noindent(= \textit{Cyperus pumilus})}} 矮扁莎\index{矮扁莎} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+pygmaeus}{\textit{C. pygmaeus} Rottb.}  \index{Cyperus@\textit{Cyperus}!pygmaeus@\textit{pygmaeus}} 矮莎草\index{矮莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+radians}{\textit{C. radians} Nees \& Meyen ex Kunth}  \index{Cyperus@\textit{Cyperus}!radians@\textit{radians}}  \index{Mariscus@\textit{Mariscus}!radians@\textit{radians}{\\\noindent(= \textit{Cyperus radians})}} 輻射磚子苗\index{輻射磚子苗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+rotundus}{\textit{C. rotundus} L.}  \index{Cyperus@\textit{Cyperus}!rotundus@\textit{rotundus}} 香附子\index{香附子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+serotinus}{\textit{C. serotinus} Rottb.}  \index{Cyperus@\textit{Cyperus}!serotinus@\textit{serotinus}} 水莎草\index{水莎草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+stolonifer}{\textit{C. stolonifer} Retz.}  \index{Cyperus@\textit{Cyperus}!stolonifer@\textit{stolonifer}} 粗根莖莎草\index{粗根莖莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+sulcinux}{\textit{C. sulcinux} C.B.Clarke}  \index{Cyperus@\textit{Cyperus}!sulcinux@\textit{sulcinux}}  \index{Pycreus@\textit{Pycreus}!sulcinux@\textit{sulcinux}{\\\noindent(= \textit{Cyperus sulcinux})}} 墾丁扁莎\index{墾丁扁莎} NA $^v$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+surinamensis}{\textit{C. surinamensis} Rottb.}  \index{Cyperus@\textit{Cyperus}!surinamensis@\textit{surinamensis}} 刺桿莎草\index{刺桿莎草} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+tenuiculmis}{\textit{C. tenuiculmis} Boeckeler}  \index{Cyperus@\textit{Cyperus}!tenuiculmis@\textit{tenuiculmis}} 四稜穗莎草\index{四稜穗莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+tenuispica}{\textit{C. tenuispica} Steud.}  \index{Cyperus@\textit{Cyperus}!tenuispica@\textit{tenuispica}} 窄翅莎草\index{窄翅莎草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+tuberosus}{\textit{C. tuberosus} Rottb.}  \index{Cyperus@\textit{Cyperus}!tuberosus@\textit{tuberosus}} 假香附子\index{假香附子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyperus+unioloides}{\textit{C. unioloides} R.Br.}  \index{Cyperus@\textit{Cyperus}!unioloides@\textit{unioloides}}  \index{Pycreus@\textit{Pycreus}!unioloides@\textit{unioloides}{\\\noindent(= \textit{Cyperus unioloides})}} 水社扁莎\index{水社扁莎} RE
  \end{itemize}
 \item[] \textit{Diplacrum} 裂穎茅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplacrum+caricinum}{\textit{D. caricinum} R.Br.}  \index{Diplacrum@\textit{Diplacrum}!caricinum@\textit{caricinum}} 裂穎茅\index{裂穎茅} VU
  \end{itemize}
 \item[] \textit{Eleocharis} 荸薺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+acicularis}{\textit{E. acicularis} (L.) Rom. \& Schult.}  \index{Eleocharis@\textit{Eleocharis}!acicularis@\textit{acicularis}} 牛毛顫\index{牛毛顫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+acutangula}{\textit{E. acutangula} (Roxb.) Schult.}  \index{Eleocharis@\textit{Eleocharis}!acutangula@\textit{acutangula}} 桃園藺\index{桃園藺} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+atropurpurea}{\textit{E. atropurpurea} (Retz.) Presl}  \index{Eleocharis@\textit{Eleocharis}!atropurpurea@\textit{atropurpurea}} 黑果藺\index{黑果藺} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+attenuata}{\textit{E. attenuata} (Franch. \& Sav.) Palla}  \index{Eleocharis@\textit{Eleocharis}!attenuata@\textit{attenuata}} 漸尖穗荸薺\index{漸尖穗荸薺} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+congesta+subsp.+japonica}{\textit{E. congesta} D.Don subsp. \textit{japonica} (Miq.) T.Koyama}  \index{Eleocharis@\textit{Eleocharis}!congesta@\textit{congesta}!subsp. japonica@subsp. \textit{japonica}} 針藺\index{針藺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+congesta+var.+subvivipara}{\textit{E. congesta} D.Don var. \textit{subvivipara} (Boeckeler) T.Koyama}  \index{Eleocharis@\textit{Eleocharis}!congesta@\textit{congesta}!var. subvivipara@var. \textit{subvivipara}} 狹穗荸薺\index{狹穗荸薺} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+congesta+var.+thermalis}{\textit{E. congesta} D.Don var. \textit{thermalis} T.Koyama}  \index{Eleocharis@\textit{Eleocharis}!congesta@\textit{congesta}!var. thermalis@var. \textit{thermalis}} 絲稈荸薺\index{絲稈荸薺} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+dulcis+var.+dulcis}{\textit{E. dulcis} (Burm.f.) Trin. ex Hensch. var. \textit{dulcis}}  \index{Eleocharis@\textit{Eleocharis}!dulcis@\textit{dulcis}!var. dulcis@var. \textit{dulcis}} 荸薺\index{荸薺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+geniculata}{\textit{E. geniculata} (L.) Rom. \& Schult.}  \index{Eleocharis@\textit{Eleocharis}!geniculata@\textit{geniculata}} 彎形藺\index{彎形藺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+ochrostachys}{\textit{E. ochrostachys} Steud.}  \index{Eleocharis@\textit{Eleocharis}!ochrostachys@\textit{ochrostachys}} 日月潭藺\index{日月潭藺} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+retroflexa}{\textit{E. retroflexa} (Poir.) Urban}  \index{Eleocharis@\textit{Eleocharis}!retroflexa@\textit{retroflexa}} 貝殼葉荸薺\index{貝殼葉荸薺} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eleocharis+tetraquetra}{\textit{E. tetraquetra} Nees ex Wight}  \index{Eleocharis@\textit{Eleocharis}!tetraquetra@\textit{tetraquetra}} 四角藺\index{四角藺} LC
  \end{itemize}
 \item[] \textit{Fimbristylis} 飄拂草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+acuminata}{\textit{F. acuminata} Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!acuminata@\textit{acuminata}} 尖穗飄拂草\index{尖穗飄拂草} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+aestivalis+var.+aestivalis}{\textit{F. aestivalis} (Retz.) Vahl var. \textit{aestivalis}}  \index{Fimbristylis@\textit{Fimbristylis}!aestivalis@\textit{aestivalis}!var. aestivalis@var. \textit{aestivalis}} 小畦畔飄拂草\index{小畦畔飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+aestivalis+var.+esquarrosa}{\textit{F. aestivalis} (Retz.) Vahl var. \textit{esquarrosa} (Makino) T.Koyama}  \index{Fimbristylis@\textit{Fimbristylis}!aestivalis@\textit{aestivalis}!var. esquarrosa@var. \textit{esquarrosa}} 牧野氏飄拂草\index{牧野氏飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+autumnalis}{\textit{F. autumnalis} (L.) Roem. \& Schult.}  \index{Fimbristylis@\textit{Fimbristylis}!autumnalis@\textit{autumnalis}} 秋飄拂草\index{秋飄拂草} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+bisumbellata}{\textit{F. bisumbellata} (Forssk.) Bubani}  \index{Fimbristylis@\textit{Fimbristylis}!bisumbellata@\textit{bisumbellata}} 大畦畔飄拂草\index{大畦畔飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+complanata}{\textit{F. complanata} (Retz.) Link}  \index{Fimbristylis@\textit{Fimbristylis}!complanata@\textit{complanata}} 野飄拂草\index{野飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+cymosa}{\textit{F. cymosa} R.Br.}  \index{Fimbristylis@\textit{Fimbristylis}!cymosa@\textit{cymosa}} 乾溝飄拂草\index{乾溝飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+dichotoma}{\textit{F. dichotoma} (L.) Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!dichotoma@\textit{dichotoma}} 竹子飄拂草\index{竹子飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+eragrostis}{\textit{F. eragrostis} (Nees \& Meyen ex Nees) Hance}  \index{Fimbristylis@\textit{Fimbristylis}!eragrostis@\textit{eragrostis}} 紫穗飄拂草\index{紫穗飄拂草} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+ferruginea+var.+anpinensis}{\textit{F. ferruginea} (L.) Vahl var. \textit{anpinensis} (Hayata) H.Y.Liu}  \index{Fimbristylis@\textit{Fimbristylis}!ferruginea@\textit{ferruginea}!var. anpinensis@var. \textit{anpinensis}} 安平飄拂草\index{安平飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+ferruginea+var.+ferruginea}{\textit{F. ferruginea} (L.) Vahl var. \textit{ferruginea}}  \index{Fimbristylis@\textit{Fimbristylis}!ferruginea@\textit{ferruginea}!var. ferruginea@var. \textit{ferruginea}} 彭佳嶼飄拂草\index{彭佳嶼飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+griffithii}{\textit{F. griffithii} Boeckeler}  \index{Fimbristylis@\textit{Fimbristylis}!griffithii@\textit{griffithii}} 葛氏飄拂草\index{葛氏飄拂草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+littoralis+var.+koidzumiana}{\textit{F. littoralis} Gaud. var. \textit{koidzumiana} (Ohwi) T.Koyama}  \index{Fimbristylis@\textit{Fimbristylis}!littoralis@\textit{littoralis}!var. koidzumiana@var. \textit{koidzumiana}} 小泉氏飄拂草\index{小泉氏飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+littoralis+var.+littoralis}{\textit{F. littoralis} Gaud. var. \textit{littoralis}}  \index{Fimbristylis@\textit{Fimbristylis}!littoralis@\textit{littoralis}!var. littoralis@var. \textit{littoralis}} 木虱草\index{木虱草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+littoralis}{\textit{F. littoralis} Gaudich.}  \index{Fimbristylis@\textit{Fimbristylis}!littoralis@\textit{littoralis}} 四稜飄拂草\index{四稜飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+macassarensis}{\textit{F. macassarensis} Stend.}  \index{Fimbristylis@\textit{Fimbristylis}!macassarensis@\textit{macassarensis}} 土城飄拂草\index{土城飄拂草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+microcarya}{\textit{F. microcarya} F.Muell.}  \index{Fimbristylis@\textit{Fimbristylis}!microcarya@\textit{microcarya}} 臺北飄拂草\index{臺北飄拂草}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+nutans}{\textit{F. nutans} (Retz.) Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!nutans@\textit{nutans}} 點頭飄拂草\index{點頭飄拂草} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+ovata}{\textit{F. ovata} (Burm.f.) J.Kern}  \index{Fimbristylis@\textit{Fimbristylis}!ovata@\textit{ovata}} 卵形飄拂草\index{卵形飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+polytrichoides}{\textit{F. polytrichoides} (Retz.) Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!polytrichoides@\textit{polytrichoides}} 高雄飄拂草\index{高雄飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+schoenoides}{\textit{F. schoenoides} (Retz.) Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!schoenoides@\textit{schoenoides}} 嘉義飄拂草\index{嘉義飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+sericea}{\textit{F. sericea} (Poir.) R.Br.}  \index{Fimbristylis@\textit{Fimbristylis}!sericea@\textit{sericea}} 黃色飄拂草\index{黃色飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+shimadana}{\textit{F. shimadana} Ohwi}  \index{Fimbristylis@\textit{Fimbristylis}!shimadana@\textit{shimadana}} 白穗飄拂草\index{白穗飄拂草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+spathacea}{\textit{F. spathacea} Roth}  \index{Fimbristylis@\textit{Fimbristylis}!spathacea@\textit{spathacea}} 佛焰苞飄拂草\index{佛焰苞飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+squarrosa}{\textit{F. squarrosa} Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!squarrosa@\textit{squarrosa}} 大屯山飄拂草\index{大屯山飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+stolonifera}{\textit{F. stolonifera} C.B.Clarke}  \index{Fimbristylis@\textit{Fimbristylis}!stolonifera@\textit{stolonifera}} 匍匐莖飄拂草\index{匍匐莖飄拂草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+subinclinata}{\textit{F. subinclinata} T.Koyama}  \index{Fimbristylis@\textit{Fimbristylis}!subinclinata@\textit{subinclinata}} 知本飄拂草\index{知本飄拂草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+tainanensis}{\textit{F. tainanensis} Ohwi}  \index{Fimbristylis@\textit{Fimbristylis}!tainanensis@\textit{tainanensis}}  \index{Fimbristylis@\textit{Fimbristylis}!microcarya@\textit{microcarya}!var. tainanensis@var. \textit{tainanensis}{\\\noindent(=\textit{Fimbristylis tainanensis})}} 臺南飄拂草\index{臺南飄拂草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+tetragona}{\textit{F. tetragona} R.Br.}  \index{Fimbristylis@\textit{Fimbristylis}!tetragona@\textit{tetragona}} 四方型飄拂草\index{四方型飄拂草} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+thomsonii}{\textit{F. thomsonii} Boeckeler}  \index{Fimbristylis@\textit{Fimbristylis}!thomsonii@\textit{thomsonii}} 鬼野飄拂草\index{鬼野飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+tomentosa}{\textit{F. tomentosa} Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!tomentosa@\textit{tomentosa}} 絨毛飄拂草\index{絨毛飄拂草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+tristachya+var.+subbispicata}{\textit{F. tristachya} R.Br. var. \textit{subbispicata} (Nees \& Meyen) T.Koyama}  \index{Fimbristylis@\textit{Fimbristylis}!tristachya@\textit{tristachya}!var. subbispicata@var. \textit{subbispicata}} 山藺\index{山藺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fimbristylis+umbellaris}{\textit{F. umbellaris} (Lam.) Vahl}  \index{Fimbristylis@\textit{Fimbristylis}!umbellaris@\textit{umbellaris}} 繖形飄拂草\index{繖形飄拂草} LC
  \end{itemize}
 \item[] \textit{Fuirena} 黑珠蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fuirena+ciliaris}{\textit{F. ciliaris} (L.) Roxb.}  \index{Fuirena@\textit{Fuirena}!ciliaris@\textit{ciliaris}} 毛三稜\index{毛三稜} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fuirena+umbellata}{\textit{F. umbellata} Rottb.}  \index{Fuirena@\textit{Fuirena}!umbellata@\textit{umbellata}} 黑珠蒿\index{黑珠蒿} LC
  \end{itemize}
 \item[] \textit{Gahnia} 黑莎草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gahnia+tristis}{\textit{G. tristis} Nees ex Hook. \& Arn.}  \index{Gahnia@\textit{Gahnia}!tristis@\textit{tristis}} 黑莎草\index{黑莎草} NT
  \end{itemize}
 \item[] \textit{Hypolytrum} 割雞芒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypolytrum+nemorum}{\textit{H. nemorum} (Vahl) Spreng.}  \index{Hypolytrum@\textit{Hypolytrum}!nemorum@\textit{nemorum}} 割雞芒\index{割雞芒} LC
  \end{itemize}
 \item[] \textit{Mariscus} 磚子苗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mariscus+sumatrensis}{\textit{M. sumatrensis} (Retz.) J.Raynal}  \index{Mariscus@\textit{Mariscus}!sumatrensis@\textit{sumatrensis}} 磚子苗\index{磚子苗} LC
  \end{itemize}
 \item[] \textit{Pycreus} 扁莎屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pycreus+flavidus}{\textit{P. flavidus} (Retz.) T.Koyama}  \index{Pycreus@\textit{Pycreus}!flavidus@\textit{flavidus}} 球穗扁莎\index{球穗扁莎} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pycreus+sanguinolentus}{\textit{P. sanguinolentus} (Vahl) Nees ex C.B.Clarke}  \index{Pycreus@\textit{Pycreus}!sanguinolentus@\textit{sanguinolentus}} 紅鱗扁莎\index{紅鱗扁莎} LC
  \end{itemize}
 \item[] \textit{Rhynchospora} 刺子莞屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+alba}{\textit{R. alba} (L.) Vahl}  \index{Rhynchospora@\textit{Rhynchospora}!alba@\textit{alba}} 白穗刺子莞\index{白穗刺子莞} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+chinensis}{\textit{R. chinensis} Nees \& Meyen ex Nees}  \index{Rhynchospora@\textit{Rhynchospora}!chinensis@\textit{chinensis}} 華刺子莞\index{華刺子莞} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+corymbosa}{\textit{R. corymbosa} (L.) Britt.}  \index{Rhynchospora@\textit{Rhynchospora}!corymbosa@\textit{corymbosa}} 三儉草\index{三儉草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+malasica}{\textit{R. malasica} C.B.Clarke}  \index{Rhynchospora@\textit{Rhynchospora}!malasica@\textit{malasica}} 馬來刺子莞\index{馬來刺子莞} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+rubra}{\textit{R. rubra} (Lour.) Makino}  \index{Rhynchospora@\textit{Rhynchospora}!rubra@\textit{rubra}} 刺子莞\index{刺子莞} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchospora+rugosa+subsp.+brownii}{\textit{R. rugosa} (Vahl) Gale subsp. \textit{brownii} (Rom. \& Schult.) T.Koyama}  \index{Rhynchospora@\textit{Rhynchospora}!rugosa@\textit{rugosa}!subsp. brownii@subsp. \textit{brownii}} 布朗氏莞\index{布朗氏莞} VU
  \end{itemize}
 \item[] \textit{Schoenoplectiella} 擬莞舅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+juncoides}{\textit{S. juncoides} (Roxb.) Lye}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!juncoides@\textit{juncoides}}  \index{Schoenoplectus@\textit{Schoenoplectus}!juncoides@\textit{juncoides}{\\\noindent(= \textit{Schoenoplectiella juncoides})}} 螢藺\index{螢藺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+lineolata}{\textit{S. lineolata} (Franch. \& Sav.) Lye}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!lineolata@\textit{lineolata}}  \index{Schoenoplectus@\textit{Schoenoplectus}!lineolatus@\textit{lineolatus}{\\\noindent(= \textit{Schoenoplectiella lineolata})}} 蘭嶼莞\index{蘭嶼莞} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+mucronata+subsp.+robusta}{\textit{S. mucronata} (L.) J.Jung \& H.K.Choi subsp. \textit{robusta} (Miq.) T.C.Hsu}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!mucronata@\textit{mucronata}!subsp. robusta@subsp. \textit{robusta}}  \index{Schoenoplectus@\textit{Schoenoplectus}!mucronatus@\textit{mucronatus}!subsp. robustus@subsp. \textit{robustus}{\\\noindent(=\textit{Schoenoplectiella mucronata} subsp. \textit{robusta})}} 水毛花\index{水毛花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+multiseta}{\textit{S. multiseta} (Hayasaka \& C.Sato) Hayasaka}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!multiseta@\textit{multiseta}} 疏稈水毛花\index{疏稈水毛花} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+supina+subsp.+lateriflora}{\textit{S. supina} (Palla) Lye subsp. \textit{lateriflora} (J.F.Gmel.) T.C.Hsu}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!supina@\textit{supina}!subsp. lateriflora@subsp. \textit{lateriflora}}  \index{Schoenoplectus@\textit{Schoenoplectus}!supinus@\textit{supinus}!subsp. lateriflorus@subsp. \textit{lateriflorus}{\\\noindent(=\textit{Schoenoplectiella supina} subsp. \textit{lateriflora})}} 小水莞\index{小水莞} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectiella+wallichii}{\textit{S. wallichii} (Nees) Lye}  \index{Schoenoplectiella@\textit{Schoenoplectiella}!wallichii@\textit{wallichii}}  \index{Schoenoplectus@\textit{Schoenoplectus}!wallichii@\textit{wallichii}{\\\noindent(= \textit{Schoenoplectiella wallichii})}} 臺灣水莞\index{臺灣水莞} NT
  \end{itemize}
 \item[] \textit{Schoenoplectus} 擬莞屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectus+tabernaemontani}{\textit{S. tabernaemontani} (C.C.Gmel.) Palla}  \index{Schoenoplectus@\textit{Schoenoplectus}!tabernaemontani@\textit{tabernaemontani}}  \index{Schoenoplectus@\textit{Schoenoplectus}!validus@\textit{validus}{\\\noindent(= \textit{Schoenoplectus tabernaemontani})}} 莞\index{莞} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenoplectus+triqueter}{\textit{S. triqueter} (L.) Palla}  \index{Schoenoplectus@\textit{Schoenoplectus}!triqueter@\textit{triqueter}} 蒲\index{蒲} NT
  \end{itemize}
 \item[] \textit{Schoenus} 赤箭莎屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenus+apogon}{\textit{S. apogon} Rom. \& Schult.}  \index{Schoenus@\textit{Schoenus}!apogon@\textit{apogon}} 矮赤箭莎\index{矮赤箭莎} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenus+falcatus}{\textit{S. falcatus} R.Br.}  \index{Schoenus@\textit{Schoenus}!falcatus@\textit{falcatus}} 赤箭莎\index{赤箭莎} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenus+nitens+subsp.+nitens}{\textit{S. nitens} (R.Br.) Poir. subsp. \textit{nitens}}  \index{Schoenus@\textit{Schoenus}!nitens@\textit{nitens}!subsp. nitens@subsp. \textit{nitens}} 匍莖赤箭莎\index{匍莖赤箭莎} DD
  \end{itemize}
 \item[] \textit{Scirpus} 莞屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scirpus+hainanensis}{\textit{S. hainanensis} S.M.Huang}  \index{Scirpus@\textit{Scirpus}!hainanensis@\textit{hainanensis}} 海南藨草\index{海南藨草} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scirpus+ternatanus}{\textit{S. ternatanus} Reinw. ex Miq.}  \index{Scirpus@\textit{Scirpus}!ternatanus@\textit{ternatanus}} 大莞草\index{大莞草} LC
  \end{itemize}
 \item[] \textit{Scleria} 珍珠茅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+biflora}{\textit{S. biflora} Roxb.}  \index{Scleria@\textit{Scleria}!biflora@\textit{biflora}} 二花珍珠茅\index{二花珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+levis}{\textit{S. levis} Retz.}  \index{Scleria@\textit{Scleria}!levis@\textit{levis}} 毛果珍珠茅\index{毛果珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+lithosperma}{\textit{S. lithosperma} (L.) Sw.}  \index{Scleria@\textit{Scleria}!lithosperma@\textit{lithosperma}} 石果珍珠茅\index{石果珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+novae-hollandiae}{\textit{S. novae-hollandiae} Boeckeler}  \index{Scleria@\textit{Scleria}!novae-hollandiae@\textit{novae-hollandiae}} 澳洲珍珠茅\index{澳洲珍珠茅} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+radula}{\textit{S. radula} Hance}  \index{Scleria@\textit{Scleria}!radula@\textit{radula}}  \index{Scleria@\textit{Scleria}!laeviformis@\textit{laeviformis}{\\\noindent(= \textit{Scleria radula})}} 光果珍珠茅\index{光果珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+rugosa}{\textit{S. rugosa} R.Br.}  \index{Scleria@\textit{Scleria}!rugosa@\textit{rugosa}} 皺果珍珠茅\index{皺果珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+scrobiculata}{\textit{S. scrobiculata} Nees \& Mey. ex Nees}  \index{Scleria@\textit{Scleria}!scrobiculata@\textit{scrobiculata}} 輪葉珍珠茅\index{輪葉珍珠茅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+sumatrensis}{\textit{S. sumatrensis} Retz.}  \index{Scleria@\textit{Scleria}!sumatrensis@\textit{sumatrensis}} 印尼珍珠茅\index{印尼珍珠茅} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scleria+terrestris}{\textit{S. terrestris} (L.) Fassett}  \index{Scleria@\textit{Scleria}!terrestris@\textit{terrestris}} 陸生珍珠茅\index{陸生珍珠茅} LC
  \end{itemize}
 \item[] \textit{Trichophorum} 針藺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trichophorum+subcapitatum}{\textit{T. subcapitatum} (Thwaites \& Hook.) D.A.Simpson}  \index{Trichophorum@\textit{Trichophorum}!subcapitatum@\textit{subcapitatum}} 玉山針藺\index{玉山針藺} LC
  \end{itemize}
  \end{itemize}
