
  \begin{itemize}
 \item[] \textit{Daphniphyllum} 虎皮楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Daphniphyllum+glaucescens+subsp.+oldhamii}{\textit{D. glaucescens} Blume subsp. \textit{oldhamii} (Hemsl.) T.C.Huang}  \index{Daphniphyllum@\textit{Daphniphyllum}!glaucescens@\textit{glaucescens}!subsp. oldhamii@subsp. \textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奧氏虎皮楠&T2_new_value=true&fr=y}}{奧氏虎皮楠}\index{奧氏虎皮楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Daphniphyllum+glaucescens+subsp.+oldhamii+var.+kengii}{\textit{D. glaucescens} Blume subsp. \textit{oldhamii} (Hemsl.) T.C.Huang var. \textit{kengii} (Hurus.) T.C.Huang}  \index{Daphniphyllum@\textit{Daphniphyllum}!glaucescens@\textit{glaucescens}!subsp. oldhamii var. kengii@subsp. \textit{oldhamii} var. \textit{kengii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=耿氏虎皮楠&T2_new_value=true&fr=y}}{耿氏虎皮楠}\index{耿氏虎皮楠}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Daphniphyllum+glaucescens+subsp.+oldhamii+var.+lanyuense}{\textit{D. glaucescens} Blume subsp. \textit{oldhamii} (Hemsl.) T.C.Huang var. \textit{lanyuense} T.C.Huang}  \index{Daphniphyllum@\textit{Daphniphyllum}!glaucescens@\textit{glaucescens}!subsp. oldhamii var. lanyuense@subsp. \textit{oldhamii} var. \textit{lanyuense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼虎皮楠&T2_new_value=true&fr=y}}{蘭嶼虎皮楠}\index{蘭嶼虎皮楠}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Daphniphyllum+himalaense+subsp.+macropodum}{\textit{D. himalaense} (Benth.) Müll.Arg. subsp. \textit{macropodum} (Miq.) T.C.Huang}  \index{Daphniphyllum@\textit{Daphniphyllum}!himalaense@\textit{himalaense}!subsp. macropodum@subsp. \textit{macropodum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉虎皮楠&T2_new_value=true&fr=y}}{薄葉虎皮楠}\index{薄葉虎皮楠} LC
  \end{itemize}
  \end{itemize}
