
  \begin{itemize}
 \item[] \textit{Dennstaedtia} 碗蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dennstaedtia+hirsuta}{\textit{D. hirsuta} (Sw.) Mett. ex Miq.}  \index{Dennstaedtia@\textit{Dennstaedtia}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細毛碗蕨&T2_new_value=true&fr=y}}{細毛碗蕨}\index{細毛碗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dennstaedtia+scandens}{\textit{D. scandens} (Blume) Moore}  \index{Dennstaedtia@\textit{Dennstaedtia}!scandens@\textit{scandens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺柄碗蕨&T2_new_value=true&fr=y}}{刺柄碗蕨}\index{刺柄碗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dennstaedtia+smithii}{\textit{D. smithii} (Hook.) Moore}  \index{Dennstaedtia@\textit{Dennstaedtia}!smithii@\textit{smithii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=司氏碗蕨&T2_new_value=true&fr=y}}{司氏碗蕨}\index{司氏碗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dennstaedtia+zeylanica}{\textit{D. zeylanica} (Sw.) Zink ex Fraser-Jenk. \& Kandel}  \index{Dennstaedtia@\textit{Dennstaedtia}!zeylanica@\textit{zeylanica}}  \index{Dennstaedtia@\textit{Dennstaedtia}!scabra@\textit{scabra}{\\\noindent(= \textit{Dennstaedtia zeylanica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=碗蕨&T2_new_value=true&fr=y}}{碗蕨}\index{碗蕨} LC
  \end{itemize}
 \item[] \textit{Histiopteris} 栗蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Histiopteris+incisa}{\textit{H. incisa} (Thunb.) J.Sm.}  \index{Histiopteris@\textit{Histiopteris}!incisa@\textit{incisa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=栗蕨&T2_new_value=true&fr=y}}{栗蕨}\index{栗蕨} LC
  \end{itemize}
 \item[] \textit{Hypolepis} 姬蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypolepis+alpina}{\textit{H. alpina} (Blume) Hook.}  \index{Hypolepis@\textit{Hypolepis}!alpina@\textit{alpina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣姬蕨&T2_new_value=true&fr=y}}{臺灣姬蕨}\index{臺灣姬蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypolepis+pallida}{\textit{H. pallida} (Blume) Hook.}  \index{Hypolepis@\textit{Hypolepis}!pallida@\textbf{\textit{pallida}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰姬蕨&T2_new_value=true&fr=y}}{灰姬蕨}\index{灰姬蕨@{\Song{灰姬蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypolepis+punctata}{\textit{H. punctata} (Thunb.) Mett. ex Kuhn}  \index{Hypolepis@\textit{Hypolepis}!punctata@\textit{punctata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=姬蕨&T2_new_value=true&fr=y}}{姬蕨}\index{姬蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypolepis+tenuifolia}{\textit{H. tenuifolia} (G.Forst.) Bernh.}  \index{Hypolepis@\textit{Hypolepis}!tenuifolia@\textit{tenuifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉姬蕨&T2_new_value=true&fr=y}}{細葉姬蕨}\index{細葉姬蕨} LC
  \end{itemize}
 \item[] \textit{Microlepia} 鱗蓋蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+calvescens}{\textit{M. calvescens} (Wall. ex Hook.) C.Presl}  \index{Microlepia@\textit{Microlepia}!calvescens@\textit{calvescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉鱗蓋蕨&T2_new_value=true&fr=y}}{光葉鱗蓋蕨}\index{光葉鱗蓋蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+hookeriana}{\textit{M. hookeriana} (Wall. ex Hook.) C.Presl}  \index{Microlepia@\textit{Microlepia}!hookeriana@\textit{hookeriana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虎克氏鱗蓋蕨&T2_new_value=true&fr=y}}{虎克氏鱗蓋蕨}\index{虎克氏鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+intramarginalis}{\textit{M. intramarginalis} (Tagawa) Seriz.}  \index{Microlepia@\textit{Microlepia}!intramarginalis@\textit{intramarginalis}}  \index{Microlepia@\textit{Microlepia}!calvescens@\textit{calvescens}!var. intramarginalis@var. \textit{intramarginalis}{\\\noindent(=\textit{Microlepia intramarginalis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽葉鱗蓋蕨&T2_new_value=true&fr=y}}{羽葉鱗蓋蕨}\index{羽葉鱗蓋蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+krameri}{\textit{M. krameri} C.M.Kuo}  \index{Microlepia@\textit{Microlepia}!krameri@\textit{krameri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=克氏鱗蓋蕨&T2_new_value=true&fr=y}}{克氏鱗蓋蕨}\index{克氏鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+marginata+var.+bipinnata}{\textit{M. marginata} (Panzer) C.Chr. var. \textit{bipinnata} Makino}  \index{Microlepia@\textit{Microlepia}!marginata@\textit{marginata}!var. bipinnata@var. \textit{bipinnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺北鱗蓋蕨&T2_new_value=true&fr=y}}{臺北鱗蓋蕨}\index{臺北鱗蓋蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+marginata+var.+marginata}{\textit{M. marginata} (Panzer) C.Chr. var. \textit{marginata}}  \index{Microlepia@\textit{Microlepia}!marginata@\textit{marginata}!var. marginata@var. \textit{marginata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=邊緣鱗蓋蕨&T2_new_value=true&fr=y}}{邊緣鱗蓋蕨}\index{邊緣鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+nepalensis}{\textit{M. nepalensis} (Spreng.) Fraser-Jenk., Kandel \& Pariyar}  \index{Microlepia@\textit{Microlepia}!nepalensis@\textit{nepalensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華南鱗蓋蕨&T2_new_value=true&fr=y}}{華南鱗蓋蕨}\index{華南鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+obtusiloba}{\textit{M. obtusiloba} Hayata}  \index{Microlepia@\textit{Microlepia}!obtusiloba@\textit{obtusiloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=團羽鱗蓋蕨&T2_new_value=true&fr=y}}{團羽鱗蓋蕨}\index{團羽鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+platyphylla}{\textit{M. platyphylla} (D.Don) J.Sm.}  \index{Microlepia@\textit{Microlepia}!platyphylla@\textbf{\textit{platyphylla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉鱗蓋蕨&T2_new_value=true&fr=y}}{闊葉鱗蓋蕨}\index{闊葉鱗蓋蕨@{\Song{闊葉鱗蓋蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+rhomboidea}{\textit{M. rhomboidea} (Wall. ex Kunze) Prantl}  \index{Microlepia@\textit{Microlepia}!rhomboidea@\textbf{\textit{rhomboidea}}}  \index{Microlepia@\textit{Microlepia}!taiwaniana@\textit{taiwaniana}{\\\noindent(= \textit{Microlepia rhomboidea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斜方鱗蓋蕨&T2_new_value=true&fr=y}}{斜方鱗蓋蕨(臺灣鱗蓋蕨)} \index{斜方鱗蓋蕨@{\Song{斜方鱗蓋蕨}}} \index{臺灣鱗蓋蕨@{\Song{臺灣鱗蓋蕨(=斜方鱗蓋蕨)}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+sinostrigosa}{\textit{M. sinostrigosa} Ching}  \index{Microlepia@\textit{Microlepia}!sinostrigosa@\textit{sinostrigosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中華鱗蓋蕨&T2_new_value=true&fr=y}}{中華鱗蓋蕨}\index{中華鱗蓋蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+speluncae}{\textit{M. speluncae} (L.) Moore}  \index{Microlepia@\textit{Microlepia}!speluncae@\textit{speluncae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=熱帶鱗蓋蕨&T2_new_value=true&fr=y}}{熱帶鱗蓋蕨}\index{熱帶鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+strigosa}{\textit{M. strigosa} (Thunb.) C.Presl}  \index{Microlepia@\textit{Microlepia}!strigosa@\textit{strigosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛鱗蓋蕨&T2_new_value=true&fr=y}}{粗毛鱗蓋蕨}\index{粗毛鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+substrigosa}{\textit{M. substrigosa} Tagawa}  \index{Microlepia@\textit{Microlepia}!substrigosa@\textit{substrigosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亞粗毛鱗蓋蕨&T2_new_value=true&fr=y}}{亞粗毛鱗蓋蕨}\index{亞粗毛鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+tenera}{\textit{M. tenera} Christ}  \index{Microlepia@\textit{Microlepia}!tenera@\textit{tenera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=嫩鱗蓋蕨&T2_new_value=true&fr=y}}{嫩鱗蓋蕨}\index{嫩鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+trapeziformis}{\textit{M. trapeziformis} (Roxb.) Kuhn}  \index{Microlepia@\textit{Microlepia}!trapeziformis@\textit{trapeziformis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=針毛鱗蓋蕨&T2_new_value=true&fr=y}}{針毛鱗蓋蕨}\index{針毛鱗蓋蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+trichocarpa}{\textit{M. trichocarpa} Hayata}  \index{Microlepia@\textit{Microlepia}!trichocarpa@\textit{trichocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果鱗蓋蕨&T2_new_value=true&fr=y}}{毛果鱗蓋蕨}\index{毛果鱗蓋蕨}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microlepia+trichosora}{\textit{M. trichosora} Ching}  \index{Microlepia@\textit{Microlepia}!trichosora@\textit{trichosora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛囊鱗蓋蕨&T2_new_value=true&fr=y}}{毛囊鱗蓋蕨}\index{毛囊鱗蓋蕨} LC
  \end{itemize}
 \item[] \textit{Monachosorum} 稀子蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monachosorum+henryi}{\textit{M. henryi} Christ}  \index{Monachosorum@\textit{Monachosorum}!henryi@\textit{henryi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=稀子蕨&T2_new_value=true&fr=y}}{稀子蕨}\index{稀子蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monachosorum+maximowiczii}{\textit{M. maximowiczii} (Baker) Hayata}  \index{Monachosorum@\textit{Monachosorum}!maximowiczii@\textit{maximowiczii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=岩穴蕨&T2_new_value=true&fr=y}}{岩穴蕨}\index{岩穴蕨} LC
  \end{itemize}
 \item[] \textit{Paesia} 曲軸蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paesia+radula}{\textit{P. radula} (Baker) C.Chr.}  \index{Paesia@\textit{Paesia}!radula@\textbf{\textit{radula}}}  \index{Paesia@\textit{Paesia}!taiwanensis@\textit{taiwanensis}{\\\noindent(= \textit{Paesia radula})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=曲軸蕨&T2_new_value=true&fr=y}}{曲軸蕨(臺灣曲軸蕨)} \index{曲軸蕨@{\Song{曲軸蕨}}} \index{臺灣曲軸蕨@{\Song{臺灣曲軸蕨(=曲軸蕨)}}} CR
  \end{itemize}
 \item[] \textit{Pteridium} 蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteridium+latiusculum+subsp.+japonicum}{\textit{P. latiusculum}  subsp. \textit{japonicum} (Nakai) Fraser-Jenk.}  \index{Pteridium@\textit{Pteridium}!latiusculum@\textit{latiusculum}!subsp. japonicum@subsp. \textit{japonicum}}  \index{Pteridium@\textit{Pteridium}!aquilinum@\textit{aquilinum}!subsp. latiusculum@subsp. \textit{latiusculum}{\\\noindent(=\textit{Pteridium latiusculum} subsp. \textit{japonicum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蕨&T2_new_value=true&fr=y}}{蕨}\index{蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteridium+revolutum}{\textit{P. revolutum} (Blume) Nakai}  \index{Pteridium@\textit{Pteridium}!revolutum@\textit{revolutum}}  \index{Pteridium@\textit{Pteridium}!aquilinum@\textit{aquilinum}!subsp. wightianum@subsp. \textit{wightianum}{\\\noindent(=\textit{Pteridium revolutum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巒大蕨&T2_new_value=true&fr=y}}{巒大蕨}\index{巒大蕨} LC
  \end{itemize}
  \end{itemize}
