
  \begin{itemize}
 \item[] \textit{Shortia} 裂緣花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Shortia+rotundifolia+var.+ritoensis}{\textit{S. rotundifolia} (Maxim.) Makino var. \textit{ritoensis} (Hayata) T.C.Huang \& A.Hsiao}  \index{Shortia@\textit{Shortia}!rotundifolia@\textit{rotundifolia}!var. ritoensis@var. \textit{ritoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=李棟山裂緣花&T2_new_value=true&fr=y}}{李棟山裂緣花}\index{李棟山裂緣花}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Shortia+rotundifolia+var.+rotundifolia}{\textit{S. rotundifolia} (Maxim.) Makino var. \textit{rotundifolia}}  \index{Shortia@\textit{Shortia}!rotundifolia@\textit{rotundifolia}!var. rotundifolia@var. \textit{rotundifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=到卵葉裂緣花&T2_new_value=true&fr=y}}{到卵葉裂緣花}\index{到卵葉裂緣花} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Shortia+rotundifolia+var.+subcordata}{\textit{S. rotundifolia} (Maxim.) Makino var. \textit{subcordata} (Hayata) T.C.Huang \& A.Hsiao}  \index{Shortia@\textit{Shortia}!rotundifolia@\textit{rotundifolia}!var. subcordata@var. \textit{subcordata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉裂緣花&T2_new_value=true&fr=y}}{圓葉裂緣花}\index{圓葉裂緣花}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Shortia+rotundifolia+var.+transalpine}{\textit{S. rotundifolia} (Maxim.) Makino var. \textit{transalpine} (Hayata) T.Yamaz.}  \index{Shortia@\textit{Shortia}!rotundifolia@\textit{rotundifolia}!var. transalpine@var. \textit{transalpine}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山裂緣花&T2_new_value=true&fr=y}}{高山裂緣花}\index{高山裂緣花}\# NT
  \end{itemize}
  \end{itemize}
