
  \begin{itemize}
 \item[] \textit{Dioscorea} 薯蕷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+alata}{\textit{D. alata} L.}  \index{Dioscorea@\textit{Dioscorea}!alata@\textit{alata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大薯&T2_new_value=true&fr=y}}{大薯}\index{大薯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+batatas}{\textit{D. batatas} Decne.}  \index{Dioscorea@\textit{Dioscorea}!batatas@\textit{batatas}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=家山藥&T2_new_value=true&fr=y}}{家山藥}\index{家山藥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+benthamii}{\textit{D. benthamii} Prain \& Burkill}  \index{Dioscorea@\textit{Dioscorea}!benthamii@\textit{benthamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大青薯&T2_new_value=true&fr=y}}{大青薯}\index{大青薯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+bulbifera}{\textit{D. bulbifera} L.}  \index{Dioscorea@\textit{Dioscorea}!bulbifera@\textit{bulbifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃獨&T2_new_value=true&fr=y}}{黃獨}\index{黃獨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+codonopsidifolia}{\textit{D. codonopsidifolia} Kamik.}  \index{Dioscorea@\textit{Dioscorea}!codonopsidifolia@\textit{codonopsidifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉薯&T2_new_value=true&fr=y}}{掌葉薯}\index{掌葉薯}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+collettii}{\textit{D. collettii} Hook.f.}  \index{Dioscorea@\textit{Dioscorea}!collettii@\textit{collettii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華南薯蕷&T2_new_value=true&fr=y}}{華南薯蕷}\index{華南薯蕷} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+cumingii}{\textit{D. cumingii} Prain \& Burkill}  \index{Dioscorea@\textit{Dioscorea}!cumingii@\textbf{\textit{cumingii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼田薯&T2_new_value=true&fr=y}}{蘭嶼田薯}\index{蘭嶼田薯@{\Song{蘭嶼田薯}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+doryphora}{\textit{D. doryphora} Hance}  \index{Dioscorea@\textit{Dioscorea}!doryphora@\textit{doryphora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=戟葉田薯&T2_new_value=true&fr=y}}{戟葉田薯}\index{戟葉田薯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+esculenta+var.+spinosa}{\textit{D. esculenta} (Lour.) Burkill var. \textit{spinosa} R.Knuth}  \index{Dioscorea@\textit{Dioscorea}!esculenta@\textit{esculenta}!var. spinosa@var. \textit{spinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺薯蕷&T2_new_value=true&fr=y}}{刺薯蕷}\index{刺薯蕷} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+hispida}{\textit{D. hispida} Dennst.}  \index{Dioscorea@\textit{Dioscorea}!hispida@\textit{hispida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白薯榔&T2_new_value=true&fr=y}}{白薯榔}\index{白薯榔} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+japonica+var.+japonica}{\textit{D. japonica} Thunb. var. \textit{japonica}}  \index{Dioscorea@\textit{Dioscorea}!japonica@\textit{japonica}!var. japonica@var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉野山藥&T2_new_value=true&fr=y}}{薄葉野山藥}\index{薄葉野山藥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+japonica+var.+oldhamii}{\textit{D. japonica} Thunb. var. \textit{oldhamii} R.Knuth}  \index{Dioscorea@\textit{Dioscorea}!japonica@\textit{japonica}!var. oldhamii@var. \textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉野山藥&T2_new_value=true&fr=y}}{細葉野山藥}\index{細葉野山藥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+japonica+var.+pseudojaponica}{\textit{D. japonica} Thunb. var. \textit{pseudojaponica} (Hayata) Yamam.}  \index{Dioscorea@\textit{Dioscorea}!japonica@\textit{japonica}!var. pseudojaponica@var. \textit{pseudojaponica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基隆野山藥&T2_new_value=true&fr=y}}{基隆野山藥}\index{基隆野山藥}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+kaoi}{\textit{D. kaoi} T.S.Liu \& T.C.Huang}  \index{Dioscorea@\textit{Dioscorea}!kaoi@\textit{kaoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓錐花薯蕷&T2_new_value=true&fr=y}}{圓錐花薯蕷}\index{圓錐花薯蕷}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+matsudae}{\textit{D. matsudae} Hayata}  \index{Dioscorea@\textit{Dioscorea}!matsudae@\textit{matsudae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白葉薯榔&T2_new_value=true&fr=y}}{裏白葉薯榔}\index{裏白葉薯榔} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+persimilis}{\textit{D. persimilis} Prain \& Burkill}  \index{Dioscorea@\textit{Dioscorea}!persimilis@\textit{persimilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假山藥薯&T2_new_value=true&fr=y}}{假山藥薯}\index{假山藥薯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dioscorea+sansibarensis}{\textit{D. sansibarensis} Pax}  \index{Dioscorea@\textit{Dioscorea}!sansibarensis@\textit{sansibarensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=非洲薯蕷&T2_new_value=true&fr=y}}{非洲薯蕷}\index{非洲薯蕷} NA$^n$
  \end{itemize}
 \item[] \textit{Tacca} 蒟蒻薯屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tacca+leontopetaloides}{\textit{T. leontopetaloides} (L.) Kuntze}  \index{Tacca@\textit{Tacca}!leontopetaloides@\textbf{\textit{leontopetaloides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蒟蒻薯&T2_new_value=true&fr=y}}{蒟蒻薯}\index{蒟蒻薯@{\Song{蒟蒻薯}}} CR
  \end{itemize}
  \end{itemize}
