
  \begin{itemize}
 \item[] \textit{Arachniodes} 複葉耳蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+aristata}{\textit{A. aristata} (G.Forst.) Tindale}  \index{Arachniodes@\textit{Arachniodes}!aristata@\textit{aristata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉複葉耳蕨&T2_new_value=true&fr=y}}{細葉複葉耳蕨}\index{細葉複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+chinensis}{\textit{A. chinensis} (Rosenst.) Ching }  \index{Arachniodes@\textit{Arachniodes}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中華複葉耳蕨&T2_new_value=true&fr=y}}{中華複葉耳蕨}\index{中華複葉耳蕨@{\Song{中華複葉耳蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+festina}{\textit{A. festina} (Hance) Ching}  \index{Arachniodes@\textit{Arachniodes}!festina@\textit{festina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣兩面複葉耳蕨&T2_new_value=true&fr=y}}{臺灣兩面複葉耳蕨}\index{臺灣兩面複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+globisora}{\textit{A. globisora} (Hayata) Ching}  \index{Arachniodes@\textit{Arachniodes}!globisora@\textit{globisora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣複葉耳蕨&T2_new_value=true&fr=y}}{臺灣複葉耳蕨}\index{臺灣複葉耳蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+nigrospinosa}{\textit{A. nigrospinosa} (Ching) Ching}  \index{Arachniodes@\textit{Arachniodes}!nigrospinosa@\textit{nigrospinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑鱗複葉耳蕨&T2_new_value=true&fr=y}}{黑鱗複葉耳蕨}\index{黑鱗複葉耳蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+pseudoaristata}{\textit{A. pseudoaristata} (Tagawa) Ohwi}  \index{Arachniodes@\textit{Arachniodes}!pseudoaristata@\textit{pseudoaristata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉複葉耳蕨&T2_new_value=true&fr=y}}{小葉複葉耳蕨}\index{小葉複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+quadripinnata}{\textit{A. quadripinnata} (Hayata) Seriz.}  \index{Arachniodes@\textit{Arachniodes}!quadripinnata@\textit{quadripinnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛苞擬複葉耳蕨&T2_new_value=true&fr=y}}{毛苞擬複葉耳蕨}\index{毛苞擬複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+rhomboidea+var.+rhomboidea}{\textit{A. rhomboidea} (Wall. ex Mett.) Ching var. \textit{rhomboidea}}  \index{Arachniodes@\textit{Arachniodes}!rhomboidea@\textit{rhomboidea}!var. rhomboidea@var. \textit{rhomboidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斜方複葉耳蕨&T2_new_value=true&fr=y}}{斜方複葉耳蕨}\index{斜方複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachniodes+rhomboidea+var.+yakusimensis}{\textit{A. rhomboidea} (Wall. ex Mett.) Ching var. \textit{yakusimensis} (H.Ito) W.C.Shieh}  \index{Arachniodes@\textit{Arachniodes}!rhomboidea@\textit{rhomboidea}!var. yakusimensis@var. \textit{yakusimensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屋久複葉耳蕨&T2_new_value=true&fr=y}}{屋久複葉耳蕨}\index{屋久複葉耳蕨} LC
  \end{itemize}
 \item[] \textit{Bolbitis} 實蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+angustipinna}{\textit{B. angustipinna} (Hayata) H.Itô}  \index{Bolbitis@\textit{Bolbitis}!angustipinna@\textit{angustipinna}}  \index{Bolbitis@\textit{Bolbitis}!contaminans@\textit{contaminans}{\\\noindent(= \textit{Bolbitis angustipinna})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉實蕨&T2_new_value=true&fr=y}}{細葉實蕨}\index{細葉實蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+appendiculata}{\textit{B. appendiculata} (Willd.) K.Iwats.}  \index{Bolbitis@\textit{Bolbitis}!appendiculata@\textit{appendiculata}}  \index{Egenolfia@\textit{Egenolfia}!appendiculata@\textit{appendiculata}{\\\noindent(= \textit{Bolbitis appendiculata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺蕨&T2_new_value=true&fr=y}}{刺蕨}\index{刺蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+heteroclita}{\textit{B. heteroclita} (C.Presl) Ching}  \index{Bolbitis@\textit{Bolbitis}!heteroclita@\textit{heteroclita}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾葉實蕨&T2_new_value=true&fr=y}}{尾葉實蕨}\index{尾葉實蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+rhizophylla}{\textit{B. rhizophylla} (Kaulf.) Hennipmam}  \index{Bolbitis@\textit{Bolbitis}!rhizophylla@\textit{rhizophylla}}  \index{Egenolfia@\textit{Egenolfia}!rhizophylla@\textit{rhizophylla}{\\\noindent(= \textit{Bolbitis rhizophylla})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大刺蕨&T2_new_value=true&fr=y}}{大刺蕨}\index{大刺蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+scalpturata}{\textit{B. scalpturata} (Fée) Ching}  \index{Bolbitis@\textit{Bolbitis}!scalpturata@\textbf{\textit{scalpturata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅柄實蕨&T2_new_value=true&fr=y}}{紅柄實蕨}\index{紅柄實蕨@{\Song{紅柄實蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+subcordata}{\textit{B. subcordata} (Copel.) Ching}  \index{Bolbitis@\textit{Bolbitis}!subcordata@\textit{subcordata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海南實蕨&T2_new_value=true&fr=y}}{海南實蕨}\index{海南實蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+×laxireticulata}{\textit{B. ×laxireticulata} K.Iwats.}  \index{Bolbitis@\textit{Bolbitis}!×laxireticulata@\textit{×laxireticulata}}  \index{Egenolfia@\textit{Egenolfia}!laxireticulata@\textit{laxireticulata}{\\\noindent(= \textit{Bolbitis ×laxireticulata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈刺蕨&T2_new_value=true&fr=y}}{網脈刺蕨}\index{網脈刺蕨} NA$^h$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bolbitis+×nanjenensis}{\textit{B. ×nanjenensis} C.M.Kuo}  \index{Bolbitis@\textit{Bolbitis}!×nanjenensis@\textit{×nanjenensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南仁實蕨&T2_new_value=true&fr=y}}{南仁實蕨(南仁刺蕨)} \index{南仁實蕨} \index{南仁刺蕨@{南仁刺蕨(=南仁實蕨)}}\# NA$^h$
  \end{itemize}
 \item[] \textit{Ctenitis} 肋毛蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ctenitis+eatonii}{\textit{C. eatonii} (Baker) Ching}  \index{Ctenitis@\textit{Ctenitis}!eatonii@\textit{eatonii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=愛德氏肋毛蕨&T2_new_value=true&fr=y}}{愛德氏肋毛蕨}\index{愛德氏肋毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ctenitis+subglandulosa}{\textit{C. subglandulosa} (Hance) Ching}  \index{Ctenitis@\textit{Ctenitis}!subglandulosa@\textit{subglandulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=肋毛蕨&T2_new_value=true&fr=y}}{肋毛蕨}\index{肋毛蕨} LC
  \end{itemize}
 \item[] \textit{Cyrtomium} 貫眾蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+anomophyllum}{\textit{C. anomophyllum} (Zenker) Fraser-Jenk.}  \index{Cyrtomium@\textit{Cyrtomium}!anomophyllum@\textit{anomophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奇葉貫眾蕨&T2_new_value=true&fr=y}}{奇葉貫眾蕨}\index{奇葉貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+caryotideum}{\textit{C. caryotideum} (Wall. ex Hook. \& Grev.) C.Presl}  \index{Cyrtomium@\textit{Cyrtomium}!caryotideum@\textit{caryotideum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細齒貫眾蕨&T2_new_value=true&fr=y}}{細齒貫眾蕨}\index{細齒貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+devexiscapulae}{\textit{C. devexiscapulae} (Koidz.) Koidz. \& Ching}  \index{Cyrtomium@\textit{Cyrtomium}!devexiscapulae@\textit{devexiscapulae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=披針貫眾蕨&T2_new_value=true&fr=y}}{披針貫眾蕨}\index{披針貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+falcatum+subsp.+australe}{\textit{C. falcatum} (L.f.) C.Presl subsp. \textit{australe} S.Matsumoto ex S.Matsumoto \& Ebihara}  \index{Cyrtomium@\textit{Cyrtomium}!falcatum@\textit{falcatum}!subsp. australe@subsp. \textit{australe}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱海全緣貫眾蕨&T2_new_value=true&fr=y}}{濱海全緣貫眾蕨}\index{濱海全緣貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+falcatum+subsp.+falcatum}{\textit{C. falcatum} (L.f.) C.Presl subsp. \textit{falcatum}}  \index{Cyrtomium@\textit{Cyrtomium}!falcatum@\textit{falcatum}!subsp. falcatum@subsp. \textit{falcatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全緣貫眾蕨&T2_new_value=true&fr=y}}{全緣貫眾蕨}\index{全緣貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+fortunei}{\textit{C. fortunei} J.Sm.}  \index{Cyrtomium@\textit{Cyrtomium}!fortunei@\textbf{\textit{fortunei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貫眾蕨&T2_new_value=true&fr=y}}{貫眾蕨}\index{貫眾蕨@{\Song{貫眾蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+hookerianum}{\textit{C. hookerianum} (C.Presl) C.Chr.}  \index{Cyrtomium@\textit{Cyrtomium}!hookerianum@\textit{hookerianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉貫眾蕨&T2_new_value=true&fr=y}}{狹葉貫眾蕨}\index{狹葉貫眾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+macrophyllum+var.+macrophyllum}{\textit{C. macrophyllum} (Makino) Tagawa var. \textit{macrophyllum}}  \index{Cyrtomium@\textit{Cyrtomium}!macrophyllum@\textit{macrophyllum}!var. macrophyllum@\textbf{var. \textit{macrophyllum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉貫眾蕨&T2_new_value=true&fr=y}}{大葉貫眾蕨}\index{大葉貫眾蕨@{\Song{大葉貫眾蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+macrophyllum+var.+simadae}{\textit{C. macrophyllum} (Makino) Tagawa var. \textit{simadae} Tagawa}  \index{Cyrtomium@\textit{Cyrtomium}!macrophyllum@\textit{macrophyllum}!var. simadae@\textbf{var. \textit{simadae}}}  \index{Cyrtomium@\textit{Cyrtomium}!macrophyllum@\textit{macrophyllum}!var. acuminatum@var. \textit{acuminatum}{\\\noindent(=\textit{Cyrtomium macrophyllum} var. \textit{simadae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尖葉貫眾蕨&T2_new_value=true&fr=y}}{尖葉貫眾蕨}\index{尖葉貫眾蕨@{\Song{尖葉貫眾蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+nervosum}{\textit{C. nervosum} Ching \& K.H.Shing}  \index{Cyrtomium@\textit{Cyrtomium}!nervosum@\textit{nervosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=顯脈貫眾蕨&T2_new_value=true&fr=y}}{顯脈貫眾蕨}\index{顯脈貫眾蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtomium+taiwanense}{\textit{C. taiwanense} Tagawa}  \index{Cyrtomium@\textit{Cyrtomium}!taiwanense@\textbf{\textit{taiwanense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣貫眾蕨&T2_new_value=true&fr=y}}{臺灣貫眾蕨}\index{臺灣貫眾蕨@{\Song{臺灣貫眾蕨}}}\# VU
  \end{itemize}
 \item[] \textit{Dryopteris} 鱗毛蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+alpestris}{\textit{D. alpestris} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!alpestris@\textit{alpestris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺鱗毛蕨&T2_new_value=true&fr=y}}{腺鱗毛蕨}\index{腺鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+apiciflora}{\textit{D. apiciflora} (Wall. ex Mett.) O.Kuntze}  \index{Dryopteris@\textit{Dryopteris}!apiciflora@\textit{apiciflora}}  \index{Ctenitis@\textit{Ctenitis}!apiciflora@\textit{apiciflora}{\\\noindent(= \textit{Dryopteris apiciflora})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=頂囊肋毛蕨&T2_new_value=true&fr=y}}{頂囊肋毛蕨}\index{頂囊肋毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+atrata}{\textit{D. atrata} (Wall. ex Kunze) Ching}  \index{Dryopteris@\textit{Dryopteris}!atrata@\textit{atrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=暗鱗鱗毛蕨&T2_new_value=true&fr=y}}{暗鱗鱗毛蕨}\index{暗鱗鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+austriaca}{\textit{D. austriaca} (Jacq.) Wayn. ex Schinz \& Thell.}  \index{Dryopteris@\textit{Dryopteris}!austriaca@\textit{austriaca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉鱗毛蕨&T2_new_value=true&fr=y}}{闊葉鱗毛蕨}\index{闊葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+barbigera}{\textit{D. barbigera} (T.Moore ex Hook.) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!barbigera@\textit{barbigera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密毛鱗毛蕨&T2_new_value=true&fr=y}}{密毛鱗毛蕨}\index{密毛鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+cacaina}{\textit{D. cacaina} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!cacaina@\textit{cacaina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊鱗毛蕨&T2_new_value=true&fr=y}}{蓬萊鱗毛蕨}\index{蓬萊鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+championii}{\textit{D. championii} (Benth.) C.Chr. ex Ching}  \index{Dryopteris@\textit{Dryopteris}!championii@\textbf{\textit{championii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊鱗鱗毛蕨&T2_new_value=true&fr=y}}{闊鱗鱗毛蕨}\index{闊鱗鱗毛蕨@{\Song{闊鱗鱗毛蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+chrysocoma}{\textit{D. chrysocoma} (Christ) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!chrysocoma@\textit{chrysocoma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬岩蕨&T2_new_value=true&fr=y}}{擬岩蕨}\index{擬岩蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+costalisora}{\textit{D. costalisora} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!costalisora@\textit{costalisora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高鱗毛蕨&T2_new_value=true&fr=y}}{能高鱗毛蕨}\index{能高鱗毛蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+cycadina}{\textit{D. cycadina} (Franch. \& Sav.) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!cycadina@\textit{cycadina}}  \index{Dryopteris@\textit{Dryopteris}!atrata@\textit{atrata}{\\\noindent(= \textit{Dryopteris cycadina})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桫欏鱗毛蕨&T2_new_value=true&fr=y}}{桫欏鱗毛蕨}\index{桫欏鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+decipiens}{\textit{D. decipiens} (Hook.) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!decipiens@\textbf{\textit{decipiens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=迷人鱗毛蕨&T2_new_value=true&fr=y}}{迷人鱗毛蕨}\index{迷人鱗毛蕨@{\Song{迷人鱗毛蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+dickinsii}{\textit{D. dickinsii} (Franch. \& Sav.) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!dickinsii@\textbf{\textit{dickinsii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=遠軸鱗毛蕨&T2_new_value=true&fr=y}}{遠軸鱗毛蕨}\index{遠軸鱗毛蕨@{\Song{遠軸鱗毛蕨}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+diffracta}{\textit{D. diffracta} (Baker) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!diffracta@\textit{diffracta}}  \index{Acrorumobra@\textit{Acrorumobra}!diffracta@\textit{diffracta}{\\\noindent(= \textit{Dryopteris diffracta})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=彎柄假複葉耳蕨&T2_new_value=true&fr=y}}{彎柄假複葉耳蕨}\index{彎柄假複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+enneaphylla+var.+enneaphylla}{\textit{D. enneaphylla} (Baker) C.Chr. var. \textit{enneaphylla}}  \index{Dryopteris@\textit{Dryopteris}!enneaphylla@\textit{enneaphylla}!var. enneaphylla@var. \textit{enneaphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=頂羽鱗毛蕨&T2_new_value=true&fr=y}}{頂羽鱗毛蕨}\index{頂羽鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+enneaphylla+var.+pseudosieboldii}{\textit{D. enneaphylla} (Baker) C.Chr. var. \textit{pseudosieboldii} (Hayata) Tagawa \& K.Iwats.}  \index{Dryopteris@\textit{Dryopteris}!enneaphylla@\textit{enneaphylla}!var. pseudosieboldii@var. \textit{pseudosieboldii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大頂羽鱗毛蕨&T2_new_value=true&fr=y}}{大頂羽鱗毛蕨}\index{大頂羽鱗毛蕨}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+erythrosora}{\textit{D. erythrosora} (D.C.Eaton) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!erythrosora@\textbf{\textit{erythrosora}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅蓋鱗毛蕨&T2_new_value=true&fr=y}}{紅蓋鱗毛蕨}\index{紅蓋鱗毛蕨@{\Song{紅蓋鱗毛蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+formosana}{\textit{D. formosana} (Christ) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鱗毛蕨&T2_new_value=true&fr=y}}{臺灣鱗毛蕨}\index{臺灣鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+fructuosa}{\textit{D. fructuosa} (Christ) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!fructuosa@\textit{fructuosa}}  \index{Dryopteris@\textit{Dryopteris}!hypophlebia@\textit{hypophlebia}{\\\noindent(= \textit{Dryopteris fructuosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=深山鱗毛蕨&T2_new_value=true&fr=y}}{深山鱗毛蕨}\index{深山鱗毛蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+hasseltii}{\textit{D. hasseltii} (Blume) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!hasseltii@\textit{hasseltii}}  \index{Acrorumobra@\textit{Acrorumobra}!hasseltii@\textit{hasseltii}{\\\noindent(= \textit{Dryopteris hasseltii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=哈氏假複葉耳蕨&T2_new_value=true&fr=y}}{哈氏假複葉耳蕨}\index{哈氏假複葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+hendersoni}{\textit{D. hendersoni} (Bedd.) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!hendersoni@\textit{hendersoni}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小苞鱗毛蕨&T2_new_value=true&fr=y}}{小苞鱗毛蕨}\index{小苞鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+huangshanensis}{\textit{D. huangshanensis} Ching}  \index{Dryopteris@\textit{Dryopteris}!huangshanensis@\textit{huangshanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃山鱗毛蕨&T2_new_value=true&fr=y}}{黃山鱗毛蕨}\index{黃山鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+indusiata}{\textit{D. indusiata} (Makino) Makino \& Yamam. ex Yamam.}  \index{Dryopteris@\textit{Dryopteris}!indusiata@\textit{indusiata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=平行鱗毛蕨&T2_new_value=true&fr=y}}{平行鱗毛蕨}\index{平行鱗毛蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+integriloba}{\textit{D. integriloba} C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!integriloba@\textit{integriloba}}  \index{Dryopteris@\textit{Dryopteris}!subintegriloba@\textit{subintegriloba}{\\\noindent(= \textit{Dryopteris integriloba})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊紅苞鱗毛蕨&T2_new_value=true&fr=y}}{蓬萊紅苞鱗毛蕨(蓬萊鱗毛蕨)} \index{蓬萊紅苞鱗毛蕨} \index{蓬萊鱗毛蕨@{蓬萊鱗毛蕨(=蓬萊紅苞鱗毛蕨)}}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+kawakamii}{\textit{D. kawakamii} Hayata}  \index{Dryopteris@\textit{Dryopteris}!kawakamii@\textit{kawakamii}}  \index{Ctenitis@\textit{Ctenitis}!kawakamii@\textit{kawakamii}{\\\noindent(= \textit{Dryopteris kawakamii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=川上氏肋毛蕨&T2_new_value=true&fr=y}}{川上氏肋毛蕨(川上氏擬鱗毛蕨)} \index{川上氏肋毛蕨} \index{川上氏擬鱗毛蕨@{川上氏擬鱗毛蕨(=川上氏肋毛蕨)}}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+kinkiensis}{\textit{D. kinkiensis} Koidz. ex Tagawa}  \index{Dryopteris@\textit{Dryopteris}!kinkiensis@\textbf{\textit{kinkiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=近畿鱗毛蕨&T2_new_value=true&fr=y}}{近畿鱗毛蕨}\index{近畿鱗毛蕨@{\Song{近畿鱗毛蕨}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+komarovii}{\textit{D. komarovii} Kossinsky}  \index{Dryopteris@\textit{Dryopteris}!komarovii@\textit{komarovii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=近多鱗鱗毛蕨&T2_new_value=true&fr=y}}{近多鱗鱗毛蕨}\index{近多鱗鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+kwanzanensis}{\textit{D. kwanzanensis} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!kwanzanensis@\textit{kwanzanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山鱗毛蕨&T2_new_value=true&fr=y}}{關山鱗毛蕨(擬倒鱗鱗毛蕨)} \index{關山鱗毛蕨} \index{擬倒鱗鱗毛蕨@{擬倒鱗鱗毛蕨(=關山鱗毛蕨)}} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+labordei}{\textit{D. labordei} (Christ) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!labordei@\textit{labordei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏葉鱗毛蕨&T2_new_value=true&fr=y}}{疏葉鱗毛蕨}\index{疏葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+lacera}{\textit{D. lacera} (Thunb.) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!lacera@\textbf{\textit{lacera}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二型鱗毛蕨&T2_new_value=true&fr=y}}{二型鱗毛蕨}\index{二型鱗毛蕨@{\Song{二型鱗毛蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+lachoongensis}{\textit{D. lachoongensis} (Bedd.) B.K.Nayar \& S.Kaur}  \index{Dryopteris@\textit{Dryopteris}!lachoongensis@\textit{lachoongensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=脈紋鱗毛蕨&T2_new_value=true&fr=y}}{脈紋鱗毛蕨}\index{脈紋鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+latibasis}{\textit{D. latibasis} Ching}  \index{Dryopteris@\textit{Dryopteris}!latibasis@\textit{latibasis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊基鱗毛蕨&T2_new_value=true&fr=y}}{闊基鱗毛蕨}\index{闊基鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+lepidopoda}{\textit{D. lepidopoda} Hayata}  \index{Dryopteris@\textit{Dryopteris}!lepidopoda@\textit{lepidopoda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉鱗毛蕨&T2_new_value=true&fr=y}}{厚葉鱗毛蕨}\index{厚葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+marginata}{\textit{D. marginata} (Wall. ex Christ) Christ}  \index{Dryopteris@\textit{Dryopteris}!marginata@\textit{marginata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三角葉鱗毛蕨&T2_new_value=true&fr=y}}{三角葉鱗毛蕨}\index{三角葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+maximowicziana}{\textit{D. maximowicziana} (Miq.) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!maximowicziana@\textbf{\textit{maximowicziana}}}  \index{Ctenitis@\textit{Ctenitis}!maximowicziana@\textit{maximowicziana}{\\\noindent(= \textit{Dryopteris maximowicziana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白鱗肋毛蕨&T2_new_value=true&fr=y}}{白鱗肋毛蕨}\index{白鱗肋毛蕨@{\Song{白鱗肋毛蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+melanocarpa}{\textit{D. melanocarpa} Hayata}  \index{Dryopteris@\textit{Dryopteris}!melanocarpa@\textit{melanocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉鱗毛蕨  &T2_new_value=true&fr=y}}{長葉鱗毛蕨  (黑孢鱗毛蕨)} \index{長葉鱗毛蕨  } \index{黑孢鱗毛蕨@{黑孢鱗毛蕨(=長葉鱗毛蕨  )}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+namegatae}{\textit{D. namegatae} (Sa.Kurata) Sa.Kurata}  \index{Dryopteris@\textit{Dryopteris}!namegatae@\textbf{\textit{namegatae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑鱗遠軸鱗毛蕨&T2_new_value=true&fr=y}}{黑鱗遠軸鱗毛蕨}\index{黑鱗遠軸鱗毛蕨@{\Song{黑鱗遠軸鱗毛蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+nidus}{\textit{D. nidus} (Baker) Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!nidus@\textit{nidus}}  \index{Ctenitis@\textit{Ctenitis}!nidus@\textit{nidus}{\\\noindent(= \textit{Dryopteris nidus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山肋毛蕨&T2_new_value=true&fr=y}}{玉山肋毛蕨}\index{玉山肋毛蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+paleolata}{\textit{D. paleolata} (Pic.Serm.) Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!paleolata@\textit{paleolata}}  \index{Acrophorus@\textit{Acrophorus}!stipellatus@\textit{stipellatus}{\\\noindent(= \textit{Dryopteris paleolata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=魚鱗蕨&T2_new_value=true&fr=y}}{魚鱗蕨}\index{魚鱗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+peranema}{\textit{D. peranema} Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!peranema@\textit{peranema}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柄囊蕨&T2_new_value=true&fr=y}}{柄囊蕨}\index{柄囊蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+polita}{\textit{D. polita} Rosenst.}  \index{Dryopteris@\textit{Dryopteris}!polita@\textit{polita}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東鱗毛蕨&T2_new_value=true&fr=y}}{臺東鱗毛蕨}\index{臺東鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+pseudocaenopteris}{\textit{D. pseudocaenopteris} (Kunze) Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!pseudocaenopteris@\textbf{\textit{pseudocaenopteris}}}  \index{Diacalpe@\textit{Diacalpe}!aspidioides@\textit{aspidioides}{\\\noindent(= \textit{Dryopteris pseudocaenopteris})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅線蕨&T2_new_value=true&fr=y}}{紅線蕨}\index{紅線蕨@{\Song{紅線蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+pseudolunanensis}{\textit{D. pseudolunanensis} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!pseudolunanensis@\textit{pseudolunanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬桫欏鱗毛蕨&T2_new_value=true&fr=y}}{擬桫欏鱗毛蕨}\index{擬桫欏鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+redactopinnata}{\textit{D. redactopinnata} Soumen K.Basu \& Panigrahi}  \index{Dryopteris@\textit{Dryopteris}!redactopinnata@\textit{redactopinnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藏布鱗毛蕨&T2_new_value=true&fr=y}}{藏布鱗毛蕨}\index{藏布鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+reflexosquamata}{\textit{D. reflexosquamata} Hayata}  \index{Dryopteris@\textit{Dryopteris}!reflexosquamata@\textit{reflexosquamata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=逆鱗鱗毛蕨&T2_new_value=true&fr=y}}{逆鱗鱗毛蕨}\index{逆鱗鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+ryo-itoana}{\textit{D. ryo-itoana} Sa.Kurata}  \index{Dryopteris@\textit{Dryopteris}!ryo-itoana@\textbf{\textit{ryo-itoana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬羽鱗毛蕨&T2_new_value=true&fr=y}}{寬羽鱗毛蕨(闊羽鱗毛蕨)} \index{寬羽鱗毛蕨@{\Song{寬羽鱗毛蕨}}} \index{闊羽鱗毛蕨@{\Song{闊羽鱗毛蕨(=寬羽鱗毛蕨)}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+scottii}{\textit{D. scottii} (Bedd.) Ching}  \index{Dryopteris@\textit{Dryopteris}!scottii@\textit{scottii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=史氏鱗毛蕨&T2_new_value=true&fr=y}}{史氏鱗毛蕨}\index{史氏鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+serratodentata}{\textit{D. serratodentata} (Bedd.) Hayata}  \index{Dryopteris@\textit{Dryopteris}!serratodentata@\textit{serratodentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鋸齒葉鱗毛蕨&T2_new_value=true&fr=y}}{鋸齒葉鱗毛蕨}\index{鋸齒葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+sinofibrillosa}{\textit{D. sinofibrillosa} Ching}  \index{Dryopteris@\textit{Dryopteris}!sinofibrillosa@\textit{sinofibrillosa}}  \index{Dryopteris@\textit{Dryopteris}!fibrillosa@\textit{fibrillosa}{\\\noindent(= \textit{Dryopteris sinofibrillosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密鱗鱗毛蕨&T2_new_value=true&fr=y}}{密鱗鱗毛蕨}\index{密鱗鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+sordidipes}{\textit{D. sordidipes} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!sordidipes@\textit{sordidipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=落鱗鱗毛蕨&T2_new_value=true&fr=y}}{落鱗鱗毛蕨}\index{落鱗鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+sparsa}{\textit{D. sparsa} (D.Don) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!sparsa@\textit{sparsa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉鱗毛蕨&T2_new_value=true&fr=y}}{長葉鱗毛蕨}\index{長葉鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+squamiseta}{\textit{D. squamiseta} (Hook.) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!squamiseta@\textit{squamiseta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山鱗毛蕨&T2_new_value=true&fr=y}}{阿里山鱗毛蕨}\index{阿里山鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+stenolepis}{\textit{D. stenolepis} (Baker) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!stenolepis@\textit{stenolepis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹鱗鱗毛蕨&T2_new_value=true&fr=y}}{狹鱗鱗毛蕨}\index{狹鱗鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+subatrata}{\textit{D. subatrata} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!subatrata@\textit{subatrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉鱗毛蕨&T2_new_value=true&fr=y}}{細葉鱗毛蕨}\index{細葉鱗毛蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+subexaltata}{\textit{D. subexaltata} (Christ) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!subexaltata@\textit{subexaltata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏鱗毛蕨&T2_new_value=true&fr=y}}{早田氏鱗毛蕨}\index{早田氏鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+sublacera}{\textit{D. sublacera} Christ}  \index{Dryopteris@\textit{Dryopteris}!sublacera@\textit{sublacera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亞二型鱗毛蕨&T2_new_value=true&fr=y}}{亞二型鱗毛蕨}\index{亞二型鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+subtriangularis}{\textit{D. subtriangularis} (C.Hope) C.Chr.}  \index{Dryopteris@\textit{Dryopteris}!subtriangularis@\textit{subtriangularis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅苞鱗毛蕨&T2_new_value=true&fr=y}}{紅苞鱗毛蕨}\index{紅苞鱗毛蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+tenuipes}{\textit{D. tenuipes} (Rosenst.) Seriz.}  \index{Dryopteris@\textit{Dryopteris}!tenuipes@\textit{tenuipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=落葉鱗毛蕨&T2_new_value=true&fr=y}}{落葉鱗毛蕨}\index{落葉鱗毛蕨}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+toyamae}{\textit{D. toyamae} Tagawa}  \index{Dryopteris@\textit{Dryopteris}!toyamae@\textbf{\textit{toyamae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=外山氏鱗毛蕨&T2_new_value=true&fr=y}}{外山氏鱗毛蕨}\index{外山氏鱗毛蕨@{\Song{外山氏鱗毛蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+varia}{\textit{D. varia} (L.) Kuntze}  \index{Dryopteris@\textit{Dryopteris}!varia@\textit{varia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南海鱗毛蕨&T2_new_value=true&fr=y}}{南海鱗毛蕨}\index{南海鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+wallichiana+subsp.+nepalensis}{\textit{D. wallichiana} (Spreng.) Hyl. subsp. \textit{nepalensis} Fraser-Jenk.}  \index{Dryopteris@\textit{Dryopteris}!wallichiana@\textit{wallichiana}!subsp. nepalensis@subsp. \textit{nepalensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尼泊爾鱗毛蕨&T2_new_value=true&fr=y}}{尼泊爾鱗毛蕨}\index{尼泊爾鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+wallichiana+subsp.+wallichiana}{\textit{D. wallichiana} (Spreng.) Hyl. subsp. \textit{wallichiana}}  \index{Dryopteris@\textit{Dryopteris}!wallichiana@\textit{wallichiana}!subsp. wallichiana@subsp. \textit{wallichiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓦氏鱗毛蕨&T2_new_value=true&fr=y}}{瓦氏鱗毛蕨}\index{瓦氏鱗毛蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+wuzhaohongii}{\textit{D. wuzhaohongii} Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!wuzhaohongii@\textbf{\textit{wuzhaohongii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大孢魚鱗蕨&T2_new_value=true&fr=y}}{大孢魚鱗蕨}\index{大孢魚鱗蕨@{\Song{大孢魚鱗蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+yoroii}{\textit{D. yoroii} Seriz.}  \index{Dryopteris@\textit{Dryopteris}!yoroii@\textbf{\textit{yoroii}}}  \index{Acrorumobra@\textit{Acrorumobra}!yoroi@\textit{yoroi}{\\\noindent(= \textit{Dryopteris yoroii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=上先型鱗毛蕨&T2_new_value=true&fr=y}}{上先型鱗毛蕨(玉山假複葉耳蕨)} \index{上先型鱗毛蕨@{\Song{上先型鱗毛蕨}}} \index{玉山假複葉耳蕨@{\Song{玉山假複葉耳蕨(=上先型鱗毛蕨)}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+×holttumii}{\textit{D. ×holttumii} Li Bing Zhang}  \index{Dryopteris@\textit{Dryopteris}!×holttumii@\textit{×holttumii}}  \index{Dryopsis@\textit{Dryopsis}!×fauriei@\textit{×fauriei}{\\\noindent(= \textit{Dryopteris ×holttumii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=傅氏擬鱗毛蕨&T2_new_value=true&fr=y}}{傅氏擬鱗毛蕨}\index{傅氏擬鱗毛蕨}\# NA$^h$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dryopteris+×subreflexipinna}{\textit{D. ×subreflexipinna} Ogata}  \index{Dryopteris@\textit{Dryopteris}!×subreflexipinna@\textit{×subreflexipinna}}  \index{Acrorumohra@\textit{Acrorumohra}!subreflexipinna@\textit{subreflexipinna}{\\\noindent(= \textit{Dryopteris ×subreflexipinna})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=微彎假複葉耳蕨&T2_new_value=true&fr=y}}{微彎假複葉耳蕨}\index{微彎假複葉耳蕨}\# NA$^h$
  \end{itemize}
 \item[] \textit{Elaphoglossum} 舌蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+angulatum}{\textit{E. angulatum} (Blume) T.Moore}  \index{Elaphoglossum@\textit{Elaphoglossum}!angulatum@\textit{angulatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=爪哇舌蕨&T2_new_value=true&fr=y}}{爪哇舌蕨}\index{爪哇舌蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+callifolium}{\textit{E. callifolium} (Blume) T.Moore}  \index{Elaphoglossum@\textit{Elaphoglossum}!callifolium@\textbf{\textit{callifolium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳頭舌蕨&T2_new_value=true&fr=y}}{銳頭舌蕨}\index{銳頭舌蕨@{\Song{銳頭舌蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+commutatum}{\textit{E. commutatum} (Mett. ex Kuhn) Alderw.}  \index{Elaphoglossum@\textit{Elaphoglossum}!commutatum@\textbf{\textit{commutatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉舌蕨&T2_new_value=true&fr=y}}{大葉舌蕨}\index{大葉舌蕨@{\Song{大葉舌蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+luzonicum}{\textit{E. luzonicum} Copel.}  \index{Elaphoglossum@\textit{Elaphoglossum}!luzonicum@\textbf{\textit{luzonicum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣舌蕨&T2_new_value=true&fr=y}}{臺灣舌蕨}\index{臺灣舌蕨@{\Song{臺灣舌蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+marginatum}{\textit{E. marginatum} (Wall. ex Fée) T.Moore}  \index{Elaphoglossum@\textit{Elaphoglossum}!marginatum@\textit{marginatum}}  \index{Elaphoglossum@\textit{Elaphoglossum}!conforme@\textit{conforme}{\\\noindent(= \textit{Elaphoglossum marginatum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂葉舌蕨&T2_new_value=true&fr=y}}{垂葉舌蕨(阿里山舌蕨)} \index{垂葉舌蕨} \index{阿里山舌蕨@{阿里山舌蕨(=垂葉舌蕨)}}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaphoglossum+yoshinagae}{\textit{E. yoshinagae} (Yatabe) Makino}  \index{Elaphoglossum@\textit{Elaphoglossum}!yoshinagae@\textit{yoshinagae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=舌蕨&T2_new_value=true&fr=y}}{舌蕨}\index{舌蕨} LC
  \end{itemize}
 \item[] \textit{Lastreopsis} 金毛蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lastreopsis+tenera}{\textit{L. tenera} (R.Br.) Tindale}  \index{Lastreopsis@\textit{Lastreopsis}!tenera@\textit{tenera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金毛蕨&T2_new_value=true&fr=y}}{金毛蕨}\index{金毛蕨} NT
  \end{itemize}
 \item[] \textit{Pleocnemia} 黃腺羽蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pleocnemia+rufinervis}{\textit{P. rufinervis} (Hayata) Nakai}  \index{Pleocnemia@\textit{Pleocnemia}!rufinervis@\textit{rufinervis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈突齒蕨&T2_new_value=true&fr=y}}{網脈突齒蕨}\index{網脈突齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pleocnemia+winitii}{\textit{P. winitii} Holttum}  \index{Pleocnemia@\textit{Pleocnemia}!winitii@\textit{winitii}}  \index{Pleocnemia@\textit{Pleocnemia}!cumingiana@\textit{cumingiana}{\\\noindent(= \textit{Pleocnemia winitii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃腺羽蕨&T2_new_value=true&fr=y}}{黃腺羽蕨}\index{黃腺羽蕨} LC
  \end{itemize}
 \item[] \textit{Polystichum} 耳蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+acanthophyllum}{\textit{P. acanthophyllum} (Franch.) Christ}  \index{Polystichum@\textit{Polystichum}!acanthophyllum@\textit{acanthophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=針葉耳蕨&T2_new_value=true&fr=y}}{針葉耳蕨}\index{針葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+acutidens}{\textit{P. acutidens} Christ}  \index{Polystichum@\textit{Polystichum}!acutidens@\textit{acutidens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東耳蕨&T2_new_value=true&fr=y}}{臺東耳蕨}\index{臺東耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+anomalum}{\textit{P. anomalum} (Hook. \& Arn.) J.Sm.}  \index{Polystichum@\textit{Polystichum}!anomalum@\textit{anomalum}}  \index{Polystichum@\textit{Polystichum}!eximium@\textit{eximium}{\\\noindent(= \textit{Polystichum anomalum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山耳蕨&T2_new_value=true&fr=y}}{阿里山耳蕨}\index{阿里山耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+atkinsonii}{\textit{P. atkinsonii} Bedd.}  \index{Polystichum@\textit{Polystichum}!atkinsonii@\textit{atkinsonii}}  \index{Polystichum@\textit{Polystichum}!morii@\textit{morii}{\\\noindent(= \textit{Polystichum atkinsonii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小芽苞耳蕨&T2_new_value=true&fr=y}}{小芽苞耳蕨(玉山耳蕨)} \index{小芽苞耳蕨} \index{玉山耳蕨@{玉山耳蕨(=小芽苞耳蕨)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+attenuatum}{\textit{P. attenuatum} Tagawa \& K.Iwats.}  \index{Polystichum@\textit{Polystichum}!attenuatum@\textbf{\textit{attenuatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長羽芽苞耳蕨&T2_new_value=true&fr=y}}{長羽芽苞耳蕨}\index{長羽芽苞耳蕨@{\Song{長羽芽苞耳蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+biaristatum}{\textit{P. biaristatum} (Blume) Moore}  \index{Polystichum@\textit{Polystichum}!biaristatum@\textit{biaristatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二尖耳蕨&T2_new_value=true&fr=y}}{二尖耳蕨}\index{二尖耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+capillipes}{\textit{P. capillipes} (Baker) Diels}  \index{Polystichum@\textit{Polystichum}!capillipes@\textbf{\textit{capillipes}}}  \index{Polystichum@\textit{Polystichum}!inaense@\textit{inaense}{\\\noindent(= \textit{Polystichum capillipes})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小耳蕨&T2_new_value=true&fr=y}}{小耳蕨}\index{小耳蕨@{\Song{小耳蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+chunii}{\textit{P. chunii} Ching}  \index{Polystichum@\textit{Polystichum}!chunii@\textbf{\textit{chunii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=陳氏耳蕨&T2_new_value=true&fr=y}}{陳氏耳蕨}\index{陳氏耳蕨@{\Song{陳氏耳蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+deltodon}{\textit{P. deltodon} (Baker) Diels}  \index{Polystichum@\textit{Polystichum}!deltodon@\textit{deltodon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=對生耳蕨&T2_new_value=true&fr=y}}{對生耳蕨}\index{對生耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+formosanum}{\textit{P. formosanum} Rosenst.}  \index{Polystichum@\textit{Polystichum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣耳蕨&T2_new_value=true&fr=y}}{臺灣耳蕨}\index{臺灣耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+fraxinellum}{\textit{P. fraxinellum} (Christ) Diels}  \index{Polystichum@\textit{Polystichum}!fraxinellum@\textbf{\textit{fraxinellum}}}  \index{Cyrtogonellum@\textit{Cyrtogonellum}!fraxinellum@\textit{fraxinellum}{\\\noindent(= \textit{Polystichum fraxinellum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈耳蕨&T2_new_value=true&fr=y}}{網脈耳蕨(柳葉蕨)} \index{網脈耳蕨@{\Song{網脈耳蕨}}} \index{柳葉蕨@{\Song{柳葉蕨(=網脈耳蕨)}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+glaciale}{\textit{P. glaciale} Christ}  \index{Polystichum@\textit{Polystichum}!glaciale@\textbf{\textit{glaciale}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉龍蕨&T2_new_value=true&fr=y}}{玉龍蕨}\index{玉龍蕨@{\Song{玉龍蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+grandifrons}{\textit{P. grandifrons} C.Chr.}  \index{Polystichum@\textit{Polystichum}!grandifrons@\textbf{\textit{grandifrons}}}  \index{Polystichum@\textit{Polystichum}!kiusiuense@\textit{kiusiuense}{\\\noindent(= \textit{Polystichum grandifrons})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=九州耳蕨&T2_new_value=true&fr=y}}{九州耳蕨}\index{九州耳蕨@{\Song{九州耳蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+hancockii}{\textit{P. hancockii} (Hance) Diels}  \index{Polystichum@\textit{Polystichum}!hancockii@\textit{hancockii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=韓氏耳蕨&T2_new_value=true&fr=y}}{韓氏耳蕨}\index{韓氏耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+hecatopterum}{\textit{P. hecatopterum} Diels}  \index{Polystichum@\textit{Polystichum}!hecatopterum@\textit{hecatopterum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鋸齒葉耳蕨&T2_new_value=true&fr=y}}{鋸齒葉耳蕨}\index{鋸齒葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+herbaceum}{\textit{P. herbaceum} Ching \& Z.Y.Liu}  \index{Polystichum@\textit{Polystichum}!herbaceum@\textbf{\textit{herbaceum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=草葉耳蕨&T2_new_value=true&fr=y}}{草葉耳蕨}\index{草葉耳蕨@{\Song{草葉耳蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+lachenense}{\textit{P. lachenense} (Hook.) Bedd.}  \index{Polystichum@\textit{Polystichum}!lachenense@\textit{lachenense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山耳蕨&T2_new_value=true&fr=y}}{高山耳蕨}\index{高山耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+lepidocaulon}{\textit{P. lepidocaulon} (Hook.) J.Sm.}  \index{Polystichum@\textit{Polystichum}!lepidocaulon@\textit{lepidocaulon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鞭葉耳蕨&T2_new_value=true&fr=y}}{鞭葉耳蕨}\index{鞭葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+luctuosum}{\textit{P. luctuosum} (Kunze) T.Moore}  \index{Polystichum@\textit{Polystichum}!luctuosum@\textit{luctuosum}}  \index{Polystichum@\textit{Polystichum}!tsus-simense@\textit{tsus-simense}{\\\noindent(= \textit{Polystichum luctuosum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬祖耳蕨&T2_new_value=true&fr=y}}{馬祖耳蕨(對馬耳蕨)} \index{馬祖耳蕨} \index{對馬耳蕨@{對馬耳蕨(=馬祖耳蕨)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+manmeiense}{\textit{P. manmeiense} (Christ.) Nakaike}  \index{Polystichum@\textit{Polystichum}!manmeiense@\textit{manmeiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐮葉耳蕨&T2_new_value=true&fr=y}}{鐮葉耳蕨}\index{鐮葉耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+mucronifolium}{\textit{P. mucronifolium} (Blume) Nayar \& Kaur}  \index{Polystichum@\textit{Polystichum}!mucronifolium@\textit{mucronifolium}}  \index{Polystichum@\textit{Polystichum}!tacticopterum@\textit{tacticopterum}{\\\noindent(= \textit{Polystichum mucronifolium})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=兒玉氏耳蕨&T2_new_value=true&fr=y}}{兒玉氏耳蕨}\index{兒玉氏耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+neo-lobatum}{\textit{P. neo-lobatum} Nakai}  \index{Polystichum@\textit{Polystichum}!neo-lobatum@\textbf{\textit{neo-lobatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=硬葉耳蕨&T2_new_value=true&fr=y}}{硬葉耳蕨}\index{硬葉耳蕨@{\Song{硬葉耳蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+nepalense}{\textit{P. nepalense} (Spreng.) C.Chr.}  \index{Polystichum@\textit{Polystichum}!nepalense@\textit{nepalense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=軟骨耳蕨&T2_new_value=true&fr=y}}{軟骨耳蕨}\index{軟骨耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+obliquum}{\textit{P. obliquum} (D.Don) Moore}  \index{Polystichum@\textit{Polystichum}!obliquum@\textbf{\textit{obliquum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=知本耳蕨&T2_new_value=true&fr=y}}{知本耳蕨}\index{知本耳蕨@{\Song{知本耳蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+parvipinnulum}{\textit{P. parvipinnulum} Tagawa}  \index{Polystichum@\textit{Polystichum}!parvipinnulum@\textit{parvipinnulum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尖葉耳蕨&T2_new_value=true&fr=y}}{尖葉耳蕨}\index{尖葉耳蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+piceopaleaceum}{\textit{P. piceopaleaceum} Tagawa}  \index{Polystichum@\textit{Polystichum}!piceopaleaceum@\textit{piceopaleaceum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑鱗耳蕨&T2_new_value=true&fr=y}}{黑鱗耳蕨}\index{黑鱗耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+prescottianum}{\textit{P. prescottianum} (Wall. ex Mett.) Moore}  \index{Polystichum@\textit{Polystichum}!prescottianum@\textbf{\textit{prescottianum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖耳蕨&T2_new_value=true&fr=y}}{南湖耳蕨}\index{南湖耳蕨@{\Song{南湖耳蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+prionolepis}{\textit{P. prionolepis} Hayata}  \index{Polystichum@\textit{Polystichum}!prionolepis@\textit{prionolepis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鋸葉耳蕨&T2_new_value=true&fr=y}}{鋸葉耳蕨}\index{鋸葉耳蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+sinense}{\textit{P. sinense} (Christ) H.Christ}  \index{Polystichum@\textit{Polystichum}!sinense@\textit{sinense}}  \index{Polystichum@\textit{Polystichum}!wilsonii@\textit{wilsonii}{\\\noindent(= \textit{Polystichum sinense})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=福山氏耳蕨&T2_new_value=true&fr=y}}{福山氏耳蕨}\index{福山氏耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+stenophyllum}{\textit{P. stenophyllum} Christ}  \index{Polystichum@\textit{Polystichum}!stenophyllum@\textit{stenophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=芽胞耳蕨&T2_new_value=true&fr=y}}{芽胞耳蕨}\index{芽胞耳蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+taizhongense}{\textit{P. taizhongense} H.S.Kung}  \index{Polystichum@\textit{Polystichum}!taizhongense@\textbf{\textit{taizhongense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺中耳蕨&T2_new_value=true&fr=y}}{臺中耳蕨}\index{臺中耳蕨@{\Song{臺中耳蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+tenuius}{\textit{P. tenuius} (Ching) Li Bing Zhang}  \index{Polystichum@\textit{Polystichum}!tenuius@\textbf{\textit{tenuius}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=離脈柳葉蕨&T2_new_value=true&fr=y}}{離脈柳葉蕨}\index{離脈柳葉蕨@{\Song{離脈柳葉蕨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+thomsonii}{\textit{P. thomsonii} (Hook.f.) Bedd.}  \index{Polystichum@\textit{Polystichum}!thomsonii@\textit{thomsonii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾葉耳蕨&T2_new_value=true&fr=y}}{尾葉耳蕨}\index{尾葉耳蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polystichum+xiphophyllum}{\textit{P. xiphophyllum} (Baker) Diels}  \index{Polystichum@\textit{Polystichum}!xiphophyllum@\textbf{\textit{xiphophyllum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山耳蕨&T2_new_value=true&fr=y}}{關山耳蕨}\index{關山耳蕨@{\Song{關山耳蕨}}} EN
  \end{itemize}
  \end{itemize}
