
  \begin{itemize}
 \item[] \textit{Diospyros} 柿樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+blancoi}{\textit{D. blancoi} A. DC.}  \index{Diospyros@\textit{Diospyros}!blancoi@\textit{blancoi}}  \index{Diospyros@\textit{Diospyros}!philippensis@\textit{philippensis}{\\\noindent(= \textit{Diospyros blancoi})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛柿&T2_new_value=true&fr=y}}{毛柿}\index{毛柿} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+eriantha}{\textit{D. eriantha} Champ. ex Benth.}  \index{Diospyros@\textit{Diospyros}!eriantha@\textit{eriantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=軟毛柿&T2_new_value=true&fr=y}}{軟毛柿}\index{軟毛柿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+ferrea}{\textit{D. ferrea} (Willd.) Bakh.f.}  \index{Diospyros@\textit{Diospyros}!ferrea@\textbf{\textit{ferrea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=象牙樹&T2_new_value=true&fr=y}}{象牙樹}\index{象牙樹@{\Song{象牙樹}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+japonica}{\textit{D. japonica} Siebold \& Zucc.}  \index{Diospyros@\textit{Diospyros}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山柿&T2_new_value=true&fr=y}}{山柿}\index{山柿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+kotoensis}{\textit{D. kotoensis} T.Yamaz.}  \index{Diospyros@\textit{Diospyros}!kotoensis@\textbf{\textit{kotoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼柿&T2_new_value=true&fr=y}}{蘭嶼柿}\index{蘭嶼柿@{\Song{蘭嶼柿}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+maritima}{\textit{D. maritima} Blume}  \index{Diospyros@\textit{Diospyros}!maritima@\textit{maritima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃心柿&T2_new_value=true&fr=y}}{黃心柿}\index{黃心柿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+morrisiana}{\textit{D. morrisiana} Hance}  \index{Diospyros@\textit{Diospyros}!morrisiana@\textit{morrisiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山紅柿&T2_new_value=true&fr=y}}{山紅柿}\index{山紅柿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+oldhamii}{\textit{D. oldhamii} Maxim.}  \index{Diospyros@\textit{Diospyros}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=俄氏柿&T2_new_value=true&fr=y}}{俄氏柿}\index{俄氏柿} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+rhombifolia}{\textit{D. rhombifolia} Hemsl.}  \index{Diospyros@\textit{Diospyros}!rhombifolia@\textbf{\textit{rhombifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菱葉柿&T2_new_value=true&fr=y}}{菱葉柿}\index{菱葉柿@{\Song{菱葉柿}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diospyros+vaccinioides}{\textit{D. vaccinioides} Lindl.}  \index{Diospyros@\textit{Diospyros}!vaccinioides@\textit{vaccinioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=楓港柿&T2_new_value=true&fr=y}}{楓港柿}\index{楓港柿} DD
  \end{itemize}
  \end{itemize}
