
  \begin{itemize}
 \item[] \textit{Elaeocarpus} 杜英屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+argenteus}{\textit{E. argenteus} Merr.}  \index{Elaeocarpus@\textit{Elaeocarpus}!argenteus@\textit{argenteus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺葉杜英&T2_new_value=true&fr=y}}{腺葉杜英}\index{腺葉杜英} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+japonicus}{\textit{E. japonicus} Siebold \& Zucc.}  \index{Elaeocarpus@\textit{Elaeocarpus}!japonicus@\textit{japonicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薯豆&T2_new_value=true&fr=y}}{薯豆}\index{薯豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+multiflorus}{\textit{E. multiflorus} (Turcz.) Fern.-Vill.}  \index{Elaeocarpus@\textit{Elaeocarpus}!multiflorus@\textbf{\textit{multiflorus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繁花薯豆&T2_new_value=true&fr=y}}{繁花薯豆}\index{繁花薯豆@{\Song{繁花薯豆}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+sphaericus+var.+hayatae}{\textit{E. sphaericus} (Gaertn.) Schumann var. \textit{hayatae} (Kaneh. \& Sasaki) C.E.Chang}  \index{Elaeocarpus@\textit{Elaeocarpus}!sphaericus@\textit{sphaericus}!var. hayatae@var. \textit{hayatae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球果杜英&T2_new_value=true&fr=y}}{球果杜英}\index{球果杜英}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+sylvestris+var.+lanyuensis}{\textit{E. sylvestris} (Lour.) Poir. var. \textit{lanyuensis} (C.E.Chang) C.E.Chang}  \index{Elaeocarpus@\textit{Elaeocarpus}!sylvestris@\textit{sylvestris}!var. lanyuensis@\textbf{var. \textit{lanyuensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼杜英&T2_new_value=true&fr=y}}{蘭嶼杜英}\index{蘭嶼杜英@{\Song{蘭嶼杜英}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elaeocarpus+sylvestris+var.+sylvestris}{\textit{E. sylvestris} (Lour.) Poir. var. \textit{sylvestris}}  \index{Elaeocarpus@\textit{Elaeocarpus}!sylvestris@\textit{sylvestris}!var. sylvestris@var. \textit{sylvestris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杜英&T2_new_value=true&fr=y}}{杜英}\index{杜英} LC
  \end{itemize}
 \item[] \textit{Sloanea} 猴歡喜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sloanea+formosana}{\textit{S. formosana} H.L.Li}  \index{Sloanea@\textit{Sloanea}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=猴歡喜&T2_new_value=true&fr=y}}{猴歡喜}\index{猴歡喜}\# LC
  \end{itemize}
  \end{itemize}
