
  \begin{itemize}
 \item[] \textit{Chimaphila} 愛冬葉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chimaphila+japonica}{\textit{C. japonica} Miq.}  \index{Chimaphila@\textit{Chimaphila}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本愛冬葉&T2_new_value=true&fr=y}}{日本愛冬葉}\index{日本愛冬葉} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chimaphila+monticola}{\textit{C. monticola} H.Andr.}  \index{Chimaphila@\textit{Chimaphila}!monticola@\textit{monticola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣愛冬葉&T2_new_value=true&fr=y}}{臺灣愛冬葉}\index{臺灣愛冬葉} DD
  \end{itemize}
 \item[] \textit{Enkianthus} 吊鐘花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Enkianthus+perulatus}{\textit{E. perulatus} C.K.Schneid.}  \index{Enkianthus@\textit{Enkianthus}!perulatus@\textbf{\textit{perulatus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣吊鐘花&T2_new_value=true&fr=y}}{臺灣吊鐘花}\index{臺灣吊鐘花@{\Song{臺灣吊鐘花}}} VU
  \end{itemize}
 \item[] \textit{Gaultheria} 白珠樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gaultheria+cumingiana}{\textit{G. cumingiana} Vidal}  \index{Gaultheria@\textit{Gaultheria}!cumingiana@\textit{cumingiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白珠樹&T2_new_value=true&fr=y}}{白珠樹}\index{白珠樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gaultheria+itoana}{\textit{G. itoana} Hayata}  \index{Gaultheria@\textit{Gaultheria}!itoana@\textit{itoana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山白珠樹&T2_new_value=true&fr=y}}{高山白珠樹}\index{高山白珠樹} LC
  \end{itemize}
 \item[] \textit{Lyonia} 南燭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lyonia+ovalifolia+var.+lanceolata}{\textit{L. ovalifolia} (Wall.) Drude var. \textit{lanceolata} (Wall.) Hand.-Mazz.}  \index{Lyonia@\textit{Lyonia}!ovalifolia@\textit{ovalifolia}!var. lanceolata@var. \textit{lanceolata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳葉南燭&T2_new_value=true&fr=y}}{銳葉南燭}\index{銳葉南燭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lyonia+ovalifolia+var.+ovalifolia}{\textit{L. ovalifolia} (Wall.) Drude var. \textit{ovalifolia}}  \index{Lyonia@\textit{Lyonia}!ovalifolia@\textit{ovalifolia}!var. ovalifolia@var. \textit{ovalifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南燭&T2_new_value=true&fr=y}}{南燭}\index{南燭} LC
  \end{itemize}
 \item[] \textit{Moneses} 單花鹿蹄草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Moneses+uniflora}{\textit{M. uniflora} (L.) A.Gray}  \index{Moneses@\textit{Moneses}!uniflora@\textit{uniflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單花鹿蹄草&T2_new_value=true&fr=y}}{單花鹿蹄草}\index{單花鹿蹄草} LC
  \end{itemize}
 \item[] \textit{Monotropa} 錫杖花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monotropa+hypopithys}{\textit{M. hypopithys} L.}  \index{Monotropa@\textit{Monotropa}!hypopithys@\textbf{\textit{hypopithys}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錫杖花&T2_new_value=true&fr=y}}{錫杖花}\index{錫杖花@{\Song{錫杖花}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monotropa+uniflora}{\textit{M. uniflora} L.}  \index{Monotropa@\textit{Monotropa}!uniflora@\textit{uniflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單花錫杖花&T2_new_value=true&fr=y}}{單花錫杖花}\index{單花錫杖花} DD
  \end{itemize}
 \item[] \textit{Monotropastrum} 水晶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monotropastrum+humile}{\textit{M. humile} (D.Don) H.Hara}  \index{Monotropastrum@\textit{Monotropastrum}!humile@\textit{humile}}  \index{Cheilotheca@\textit{Cheilotheca}!humilis@\textit{humilis}{\\\noindent(= \textit{Monotropastrum humile})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水晶蘭&T2_new_value=true&fr=y}}{水晶蘭}\index{水晶蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Monotropastrum+macrocarpum}{\textit{M. macrocarpum} Andres}  \index{Monotropastrum@\textit{Monotropastrum}!macrocarpum@\textit{macrocarpum}}  \index{Cheilotheca@\textit{Cheilotheca}!macrocarpa@\textit{macrocarpa}{\\\noindent(= \textit{Monotropastrum macrocarpum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山水晶蘭&T2_new_value=true&fr=y}}{阿里山水晶蘭}\index{阿里山水晶蘭} LC
  \end{itemize}
 \item[] \textit{Pieris} 馬醉木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pieris+taiwanensis}{\textit{P. taiwanensis} Hayata}  \index{Pieris@\textit{Pieris}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣馬醉木&T2_new_value=true&fr=y}}{臺灣馬醉木}\index{臺灣馬醉木} LC
  \end{itemize}
 \item[] \textit{Pyrola} 鹿蹄草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrola+alboreticulata}{\textit{P. alboreticulata} Hayata}  \index{Pyrola@\textit{Pyrola}!alboreticulata@\textit{alboreticulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斑紋鹿蹄草&T2_new_value=true&fr=y}}{斑紋鹿蹄草}\index{斑紋鹿蹄草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrola+japonica}{\textit{P. japonica} Klenze ex Alef.}  \index{Pyrola@\textit{Pyrola}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本鹿蹄草&T2_new_value=true&fr=y}}{日本鹿蹄草}\index{日本鹿蹄草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrola+morrisonensis}{\textit{P. morrisonensis} (Hayata) Hayata}  \index{Pyrola@\textit{Pyrola}!morrisonensis@\textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山鹿蹄草&T2_new_value=true&fr=y}}{玉山鹿蹄草}\index{玉山鹿蹄草}\# LC
  \end{itemize}
 \item[] \textit{Rhododendron} 杜鵑花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+breviperulatum}{\textit{R. breviperulatum} Hayata}  \index{Rhododendron@\textit{Rhododendron}!breviperulatum@\textit{breviperulatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南澳杜鵑&T2_new_value=true&fr=y}}{南澳杜鵑}\index{南澳杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+chilanshanense}{\textit{R. chilanshanense} Kurashige}  \index{Rhododendron@\textit{Rhododendron}!chilanshanense@\textbf{\textit{chilanshanense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=棲蘭山杜鵑&T2_new_value=true&fr=y}}{棲蘭山杜鵑}\index{棲蘭山杜鵑@{\Song{棲蘭山杜鵑}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+farrerae}{\textit{R. farrerae} Sweet}  \index{Rhododendron@\textit{Rhododendron}!farrerae@\textit{farrerae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=丁香杜鵑&T2_new_value=true&fr=y}}{丁香杜鵑}\index{丁香杜鵑} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+formosanum}{\textit{R. formosanum} Hemsl.}  \index{Rhododendron@\textit{Rhododendron}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣杜鵑&T2_new_value=true&fr=y}}{臺灣杜鵑}\index{臺灣杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+hyperythrum}{\textit{R. hyperythrum} Hayata}  \index{Rhododendron@\textit{Rhododendron}!hyperythrum@\textit{hyperythrum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖杜鵑&T2_new_value=true&fr=y}}{南湖杜鵑}\index{南湖杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+kanehirai}{\textit{R. kanehirai} E.H.Wilson}  \index{Rhododendron@\textit{Rhododendron}!kanehirai@\textit{kanehirai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來杜鵑&T2_new_value=true&fr=y}}{烏來杜鵑}\index{烏來杜鵑}\# EW
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+kawakamii}{\textit{R. kawakamii} Hayata}  \index{Rhododendron@\textit{Rhododendron}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=著生杜鵑&T2_new_value=true&fr=y}}{著生杜鵑}\index{著生杜鵑}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+lasiostylum}{\textit{R. lasiostylum} Hayata}  \index{Rhododendron@\textit{Rhododendron}!lasiostylum@\textit{lasiostylum}}  \index{Rhododendron@\textit{Rhododendron}!latoucheae@\textit{latoucheae}{\\\noindent(= \textit{Rhododendron lasiostylum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=埔里杜鵑&T2_new_value=true&fr=y}}{埔里杜鵑}\index{埔里杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+leptosanthum}{\textit{R. leptosanthum} Hayata}  \index{Rhododendron@\textit{Rhododendron}!leptosanthum@\textit{leptosanthum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=西施花&T2_new_value=true&fr=y}}{西施花}\index{西施花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+mariesii}{\textit{R. mariesii} Hemsl. \& E.H.Wils.}  \index{Rhododendron@\textit{Rhododendron}!mariesii@\textit{mariesii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=守城滿山紅&T2_new_value=true&fr=y}}{守城滿山紅}\index{守城滿山紅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+noriakianum}{\textit{R. noriakianum} T.Suzuki}  \index{Rhododendron@\textit{Rhododendron}!noriakianum@\textit{noriakianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉杜鵑&T2_new_value=true&fr=y}}{細葉杜鵑}\index{細葉杜鵑}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+oldhamii}{\textit{R. oldhamii} Maxim.}  \index{Rhododendron@\textit{Rhododendron}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金毛杜鵑&T2_new_value=true&fr=y}}{金毛杜鵑}\index{金毛杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+ovatum+var.+lamprophyllum}{\textit{R. ovatum} Planch. var. \textit{lamprophyllum} (Hayata) Y.C.Liu, F.Y.Lu \& C.H.Ou}  \index{Rhododendron@\textit{Rhododendron}!ovatum@\textit{ovatum}!var. lamprophyllum@var. \textit{lamprophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長卵葉馬銀花&T2_new_value=true&fr=y}}{長卵葉馬銀花}\index{長卵葉馬銀花}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+ovatum+var.+ovatum}{\textit{R. ovatum} Planch. var. \textit{ovatum}}  \index{Rhododendron@\textit{Rhododendron}!ovatum@\textit{ovatum}!var. ovatum@var. \textit{ovatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬銀花&T2_new_value=true&fr=y}}{馬銀花}\index{馬銀花} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+pseudochrysanthum}{\textit{R. pseudochrysanthum} Hayata}  \index{Rhododendron@\textit{Rhododendron}!pseudochrysanthum@\textit{pseudochrysanthum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山杜鵑&T2_new_value=true&fr=y}}{玉山杜鵑}\index{玉山杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+rubropilosum+var.+rubropilosum}{\textit{R. rubropilosum} Hayata var. \textit{rubropilosum}}  \index{Rhododendron@\textit{Rhododendron}!rubropilosum@\textit{rubropilosum}!var. rubropilosum@var. \textit{rubropilosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅毛杜鵑&T2_new_value=true&fr=y}}{紅毛杜鵑}\index{紅毛杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+rubropilosum+var.+taiwanalpinum}{\textit{R. rubropilosum} Hayata var. \textit{taiwanalpinum} (Ohwi) S.Y.Lu, Yuen P.Yang \& Y.H.Tseng}  \index{Rhododendron@\textit{Rhododendron}!rubropilosum@\textit{rubropilosum}!var. taiwanalpinum@var. \textit{taiwanalpinum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣高山杜鵑&T2_new_value=true&fr=y}}{臺灣高山杜鵑}\index{臺灣高山杜鵑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhododendron+simsii}{\textit{R. simsii} Planch.}  \index{Rhododendron@\textit{Rhododendron}!simsii@\textit{simsii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=唐杜鵑&T2_new_value=true&fr=y}}{唐杜鵑}\index{唐杜鵑} NT
  \end{itemize}
 \item[] \textit{Vaccinium} 越橘屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+bracteatum}{\textit{V. bracteatum} Thunb.}  \index{Vaccinium@\textit{Vaccinium}!bracteatum@\textit{bracteatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=米飯花&T2_new_value=true&fr=y}}{米飯花}\index{米飯花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+dunalianum+var.+caudatifolium}{\textit{V. dunalianum} Wight var. \textit{caudatifolium} (Hayata) H.L.Li}  \index{Vaccinium@\textit{Vaccinium}!dunalianum@\textit{dunalianum}!var. caudatifolium@var. \textit{caudatifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=珍珠花&T2_new_value=true&fr=y}}{珍珠花}\index{珍珠花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+emarginatum}{\textit{V. emarginatum} Hayata}  \index{Vaccinium@\textit{Vaccinium}!emarginatum@\textit{emarginatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹葉越橘&T2_new_value=true&fr=y}}{凹葉越橘}\index{凹葉越橘}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+japonicum+var.+lasiostemon}{\textit{V. japonicum} Miq. var. \textit{lasiostemon} Hayata}  \index{Vaccinium@\textit{Vaccinium}!japonicum@\textit{japonicum}!var. lasiostemon@var. \textit{lasiostemon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛蕊花&T2_new_value=true&fr=y}}{毛蕊花}\index{毛蕊花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+kengii}{\textit{V. kengii} C.E.Chang}  \index{Vaccinium@\textit{Vaccinium}!kengii@\textit{kengii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鞍馬山越橘&T2_new_value=true&fr=y}}{鞍馬山越橘}\index{鞍馬山越橘}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+merrillianum}{\textit{V. merrillianum} Hayata}  \index{Vaccinium@\textit{Vaccinium}!merrillianum@\textit{merrillianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山越橘&T2_new_value=true&fr=y}}{高山越橘}\index{高山越橘}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+randaiense}{\textit{V. randaiense} Hayata}  \index{Vaccinium@\textit{Vaccinium}!randaiense@\textit{randaiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巒大越橘&T2_new_value=true&fr=y}}{巒大越橘}\index{巒大越橘}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+wrightii+var.+formosanum}{\textit{V. wrightii} A.Gray var. \textit{formosanum} (Hayata) H.L.Li}  \index{Vaccinium@\textit{Vaccinium}!wrightii@\textit{wrightii}!var. formosanum@var. \textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣大葉越橘&T2_new_value=true&fr=y}}{臺灣大葉越橘}\index{臺灣大葉越橘}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaccinium+wrightii+var.+wrightii}{\textit{V. wrightii} A.Gray var. \textit{wrightii}}  \index{Vaccinium@\textit{Vaccinium}!wrightii@\textit{wrightii}!var. wrightii@var. \textit{wrightii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉越橘&T2_new_value=true&fr=y}}{大葉越橘}\index{大葉越橘} LC
  \end{itemize}
  \end{itemize}
