
  \begin{itemize}
 \item[] \textit{Acalypha} 鐵莧屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+akoensis}{\textit{A. akoensis} Hayata}  \index{Acalypha@\textit{Acalypha}!akoensis@\textit{akoensis}} 屏東鐵莧 \index{屏東鐵莧} \# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+angatensis}{\textit{A. angatensis} Blanco}  \index{Acalypha@\textit{Acalypha}!angatensis@\textit{angatensis}} 臺灣鐵莧 \index{臺灣鐵莧}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+aristata}{\textit{A. aristata} Kunth}  \index{Acalypha@\textit{Acalypha}!aristata@\textit{aristata}} 南美鐵莧 \index{南美鐵莧}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+australis}{\textit{A. australis} L.}  \index{Acalypha@\textit{Acalypha}!australis@\textit{australis}} 鐵莧菜 \index{鐵莧菜}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+brachystachya}{\textit{A. brachystachya} Hornem.}  \index{Acalypha@\textit{Acalypha}!brachystachya@\textit{brachystachya}} 短序鐵莧菜 \index{短序鐵莧菜}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+caturus}{\textit{A. caturus} Blume}  \index{Acalypha@\textit{Acalypha}!caturus@\textit{caturus}} 蘭嶼鐵莧 \index{蘭嶼鐵莧}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+hontauyuensis}{\textit{A. hontauyuensis} H.Keng.}  \index{Acalypha@\textit{Acalypha}!hontauyuensis@\textit{hontauyuensis}} 紅頭鐵莧 \index{紅頭鐵莧} \# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+indica+var.+indica}{\textit{A. indica} L. var. \textit{indica}}  \index{Acalypha@\textit{Acalypha}!indica@\textit{indica}!var. indica@var. \textit{indica}} 印度鐵莧 \index{印度鐵莧}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+indica+var.+minima}{\textit{A. indica} L. var. \textit{minima} (H.Keng) S.F.Huang \& T.C.Huang}  \index{Acalypha@\textit{Acalypha}!indica@\textit{indica}!var. minima@var. \textit{minima}} 小葉鐵莧 \index{小葉鐵莧} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+longi-acuminata}{\textit{A. longi-acuminata} Hayata}  \index{Acalypha@\textit{Acalypha}!longi-acuminata@\textit{longi-acuminata}} 尖尾鐵莧 \index{尖尾鐵莧} \# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+matudai}{\textit{A. matudai} Hayata}  \index{Acalypha@\textit{Acalypha}!matudai@\textit{matudai}} 恆春鐵莧 \index{恆春鐵莧} \# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acalypha+suirenbiensis}{\textit{A. suirenbiensis} Yamam.}  \index{Acalypha@\textit{Acalypha}!suirenbiensis@\textit{suirenbiensis}} 花蓮鐵莧 \index{花蓮鐵莧} \# DD
  \end{itemize}
 \item[] \textit{Alchornea} 山麻桿屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alchornea+trewioides+var.+formosae}{\textit{A. trewioides} (Benth.) Müll.Arg. var. \textit{formosae} (Müll.Arg.) Pax \& Hoffm.}  \index{Alchornea@\textit{Alchornea}!trewioides@\textit{trewioides}!var. formosae@var. \textit{formosae}} 臺灣山麻桿 \index{臺灣山麻桿} \# VU
  \end{itemize}
 \item[] \textit{Chamaesyce} 地錦草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+atoto}{\textit{C. atoto} (Forst.f.) Croizat}  \index{Chamaesyce@\textit{Chamaesyce}!atoto@\textit{atoto}} 濱大戟 \index{濱大戟}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+garanbiensis}{\textit{C. garanbiensis} (Hayata) H.Hara}  \index{Chamaesyce@\textit{Chamaesyce}!garanbiensis@\textit{garanbiensis}} 鵝鑾鼻大戟 \index{鵝鑾鼻大戟} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+hirta}{\textit{C. hirta} (L.) Millsp.}  \index{Chamaesyce@\textit{Chamaesyce}!hirta@\textit{hirta}} 大飛揚草 \index{大飛揚草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+hsinchuensis}{\textit{C. hsinchuensis} S.C.Lin \& S.M.Chaw}  \index{Chamaesyce@\textit{Chamaesyce}!hsinchuensis@\textit{hsinchuensis}} 新竹地錦 \index{新竹地錦} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+hypericifolia}{\textit{C. hypericifolia} (L.) Millsp.}  \index{Chamaesyce@\textit{Chamaesyce}!hypericifolia@\textit{hypericifolia}} 假紫斑大戟 \index{假紫斑大戟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+hyssopifolia}{\textit{C. hyssopifolia} (L.) Small}  \index{Chamaesyce@\textit{Chamaesyce}!hyssopifolia@\textit{hyssopifolia}} 紫斑大戟 \index{紫斑大戟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+maculata}{\textit{C. maculata} (L.) Small}  \index{Chamaesyce@\textit{Chamaesyce}!maculata@\textit{maculata}} 斑地錦 \index{斑地錦}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+makinoi}{\textit{C. makinoi} (Hayata) H.Hara}  \index{Chamaesyce@\textit{Chamaesyce}!makinoi@\textit{makinoi}} 小葉大戟 \index{小葉大戟}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+prostrata}{\textit{C. prostrata} (Aiton) Small}  \index{Chamaesyce@\textit{Chamaesyce}!prostrata@\textit{prostrata}} 伏生大戟 \index{伏生大戟}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+serpens}{\textit{C. serpens} (Kunth) Small}  \index{Chamaesyce@\textit{Chamaesyce}!serpens@\textit{serpens}} 匍根大戟 \index{匍根大戟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+sparrmannii}{\textit{C. sparrmannii} (Boiss.) Hurus.}  \index{Chamaesyce@\textit{Chamaesyce}!sparrmannii@\textit{sparrmannii}} 心葉大戟 \index{心葉大戟}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+taihsiensis}{\textit{C. taihsiensis} S.M.Chaw ＆ Koutnik}  \index{Chamaesyce@\textit{Chamaesyce}!taihsiensis@\textit{taihsiensis}} 臺西大戟 \index{臺西大戟} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+tashiroi}{\textit{C. tashiroi} (Hayata) H.Hara}  \index{Chamaesyce@\textit{Chamaesyce}!tashiroi@\textit{tashiroi}} 田代氏大戟 \index{田代氏大戟} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+thymifolia}{\textit{C. thymifolia} (L.) Millsp.}  \index{Chamaesyce@\textit{Chamaesyce}!thymifolia@\textit{thymifolia}} 千根草 \index{千根草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaesyce+vachellii}{\textit{C. vachellii} (Hook. \& Arn.) Hurus.}  \index{Chamaesyce@\textit{Chamaesyce}!vachellii@\textit{vachellii}} 華南大戟 \index{華南大戟}  LC
  \end{itemize}
 \item[] \textit{Claoxylon} 假鐵莧屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Claoxylon+brachyandrum}{\textit{C. brachyandrum} Pax \& Hoffm.}  \index{Claoxylon@\textit{Claoxylon}!brachyandrum@\textit{brachyandrum}} 假鐵莧 \index{假鐵莧}  NT
  \end{itemize}
 \item[] \textit{Croton} 巴豆屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Croton+bonplandianus}{\textit{C. bonplandianus} Baillon}  \index{Croton@\textit{Croton}!bonplandianus@\textit{bonplandianus}} 波氏巴豆 \index{波氏巴豆}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Croton+cascarilloides}{\textit{C. cascarilloides} Raeusch.}  \index{Croton@\textit{Croton}!cascarilloides@\textit{cascarilloides}} 裏白巴豆 \index{裏白巴豆}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Croton+tiglium}{\textit{C. tiglium} L.}  \index{Croton@\textit{Croton}!tiglium@\textit{tiglium}} 巴豆 \index{巴豆}  NA (N)
  \end{itemize}
 \item[] \textit{Euphorbia} 大戟屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+cyathophora}{\textit{E. cyathophora} Murray}  \index{Euphorbia@\textit{Euphorbia}!cyathophora@\textit{cyathophora}} 猩猩草 \index{猩猩草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+formosana}{\textit{E. formosana} Hayata}  \index{Euphorbia@\textit{Euphorbia}!formosana@\textit{formosana}} 臺灣大戟 \index{臺灣大戟} \# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+graminea}{\textit{E. graminea} Jacquin}  \index{Euphorbia@\textit{Euphorbia}!graminea@\textit{graminea}} 禾葉大戟 \index{禾葉大戟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+heterophylla}{\textit{E. heterophylla} L.}  \index{Euphorbia@\textit{Euphorbia}!heterophylla@\textit{heterophylla}} 白苞猩猩草 \index{白苞猩猩草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+jolkini}{\textit{E. jolkini} Boiss.}  \index{Euphorbia@\textit{Euphorbia}!jolkini@\textit{jolkini}} 岩大戟 \index{岩大戟}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+peplus}{\textit{E. peplus} L.}  \index{Euphorbia@\textit{Euphorbia}!peplus@\textit{peplus}} 荸艾類大戟 \index{荸艾類大戟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+shouanensis}{\textit{E. shouanensis} H.Keng}  \index{Euphorbia@\textit{Euphorbia}!shouanensis@\textit{shouanensis}} 霞山大戟 \index{霞山大戟} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+tarokoensis}{\textit{E. tarokoensis} Hayata}  \index{Euphorbia@\textit{Euphorbia}!tarokoensis@\textit{tarokoensis}} 太魯閣大戟 \index{太魯閣大戟} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphorbia+tirucalli}{\textit{E. tirucalli} L.}  \index{Euphorbia@\textit{Euphorbia}!tirucalli@\textit{tirucalli}} 綠珊瑚 \index{綠珊瑚}  NA (N)
  \end{itemize}
 \item[] \textit{Excoecaria} 土沉香屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Excoecaria+agallocha}{\textit{E. agallocha} L.}  \index{Excoecaria@\textit{Excoecaria}!agallocha@\textit{agallocha}} 土沉香 \index{土沉香}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Excoecaria+formosana}{\textit{E. formosana} (Hayata) Hayata}  \index{Excoecaria@\textit{Excoecaria}!formosana@\textit{formosana}} 臺灣土沉香 \index{臺灣土沉香}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Excoecaria+kawakamii}{\textit{E. kawakamii} Hayata}  \index{Excoecaria@\textit{Excoecaria}!kawakamii@\textit{kawakamii}} 蘭嶼土沉香 \index{蘭嶼土沉香} \# VU
  \end{itemize}
 \item[] \textit{Gelonium} 白樹屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gelonium+aequoreum}{\textit{G. aequoreum} Hance}  \index{Gelonium@\textit{Gelonium}!aequoreum@\textit{aequoreum}} 白樹仔 \index{白樹仔} \# VU
  \end{itemize}
 \item[] \textit{Hevea} 橡膠樹屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hevea+brasiliensis}{\textit{H. brasiliensis} (Willd. ex A.Juss.) Müll.Arg.}  \index{Hevea@\textit{Hevea}!brasiliensis@\textit{brasiliensis}} 巴西橡膠樹 \index{巴西橡膠樹}  NA (N)
  \end{itemize}
 \item[] \textit{Homalanthus} 澳楊屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Homalanthus+fastuosus}{\textit{H. fastuosus} (Linden) Fern.-Vill.}  \index{Homalanthus@\textit{Homalanthus}!fastuosus@\textit{fastuosus}} 圓葉血桐 \index{圓葉血桐}  LC
  \end{itemize}
 \item[] \textit{Homonoia} 水楊梅屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Homonoia+riparia}{\textit{H. riparia} Lour.}  \index{Homonoia@\textit{Homonoia}!riparia@\textit{riparia}} 水楊梅 \index{水楊梅}  NT
  \end{itemize}
 \item[] \textit{Macaranga} 血桐屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macaranga+sinensis}{\textit{M. sinensis} Müll.Arg.}  \index{Macaranga@\textit{Macaranga}!sinensis@\textit{sinensis}} 紅肉橙蘭 \index{紅肉橙蘭}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macaranga+tanarius}{\textit{M. tanarius} (L.) Müll.Arg.}  \index{Macaranga@\textit{Macaranga}!tanarius@\textit{tanarius}} 血桐 \index{血桐}  LC
  \end{itemize}
 \item[] \textit{Mallotus} 野桐屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+japonicus}{\textit{M. japonicus} (Thunb.) Müll.Arg.}  \index{Mallotus@\textit{Mallotus}!japonicus@\textit{japonicus}} 野桐 \index{野桐}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+paniculatus+var.+formosanus}{\textit{M. paniculatus} (Lam.) Müll.Arg. var. \textit{formosanus} (Hayata) Hurus.}  \index{Mallotus@\textit{Mallotus}!paniculatus@\textit{paniculatus}!var. formosanus@var. \textit{formosanus}} 臺灣白匏子 \index{臺灣白匏子} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+paniculatus+var.+paniculatus}{\textit{M. paniculatus} (Lam.) Müll.Arg. var. \textit{paniculatus}}  \index{Mallotus@\textit{Mallotus}!paniculatus@\textit{paniculatus}!var. paniculatus@var. \textit{paniculatus}} 白匏子 \index{白匏子}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+philippensis}{\textit{M. philippensis} (Lam.) Müll.Arg.}  \index{Mallotus@\textit{Mallotus}!philippensis@\textit{philippensis}} 粗糠柴 \index{粗糠柴}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+repandus}{\textit{M. repandus} (Willd.) Müll.Arg.}  \index{Mallotus@\textit{Mallotus}!repandus@\textit{repandus}} 扛香藤 \index{扛香藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mallotus+tiliifolius}{\textit{M. tiliifolius} (Blume) Müll.Arg.}  \index{Mallotus@\textit{Mallotus}!tiliifolius@\textit{tiliifolius}} 椴葉野桐 \index{椴葉野桐}  VU
  \end{itemize}
 \item[] \textit{Manihot} 木薯屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Manihot+esculenta}{\textit{M. esculenta} Crantz}  \index{Manihot@\textit{Manihot}!esculenta@\textit{esculenta}} 樹薯 \index{樹薯}  NA (N)
  \end{itemize}
 \item[] \textit{Melanolepis} 蟲屎屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melanolepis+multiglandulosa}{\textit{M. multiglandulosa} (Reinw.) Rchb.f. \& Zoll.}  \index{Melanolepis@\textit{Melanolepis}!multiglandulosa@\textit{multiglandulosa}} 蟲屎 \index{蟲屎}  LC
  \end{itemize}
 \item[] \textit{Mercurialis} 山靛屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mercurialis+leiocarpa}{\textit{M. leiocarpa} Siebold \& Zucc.}  \index{Mercurialis@\textit{Mercurialis}!leiocarpa@\textit{leiocarpa}} 山靛 \index{山靛}  LC
  \end{itemize}
 \item[] \textit{Ricinus} 蓖麻屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ricinus+communis}{\textit{R. communis} L.}  \index{Ricinus@\textit{Ricinus}!communis@\textit{communis}} 蓖麻 \index{蓖麻}  NA (N)
  \end{itemize}
 \item[] \textit{Triadica} 烏桕屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triadica+cochinchinensis}{\textit{T. cochinchinensis} Lour.}  \index{Triadica@\textit{Triadica}!cochinchinensis@\textit{cochinchinensis}} 白桕 \index{白桕}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triadica+sebifera}{\textit{T. sebifera} (L.) Small}  \index{Triadica@\textit{Triadica}!sebifera@\textit{sebifera}} 烏桕 \index{烏桕}  NA (N)
  \end{itemize}
 \item[] \textit{Vernicia} 油桐屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernicia+fordii}{\textit{V. fordii} (Hemsl.) Airy Shaw}  \index{Vernicia@\textit{Vernicia}!fordii@\textit{fordii}} 油桐 \index{油桐}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vernicia+montana}{\textit{V. montana} Lour.}  \index{Vernicia@\textit{Vernicia}!montana@\textit{montana}} 千年桐 \index{千年桐}  NA (N)
  \end{itemize}
  \end{itemize}
