
  \begin{itemize}
 \item[] \textit{Abrus} 雞母珠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abrus+precatorius}{\textit{A. precatorius} L.}  \index{Abrus@\textit{Abrus}!precatorius@\textit{precatorius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞母珠&T2_new_value=true&fr=y}}{雞母珠}\index{雞母珠} LC
  \end{itemize}
 \item[] \textit{Acacia} 相思樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acacia+caesia}{\textit{A. caesia} (L.) Willd}  \index{Acacia@\textit{Acacia}!caesia@\textit{caesia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藤相思樹&T2_new_value=true&fr=y}}{藤相思樹}\index{藤相思樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acacia+confusa}{\textit{A. confusa} Merr.}  \index{Acacia@\textit{Acacia}!confusa@\textit{confusa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=相思樹&T2_new_value=true&fr=y}}{相思樹}\index{相思樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acacia+farnesiana}{\textit{A. farnesiana} (L.) Willd.}  \index{Acacia@\textit{Acacia}!farnesiana@\textit{farnesiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金合歡&T2_new_value=true&fr=y}}{金合歡}\index{金合歡} NA$^n$
  \end{itemize}
 \item[] \textit{Aeschynomene} 合萌屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeschynomene+americana+var.+americana}{\textit{A. americana} L. var. \textit{americana}}  \index{Aeschynomene@\textit{Aeschynomene}!americana@\textit{americana}!var. americana@var. \textit{americana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=敏感合萌&T2_new_value=true&fr=y}}{敏感合萌}\index{敏感合萌} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeschynomene+americana+var.+glandulosa}{\textit{A. americana} L. var. \textit{glandulosa} (Poir.) Rudd.}  \index{Aeschynomene@\textit{Aeschynomene}!americana@\textit{americana}!var. glandulosa@var. \textit{glandulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果美洲合萌&T2_new_value=true&fr=y}}{毛果美洲合萌}\index{毛果美洲合萌} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeschynomene+indica}{\textit{A. indica} L.}  \index{Aeschynomene@\textit{Aeschynomene}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=合萌&T2_new_value=true&fr=y}}{合萌}\index{合萌} NA$^n$
  \end{itemize}
 \item[] \textit{Albizia} 合歡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Albizia+julibrissin}{\textit{A. julibrissin} Durazz.}  \index{Albizia@\textit{Albizia}!julibrissin@\textit{julibrissin}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=合歡&T2_new_value=true&fr=y}}{合歡}\index{合歡} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Albizia+kalkora}{\textit{A. kalkora} Prain}  \index{Albizia@\textit{Albizia}!kalkora@\textit{kalkora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山合歡&T2_new_value=true&fr=y}}{山合歡}\index{山合歡} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Albizia+lebbeck}{\textit{A. lebbeck} (L.) Benth.}  \index{Albizia@\textit{Albizia}!lebbeck@\textit{lebbeck}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉合歡&T2_new_value=true&fr=y}}{大葉合歡}\index{大葉合歡} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Albizia+procera}{\textit{A. procera} (Roxb.) Benth.}  \index{Albizia@\textit{Albizia}!procera@\textit{procera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃豆樹&T2_new_value=true&fr=y}}{黃豆樹}\index{黃豆樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Albizia+retusa}{\textit{A. retusa} Benth.}  \index{Albizia@\textit{Albizia}!retusa@\textbf{\textit{retusa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼合歡&T2_new_value=true&fr=y}}{蘭嶼合歡}\index{蘭嶼合歡@{\Song{蘭嶼合歡}}} EN
  \end{itemize}
 \item[] \textit{Alysicarpus} 煉莢豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alysicarpus+bupleurifolius}{\textit{A. bupleurifolius} (L.) DC.}  \index{Alysicarpus@\textit{Alysicarpus}!bupleurifolius@\textit{bupleurifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉煉莢豆&T2_new_value=true&fr=y}}{長葉煉莢豆}\index{長葉煉莢豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alysicarpus+ovalifolius}{\textit{A. ovalifolius} (Schum.) J.Léonard}  \index{Alysicarpus@\textit{Alysicarpus}!ovalifolius@\textit{ovalifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉煉莢豆&T2_new_value=true&fr=y}}{圓葉煉莢豆}\index{圓葉煉莢豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alysicarpus+rugosus}{\textit{A. rugosus} (Willd.) DC.}  \index{Alysicarpus@\textit{Alysicarpus}!rugosus@\textit{rugosus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=皺果煉莢豆&T2_new_value=true&fr=y}}{皺果煉莢豆}\index{皺果煉莢豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alysicarpus+vaginalis+var.+taiwanensis}{\textit{A. vaginalis} (L.) DC. var. \textit{taiwanensis} S.S.Ying}  \index{Alysicarpus@\textit{Alysicarpus}!vaginalis@\textit{vaginalis}!var. taiwanensis@var. \textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花煉莢豆&T2_new_value=true&fr=y}}{黃花煉莢豆}\index{黃花煉莢豆}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alysicarpus+vaginalis+var.+vaginalis}{\textit{A. vaginalis} (L.) DC. var. \textit{vaginalis}}  \index{Alysicarpus@\textit{Alysicarpus}!vaginalis@\textit{vaginalis}!var. vaginalis@var. \textit{vaginalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=煉莢豆&T2_new_value=true&fr=y}}{煉莢豆}\index{煉莢豆} LC
  \end{itemize}
 \item[] \textit{Amorpha} 紫穗槐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amorpha+fruticosa}{\textit{A. fruticosa} L.}  \index{Amorpha@\textit{Amorpha}!fruticosa@\textit{fruticosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫穗槐&T2_new_value=true&fr=y}}{紫穗槐}\index{紫穗槐} NA$^n$
  \end{itemize}
 \item[] \textit{Amphicarpaea} 野毛扁豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amphicarpaea+bracteata+subsp.+edgeworthii+var.+japonica}{\textit{A. bracteata} (L.) subsp. \textit{edgeworthii} (Benth.) Ohashi var. \textit{japonica} (Oliver) H.Ohashi}  \index{Amphicarpaea@\textit{Amphicarpaea}!bracteata@\textit{bracteata}!subsp. edgeworthii var. japonica@subsp. \textit{edgeworthii} var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野毛扁豆&T2_new_value=true&fr=y}}{野毛扁豆}\index{野毛扁豆} LC
  \end{itemize}
 \item[] \textit{Apios} 土圞兒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Apios+taiwanianus}{\textit{A. taiwanianus} Hosok.}  \index{Apios@\textit{Apios}!taiwanianus@\textbf{\textit{taiwanianus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣土圞兒&T2_new_value=true&fr=y}}{臺灣土圞兒}\index{臺灣土圞兒@{\Song{臺灣土圞兒}}}\# EN
  \end{itemize}
 \item[] \textit{Archidendron} 頷垂豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Archidendron+lucidum}{\textit{A. lucidum} (Benth.) I.Nielsen}  \index{Archidendron@\textit{Archidendron}!lucidum@\textit{lucidum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=頷垂豆&T2_new_value=true&fr=y}}{頷垂豆}\index{頷垂豆} LC
  \end{itemize}
 \item[] \textit{Astragalus} 紫雲英屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Astragalus+nankotaizanensis}{\textit{A. nankotaizanensis} Sasaki}  \index{Astragalus@\textit{Astragalus}!nankotaizanensis@\textbf{\textit{nankotaizanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖大山紫雲英&T2_new_value=true&fr=y}}{南湖大山紫雲英}\index{南湖大山紫雲英@{\Song{南湖大山紫雲英}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Astragalus+nokoensis}{\textit{A. nokoensis} Sasaki}  \index{Astragalus@\textit{Astragalus}!nokoensis@\textbf{\textit{nokoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高大山紫雲英&T2_new_value=true&fr=y}}{能高大山紫雲英}\index{能高大山紫雲英@{\Song{能高大山紫雲英}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Astragalus+sinicus}{\textit{A. sinicus} L.}  \index{Astragalus@\textit{Astragalus}!sinicus@\textit{sinicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫雲英&T2_new_value=true&fr=y}}{紫雲英}\index{紫雲英} NA$^n$
  \end{itemize}
 \item[] \textit{Bauhinia} 羊蹄甲屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bauhinia+championii}{\textit{B. championii} (Benth.) Benth.}  \index{Bauhinia@\textit{Bauhinia}!championii@\textit{championii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菊花木&T2_new_value=true&fr=y}}{菊花木}\index{菊花木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bauhinia+purpurea}{\textit{B. purpurea} L.}  \index{Bauhinia@\textit{Bauhinia}!purpurea@\textit{purpurea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=洋紫荊&T2_new_value=true&fr=y}}{洋紫荊}\index{洋紫荊} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bauhinia+variegata}{\textit{B. variegata} L.}  \index{Bauhinia@\textit{Bauhinia}!variegata@\textit{variegata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羊蹄甲&T2_new_value=true&fr=y}}{羊蹄甲}\index{羊蹄甲} NA$^n$
  \end{itemize}
 \item[] \textit{Caesalpinia} 蘇木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Caesalpinia+bonduc}{\textit{C. bonduc} (L.) Roxb.}  \index{Caesalpinia@\textit{Caesalpinia}!bonduc@\textbf{\textit{bonduc}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=老虎心&T2_new_value=true&fr=y}}{老虎心}\index{老虎心@{\Song{老虎心}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Caesalpinia+crista}{\textit{C. crista} L.}  \index{Caesalpinia@\textit{Caesalpinia}!crista@\textit{crista}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=搭肉刺&T2_new_value=true&fr=y}}{搭肉刺}\index{搭肉刺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Caesalpinia+decapetala}{\textit{C. decapetala} (Roth) Alston}  \index{Caesalpinia@\textit{Caesalpinia}!decapetala@\textit{decapetala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雲實&T2_new_value=true&fr=y}}{雲實}\index{雲實} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Caesalpinia+minax}{\textit{C. minax} Hance}  \index{Caesalpinia@\textit{Caesalpinia}!minax@\textbf{\textit{minax}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓮實藤&T2_new_value=true&fr=y}}{蓮實藤}\index{蓮實藤@{\Song{蓮實藤}}} VU
  \end{itemize}
 \item[] \textit{Cajanus} 木豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cajanus+cajan}{\textit{C. cajan} (L.) Millsp.}  \index{Cajanus@\textit{Cajanus}!cajan@\textit{cajan}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木豆&T2_new_value=true&fr=y}}{木豆}\index{木豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cajanus+scarabaeoides}{\textit{C. scarabaeoides} (L.) Thouars}  \index{Cajanus@\textit{Cajanus}!scarabaeoides@\textit{scarabaeoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓蟲豆&T2_new_value=true&fr=y}}{蔓蟲豆}\index{蔓蟲豆} LC
  \end{itemize}
 \item[] \textit{Callerya} 崖豆藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callerya+nitida}{\textit{C. nitida} (Benth.) R.Geesink}  \index{Callerya@\textit{Callerya}!nitida@\textbf{\textit{nitida}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉魚藤&T2_new_value=true&fr=y}}{光葉魚藤}\index{光葉魚藤@{\Song{光葉魚藤}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callerya+reticulata}{\textit{C. reticulata} (Benth.) Schot}  \index{Callerya@\textit{Callerya}!reticulata@\textit{reticulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=老荊藤&T2_new_value=true&fr=y}}{老荊藤}\index{老荊藤} LC
  \end{itemize}
 \item[] \textit{Calopogonium} 擬大豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calopogonium+mucunoides}{\textit{C. mucunoides} Desv.}  \index{Calopogonium@\textit{Calopogonium}!mucunoides@\textit{mucunoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬大豆&T2_new_value=true&fr=y}}{擬大豆}\index{擬大豆} NA$^n$
  \end{itemize}
 \item[] \textit{Campylotropis} 彎龍骨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Campylotropis+giraldii}{\textit{C. giraldii} (Schindl.) Schindl.}  \index{Campylotropis@\textit{Campylotropis}!giraldii@\textit{giraldii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=彎龍骨&T2_new_value=true&fr=y}}{彎龍骨}\index{彎龍骨} LC
  \end{itemize}
 \item[] \textit{Canavalia} 刀豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Canavalia+cathartica}{\textit{C. cathartica} Thouars}  \index{Canavalia@\textit{Canavalia}!cathartica@\textit{cathartica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小果刀豆&T2_new_value=true&fr=y}}{小果刀豆}\index{小果刀豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Canavalia+ensiformis}{\textit{C. ensiformis} (L.) DC.}  \index{Canavalia@\textit{Canavalia}!ensiformis@\textit{ensiformis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關刀豆&T2_new_value=true&fr=y}}{關刀豆}\index{關刀豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Canavalia+lineata}{\textit{C. lineata} (Thunb.) DC.}  \index{Canavalia@\textit{Canavalia}!lineata@\textit{lineata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=肥豬豆&T2_new_value=true&fr=y}}{肥豬豆}\index{肥豬豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Canavalia+rosea}{\textit{C. rosea} (Sw.) DC.}  \index{Canavalia@\textit{Canavalia}!rosea@\textit{rosea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱刀豆&T2_new_value=true&fr=y}}{濱刀豆}\index{濱刀豆} LC
  \end{itemize}
 \item[] \textit{Cassia} 決明屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cassia+sophora+var.+penghuana}{\textit{C. sophora} L. var. \textit{penghuana} Y.C.Liu ＆ F.Y.Lu}  \index{Cassia@\textit{Cassia}!sophora@\textit{sophora}!var. penghuana@\textbf{var. \textit{penghuana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澎湖決明&T2_new_value=true&fr=y}}{澎湖決明}\index{澎湖決明@{\Song{澎湖決明}}}\# VU
  \end{itemize}
 \item[] \textit{Centrosema} 山珠豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Centrosema+pubescens}{\textit{C. pubescens} Benth.}  \index{Centrosema@\textit{Centrosema}!pubescens@\textit{pubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山珠豆&T2_new_value=true&fr=y}}{山珠豆}\index{山珠豆} NA$^n$
  \end{itemize}
 \item[] \textit{Chamaecrista} 假含羞草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecrista+garambiensis}{\textit{C. garambiensis} (Hosok.) H.Ohashi, Tateishi \& T.Nemoto}  \index{Chamaecrista@\textit{Chamaecrista}!garambiensis@\textbf{\textit{garambiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝鑾鼻決明&T2_new_value=true&fr=y}}{鵝鑾鼻決明}\index{鵝鑾鼻決明@{\Song{鵝鑾鼻決明}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecrista+mimosoides}{\textit{C. mimosoides} (L.) Greene}  \index{Chamaecrista@\textit{Chamaecrista}!mimosoides@\textit{mimosoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假含羞草&T2_new_value=true&fr=y}}{假含羞草}\index{假含羞草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecrista+nictitans+subsp.+patellaria+var.+glabrata}{\textit{C. nictitans} (L.) subsp. \textit{patellaria} (DC. ex Collad.) H.S.Irwin \& Barneby var. \textit{glabrata} (Vogel) H.S.Irwin \& Barneby}  \index{Chamaecrista@\textit{Chamaecrista}!nictitans@\textit{nictitans}!subsp. patellaria var. glabrata@subsp. \textit{patellaria} var. \textit{glabrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉假含羞草&T2_new_value=true&fr=y}}{大葉假含羞草}\index{大葉假含羞草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamaecrista+nomame}{\textit{C. nomame} (Siebold) H.Ohashi}  \index{Chamaecrista@\textit{Chamaecrista}!nomame@\textit{nomame}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豆茶決明&T2_new_value=true&fr=y}}{豆茶決明}\index{豆茶決明} DD
  \end{itemize}
 \item[] \textit{Christia} 蝙蝠草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Christia+campanulata}{\textit{C. campanulata} (Benth.) Thoth.}  \index{Christia@\textit{Christia}!campanulata@\textit{campanulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蝙蝠草&T2_new_value=true&fr=y}}{蝙蝠草}\index{蝙蝠草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Christia+obcordata}{\textit{C. obcordata} (Poir.) Bakh.f. ex Meeuwen}  \index{Christia@\textit{Christia}!obcordata@\textit{obcordata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=舖地蝙蝠草&T2_new_value=true&fr=y}}{舖地蝙蝠草}\index{舖地蝙蝠草} LC
  \end{itemize}
 \item[] \textit{Clitoria} 蝶豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clitoria+falcata}{\textit{C. falcata} Lam.}  \index{Clitoria@\textit{Clitoria}!falcata@\textit{falcata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐮刀莢蝶豆&T2_new_value=true&fr=y}}{鐮刀莢蝶豆}\index{鐮刀莢蝶豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clitoria+ternatea}{\textit{C. ternatea} L.}  \index{Clitoria@\textit{Clitoria}!ternatea@\textit{ternatea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蝶豆&T2_new_value=true&fr=y}}{蝶豆}\index{蝶豆} NA$^n$
  \end{itemize}
 \item[] \textit{Codoriocalyx} 舞草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Codoriocalyx+motorius}{\textit{C. motorius} (Houtt.) H. Ohashi}  \index{Codoriocalyx@\textit{Codoriocalyx}!motorius@\textit{motorius}}  \index{Codariocalyx@\textit{Codariocalyx}!motorius@\textit{motorius}{\\\noindent(= \textit{Codoriocalyx motorius})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐘萼豆&T2_new_value=true&fr=y}}{鐘萼豆}\index{鐘萼豆} LC
  \end{itemize}
 \item[] \textit{Crotalaria} 野百合屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+acicularis}{\textit{C. acicularis} Buch.-Ham. ex Benth.}  \index{Crotalaria@\textit{Crotalaria}!acicularis@\textit{acicularis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉野百合&T2_new_value=true&fr=y}}{圓葉野百合}\index{圓葉野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+albida}{\textit{C. albida} Heyne ex Roth}  \index{Crotalaria@\textit{Crotalaria}!albida@\textit{albida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=響鈴豆&T2_new_value=true&fr=y}}{響鈴豆}\index{響鈴豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+bialata}{\textit{C. bialata} Schrank}  \index{Crotalaria@\textit{Crotalaria}!bialata@\textit{bialata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼莖野百合&T2_new_value=true&fr=y}}{翼莖野百合}\index{翼莖野百合} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+calycina}{\textit{C. calycina} Schrank}  \index{Crotalaria@\textit{Crotalaria}!calycina@\textit{calycina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長萼野百合&T2_new_value=true&fr=y}}{長萼野百合}\index{長萼野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+chiayiana}{\textit{C. chiayiana} Y.C.Liu \& F.Y.Lu}  \index{Crotalaria@\textit{Crotalaria}!chiayiana@\textit{chiayiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花假地藍&T2_new_value=true&fr=y}}{紅花假地藍}\index{紅花假地藍}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+chinensis}{\textit{C. chinensis} L.}  \index{Crotalaria@\textit{Crotalaria}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華野百合&T2_new_value=true&fr=y}}{華野百合}\index{華野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+elliptica}{\textit{C. elliptica} Roxb.}  \index{Crotalaria@\textit{Crotalaria}!elliptica@\textbf{\textit{elliptica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙子野百合&T2_new_value=true&fr=y}}{雙子野百合}\index{雙子野百合@{\Song{雙子野百合}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+ferruginea}{\textit{C. ferruginea} Graham ex Benth.}  \index{Crotalaria@\textit{Crotalaria}!ferruginea@\textit{ferruginea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假地藍&T2_new_value=true&fr=y}}{假地藍}\index{假地藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+goreensis}{\textit{C. goreensis} Guill. \& Perr.}  \index{Crotalaria@\textit{Crotalaria}!goreensis@\textit{goreensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=西非豬屎豆&T2_new_value=true&fr=y}}{西非豬屎豆}\index{西非豬屎豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+incana}{\textit{C. incana} L.}  \index{Crotalaria@\textit{Crotalaria}!incana@\textit{incana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春野百合&T2_new_value=true&fr=y}}{恆春野百合}\index{恆春野百合} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+juncea}{\textit{C. juncea} L}  \index{Crotalaria@\textit{Crotalaria}!juncea@\textit{juncea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太陽麻&T2_new_value=true&fr=y}}{太陽麻}\index{太陽麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+lanceolata}{\textit{C. lanceolata} E.Mey.}  \index{Crotalaria@\textit{Crotalaria}!lanceolata@\textit{lanceolata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=披針葉野百合&T2_new_value=true&fr=y}}{披針葉野百合}\index{披針葉野百合} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+linifolia}{\textit{C. linifolia} L.f.}  \index{Crotalaria@\textit{Crotalaria}!linifolia@\textit{linifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=線葉野百合&T2_new_value=true&fr=y}}{線葉野百合}\index{線葉野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+medicaginea}{\textit{C. medicaginea} Lam.}  \index{Crotalaria@\textit{Crotalaria}!medicaginea@\textit{medicaginea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假苜蓿&T2_new_value=true&fr=y}}{假苜蓿}\index{假苜蓿} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+micans}{\textit{C. micans} Link}  \index{Crotalaria@\textit{Crotalaria}!micans@\textit{micans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃豬屎豆&T2_new_value=true&fr=y}}{黃豬屎豆}\index{黃豬屎豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+pallida+var.+obovata}{\textit{C. pallida} Aiton var. \textit{obovata} (G.Don) Polhill}  \index{Crotalaria@\textit{Crotalaria}!pallida@\textit{pallida}!var. obovata@var. \textit{obovata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃野百合&T2_new_value=true&fr=y}}{黃野百合}\index{黃野百合} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+retusa}{\textit{C. retusa} L.}  \index{Crotalaria@\textit{Crotalaria}!retusa@\textit{retusa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹葉野百合&T2_new_value=true&fr=y}}{凹葉野百合}\index{凹葉野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+sessiliflora}{\textit{C. sessiliflora} L.}  \index{Crotalaria@\textit{Crotalaria}!sessiliflora@\textit{sessiliflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野百合&T2_new_value=true&fr=y}}{野百合}\index{野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+similes}{\textit{C. similes} Hemsl.}  \index{Crotalaria@\textit{Crotalaria}!similes@\textbf{\textit{similes}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝鑾鼻野百合&T2_new_value=true&fr=y}}{鵝鑾鼻野百合}\index{鵝鑾鼻野百合@{\Song{鵝鑾鼻野百合}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+spectabilis}{\textit{C. spectabilis} Roth}  \index{Crotalaria@\textit{Crotalaria}!spectabilis@\textit{spectabilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花野百合&T2_new_value=true&fr=y}}{紫花野百合}\index{紫花野百合} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+triquetra}{\textit{C. triquetra} Dalzell}  \index{Crotalaria@\textit{Crotalaria}!triquetra@\textit{triquetra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=砂地野百合&T2_new_value=true&fr=y}}{砂地野百合}\index{砂地野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+verrucosa}{\textit{C. verrucosa} L.}  \index{Crotalaria@\textit{Crotalaria}!verrucosa@\textit{verrucosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉野百合&T2_new_value=true&fr=y}}{大葉野百合}\index{大葉野百合} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crotalaria+zanzibarica}{\textit{C. zanzibarica} Benth.}  \index{Crotalaria@\textit{Crotalaria}!zanzibarica@\textit{zanzibarica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南美豬屎豆&T2_new_value=true&fr=y}}{南美豬屎豆}\index{南美豬屎豆} NA$^n$
  \end{itemize}
 \item[] \textit{Cyamopsis} 瓜兒豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyamopsis+tetragonoloba}{\textit{C. tetragonoloba} (L.) Toubert}  \index{Cyamopsis@\textit{Cyamopsis}!tetragonoloba@\textit{tetragonoloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓜兒豆&T2_new_value=true&fr=y}}{瓜兒豆}\index{瓜兒豆} NA$^n$
  \end{itemize}
 \item[] \textit{Dalbergia} 黃檀屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dalbergia+benthamii}{\textit{D. benthamii} Prain}  \index{Dalbergia@\textit{Dalbergia}!benthamii@\textit{benthamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藤黃檀&T2_new_value=true&fr=y}}{藤黃檀}\index{藤黃檀} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dalbergia+sissoo}{\textit{D. sissoo} DC.}  \index{Dalbergia@\textit{Dalbergia}!sissoo@\textit{sissoo}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度黃檀&T2_new_value=true&fr=y}}{印度黃檀}\index{印度黃檀} NA$^n$
  \end{itemize}
 \item[] \textit{Delonix} 鳳凰木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Delonix+regia}{\textit{D. regia} (Hook.) Raf.}  \index{Delonix@\textit{Delonix}!regia@\textit{regia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鳳凰木&T2_new_value=true&fr=y}}{鳳凰木}\index{鳳凰木} NA$^n$
  \end{itemize}
 \item[] \textit{Dendrolobium} 木山螞蝗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrolobium+dispermum}{\textit{D. dispermum} (Hayata) Schindl.}  \index{Dendrolobium@\textit{Dendrolobium}!dispermum@\textit{dispermum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙節山螞蝗&T2_new_value=true&fr=y}}{雙節山螞蝗}\index{雙節山螞蝗}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrolobium+trianglare}{\textit{D. trianglare} (Retz.) Schindl.}  \index{Dendrolobium@\textit{Dendrolobium}!trianglare@\textit{trianglare}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假木豆&T2_new_value=true&fr=y}}{假木豆}\index{假木豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrolobium+umbellatum}{\textit{D. umbellatum} (L.) Benth.}  \index{Dendrolobium@\textit{Dendrolobium}!umbellatum@\textit{umbellatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白木蘇花&T2_new_value=true&fr=y}}{白木蘇花}\index{白木蘇花} LC
  \end{itemize}
 \item[] \textit{Derris} 魚藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Derris+canarensis}{\textit{D. canarensis} (Dalzell) Baker}  \index{Derris@\textit{Derris}!canarensis@\textbf{\textit{canarensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼魚藤&T2_new_value=true&fr=y}}{蘭嶼魚藤}\index{蘭嶼魚藤@{\Song{蘭嶼魚藤}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Derris+elliptica}{\textit{D. elliptica} (Roxb.) Benth.}  \index{Derris@\textit{Derris}!elliptica@\textit{elliptica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛魚藤&T2_new_value=true&fr=y}}{毛魚藤}\index{毛魚藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Derris+laxiflora}{\textit{D. laxiflora} Benth.}  \index{Derris@\textit{Derris}!laxiflora@\textit{laxiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花魚藤&T2_new_value=true&fr=y}}{疏花魚藤}\index{疏花魚藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Derris+trifoliata}{\textit{D. trifoliata} Lour.}  \index{Derris@\textit{Derris}!trifoliata@\textit{trifoliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葉魚藤&T2_new_value=true&fr=y}}{三葉魚藤}\index{三葉魚藤} LC
  \end{itemize}
 \item[] \textit{Desmanthus} 草合歡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmanthus+virgatus}{\textit{D. virgatus} (L.) Willd.}  \index{Desmanthus@\textit{Desmanthus}!virgatus@\textit{virgatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多枝草合歡&T2_new_value=true&fr=y}}{多枝草合歡}\index{多枝草合歡} NA$^n$
  \end{itemize}
 \item[] \textit{Desmodium} 山螞蝗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+diffusum}{\textit{D. diffusum} DC.}  \index{Desmodium@\textit{Desmodium}!diffusum@\textit{diffusum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=散花山螞蝗&T2_new_value=true&fr=y}}{散花山螞蝗}\index{散花山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+gangeticum}{\textit{D. gangeticum} (L.) DC.}  \index{Desmodium@\textit{Desmodium}!gangeticum@\textit{gangeticum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉山螞蝗&T2_new_value=true&fr=y}}{大葉山螞蝗}\index{大葉山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+gracillimum}{\textit{D. gracillimum} Hemsl.}  \index{Desmodium@\textit{Desmodium}!gracillimum@\textbf{\textit{gracillimum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉山螞蝗&T2_new_value=true&fr=y}}{細葉山螞蝗}\index{細葉山螞蝗@{\Song{細葉山螞蝗}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+heterocarpon+var.+heterocarpon}{\textit{D. heterocarpon} (L.) DC. var. \textit{heterocarpon}}  \index{Desmodium@\textit{Desmodium}!heterocarpon@\textit{heterocarpon}!var. heterocarpon@var. \textit{heterocarpon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假地豆&T2_new_value=true&fr=y}}{假地豆}\index{假地豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+heterocarpon+var.+strigosum}{\textit{D. heterocarpon} (L.) DC. var. \textit{strigosum} Meeuwen}  \index{Desmodium@\textit{Desmodium}!heterocarpon@\textit{heterocarpon}!var. strigosum@var. \textit{strigosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=直毛假地豆&T2_new_value=true&fr=y}}{直毛假地豆}\index{直毛假地豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+heterophyllum}{\textit{D. heterophyllum} (Willd.) DC.}  \index{Desmodium@\textit{Desmodium}!heterophyllum@\textit{heterophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉山螞蝗&T2_new_value=true&fr=y}}{變葉山螞蝗}\index{變葉山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+intortum}{\textit{D. intortum} (DC.) Urb.}  \index{Desmodium@\textit{Desmodium}!intortum@\textit{intortum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=西班牙三葉草&T2_new_value=true&fr=y}}{西班牙三葉草}\index{西班牙三葉草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+laxiflorum}{\textit{D. laxiflorum} DC.}  \index{Desmodium@\textit{Desmodium}!laxiflorum@\textit{laxiflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花山螞蝗&T2_new_value=true&fr=y}}{疏花山螞蝗}\index{疏花山螞蝗} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+microphyllum}{\textit{D. microphyllum} (Thunb.) DC.}  \index{Desmodium@\textit{Desmodium}!microphyllum@\textit{microphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉山螞蝗&T2_new_value=true&fr=y}}{小葉山螞蝗}\index{小葉山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+multiflorum}{\textit{D. multiflorum} DC.}  \index{Desmodium@\textit{Desmodium}!multiflorum@\textit{multiflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多花山螞蝗&T2_new_value=true&fr=y}}{多花山螞蝗}\index{多花山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+renifolium}{\textit{D. renifolium} (L.) Schindl.}  \index{Desmodium@\textit{Desmodium}!renifolium@\textbf{\textit{renifolium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腎葉山螞蝗&T2_new_value=true&fr=y}}{腎葉山螞蝗}\index{腎葉山螞蝗@{\Song{腎葉山螞蝗}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+scorpiurus}{\textit{D. scorpiurus} (Sw.) Desv.}  \index{Desmodium@\textit{Desmodium}!scorpiurus@\textit{scorpiurus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蝦尾山螞蝗&T2_new_value=true&fr=y}}{蝦尾山螞蝗}\index{蝦尾山螞蝗} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+sequax}{\textit{D. sequax} Wall.}  \index{Desmodium@\textit{Desmodium}!sequax@\textit{sequax}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=波葉山螞蝗&T2_new_value=true&fr=y}}{波葉山螞蝗}\index{波葉山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+tortuosum}{\textit{D. tortuosum} (SW.) DC.}  \index{Desmodium@\textit{Desmodium}!tortuosum@\textit{tortuosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花山螞蝗&T2_new_value=true&fr=y}}{紫花山螞蝗}\index{紫花山螞蝗} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+triflorum}{\textit{D. triflorum} (L.) DC.}  \index{Desmodium@\textit{Desmodium}!triflorum@\textit{triflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蠅翼草&T2_new_value=true&fr=y}}{蠅翼草}\index{蠅翼草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+uncinatum}{\textit{D. uncinatum} (Jacq.) DC.}  \index{Desmodium@\textit{Desmodium}!uncinatum@\textit{uncinatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀葉藤&T2_new_value=true&fr=y}}{銀葉藤}\index{銀葉藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+velutinum}{\textit{D. velutinum} (Willd.) DC.}  \index{Desmodium@\textit{Desmodium}!velutinum@\textit{velutinum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絨毛葉山螞蝗&T2_new_value=true&fr=y}}{絨毛葉山螞蝗}\index{絨毛葉山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Desmodium+zonatum}{\textit{D. zonatum} Miq.}  \index{Desmodium@\textit{Desmodium}!zonatum@\textit{zonatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單葉拿身草&T2_new_value=true&fr=y}}{單葉拿身草}\index{單葉拿身草} LC
  \end{itemize}
 \item[] \textit{Dolichos} 扁豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dolichos+trilobus+var.+kosyunensis}{\textit{D. trilobus} L. var. \textit{kosyunensis} (Hosok.) H.Ohashi \& Tateishi}  \index{Dolichos@\textit{Dolichos}!trilobus@\textit{trilobus}!var. kosyunensis@\textbf{var. \textit{kosyunensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三裂葉扁豆&T2_new_value=true&fr=y}}{三裂葉扁豆}\index{三裂葉扁豆@{\Song{三裂葉扁豆}}}\# VU
  \end{itemize}
 \item[] \textit{Dumasia} 山黑扁豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dumasia+miaoliensis}{\textit{D. miaoliensis} Y.C.Liu \& F.Y.Lu}  \index{Dumasia@\textit{Dumasia}!miaoliensis@\textbf{\textit{miaoliensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苗栗野豇豆&T2_new_value=true&fr=y}}{苗栗野豇豆}\index{苗栗野豇豆@{\Song{苗栗野豇豆}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dumasia+villosa+subsp.+bicolor}{\textit{D. villosa} DC. subsp. \textit{bicolor} (Hayata) H.Ohashi \& Tateishi}  \index{Dumasia@\textit{Dumasia}!villosa@\textit{villosa}!subsp. bicolor@subsp. \textit{bicolor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山黑扁豆&T2_new_value=true&fr=y}}{臺灣山黑扁豆}\index{臺灣山黑扁豆}\# LC
  \end{itemize}
 \item[] \textit{Dunbaria} 野扁豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dunbaria+merrillii}{\textit{D. merrillii} Elmer}  \index{Dunbaria@\textit{Dunbaria}!merrillii@\textbf{\textit{merrillii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=麥氏野扁豆&T2_new_value=true&fr=y}}{麥氏野扁豆}\index{麥氏野扁豆@{\Song{麥氏野扁豆}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dunbaria+rotundifolia}{\textit{D. rotundifolia} (Lour.) Merr.}  \index{Dunbaria@\textit{Dunbaria}!rotundifolia@\textit{rotundifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉野扁豆&T2_new_value=true&fr=y}}{圓葉野扁豆}\index{圓葉野扁豆} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dunbaria+villosa}{\textit{D. villosa} (Thunb.) Makino}  \index{Dunbaria@\textit{Dunbaria}!villosa@\textit{villosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛野扁豆&T2_new_value=true&fr=y}}{毛野扁豆}\index{毛野扁豆} LC
  \end{itemize}
 \item[] \textit{Dysolobium} 毛豇豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dysolobium+pilosum}{\textit{D. pilosum} (Willd.) Maréchal}  \index{Dysolobium@\textit{Dysolobium}!pilosum@\textit{pilosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛豇豆&T2_new_value=true&fr=y}}{毛豇豆}\index{毛豇豆} NT
  \end{itemize}
 \item[] \textit{Entada} 鴨腱藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Entada+koshunensis}{\textit{E. koshunensis} Hayata \& Kaneh.}  \index{Entada@\textit{Entada}!koshunensis@\textbf{\textit{koshunensis}}}  \index{Entada@\textit{Entada}!parvifolia@\textit{parvifolia}{\\\noindent(= \textit{Entada koshunensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春鴨腱藤&T2_new_value=true&fr=y}}{恆春鴨腱藤}\index{恆春鴨腱藤@{\Song{恆春鴨腱藤}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Entada+phaseoloides+subsp.+phaseoloides}{\textit{E. phaseoloides} (L.) Merr. subsp. \textit{phaseoloides}}  \index{Entada@\textit{Entada}!phaseoloides@\textit{phaseoloides}!subsp. phaseoloides@subsp. \textit{phaseoloides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=榼藤子&T2_new_value=true&fr=y}}{榼藤子}\index{榼藤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Entada+phaseoloides+subsp.+tonkinensis}{\textit{E. phaseoloides} (L.) Merr. subsp. \textit{tonkinensis} (Gagnep.) H.Ohashi}  \index{Entada@\textit{Entada}!phaseoloides@\textit{phaseoloides}!subsp. tonkinensis@subsp. \textit{tonkinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=越南鴨腱藤&T2_new_value=true&fr=y}}{越南鴨腱藤}\index{越南鴨腱藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Entada+rheedei}{\textit{E. rheedei} Spreng.}  \index{Entada@\textit{Entada}!rheedei@\textit{rheedei}}  \index{Entada@\textit{Entada}!pursaetha@\textit{pursaetha}{\\\noindent(= \textit{Entada rheedei})}}   \index{Entada@\textit{Entada}!pursaetha@\textit{pursaetha}!var. formosana@var. \textit{formosana}{\\\noindent(=\textit{Entada rheedei})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚殼鴨腱藤&T2_new_value=true&fr=y}}{厚殼鴨腱藤(鴨腱藤)} \index{厚殼鴨腱藤} \index{鴨腱藤@{鴨腱藤(=厚殼鴨腱藤)}} LC
  \end{itemize}
 \item[] \textit{Eriosema} 豬仔笠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eriosema+chinense}{\textit{E. chinense} Vogel}  \index{Eriosema@\textit{Eriosema}!chinense@\textbf{\textit{chinense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豬仔笠&T2_new_value=true&fr=y}}{豬仔笠}\index{豬仔笠@{\Song{豬仔笠}}} VU
  \end{itemize}
 \item[] \textit{Erythrina} 刺桐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrina+variegata}{\textit{E. variegata} L.}  \index{Erythrina@\textit{Erythrina}!variegata@\textit{variegata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺桐&T2_new_value=true&fr=y}}{刺桐}\index{刺桐} LC
  \end{itemize}
 \item[] \textit{Euchresta} 山豆根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euchresta+formosana}{\textit{E. formosana} (Hayata) Ohwi}  \index{Euchresta@\textit{Euchresta}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山豆根&T2_new_value=true&fr=y}}{臺灣山豆根}\index{臺灣山豆根} LC
  \end{itemize}
 \item[] \textit{Flemingia} 佛來明豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flemingia+lineata}{\textit{F. lineata} (L.) Roxb.}  \index{Flemingia@\textit{Flemingia}!lineata@\textit{lineata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=線葉佛來明豆&T2_new_value=true&fr=y}}{線葉佛來明豆}\index{線葉佛來明豆} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flemingia+macrophylla+var.+macrophylla}{\textit{F. macrophylla} (Willd.) Kuntze ex Prain var. \textit{macrophylla}}  \index{Flemingia@\textit{Flemingia}!macrophylla@\textit{macrophylla}!var. macrophylla@var. \textit{macrophylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉佛來明豆&T2_new_value=true&fr=y}}{大葉佛來明豆}\index{大葉佛來明豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flemingia+macrophylla+var.+philippinensis}{\textit{F. macrophylla} (Willd.) Kuntze ex Prain var. \textit{philippinensis} (Merr. \& Rofle) H.Ohashi}  \index{Flemingia@\textit{Flemingia}!macrophylla@\textit{macrophylla}!var. philippinensis@var. \textit{philippinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲島佛來明豆&T2_new_value=true&fr=y}}{菲島佛來明豆}\index{菲島佛來明豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flemingia+strobilifera}{\textit{F. strobilifera} (L.) R.Br. ex W.T.Aiton}  \index{Flemingia@\textit{Flemingia}!strobilifera@\textit{strobilifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=佛來明豆&T2_new_value=true&fr=y}}{佛來明豆}\index{佛來明豆} LC
  \end{itemize}
 \item[] \textit{Galactia} 乳豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galactia+tashiroi}{\textit{G. tashiroi} Maxim.}  \index{Galactia@\textit{Galactia}!tashiroi@\textit{tashiroi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田代氏乳豆&T2_new_value=true&fr=y}}{田代氏乳豆}\index{田代氏乳豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galactia+tenuiflora+var.+tenuiflora}{\textit{G. tenuiflora} (Klein ex Willd.) Wight \& Arn. var. \textit{tenuiflora}}  \index{Galactia@\textit{Galactia}!tenuiflora@\textit{tenuiflora}!var. tenuiflora@var. \textit{tenuiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細花乳豆&T2_new_value=true&fr=y}}{細花乳豆}\index{細花乳豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galactia+tenuiflora+var.+villosa}{\textit{G. tenuiflora} (Klein ex Willd.) Wight \& Arn. var. \textit{villosa} (Wight \& Arn.) Baker}  \index{Galactia@\textit{Galactia}!tenuiflora@\textit{tenuiflora}!var. villosa@var. \textit{villosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛細花乳豆&T2_new_value=true&fr=y}}{毛細花乳豆}\index{毛細花乳豆}\# LC
  \end{itemize}
 \item[] \textit{Gleditsia} 皂莢屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gleditsia+rolfei}{\textit{G. rolfei} Vidal}  \index{Gleditsia@\textit{Gleditsia}!rolfei@\textbf{\textit{rolfei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春皂莢&T2_new_value=true&fr=y}}{恆春皂莢}\index{恆春皂莢@{\Song{恆春皂莢}}} VU
  \end{itemize}
 \item[] \textit{Glycine} 大豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycine+dolichocarpa}{\textit{G. dolichocarpa} Tateishi \& H.Ohashi}  \index{Glycine@\textit{Glycine}!dolichocarpa@\textbf{\textit{dolichocarpa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=扁豆莢大豆&T2_new_value=true&fr=y}}{扁豆莢大豆}\index{扁豆莢大豆@{\Song{扁豆莢大豆}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycine+max+subsp.+formosana}{\textit{G. max} (L.) Merr. subsp. \textit{formosana} (Hosok.) Tateishi \& H.Ohashi}  \index{Glycine@\textit{Glycine}!max@\textit{max}!subsp. formosana@\textbf{subsp. \textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣大豆&T2_new_value=true&fr=y}}{臺灣大豆}\index{臺灣大豆@{\Song{臺灣大豆}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycine+tabacina}{\textit{G. tabacina} (Labill.) Benth}  \index{Glycine@\textit{Glycine}!tabacina@\textbf{\textit{tabacina}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澎湖大豆&T2_new_value=true&fr=y}}{澎湖大豆}\index{澎湖大豆@{\Song{澎湖大豆}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycine+tomentella}{\textit{G. tomentella} Hayata}  \index{Glycine@\textit{Glycine}!tomentella@\textit{tomentella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉大豆&T2_new_value=true&fr=y}}{闊葉大豆}\index{闊葉大豆} LC
  \end{itemize}
 \item[] \textit{Haematoxylum} 墨水樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haematoxylum+campechianum}{\textit{H. campechianum} L.}  \index{Haematoxylum@\textit{Haematoxylum}!campechianum@\textit{campechianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=墨水樹&T2_new_value=true&fr=y}}{墨水樹}\index{墨水樹} NA$^n$
  \end{itemize}
 \item[] \textit{Hylodesmum} 長柄山螞蝗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylodesmum+densum}{\textit{H. densum} (C.Chen \& X.J.Cui) H.Ohashi \& R.R.Mill}  \index{Hylodesmum@\textit{Hylodesmum}!densum@\textbf{\textit{densum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菱葉山螞蝗&T2_new_value=true&fr=y}}{菱葉山螞蝗}\index{菱葉山螞蝗@{\Song{菱葉山螞蝗}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylodesmum+laterale}{\textit{H. laterale} (Schindl.) H.Ohashi \& R.R.Mill}  \index{Hylodesmum@\textit{Hylodesmum}!laterale@\textit{laterale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球山螞蝗&T2_new_value=true&fr=y}}{琉球山螞蝗}\index{琉球山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylodesmum+leptopus}{\textit{H. leptopus} (A.Gray ex Benth.) H.Ohashi \& R.R.Mill}  \index{Hylodesmum@\textit{Hylodesmum}!leptopus@\textit{leptopus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細梗山螞蝗&T2_new_value=true&fr=y}}{細梗山螞蝗}\index{細梗山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylodesmum+podocarpum+subsp.+oxyphyllum}{\textit{H. podocarpum} (DC.) H.Ohashi \& R.R.Mill subsp. \textit{oxyphyllum} (DC.) H.Ohashi \& R.R.Mill}  \index{Hylodesmum@\textit{Hylodesmum}!podocarpum@\textit{podocarpum}!subsp. oxyphyllum@subsp. \textit{oxyphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小山螞蝗&T2_new_value=true&fr=y}}{小山螞蝗}\index{小山螞蝗} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylodesmum+podocarpum+var.+podocarpum}{\textit{H. podocarpum} (DC.) H.Ohashi \& R.R.Mill subsp. \textit{podocarpum}}  \index{Hylodesmum@\textit{Hylodesmum}!podocarpum@\textit{podocarpum}!var. podocarpum@\textbf{var. \textit{podocarpum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓菱葉山螞蝗&T2_new_value=true&fr=y}}{圓菱葉山螞蝗}\index{圓菱葉山螞蝗@{\Song{圓菱葉山螞蝗}}} VU
  \end{itemize}
 \item[] \textit{Indigofera} 木藍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+byobiensis}{\textit{I. byobiensis} Hosok.}  \index{Indigofera@\textit{Indigofera}!byobiensis@\textbf{\textit{byobiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貓鼻頭木藍&T2_new_value=true&fr=y}}{貓鼻頭木藍}\index{貓鼻頭木藍@{\Song{貓鼻頭木藍}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+galegoides}{\textit{I. galegoides} DC.}  \index{Indigofera@\textit{Indigofera}!galegoides@\textit{galegoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假大青藍&T2_new_value=true&fr=y}}{假大青藍}\index{假大青藍} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+glandulifera}{\textit{I. glandulifera} Hayata}  \index{Indigofera@\textit{Indigofera}!glandulifera@\textit{glandulifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺葉木藍&T2_new_value=true&fr=y}}{腺葉木藍}\index{腺葉木藍}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+hirsuta}{\textit{I. hirsuta} L.}  \index{Indigofera@\textit{Indigofera}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛木藍&T2_new_value=true&fr=y}}{毛木藍}\index{毛木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+linifolia}{\textit{I. linifolia} (L.f.) Retz.}  \index{Indigofera@\textit{Indigofera}!linifolia@\textit{linifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉木藍&T2_new_value=true&fr=y}}{細葉木藍}\index{細葉木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+nigrescens}{\textit{I. nigrescens} Kurz ex Prain}  \index{Indigofera@\textit{Indigofera}!nigrescens@\textit{nigrescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑木藍&T2_new_value=true&fr=y}}{黑木藍}\index{黑木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+pedicellata}{\textit{I. pedicellata} Wight \& Arn.}  \index{Indigofera@\textit{Indigofera}!pedicellata@\textbf{\textit{pedicellata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長梗木藍&T2_new_value=true&fr=y}}{長梗木藍}\index{長梗木藍@{\Song{長梗木藍}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+pseudo-tinctoria}{\textit{I. pseudo-tinctoria} Matsum.}  \index{Indigofera@\textit{Indigofera}!pseudo-tinctoria@\textit{pseudo-tinctoria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬棘&T2_new_value=true&fr=y}}{馬棘}\index{馬棘} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+ramulosissima}{\textit{I. ramulosissima} Hosok.}  \index{Indigofera@\textit{Indigofera}!ramulosissima@\textbf{\textit{ramulosissima}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣木藍&T2_new_value=true&fr=y}}{太魯閣木藍}\index{太魯閣木藍@{\Song{太魯閣木藍}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+spicata}{\textit{I. spicata} Forssk.}  \index{Indigofera@\textit{Indigofera}!spicata@\textit{spicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=穗花木藍&T2_new_value=true&fr=y}}{穗花木藍}\index{穗花木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+suffruticosa}{\textit{I. suffruticosa} Mill.}  \index{Indigofera@\textit{Indigofera}!suffruticosa@\textit{suffruticosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野木藍&T2_new_value=true&fr=y}}{野木藍}\index{野木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+taiwaniana}{\textit{I. taiwaniana} T.C.Huang \& M.J.Wu}  \index{Indigofera@\textit{Indigofera}!taiwaniana@\textbf{\textit{taiwaniana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣木藍&T2_new_value=true&fr=y}}{臺灣木藍}\index{臺灣木藍@{\Song{臺灣木藍}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+tinctoria}{\textit{I. tinctoria} L.}  \index{Indigofera@\textit{Indigofera}!tinctoria@\textit{tinctoria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木藍&T2_new_value=true&fr=y}}{木藍}\index{木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+trifoliata}{\textit{I. trifoliata} L.}  \index{Indigofera@\textit{Indigofera}!trifoliata@\textit{trifoliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葉木藍&T2_new_value=true&fr=y}}{三葉木藍}\index{三葉木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+venulosa}{\textit{I. venulosa} Champ. ex Benth.}  \index{Indigofera@\textit{Indigofera}!venulosa@\textit{venulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=脈葉木藍&T2_new_value=true&fr=y}}{脈葉木藍}\index{脈葉木藍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Indigofera+zollingeriana}{\textit{I. zollingeriana} Miq.}  \index{Indigofera@\textit{Indigofera}!zollingeriana@\textbf{\textit{zollingeriana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼木藍&T2_new_value=true&fr=y}}{蘭嶼木藍}\index{蘭嶼木藍@{\Song{蘭嶼木藍}}} VU
  \end{itemize}
 \item[] \textit{Kummerowia} 雞眼草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kummerowia+stipulacea}{\textit{K. stipulacea} (Maxim.) Makino}  \index{Kummerowia@\textit{Kummerowia}!stipulacea@\textbf{\textit{stipulacea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉雞眼草&T2_new_value=true&fr=y}}{圓葉雞眼草}\index{圓葉雞眼草@{\Song{圓葉雞眼草}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kummerowia+striata}{\textit{K. striata} (Thunb.) Schindl.}  \index{Kummerowia@\textit{Kummerowia}!striata@\textit{striata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞眼草&T2_new_value=true&fr=y}}{雞眼草}\index{雞眼草} LC
  \end{itemize}
 \item[] \textit{Lablab} 鵲豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lablab+purpureus}{\textit{L. purpureus} (L.) Sweet}  \index{Lablab@\textit{Lablab}!purpureus@\textit{purpureus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵲豆&T2_new_value=true&fr=y}}{鵲豆}\index{鵲豆} NA$^n$
  \end{itemize}
 \item[] \textit{Lespedeza} 胡枝子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lespedeza+chinensis}{\textit{L. chinensis} G.Don.}  \index{Lespedeza@\textit{Lespedeza}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華胡枝子&T2_new_value=true&fr=y}}{華胡枝子}\index{華胡枝子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lespedeza+cuneata}{\textit{L. cuneata} (Dum-Cours.) G.Don.}  \index{Lespedeza@\textit{Lespedeza}!cuneata@\textit{cuneata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐵掃帚&T2_new_value=true&fr=y}}{鐵掃帚}\index{鐵掃帚} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lespedeza+daurica}{\textit{L. daurica} (Laxm.) Schindl.}  \index{Lespedeza@\textit{Lespedeza}!daurica@\textbf{\textit{daurica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大胡枝子&T2_new_value=true&fr=y}}{大胡枝子}\index{大胡枝子@{\Song{大胡枝子}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lespedeza+thunbergii+subsp.+formosa}{\textit{L. thunbergii} (DC.) Nakai subsp. \textit{formosa} (Vogel) H.Ohashi}  \index{Lespedeza@\textit{Lespedeza}!thunbergii@\textit{thunbergii}!subsp. formosa@subsp. \textit{formosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛胡枝子&T2_new_value=true&fr=y}}{毛胡枝子}\index{毛胡枝子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lespedeza+virgata}{\textit{L. virgata} (Thunb.) DC.}  \index{Lespedeza@\textit{Lespedeza}!virgata@\textit{virgata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細梗胡枝子&T2_new_value=true&fr=y}}{細梗胡枝子}\index{細梗胡枝子} LC
  \end{itemize}
 \item[] \textit{Leucaena} 銀合歡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leucaena+leucocephala}{\textit{L. leucocephala} (Lam.) de Wit}  \index{Leucaena@\textit{Leucaena}!leucocephala@\textit{leucocephala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀合歡&T2_new_value=true&fr=y}}{銀合歡}\index{銀合歡} NA$^n$
  \end{itemize}
 \item[] \textit{Lotus} 百脈根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lotus+corniculatus+subsp.+japonicus}{\textit{L. corniculatus} L. subsp. \textit{japonicus} (Regel) H.Ohashi}  \index{Lotus@\textit{Lotus}!corniculatus@\textit{corniculatus}!subsp. japonicus@subsp. \textit{japonicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=百脈根&T2_new_value=true&fr=y}}{百脈根}\index{百脈根} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lotus+pacifica}{\textit{L. pacifica} Kramina \& D.D.Sokollof}  \index{Lotus@\textit{Lotus}!pacifica@\textbf{\textit{pacifica}}}  \index{Lotus@\textit{Lotus}!australis@\textit{australis}{\\\noindent(= \textit{Lotus pacifica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼百脈根&T2_new_value=true&fr=y}}{蘭嶼百脈根}\index{蘭嶼百脈根@{\Song{蘭嶼百脈根}}} VU
  \end{itemize}
 \item[] \textit{Maackia} 馬鞍樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maackia+taiwanensis}{\textit{M. taiwanensis} Hoshi \& H.Ohashi}  \index{Maackia@\textit{Maackia}!taiwanensis@\textbf{\textit{taiwanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣馬鞍樹&T2_new_value=true&fr=y}}{臺灣馬鞍樹}\index{臺灣馬鞍樹@{\Song{臺灣馬鞍樹}}}\# VU
  \end{itemize}
 \item[] \textit{Macroptilium} 賽芻豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macroptilium+atropurpureus}{\textit{M. atropurpureus} (DC.) Urb.}  \index{Macroptilium@\textit{Macroptilium}!atropurpureus@\textit{atropurpureus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賽芻豆&T2_new_value=true&fr=y}}{賽芻豆}\index{賽芻豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macroptilium+bracteatum}{\textit{M. bracteatum} (Nees \& Mart.) Maréchal \& Baudet}  \index{Macroptilium@\textit{Macroptilium}!bracteatum@\textit{bracteatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苞葉賽芻豆&T2_new_value=true&fr=y}}{苞葉賽芻豆}\index{苞葉賽芻豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macroptilium+lathyroides}{\textit{M. lathyroides} (L.) Urb.}  \index{Macroptilium@\textit{Macroptilium}!lathyroides@\textit{lathyroides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬翼豆&T2_new_value=true&fr=y}}{寬翼豆}\index{寬翼豆} NA$^n$
  \end{itemize}
 \item[] \textit{Macrotyloma} 長硬皮豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macrotyloma+uniflorum}{\textit{M. uniflorum} (Lam.) Verdc.}  \index{Macrotyloma@\textit{Macrotyloma}!uniflorum@\textit{uniflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長硬皮豆&T2_new_value=true&fr=y}}{長硬皮豆}\index{長硬皮豆} DD
  \end{itemize}
 \item[] \textit{Medicago} 苜蓿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medicago+arabica}{\textit{M. arabica} (L.) Huds.}  \index{Medicago@\textit{Medicago}!arabica@\textit{arabica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=褐斑苜蓿&T2_new_value=true&fr=y}}{褐斑苜蓿}\index{褐斑苜蓿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medicago+lupulina}{\textit{M. lupulina} L.}  \index{Medicago@\textit{Medicago}!lupulina@\textit{lupulina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天藍苜蓿&T2_new_value=true&fr=y}}{天藍苜蓿}\index{天藍苜蓿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medicago+minima}{\textit{M. minima} (L.) Bartal.}  \index{Medicago@\textit{Medicago}!minima@\textit{minima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小苜蓿&T2_new_value=true&fr=y}}{小苜蓿}\index{小苜蓿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medicago+polymorpha}{\textit{M. polymorpha} L.}  \index{Medicago@\textit{Medicago}!polymorpha@\textit{polymorpha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苜蓿&T2_new_value=true&fr=y}}{苜蓿}\index{苜蓿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medicago+sativa}{\textit{M. sativa} L.}  \index{Medicago@\textit{Medicago}!sativa@\textit{sativa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫苜蓿&T2_new_value=true&fr=y}}{紫苜蓿}\index{紫苜蓿} NA$^n$
  \end{itemize}
 \item[] \textit{Melilotus} 草木樨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melilotus+indicus}{\textit{M. indicus} (L.) All.}  \index{Melilotus@\textit{Melilotus}!indicus@\textit{indicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度草木樨&T2_new_value=true&fr=y}}{印度草木樨}\index{印度草木樨} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melilotus+officinalis}{\textit{M. officinalis} (L.) Pall.}  \index{Melilotus@\textit{Melilotus}!officinalis@\textit{officinalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃香草木樨&T2_new_value=true&fr=y}}{黃香草木樨}\index{黃香草木樨} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melilotus+suaveolens}{\textit{M. suaveolens} Ledeb.}  \index{Melilotus@\textit{Melilotus}!suaveolens@\textit{suaveolens}}  \index{Melilotus@\textit{Melilotus}!officinalis@\textit{officinalis}!subsp. suaveolens@subsp. \textit{suaveolens}{\\\noindent(=\textit{Melilotus suaveolens})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=草木樨&T2_new_value=true&fr=y}}{草木樨}\index{草木樨} LC
  \end{itemize}
 \item[] \textit{Millettia} 老荊藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Millettia+pachycarpa}{\textit{M. pachycarpa} Benth.}  \index{Millettia@\textit{Millettia}!pachycarpa@\textit{pachycarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣魚藤&T2_new_value=true&fr=y}}{臺灣魚藤}\index{臺灣魚藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Millettia+pinnata}{\textit{M. pinnata} (L.) G.Panigrahi}  \index{Millettia@\textit{Millettia}!pinnata@\textit{pinnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水黃皮&T2_new_value=true&fr=y}}{水黃皮}\index{水黃皮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Millettia+pulchra+var.+microphylla}{\textit{M. pulchra} (Benth.) Kurz. var. \textit{microphylla} Dunn}  \index{Millettia@\textit{Millettia}!pulchra@\textit{pulchra}!var. microphylla@\textbf{var. \textit{microphylla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉魚藤&T2_new_value=true&fr=y}}{小葉魚藤}\index{小葉魚藤@{\Song{小葉魚藤}}}\# CR
  \end{itemize}
 \item[] \textit{Mimosa} 含羞草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mimosa+diplotricha}{\textit{M. diplotricha} C.Wright ex Sauvalle}  \index{Mimosa@\textit{Mimosa}!diplotricha@\textit{diplotricha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=美洲含羞草&T2_new_value=true&fr=y}}{美洲含羞草}\index{美洲含羞草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mimosa+pigra}{\textit{M. pigra} L.}  \index{Mimosa@\textit{Mimosa}!pigra@\textit{pigra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺軸含羞木&T2_new_value=true&fr=y}}{刺軸含羞木}\index{刺軸含羞木} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mimosa+pudica}{\textit{M. pudica} L.}  \index{Mimosa@\textit{Mimosa}!pudica@\textit{pudica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=含羞草&T2_new_value=true&fr=y}}{含羞草}\index{含羞草} NA$^n$
  \end{itemize}
 \item[] \textit{Mucuna} 血藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mucuna+gigantea+subsp.+tashiroi}{\textit{M. gigantea} (Willd.) DC. subsp. \textit{tashiroi} (Hayata) H.Ohashi \& Tateishi}  \index{Mucuna@\textit{Mucuna}!gigantea@\textit{gigantea}!subsp. tashiroi@\textbf{subsp. \textit{tashiroi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大血藤&T2_new_value=true&fr=y}}{大血藤}\index{大血藤@{\Song{大血藤}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mucuna+macrocarpa}{\textit{M. macrocarpa} Wall.}  \index{Mucuna@\textit{Mucuna}!macrocarpa@\textit{macrocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=血藤&T2_new_value=true&fr=y}}{血藤}\index{血藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mucuna+membranacea}{\textit{M. membranacea} Hayata}  \index{Mucuna@\textit{Mucuna}!membranacea@\textbf{\textit{membranacea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼血藤&T2_new_value=true&fr=y}}{蘭嶼血藤}\index{蘭嶼血藤@{\Song{蘭嶼血藤}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mucuna+pruriens+var.+pruriens}{\textit{M. pruriens} (L.) DC. var. \textit{pruriens}}  \index{Mucuna@\textit{Mucuna}!pruriens@\textit{pruriens}!var. pruriens@var. \textit{pruriens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花黎豆&T2_new_value=true&fr=y}}{白花黎豆}\index{白花黎豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mucuna+pruriens+var.+utilis}{\textit{M. pruriens} (L.) DC. var. \textit{utilis} (Wall. ex Wight) Burck}  \index{Mucuna@\textit{Mucuna}!pruriens@\textit{pruriens}!var. utilis@var. \textit{utilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虎爪豆&T2_new_value=true&fr=y}}{虎爪豆}\index{虎爪豆} NA$^n$
  \end{itemize}
 \item[] \textit{Neonotonia} 爪哇大豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neonotonia+wightii}{\textit{N. wightii} (Wight \& Arn.) Lackey}  \index{Neonotonia@\textit{Neonotonia}!wightii@\textit{wightii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=爪哇大豆&T2_new_value=true&fr=y}}{爪哇大豆}\index{爪哇大豆} NA$^n$
  \end{itemize}
 \item[] \textit{Neptunia} 細枝水合歡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neptunia+gracilis}{\textit{N. gracilis} Benth.}  \index{Neptunia@\textit{Neptunia}!gracilis@\textit{gracilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細枝水合歡&T2_new_value=true&fr=y}}{細枝水合歡}\index{細枝水合歡} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neptunia+plena}{\textit{N. plena} (L.) Benth.}  \index{Neptunia@\textit{Neptunia}!plena@\textit{plena}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=直立水含羞草&T2_new_value=true&fr=y}}{直立水含羞草}\index{直立水含羞草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neptunia+pubescens}{\textit{N. pubescens} Benth. }  \index{Neptunia@\textit{Neptunia}!pubescens@\textit{pubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛水含羞&T2_new_value=true&fr=y}}{毛水含羞}\index{毛水含羞} NA$^n$
  \end{itemize}
 \item[] \textit{Ohwia} 小槐花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ohwia+caudata}{\textit{O. caudata} (Thunb.) H.Ohashi}  \index{Ohwia@\textit{Ohwia}!caudata@\textit{caudata}}  \index{Desmodium@\textit{Desmodium}!caudatum@\textit{caudatum}{\\\noindent(= \textit{Ohwia caudata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小槐花&T2_new_value=true&fr=y}}{小槐花}\index{小槐花} DD
  \end{itemize}
 \item[] \textit{Ormocarpum} 濱槐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ormocarpum+cochinchinensis}{\textit{O. cochinchinensis} (Lour.) Merr}  \index{Ormocarpum@\textit{Ormocarpum}!cochinchinensis@\textbf{\textit{cochinchinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱槐&T2_new_value=true&fr=y}}{濱槐}\index{濱槐@{\Song{濱槐}}} VU
  \end{itemize}
 \item[] \textit{Ormosia} 紅豆樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ormosia+formosana}{\textit{O. formosana} Kaneh.}  \index{Ormosia@\textit{Ormosia}!formosana@\textbf{\textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣紅豆樹&T2_new_value=true&fr=y}}{臺灣紅豆樹}\index{臺灣紅豆樹@{\Song{臺灣紅豆樹}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ormosia+hengchuniana}{\textit{O. hengchuniana} T.C.Huang, S.F.Huang \& K.C.Yang}  \index{Ormosia@\textit{Ormosia}!hengchuniana@\textit{hengchuniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春紅豆樹&T2_new_value=true&fr=y}}{恆春紅豆樹}\index{恆春紅豆樹}\# NT
  \end{itemize}
 \item[] \textit{Pachyrhizus} 豆薯屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pachyrhizus+erosus}{\textit{P. erosus} (L.) Urb.}  \index{Pachyrhizus@\textit{Pachyrhizus}!erosus@\textit{erosus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豆薯&T2_new_value=true&fr=y}}{豆薯}\index{豆薯} NA$^n$
  \end{itemize}
 \item[] \textit{Phyllodium} 排錢樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllodium+pulchellum}{\textit{P. pulchellum} (L.) Desv.}  \index{Phyllodium@\textit{Phyllodium}!pulchellum@\textit{pulchellum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=排錢樹&T2_new_value=true&fr=y}}{排錢樹}\index{排錢樹} LC
  \end{itemize}
 \item[] \textit{Psoralea} 補骨脂屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psoralea+corylifolia}{\textit{P. corylifolia} L.}  \index{Psoralea@\textit{Psoralea}!corylifolia@\textit{corylifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=補骨脂&T2_new_value=true&fr=y}}{補骨脂}\index{補骨脂} NA$^n$
  \end{itemize}
 \item[] \textit{Pueraria} 葛藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pueraria+lobata+subsp.+thomsonii}{\textit{P. lobata} (Willd.) Ohwi subsp. \textit{thomsonii} (Benth.) H.Ohashi \& Tateishi}  \index{Pueraria@\textit{Pueraria}!lobata@\textit{lobata}!subsp. thomsonii@subsp. \textit{thomsonii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葛藤&T2_new_value=true&fr=y}}{大葛藤}\index{大葛藤} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pueraria+montana}{\textit{P. montana} (Lour.) Merr.}  \index{Pueraria@\textit{Pueraria}!montana@\textit{montana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山葛&T2_new_value=true&fr=y}}{山葛}\index{山葛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pueraria+phaseoloides}{\textit{P. phaseoloides} (Roxb.) Benth.}  \index{Pueraria@\textit{Pueraria}!phaseoloides@\textit{phaseoloides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假菜豆&T2_new_value=true&fr=y}}{假菜豆}\index{假菜豆} NA$^n$
  \end{itemize}
 \item[] \textit{Pycnospora} 密子豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pycnospora+lutescens}{\textit{P. lutescens} (Poir.) Schindl.}  \index{Pycnospora@\textit{Pycnospora}!lutescens@\textit{lutescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密子豆&T2_new_value=true&fr=y}}{密子豆}\index{密子豆} LC
  \end{itemize}
 \item[] \textit{Rhynchosia} 括根屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchosia+minima}{\textit{R. minima} (L.) DC.}  \index{Rhynchosia@\textit{Rhynchosia}!minima@\textit{minima}}  \index{Rhynchosia@\textit{Rhynchosia}!minima@\textit{minima}{\\\noindent(= \textit{Rhynchosia minima})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉括根&T2_new_value=true&fr=y}}{小葉括根}\index{小葉括根} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchosia+rothii}{\textit{R. rothii} Benth. ex Aitch.}  \index{Rhynchosia@\textit{Rhynchosia}!rothii@\textit{rothii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絨葉括根&T2_new_value=true&fr=y}}{絨葉括根}\index{絨葉括根} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchosia+volubilis}{\textit{R. volubilis} Lour.}  \index{Rhynchosia@\textit{Rhynchosia}!volubilis@\textit{volubilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鹿藿&T2_new_value=true&fr=y}}{鹿藿}\index{鹿藿} LC
  \end{itemize}
 \item[] \textit{Senna} 黃槐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+alata}{\textit{S. alata} (L.) Roxb.}  \index{Senna@\textit{Senna}!alata@\textit{alata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼柄決明&T2_new_value=true&fr=y}}{翼柄決明}\index{翼柄決明} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+hirsuta}{\textit{S. hirsuta} (L.) Irwin \& Barneby}  \index{Senna@\textit{Senna}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛決明&T2_new_value=true&fr=y}}{毛決明}\index{毛決明} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+occidentalis}{\textit{S. occidentalis} (L.) Link}  \index{Senna@\textit{Senna}!occidentalis@\textit{occidentalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=望江南&T2_new_value=true&fr=y}}{望江南}\index{望江南} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+siamea}{\textit{S. siamea} (Lam.) Irwin \& Barneby}  \index{Senna@\textit{Senna}!siamea@\textit{siamea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐵刀木&T2_new_value=true&fr=y}}{鐵刀木}\index{鐵刀木} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+sulfurea}{\textit{S. sulfurea} (Collad.) Irwin \& Barneby}  \index{Senna@\textit{Senna}!sulfurea@\textit{sulfurea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃槐&T2_new_value=true&fr=y}}{黃槐}\index{黃槐} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+tora}{\textit{S. tora} (L.) Roxb.}  \index{Senna@\textit{Senna}!tora@\textit{tora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=決明&T2_new_value=true&fr=y}}{決明}\index{決明} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Senna+×floribunda}{\textit{S. ×floribunda} (Cav.) Irwin \& Barneby}  \index{Senna@\textit{Senna}!×floribunda@\textit{×floribunda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花黃槐&T2_new_value=true&fr=y}}{大花黃槐}\index{大花黃槐} NA$^h$
  \end{itemize}
 \item[] \textit{Sesbania} 田菁屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sesbania+cannabina}{\textit{S. cannabina} (Retz.) Poir.}  \index{Sesbania@\textit{Sesbania}!cannabina@\textit{cannabina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田菁&T2_new_value=true&fr=y}}{田菁}\index{田菁} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sesbania+grandiflora}{\textit{S. grandiflora} (L.) Pers.}  \index{Sesbania@\textit{Sesbania}!grandiflora@\textit{grandiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花田菁&T2_new_value=true&fr=y}}{大花田菁}\index{大花田菁} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sesbania+sesban}{\textit{S. sesban} (L.) Merr.}  \index{Sesbania@\textit{Sesbania}!sesban@\textit{sesban}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度田菁&T2_new_value=true&fr=y}}{印度田菁}\index{印度田菁} NA$^n$
  \end{itemize}
 \item[] \textit{Smithia} 坡油甘屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smithia+ciliata}{\textit{S. ciliata} Royle}  \index{Smithia@\textit{Smithia}!ciliata@\textit{ciliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄萼坡油甘&T2_new_value=true&fr=y}}{薄萼坡油甘}\index{薄萼坡油甘} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smithia+sensitiva}{\textit{S. sensitiva} Aiton}  \index{Smithia@\textit{Smithia}!sensitiva@\textit{sensitiva}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=坡油甘&T2_new_value=true&fr=y}}{坡油甘}\index{坡油甘} LC
  \end{itemize}
 \item[] \textit{Sophora} 苦參屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sophora+flavescens}{\textit{S. flavescens} Aiton}  \index{Sophora@\textit{Sophora}!flavescens@\textit{flavescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦參&T2_new_value=true&fr=y}}{苦參}\index{苦參} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sophora+tomentosa}{\textit{S. tomentosa} L.}  \index{Sophora@\textit{Sophora}!tomentosa@\textit{tomentosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛苦參&T2_new_value=true&fr=y}}{毛苦參}\index{毛苦參} LC
  \end{itemize}
 \item[] \textit{Stylosanthes} 筆花豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stylosanthes+guianensis}{\textit{S. guianensis} (Aubl.) Sw.}  \index{Stylosanthes@\textit{Stylosanthes}!guianensis@\textit{guianensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=筆花豆&T2_new_value=true&fr=y}}{筆花豆}\index{筆花豆} NA$^n$
  \end{itemize}
 \item[] \textit{Tadehagi} 胡蘆茶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tadehagi+triquetrum+subsp.+pseudotriquetrum}{\textit{T. triquetrum} (L.) H.Ohashi subsp. \textit{pseudotriquetrum} (DC.) H.Ohashi}  \index{Tadehagi@\textit{Tadehagi}!triquetrum@\textit{triquetrum}!subsp. pseudotriquetrum@subsp. \textit{pseudotriquetrum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葫蘆茶&T2_new_value=true&fr=y}}{葫蘆茶}\index{葫蘆茶} LC
  \end{itemize}
 \item[] \textit{Tephrosia} 灰毛豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephrosia+candida}{\textit{T. candida} (Roxb.) DC.}  \index{Tephrosia@\textit{Tephrosia}!candida@\textit{candida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花鐵富豆&T2_new_value=true&fr=y}}{白花鐵富豆}\index{白花鐵富豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephrosia+noctiflora}{\textit{T. noctiflora} Bojer ex Baker}  \index{Tephrosia@\textit{Tephrosia}!noctiflora@\textit{noctiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花鐵富豆&T2_new_value=true&fr=y}}{黃花鐵富豆}\index{黃花鐵富豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephrosia+obovata}{\textit{T. obovata} Merr.}  \index{Tephrosia@\textit{Tephrosia}!obovata@\textit{obovata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣灰毛豆&T2_new_value=true&fr=y}}{臺灣灰毛豆}\index{臺灣灰毛豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tephrosia+purpurea}{\textit{T. purpurea} (L.) Pers.}  \index{Tephrosia@\textit{Tephrosia}!purpurea@\textit{purpurea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰毛豆&T2_new_value=true&fr=y}}{灰毛豆}\index{灰毛豆} LC
  \end{itemize}
 \item[] \textit{Teramnus} 野黃豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Teramnus+labialis}{\textit{T. labialis} (L.f.) Spur.}  \index{Teramnus@\textit{Teramnus}!labialis@\textit{labialis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野黃豆&T2_new_value=true&fr=y}}{野黃豆}\index{野黃豆} LC
  \end{itemize}
 \item[] \textit{Trifolium} 菽草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trifolium+dubium}{\textit{T. dubium} Sibth.}  \index{Trifolium@\textit{Trifolium}!dubium@\textit{dubium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃菽草&T2_new_value=true&fr=y}}{黃菽草}\index{黃菽草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trifolium+pratense}{\textit{T. pratense} L.}  \index{Trifolium@\textit{Trifolium}!pratense@\textit{pratense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅菽草&T2_new_value=true&fr=y}}{紅菽草}\index{紅菽草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trifolium+repens}{\textit{T. repens} L.}  \index{Trifolium@\textit{Trifolium}!repens@\textit{repens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菽草&T2_new_value=true&fr=y}}{菽草}\index{菽草} NA$^n$
  \end{itemize}
 \item[] \textit{Trigonella} 胡蘆巴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trigonella+hamosa}{\textit{T. hamosa} Forssk.}  \index{Trigonella@\textit{Trigonella}!hamosa@\textit{hamosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=彎果胡蘆巴&T2_new_value=true&fr=y}}{彎果胡蘆巴}\index{彎果胡蘆巴} NA$^n$
  \end{itemize}
 \item[] \textit{Uraria} 兔尾草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uraria+crinita}{\textit{U. crinita} (L.) Desv. ex DC.}  \index{Uraria@\textit{Uraria}!crinita@\textit{crinita}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=兔尾草&T2_new_value=true&fr=y}}{兔尾草}\index{兔尾草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uraria+lagopodioides}{\textit{U. lagopodioides} (L.) Desv. ex DC.}  \index{Uraria@\textit{Uraria}!lagopodioides@\textit{lagopodioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉兔尾草&T2_new_value=true&fr=y}}{大葉兔尾草}\index{大葉兔尾草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uraria+neglecta}{\textit{U. neglecta} Prain}  \index{Uraria@\textit{Uraria}!neglecta@\textbf{\textit{neglecta}}}  \index{Uraria@\textit{Uraria}!aequilobata@\textit{aequilobata}{\\\noindent(= \textit{Uraria neglecta})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉兔尾草&T2_new_value=true&fr=y}}{圓葉兔尾草}\index{圓葉兔尾草@{\Song{圓葉兔尾草}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uraria+picta}{\textit{U. picta} (Jacq.) DC.}  \index{Uraria@\textit{Uraria}!picta@\textit{picta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽葉兔尾草&T2_new_value=true&fr=y}}{羽葉兔尾草}\index{羽葉兔尾草} DD
  \end{itemize}
 \item[] \textit{Vicia} 蠶豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vicia+cracca}{\textit{V. cracca} L.}  \index{Vicia@\textit{Vicia}!cracca@\textit{cracca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多花野豌豆&T2_new_value=true&fr=y}}{多花野豌豆}\index{多花野豌豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vicia+hirsuta}{\textit{V. hirsuta} (L.) S.F.Gray}  \index{Vicia@\textit{Vicia}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小巢豆&T2_new_value=true&fr=y}}{小巢豆}\index{小巢豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vicia+sativa+subsp.+nigra}{\textit{V. sativa} L. subsp. \textit{nigra} (L.) Ehrh.}  \index{Vicia@\textit{Vicia}!sativa@\textit{sativa}!subsp. nigra@subsp. \textit{nigra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野豌豆&T2_new_value=true&fr=y}}{野豌豆}\index{野豌豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vicia+tetrasperma}{\textit{V. tetrasperma} (L.) Moench}  \index{Vicia@\textit{Vicia}!tetrasperma@\textit{tetrasperma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏嘴豆&T2_new_value=true&fr=y}}{烏嘴豆}\index{烏嘴豆} NA$^n$
  \end{itemize}
 \item[] \textit{Vigna} 豇豆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+adenantha}{\textit{V. adenantha} (G.F.Meyer) Maréchal}  \index{Vigna@\textit{Vigna}!adenantha@\textbf{\textit{adenantha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺葯豇豆&T2_new_value=true&fr=y}}{腺葯豇豆}\index{腺葯豇豆@{\Song{腺葯豇豆}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+angularis+var.+nipponensis}{\textit{V. angularis} (Willd.) Ohwi \& H.Ohashi var. \textit{nipponensis} (Ohwi) Ohwi \& H.Ohashi}  \index{Vigna@\textit{Vigna}!angularis@\textit{angularis}!var. nipponensis@var. \textit{nipponensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野紅豆&T2_new_value=true&fr=y}}{野紅豆}\index{野紅豆} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+hosei}{\textit{V. hosei} (Craib) Backer}  \index{Vigna@\textit{Vigna}!hosei@\textit{hosei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=和氏豇豆&T2_new_value=true&fr=y}}{和氏豇豆}\index{和氏豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+luteola}{\textit{V. luteola} (Jacq.) Benth.}  \index{Vigna@\textit{Vigna}!luteola@\textit{luteola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉豇豆&T2_new_value=true&fr=y}}{長葉豇豆}\index{長葉豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+marina}{\textit{V. marina} (Burm.) Merr.}  \index{Vigna@\textit{Vigna}!marina@\textit{marina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱豇豆&T2_new_value=true&fr=y}}{濱豇豆}\index{濱豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+minima+var.+minima}{\textit{V. minima} (Roxb.) Ohwi \& H.Ohashi var. \textit{minima}}  \index{Vigna@\textit{Vigna}!minima@\textit{minima}!var. minima@var. \textit{minima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小豇豆&T2_new_value=true&fr=y}}{小豇豆}\index{小豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+minima+var.+minor}{\textit{V. minima} (Roxb.) Ohwi \& H.Ohashi var. \textit{minor} (Matsum.) Tateishi}  \index{Vigna@\textit{Vigna}!minima@\textit{minima}!var. minor@var. \textit{minor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉豇豆&T2_new_value=true&fr=y}}{小葉豇豆}\index{小葉豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+radiata+var.+radiata}{\textit{V. radiata} (L.) Wilczek var. \textit{radiata}}  \index{Vigna@\textit{Vigna}!radiata@\textit{radiata}!var. radiata@var. \textit{radiata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠豆&T2_new_value=true&fr=y}}{綠豆}\index{綠豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+radiata+var.+sublobata}{\textit{V. radiata} (L.) Wilczek var. \textit{sublobata} (Roxb.) Verdc.}  \index{Vigna@\textit{Vigna}!radiata@\textit{radiata}!var. sublobata@var. \textit{sublobata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三裂葉豇豆&T2_new_value=true&fr=y}}{三裂葉豇豆}\index{三裂葉豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+reflexopilosa}{\textit{V. reflexopilosa} Hayata}  \index{Vigna@\textit{Vigna}!reflexopilosa@\textit{reflexopilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=曲毛豇豆&T2_new_value=true&fr=y}}{曲毛豇豆}\index{曲毛豇豆} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+umbellata}{\textit{V. umbellata} (Thunb.) Ohwi \& H.Ohashi}  \index{Vigna@\textit{Vigna}!umbellata@\textit{umbellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=赤小豆&T2_new_value=true&fr=y}}{赤小豆}\index{赤小豆} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vigna+vexillata+var.+tsusimensis}{\textit{V. vexillata} (L.) A.Rich. var. \textit{tsusimensis} Matsum.}  \index{Vigna@\textit{Vigna}!vexillata@\textit{vexillata}!var. tsusimensis@var. \textit{tsusimensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野豇豆&T2_new_value=true&fr=y}}{野豇豆}\index{野豇豆} LC
  \end{itemize}
 \item[] \textit{Zornia} 丁葵草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zornia+cantoniensis}{\textit{Z. cantoniensis} Mohlenbr.}  \index{Zornia@\textit{Zornia}!cantoniensis@\textit{cantoniensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=丁葵草&T2_new_value=true&fr=y}}{丁葵草}\index{丁葵草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zornia+intecta}{\textit{Z. intecta} Mohlenbr.}  \index{Zornia@\textit{Zornia}!intecta@\textbf{\textit{intecta}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東葵草&T2_new_value=true&fr=y}}{臺東葵草}\index{臺東葵草@{\Song{臺東葵草}}}\# VU
  \end{itemize}
  \end{itemize}
