
  \begin{itemize}
 \item[] \textit{Castanopsis} 栲屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+chinensis}{\textit{C. chinensis} Hance}  \index{Castanopsis@\textit{Castanopsis}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桂林栲&T2_new_value=true&fr=y}}{桂林栲}\index{桂林栲@{\Song{桂林栲}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+cuspidata+var.+carlesii}{\textit{C. cuspidata} (Thunb.) Schottky var. \textit{carlesii} (Hemsl.) T.Yamaz.}  \index{Castanopsis@\textit{Castanopsis}!cuspidata@\textit{cuspidata}!var. carlesii@var. \textit{carlesii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長尾尖葉櫧&T2_new_value=true&fr=y}}{長尾尖葉櫧}\index{長尾尖葉櫧} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+cuspidata+var.+carlesii+ f. +sessilis}{\textit{C. cuspidata} (Thunb.) var. \textit{carlesii} (Hemsl.) T.Yamaz.  f.  \textit{sessilis} (Nakai) J.C.Liao}  \index{Castanopsis@\textit{Castanopsis}!cuspidata@\textit{cuspidata}!var. carlesii f. sessilis@var. \textit{carlesii} f. \textit{sessilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白校欑&T2_new_value=true&fr=y}}{白校欑}\index{白校欑}\# NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+eyrei}{\textit{C. eyrei} (Champ. ex Benth.) Hutch.}  \index{Castanopsis@\textit{Castanopsis}!eyrei@\textbf{\textit{eyrei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=反刺苦櫧&T2_new_value=true&fr=y}}{反刺苦櫧}\index{反刺苦櫧@{\Song{反刺苦櫧}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+fabri}{\textit{C. fabri} Hance}  \index{Castanopsis@\textit{Castanopsis}!fabri@\textit{fabri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=星刺栲&T2_new_value=true&fr=y}}{星刺栲}\index{星刺栲} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+fargesii}{\textit{C. fargesii} Franch.}  \index{Castanopsis@\textit{Castanopsis}!fargesii@\textit{fargesii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=火燒柯&T2_new_value=true&fr=y}}{火燒柯}\index{火燒柯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+formosana}{\textit{C. formosana} (Skan) Hayata}  \index{Castanopsis@\textit{Castanopsis}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣苦櫧&T2_new_value=true&fr=y}}{臺灣苦櫧}\index{臺灣苦櫧} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+indica}{\textit{C. indica} (Rox.) A.DC.}  \index{Castanopsis@\textit{Castanopsis}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度苦櫧&T2_new_value=true&fr=y}}{印度苦櫧}\index{印度苦櫧} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+kawakamii}{\textit{C. kawakamii} Hayata}  \index{Castanopsis@\textit{Castanopsis}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉苦櫧&T2_new_value=true&fr=y}}{大葉苦櫧}\index{大葉苦櫧} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+kusanoi}{\textit{C. kusanoi} Hayata}  \index{Castanopsis@\textit{Castanopsis}!kusanoi@\textit{kusanoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細刺苦櫧&T2_new_value=true&fr=y}}{細刺苦櫧}\index{細刺苦櫧}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Castanopsis+uraiana}{\textit{C. uraiana} (Hayata) Kaneh. \& Hatus.}  \index{Castanopsis@\textit{Castanopsis}!uraiana@\textit{uraiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來柯&T2_new_value=true&fr=y}}{烏來柯}\index{烏來柯} LC
  \end{itemize}
 \item[] \textit{Fagus} 水青岡屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fagus+hayatae}{\textit{F. hayatae} Palib.}  \index{Fagus@\textit{Fagus}!hayatae@\textit{hayatae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣水青岡&T2_new_value=true&fr=y}}{臺灣水青岡(臺灣山毛櫸)} \index{臺灣水青岡} \index{臺灣山毛櫸@{臺灣山毛櫸(=臺灣水青岡)}} LC
  \end{itemize}
 \item[] \textit{Lithocarpus} 石櫟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+amygdalifolius}{\textit{L. amygdalifolius} (Skan ex Forbes \& Hemsl.) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!amygdalifolius@\textit{amygdalifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杏葉石櫟&T2_new_value=true&fr=y}}{杏葉石櫟}\index{杏葉石櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+chiaratuangensis}{\textit{L. chiaratuangensis} (J.C.Liao) J.C.Liao}  \index{Lithocarpus@\textit{Lithocarpus}!chiaratuangensis@\textbf{\textit{chiaratuangensis}}}  \index{Pasania@\textit{Pasania}!chiaratuangensis@\textit{chiaratuangensis}{\\\noindent(= \textit{Lithocarpus chiaratuangensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=加拉段柯&T2_new_value=true&fr=y}}{加拉段柯}\index{加拉段柯@{\Song{加拉段柯}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+corneus}{\textit{L. corneus} (Lour.) Rehder}  \index{Lithocarpus@\textit{Lithocarpus}!corneus@\textit{corneus}}  \index{Pasania@\textit{Pasania}!cornea@\textit{cornea}{\\\noindent(= \textit{Lithocarpus corneus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=後大埔石櫟&T2_new_value=true&fr=y}}{後大埔石櫟}\index{後大埔石櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+dodonaeifolius}{\textit{L. dodonaeifolius} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!dodonaeifolius@\textbf{\textit{dodonaeifolius}}}  \index{Pasania@\textit{Pasania}!dodonaeifolia@\textit{dodonaeifolia}{\\\noindent(= \textit{Lithocarpus dodonaeifolius})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柳葉石櫟&T2_new_value=true&fr=y}}{柳葉石櫟}\index{柳葉石櫟@{\Song{柳葉石櫟}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+formosanus}{\textit{L. formosanus} (Skan ex Forbes \& Hemsl.) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!formosanus@\textbf{\textit{formosanus}}}  \index{Pasania@\textit{Pasania}!formosana@\textit{formosana}{\\\noindent(= \textit{Lithocarpus formosanus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣石櫟&T2_new_value=true&fr=y}}{臺灣石櫟}\index{臺灣石櫟@{\Song{臺灣石櫟}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+glaber}{\textit{L. glaber} (Thunb.) Nakai}  \index{Lithocarpus@\textit{Lithocarpus}!glaber@\textit{glaber}}  \index{Pasania@\textit{Pasania}!glabra@\textit{glabra}{\\\noindent(= \textit{Lithocarpus glaber})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=子彈石櫟&T2_new_value=true&fr=y}}{子彈石櫟}\index{子彈石櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+hancei}{\textit{L. hancei} (Benth.) Rehder}  \index{Lithocarpus@\textit{Lithocarpus}!hancei@\textit{hancei}}  \index{Pasania@\textit{Pasania}!hancei@\textit{hancei}!var. arisanensis@var. \textit{arisanensis}{\\\noindent(=\textit{Lithocarpus hancei})}}   \index{Pasania@\textit{Pasania}!hancei@\textit{hancei}!var. ternaticupula@var. \textit{ternaticupula}{\\\noindent(=\textit{Lithocarpus hancei})}}   \index{Pasania@\textit{Pasania}!hancei@\textit{hancei}!var. ternaticupula fo. subreticulata@var. \textit{ternaticupula} fo. \textit{subreticulata}{\\\noindent~~(=\textit{Lithocarpus hancei})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三斗石櫟&T2_new_value=true&fr=y}}{三斗石櫟(阿里山三斗石櫟、細葉三斗石櫟)} \index{三斗石櫟} \index{阿里山三斗石櫟@{阿里山三斗石櫟(=三斗石櫟)}} \index{細葉三斗石櫟@{細葉三斗石櫟(=三斗石櫟)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+harlandii}{\textit{L. harlandii} (Hance ex Walp.) Rehder}  \index{Lithocarpus@\textit{Lithocarpus}!harlandii@\textit{harlandii}}  \index{Pasania@\textit{Pasania}!harlandii@\textit{harlandii}{\\\noindent(= \textit{Lithocarpus harlandii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短尾葉石櫟&T2_new_value=true&fr=y}}{短尾葉石櫟}\index{短尾葉石櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+kawakamii}{\textit{L. kawakamii} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!kawakamii@\textit{kawakamii}}  \index{Pasania@\textit{Pasania}!kawakamii@\textit{kawakamii}{\\\noindent(= \textit{Lithocarpus kawakamii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉石櫟&T2_new_value=true&fr=y}}{大葉石櫟}\index{大葉石櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+konishii}{\textit{L. konishii} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!konishii@\textit{konishii}}  \index{Pasania@\textit{Pasania}!konishii@\textit{konishii}{\\\noindent(= \textit{Lithocarpus konishii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=油葉石櫟&T2_new_value=true&fr=y}}{油葉石櫟}\index{油葉石櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+lepidocarpus}{\textit{L. lepidocarpus} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!lepidocarpus@\textit{lepidocarpus}}  \index{Lithocarpus@\textit{Lithocarpus}!castanopsisifolius@\textit{castanopsisifolius}{\\\noindent(= \textit{Lithocarpus lepidocarpus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼石櫟&T2_new_value=true&fr=y}}{鬼石櫟}\index{鬼石櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+nantoensis}{\textit{L. nantoensis} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!nantoensis@\textbf{\textit{nantoensis}}}  \index{Pasania@\textit{Pasania}!nantoensis@\textit{nantoensis}{\\\noindent(= \textit{Lithocarpus nantoensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投石櫟&T2_new_value=true&fr=y}}{南投石櫟}\index{南投石櫟@{\Song{南投石櫟}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+shinsuiensis}{\textit{L. shinsuiensis} Hayata \& Kaneh.}  \index{Lithocarpus@\textit{Lithocarpus}!shinsuiensis@\textbf{\textit{shinsuiensis}}}  \index{Pasania@\textit{Pasania}!shinsuiensis@\textit{shinsuiensis}{\\\noindent(= \textit{Lithocarpus shinsuiensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=浸水營石櫟&T2_new_value=true&fr=y}}{浸水營石櫟}\index{浸水營石櫟@{\Song{浸水營石櫟}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+synbalanos}{\textit{L. synbalanos} (Hance) Chun}  \index{Lithocarpus@\textit{Lithocarpus}!synbalanos@\textit{synbalanos}}  \index{Pasania@\textit{Pasania}!synbalanos@\textit{synbalanos}{\\\noindent(= \textit{Lithocarpus synbalanos})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菱果石櫟&T2_new_value=true&fr=y}}{菱果石櫟}\index{菱果石櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lithocarpus+taitoensis}{\textit{L. taitoensis} (Hayata) Hayata}  \index{Lithocarpus@\textit{Lithocarpus}!taitoensis@\textit{taitoensis}}  \index{Pasania@\textit{Pasania}!taitoensis@\textit{taitoensis}{\\\noindent(= \textit{Lithocarpus taitoensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東石櫟&T2_new_value=true&fr=y}}{臺東石櫟}\index{臺東石櫟} LC
  \end{itemize}
 \item[] \textit{Quercus} 櫟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+acutissima}{\textit{Q. acutissima} Carruth.}  \index{Quercus@\textit{Quercus}!acutissima@\textit{acutissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=麻櫟&T2_new_value=true&fr=y}}{麻櫟}\index{麻櫟} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+aliena}{\textit{Q. aliena} Blume}  \index{Quercus@\textit{Quercus}!aliena@\textbf{\textit{aliena}}}  \index{Quercus@\textit{Quercus}!aliena@\textit{aliena}!var. acutiserrata@var. \textit{acutiserrata}{\\\noindent(=\textit{Quercus aliena})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大槲樹&T2_new_value=true&fr=y}}{大槲樹(槲櫟、孛孛櫟)} \index{大槲樹@{\Song{大槲樹}}} \index{槲櫟@{\Song{槲櫟(=大槲樹)}}} \index{孛孛櫟@{\Song{孛孛櫟(=大槲樹)}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+championii}{\textit{Q. championii} Benth.}  \index{Quercus@\textit{Quercus}!championii@\textit{championii}}  \index{Cyclobalanopsis championii@\textit{Cyclobalanopsis championii}!(Benth.)@\textit{(Benth.)}{\\\noindent(= \textit{Quercus championii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=嶺南青剛櫟&T2_new_value=true&fr=y}}{嶺南青剛櫟}\index{嶺南青剛櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+dentata}{\textit{Q. dentata} Thunb.}  \index{Quercus@\textit{Quercus}!dentata@\textit{dentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=槲樹&T2_new_value=true&fr=y}}{槲樹}\index{槲樹} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+gilva}{\textit{Q. gilva} Blume}  \index{Quercus@\textit{Quercus}!gilva@\textit{gilva}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!gilva@\textit{gilva}{\\\noindent(= \textit{Quercus gilva})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=赤皮&T2_new_value=true&fr=y}}{赤皮}\index{赤皮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+glandulifera+var.+brevipetiolata}{\textit{Q. glandulifera} Blume var. \textit{brevipetiolata} (A.DC.) Nakai}  \index{Quercus@\textit{Quercus}!glandulifera@\textit{glandulifera}!var. brevipetiolata@\textbf{var. \textit{brevipetiolata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=思茅櫧櫟&T2_new_value=true&fr=y}}{思茅櫧櫟}\index{思茅櫧櫟@{\Song{思茅櫧櫟}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+glauca+var.+glauca}{\textit{Q. glauca} Thunb. var. \textit{glauca}}  \index{Quercus@\textit{Quercus}!glauca@\textit{glauca}!var. glauca@var. \textit{glauca}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!glauca@\textit{glauca}{\\\noindent(= \textit{Quercus glauca} var. \textit{glauca})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=青剛櫟&T2_new_value=true&fr=y}}{青剛櫟}\index{青剛櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+glauca+var.+kuyuensis}{\textit{Q. glauca} Thunb. var. \textit{kuyuensis} J.C.Liao}  \index{Quercus@\textit{Quercus}!glauca@\textit{glauca}!var. kuyuensis@var. \textit{kuyuensis}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!glauca@\textit{glauca}!var. kuyuensis@var. \textit{kuyuensis}{\\\noindent(=\textit{Quercus glauca} var. \textit{kuyuensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=谷園青剛櫟&T2_new_value=true&fr=y}}{谷園青剛櫟}\index{谷園青剛櫟}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+globosa}{\textit{Q. globosa} (W.F.Lin \& T.Liu) J.C.Liao}  \index{Quercus@\textit{Quercus}!globosa@\textit{globosa}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!globosa@\textit{globosa}{\\\noindent(= \textit{Quercus globosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓果青剛櫟&T2_new_value=true&fr=y}}{圓果青剛櫟}\index{圓果青剛櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+globosa+ f. +chiapautaiensis}{\textit{Q. globosa} (W.F.Lin \& T.Liu) J.C.Liao  f.  \textit{chiapautaiensis} J.C.Liao}  \index{Quercus@\textit{Quercus}!globosa@\textit{globosa}!f. chiapautaiensis@f. \textit{chiapautaiensis}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!globosa@\textit{globosa}!fo. chiapautaiensis@fo. \textit{chiapautaiensis}{\\\noindent(=\textit{Quercus globosa} fo. \textit{chiapautaiensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=佳保臺圓果青剛櫟&T2_new_value=true&fr=y}}{佳保臺圓果青剛櫟}\index{佳保臺圓果青剛櫟}\# NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+hypophaea}{\textit{Q. hypophaea} Hayata}  \index{Quercus@\textit{Quercus}!hypophaea@\textit{hypophaea}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!hypophaea@\textit{hypophaea}{\\\noindent(= \textit{Quercus hypophaea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰背櫟&T2_new_value=true&fr=y}}{灰背櫟}\index{灰背櫟}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+longinux+var.+kuoi}{\textit{Q. longinux} Hayata var. \textit{kuoi} (J.C.Liao) C.F.Shen}  \index{Quercus@\textit{Quercus}!longinux@\textit{longinux}!var. kuoi@var. \textit{kuoi}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!longinux@\textit{longinux}{\\\noindent(= \textit{Quercus longinux} var. \textit{kuoi})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=郭氏錐果櫟&T2_new_value=true&fr=y}}{郭氏錐果櫟}\index{郭氏錐果櫟}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+longinux+var.+lativiolacifolia}{\textit{Q. longinux} Hayata var. \textit{lativiolacifolia} (J.C.Liao ex J.C.Liao) J.C.Liao}  \index{Quercus@\textit{Quercus}!longinux@\textit{longinux}!var. lativiolacifolia@var. \textit{lativiolacifolia}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!longinux@\textit{longinux}!var. kuoi@var. \textit{kuoi}{\\\noindent(=\textit{Quercus longinux} var. \textit{lativiolacifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫背錐果櫟&T2_new_value=true&fr=y}}{紫背錐果櫟}\index{紫背錐果櫟}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+longinux+var.+longinux}{\textit{Q. longinux} Hayata var. \textit{longinux}}  \index{Quercus@\textit{Quercus}!longinux@\textit{longinux}!var. longinux@var. \textit{longinux}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!longinux@\textit{longinux}!var. lativiolacifolia@var. \textit{lativiolacifolia}{\\\noindent(=\textit{Quercus longinux} var. \textit{longinux})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錐果櫟&T2_new_value=true&fr=y}}{錐果櫟}\index{錐果櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+morii}{\textit{Q. morii} Hayata}  \index{Quercus@\textit{Quercus}!morii@\textit{morii}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!morii@\textit{morii}{\\\noindent(= \textit{Quercus morii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=赤柯&T2_new_value=true&fr=y}}{赤柯}\index{赤柯}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+myrsinifolia}{\textit{Q. myrsinifolia} Blume}  \index{Quercus@\textit{Quercus}!myrsinifolia@\textit{myrsinifolia}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!myrsinifolia@\textit{myrsinifolia}{\\\noindent(= \textit{Quercus myrsinifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑櫟&T2_new_value=true&fr=y}}{黑櫟}\index{黑櫟} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+pachyloma}{\textit{Q. pachyloma} Seemen}  \index{Quercus@\textit{Quercus}!pachyloma@\textit{pachyloma}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!pachyloma@\textit{pachyloma}{\\\noindent(= \textit{Quercus pachyloma})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=捲斗櫟&T2_new_value=true&fr=y}}{捲斗櫟}\index{捲斗櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+repandifolia}{\textit{Q. repandifolia} J.C.Liao}  \index{Quercus@\textit{Quercus}!repandifolia@\textbf{\textit{repandifolia}}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!repandifolia@\textit{repandifolia}{\\\noindent(= \textit{Quercus repandifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=波葉櫟&T2_new_value=true&fr=y}}{波葉櫟}\index{波葉櫟@{\Song{波葉櫟}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+salicina}{\textit{Q. salicina} Blume}  \index{Quercus@\textit{Quercus}!salicina@\textit{salicina}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!salicina@\textit{salicina}{\\\noindent(= \textit{Quercus salicina})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白背櫟&T2_new_value=true&fr=y}}{白背櫟}\index{白背櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+sessilifolia}{\textit{Q. sessilifolia} Blume}  \index{Quercus@\textit{Quercus}!sessilifolia@\textit{sessilifolia}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!sessilifolia@\textit{sessilifolia}{\\\noindent(= \textit{Quercus sessilifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毽子櫟&T2_new_value=true&fr=y}}{毽子櫟}\index{毽子櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+spinosa}{\textit{Q. spinosa} David ex Franch.}  \index{Quercus@\textit{Quercus}!spinosa@\textit{spinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山櫟&T2_new_value=true&fr=y}}{高山櫟}\index{高山櫟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+stenophylloides}{\textit{Q. stenophylloides} Hayata}  \index{Quercus@\textit{Quercus}!stenophylloides@\textit{stenophylloides}}  \index{Cyclobalanopsis@\textit{Cyclobalanopsis}!stenophylloides@\textit{stenophylloides}{\\\noindent(= \textit{Quercus stenophylloides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉櫟&T2_new_value=true&fr=y}}{狹葉櫟}\index{狹葉櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+tarokoensis}{\textit{Q. tarokoensis} Hayata}  \index{Quercus@\textit{Quercus}!tarokoensis@\textit{tarokoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣櫟&T2_new_value=true&fr=y}}{太魯閣櫟}\index{太魯閣櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+tatakaensis}{\textit{Q. tatakaensis} Tomiya}  \index{Quercus@\textit{Quercus}!tatakaensis@\textit{tatakaensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳葉高山櫟&T2_new_value=true&fr=y}}{銳葉高山櫟}\index{銳葉高山櫟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Quercus+variabilis}{\textit{Q. variabilis} Blume}  \index{Quercus@\textit{Quercus}!variabilis@\textit{variabilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=栓皮櫟&T2_new_value=true&fr=y}}{栓皮櫟}\index{栓皮櫟} LC
  \end{itemize}
  \end{itemize}
