
  \begin{itemize}
 \item[] \textit{Centaurium}\index{Centaurium@\textit{Centaurium}} 百金屬
                                
  \begin{itemize}
        \item[] \textit{C. japonicum} (Maxim.) Druce \index{Centaurium@\textit{Centaurium}!japonicum@\textit{japonicum}} 百金 \index{百金}  LC
        \item[] \textit{C. pulchellum} var. \textit{altaicum} (Griseb.) Kitag. et Hara \index{Centaurium@\textit{Centaurium}!pulchellum@\textit{pulchellum}!var. altaicum@var. \textit{altaicum}} 百金花 \index{百金花}  VU
  \end{itemize}
 \item[] \textit{Fagraea}\index{Fagraea@\textit{Fagraea}} 灰莉屬
                                
  \begin{itemize}
        \item[] \textit{F. ceilanica} Thumb. \index{Fagraea@\textit{Fagraea}!ceilanica@\textit{ceilanica}} 灰莉 \index{灰莉}  VU
  \end{itemize}
 \item[] \textit{Gentiana}\index{Gentiana@\textit{Gentiana}} 龍膽屬
                                
  \begin{itemize}
        \item[] \textit{G. arisanensis} Hayata \index{Gentiana@\textit{Gentiana}!arisanensis@\textit{arisanensis}} 阿里山龍膽 \index{阿里山龍膽} \# LC
        \item[] \textit{G. bambuseti} T. Y. Hsieh, T. C Hsu, S. M. Ku \& 
C.-I Peng \index{Gentiana@\textit{Gentiana}!bambuseti@\textit{bambuseti}} 竹林龍膽 \index{竹林龍膽} \# VU
        \item[] \textit{G. davidii} var. \textit{formosana} (Hayata) T. N. Ho \index{Gentiana@\textit{Gentiana}!davidii@\textit{davidii}!var. formosana@var. \textit{formosana}} 臺灣龍膽 \index{臺灣龍膽}  LC
        \item[] \textit{G. flavomaculata} Hayata \index{Gentiana@\textit{Gentiana}!flavomaculata@\textit{flavomaculata}} 黃斑龍膽 \index{黃斑龍膽} \# LC
        \item[] \textit{G. flavomaculata} var. \textit{yuanyanghuensis} C. H. Chen \& J. C. Wang \index{Gentiana@\textit{Gentiana}!flavomaculata@\textit{flavomaculata}!var. yuanyanghuensis@var. \textit{yuanyanghuensis}} 鴛鴦湖龍膽 \index{鴛鴦湖龍膽} \# LC
        \item[] \textit{G. horaimontana} Masam. \index{Gentiana@\textit{Gentiana}!horaimontana@\textit{horaimontana}} 高山龍膽 \index{高山龍膽} \# EN
        \item[] \textit{G. itzershanensis} T. S. Liu \& Chiu C. Kuo \index{Gentiana@\textit{Gentiana}!itzershanensis@\textit{itzershanensis}} 伊澤山龍膽 \index{伊澤山龍膽} \# NT
        \item[] \textit{G. kaohsiungensis} C. H. Chen \& J. C. Wang \index{Gentiana@\textit{Gentiana}!kaohsiungensis@\textit{kaohsiungensis}} 高雄龍膽 \index{高雄龍膽} \# NT
        \item[] \textit{G. scabrida} Hayata \index{Gentiana@\textit{Gentiana}!scabrida@\textit{scabrida}} 玉山龍膽 \index{玉山龍膽} \# LC
        \item[] \textit{G. scabrida} var. \textit{punctulata} S. S. Ying \index{Gentiana@\textit{Gentiana}!scabrida@\textit{scabrida}!var. punctulata@var. \textit{punctulata}} 黑斑龍膽 \index{黑斑龍膽} \# LC
        \item[] \textit{G. tarokoensis} C. H. Chen \& J. C. Wang \index{Gentiana@\textit{Gentiana}!tarokoensis@\textit{tarokoensis}} 太魯閣龍膽 \index{太魯閣龍膽} \# CR
        \item[] \textit{G. tatakensis} Masam. \index{Gentiana@\textit{Gentiana}!tatakensis@\textit{tatakensis}} 塔塔加龍膽 \index{塔塔加龍膽} \# VU
        \item[] \textit{G. tentyoensis} Masam. \index{Gentiana@\textit{Gentiana}!tentyoensis@\textit{tentyoensis}} 厚葉龍膽 \index{厚葉龍膽} \# CR
        \item[] \textit{G. tenuissima} Hayata \index{Gentiana@\textit{Gentiana}!tenuissima@\textit{tenuissima}} 臺東龍膽 \index{臺東龍膽} \# NT
  \end{itemize}
 \item[] \textit{Lomatogonium}\index{Lomatogonium@\textit{Lomatogonium}} 肋柱花屬
                                
  \begin{itemize}
        \item[] \textit{L. chilaiensis} C. H. Chen \& J. C. Wang \index{Lomatogonium@\textit{Lomatogonium}!chilaiensis@\textit{chilaiensis}} 奇萊肋柱花 \index{奇萊肋柱花} \# CR
  \end{itemize}
 \item[] \textit{Pterygocalyx}\index{Pterygocalyx@\textit{Pterygocalyx}} 翼萼蔓屬
                                
  \begin{itemize}
        \item[] \textit{P. volubilis} Maxim. \index{Pterygocalyx@\textit{Pterygocalyx}!volubilis@\textit{volubilis}} 翼萼蔓 \index{翼萼蔓}  VU
  \end{itemize}
 \item[] \textit{Swertia}\index{Swertia@\textit{Swertia}} 當藥屬
                                
  \begin{itemize}
        \item[] \textit{S. arisanensis} Hayata \index{Swertia@\textit{Swertia}!arisanensis@\textit{arisanensis}} 阿里山當藥 \index{阿里山當藥} \# VU
        \item[] \textit{S. changii} S. Z. Yang, C. F. Chen \& C. H. Chen \index{Swertia@\textit{Swertia}!changii@\textit{changii}} 大漢山當藥 \index{大漢山當藥} \# EN
        \item[] \textit{S. macrosperma} (C. B. Clarke) C. B. Clarke \index{Swertia@\textit{Swertia}!macrosperma@\textit{macrosperma}} 大籽當藥 \index{大籽當藥}  LC
        \item[] \textit{S. shintenensis} Hayata \index{Swertia@\textit{Swertia}!shintenensis@\textit{shintenensis}} 新店當藥 \index{新店當藥} \# NT
        \item[] \textit{S. tozanensis} Hayata \index{Swertia@\textit{Swertia}!tozanensis@\textit{tozanensis}} 高山當藥 \index{高山當藥} \# VU
  \end{itemize}
 \item[] \textit{Tripterospermum}\index{Tripterospermum@\textit{Tripterospermum}} 肺形草屬
                                
  \begin{itemize}
        \item[] \textit{T. alutaceifolium} (T. S. Liu \& Chiu C. Kuo) J. Murata \index{Tripterospermum@\textit{Tripterospermum}!alutaceifolium@\textit{alutaceifolium}} 臺北肺形草 \index{臺北肺形草} \# LC
        \item[] \textit{T. cordifolium} (Yamam.) Satake \index{Tripterospermum@\textit{Tripterospermum}!cordifolium@\textit{cordifolium}} 高山肺形草 \index{高山肺形草} \# VU
        \item[] \textit{T. hualienense} T. C. Hsu \& S. W. Chung \index{Tripterospermum@\textit{Tripterospermum}!hualienense@\textit{hualienense}} 東臺肺形草 \index{東臺肺形草} \# VU
        \item[] \textit{T. lanceolatum} (Hayata) H. Hara ex Satake \index{Tripterospermum@\textit{Tripterospermum}!lanceolatum@\textit{lanceolatum}} 玉山肺形草 \index{玉山肺形草} \# LC
        \item[] \textit{T. lilungshanensis} C. H. Chen, J. C. Wang \& Y. C. Chang \index{Tripterospermum@\textit{Tripterospermum}!lilungshanensis@\textit{lilungshanensis}} 里龍山肺形草 \index{里龍山肺形草} \# CR
        \item[] \textit{T. luzonense} (Vidal) J. Murata \index{Tripterospermum@\textit{Tripterospermum}!luzonense@\textit{luzonense}} 高山雙蝴蝶 \index{高山雙蝴蝶}  LC
        \item[] \textit{T. microphyllum} Harry Sm. \index{Tripterospermum@\textit{Tripterospermum}!microphyllum@\textit{microphyllum}} 小葉雙蝴蝶 \index{小葉雙蝴蝶} \# NT
        \item[] \textit{T. taiwanense} (Masam.) Satake \index{Tripterospermum@\textit{Tripterospermum}!taiwanense@\textit{taiwanense}} 臺灣肺形草 \index{臺灣肺形草} \# LC
  \end{itemize}
  \end{itemize}
