
  \begin{itemize}
 \item[] \textit{Aeschynanthus} 長果藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeschynanthus+acuminatus}{\textit{A. acuminatus} Wall. ex A.DC.}  \index{Aeschynanthus@\textit{Aeschynanthus}!acuminatus@\textit{acuminatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長果藤&T2_new_value=true&fr=y}}{長果藤}\index{長果藤} LC
  \end{itemize}
 \item[] \textit{Chirita} 雙心皮草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chirita+anachoreta}{\textit{C. anachoreta} Hance}  \index{Chirita@\textit{Chirita}!anachoreta@\textbf{\textit{anachoreta}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙心皮草&T2_new_value=true&fr=y}}{雙心皮草}\index{雙心皮草@{\Song{雙心皮草}}} VU
  \end{itemize}
 \item[] \textit{Conandron} 苦苣苔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Conandron+ramondioides}{\textit{C. ramondioides} Siebold \& Zucc.}  \index{Conandron@\textit{Conandron}!ramondioides@\textit{ramondioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦苣苔&T2_new_value=true&fr=y}}{苦苣苔}\index{苦苣苔} NT
  \end{itemize}
 \item[] \textit{Cyrtandra} 偽苦苣苔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtandra+umbellifera}{\textit{C. umbellifera} Merr.}  \index{Cyrtandra@\textit{Cyrtandra}!umbellifera@\textbf{\textit{umbellifera}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雄胞囊草&T2_new_value=true&fr=y}}{雄胞囊草}\index{雄胞囊草@{\Song{雄胞囊草}}} VU
  \end{itemize}
 \item[] \textit{Epithema} 盾座苣苔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epithema+taiwanense+var.+fasciculatum}{\textit{E. taiwanense} S.S.Ying var. \textit{fasciculatum} (C.B. Clarke) Z.Yu Li \& M.T. Kao}  \index{Epithema@\textit{Epithema}!taiwanense@\textit{taiwanense}!var. fasciculatum@\textbf{var. \textit{fasciculatum}}}  \index{Epithema@\textit{Epithema}!taiwanensis@\textit{taiwanensis}!var. fasciculata@var. \textit{fasciculata}{\\\noindent(=\textit{Epithema taiwanense} var. \textit{fasciculatum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花苣苔&T2_new_value=true&fr=y}}{密花苣苔}\index{密花苣苔@{\Song{密花苣苔}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epithema+taiwanense+var.+taiwanensis}{\textit{E. taiwanense} S.S.Ying var. \textit{taiwanensis} }  \index{Epithema@\textit{Epithema}!taiwanense@\textit{taiwanense}!var. taiwanensis@\textbf{var. \textit{taiwanensis}}}  \index{Epithema@\textit{Epithema}!taiwanensis@\textit{taiwanensis}!var. taiwanensis@var. \textit{taiwanensis}{\\\noindent(=\textit{Epithema taiwanense} var. \textit{taiwanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣苣苔&T2_new_value=true&fr=y}}{臺灣苣苔}\index{臺灣苣苔@{\Song{臺灣苣苔}}}\# EN
  \end{itemize}
 \item[] \textit{Hemiboea} 角桐草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemiboea+bicornuta}{\textit{H. bicornuta} (Hayata) Ohwi}  \index{Hemiboea@\textit{Hemiboea}!bicornuta@\textit{bicornuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=角桐草&T2_new_value=true&fr=y}}{角桐草}\index{角桐草} LC
  \end{itemize}
 \item[] \textit{Lysionotus} 石吊蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysionotus+pauciflorus+var.+ikedae}{\textit{L. pauciflorus} Maxim. var. \textit{ikedae} (Hatus.) W.T.Wang}  \index{Lysionotus@\textit{Lysionotus}!pauciflorus@\textit{pauciflorus}!var. ikedae@\textbf{var. \textit{ikedae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼石吊蘭&T2_new_value=true&fr=y}}{蘭嶼石吊蘭}\index{蘭嶼石吊蘭@{\Song{蘭嶼石吊蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysionotus+pauciflorus+var.+pauciflorus}{\textit{L. pauciflorus} Maxim. var. \textit{pauciflorus}}  \index{Lysionotus@\textit{Lysionotus}!pauciflorus@\textit{pauciflorus}!var. pauciflorus@var. \textit{pauciflorus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石吊蘭&T2_new_value=true&fr=y}}{石吊蘭}\index{石吊蘭} LC
  \end{itemize}
 \item[] \textit{Paraboea} 旋莢木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraboea+swinhoii}{\textit{P. swinhoii} (Hance) B.L.Burtt}  \index{Paraboea@\textit{Paraboea}!swinhoii@\textit{swinhoii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=旋莢木&T2_new_value=true&fr=y}}{旋莢木}\index{旋莢木} LC
  \end{itemize}
 \item[] \textit{Rhynchoglossum} 尖舌草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchoglossum+obliquum+var.+hologlossum}{\textit{R. obliquum} Blume var. \textit{hologlossum} (Hayata) W.T.Wang}  \index{Rhynchoglossum@\textit{Rhynchoglossum}!obliquum@\textit{obliquum}!var. hologlossum@var. \textit{hologlossum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尖舌草&T2_new_value=true&fr=y}}{尖舌草}\index{尖舌草}\# LC
  \end{itemize}
 \item[] \textit{Rhynchotechum} 同蕊草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchotechum+brevipedunculatum}{\textit{R. brevipedunculatum} J.C.Wang}  \index{Rhynchotechum@\textit{Rhynchotechum}!brevipedunculatum@\textit{brevipedunculatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短梗同蕊草&T2_new_value=true&fr=y}}{短梗同蕊草}\index{短梗同蕊草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchotechum+discolor}{\textit{R. discolor} (Maxim.) B.L.Burtt}  \index{Rhynchotechum@\textit{Rhynchotechum}!discolor@\textit{discolor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=同蕊草&T2_new_value=true&fr=y}}{同蕊草}\index{同蕊草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchotechum+discolor+ f. +incisum}{\textit{R. discolor} (Maxim.) B.L.Burtt  f.  \textit{incisum} (Ohwi) Hatus. ex J.C.Wang}  \index{Rhynchotechum@\textit{Rhynchotechum}!discolor@\textit{discolor}!f. incisum@f. \textit{incisum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽裂同蕊草&T2_new_value=true&fr=y}}{羽裂同蕊草}\index{羽裂同蕊草} NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhynchotechum+formosanum}{\textit{R. formosanum} Hatus.}  \index{Rhynchotechum@\textit{Rhynchotechum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊同蕊草&T2_new_value=true&fr=y}}{蓬萊同蕊草}\index{蓬萊同蕊草} NT
  \end{itemize}
 \item[] \textit{Titanotrichum} 俄氏草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Titanotrichum+oldhamii}{\textit{T. oldhamii} (Hemsl.) Soler.}  \index{Titanotrichum@\textit{Titanotrichum}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=俄氏草&T2_new_value=true&fr=y}}{俄氏草}\index{俄氏草} LC
  \end{itemize}
 \item[] \textit{Whytockia} 玉玲花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Whytockia+sasakii}{\textit{W. sasakii} (Hayata) B.L.Burtt}  \index{Whytockia@\textit{Whytockia}!sasakii@\textit{sasakii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉玲花&T2_new_value=true&fr=y}}{玉玲花}\index{玉玲花}\# LC
  \end{itemize}
  \end{itemize}
