
  \begin{itemize}
 \item[] \textit{Dicranopteris} 芒萁屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dicranopteris+linearis}{\textit{D. linearis} (Burm.f.) Underw.}  \index{Dicranopteris@\textit{Dicranopteris}!linearis@\textit{linearis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=芒萁&T2_new_value=true&fr=y}}{芒萁}\index{芒萁} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dicranopteris+subpectinata}{\textit{D. subpectinata} (Christ) C.M.Kuo}  \index{Dicranopteris@\textit{Dicranopteris}!subpectinata@\textit{subpectinata}}  \index{Dicranopteris@\textit{Dicranopteris}!linearis@\textit{linearis}!var. subpectinata@var. \textit{subpectinata}{\\\noindent(=\textit{Dicranopteris subpectinata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賽芒萁&T2_new_value=true&fr=y}}{賽芒萁}\index{賽芒萁} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dicranopteris+taiwanensis}{\textit{D. taiwanensis} Ching \& P.S.Chiu}  \index{Dicranopteris@\textit{Dicranopteris}!taiwanensis@\textit{taiwanensis}}  \index{Dicranopteris@\textit{Dicranopteris}!linearis@\textit{linearis}!var. montana@var. \textit{montana}{\\\noindent(=\textit{Dicranopteris taiwanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣芒萁&T2_new_value=true&fr=y}}{臺灣芒萁(大羽芒萁)} \index{臺灣芒萁} \index{大羽芒萁@{大羽芒萁(=臺灣芒萁)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dicranopteris+tetraphylla}{\textit{D. tetraphylla} (Rosenst.) C.M.Kuo}  \index{Dicranopteris@\textit{Dicranopteris}!tetraphylla@\textit{tetraphylla}}  \index{Dicranopteris@\textit{Dicranopteris}!linearis@\textit{linearis}!var. tetraphylla@var. \textit{tetraphylla}{\\\noindent(=\textit{Dicranopteris tetraphylla})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓芒萁&T2_new_value=true&fr=y}}{蔓芒萁}\index{蔓芒萁} LC
  \end{itemize}
 \item[] \textit{Diplopterygium} 裏白屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplopterygium+blotianum}{\textit{D. blotianum} (C.Chr.) Nakai}  \index{Diplopterygium@\textit{Diplopterygium}!blotianum@\textit{blotianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=逆羽裏白&T2_new_value=true&fr=y}}{逆羽裏白}\index{逆羽裏白} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplopterygium+chinensis}{\textit{D. chinensis} (Rosenst.) DeVol}  \index{Diplopterygium@\textit{Diplopterygium}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中華裏白&T2_new_value=true&fr=y}}{中華裏白}\index{中華裏白} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplopterygium+glaucum}{\textit{D. glaucum} (Thunb. ex Houtt.) Nakai}  \index{Diplopterygium@\textit{Diplopterygium}!glaucum@\textit{glaucum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白&T2_new_value=true&fr=y}}{裏白}\index{裏白} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diplopterygium+laevissimum}{\textit{D. laevissimum} (H.Christ) Nakai}  \index{Diplopterygium@\textit{Diplopterygium}!laevissimum@\textit{laevissimum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鱗芽裏白&T2_new_value=true&fr=y}}{鱗芽裏白}\index{鱗芽裏白} LC
  \end{itemize}
  \end{itemize}
