
  \begin{itemize}
 \item[] \textit{Blyxa} 簀藻屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blyxa+aubertii}{\textit{B. aubertii} Rich.}  \index{Blyxa@\textit{Blyxa}!aubertii@\textit{aubertii}} 瘤果簀藻 \index{瘤果簀藻}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blyxa+echinosperma}{\textit{B. echinosperma} (C.B.Clarke) Hook.f.}  \index{Blyxa@\textit{Blyxa}!echinosperma@\textit{echinosperma}} 臺灣簀藻 \index{臺灣簀藻}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blyxa+japonica}{\textit{B. japonica} (Miq.) Maxim. ex Asch. \& Gürke}  \index{Blyxa@\textit{Blyxa}!japonica@\textit{japonica}} 日本簀藻 \index{日本簀藻}  NT
  \end{itemize}
 \item[] \textit{Egeria} 水蘊草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Egeria+densa}{\textit{E. densa} Planchon}  \index{Egeria@\textit{Egeria}!densa@\textit{densa}} 水蘊草 \index{水蘊草}  NA (N)
  \end{itemize}
 \item[] \textit{Halophila} 鹽藻屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Halophila+beccari}{\textit{H. beccari} Asch.}  \index{Halophila@\textit{Halophila}!beccari@\textit{beccari}} 貝氏鹽藻 \index{貝氏鹽藻}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Halophila+decipiens}{\textit{H. decipiens} Ostenf.}  \index{Halophila@\textit{Halophila}!decipiens@\textit{decipiens}} 毛葉鹽藻 \index{毛葉鹽藻}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Halophila+ovalis}{\textit{H. ovalis} (R.Br.) Hook.f.}  \index{Halophila@\textit{Halophila}!ovalis@\textit{ovalis}} 卵葉鹽藻 \index{卵葉鹽藻}  LC
  \end{itemize}
 \item[] \textit{Hydrilla} 水王孫屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrilla+verticillata}{\textit{H. verticillata} (L.f.) Royle}  \index{Hydrilla@\textit{Hydrilla}!verticillata@\textit{verticillata}} 水王孫 \index{水王孫}  LC
  \end{itemize}
 \item[] \textit{Hydrocharis} 水鼈屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hydrocharis+dubia}{\textit{H. dubia} (Blume) Backer}  \index{Hydrocharis@\textit{Hydrocharis}!dubia@\textit{dubia}} 水鱉 \index{水鱉}  NT
  \end{itemize}
 \item[] \textit{Limnobium} 南美海綿屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnobium+laevigatum}{\textit{L. laevigatum} (Humb. \& Bonpl. ex Willd.) Heine}  \index{Limnobium@\textit{Limnobium}!laevigatum@\textit{laevigatum}} 美洲水鱉 \index{美洲水鱉}  NA (N)
  \end{itemize}
 \item[] \textit{Najas} 拂尾藻屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+ancistrocarpa}{\textit{N. ancistrocarpa} A.Br. ex Magnus}  \index{Najas@\textit{Najas}!ancistrocarpa@\textit{ancistrocarpa}} 士林拂尾藻 \index{士林拂尾藻}  RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+browniana}{\textit{N. browniana} Rendle}  \index{Najas@\textit{Najas}!browniana@\textit{browniana}} 高雄茨藻 \index{高雄茨藻}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+gracillima}{\textit{N. gracillima} A.Br. ex Magnus}  \index{Najas@\textit{Najas}!gracillima@\textit{gracillima}} 日本茨藻 \index{日本茨藻}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+graminea}{\textit{N. graminea} Delile}  \index{Najas@\textit{Najas}!graminea@\textit{graminea}} 拂尾藻 \index{拂尾藻}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+indica}{\textit{N. indica} (Willd.) Cham.}  \index{Najas@\textit{Najas}!indica@\textit{indica}} 印度茨藻 \index{印度茨藻}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+marina}{\textit{N. marina} L.}  \index{Najas@\textit{Najas}!marina@\textit{marina}} 大茨藻 \index{大茨藻}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Najas+minor}{\textit{N. minor} All.}  \index{Najas@\textit{Najas}!minor@\textit{minor}} 小茨藻 \index{小茨藻}  LC
  \end{itemize}
 \item[] \textit{Ottelia} 水車前屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ottelia+alismoides}{\textit{O. alismoides} (L.) Pers.}  \index{Ottelia@\textit{Ottelia}!alismoides@\textit{alismoides}} 水車前草 \index{水車前草}  NT
  \end{itemize}
 \item[] \textit{Thalassia} 泰來藻屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalassia+hemprichii}{\textit{T. hemprichii} (Ehrenb.) Asch.}  \index{Thalassia@\textit{Thalassia}!hemprichii@\textit{hemprichii}} 泰來藻 \index{泰來藻}  LC
  \end{itemize}
 \item[] \textit{Vallisneria} 苦草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vallisneria+americana}{\textit{V. americana} Michx.}  \index{Vallisneria@\textit{Vallisneria}!americana@\textit{americana}} 美洲苦草 \index{美洲苦草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vallisneria+gigantea}{\textit{V. gigantea} Graebn.}  \index{Vallisneria@\textit{Vallisneria}!gigantea@\textit{gigantea}} 大苦草 \index{大苦草}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vallisneria+spiralis}{\textit{V. spiralis} L.}  \index{Vallisneria@\textit{Vallisneria}!spiralis@\textit{spiralis}} 旋葉苦草 \index{旋葉苦草}  NA (N)
  \end{itemize}
  \end{itemize}
