
  \begin{itemize}
 \item[] \textit{Abrodictyum} 長片蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abrodictyum+clathratum}{\textit{A. clathratum} (Tagawa) Ebihara \& K.Iwats.}  \index{Abrodictyum@\textit{Abrodictyum}!clathratum@\textit{clathratum}}  \index{Cephalomanes@\textit{Cephalomanes}!clathratum@\textit{clathratum}{\\\noindent(= \textit{Abrodictyum clathratum})}} 窗格長片蕨(厚葉蕨) \index{窗格長片蕨} \index{厚葉蕨@{厚葉蕨(=窗格長片蕨)}} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abrodictyum+cumingii}{\textit{A. cumingii} C.Presl}  \index{Abrodictyum@\textit{Abrodictyum}!cumingii@\textit{cumingii}} 長片蕨\index{長片蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abrodictyum+obscurum}{\textit{A. obscurum} (Blume) Ebihara \& K.Iwats.}  \index{Abrodictyum@\textit{Abrodictyum}!obscurum@\textit{obscurum}}  \index{Selenodesmium@\textit{Selenodesmium}!obscurum@\textit{obscurum}{\\\noindent(= \textit{Abrodictyum obscurum})}} 線片長筒蕨\index{線片長筒蕨} LC
  \end{itemize}
 \item[] \textit{Callistopteris} 毛桿蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callistopteris+apiifolia}{\textit{C. apiifolia} (C.Presl.) Copel.}  \index{Callistopteris@\textit{Callistopteris}!apiifolia@\textit{apiifolia}} 毛桿蕨\index{毛桿蕨} LC
  \end{itemize}
 \item[] \textit{Cephalomanes} 厚葉蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalomanes+javanicum+var.+asplenioides}{\textit{C. javanicum} (Blume) C.Presl var. \textit{asplenioides} (C.Presl) K.Iwats.}  \index{Cephalomanes@\textit{Cephalomanes}!javanicum@\textit{javanicum}!var. asplenioides@var. \textit{asplenioides}}  \index{Cephalomanes@\textit{Cephalomanes}!laciniatum@\textit{laciniatum}{\\\noindent(= \textit{Cephalomanes javanicum} var. \textit{asplenioides})}} 菲律賓厚葉蕨\index{菲律賓厚葉蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalomanes+thysanostomum}{\textit{C. thysanostomum} (Makino) Ebihara \& K.Iwats.}  \index{Cephalomanes@\textit{Cephalomanes}!thysanostomum@\textit{thysanostomum}}  \index{Nesopteris@\textit{Nesopteris}!thysanostomum@\textit{thysanostomum}{\\\noindent(= \textit{Cephalomanes thysanostomum})}} 球桿毛蕨\index{球桿毛蕨} NT
  \end{itemize}
 \item[] \textit{Crepidomanes} 假脈蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+bilabiatum}{\textit{C. bilabiatum} (Nees \& Blume) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!bilabiatum@\textit{bilabiatum}} 圓唇假脈蕨\index{圓唇假脈蕨} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+bipunctatum}{\textit{C. bipunctatum} (Poir.) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!bipunctatum@\textit{bipunctatum}} 南洋假脈蕨\index{南洋假脈蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+grande}{\textit{C. grande} (Copel.) Ebihara \& K.Iwats.}  \index{Crepidomanes@\textit{Crepidomanes}!grande@\textit{grande}} 大球稈毛蕨\index{大球稈毛蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+humile}{\textit{C. humile} (G.Forst.) Bosch}  \index{Crepidomanes@\textit{Crepidomanes}!humile@\textit{humile}}  \index{Reediella@\textit{Reediella}!humile@\textit{humile}{\\\noindent(= \textit{Crepidomanes humile})}} 厚邊蕨\index{厚邊蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+kurzii}{\textit{C. kurzii} (Bedd.) Tagawa \& K.Iwats.}  \index{Crepidomanes@\textit{Crepidomanes}!kurzii@\textit{kurzii}} 假脈蕨\index{假脈蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+latealatum}{\textit{C. latealatum} (Bosch) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!latealatum@\textit{latealatum}} 翅柄假脈蕨\index{翅柄假脈蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+latemarginale}{\textit{C. latemarginale} (D.C.Eaton) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!latemarginale@\textit{latemarginale}} 澗邊假脈蕨\index{澗邊假脈蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+makinoi}{\textit{C. makinoi} (C.Chr.) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!makinoi@\textit{makinoi}}  \index{Crepidomanes@\textit{Crepidomanes}!palmifolium@\textit{palmifolium}{\\\noindent(= \textit{Crepidomanes makinoi})}} 變葉假脈蕨\index{變葉假脈蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+minutum}{\textit{C. minutum} (Blume) K.Iwats.}  \index{Crepidomanes@\textit{Crepidomanes}!minutum@\textit{minutum}}  \index{Gonocormus@\textit{Gonocormus}!minutum@\textit{minutum}{\\\noindent(= \textit{Crepidomanes minutum})}} 團扇蕨\index{團扇蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+parvifolium}{\textit{C. parvifolium} (Baker) K.Iwats.}  \index{Crepidomanes@\textit{Crepidomanes}!parvifolium@\textit{parvifolium}} 小葉假脈蕨\index{小葉假脈蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+rupicola}{\textit{C. rupicola} (Racib.) Copel.}  \index{Crepidomanes@\textit{Crepidomanes}!rupicola@\textit{rupicola}} 石生假脈蕨\index{石生假脈蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+schmidtianum+var.+latifrons}{\textit{C. schmidtianum} (Zenker ex Taschner) K.Iwats. var. \textit{latifrons} (Bosch) K.Iwats.}  \index{Crepidomanes@\textit{Crepidomanes}!schmidtianum@\textit{schmidtianum}!var. latifrons@var. \textit{latifrons}} 寬葉瓶蕨\index{寬葉瓶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidomanes+vitiense}{\textit{C. vitiense} (Baker) Bostock}  \index{Crepidomanes@\textit{Crepidomanes}!vitiense@\textit{vitiense}} 斐濟假脈蕨\index{斐濟假脈蕨} VU
  \end{itemize}
 \item[] \textit{Didymoglossum} 單葉假脈蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoglossum+beccarianum}{\textit{D. beccarianum} (Cesati) Senterre \& Rouhan}  \index{Didymoglossum@\textit{Didymoglossum}!beccarianum@\textit{beccarianum}}  \index{Microgonium@\textit{Microgonium}!motleyi@\textit{motleyi}{\\\noindent(= \textit{Didymoglossum beccarianum})}} 細柄單葉假脈蕨\index{細柄單葉假脈蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoglossum+bimarginatum}{\textit{D. bimarginatum} (Bosch) Ebihara \& K.Iwats.}  \index{Didymoglossum@\textit{Didymoglossum}!bimarginatum@\textit{bimarginatum}}  \index{Microgonium@\textit{Microgonium}!bimarginatum@\textit{bimarginatum}{\\\noindent(= \textit{Didymoglossum bimarginatum})}} 叉脈單葉假脈蕨\index{叉脈單葉假脈蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoglossum+motleyi}{\textit{D. motleyi} (Bosch) Ebihara \& K.Iwats.}  \index{Didymoglossum@\textit{Didymoglossum}!motleyi@\textit{motleyi}} 短柄單葉假脈蕨\index{短柄單葉假脈蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoglossum+sublimbatum}{\textit{D. sublimbatum} (Müll.Berol.) Ebihara \& K.Iwats.}  \index{Didymoglossum@\textit{Didymoglossum}!sublimbatum@\textit{sublimbatum}} 亞緣單葉假脈蕨\index{亞緣單葉假脈蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoglossum+tahitense}{\textit{D. tahitense} (Nadeaud) Ebihara \& K.Iwats.}  \index{Didymoglossum@\textit{Didymoglossum}!tahitense@\textit{tahitense}}  \index{Microgonium@\textit{Microgonium}!omphalodes@\textit{omphalodes}{\\\noindent(= \textit{Didymoglossum tahitense})}} 盾形單葉假脈蕨\index{盾形單葉假脈蕨} LC
  \end{itemize}
 \item[] \textit{Hymenophyllum} 膜蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+acutum}{\textit{H. acutum} (C.Presl) Ebihara \& K.Iwats.}  \index{Hymenophyllum@\textit{Hymenophyllum}!acutum@\textit{acutum}} 疏毛毛葉蕨\index{疏毛毛葉蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+badium}{\textit{H. badium} Hook. \& Grev.}  \index{Hymenophyllum@\textit{Hymenophyllum}!badium@\textit{badium}}  \index{Mecodium@\textit{Mecodium}!badium@\textit{badium}{\\\noindent(= \textit{Hymenophyllum badium})}} 蕗蕨\index{蕗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+barbatum}{\textit{H. barbatum} (Bosch) Baker}  \index{Hymenophyllum@\textit{Hymenophyllum}!barbatum@\textit{barbatum}} 華東膜蕨\index{華東膜蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+blandum}{\textit{H. blandum} Racib.}  \index{Hymenophyllum@\textit{Hymenophyllum}!blandum@\textit{blandum}} 爪哇厚壁蕨\index{爪哇厚壁蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+denticulatum}{\textit{H. denticulatum} Sw.}  \index{Hymenophyllum@\textit{Hymenophyllum}!denticulatum@\textit{denticulatum}} 厚壁蕨\index{厚壁蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+devolii}{\textit{H. devolii} M.J.Lai}  \index{Hymenophyllum@\textit{Hymenophyllum}!devolii@\textit{devolii}} 臺灣膜蕨\index{臺灣膜蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+digitatum}{\textit{H. digitatum} (Sw.) Fosberg}  \index{Hymenophyllum@\textit{Hymenophyllum}!digitatum@\textit{digitatum}} 指裂細口團扇蕨\index{指裂細口團扇蕨} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+fimbriatum}{\textit{H. fimbriatum} J.Sm.}  \index{Hymenophyllum@\textit{Hymenophyllum}!fimbriatum@\textit{fimbriatum}} 叢葉蕗蕨\index{叢葉蕗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+holochilum}{\textit{H. holochilum} (Bosch) C.Chr.}  \index{Hymenophyllum@\textit{Hymenophyllum}!holochilum@\textit{holochilum}}  \index{Mecodium@\textit{Mecodium}!holochilum@\textit{holochilum}{\\\noindent(= \textit{Hymenophyllum holochilum})}} 南洋厚壁蕨\index{南洋厚壁蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+javanicum}{\textit{H. javanicum} Spreng.}  \index{Hymenophyllum@\textit{Hymenophyllum}!javanicum@\textit{javanicum}} 爪哇蕗蕨\index{爪哇蕗蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+nitidulum}{\textit{H. nitidulum} (Bosch) Ebihara \& K.Iwats.}  \index{Hymenophyllum@\textit{Hymenophyllum}!nitidulum@\textit{nitidulum}}  \index{Microtrichomanes@\textit{Microtrichomanes}!nitidulum@\textit{nitidulum}{\\\noindent(= \textit{Hymenophyllum nitidulum})}} 細口團扇蕨\index{細口團扇蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+okadae}{\textit{H. okadae} Masam.}  \index{Hymenophyllum@\textit{Hymenophyllum}!okadae@\textit{okadae}} 青綠膜蕨\index{青綠膜蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+oligosorum}{\textit{H. oligosorum} Makino}  \index{Hymenophyllum@\textit{Hymenophyllum}!oligosorum@\textit{oligosorum}}  \index{Mecodium@\textit{Mecodium}!oligosorum@\textit{oligosorum}{\\\noindent(= \textit{Hymenophyllum oligosorum})}} 長毛蕗蕨\index{長毛蕗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+pallidum}{\textit{H. pallidum} (Blume) Ebihara \& K.Iwats.}  \index{Hymenophyllum@\textit{Hymenophyllum}!pallidum@\textit{pallidum}}  \index{Pleuromanes@\textit{Pleuromanes}!pallidum@\textit{pallidum}{\\\noindent(= \textit{Hymenophyllum pallidum})}} 毛葉蕨\index{毛葉蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+palmatifidum}{\textit{H. palmatifidum} (Mull.Berol.) Ebihara \& K.Iwats.}  \index{Hymenophyllum@\textit{Hymenophyllum}!palmatifidum@\textit{palmatifidum}} 毛緣細口團扇蕨\index{毛緣細口團扇蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+paniculiflorum}{\textit{H. paniculiflorum} C.Presl}  \index{Hymenophyllum@\textit{Hymenophyllum}!paniculiflorum@\textit{paniculiflorum}} 圓錐孢膜蕨\index{圓錐孢膜蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+pilosissimum}{\textit{H. pilosissimum} C.Chr.}  \index{Hymenophyllum@\textit{Hymenophyllum}!pilosissimum@\textit{pilosissimum}} 星毛膜蕨\index{星毛膜蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+polyanthos}{\textit{H. polyanthos} (Sw.) Sw.}  \index{Hymenophyllum@\textit{Hymenophyllum}!polyanthos@\textit{polyanthos}}  \index{Mecodium@\textit{Mecodium}!polyanthos@\textit{polyanthos}{\\\noindent(= \textit{Hymenophyllum polyanthos})}} 細葉蕗蕨\index{細葉蕗蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+productum}{\textit{H. productum} Kunze}  \index{Hymenophyllum@\textit{Hymenophyllum}!productum@\textit{productum}} 南洋蕗蕨\index{南洋蕗蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+semialatum}{\textit{H. semialatum} T.C.Hsu}  \index{Hymenophyllum@\textit{Hymenophyllum}!semialatum@\textit{semialatum}} 半翼柄蕗蕨\index{半翼柄蕗蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+simonsianum}{\textit{H. simonsianum} Hook.}  \index{Hymenophyllum@\textit{Hymenophyllum}!simonsianum@\textit{simonsianum}}  \index{Hymenophyllum@\textit{Hymenophyllum}!alishanense@\textit{alishanense}{\\\noindent(= \textit{Hymenophyllum simonsianum})}} 寬片膜蕨(阿里山膜蕨) \index{寬片膜蕨} \index{阿里山膜蕨@{阿里山膜蕨(=寬片膜蕨)}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hymenophyllum+taiwanense}{\textit{H. taiwanense} (Tagawa) C.V.Morton}  \index{Hymenophyllum@\textit{Hymenophyllum}!taiwanense@\textit{taiwanense}} 臺灣蕗蕨\index{臺灣蕗蕨} CR
  \end{itemize}
 \item[] \textit{Vandenboschia} 瓶蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandenboschia+auriculata}{\textit{V. auriculata} (Blume) Copel.}  \index{Vandenboschia@\textit{Vandenboschia}!auriculata@\textit{auriculata}} 瓶蕨\index{瓶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandenboschia+kalamocarpa}{\textit{V. kalamocarpa} (Hayata) Ebihara}  \index{Vandenboschia@\textit{Vandenboschia}!kalamocarpa@\textit{kalamocarpa}} 華東瓶蕨\index{華東瓶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandenboschia+maxima}{\textit{V. maxima} (Blume) Copel.}  \index{Vandenboschia@\textit{Vandenboschia}!maxima@\textit{maxima}} 大葉瓶蕨\index{大葉瓶蕨} LC
  \end{itemize}
 \item[] \textit{Vandenboschoa} 西藏瓶蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandenboschoa+striata}{\textit{V. striata} (D.Don) Ebihara}  \index{Vandenboschoa@\textit{Vandenboschoa}!striata@\textit{striata}}  \index{Crepidomanes@\textit{Crepidomanes}!birmanicum@\textit{birmanicum}{\\\noindent(= \textit{Vandenboschoa striata})}}   \index{Vandenboschia@\textit{Vandenboschia}!radicans@\textit{radicans}{\\\noindent(= \textit{Vandenboschoa striata})}} 南海瓶蕨(華東瓶蕨) \index{南海瓶蕨} \index{華東瓶蕨@{華東瓶蕨(=南海瓶蕨)}} LC
  \end{itemize}
  \end{itemize}
