
  \begin{itemize}
 \item[] \textit{Hypericum} 金絲桃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+ascyron}{\textit{H. ascyron} L.}  \index{Hypericum@\textit{Hypericum}!ascyron@\textit{ascyron}} 連翹\index{連翹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+erectum}{\textit{H. erectum} Thunb.}  \index{Hypericum@\textit{Hypericum}!erectum@\textit{erectum}} 小連翹\index{小連翹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+formosanum}{\textit{H. formosanum} Maxim.}  \index{Hypericum@\textit{Hypericum}!formosanum@\textit{formosanum}} 臺灣金絲桃\index{臺灣金絲桃}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+geminiflorum}{\textit{H. geminiflorum} Hemsl.}  \index{Hypericum@\textit{Hypericum}!geminiflorum@\textit{geminiflorum}} 雙花金絲桃\index{雙花金絲桃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+geminiflorum+var.+simplicistylum}{\textit{H. geminiflorum} Hemsl. var. \textit{simplicistylum} (Hayata) N.Robson}  \index{Hypericum@\textit{Hypericum}!geminiflorum@\textit{geminiflorum}!var. simplicistylum@var. \textit{simplicistylum}} 小雙花金絲桃\index{小雙花金絲桃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+gramineum}{\textit{H. gramineum} G.Forst.}  \index{Hypericum@\textit{Hypericum}!gramineum@\textit{gramineum}} 細葉金絲桃\index{細葉金絲桃} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+japonicum}{\textit{H. japonicum} Thunb.}  \index{Hypericum@\textit{Hypericum}!japonicum@\textit{japonicum}} 地耳草\index{地耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+nagasawai}{\textit{H. nagasawai} Hayata}  \index{Hypericum@\textit{Hypericum}!nagasawai@\textit{nagasawai}} 玉山金絲桃\index{玉山金絲桃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+nakamurai}{\textit{H. nakamurai} (Masam.) Robson}  \index{Hypericum@\textit{Hypericum}!nakamurai@\textit{nakamurai}} 清水金絲桃\index{清水金絲桃}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+nokoense}{\textit{H. nokoense} Ohwi}  \index{Hypericum@\textit{Hypericum}!nokoense@\textit{nokoense}} 能高金絲桃\index{能高金絲桃}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+patulum}{\textit{H. patulum} Thunb. ex Murray}  \index{Hypericum@\textit{Hypericum}!patulum@\textit{patulum}} 金絲梅\index{金絲梅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+sampsonii}{\textit{H. sampsonii} Hance}  \index{Hypericum@\textit{Hypericum}!sampsonii@\textit{sampsonii}} 元寶草\index{元寶草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+subalatum}{\textit{H. subalatum} Hayata}  \index{Hypericum@\textit{Hypericum}!subalatum@\textit{subalatum}} 方莖金絲桃\index{方莖金絲桃}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hypericum+taihezanense}{\textit{H. taihezanense} Sasaki ex S.Suzuki}  \index{Hypericum@\textit{Hypericum}!taihezanense@\textit{taihezanense}} 短柄金絲桃\index{短柄金絲桃} LC
  \end{itemize}
 \item[] \textit{Triadenum} 三腺金絲桃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triadenum+breviflorum}{\textit{T. breviflorum} (Wall. ex Dyer) Y.Kimura}  \index{Triadenum@\textit{Triadenum}!breviflorum@\textit{breviflorum}} 三腺金絲桃\index{三腺金絲桃} DD
  \end{itemize}
  \end{itemize}
