
  \begin{itemize}
 \item[] \textit{Agastache} 藿香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agastache+rugosa}{\textit{A. rugosa} (Fisch. \& Mey.) Kuntze}  \index{Agastache@\textit{Agastache}!rugosa@\textit{rugosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藿香&T2_new_value=true&fr=y}}{藿香}\index{藿香} NT
  \end{itemize}
 \item[] \textit{Ajuga} 筋骨草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ajuga+decumbens}{\textit{A. decumbens} Thunb.}  \index{Ajuga@\textit{Ajuga}!decumbens@\textit{decumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匍伏筋骨草&T2_new_value=true&fr=y}}{匍伏筋骨草}\index{匍伏筋骨草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ajuga+dictyocarpa}{\textit{A. dictyocarpa} Hayata}  \index{Ajuga@\textit{Ajuga}!dictyocarpa@\textbf{\textit{dictyocarpa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網果筋骨草&T2_new_value=true&fr=y}}{網果筋骨草}\index{網果筋骨草@{\Song{網果筋骨草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ajuga+nipponensis}{\textit{A. nipponensis} Makino}  \index{Ajuga@\textit{Ajuga}!nipponensis@\textbf{\textit{nipponensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本筋骨草&T2_new_value=true&fr=y}}{日本筋骨草}\index{日本筋骨草@{\Song{日本筋骨草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ajuga+pygmaea}{\textit{A. pygmaea} A.Gray}  \index{Ajuga@\textit{Ajuga}!pygmaea@\textbf{\textit{pygmaea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=矮筋骨草&T2_new_value=true&fr=y}}{矮筋骨草}\index{矮筋骨草@{\Song{矮筋骨草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ajuga+taiwanensis}{\textit{A. taiwanensis} Nakai ex Murata}  \index{Ajuga@\textit{Ajuga}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣筋骨草&T2_new_value=true&fr=y}}{臺灣筋骨草}\index{臺灣筋骨草} LC
  \end{itemize}
 \item[] \textit{Anisomeles} 金劍草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anisomeles+indica}{\textit{A. indica} (L.) Kuntze}  \index{Anisomeles@\textit{Anisomeles}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金劍草&T2_new_value=true&fr=y}}{金劍草}\index{金劍草} LC
  \end{itemize}
 \item[] \textit{Basilicum} 小冠薰屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Basilicum+polystachyon}{\textit{B. polystachyon} (L.) Moench.}  \index{Basilicum@\textit{Basilicum}!polystachyon@\textbf{\textit{polystachyon}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小冠薰&T2_new_value=true&fr=y}}{小冠薰}\index{小冠薰@{\Song{小冠薰}}} VU
  \end{itemize}
 \item[] \textit{Bostrychanthera} 毛葯花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bostrychanthera+deflexa}{\textit{B. deflexa} Benth.}  \index{Bostrychanthera@\textit{Bostrychanthera}!deflexa@\textit{deflexa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛葯花&T2_new_value=true&fr=y}}{毛葯花}\index{毛葯花} LC
  \end{itemize}
 \item[] \textit{Callicarpa} 紫珠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+formosana+var.+formosana}{\textit{C. formosana} Rolfe var. \textit{formosana}}  \index{Callicarpa@\textit{Callicarpa}!formosana@\textit{formosana}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杜虹花&T2_new_value=true&fr=y}}{杜虹花}\index{杜虹花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+formosana+var.+glabrata}{\textit{C. formosana} Rolfe var. \textit{glabrata} Tien T.Chen, S.M.Chaw \& Yuen P.Yang}  \index{Callicarpa@\textit{Callicarpa}!formosana@\textit{formosana}!var. glabrata@var. \textit{glabrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=六龜粗糠樹&T2_new_value=true&fr=y}}{六龜粗糠樹}\index{六龜粗糠樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+formosana+var.+longifolia}{\textit{C. formosana} Rolfe var. \textit{longifolia} Suzuki}  \index{Callicarpa@\textit{Callicarpa}!formosana@\textit{formosana}!var. longifolia@\textbf{var. \textit{longifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉杜虹花&T2_new_value=true&fr=y}}{長葉杜虹花}\index{長葉杜虹花@{\Song{長葉杜虹花}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+hypoleucophylla}{\textit{C. hypoleucophylla} W.F.Lin \& J.L.Wang}  \index{Callicarpa@\textit{Callicarpa}!hypoleucophylla@\textbf{\textit{hypoleucophylla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰背葉紫珠&T2_new_value=true&fr=y}}{灰背葉紫珠}\index{灰背葉紫珠@{\Song{灰背葉紫珠}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+japonica+var.+luxurians}{\textit{C. japonica} Thunb. var. \textit{luxurians} Rehder}  \index{Callicarpa@\textit{Callicarpa}!japonica@\textit{japonica}!var. luxurians@var. \textit{luxurians}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=朝鮮紫珠&T2_new_value=true&fr=y}}{朝鮮紫珠}\index{朝鮮紫珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+kochiana}{\textit{C. kochiana} Makino}  \index{Callicarpa@\textit{Callicarpa}!kochiana@\textit{kochiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼紫珠&T2_new_value=true&fr=y}}{鬼紫珠}\index{鬼紫珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+longissima}{\textit{C. longissima} (Hemsl.) Merr.}  \index{Callicarpa@\textit{Callicarpa}!longissima@\textit{longissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉紫珠&T2_new_value=true&fr=y}}{長葉紫珠}\index{長葉紫珠} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+pilosissima}{\textit{C. pilosissima} Maxim.}  \index{Callicarpa@\textit{Callicarpa}!pilosissima@\textit{pilosissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉紫珠&T2_new_value=true&fr=y}}{細葉紫珠}\index{細葉紫珠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+randaiensis}{\textit{C. randaiensis} Hayata}  \index{Callicarpa@\textit{Callicarpa}!randaiensis@\textit{randaiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巒大紫珠&T2_new_value=true&fr=y}}{巒大紫珠}\index{巒大紫珠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+remotiflora}{\textit{C. remotiflora} W.F.Lin \& J.L.Wang}  \index{Callicarpa@\textit{Callicarpa}!remotiflora@\textit{remotiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花紫珠&T2_new_value=true&fr=y}}{疏花紫珠}\index{疏花紫珠}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+remotiserrulata}{\textit{C. remotiserrulata} Hayata}  \index{Callicarpa@\textit{Callicarpa}!remotiserrulata@\textit{remotiserrulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏齒紫珠&T2_new_value=true&fr=y}}{疏齒紫珠}\index{疏齒紫珠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callicarpa+tikusikensis}{\textit{C. tikusikensis} Masam.}  \index{Callicarpa@\textit{Callicarpa}!tikusikensis@\textit{tikusikensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳葉紫珠&T2_new_value=true&fr=y}}{銳葉紫珠}\index{銳葉紫珠}\# LC
  \end{itemize}
 \item[] \textit{Caryopteris} 蕕屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Caryopteris+incana}{\textit{C. incana} (Thunb. ex Houtt.) Miq.}  \index{Caryopteris@\textit{Caryopteris}!incana@\textit{incana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰葉蕕&T2_new_value=true&fr=y}}{灰葉蕕}\index{灰葉蕕} LC
  \end{itemize}
 \item[] \textit{Clerodendrum} 海州常山屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+canescens}{\textit{C. canescens} Wall. ex Walp.}  \index{Clerodendrum@\textit{Clerodendrum}!canescens@\textit{canescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白毛臭牡丹&T2_new_value=true&fr=y}}{白毛臭牡丹}\index{白毛臭牡丹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+chinense}{\textit{C. chinense} (Osbeck) Mabb.}  \index{Clerodendrum@\textit{Clerodendrum}!chinense@\textit{chinense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭茉莉&T2_new_value=true&fr=y}}{臭茉莉}\index{臭茉莉} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+cyrtophyllum}{\textit{C. cyrtophyllum} Turcz.}  \index{Clerodendrum@\textit{Clerodendrum}!cyrtophyllum@\textit{cyrtophyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大青&T2_new_value=true&fr=y}}{大青}\index{大青} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+inerme}{\textit{C. inerme} (L.) Gaertn.}  \index{Clerodendrum@\textit{Clerodendrum}!inerme@\textit{inerme}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦林盤&T2_new_value=true&fr=y}}{苦林盤}\index{苦林盤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+japonicum+var.+album}{\textit{C. japonicum} (Thunb.) Sweet var. \textit{album} C.Pei}  \index{Clerodendrum@\textit{Clerodendrum}!japonicum@\textit{japonicum}!var. album@var. \textit{album}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白龍船花&T2_new_value=true&fr=y}}{白龍船花}\index{白龍船花} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+japonicum+var.+japonicum}{\textit{C. japonicum} (Thunb.) Sweet var. \textit{japonicum}}  \index{Clerodendrum@\textit{Clerodendrum}!japonicum@\textit{japonicum}!var. japonicum@var. \textit{japonicum}}  \index{Clerodendrum@\textit{Clerodendrum}!kaempferi@\textit{kaempferi}{\\\noindent(= \textit{Clerodendrum japonicum} var. \textit{japonicum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=龍船花&T2_new_value=true&fr=y}}{龍船花}\index{龍船花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+ohwi}{\textit{C. ohwi} Kaneh. \& Hatus.}  \index{Clerodendrum@\textit{Clerodendrum}!ohwi@\textit{ohwi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=花蓮海州常山&T2_new_value=true&fr=y}}{花蓮海州常山}\index{花蓮海州常山}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clerodendrum+trichotomum}{\textit{C. trichotomum} Thunb.}  \index{Clerodendrum@\textit{Clerodendrum}!trichotomum@\textit{trichotomum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海州常山&T2_new_value=true&fr=y}}{海州常山}\index{海州常山} LC
  \end{itemize}
 \item[] \textit{Clinopodium} 風輪菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clinopodium+brownei}{\textit{C. brownei} (Sw.) Kuntze }  \index{Clinopodium@\textit{Clinopodium}!brownei@\textit{brownei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=伏生風輪菜&T2_new_value=true&fr=y}}{伏生風輪菜}\index{伏生風輪菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clinopodium+chinense}{\textit{C. chinense} (Benth.) Kuntze}  \index{Clinopodium@\textit{Clinopodium}!chinense@\textit{chinense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=風輪菜&T2_new_value=true&fr=y}}{風輪菜}\index{風輪菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clinopodium+gracile}{\textit{C. gracile} (Benth.) Kuntze}  \index{Clinopodium@\textit{Clinopodium}!gracile@\textit{gracile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光風輪&T2_new_value=true&fr=y}}{光風輪}\index{光風輪} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clinopodium+laxiflorum}{\textit{C. laxiflorum} (Hayata) Mori}  \index{Clinopodium@\textit{Clinopodium}!laxiflorum@\textit{laxiflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花風輪菜&T2_new_value=true&fr=y}}{疏花風輪菜}\index{疏花風輪菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clinopodium+laxiflorum+var.+taiwanianum}{\textit{C. laxiflorum} (Hayata) Mori var. \textit{taiwanianum} T.H.Hsieh \& T.C.Huang}  \index{Clinopodium@\textit{Clinopodium}!laxiflorum@\textit{laxiflorum}!var. taiwanianum@var. \textit{taiwanianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣風輪菜&T2_new_value=true&fr=y}}{臺灣風輪菜}\index{臺灣風輪菜}\# NT
  \end{itemize}
 \item[] \textit{Coleus} 鞘蕊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coleus+amboinicus}{\textit{C. amboinicus} Lour.}  \index{Coleus@\textit{Coleus}!amboinicus@\textit{amboinicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=到手香&T2_new_value=true&fr=y}}{到手香}\index{到手香} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coleus+formosanus}{\textit{C. formosanus} Hayata}  \index{Coleus@\textit{Coleus}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼小鞘蕊花&T2_new_value=true&fr=y}}{蘭嶼小鞘蕊花}\index{蘭嶼小鞘蕊花} LC
  \end{itemize}
 \item[] \textit{Collinsonia} 馬香草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Collinsonia+macrobracteata}{\textit{C. macrobracteata} (Masam.) Harley}  \index{Collinsonia@\textit{Collinsonia}!macrobracteata@\textbf{\textit{macrobracteata}}}  \index{Keiskea@\textit{Keiskea}!macrobracteata@\textit{macrobracteata}{\\\noindent(= \textit{Collinsonia macrobracteata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大苞偏穗花&T2_new_value=true&fr=y}}{大苞偏穗花}\index{大苞偏穗花@{\Song{大苞偏穗花}}}\# VU
  \end{itemize}
 \item[] \textit{Comanthosphace} 綿穗蘇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Comanthosphace+formosana}{\textit{C. formosana} Ohwi}  \index{Comanthosphace@\textit{Comanthosphace}!formosana@\textbf{\textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣白木草&T2_new_value=true&fr=y}}{臺灣白木草}\index{臺灣白木草@{\Song{臺灣白木草}}}\# VU
  \end{itemize}
 \item[] \textit{Elsholtzia} 香薷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elsholtzia+ciliata}{\textit{E. ciliata} (Thunb.) Hylander}  \index{Elsholtzia@\textit{Elsholtzia}!ciliata@\textit{ciliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香薷&T2_new_value=true&fr=y}}{香薷}\index{香薷} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elsholtzia+strobilifera}{\textit{E. strobilifera} Benth.}  \index{Elsholtzia@\textit{Elsholtzia}!strobilifera@\textit{strobilifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球花香薷&T2_new_value=true&fr=y}}{球花香薷}\index{球花香薷} LC
  \end{itemize}
 \item[] \textit{Glechoma} 金錢薄荷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glechoma+hederacea+var.+grandis}{\textit{G. hederacea} L. var. \textit{grandis} (A.Gray) Kudo}  \index{Glechoma@\textit{Glechoma}!hederacea@\textit{hederacea}!var. grandis@var. \textit{grandis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金錢薄荷&T2_new_value=true&fr=y}}{金錢薄荷}\index{金錢薄荷} LC
  \end{itemize}
 \item[] \textit{Gomphostemma} 錐花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gomphostemma+callicarpoides}{\textit{G. callicarpoides} (Yamam.) Masam.}  \index{Gomphostemma@\textit{Gomphostemma}!callicarpoides@\textit{callicarpoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣錐花&T2_new_value=true&fr=y}}{臺灣錐花}\index{臺灣錐花}\# LC
  \end{itemize}
 \item[] \textit{Hyptis} 香苦草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hyptis+brevipes}{\textit{H. brevipes} Poir.}  \index{Hyptis@\textit{Hyptis}!brevipes@\textit{brevipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短柄香苦草&T2_new_value=true&fr=y}}{短柄香苦草}\index{短柄香苦草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hyptis+pectinata}{\textit{H. pectinata} (L.) Poit.}  \index{Hyptis@\textit{Hyptis}!pectinata@\textit{pectinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=櫛穗香苦草&T2_new_value=true&fr=y}}{櫛穗香苦草}\index{櫛穗香苦草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hyptis+rhomboides}{\textit{H. rhomboides} Mart. \& Gal.}  \index{Hyptis@\textit{Hyptis}!rhomboides@\textit{rhomboides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=頭花香苦草&T2_new_value=true&fr=y}}{頭花香苦草}\index{頭花香苦草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hyptis+spicigera}{\textit{H. spicigera} Lam.}  \index{Hyptis@\textit{Hyptis}!spicigera@\textit{spicigera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=穗花香苦草&T2_new_value=true&fr=y}}{穗花香苦草}\index{穗花香苦草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hyptis+suaveolens}{\textit{H. suaveolens} (L.) Poir.}  \index{Hyptis@\textit{Hyptis}!suaveolens@\textit{suaveolens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香苦草&T2_new_value=true&fr=y}}{香苦草}\index{香苦草} LC
  \end{itemize}
 \item[] \textit{Isodon} 香茶菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Isodon+amethystoides}{\textit{I. amethystoides} (Benth.) H.Hara}  \index{Isodon@\textit{Isodon}!amethystoides@\textit{amethystoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香茶菜&T2_new_value=true&fr=y}}{香茶菜}\index{香茶菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Isodon+macrocalyx}{\textit{I. macrocalyx} (Dunn) Kudo}  \index{Isodon@\textit{Isodon}!macrocalyx@\textit{macrocalyx}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大萼香茶菜&T2_new_value=true&fr=y}}{大萼香茶菜}\index{大萼香茶菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Isodon+serra}{\textit{I. serra} (Maxim.) Kudo}  \index{Isodon@\textit{Isodon}!serra@\textit{serra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鋸葉香茶菜&T2_new_value=true&fr=y}}{鋸葉香茶菜}\index{鋸葉香茶菜} LC
  \end{itemize}
 \item[] \textit{Lamium} 野芝麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lamium+amplexicaule}{\textit{L. amplexicaule} L.}  \index{Lamium@\textit{Lamium}!amplexicaule@\textbf{\textit{amplexicaule}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寶蓋草&T2_new_value=true&fr=y}}{寶蓋草}\index{寶蓋草@{\Song{寶蓋草}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lamium+hybridum}{\textit{L. hybridum} Vill.}  \index{Lamium@\textit{Lamium}!hybridum@\textit{hybridum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雜種野芝麻&T2_new_value=true&fr=y}}{雜種野芝麻}\index{雜種野芝麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lamium+purpureum}{\textit{L. purpureum} L.}  \index{Lamium@\textit{Lamium}!purpureum@\textit{purpureum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓齒野芝麻&T2_new_value=true&fr=y}}{圓齒野芝麻}\index{圓齒野芝麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lamium+tuberiferum}{\textit{L. tuberiferum} (Makino) Ohwi}  \index{Lamium@\textit{Lamium}!tuberiferum@\textit{tuberiferum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=塊莖小野芝麻&T2_new_value=true&fr=y}}{塊莖小野芝麻}\index{塊莖小野芝麻} LC
  \end{itemize}
 \item[] \textit{Leonurus} 益母草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leonurus+japonicus}{\textit{L. japonicus} Houtt.}  \index{Leonurus@\textit{Leonurus}!japonicus@\textit{japonicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=益母草&T2_new_value=true&fr=y}}{益母草}\index{益母草} LC
  \end{itemize}
 \item[] \textit{Leucas} 白花草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leucas+chinensis}{\textit{L. chinensis} (Retz.) R.Br.}  \index{Leucas@\textit{Leucas}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花草&T2_new_value=true&fr=y}}{白花草}\index{白花草} LC
  \end{itemize}
 \item[] \textit{Lycopus} 地筍屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lycopus+lucidus}{\textit{L. lucidus} Turcz.}  \index{Lycopus@\textit{Lycopus}!lucidus@\textbf{\textit{lucidus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=地筍&T2_new_value=true&fr=y}}{地筍}\index{地筍@{\Song{地筍}}} EN
  \end{itemize}
 \item[] \textit{Melissa} 蜜蜂花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melissa+axillaris}{\textit{M. axillaris} Bakh.f.}  \index{Melissa@\textit{Melissa}!axillaris@\textit{axillaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蜜蜂花&T2_new_value=true&fr=y}}{蜜蜂花}\index{蜜蜂花} LC
  \end{itemize}
 \item[] \textit{Mentha} 薄荷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mentha+arvensis+subsp.+piperascens}{\textit{M. arvensis} L. subsp. \textit{piperascens} (Malinv. ex Holmes) H.Hara}  \index{Mentha@\textit{Mentha}!arvensis@\textit{arvensis}!subsp. piperascens@subsp. \textit{piperascens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本薄荷&T2_new_value=true&fr=y}}{日本薄荷}\index{日本薄荷} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mentha+canadensis}{\textit{M. canadensis} L.}  \index{Mentha@\textit{Mentha}!canadensis@\textit{canadensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄荷&T2_new_value=true&fr=y}}{薄荷}\index{薄荷} LC
  \end{itemize}
 \item[] \textit{Mosla} 乾汗草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mosla+chinensis}{\textit{M. chinensis} Maxim.}  \index{Mosla@\textit{Mosla}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=乾汗草&T2_new_value=true&fr=y}}{乾汗草}\index{乾汗草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mosla+dianthera}{\textit{M. dianthera} (Buch.-Ham. ex Roxb.) Maxim.}  \index{Mosla@\textit{Mosla}!dianthera@\textit{dianthera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗鋸齒薺薴&T2_new_value=true&fr=y}}{粗鋸齒薺薴}\index{粗鋸齒薺薴} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mosla+scabra}{\textit{M. scabra} (Thunb.) C.Y.Wu \& H.W.Li}  \index{Mosla@\textit{Mosla}!scabra@\textit{scabra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石薺薴&T2_new_value=true&fr=y}}{石薺薴}\index{石薺薴} LC
  \end{itemize}
 \item[] \textit{Ocimum} 羅勒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ocimum+basilicum}{\textit{O. basilicum} L.}  \index{Ocimum@\textit{Ocimum}!basilicum@\textit{basilicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羅勒&T2_new_value=true&fr=y}}{羅勒}\index{羅勒} NA$^n$
  \end{itemize}
 \item[] \textit{Origanum} 野薄荷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Origanum+vulgare}{\textit{O. vulgare} L.}  \index{Origanum@\textit{Origanum}!vulgare@\textit{vulgare}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野薄荷&T2_new_value=true&fr=y}}{野薄荷}\index{野薄荷} LC
  \end{itemize}
 \item[] \textit{Orthosiphon} 貓鬚草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Orthosiphon+aristatus}{\textit{O. aristatus} (Blume) Miq.}  \index{Orthosiphon@\textit{Orthosiphon}!aristatus@\textit{aristatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貓鬚草&T2_new_value=true&fr=y}}{貓鬚草}\index{貓鬚草} NA$^n$
  \end{itemize}
 \item[] \textit{Paraphlomis} 假糙蘇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraphlomis+formosana}{\textit{P. formosana} (Hayata) T.H.Hsieh \& T.C.Huang}  \index{Paraphlomis@\textit{Paraphlomis}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣假糙蘇&T2_new_value=true&fr=y}}{臺灣假糙蘇}\index{臺灣假糙蘇}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraphlomis+javanica}{\textit{P. javanica} (Blume) Prain}  \index{Paraphlomis@\textit{Paraphlomis}!javanica@\textit{javanica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假糙蘇&T2_new_value=true&fr=y}}{假糙蘇}\index{假糙蘇} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraphlomis+tomentoso-capitata}{\textit{P. tomentoso-capitata} Yamam.}  \index{Paraphlomis@\textit{Paraphlomis}!tomentoso-capitata@\textit{tomentoso-capitata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絨萼舞子草&T2_new_value=true&fr=y}}{絨萼舞子草}\index{絨萼舞子草}\# LC
  \end{itemize}
 \item[] \textit{Perilla} 紫蘇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Perilla+frutescens}{\textit{P. frutescens} (L.) Britt.}  \index{Perilla@\textit{Perilla}!frutescens@\textit{frutescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫蘇&T2_new_value=true&fr=y}}{紫蘇}\index{紫蘇} NA$^n$
  \end{itemize}
 \item[] \textit{Platostoma} 仙草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platostoma+hispidum}{\textit{P. hispidum} (L.) A.J.Paton}  \index{Platostoma@\textit{Platostoma}!hispidum@\textbf{\textit{hispidum}}}  \index{Acrocephalus@\textit{Acrocephalus}!indicus@\textit{indicus}{\\\noindent(= \textit{Platostoma hispidum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=頂頭花&T2_new_value=true&fr=y}}{頂頭花}\index{頂頭花@{\Song{頂頭花}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platostoma+palustre}{\textit{P. palustre} (Blume) A.J.Paton}  \index{Platostoma@\textit{Platostoma}!palustre@\textit{palustre}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=仙草&T2_new_value=true&fr=y}}{仙草}\index{仙草} LC
  \end{itemize}
 \item[] \textit{Pogostemon} 刺蕊草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pogostemon+auricularia}{\textit{P. auricularia} (L.) Hassk.}  \index{Pogostemon@\textit{Pogostemon}!auricularia@\textit{auricularia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=耳葉刺蕊草&T2_new_value=true&fr=y}}{耳葉刺蕊草}\index{耳葉刺蕊草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pogostemon+formosanus}{\textit{P. formosanus} Oliv.}  \index{Pogostemon@\textit{Pogostemon}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣刺蕊草&T2_new_value=true&fr=y}}{臺灣刺蕊草}\index{臺灣刺蕊草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pogostemon+stellatus}{\textit{P. stellatus} (Lour.) Kuntze}  \index{Pogostemon@\textit{Pogostemon}!stellatus@\textbf{\textit{stellatus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水虎尾&T2_new_value=true&fr=y}}{水虎尾}\index{水虎尾@{\Song{水虎尾}}} EN
  \end{itemize}
 \item[] \textit{Premna} 魚臭木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Premna+hengchunensis}{\textit{P. hengchunensis} S.Y.Lu \& Yuen P.Yang}  \index{Premna@\textit{Premna}!hengchunensis@\textit{hengchunensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春臭黃荊&T2_new_value=true&fr=y}}{恆春臭黃荊}\index{恆春臭黃荊}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Premna+microphylla}{\textit{P. microphylla} Turcz.}  \index{Premna@\textit{Premna}!microphylla@\textit{microphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭黃荊&T2_new_value=true&fr=y}}{臭黃荊}\index{臭黃荊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Premna+octonervia}{\textit{P. octonervia} Merr. \& F.P.Metcalf}  \index{Premna@\textit{Premna}!octonervia@\textit{octonervia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=八脈臭黃荊&T2_new_value=true&fr=y}}{八脈臭黃荊}\index{八脈臭黃荊} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Premna+odorata}{\textit{P. odorata} Blanco}  \index{Premna@\textit{Premna}!odorata@\textit{odorata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛魚臭木&T2_new_value=true&fr=y}}{毛魚臭木}\index{毛魚臭木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Premna+serratifolia}{\textit{P. serratifolia} L.}  \index{Premna@\textit{Premna}!serratifolia@\textit{serratifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭娘子&T2_new_value=true&fr=y}}{臭娘子}\index{臭娘子} LC
  \end{itemize}
 \item[] \textit{Prunella} 夏枯草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunella+vulgaris+subsp.+asiatica}{\textit{P. vulgaris} L. subsp. \textit{asiatica} (Nakai) H.Hara}  \index{Prunella@\textit{Prunella}!vulgaris@\textit{vulgaris}!subsp. asiatica@subsp. \textit{asiatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=夏枯草&T2_new_value=true&fr=y}}{夏枯草}\index{夏枯草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunella+vulgaris+subsp.+asiatica+var.+nanhutashanensis}{\textit{P. vulgaris} L. subsp. \textit{asiatica} (Nakai) H.Hara var. \textit{nanhutashanensis} S.S.Ying}  \index{Prunella@\textit{Prunella}!vulgaris@\textit{vulgaris}!subsp. asiatica var. nanhutashanensis@\textbf{subsp. \textit{asiatica} var. \textit{nanhutashanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山夏枯草&T2_new_value=true&fr=y}}{高山夏枯草}\index{高山夏枯草@{\Song{高山夏枯草}}}\# VU
  \end{itemize}
 \item[] \textit{Rubiteucris} 野藿香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubiteucris+palmata}{\textit{R. palmata} (Benth. ex Hook.f.) Kudo}  \index{Rubiteucris@\textit{Rubiteucris}!palmata@\textit{palmata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉野藿香&T2_new_value=true&fr=y}}{掌葉野藿香}\index{掌葉野藿香} LC
  \end{itemize}
 \item[] \textit{Salvia} 鼠尾草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+arisanensis}{\textit{S. arisanensis} Hayata}  \index{Salvia@\textit{Salvia}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山紫花鼠尾草&T2_new_value=true&fr=y}}{阿里山紫花鼠尾草}\index{阿里山紫花鼠尾草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+coccinea}{\textit{S. coccinea} Juss. ex Murray}  \index{Salvia@\textit{Salvia}!coccinea@\textit{coccinea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花鼠尾草&T2_new_value=true&fr=y}}{紅花鼠尾草}\index{紅花鼠尾草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+formosana}{\textit{S. formosana} (Murata) T.Yamaz.}  \index{Salvia@\textit{Salvia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣紫花鼠尾草&T2_new_value=true&fr=y}}{臺灣紫花鼠尾草}\index{臺灣紫花鼠尾草}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+formosana+var.+matsudae}{\textit{S. formosana} (Murata) T.Yamaz. var. \textit{matsudae} (Kudo) T.C.Huang \& J.T.Wu}  \index{Salvia@\textit{Salvia}!formosana@\textit{formosana}!var. matsudae@var. \textit{matsudae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蕨葉紫花鼠尾草&T2_new_value=true&fr=y}}{蕨葉紫花鼠尾草}\index{蕨葉紫花鼠尾草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+hayatana}{\textit{S. hayatana} Makino ex Hayata}  \index{Salvia@\textit{Salvia}!hayatana@\textbf{\textit{hayatana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏鼠尾草&T2_new_value=true&fr=y}}{早田氏鼠尾草}\index{早田氏鼠尾草@{\Song{早田氏鼠尾草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+japonica}{\textit{S. japonica} Thunb.}  \index{Salvia@\textit{Salvia}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本紫花鼠尾草&T2_new_value=true&fr=y}}{日本紫花鼠尾草}\index{日本紫花鼠尾草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+keitaoensis}{\textit{S. keitaoensis} Hayata}  \index{Salvia@\textit{Salvia}!keitaoensis@\textit{keitaoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=隱葯鼠尾草&T2_new_value=true&fr=y}}{隱葯鼠尾草}\index{隱葯鼠尾草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+lyrata}{\textit{S. lyrata} L.}  \index{Salvia@\textit{Salvia}!lyrata@\textit{lyrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琴葉鼠尾草&T2_new_value=true&fr=y}}{琴葉鼠尾草}\index{琴葉鼠尾草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+nipponica+var.+formosana}{\textit{S. nipponica} Miq. var. \textit{formosana} (Hayata) Kudo}  \index{Salvia@\textit{Salvia}!nipponica@\textit{nipponica}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花鼠尾草&T2_new_value=true&fr=y}}{黃花鼠尾草}\index{黃花鼠尾草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+occidentalis}{\textit{S. occidentalis} Sw.}  \index{Salvia@\textit{Salvia}!occidentalis@\textit{occidentalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腺萼鼠尾草&T2_new_value=true&fr=y}}{腺萼鼠尾草}\index{腺萼鼠尾草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+plebeia}{\textit{S. plebeia} R.Br.}  \index{Salvia@\textit{Salvia}!plebeia@\textit{plebeia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=節毛鼠尾草&T2_new_value=true&fr=y}}{節毛鼠尾草}\index{節毛鼠尾草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+scapiformis}{\textit{S. scapiformis} Hance}  \index{Salvia@\textit{Salvia}!scapiformis@\textit{scapiformis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=卵葉鼠尾草&T2_new_value=true&fr=y}}{卵葉鼠尾草}\index{卵葉鼠尾草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salvia+tashiroi}{\textit{S. tashiroi} Hayata}  \index{Salvia@\textit{Salvia}!tashiroi@\textbf{\textit{tashiroi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田代氏鼠尾草&T2_new_value=true&fr=y}}{田代氏鼠尾草}\index{田代氏鼠尾草@{\Song{田代氏鼠尾草}}}\# EN
  \end{itemize}
 \item[] \textit{Scutellaria} 黃芩屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+austrotaiwanensis}{\textit{S. austrotaiwanensis} T.H.Hsieh \& T.C.Huang}  \index{Scutellaria@\textit{Scutellaria}!austrotaiwanensis@\textbf{\textit{austrotaiwanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南臺灣黃芩&T2_new_value=true&fr=y}}{南臺灣黃芩}\index{南臺灣黃芩@{\Song{南臺灣黃芩}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+barbata}{\textit{S. barbata} D.Don}  \index{Scutellaria@\textit{Scutellaria}!barbata@\textit{barbata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=向天盞&T2_new_value=true&fr=y}}{向天盞}\index{向天盞} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+hsiehii}{\textit{S. hsiehii} T.H.Hsieh}  \index{Scutellaria@\textit{Scutellaria}!hsiehii@\textit{hsiehii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉黃芩&T2_new_value=true&fr=y}}{長葉黃芩}\index{長葉黃芩} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+indica}{\textit{S. indica} L.}  \index{Scutellaria@\textit{Scutellaria}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度黃芩&T2_new_value=true&fr=y}}{印度黃芩}\index{印度黃芩} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+playfairii}{\textit{S. playfairii} Kudo}  \index{Scutellaria@\textit{Scutellaria}!playfairii@\textbf{\textit{playfairii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=布烈氏黃芩&T2_new_value=true&fr=y}}{布烈氏黃芩}\index{布烈氏黃芩@{\Song{布烈氏黃芩}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+taipeiensis}{\textit{S. taipeiensis} T.C.Huang, A.Hsiao \& M.J.Wu}  \index{Scutellaria@\textit{Scutellaria}!taipeiensis@\textit{taipeiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺北黃芩&T2_new_value=true&fr=y}}{臺北黃芩}\index{臺北黃芩}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+taiwanensis}{\textit{S. taiwanensis} C.Y.Wu}  \index{Scutellaria@\textit{Scutellaria}!taiwanensis@\textbf{\textit{taiwanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃芩&T2_new_value=true&fr=y}}{臺灣黃芩}\index{臺灣黃芩@{\Song{臺灣黃芩}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scutellaria+tashiroi}{\textit{S. tashiroi} Hayata}  \index{Scutellaria@\textit{Scutellaria}!tashiroi@\textbf{\textit{tashiroi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田代氏黃芩&T2_new_value=true&fr=y}}{田代氏黃芩}\index{田代氏黃芩@{\Song{田代氏黃芩}}}\# VU
  \end{itemize}
 \item[] \textit{Sphenodesme} 楔翅藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sphenodesme+involucrata}{\textit{S. involucrata} (C.Presl) B.L.Rob.}  \index{Sphenodesme@\textit{Sphenodesme}!involucrata@\textit{involucrata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=爪楔翅藤&T2_new_value=true&fr=y}}{爪楔翅藤}\index{爪楔翅藤} DD
  \end{itemize}
 \item[] \textit{Stachys} 水蘇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stachys+arvensis}{\textit{S. arvensis} L.}  \index{Stachys@\textit{Stachys}!arvensis@\textit{arvensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田野水蘇&T2_new_value=true&fr=y}}{田野水蘇}\index{田野水蘇} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stachys+oblongifolia}{\textit{S. oblongifolia} Benth.}  \index{Stachys@\textit{Stachys}!oblongifolia@\textit{oblongifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉水蘇&T2_new_value=true&fr=y}}{長葉水蘇}\index{長葉水蘇} LC
  \end{itemize}
 \item[] \textit{Suzukia} 鈴木草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Suzukia+luchuensis}{\textit{S. luchuensis} Kudo}  \index{Suzukia@\textit{Suzukia}!luchuensis@\textbf{\textit{luchuensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球鈴木草&T2_new_value=true&fr=y}}{琉球鈴木草}\index{琉球鈴木草@{\Song{琉球鈴木草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Suzukia+shikikunensis}{\textit{S. shikikunensis} Kudo}  \index{Suzukia@\textit{Suzukia}!shikikunensis@\textit{shikikunensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈴木草&T2_new_value=true&fr=y}}{鈴木草}\index{鈴木草}\# LC
  \end{itemize}
 \item[] \textit{Teucrium} 香科科屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Teucrium+bidentatum}{\textit{T. bidentatum} Hemsl.}  \index{Teucrium@\textit{Teucrium}!bidentatum@\textit{bidentatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二齒香科科&T2_new_value=true&fr=y}}{二齒香科科}\index{二齒香科科} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Teucrium+taiwanianum}{\textit{T. taiwanianum} T.H.Hsieh \& T.C.Huang}  \index{Teucrium@\textit{Teucrium}!taiwanianum@\textbf{\textit{taiwanianum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣香科科&T2_new_value=true&fr=y}}{臺灣香科科}\index{臺灣香科科@{\Song{臺灣香科科}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Teucrium+viscidum}{\textit{T. viscidum} Blume}  \index{Teucrium@\textit{Teucrium}!viscidum@\textit{viscidum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=血見愁&T2_new_value=true&fr=y}}{血見愁}\index{血見愁} LC
  \end{itemize}
 \item[] \textit{Vitex} 牡荊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitex+negundo}{\textit{V. negundo} L.}  \index{Vitex@\textit{Vitex}!negundo@\textit{negundo}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃荊&T2_new_value=true&fr=y}}{黃荊}\index{黃荊} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitex+quinata}{\textit{V. quinata} (Lour.) F.N.Williams}  \index{Vitex@\textit{Vitex}!quinata@\textit{quinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山埔姜&T2_new_value=true&fr=y}}{山埔姜}\index{山埔姜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitex+rotundifolia}{\textit{V. rotundifolia} L.f.}  \index{Vitex@\textit{Vitex}!rotundifolia@\textit{rotundifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海埔姜&T2_new_value=true&fr=y}}{海埔姜}\index{海埔姜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitex+trifolia}{\textit{V. trifolia} L.}  \index{Vitex@\textit{Vitex}!trifolia@\textbf{\textit{trifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葉埔姜&T2_new_value=true&fr=y}}{三葉埔姜}\index{三葉埔姜@{\Song{三葉埔姜}}} VU
  \end{itemize}
  \end{itemize}
