
  \begin{itemize}
 \item[] \textit{Beilschmiedia} 瓊楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Beilschmiedia+erythrophloia}{\textit{B. erythrophloia} Hayata}  \index{Beilschmiedia@\textit{Beilschmiedia}!erythrophloia@\textit{erythrophloia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓊楠&T2_new_value=true&fr=y}}{瓊楠}\index{瓊楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Beilschmiedia+tsangii}{\textit{B. tsangii} Merr.}  \index{Beilschmiedia@\textit{Beilschmiedia}!tsangii@\textit{tsangii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華河瓊楠&T2_new_value=true&fr=y}}{華河瓊楠}\index{華河瓊楠} LC
  \end{itemize}
 \item[] \textit{Cassytha} 無根草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cassytha+filiformis}{\textit{C. filiformis} L.}  \index{Cassytha@\textit{Cassytha}!filiformis@\textit{filiformis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無根草&T2_new_value=true&fr=y}}{無根草}\index{無根草} LC
  \end{itemize}
 \item[] \textit{Cinnamomum} 樟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+austrosinense}{\textit{C. austrosinense} H.T.Chang}  \index{Cinnamomum@\textit{Cinnamomum}!austrosinense@\textbf{\textit{austrosinense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牡丹葉桂皮&T2_new_value=true&fr=y}}{牡丹葉桂皮}\index{牡丹葉桂皮@{\Song{牡丹葉桂皮}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+brevipedunculatum}{\textit{C. brevipedunculatum} C.E.Chang}  \index{Cinnamomum@\textit{Cinnamomum}!brevipedunculatum@\textbf{\textit{brevipedunculatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉樟&T2_new_value=true&fr=y}}{小葉樟}\index{小葉樟@{\Song{小葉樟}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+burmannii}{\textit{C. burmannii} (Nees) Blume}  \index{Cinnamomum@\textit{Cinnamomum}!burmannii@\textit{burmannii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=陰香&T2_new_value=true&fr=y}}{陰香}\index{陰香} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+camphora+var.+camphora}{\textit{C. camphora} (L.) J.Presl. var. \textit{camphora}}  \index{Cinnamomum@\textit{Cinnamomum}!camphora@\textit{camphora}!var. camphora@var. \textit{camphora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樟樹&T2_new_value=true&fr=y}}{樟樹}\index{樟樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+camphora+var.+nominale}{\textit{C. camphora} (L.) J.Presl. var. \textit{nominale} Hayata ex Matsum. \& Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!camphora@\textit{camphora}!var. nominale@var. \textit{nominale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=栳樟&T2_new_value=true&fr=y}}{栳樟}\index{栳樟}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+insulari-montanum}{\textit{C. insulari-montanum} Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!insulari-montanum@\textit{insulari-montanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣肉桂&T2_new_value=true&fr=y}}{臺灣肉桂}\index{臺灣肉桂}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+kanehirae}{\textit{C. kanehirae} Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!kanehirae@\textbf{\textit{kanehirae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牛樟&T2_new_value=true&fr=y}}{牛樟}\index{牛樟@{\Song{牛樟}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+kotoense}{\textit{C. kotoense} Kaneh. \& Sasaki}  \index{Cinnamomum@\textit{Cinnamomum}!kotoense@\textbf{\textit{kotoense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼肉桂&T2_new_value=true&fr=y}}{蘭嶼肉桂}\index{蘭嶼肉桂@{\Song{蘭嶼肉桂}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+macrostemon}{\textit{C. macrostemon} Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!macrostemon@\textit{macrostemon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=胡氏肉桂&T2_new_value=true&fr=y}}{胡氏肉桂}\index{胡氏肉桂}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+micranthum}{\textit{C. micranthum} (Hayata) Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!micranthum@\textit{micranthum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冇樟&T2_new_value=true&fr=y}}{冇樟}\index{冇樟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+osmophloeum}{\textit{C. osmophloeum} Kaneh.}  \index{Cinnamomum@\textit{Cinnamomum}!osmophloeum@\textit{osmophloeum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=土肉桂&T2_new_value=true&fr=y}}{土肉桂}\index{土肉桂}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+reticulatum}{\textit{C. reticulatum} Hayata}  \index{Cinnamomum@\textit{Cinnamomum}!reticulatum@\textit{reticulatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=土樟&T2_new_value=true&fr=y}}{土樟}\index{土樟}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+subavenium}{\textit{C. subavenium} Miq.}  \index{Cinnamomum@\textit{Cinnamomum}!subavenium@\textit{subavenium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香桂&T2_new_value=true&fr=y}}{香桂}\index{香桂} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cinnamomum+tenuifolium}{\textit{C. tenuifolium} (Makino) Sugim.}  \index{Cinnamomum@\textit{Cinnamomum}!tenuifolium@\textit{tenuifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天竺桂&T2_new_value=true&fr=y}}{天竺桂}\index{天竺桂} NT
  \end{itemize}
 \item[] \textit{Cryptocarya} 厚殼桂屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptocarya+chinensis}{\textit{C. chinensis} (Hance) Hemsl.}  \index{Cryptocarya@\textit{Cryptocarya}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚殼桂&T2_new_value=true&fr=y}}{厚殼桂}\index{厚殼桂} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptocarya+concinna}{\textit{C. concinna} Hance}  \index{Cryptocarya@\textit{Cryptocarya}!concinna@\textit{concinna}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=土楠&T2_new_value=true&fr=y}}{土楠}\index{土楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptocarya+elliptifolia}{\textit{C. elliptifolia} Merr.}  \index{Cryptocarya@\textit{Cryptocarya}!elliptifolia@\textbf{\textit{elliptifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲律賓厚殼桂&T2_new_value=true&fr=y}}{菲律賓厚殼桂}\index{菲律賓厚殼桂@{\Song{菲律賓厚殼桂}}} CR
  \end{itemize}
 \item[] \textit{Dehaasia} 腰果楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dehaasia+incrassata}{\textit{D. incrassata} (Jack.) Kosterm.}  \index{Dehaasia@\textit{Dehaasia}!incrassata@\textbf{\textit{incrassata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=腰果楠&T2_new_value=true&fr=y}}{腰果楠}\index{腰果楠@{\Song{腰果楠}}} CR
  \end{itemize}
 \item[] \textit{Endiandra} 三蕊楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Endiandra+coriacea}{\textit{E. coriacea} Merr.}  \index{Endiandra@\textit{Endiandra}!coriacea@\textbf{\textit{coriacea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三蕊楠&T2_new_value=true&fr=y}}{三蕊楠}\index{三蕊楠@{\Song{三蕊楠}}} CR
  \end{itemize}
 \item[] \textit{Lindera} 釣樟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+aggregata}{\textit{L. aggregata} (Sims) Kosterm.}  \index{Lindera@\textit{Lindera}!aggregata@\textit{aggregata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天臺烏藥&T2_new_value=true&fr=y}}{天臺烏藥}\index{天臺烏藥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+aggregata+ f. +playfairii}{\textit{L. aggregata} (Sims) Kosterm.  f.  \textit{playfairii} (Hemsl.) J.C.Liao}  \index{Lindera@\textit{Lindera}!aggregata@\textit{aggregata}!f. playfairii@f. \textit{playfairii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉烏藥&T2_new_value=true&fr=y}}{小葉烏藥}\index{小葉烏藥} NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+akoensis}{\textit{L. akoensis} Hayata}  \index{Lindera@\textit{Lindera}!akoensis@\textit{akoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=內苳子&T2_new_value=true&fr=y}}{內苳子}\index{內苳子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+communis}{\textit{L. communis} Hemsl.}  \index{Lindera@\textit{Lindera}!communis@\textit{communis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香葉樹&T2_new_value=true&fr=y}}{香葉樹}\index{香葉樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+erythrocarpa}{\textit{L. erythrocarpa} Makino}  \index{Lindera@\textit{Lindera}!erythrocarpa@\textit{erythrocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐵釘樹&T2_new_value=true&fr=y}}{鐵釘樹}\index{鐵釘樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+glauca}{\textit{L. glauca} (Siebold \& Zucc.) Blume}  \index{Lindera@\textit{Lindera}!glauca@\textit{glauca}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白葉釣樟&T2_new_value=true&fr=y}}{白葉釣樟}\index{白葉釣樟} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+megaphylla}{\textit{L. megaphylla} Hemsl.}  \index{Lindera@\textit{Lindera}!megaphylla@\textit{megaphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大香葉樹&T2_new_value=true&fr=y}}{大香葉樹}\index{大香葉樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindera+thunbergii}{\textit{L. thunbergii} (Sieb. \& Zucc.) Makino}  \index{Lindera@\textit{Lindera}!thunbergii@\textit{thunbergii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=脈葉釣樟&T2_new_value=true&fr=y}}{脈葉釣樟}\index{脈葉釣樟} LC
  \end{itemize}
 \item[] \textit{Litsea} 木薑子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+acuminata}{\textit{L. acuminata} (Blume) Kurata}  \index{Litsea@\textit{Litsea}!acuminata@\textit{acuminata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉木薑子&T2_new_value=true&fr=y}}{長葉木薑子}\index{長葉木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+acutivena}{\textit{L. acutivena} Hayata}  \index{Litsea@\textit{Litsea}!acutivena@\textit{acutivena}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳脈木薑子&T2_new_value=true&fr=y}}{銳脈木薑子}\index{銳脈木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+akoensis+var.+akoensis}{\textit{L. akoensis} Hayata var. \textit{akoensis}}  \index{Litsea@\textit{Litsea}!akoensis@\textit{akoensis}!var. akoensis@var. \textit{akoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東木薑子&T2_new_value=true&fr=y}}{屏東木薑子}\index{屏東木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+akoensis+var.+chitouchiaoensis}{\textit{L. akoensis} Hayata var. \textit{chitouchiaoensis} J.C.Liao}  \index{Litsea@\textit{Litsea}!akoensis@\textit{akoensis}!var. chitouchiaoensis@var. \textit{chitouchiaoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=竹頭角木薑子&T2_new_value=true&fr=y}}{竹頭角木薑子}\index{竹頭角木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+akoensis+var.+sasakii}{\textit{L. akoensis} Hayata var. \textit{sasakii} (Kamik.) J.C.Liao}  \index{Litsea@\textit{Litsea}!akoensis@\textit{akoensis}!var. sasakii@var. \textit{sasakii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉木薑子&T2_new_value=true&fr=y}}{狹葉木薑子}\index{狹葉木薑子}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+coreana}{\textit{L. coreana} H.Lév.}  \index{Litsea@\textit{Litsea}!coreana@\textit{coreana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鹿皮斑木薑子&T2_new_value=true&fr=y}}{鹿皮斑木薑子}\index{鹿皮斑木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+cubeba}{\textit{L. cubeba} (Lour.) Per.}  \index{Litsea@\textit{Litsea}!cubeba@\textit{cubeba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山胡椒&T2_new_value=true&fr=y}}{山胡椒}\index{山胡椒} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+elongata+var.+mushaensis}{\textit{L. elongata} (Wall. ex Nees) Benth. \& Hook.f. var. \textit{mushaensis} (Hayata) J.C.Liao}  \index{Litsea@\textit{Litsea}!elongata@\textit{elongata}!var. mushaensis@var. \textit{mushaensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=霧社木薑子&T2_new_value=true&fr=y}}{霧社木薑子}\index{霧社木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+garciae}{\textit{L. garciae} Vidal}  \index{Litsea@\textit{Litsea}!garciae@\textbf{\textit{garciae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼木薑子&T2_new_value=true&fr=y}}{蘭嶼木薑子}\index{蘭嶼木薑子@{\Song{蘭嶼木薑子}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+hypophaea}{\textit{L. hypophaea} Hayata}  \index{Litsea@\textit{Litsea}!hypophaea@\textit{hypophaea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃肉樹&T2_new_value=true&fr=y}}{黃肉樹}\index{黃肉樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+lii+var.+lii}{\textit{L. lii} C.E.Chang var. \textit{lii}}  \index{Litsea@\textit{Litsea}!lii@\textit{lii}!var. lii@var. \textit{lii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=李氏木薑子&T2_new_value=true&fr=y}}{李氏木薑子}\index{李氏木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+lii+var.+nunkao-tahangensis}{\textit{L. lii} C.E.Chang var. \textit{nunkao-tahangensis} (J.C.Liao) J.C.Liao}  \index{Litsea@\textit{Litsea}!lii@\textit{lii}!var. nunkao-tahangensis@var. \textit{nunkao-tahangensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能漢木薑子&T2_new_value=true&fr=y}}{能漢木薑子}\index{能漢木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+linii}{\textit{L. linii} Chang}  \index{Litsea@\textit{Litsea}!linii@\textit{linii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=林氏木薑子&T2_new_value=true&fr=y}}{林氏木薑子}\index{林氏木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+morrisonensis}{\textit{L. morrisonensis} Hayata}  \index{Litsea@\textit{Litsea}!morrisonensis@\textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山木薑子&T2_new_value=true&fr=y}}{玉山木薑子}\index{玉山木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+perrottetii}{\textit{L. perrottetii} (Blume) Fern-Vill.}  \index{Litsea@\textit{Litsea}!perrottetii@\textit{perrottetii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=佩羅特木薑子&T2_new_value=true&fr=y}}{佩羅特木薑子}\index{佩羅特木薑子} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litsea+rotundifolia+var.+oblongifolia}{\textit{L. rotundifolia} Hemsl. var. \textit{oblongifolia} (Nees) Allen}  \index{Litsea@\textit{Litsea}!rotundifolia@\textit{rotundifolia}!var. oblongifolia@var. \textit{oblongifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=橢圓葉木薑子&T2_new_value=true&fr=y}}{橢圓葉木薑子}\index{橢圓葉木薑子} LC
  \end{itemize}
 \item[] \textit{Machilus} 楨楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+japonica+var.+japonica}{\textit{M. japonica} Siebold \& Zucc. var. \textit{japonica}}  \index{Machilus@\textit{Machilus}!japonica@\textit{japonica}!var. japonica@var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假長葉楠&T2_new_value=true&fr=y}}{假長葉楠}\index{假長葉楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+japonica+var.+kusanoi}{\textit{M. japonica} Siebold \& Zucc. var. \textit{kusanoi} (Hayata) J.C.Liao}  \index{Machilus@\textit{Machilus}!japonica@\textit{japonica}!var. kusanoi@var. \textit{kusanoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉楠&T2_new_value=true&fr=y}}{大葉楠}\index{大葉楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+konishii}{\textit{M. konishii} Hayata}  \index{Machilus@\textit{Machilus}!konishii@\textit{konishii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小西氏楠&T2_new_value=true&fr=y}}{小西氏楠}\index{小西氏楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+obovatifolia+var.+obovatifolia}{\textit{M. obovatifolia} (Hayata) Kaneh. \& Sasaki var. \textit{obovatifolia}}  \index{Machilus@\textit{Machilus}!obovatifolia@\textit{obovatifolia}!var. obovatifolia@var. \textit{obovatifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春楨楠&T2_new_value=true&fr=y}}{恆春楨楠}\index{恆春楨楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+obovatifolia+var.+taiwuensis}{\textit{M. obovatifolia} (Hayata) Kaneh. \& Sasaki var. \textit{taiwuensis} S.Y.Lu \& T.T.Chen}  \index{Machilus@\textit{Machilus}!obovatifolia@\textit{obovatifolia}!var. taiwuensis@var. \textit{taiwuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大武楨楠&T2_new_value=true&fr=y}}{大武楨楠}\index{大武楨楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+philippinensis}{\textit{M. philippinensis} Merr.}  \index{Machilus@\textit{Machilus}!philippinensis@\textit{philippinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲律賓楠&T2_new_value=true&fr=y}}{菲律賓楠}\index{菲律賓楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+thunbergii}{\textit{M. thunbergii} Siebold \& Zucc.}  \index{Machilus@\textit{Machilus}!thunbergii@\textit{thunbergii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豬腳楠&T2_new_value=true&fr=y}}{豬腳楠}\index{豬腳楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+zuihoensis+var.+mushaensis}{\textit{M. zuihoensis} Hayata var. \textit{mushaensis} (F.Y.Lu) Y.C.Liu}  \index{Machilus@\textit{Machilus}!zuihoensis@\textit{zuihoensis}!var. mushaensis@var. \textit{mushaensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=青葉楠&T2_new_value=true&fr=y}}{青葉楠}\index{青葉楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Machilus+zuihoensis+var.+zuihoensis}{\textit{M. zuihoensis} Hayata var. \textit{zuihoensis}}  \index{Machilus@\textit{Machilus}!zuihoensis@\textit{zuihoensis}!var. zuihoensis@var. \textit{zuihoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香楠&T2_new_value=true&fr=y}}{香楠}\index{香楠}\# LC
  \end{itemize}
 \item[] \textit{Neolitsea} 新木薑子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+aciculata+var.+aciculata}{\textit{N. aciculata} (Blume) Koidz. var. \textit{aciculata}}  \index{Neolitsea@\textit{Neolitsea}!aciculata@\textit{aciculata}!var. aciculata@var. \textit{aciculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銳葉新木薑子&T2_new_value=true&fr=y}}{銳葉新木薑子}\index{銳葉新木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+aciculata+var.+variabillima}{\textit{N. aciculata} (Blume) Koidz. var. \textit{variabillima} (Hayata) J.C.Liao}  \index{Neolitsea@\textit{Neolitsea}!aciculata@\textit{aciculata}!var. variabillima@var. \textit{variabillima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉新木薑子&T2_new_value=true&fr=y}}{變葉新木薑子}\index{變葉新木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+acuminatissima}{\textit{N. acuminatissima} (Hayata) Kaneh. \& Sasaki}  \index{Neolitsea@\textit{Neolitsea}!acuminatissima@\textit{acuminatissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山新木薑子&T2_new_value=true&fr=y}}{高山新木薑子}\index{高山新木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+buisanensis}{\textit{N. buisanensis} Yamam. \& Kamik.}  \index{Neolitsea@\textit{Neolitsea}!buisanensis@\textit{buisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=武威山新木薑子&T2_new_value=true&fr=y}}{武威山新木薑子}\index{武威山新木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+buisanensis+ f. +sutsuoensis}{\textit{N. buisanensis} Yamam. \& Kamik.  f.  \textit{sutsuoensis} J.C.Liao}  \index{Neolitsea@\textit{Neolitsea}!buisanensis@\textit{buisanensis}!f. sutsuoensis@f. \textit{sutsuoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石厝新木薑子&T2_new_value=true&fr=y}}{石厝新木薑子}\index{石厝新木薑子}\# NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+daibuensis}{\textit{N. daibuensis} Kamik.}  \index{Neolitsea@\textit{Neolitsea}!daibuensis@\textit{daibuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大武新木薑子&T2_new_value=true&fr=y}}{大武新木薑子}\index{大武新木薑子}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+hiiranensis}{\textit{N. hiiranensis} T.S.Liu \& J.C.Liao}  \index{Neolitsea@\textit{Neolitsea}!hiiranensis@\textbf{\textit{hiiranensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南仁山新木薑子&T2_new_value=true&fr=y}}{南仁山新木薑子}\index{南仁山新木薑子@{\Song{南仁山新木薑子}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+konishii}{\textit{N. konishii} (Hayata) Kaneh. \& Sasaki}  \index{Neolitsea@\textit{Neolitsea}!konishii@\textit{konishii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=五掌楠&T2_new_value=true&fr=y}}{五掌楠}\index{五掌楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+parvigemma}{\textit{N. parvigemma} (Hayata) Kaneh. \& Sasaki}  \index{Neolitsea@\textit{Neolitsea}!parvigemma@\textit{parvigemma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小芽新木薑子&T2_new_value=true&fr=y}}{小芽新木薑子}\index{小芽新木薑子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+sericea+var.+aurata}{\textit{N. sericea} (Blume) Koidz. var. \textit{aurata} (Hayata) Hatus.}  \index{Neolitsea@\textit{Neolitsea}!sericea@\textit{sericea}!var. aurata@\textbf{var. \textit{aurata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金新木薑子&T2_new_value=true&fr=y}}{金新木薑子}\index{金新木薑子@{\Song{金新木薑子}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+sericea+var.+sericea}{\textit{N. sericea} (Blume) Koidz. var. \textit{sericea}}  \index{Neolitsea@\textit{Neolitsea}!sericea@\textit{sericea}!var. sericea@var. \textit{sericea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白新木薑子&T2_new_value=true&fr=y}}{白新木薑子}\index{白新木薑子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neolitsea+villosa}{\textit{N. villosa} (Blume) Merr.}  \index{Neolitsea@\textit{Neolitsea}!villosa@\textbf{\textit{villosa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼新木薑子&T2_new_value=true&fr=y}}{蘭嶼新木薑子}\index{蘭嶼新木薑子@{\Song{蘭嶼新木薑子}}} CR
  \end{itemize}
 \item[] \textit{Phoebe} 雅楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phoebe+formosana}{\textit{P. formosana} (Hayata) Hayata}  \index{Phoebe@\textit{Phoebe}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣雅楠&T2_new_value=true&fr=y}}{臺灣雅楠}\index{臺灣雅楠} LC
  \end{itemize}
 \item[] \textit{Sassafras} 檫樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sassafras+randaiense}{\textit{S. randaiense} (Hayata) Rehder}  \index{Sassafras@\textit{Sassafras}!randaiense@\textit{randaiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣檫樹&T2_new_value=true&fr=y}}{臺灣檫樹}\index{臺灣檫樹}\# NT
  \end{itemize}
  \end{itemize}
