
  \begin{itemize}
 \item[] \textit{Lilium} 百合屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lilium+callosum}{\textit{L. callosum} Siebold \& Zucc.}  \index{Lilium@\textit{Lilium}!callosum@\textit{callosum}}  \index{Lilium@\textit{Lilium}!callosum@\textit{callosum}!var. flaviflorum@var. \textit{flaviflorum}{\\\noindent(=\textit{Lilium callosum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野小百合&T2_new_value=true&fr=y}}{野小百合}\index{野小百合} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lilium+formosanum}{\textit{L. formosanum} Wallace}  \index{Lilium@\textit{Lilium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣百合&T2_new_value=true&fr=y}}{臺灣百合}\index{臺灣百合}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lilium+longiflorum+var.+scabrum}{\textit{L. longiflorum} Thunb. var. \textit{scabrum} Masam.}  \index{Lilium@\textit{Lilium}!longiflorum@\textit{longiflorum}!var. scabrum@var. \textit{scabrum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗莖麝香百合&T2_new_value=true&fr=y}}{粗莖麝香百合}\index{粗莖麝香百合}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lilium+speciosum+var.+gloriosoides}{\textit{L. speciosum} Thunb. var. \textit{gloriosoides} Baker}  \index{Lilium@\textit{Lilium}!speciosum@\textit{speciosum}!var. gloriosoides@\textbf{var. \textit{gloriosoides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=艷紅鹿子百合&T2_new_value=true&fr=y}}{艷紅鹿子百合}\index{艷紅鹿子百合@{\Song{艷紅鹿子百合}}} CR
  \end{itemize}
 \item[] \textit{Tricyrtis} 油點草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+formosana+var.+formosana}{\textit{T. formosana} Baker var. \textit{formosana}}  \index{Tricyrtis@\textit{Tricyrtis}!formosana@\textit{formosana}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣油點草&T2_new_value=true&fr=y}}{臺灣油點草}\index{臺灣油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+formosana+var.+grandiflora}{\textit{T. formosana} Baker var. \textit{grandiflora} S.S.Ying}  \index{Tricyrtis@\textit{Tricyrtis}!formosana@\textit{formosana}!var. grandiflora@var. \textit{grandiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花油點草&T2_new_value=true&fr=y}}{大花油點草}\index{大花油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+formosana+var.+lasiocarpa}{\textit{T. formosana} Baker var. \textit{lasiocarpa} (Matsum.) Masam.}  \index{Tricyrtis@\textit{Tricyrtis}!formosana@\textit{formosana}!var. lasiocarpa@var. \textit{lasiocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果油點草&T2_new_value=true&fr=y}}{毛果油點草}\index{毛果油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+formosana+var.+ovatifolia}{\textit{T. formosana} Baker var. \textit{ovatifolia} (S.S.Ying) S.S.Ying}  \index{Tricyrtis@\textit{Tricyrtis}!formosana@\textit{formosana}!var. ovatifolia@var. \textit{ovatifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=卵葉油點草&T2_new_value=true&fr=y}}{卵葉油點草}\index{卵葉油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+formosana+var.+stolonifera}{\textit{T. formosana} Baker var. \textit{stolonifera} (Matsum.) Masam.}  \index{Tricyrtis@\textit{Tricyrtis}!formosana@\textit{formosana}!var. stolonifera@var. \textit{stolonifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山油點草&T2_new_value=true&fr=y}}{山油點草}\index{山油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+ravenii}{\textit{T. ravenii} C.I Peng \& C.L.Tiang}  \index{Tricyrtis@\textit{Tricyrtis}!ravenii@\textit{ravenii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山油點草&T2_new_value=true&fr=y}}{高山油點草}\index{高山油點草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricyrtis+suzukii}{\textit{T. suzukii} Masam.}  \index{Tricyrtis@\textit{Tricyrtis}!suzukii@\textbf{\textit{suzukii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈴木氏油點草&T2_new_value=true&fr=y}}{鈴木氏油點草}\index{鈴木氏油點草@{\Song{鈴木氏油點草}}}\# VU
  \end{itemize}
  \end{itemize}
