
  \begin{itemize}
 \item[] \textit{Bonnaya} 泥花草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bonnaya+antipoda}{\textit{B. antipoda} (L.) Druce}  \index{Bonnaya@\textit{Bonnaya}!antipoda@\textit{antipoda}}  \index{Lindernia@\textit{Lindernia}!antipoda@\textit{antipoda}{\\\noindent(= \textit{Bonnaya antipoda})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泥花草&T2_new_value=true&fr=y}}{泥花草}\index{泥花草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bonnaya+ciliata}{\textit{B. ciliata} (Colsm.) Spreng.}  \index{Bonnaya@\textit{Bonnaya}!ciliata@\textit{ciliata}}  \index{Lindernia@\textit{Lindernia}!ciliata@\textit{ciliata}{\\\noindent(= \textit{Bonnaya ciliata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水丁黃&T2_new_value=true&fr=y}}{水丁黃}\index{水丁黃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bonnaya+ruellioides}{\textit{B. ruellioides} (Colsm.) Spreng.}  \index{Bonnaya@\textit{Bonnaya}!ruellioides@\textit{ruellioides}}  \index{Lindernia@\textit{Lindernia}!ruellioides@\textit{ruellioides}{\\\noindent(= \textit{Bonnaya ruellioides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=旱田草&T2_new_value=true&fr=y}}{旱田草}\index{旱田草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bonnaya+tenuifolia}{\textit{B. tenuifolia} (Colsm.) Spreng.}  \index{Bonnaya@\textit{Bonnaya}!tenuifolia@\textbf{\textit{tenuifolia}}}  \index{Lindernia@\textit{Lindernia}!tenuifolia@\textit{tenuifolia}{\\\noindent(= \textit{Bonnaya tenuifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉見風紅&T2_new_value=true&fr=y}}{薄葉見風紅}\index{薄葉見風紅@{\Song{薄葉見風紅}}} VU
  \end{itemize}
 \item[] \textit{Legazpia} 三翅萼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Legazpia+polygonoides}{\textit{L. polygonoides} (Benth.) T.Yamaz.}  \index{Legazpia@\textit{Legazpia}!polygonoides@\textbf{\textit{polygonoides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三翅萼&T2_new_value=true&fr=y}}{三翅萼}\index{三翅萼@{\Song{三翅萼}}} VU
  \end{itemize}
 \item[] \textit{Lindernia} 母草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+dubia+var.+dubia}{\textit{L. dubia} (L.) Pennell var. \textit{dubia}}  \index{Lindernia@\textit{Lindernia}!dubia@\textit{dubia}!var. dubia@var. \textit{dubia}}  \index{Lindernia@\textit{Lindernia}!dubia@\textit{dubia}{\\\noindent(= \textit{Lindernia dubia} var. \textit{dubia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=美洲母草&T2_new_value=true&fr=y}}{美洲母草}\index{美洲母草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+dubia+var.+anagallidea}{\textit{L. dubia} L. var. \textit{anagallidea} (Michx.) Cooperr.}  \index{Lindernia@\textit{Lindernia}!dubia@\textit{dubia}!var. anagallidea@var. \textit{anagallidea}}  \index{Lindernia@\textit{Lindernia}!anagallidea@\textit{anagallidea}{\\\noindent(= \textit{Lindernia dubia} var. \textit{anagallidea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬櫻草&T2_new_value=true&fr=y}}{擬櫻草}\index{擬櫻草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+hyssopoides}{\textit{L. hyssopoides} (L.) Haines}  \index{Lindernia@\textit{Lindernia}!hyssopoides@\textit{hyssopoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尖果母草&T2_new_value=true&fr=y}}{尖果母草}\index{尖果母草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+mollis}{\textit{L. mollis} (Benth.) Wettst.}  \index{Lindernia@\textit{Lindernia}!mollis@\textit{mollis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=見風黃&T2_new_value=true&fr=y}}{見風黃}\index{見風黃} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+nummularifolia}{\textit{L. nummularifolia} (D.Don) Wettst.}  \index{Lindernia@\textit{Lindernia}!nummularifolia@\textit{nummularifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬葉母草&T2_new_value=true&fr=y}}{寬葉母草}\index{寬葉母草} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+procumbens}{\textit{L. procumbens} (Krock.) Borbas}  \index{Lindernia@\textit{Lindernia}!procumbens@\textit{procumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=陌上草&T2_new_value=true&fr=y}}{陌上草}\index{陌上草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+pusilla}{\textit{L. pusilla} (Willd.) Bold.}  \index{Lindernia@\textit{Lindernia}!pusilla@\textit{pusilla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=見風紅&T2_new_value=true&fr=y}}{見風紅}\index{見風紅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindernia+rotunndifolia}{\textit{L. rotunndifolia} (L.) Alston}  \index{Lindernia@\textit{Lindernia}!rotunndifolia@\textit{rotunndifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉母草&T2_new_value=true&fr=y}}{圓葉母草}\index{圓葉母草} NA
  \end{itemize}
 \item[] \textit{Micranthemum} 珍珠草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Micranthemum+micranthemoides}{\textit{M. micranthemoides} (Nutt.) Wettst.}  \index{Micranthemum@\textit{Micranthemum}!micranthemoides@\textit{micranthemoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小蕊珍珠草&T2_new_value=true&fr=y}}{小蕊珍珠草}\index{小蕊珍珠草} NA$^n$
  \end{itemize}
 \item[] \textit{Torenia} 倒地蜈蚣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+benthamiana}{\textit{T. benthamiana} Hance}  \index{Torenia@\textit{Torenia}!benthamiana@\textbf{\textit{benthamiana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛葉蝴蝶草&T2_new_value=true&fr=y}}{毛葉蝴蝶草}\index{毛葉蝴蝶草@{\Song{毛葉蝴蝶草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+concolor}{\textit{T. concolor} Lindl.}  \index{Torenia@\textit{Torenia}!concolor@\textit{concolor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=倒地蜈蚣&T2_new_value=true&fr=y}}{倒地蜈蚣}\index{倒地蜈蚣} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+crustacea}{\textit{T. crustacea} (L.) Cham. \& Schltdl.}  \index{Torenia@\textit{Torenia}!crustacea@\textit{crustacea}}  \index{Lindernia@\textit{Lindernia}!crustacea@\textit{crustacea}{\\\noindent(= \textit{Torenia crustacea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藍豬耳&T2_new_value=true&fr=y}}{藍豬耳}\index{藍豬耳} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+flava}{\textit{T. flava} Buch.-Ham. ex Benth.}  \index{Torenia@\textit{Torenia}!flava@\textit{flava}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=母丁香&T2_new_value=true&fr=y}}{母丁香}\index{母丁香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+fournieri}{\textit{T. fournieri} L.}  \index{Torenia@\textit{Torenia}!fournieri@\textit{fournieri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=夏菫&T2_new_value=true&fr=y}}{夏菫}\index{夏菫} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Torenia+violacea}{\textit{T. violacea} (Azaola ex Blanco) Pennell}  \index{Torenia@\textit{Torenia}!violacea@\textit{violacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫萼蝴蝶草&T2_new_value=true&fr=y}}{紫萼蝴蝶草}\index{紫萼蝴蝶草} NT
  \end{itemize}
 \item[] \textit{Vandellia} 見風紅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandellia+anagallis}{\textit{V. anagallis} (Burm.f.) T. Yamaz.}  \index{Vandellia@\textit{Vandellia}!anagallis@\textit{anagallis}}  \index{Lindernia@\textit{Lindernia}!anagallis@\textit{anagallis}{\\\noindent(= \textit{Vandellia anagallis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=定經草&T2_new_value=true&fr=y}}{定經草}\index{定經草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandellia+scutellariiformis}{\textit{V. scutellariiformis} (T. Yamaz.) T. Yamaz.}  \index{Vandellia@\textit{Vandellia}!scutellariiformis@\textbf{\textit{scutellariiformis}}}  \index{Lindernia@\textit{Lindernia}!scutellariiformis@\textit{scutellariiformis}{\\\noindent(= \textit{Vandellia scutellariiformis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺南見風紅&T2_new_value=true&fr=y}}{臺南見風紅}\index{臺南見風紅@{\Song{臺南見風紅}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vandellia+viscosa}{\textit{V. viscosa} (Hornem.) Merr.}  \index{Vandellia@\textit{Vandellia}!viscosa@\textbf{\textit{viscosa}}}  \index{Lindernia@\textit{Lindernia}!viscosa@\textit{viscosa}{\\\noindent(= \textit{Vandellia viscosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東見風紅&T2_new_value=true&fr=y}}{屏東見風紅}\index{屏東見風紅@{\Song{屏東見風紅}}} EN
  \end{itemize}
  \end{itemize}
