
  \begin{itemize}
 \item[] \textit{Lindsaea} 陵齒蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+chienii}{\textit{L. chienii} Ching}  \index{Lindsaea@\textit{Lindsaea}!chienii@\textit{chienii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錢氏鱗始蕨&T2_new_value=true&fr=y}}{錢氏鱗始蕨}\index{錢氏鱗始蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+cultrata}{\textit{L. cultrata} (Willd.) Sw.}  \index{Lindsaea@\textit{Lindsaea}!cultrata@\textbf{\textit{cultrata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈陵齒蕨&T2_new_value=true&fr=y}}{網脈陵齒蕨}\index{網脈陵齒蕨@{\Song{網脈陵齒蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+ensifolia}{\textit{L. ensifolia} Sw.}  \index{Lindsaea@\textit{Lindsaea}!ensifolia@\textit{ensifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=箭葉陵齒蕨&T2_new_value=true&fr=y}}{箭葉陵齒蕨}\index{箭葉陵齒蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+kawabatae}{\textit{L. kawabatae} Sa.Kurata}  \index{Lindsaea@\textit{Lindsaea}!kawabatae@\textbf{\textit{kawabatae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉陵齒蕨&T2_new_value=true&fr=y}}{細葉陵齒蕨}\index{細葉陵齒蕨@{\Song{細葉陵齒蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+lucida}{\textit{L. lucida} Blume}  \index{Lindsaea@\textit{Lindsaea}!lucida@\textbf{\textit{lucida}}}  \index{Lindsaea@\textit{Lindsaea}!securifolia@\textit{securifolia}!var. kusukusensis@var. \textit{kusukusensis}{\\\noindent(=\textit{Lindsaea lucida})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=方柄陵齒蕨&T2_new_value=true&fr=y}}{方柄陵齒蕨}\index{方柄陵齒蕨@{\Song{方柄陵齒蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+merrillii+var.+yaeyamensis}{\textit{L. merrillii} Copel. var. \textit{yaeyamensis} (Tagawa) W.C.Shieh}  \index{Lindsaea@\textit{Lindsaea}!merrillii@\textit{merrillii}!var. yaeyamensis@var. \textit{yaeyamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=攀緣陵齒蕨&T2_new_value=true&fr=y}}{攀緣陵齒蕨}\index{攀緣陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+obtusa}{\textit{L. obtusa} J.Sm.}  \index{Lindsaea@\textit{Lindsaea}!obtusa@\textit{obtusa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍齒陵齒蕨&T2_new_value=true&fr=y}}{鈍齒陵齒蕨}\index{鈍齒陵齒蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+orbiculata+var.+commixta}{\textit{L. orbiculata} (Lam.) Mett. ex Kuhn var. \textit{commixta} (Tagawa) W.C.Shieh}  \index{Lindsaea@\textit{Lindsaea}!orbiculata@\textit{orbiculata}!var. commixta@var. \textit{commixta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海島陵齒蕨&T2_new_value=true&fr=y}}{海島陵齒蕨}\index{海島陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+orbiculata+var.+deltoidea}{\textit{L. orbiculata} (Lam.) Mett. ex Kuhn var. \textit{deltoidea} Y.C.Wu}  \index{Lindsaea@\textit{Lindsaea}!orbiculata@\textit{orbiculata}!var. deltoidea@var. \textit{deltoidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三角葉陵齒蕨&T2_new_value=true&fr=y}}{三角葉陵齒蕨}\index{三角葉陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+orbiculata+var.+orbiculata}{\textit{L. orbiculata} (Lam.) Mett. ex Kuhn var. \textit{orbiculata}}  \index{Lindsaea@\textit{Lindsaea}!orbiculata@\textit{orbiculata}!var. orbiculata@var. \textit{orbiculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉陵齒蕨&T2_new_value=true&fr=y}}{圓葉陵齒蕨}\index{圓葉陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+orbiculata+var.+recedens}{\textit{L. orbiculata} (Lam.) Mett. ex Kuhn var. \textit{recedens} (Ching) W.C.Shieh}  \index{Lindsaea@\textit{Lindsaea}!orbiculata@\textit{orbiculata}!var. recedens@var. \textit{recedens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊片陵齒蕨&T2_new_value=true&fr=y}}{闊片陵齒蕨}\index{闊片陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lindsaea+×heterophylla}{\textit{L. ×heterophylla} Dryand.}  \index{Lindsaea@\textit{Lindsaea}!×heterophylla@\textit{×heterophylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=異葉陵齒蕨&T2_new_value=true&fr=y}}{異葉陵齒蕨}\index{異葉陵齒蕨} NA$^h$
  \end{itemize}
 \item[] \textit{Odontosoria} 烏蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontosoria+biflora}{\textit{O. biflora} (Kaulf.) C.Chr.}  \index{Odontosoria@\textit{Odontosoria}!biflora@\textit{biflora}}  \index{Sphenomeris@\textit{Sphenomeris}!biflora@\textit{biflora}{\\\noindent(= \textit{Odontosoria biflora})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊片烏蕨&T2_new_value=true&fr=y}}{闊片烏蕨}\index{闊片烏蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontosoria+chinensis}{\textit{O. chinensis} (L.) J.Sm.}  \index{Odontosoria@\textit{Odontosoria}!chinensis@\textit{chinensis}}  \index{Sphenomeris@\textit{Sphenomeris}!chusana@\textit{chusana}{\\\noindent(= \textit{Odontosoria chinensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏蕨&T2_new_value=true&fr=y}}{烏蕨}\index{烏蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontosoria+gracilis}{\textit{O. gracilis} (Tagawa) Ralf Knapp}  \index{Odontosoria@\textit{Odontosoria}!gracilis@\textit{gracilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小烏蕨&T2_new_value=true&fr=y}}{小烏蕨}\index{小烏蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontosoria+×intermedia}{\textit{O. ×intermedia} (S.J.Lin, M.Kato \& K.Iwats.) Nakaike}  \index{Odontosoria@\textit{Odontosoria}!×intermedia@\textit{×intermedia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中間烏蕨&T2_new_value=true&fr=y}}{中間烏蕨}\index{中間烏蕨} NA$^h$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontosoria+×yaeyamensis}{\textit{O. ×yaeyamensis} (S.J.Lin, M.Kato \& K.Iwats.) Ebihara}  \index{Odontosoria@\textit{Odontosoria}!×yaeyamensis@\textit{×yaeyamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=八重山烏蕨&T2_new_value=true&fr=y}}{八重山烏蕨}\index{八重山烏蕨} NA$^h$
  \end{itemize}
 \item[] \textit{Osmolindsaea} 香鱗始蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osmolindsaea+japonica}{\textit{O. japonica} (Baker) Lehtonen \& Christenh.}  \index{Osmolindsaea@\textit{Osmolindsaea}!japonica@\textit{japonica}}  \index{Lindsaea@\textit{Lindsaea}!japonica@\textit{japonica}{\\\noindent(= \textit{Osmolindsaea japonica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本陵齒蕨&T2_new_value=true&fr=y}}{日本陵齒蕨}\index{日本陵齒蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osmolindsaea+odorata}{\textit{O. odorata} (Roxb.) Lehtonen \& Christenh.}  \index{Osmolindsaea@\textit{Osmolindsaea}!odorata@\textit{odorata}}  \index{Lindsaea@\textit{Lindsaea}!odorata@\textit{odorata}{\\\noindent(= \textit{Osmolindsaea odorata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=陵齒蕨&T2_new_value=true&fr=y}}{陵齒蕨}\index{陵齒蕨} LC
  \end{itemize}
 \item[] \textit{Tapeinidium} 達邊蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tapeinidium+pinnatum+var.+biserratum}{\textit{T. pinnatum} (Cav.) C.Chr. var. \textit{biserratum} (Blume) W.C.Shieh}  \index{Tapeinidium@\textit{Tapeinidium}!pinnatum@\textit{pinnatum}!var. biserratum@\textbf{var. \textit{biserratum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二羽達邊蕨&T2_new_value=true&fr=y}}{二羽達邊蕨}\index{二羽達邊蕨@{\Song{二羽達邊蕨}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tapeinidium+pinnatum+var.+pinnatum}{\textit{T. pinnatum} (Cav.) C.Chr. var. \textit{pinnatum}}  \index{Tapeinidium@\textit{Tapeinidium}!pinnatum@\textit{pinnatum}!var. pinnatum@var. \textit{pinnatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=達邊蕨&T2_new_value=true&fr=y}}{達邊蕨}\index{達邊蕨} LC
  \end{itemize}
  \end{itemize}
