
  \begin{itemize}
 \item[] \textit{Loranthus} 桑寄生屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Loranthus+delavayi}{\textit{L. delavayi} Tiegh.}  \index{Loranthus@\textit{Loranthus}!delavayi@\textit{delavayi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=椆樹桑寄生&T2_new_value=true&fr=y}}{椆樹桑寄生}\index{椆樹桑寄生} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Loranthus+kaoi}{\textit{L. kaoi} (J.M.Chao) H.S.Kiu}  \index{Loranthus@\textit{Loranthus}!kaoi@\textit{kaoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高氏桑寄生&T2_new_value=true&fr=y}}{高氏桑寄生}\index{高氏桑寄生}\# NT
  \end{itemize}
 \item[] \textit{Taxillus} 松寄生屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+limprichtii+var.+limprichtii}{\textit{T. limprichtii} (Grüning) H.S.Kiu var. \textit{limprichtii}}  \index{Taxillus@\textit{Taxillus}!limprichtii@\textit{limprichtii}!var. limprichtii@\textbf{var. \textit{limprichtii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木蘭桑寄生&T2_new_value=true&fr=y}}{木蘭桑寄生}\index{木蘭桑寄生@{\Song{木蘭桑寄生}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+limprichtii+var.+longiflorus}{\textit{T. limprichtii} (Grüning) H.S.Kiu var. \textit{longiflorus} (Lecomte) H.S.Kiu}  \index{Taxillus@\textit{Taxillus}!limprichtii@\textit{limprichtii}!var. longiflorus@\textbf{var. \textit{longiflorus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亮葉木蘭寄生&T2_new_value=true&fr=y}}{亮葉木蘭寄生}\index{亮葉木蘭寄生@{\Song{亮葉木蘭寄生}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+liquidambaricolus}{\textit{T. liquidambaricolus} (Hayata) Hosok.}  \index{Taxillus@\textit{Taxillus}!liquidambaricolus@\textit{liquidambaricolus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉桑寄生&T2_new_value=true&fr=y}}{大葉桑寄生}\index{大葉桑寄生}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+lonicerifolius+var.+longifolius}{\textit{T. lonicerifolius} (Hayata) S.T.Chiu var. \textit{longifolius} S.T.Chiu}  \index{Taxillus@\textit{Taxillus}!lonicerifolius@\textit{lonicerifolius}!var. longifolius@var. \textit{longifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花忍冬葉桑寄生&T2_new_value=true&fr=y}}{大花忍冬葉桑寄生}\index{大花忍冬葉桑寄生}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+lonicerifolius+var.+lonicerifolius}{\textit{T. lonicerifolius} (Hayata) S.T.Chiu var. \textit{lonicerifolius}}  \index{Taxillus@\textit{Taxillus}!lonicerifolius@\textit{lonicerifolius}!var. lonicerifolius@var. \textit{lonicerifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=忍冬葉桑寄生&T2_new_value=true&fr=y}}{忍冬葉桑寄生}\index{忍冬葉桑寄生}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+matsudae}{\textit{T. matsudae} (Hayata) Danser}  \index{Taxillus@\textit{Taxillus}!matsudae@\textit{matsudae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=松寄生&T2_new_value=true&fr=y}}{松寄生}\index{松寄生}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+parasiticus}{\textit{T. parasiticus} (L.) S.T.Chiu}  \index{Taxillus@\textit{Taxillus}!parasiticus@\textit{parasiticus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桑寄生&T2_new_value=true&fr=y}}{桑寄生}\index{桑寄生} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+pseudochinensis}{\textit{T. pseudochinensis} (Yamam.) Danser}  \index{Taxillus@\textit{Taxillus}!pseudochinensis@\textbf{\textit{pseudochinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春桑寄生&T2_new_value=true&fr=y}}{恆春桑寄生}\index{恆春桑寄生@{\Song{恆春桑寄生}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+rhododendricolius}{\textit{T. rhododendricolius} (Hayata) S.T.Chiu}  \index{Taxillus@\textit{Taxillus}!rhododendricolius@\textit{rhododendricolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杜鵑桑寄生&T2_new_value=true&fr=y}}{杜鵑桑寄生}\index{杜鵑桑寄生}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+ritozanensis}{\textit{T. ritozanensis} (Hayata) S.T.Chiu}  \index{Taxillus@\textit{Taxillus}!ritozanensis@\textit{ritozanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=李棟山桑寄生&T2_new_value=true&fr=y}}{李棟山桑寄生}\index{李棟山桑寄生}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+theifer}{\textit{T. theifer} (Hayata) H.S.Kiu}  \index{Taxillus@\textit{Taxillus}!theifer@\textit{theifer}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=埔姜桑寄生&T2_new_value=true&fr=y}}{埔姜桑寄生}\index{埔姜桑寄生}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taxillus+tsaii}{\textit{T. tsaii} S.T.Chiu}  \index{Taxillus@\textit{Taxillus}!tsaii@\textit{tsaii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓮華池桑寄生&T2_new_value=true&fr=y}}{蓮華池桑寄生}\index{蓮華池桑寄生} LC
  \end{itemize}
  \end{itemize}
