
  \begin{itemize}
 \item[] \textit{Huperzia} 石杉屬
                                
  \begin{itemize}
        \item[] \textit{H. emeiensis} (Ching \& H.S.Kung) Ching \& H.S.Kung \index{Huperzia@\textit{Huperzia}!emeiensis@\textit{emeiensis}} 峨眉石杉 \index{峨眉石杉}  DD
        \item[] \textit{H. herteriana} (Kummerle) T.Sen \& U.Sen \index{Huperzia@\textit{Huperzia}!herteriana@\textit{herteriana}} 錫金石杉 \index{錫金石杉}  DD
        \item[] \textit{H. liangshanica} (H.S.Kung) Ching \& H.S.Kung \index{Huperzia@\textit{Huperzia}!liangshanica@\textit{liangshanica}} 凉山石杉 \index{凉山石杉}  DD
        \item[] \textit{H. quasipolytrichoides} (Hayata) Ching \index{Huperzia@\textit{Huperzia}!quasipolytrichoides@\textit{quasipolytrichoides}} 反捲葉石松 \index{反捲葉石松}  LC
        \item[] \textit{H. selago} (L.) Bernh. ex Schrank \& Mart. \index{Huperzia@\textit{Huperzia}!selago@\textit{selago}} 小杉葉石松 \index{小杉葉石松}  VU
        \item[] \textit{H. serrata} (Thunb.) Trevis. \index{Huperzia@\textit{Huperzia}!serrata@\textit{serrata}} 千層塔 \index{千層塔}  DD
        \item[] \textit{H. serrata} var. \textit{longipetiolata} (Spring) H.M.Chang \index{Huperzia@\textit{Huperzia}!serrata@\textit{serrata}!var. longipetiolata@var. \textit{longipetiolata}}
                                        長柄千層塔 \index{長柄千層塔}  DD
        \item[] \textit{H. serrata} var. \textit{myriophyllifolia} (Spring) H.M.Chang \index{Huperzia@\textit{Huperzia}!serrata@\textit{serrata}!var. myriophyllifolia@var. \textit{myriophyllifolia}}
                                        阿里山千層塔 \index{阿里山千層塔}  DD
        \item[] \textit{H. somae} (Hayata) Ching \index{Huperzia@\textit{Huperzia}!somae@\textit{somae}} 相馬氏石松 \index{相馬氏石松}  LC
  \end{itemize}
 \item[] \textit{Lycopodiastrum} 藤石松屬
                                
  \begin{itemize}
        \item[] \textit{L. casuarinoides} (Spring) Holub \index{Lycopodiastrum@\textit{Lycopodiastrum}!casuarinoides@\textit{casuarinoides}} 木賊葉石松 \index{木賊葉石松}  LC
  \end{itemize}
 \item[] \textit{Lycopodiella} 小石松屬
                                
  \begin{itemize}
        \item[] \textit{L. cernua} (L.) Pic.Serm. \index{Lycopodiella@\textit{Lycopodiella}!cernua@\textit{cernua}} 過山龍 \index{過山龍}  LC
  \end{itemize}
 \item[] \textit{Lycopodium} 石松屬
                                
  \begin{itemize}
        \item[] \textit{L. annotinum} L. \index{Lycopodium@\textit{Lycopodium}!annotinum@\textit{annotinum}} 杉葉蔓石松 \index{杉葉蔓石松}  VU
        \item[] \textit{L. clavatum} L. \index{Lycopodium@\textit{Lycopodium}!clavatum@\textit{clavatum}} 石松 \index{石松}  LC
        \item[] \textit{L. complanatum} L. \index{Lycopodium@\textit{Lycopodium}!complanatum@\textit{complanatum}} 地刷子 \index{地刷子}  LC
        \item[] \textit{L. obscurum} L. \index{Lycopodium@\textit{Lycopodium}!obscurum@\textit{obscurum}} 玉柏 \index{玉柏}  LC
        \item[] \textit{L. veitchii} H.Christ \index{Lycopodium@\textit{Lycopodium}!veitchii@\textit{veitchii}} 玉山石松 \index{玉山石松}  LC
        \item[] \textit{L. yueshanense} C.M.Kuo \index{Lycopodium@\textit{Lycopodium}!yueshanense@\textit{yueshanense}} 玉山地刷 \index{玉山地刷}  DD
  \end{itemize}
 \item[] \textit{Phlegmariurus} 馬尾杉屬
                                
  \begin{itemize}
        \item[] \textit{P. carinatus} (Desv.) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!carinatus@\textit{carinatus}} 覆葉石松 \index{覆葉石松}  EN
        \item[] \textit{P. changii} T.Y.Hsieh \index{Phlegmariurus@\textit{Phlegmariurus}!changii@\textit{changii}} 張氏石松 \index{張氏石松}  DD
        \item[] \textit{P. cryptomerianus} (Maxim.) Satou \index{Phlegmariurus@\textit{Phlegmariurus}!cryptomerianus@\textit{cryptomerianus}} 柳杉葉石松 \index{柳杉葉石松}  NT
        \item[] \textit{P. cunninghamioides} (Hayata) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!cunninghamioides@\textit{cunninghamioides}} 寬葉石松 \index{寬葉石松}  CR*
        \item[] \textit{P. fargesii} (Herter) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!fargesii@\textit{fargesii}} 銳葉石松 \index{銳葉石松}  EN
        \item[] \textit{P. fordii} (Baker) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!fordii@\textit{fordii}} 福氏石松 \index{福氏石松}  LC
        \item[] \textit{P. phlegmaria} (L.) T.Sen \& U.Sen \index{Phlegmariurus@\textit{Phlegmariurus}!phlegmaria@\textit{phlegmaria}} 垂枝石松 \index{垂枝石松}  EN
        \item[] \textit{P. salvinioides} (Herter) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!salvinioides@\textit{salvinioides}} 小垂枝石松 \index{小垂枝石松}  EN
        \item[] \textit{P. sieboldii} (Miq.) Ching \index{Phlegmariurus@\textit{Phlegmariurus}!sieboldii@\textit{sieboldii}} 鱗葉石松 \index{鱗葉石松}  EN
        \item[] \textit{P. squarrosus} (G.Forst.) A.Love \& D.Love \index{Phlegmariurus@\textit{Phlegmariurus}!squarrosus@\textit{squarrosus}} 杉葉石松 \index{杉葉石松}  EN
  \end{itemize}
  \end{itemize}
