
  \begin{itemize}
 \item[] \textit{Ammannia} 水莧菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ammannia+auriculata}{\textit{A. auriculata} Willd.}  \index{Ammannia@\textit{Ammannia}!auriculata@\textit{auriculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=耳葉水莧菜&T2_new_value=true&fr=y}}{耳葉水莧菜}\index{耳葉水莧菜} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ammannia+baccifera}{\textit{A. baccifera} L.}  \index{Ammannia@\textit{Ammannia}!baccifera@\textit{baccifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水莧菜&T2_new_value=true&fr=y}}{水莧菜}\index{水莧菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ammannia+coccinea}{\textit{A. coccinea} Rathb.}  \index{Ammannia@\textit{Ammannia}!coccinea@\textit{coccinea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉水莧菜&T2_new_value=true&fr=y}}{長葉水莧菜}\index{長葉水莧菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ammannia+multiflora}{\textit{A. multiflora} Roxb.}  \index{Ammannia@\textit{Ammannia}!multiflora@\textit{multiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多花水莧菜&T2_new_value=true&fr=y}}{多花水莧菜}\index{多花水莧菜} LC
  \end{itemize}
 \item[] \textit{Cuphea} 克非亞草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cuphea+cartagenesis}{\textit{C. cartagenesis} (Jacq.) Macbride}  \index{Cuphea@\textit{Cuphea}!cartagenesis@\textit{cartagenesis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=克非亞草&T2_new_value=true&fr=y}}{克非亞草}\index{克非亞草} NA$^n$
  \end{itemize}
 \item[] \textit{Lagerstroemia} 紫薇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lagerstroemia+subcostata}{\textit{L. subcostata} Koehne}  \index{Lagerstroemia@\textit{Lagerstroemia}!subcostata@\textit{subcostata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=九芎&T2_new_value=true&fr=y}}{九芎}\index{九芎} LC
  \end{itemize}
 \item[] \textit{Pemphis} 水芫花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pemphis+acidula}{\textit{P. acidula} J.R.Forst. \& G.Forst.}  \index{Pemphis@\textit{Pemphis}!acidula@\textit{acidula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水芫花&T2_new_value=true&fr=y}}{水芫花}\index{水芫花} LC
  \end{itemize}
 \item[] \textit{Rotala} 水豬母乳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+hippuris}{\textit{R. hippuris} Makino}  \index{Rotala@\textit{Rotala}!hippuris@\textbf{\textit{hippuris}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水杉菜&T2_new_value=true&fr=y}}{水杉菜}\index{水杉菜@{\Song{水杉菜}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+indica+var.+uliginosa}{\textit{R. indica} (Willd) Koehne var. \textit{uliginosa} (Miq.) Koehne}  \index{Rotala@\textit{Rotala}!indica@\textit{indica}!var. uliginosa@var. \textit{uliginosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度節節菜&T2_new_value=true&fr=y}}{印度節節菜}\index{印度節節菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+mexicana}{\textit{R. mexicana} Cham. \& Schltd.}  \index{Rotala@\textit{Rotala}!mexicana@\textit{mexicana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=輪生葉水豬母乳&T2_new_value=true&fr=y}}{輪生葉水豬母乳}\index{輪生葉水豬母乳} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+ramosior}{\textit{R. ramosior} (L.) Koehne}  \index{Rotala@\textit{Rotala}!ramosior@\textit{ramosior}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=美洲水豬母乳&T2_new_value=true&fr=y}}{美洲水豬母乳}\index{美洲水豬母乳} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+rosea}{\textit{R. rosea} (Poir.) C.D.K.Cook}  \index{Rotala@\textit{Rotala}!rosea@\textit{rosea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=五蕊水豬母乳&T2_new_value=true&fr=y}}{五蕊水豬母乳}\index{五蕊水豬母乳} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+rotundifolia}{\textit{R. rotundifolia} (Wall. ex Roxb.) Koehne}  \index{Rotala@\textit{Rotala}!rotundifolia@\textit{rotundifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水豬母乳&T2_new_value=true&fr=y}}{水豬母乳}\index{水豬母乳} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+taiwaniana}{\textit{R. taiwaniana} Y.C.Liu \& F.Y.Lu}  \index{Rotala@\textit{Rotala}!taiwaniana@\textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉里水豬母乳&T2_new_value=true&fr=y}}{玉里水豬母乳}\index{玉里水豬母乳} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rotala+wallichii}{\textit{R. wallichii} (Hook.f.) Koehne}  \index{Rotala@\textit{Rotala}!wallichii@\textbf{\textit{wallichii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓦氏水豬母乳&T2_new_value=true&fr=y}}{瓦氏水豬母乳}\index{瓦氏水豬母乳@{\Song{瓦氏水豬母乳}}} VU
  \end{itemize}
 \item[] \textit{Trapa} 菱屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+bicornis+var.+taiwanensis}{\textit{T. bicornis} Osbeck var. \textit{taiwanensis} (Nakai) Z.T.Xiong}  \index{Trapa@\textit{Trapa}!bicornis@\textit{bicornis}!var. taiwanensis@var. \textit{taiwanensis}}  \index{Trapa@\textit{Trapa}!taiwanensis@\textit{taiwanensis}{\\\noindent(= \textit{Trapa bicornis} var. \textit{taiwanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣菱&T2_new_value=true&fr=y}}{臺灣菱}\index{臺灣菱} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+bispinosa}{\textit{T. bispinosa} Roxb.}  \index{Trapa@\textit{Trapa}!bispinosa@\textit{bispinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二角菱&T2_new_value=true&fr=y}}{二角菱}\index{二角菱} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+incisa}{\textit{T. incisa} Siebold \& Zucc.}  \index{Trapa@\textit{Trapa}!incisa@\textbf{\textit{incisa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小果菱&T2_new_value=true&fr=y}}{小果菱}\index{小果菱@{\Song{小果菱}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+japonica}{\textit{T. japonica} Flerow}  \index{Trapa@\textit{Trapa}!japonica@\textbf{\textit{japonica}}}  \index{Trapa@\textit{Trapa}!bicornis@\textit{bicornis}!var. jinumai@var. \textit{jinumai}{\\\noindent(=\textit{Trapa japonica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本菱&T2_new_value=true&fr=y}}{日本菱}\index{日本菱@{\Song{日本菱}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+maximowiczii}{\textit{T. maximowiczii} Korsh.}  \index{Trapa@\textit{Trapa}!maximowiczii@\textit{maximowiczii}}  \index{Trapa@\textit{Trapa}!natans@\textit{natans}!var. japonica@var. \textit{japonica}{\\\noindent(=\textit{Trapa maximowiczii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼菱&T2_new_value=true&fr=y}}{鬼菱}\index{鬼菱} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trapa+pseudoincisa}{\textit{T. pseudoincisa} Nakai}  \index{Trapa@\textit{Trapa}!pseudoincisa@\textit{pseudoincisa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=格菱&T2_new_value=true&fr=y}}{格菱}\index{格菱} DD
  \end{itemize}
  \end{itemize}
