
  \begin{itemize}
 \item[] \textit{Abelmoschus} 秋葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abelmoschus+manihot+var.+pungens}{\textit{A. manihot} (L.) Medik. var. \textit{pungens} (Roxb.) Hochr.}  \index{Abelmoschus@\textit{Abelmoschus}!manihot@\textit{manihot}!var. pungens@var. \textit{pungens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=剛毛黃蜀葵&T2_new_value=true&fr=y}}{剛毛黃蜀葵}\index{剛毛黃蜀葵} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abelmoschus+moschatus}{\textit{A. moschatus} (L.) Medik.}  \index{Abelmoschus@\textit{Abelmoschus}!moschatus@\textit{moschatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香葵&T2_new_value=true&fr=y}}{香葵}\index{香葵} NA$^n$
  \end{itemize}
 \item[] \textit{Abutilon} 莔麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+crispum}{\textit{A. crispum} (L.) Medik.}  \index{Abutilon@\textit{Abutilon}!crispum@\textit{crispum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泡果莔&T2_new_value=true&fr=y}}{泡果莔}\index{泡果莔} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+grandifolium}{\textit{A. grandifolium} (Willd.) Sweet}  \index{Abutilon@\textit{Abutilon}!grandifolium@\textit{grandifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉莔麻&T2_new_value=true&fr=y}}{大葉莔麻}\index{大葉莔麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+hirtum}{\textit{A. hirtum} (Lamk.) Sweet}  \index{Abutilon@\textit{Abutilon}!hirtum@\textit{hirtum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛莔&T2_new_value=true&fr=y}}{毛莔}\index{毛莔} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+hulseanum}{\textit{A. hulseanum} (Torr. \& A.Gray) Torr. ex A.Gray }  \index{Abutilon@\textit{Abutilon}!hulseanum@\textit{hulseanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花莔麻&T2_new_value=true&fr=y}}{疏花莔麻}\index{疏花莔麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+indicum+var.+guineense}{\textit{A. indicum} (L.) Sweet var. \textit{guineense} (Schumach.) K.M.Feng}  \index{Abutilon@\textit{Abutilon}!indicum@\textit{indicum}!var. guineense@var. \textit{guineense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=畿內冬葵子&T2_new_value=true&fr=y}}{畿內冬葵子}\index{畿內冬葵子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+indicum+var.+indicum}{\textit{A. indicum} (L.) Sweet var. \textit{indicum}}  \index{Abutilon@\textit{Abutilon}!indicum@\textit{indicum}!var. indicum@var. \textit{indicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冬葵子&T2_new_value=true&fr=y}}{冬葵子}\index{冬葵子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abutilon+striatum}{\textit{A. striatum} Dicks.}  \index{Abutilon@\textit{Abutilon}!striatum@\textit{striatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=風鈴花&T2_new_value=true&fr=y}}{風鈴花}\index{風鈴花} NA$^n$
  \end{itemize}
 \item[] \textit{Anoda} 蔓錦葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anoda+cristata}{\textit{A. cristata} (L.) Schltdl.}  \index{Anoda@\textit{Anoda}!cristata@\textit{cristata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冠萼蔓錦葵&T2_new_value=true&fr=y}}{冠萼蔓錦葵}\index{冠萼蔓錦葵} NA$^n$
  \end{itemize}
 \item[] \textit{Berrya} 六翅木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berrya+ammonilla}{\textit{B. ammonilla} Roxb.}  \index{Berrya@\textit{Berrya}!ammonilla@\textbf{\textit{ammonilla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=六翅木&T2_new_value=true&fr=y}}{六翅木}\index{六翅木@{\Song{六翅木}}} EN
  \end{itemize}
 \item[] \textit{Bombax} 木棉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bombax+ceiba}{\textit{B. ceiba} L.}  \index{Bombax@\textit{Bombax}!ceiba@\textit{ceiba}}  \index{Bombax@\textit{Bombax}!malabarica@\textit{malabarica}{\\\noindent(= \textit{Bombax ceiba})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木棉&T2_new_value=true&fr=y}}{木棉}\index{木棉} NA$^n$
  \end{itemize}
 \item[] \textit{Corchorus} 黃麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corchorus+aestuans+var.+aestuans}{\textit{C. aestuans} L. var. \textit{aestuans}}  \index{Corchorus@\textit{Corchorus}!aestuans@\textit{aestuans}!var. aestuans@var. \textit{aestuans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繩黃麻&T2_new_value=true&fr=y}}{繩黃麻}\index{繩黃麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corchorus+aestuans+var.+brevicaulis}{\textit{C. aestuans} L. var. \textit{brevicaulis} (Hosok.) T.S.Liu \& H.C.Lo}  \index{Corchorus@\textit{Corchorus}!aestuans@\textit{aestuans}!var. brevicaulis@var. \textit{brevicaulis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短莖繩黃麻&T2_new_value=true&fr=y}}{短莖繩黃麻}\index{短莖繩黃麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corchorus+capsularis}{\textit{C. capsularis} L.}  \index{Corchorus@\textit{Corchorus}!capsularis@\textit{capsularis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃麻&T2_new_value=true&fr=y}}{黃麻}\index{黃麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corchorus+olitorius}{\textit{C. olitorius} L.}  \index{Corchorus@\textit{Corchorus}!olitorius@\textit{olitorius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山麻&T2_new_value=true&fr=y}}{山麻}\index{山麻} NA$^n$
  \end{itemize}
 \item[] \textit{Firmiana} 梧桐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Firmiana+simplex}{\textit{F. simplex} (L.) W.F.Wight}  \index{Firmiana@\textit{Firmiana}!simplex@\textit{simplex}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梧桐&T2_new_value=true&fr=y}}{梧桐}\index{梧桐} LC
  \end{itemize}
 \item[] \textit{Grewia} 捕魚木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Grewia+biloba}{\textit{G. biloba} Wall.}  \index{Grewia@\textit{Grewia}!biloba@\textit{biloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉捕魚木&T2_new_value=true&fr=y}}{厚葉捕魚木}\index{厚葉捕魚木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Grewia+eriocarpa}{\textit{G. eriocarpa} Juss.}  \index{Grewia@\textit{Grewia}!eriocarpa@\textbf{\textit{eriocarpa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉捕魚木&T2_new_value=true&fr=y}}{大葉捕魚木}\index{大葉捕魚木@{\Song{大葉捕魚木}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Grewia+piscatorum}{\textit{G. piscatorum} Hance}  \index{Grewia@\textit{Grewia}!piscatorum@\textit{piscatorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉捕魚木&T2_new_value=true&fr=y}}{小葉捕魚木}\index{小葉捕魚木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Grewia+rhombifolia}{\textit{G. rhombifolia} Kaneh. \& Sasaki}  \index{Grewia@\textit{Grewia}!rhombifolia@\textit{rhombifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菱葉捕魚木&T2_new_value=true&fr=y}}{菱葉捕魚木}\index{菱葉捕魚木}\# LC
  \end{itemize}
 \item[] \textit{Helicteres} 山芝麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Helicteres+augustifolia}{\textit{H. augustifolia} L.}  \index{Helicteres@\textit{Helicteres}!augustifolia@\textit{augustifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山芝麻&T2_new_value=true&fr=y}}{山芝麻}\index{山芝麻} LC
  \end{itemize}
 \item[] \textit{Heritiera} 銀葉樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Heritiera+littoralis}{\textit{H. littoralis} Dryand.}  \index{Heritiera@\textit{Heritiera}!littoralis@\textbf{\textit{littoralis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀葉樹&T2_new_value=true&fr=y}}{銀葉樹}\index{銀葉樹@{\Song{銀葉樹}}} EN
  \end{itemize}
 \item[] \textit{Hibiscus} 木槿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+asper}{\textit{H. asper} Hook.f.}  \index{Hibiscus@\textit{Hibiscus}!asper@\textit{asper}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=糙葉木槿&T2_new_value=true&fr=y}}{糙葉木槿}\index{糙葉木槿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+cannabinus}{\textit{H. cannabinus} L.}  \index{Hibiscus@\textit{Hibiscus}!cannabinus@\textit{cannabinus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大麻槿&T2_new_value=true&fr=y}}{大麻槿}\index{大麻槿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+makinoi}{\textit{H. makinoi} Y.Jotani \& H.Ohba}  \index{Hibiscus@\textit{Hibiscus}!makinoi@\textit{makinoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=牧野氏山芙蓉&T2_new_value=true&fr=y}}{牧野氏山芙蓉}\index{牧野氏山芙蓉} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+mutabilis}{\textit{H. mutabilis} L.}  \index{Hibiscus@\textit{Hibiscus}!mutabilis@\textit{mutabilis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木芙蓉&T2_new_value=true&fr=y}}{木芙蓉}\index{木芙蓉} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+surattensis}{\textit{H. surattensis} L.}  \index{Hibiscus@\textit{Hibiscus}!surattensis@\textbf{\textit{surattensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺芙蓉&T2_new_value=true&fr=y}}{刺芙蓉}\index{刺芙蓉@{\Song{刺芙蓉}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+syriacus}{\textit{H. syriacus} L.}  \index{Hibiscus@\textit{Hibiscus}!syriacus@\textit{syriacus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木槿&T2_new_value=true&fr=y}}{木槿}\index{木槿} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+taiwanensis}{\textit{H. taiwanensis} S.Y.Hu}  \index{Hibiscus@\textit{Hibiscus}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山芙蓉&T2_new_value=true&fr=y}}{山芙蓉}\index{山芙蓉}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hibiscus+tiliaceus}{\textit{H. tiliaceus} L.}  \index{Hibiscus@\textit{Hibiscus}!tiliaceus@\textit{tiliaceus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃槿&T2_new_value=true&fr=y}}{黃槿}\index{黃槿} LC
  \end{itemize}
 \item[] \textit{Kleinhovia} 克蘭樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Kleinhovia+hospita}{\textit{K. hospita} L.}  \index{Kleinhovia@\textit{Kleinhovia}!hospita@\textit{hospita}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=克蘭樹&T2_new_value=true&fr=y}}{克蘭樹}\index{克蘭樹} LC
  \end{itemize}
 \item[] \textit{Malachra} 旋葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malachra+capitata}{\textit{M. capitata} L.}  \index{Malachra@\textit{Malachra}!capitata@\textit{capitata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=旋葵&T2_new_value=true&fr=y}}{旋葵}\index{旋葵} NA$^n$
  \end{itemize}
 \item[] \textit{Malva} 錦葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malva+cathayensis}{\textit{M. cathayensis} M.G. Gilbert, Y. Tang \& Dorr}  \index{Malva@\textit{Malva}!cathayensis@\textit{cathayensis}}  \index{Malva@\textit{Malva}!sinensis@\textit{sinensis}{\\\noindent(= \textit{Malva cathayensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華錦葵&T2_new_value=true&fr=y}}{華錦葵}\index{華錦葵} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malva+neglecta}{\textit{M. neglecta} Wall.}  \index{Malva@\textit{Malva}!neglecta@\textit{neglecta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉錦葵&T2_new_value=true&fr=y}}{圓葉錦葵}\index{圓葉錦葵} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malva+parviflora}{\textit{M. parviflora} L.}  \index{Malva@\textit{Malva}!parviflora@\textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花錦葵&T2_new_value=true&fr=y}}{小花錦葵}\index{小花錦葵} NA$^n$
  \end{itemize}
 \item[] \textit{Malvastrum} 賽葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malvastrum+coromandelianum}{\textit{M. coromandelianum} (L.) Garcke}  \index{Malvastrum@\textit{Malvastrum}!coromandelianum@\textit{coromandelianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賽葵&T2_new_value=true&fr=y}}{賽葵}\index{賽葵} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malvastrum+spicatum}{\textit{M. spicatum} (L.) A.Gray}  \index{Malvastrum@\textit{Malvastrum}!spicatum@\textit{spicatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=穗花賽葵&T2_new_value=true&fr=y}}{穗花賽葵}\index{穗花賽葵} NA$^n$
  \end{itemize}
 \item[] \textit{Melochia} 野路葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melochia+corchorifolia}{\textit{M. corchorifolia} L.}  \index{Melochia@\textit{Melochia}!corchorifolia@\textit{corchorifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野路葵&T2_new_value=true&fr=y}}{野路葵}\index{野路葵} LC
  \end{itemize}
 \item[] \textit{Modiola} 蔓葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Modiola+caroliniana}{\textit{M. caroliniana} (L.) G.Don}  \index{Modiola@\textit{Modiola}!caroliniana@\textit{caroliniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺果錦葵&T2_new_value=true&fr=y}}{刺果錦葵}\index{刺果錦葵} NA$^n$
  \end{itemize}
 \item[] \textit{Pachira} 瓜栗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pachira+aquatica}{\textit{P. aquatica} Aubl.}  \index{Pachira@\textit{Pachira}!aquatica@\textit{aquatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬拉巴栗&T2_new_value=true&fr=y}}{馬拉巴栗}\index{馬拉巴栗} NA$^n$
  \end{itemize}
 \item[] \textit{Pterospermum} 翅子樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pterospermum+niveum}{\textit{P. niveum} Vidal}  \index{Pterospermum@\textit{Pterospermum}!niveum@\textbf{\textit{niveum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翅子樹&T2_new_value=true&fr=y}}{翅子樹}\index{翅子樹@{\Song{翅子樹}}} VU
  \end{itemize}
 \item[] \textit{Reevesia} 梭羅樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Reevesia+formosana}{\textit{R. formosana} Sprague}  \index{Reevesia@\textit{Reevesia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣梭羅樹&T2_new_value=true&fr=y}}{臺灣梭羅樹}\index{臺灣梭羅樹}\# NT
  \end{itemize}
 \item[] \textit{Sida} 金午時花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+acuta}{\textit{S. acuta} Burm.f.}  \index{Sida@\textit{Sida}!acuta@\textit{acuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉金午時花&T2_new_value=true&fr=y}}{細葉金午時花}\index{細葉金午時花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+cordifolia}{\textit{S. cordifolia} L.}  \index{Sida@\textit{Sida}!cordifolia@\textit{cordifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉金午時花&T2_new_value=true&fr=y}}{圓葉金午時花}\index{圓葉金午時花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+javensis}{\textit{S. javensis} Cav.}  \index{Sida@\textit{Sida}!javensis@\textit{javensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=爪哇金午時花&T2_new_value=true&fr=y}}{爪哇金午時花}\index{爪哇金午時花} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+mysorensis}{\textit{S. mysorensis} Wight \& Arn.}  \index{Sida@\textit{Sida}!mysorensis@\textit{mysorensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉金午時花&T2_new_value=true&fr=y}}{薄葉金午時花}\index{薄葉金午時花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+rhombifolia+subsp.+insularis}{\textit{S. rhombifolia} L. subsp. \textit{insularis} (Hatus.) Hatus.}  \index{Sida@\textit{Sida}!rhombifolia@\textit{rhombifolia}!subsp. insularis@subsp. \textit{insularis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春金午時花&T2_new_value=true&fr=y}}{恆春金午時花}\index{恆春金午時花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+rhombifolia+subsp.+rhombifolia}{\textit{S. rhombifolia} L. subsp. \textit{rhombifolia}}  \index{Sida@\textit{Sida}!rhombifolia@\textit{rhombifolia}!subsp. rhombifolia@subsp. \textit{rhombifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金午時花&T2_new_value=true&fr=y}}{金午時花}\index{金午時花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+rhombifolia+var.+maderensis}{\textit{S. rhombifolia} L. var. \textit{maderensis} (Lowe) Lowe}  \index{Sida@\textit{Sida}!rhombifolia@\textit{rhombifolia}!var. maderensis@var. \textit{maderensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單芒金午時花&T2_new_value=true&fr=y}}{單芒金午時花}\index{單芒金午時花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+rhomboidea}{\textit{S. rhomboidea} Roxb. ex Fleming}  \index{Sida@\textit{Sida}!rhomboidea@\textit{rhomboidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬金午時花&T2_new_value=true&fr=y}}{擬金午時花}\index{擬金午時花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+spinosa}{\textit{S. spinosa} L.}  \index{Sida@\textit{Sida}!spinosa@\textit{spinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺金午時花&T2_new_value=true&fr=y}}{刺金午時花}\index{刺金午時花} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sida+veronicaefolia}{\textit{S. veronicaefolia} Lam.}  \index{Sida@\textit{Sida}!veronicaefolia@\textit{veronicaefolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澎湖金午時花&T2_new_value=true&fr=y}}{澎湖金午時花}\index{澎湖金午時花} LC
  \end{itemize}
 \item[] \textit{Sterculia} 蘋婆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sterculia+ceramica}{\textit{S. ceramica} R.Br.}  \index{Sterculia@\textit{Sterculia}!ceramica@\textit{ceramica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼蘋婆&T2_new_value=true&fr=y}}{蘭嶼蘋婆}\index{蘭嶼蘋婆} LC
  \end{itemize}
 \item[] \textit{Thespesia} 繖楊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thespesia+populnea}{\textit{T. populnea} (L.) Soladoye ex Correa}  \index{Thespesia@\textit{Thespesia}!populnea@\textbf{\textit{populnea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繖楊&T2_new_value=true&fr=y}}{繖楊}\index{繖楊@{\Song{繖楊}}} EN
  \end{itemize}
 \item[] \textit{Triumfetta} 垂桉草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triumfetta+pilosa}{\textit{T. pilosa} Roth.}  \index{Triumfetta@\textit{Triumfetta}!pilosa@\textit{pilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉垂桉草&T2_new_value=true&fr=y}}{長葉垂桉草}\index{長葉垂桉草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triumfetta+rhomboidea}{\textit{T. rhomboidea} Jacq.}  \index{Triumfetta@\textit{Triumfetta}!rhomboidea@\textit{rhomboidea}}  \index{Triumfetta@\textit{Triumfetta}!bartramia@\textit{bartramia}{\\\noindent(= \textit{Triumfetta rhomboidea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂桉草&T2_new_value=true&fr=y}}{垂桉草}\index{垂桉草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triumfetta+semitriloba}{\textit{T. semitriloba} Jacq.}  \index{Triumfetta@\textit{Triumfetta}!semitriloba@\textit{semitriloba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲島垂桉草&T2_new_value=true&fr=y}}{菲島垂桉草}\index{菲島垂桉草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Triumfetta+tomentosa}{\textit{T. tomentosa} Baker}  \index{Triumfetta@\textit{Triumfetta}!tomentosa@\textit{tomentosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭垂桉草&T2_new_value=true&fr=y}}{臭垂桉草}\index{臭垂桉草} LC
  \end{itemize}
 \item[] \textit{Urena} 野棉花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Urena+lobata}{\textit{U. lobata} L.}  \index{Urena@\textit{Urena}!lobata@\textit{lobata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野棉花&T2_new_value=true&fr=y}}{野棉花}\index{野棉花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Urena+procumbens}{\textit{U. procumbens} L.}  \index{Urena@\textit{Urena}!procumbens@\textit{procumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梵天花&T2_new_value=true&fr=y}}{梵天花}\index{梵天花} LC
  \end{itemize}
 \item[] \textit{Waltheria} 草梧桐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Waltheria+americana}{\textit{W. americana} L.}  \index{Waltheria@\textit{Waltheria}!americana@\textit{americana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=草梧桐&T2_new_value=true&fr=y}}{草梧桐}\index{草梧桐} LC
  \end{itemize}
  \end{itemize}
