
  \begin{itemize}
 \item[] \textit{Astronia} 大野牡丹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Astronia+formosana}{\textit{A. formosana} Kaneh.}  \index{Astronia@\textit{Astronia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大野牡丹&T2_new_value=true&fr=y}}{大野牡丹}\index{大野牡丹}\# LC
  \end{itemize}
 \item[] \textit{Barthea} 深山野牡丹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Barthea+barthei}{\textit{B. barthei} (Hance ex Benth.) Krasser}  \index{Barthea@\textit{Barthea}!barthei@\textit{barthei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=深山野牡丹&T2_new_value=true&fr=y}}{深山野牡丹}\index{深山野牡丹} LC
  \end{itemize}
 \item[] \textit{Blastus} 柏拉木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Blastus+cochinchinensis}{\textit{B. cochinchinensis} Lour.}  \index{Blastus@\textit{Blastus}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柏拉木&T2_new_value=true&fr=y}}{柏拉木}\index{柏拉木} LC
  \end{itemize}
 \item[] \textit{Bredia} 金石榴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+dulanica}{\textit{B. dulanica} C.L.Yeh, S.W.Chung \& T.C.Hsu}  \index{Bredia@\textit{Bredia}!dulanica@\textbf{\textit{dulanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=都蘭山金石榴&T2_new_value=true&fr=y}}{都蘭山金石榴}\index{都蘭山金石榴@{\Song{都蘭山金石榴}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+gibba}{\textit{B. gibba} Ohwi}  \index{Bredia@\textit{Bredia}!gibba@\textit{gibba}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小金石榴&T2_new_value=true&fr=y}}{小金石榴}\index{小金石榴}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+hirsuta+var.+hirsuta}{\textit{B. hirsuta} Blume var. \textit{hirsuta}}  \index{Bredia@\textit{Bredia}!hirsuta@\textit{hirsuta}!var. hirsuta@var. \textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛布勒德藤&T2_new_value=true&fr=y}}{毛布勒德藤}\index{毛布勒德藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+hirsuta+var.+rotundifolia}{\textit{B. hirsuta} Blume var. \textit{rotundifolia} (Y.C.Liu \& C.H.Ou) S.F.Huang \& T.C.Huang}  \index{Bredia@\textit{Bredia}!hirsuta@\textit{hirsuta}!var. rotundifolia@var. \textit{rotundifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉布勒徳藤&T2_new_value=true&fr=y}}{圓葉布勒徳藤}\index{圓葉布勒徳藤}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+hirsuta+var.+scandens}{\textit{B. hirsuta} Blume var. \textit{scandens} Ito \& Matsum.}  \index{Bredia@\textit{Bredia}!hirsuta@\textit{hirsuta}!var. scandens@var. \textit{scandens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=布勒德藤&T2_new_value=true&fr=y}}{布勒德藤}\index{布勒德藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+laisherana}{\textit{B. laisherana} C.L.Yeh \& C.R.Yeh}  \index{Bredia@\textit{Bredia}!laisherana@\textbf{\textit{laisherana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=來社山布勒德藤&T2_new_value=true&fr=y}}{來社山布勒德藤}\index{來社山布勒德藤@{\Song{來社山布勒德藤}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bredia+oldhamii}{\textit{B. oldhamii} Hook.f.}  \index{Bredia@\textit{Bredia}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金石榴&T2_new_value=true&fr=y}}{金石榴}\index{金石榴}\# LC
  \end{itemize}
 \item[] \textit{Clidemia} 毛野牡丹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clidemia+hirta}{\textit{C. hirta} (L.) D.Don}  \index{Clidemia@\textit{Clidemia}!hirta@\textit{hirta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛野牡丹&T2_new_value=true&fr=y}}{毛野牡丹}\index{毛野牡丹} NA$^n$
  \end{itemize}
 \item[] \textit{Medinilla} 野牡丹藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medinilla+formosana}{\textit{M. formosana} Hayata}  \index{Medinilla@\textit{Medinilla}!formosana@\textbf{\textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣野牡丹藤&T2_new_value=true&fr=y}}{臺灣野牡丹藤}\index{臺灣野牡丹藤@{\Song{臺灣野牡丹藤}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Medinilla+hayatana}{\textit{M. hayatana} H.Keng}  \index{Medinilla@\textit{Medinilla}!hayatana@\textbf{\textit{hayatana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼野牡丹藤&T2_new_value=true&fr=y}}{蘭嶼野牡丹藤}\index{蘭嶼野牡丹藤@{\Song{蘭嶼野牡丹藤}}}\# EN
  \end{itemize}
 \item[] \textit{Melastoma} 野牡丹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melastoma+affine}{\textit{M. affine} D.Don}  \index{Melastoma@\textit{Melastoma}!affine@\textit{affine}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基尖葉野牡丹&T2_new_value=true&fr=y}}{基尖葉野牡丹}\index{基尖葉野牡丹} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melastoma+candidum}{\textit{M. candidum} D.Don}  \index{Melastoma@\textit{Melastoma}!candidum@\textit{candidum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野牡丹&T2_new_value=true&fr=y}}{野牡丹}\index{野牡丹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melastoma+intermedia}{\textit{M. intermedia} Dunn}  \index{Melastoma@\textit{Melastoma}!intermedia@\textbf{\textit{intermedia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水社野牡丹&T2_new_value=true&fr=y}}{水社野牡丹}\index{水社野牡丹@{\Song{水社野牡丹}}} VU
  \end{itemize}
 \item[] \textit{Memecylon} 羊角扭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Memecylon+lanceolatum}{\textit{M. lanceolatum} Blanco}  \index{Memecylon@\textit{Memecylon}!lanceolatum@\textbf{\textit{lanceolatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=革葉羊角扭&T2_new_value=true&fr=y}}{革葉羊角扭}\index{革葉羊角扭@{\Song{革葉羊角扭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Memecylon+pendulum}{\textit{M. pendulum} Chih C.Wang, Y.H.Tseng, Y.T.Chen \& Kun C.Chang}  \index{Memecylon@\textit{Memecylon}!pendulum@\textbf{\textit{pendulum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂枝羊角扭&T2_new_value=true&fr=y}}{垂枝羊角扭}\index{垂枝羊角扭@{\Song{垂枝羊角扭}}}\# EN
  \end{itemize}
 \item[] \textit{Osbeckia} 金錦香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osbeckia+chinensis}{\textit{O. chinensis} L.}  \index{Osbeckia@\textit{Osbeckia}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金錦香&T2_new_value=true&fr=y}}{金錦香}\index{金錦香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osbeckia+opipara}{\textit{O. opipara} C.Y.Wu \& C.Chen}  \index{Osbeckia@\textit{Osbeckia}!opipara@\textbf{\textit{opipara}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉金錦香&T2_new_value=true&fr=y}}{闊葉金錦香}\index{闊葉金錦香@{\Song{闊葉金錦香}}} EN
  \end{itemize}
 \item[] \textit{Otanthera} 耳葯花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Otanthera+scaberrima}{\textit{O. scaberrima} (Hayata) Ohwi}  \index{Otanthera@\textit{Otanthera}!scaberrima@\textit{scaberrima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=糙葉耳藥花&T2_new_value=true&fr=y}}{糙葉耳藥花}\index{糙葉耳藥花}\# LC
  \end{itemize}
 \item[] \textit{Pachycentria} 厚距花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pachycentria+formosana}{\textit{P. formosana} Hayata}  \index{Pachycentria@\textit{Pachycentria}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣厚距花&T2_new_value=true&fr=y}}{臺灣厚距花}\index{臺灣厚距花}\# LC
  \end{itemize}
 \item[] \textit{Sarcopyramis} 肉穗野牡丹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sarcopyramis+napalensis+var.+bodinieri}{\textit{S. napalensis} Wall. var. \textit{bodinieri} (H.Lév. \& Vaniot) H.Lév.}  \index{Sarcopyramis@\textit{Sarcopyramis}!napalensis@\textit{napalensis}!var. bodinieri@var. \textit{bodinieri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=肉穗野牡丹&T2_new_value=true&fr=y}}{肉穗野牡丹}\index{肉穗野牡丹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sarcopyramis+napalensis+var.+delicata}{\textit{S. napalensis} Wall. var. \textit{delicata} (C.B.Rob.) S.F.Huang \& T.C.Huang}  \index{Sarcopyramis@\textit{Sarcopyramis}!napalensis@\textit{napalensis}!var. delicata@var. \textit{delicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=東方肉穗野牡丹&T2_new_value=true&fr=y}}{東方肉穗野牡丹}\index{東方肉穗野牡丹} LC
  \end{itemize}
 \item[] \textit{Sonerila} 蜂鬥草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sonerila+erecta}{\textit{S. erecta} Jack}  \index{Sonerila@\textit{Sonerila}!erecta@\textbf{\textit{erecta}}}  \index{Sonerila@\textit{Sonerila}!tenera@\textit{tenera}{\\\noindent(= \textit{Sonerila erecta})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三蕊草&T2_new_value=true&fr=y}}{三蕊草}\index{三蕊草@{\Song{三蕊草}}} EN
  \end{itemize}
  \end{itemize}
