
  \begin{itemize}
 \item[] \textit{Helonias} 胡麻花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Helonias+umbellata}{\textit{H. umbellata} (Baker) N.Tanaka}  \index{Helonias@\textit{Helonias}!umbellata@\textit{umbellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣胡麻花&T2_new_value=true&fr=y}}{臺灣胡麻花}\index{臺灣胡麻花}\# LC
  \end{itemize}
 \item[] \textit{Paris} 七葉一枝花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paris+fargesii+var.+brevipetalata}{\textit{P. fargesii} Franch. var. \textit{brevipetalata} (T.C.Huang \& K.C.Yang) T.C.Huang \& K.C.Yang}  \index{Paris@\textit{Paris}!fargesii@\textit{fargesii}!var. brevipetalata@var. \textit{brevipetalata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短瓣球葯隔七葉一枝花&T2_new_value=true&fr=y}}{短瓣球葯隔七葉一枝花}\index{短瓣球葯隔七葉一枝花} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paris+polyphylla+var.+polyphylla}{\textit{P. polyphylla} Sm. var. \textit{polyphylla}}  \index{Paris@\textit{Paris}!polyphylla@\textit{polyphylla}!var. polyphylla@var. \textit{polyphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=七葉一枝花&T2_new_value=true&fr=y}}{七葉一枝花}\index{七葉一枝花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paris+polyphylla+var.+stenophylla}{\textit{P. polyphylla} Sm. var. \textit{stenophylla} Franch.}  \index{Paris@\textit{Paris}!polyphylla@\textit{polyphylla}!var. stenophylla@var. \textit{stenophylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉七葉一枝花&T2_new_value=true&fr=y}}{狹葉七葉一枝花}\index{狹葉七葉一枝花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paris+polyphylla+var.+taitungensis}{\textit{P. polyphylla} Sm. var. \textit{taitungensis} (S.S.Ying) S.S.Ying}  \index{Paris@\textit{Paris}!polyphylla@\textit{polyphylla}!var. taitungensis@var. \textit{taitungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東七葉一枝花&T2_new_value=true&fr=y}}{臺東七葉一枝花}\index{臺東七葉一枝花}\# DD
  \end{itemize}
 \item[] \textit{Trillium} 延齡草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trillium+tschonoskii}{\textit{T. tschonoskii} Maxim.}  \index{Trillium@\textit{Trillium}!tschonoskii@\textit{tschonoskii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=延齡草&T2_new_value=true&fr=y}}{延齡草}\index{延齡草} NT
  \end{itemize}
 \item[] \textit{Veratrum} 黎蘆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veratrum+formosanum}{\textit{V. formosanum} O.Loes.}  \index{Veratrum@\textit{Veratrum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣藜蘆&T2_new_value=true&fr=y}}{臺灣藜蘆}\index{臺灣藜蘆}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veratrum+shuehshanarum}{\textit{V. shuehshanarum} S.S.Ying}  \index{Veratrum@\textit{Veratrum}!shuehshanarum@\textit{shuehshanarum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪山藜蘆&T2_new_value=true&fr=y}}{雪山藜蘆}\index{雪山藜蘆}\# DD
  \end{itemize}
 \item[] \textit{Ypsilandra} 丫蕊花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ypsilandra+thibetica}{\textit{Y. thibetica} Franch.}  \index{Ypsilandra@\textit{Ypsilandra}!thibetica@\textit{thibetica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=丫蕊花&T2_new_value=true&fr=y}}{丫蕊花}\index{丫蕊花} LC
  \end{itemize}
  \end{itemize}
