
  \begin{itemize}
 \item[] \textit{Cissampelos} 錫生藤屬 
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissampelos+pareira}{\textit{C. pareira} L.}  \index{Cissampelos@\textit{Cissampelos}!pareira@\textit{pareira}} 毛錫生藤\index{毛錫生藤} CR
  \end{itemize}
 \item[] \textit{Cocculus} 木防己屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cocculus+laurifolius}{\textit{C. laurifolius} DC.}  \index{Cocculus@\textit{Cocculus}!laurifolius@\textit{laurifolius}} 樟葉木防己\index{樟葉木防己} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cocculus+orbiculatus}{\textit{C. orbiculatus} (L.) DC.}  \index{Cocculus@\textit{Cocculus}!orbiculatus@\textit{orbiculatus}} 木防己\index{木防己} LC
  \end{itemize}
 \item[] \textit{Cyclea} 土防己屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyclea+gracillima}{\textit{C. gracillima} Diels}  \index{Cyclea@\textit{Cyclea}!gracillima@\textit{gracillima}} 土防己\index{土防己}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyclea+insularis}{\textit{C. insularis} (Makino) Hatus.}  \index{Cyclea@\textit{Cyclea}!insularis@\textit{insularis}} 蘭嶼土防己\index{蘭嶼土防己} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyclea+ochiaiana}{\textit{C. ochiaiana} (Yamam.) S.F.Huang \& T.C.Huang}  \index{Cyclea@\textit{Cyclea}!ochiaiana@\textit{ochiaiana}} 臺灣土防己\index{臺灣土防己}\# LC
  \end{itemize}
 \item[] \textit{Pericampylus} 細圓藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pericampylus+formosanus}{\textit{P. formosanus} Diels}  \index{Pericampylus@\textit{Pericampylus}!formosanus@\textit{formosanus}} 蓬萊藤\index{蓬萊藤} LC
  \end{itemize}
 \item[] \textit{Sinomenium} 漢防己屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sinomenium+acutum}{\textit{S. acutum} (Thunb.) Rehder \& E.H.Wils.}  \index{Sinomenium@\textit{Sinomenium}!acutum@\textit{acutum}} 漢防己\index{漢防己} EN
  \end{itemize}
 \item[] \textit{Stephania} 千金藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephania+cephalantha}{\textit{S. cephalantha} Hayata}  \index{Stephania@\textit{Stephania}!cephalantha@\textit{cephalantha}} 大還魂\index{大還魂} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephania+japonica+var.+hispidula}{\textit{S. japonica} (Thunb.) Miers var. \textit{hispidula} Yamam.}  \index{Stephania@\textit{Stephania}!japonica@\textit{japonica}!var. hispidula@var. \textit{hispidula}} 毛千金藤\index{毛千金藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephania+japonica+var.+japonica}{\textit{S. japonica} (Thunb.) Miers var. \textit{japonica}}  \index{Stephania@\textit{Stephania}!japonica@\textit{japonica}!var. japonica@var. \textit{japonica}} 千金藤\index{千金藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephania+merrillii}{\textit{S. merrillii} Diels}  \index{Stephania@\textit{Stephania}!merrillii@\textit{merrillii}} 蘭嶼千金藤\index{蘭嶼千金藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephania+tetrandra}{\textit{S. tetrandra} S.Moore}  \index{Stephania@\textit{Stephania}!tetrandra@\textit{tetrandra}} 石蟾蜍\index{石蟾蜍} VU
  \end{itemize}
 \item[] \textit{Tinospora} 青牛膽屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tinospora+dentata}{\textit{T. dentata} Diels}  \index{Tinospora@\textit{Tinospora}!dentata@\textit{dentata}} 恆春青牛膽\index{恆春青牛膽}\# EN
  \end{itemize}
  \end{itemize}
