
  \begin{itemize}
 \item[] \textit{Ensete} 拔蕉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ensete+glaucum}{\textit{E. glaucum} (Roxb.) Cheesman}  \index{Ensete@\textit{Ensete}!glaucum@\textit{glaucum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=象腿蕉&T2_new_value=true&fr=y}}{象腿蕉}\index{象腿蕉} LC
  \end{itemize}
 \item[] \textit{Musa} 芭蕉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+balbisiana}{\textit{M. balbisiana} Colla}  \index{Musa@\textit{Musa}!balbisiana@\textit{balbisiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=拔蕉&T2_new_value=true&fr=y}}{拔蕉}\index{拔蕉} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+basjoo+var.+formosana}{\textit{M. basjoo} Siebold var. \textit{formosana} (Warb.) S.S.Ying}  \index{Musa@\textit{Musa}!basjoo@\textit{basjoo}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣芭蕉&T2_new_value=true&fr=y}}{臺灣芭蕉}\index{臺灣芭蕉}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+insularimontana}{\textit{M. insularimontana} Hayata}  \index{Musa@\textit{Musa}!insularimontana@\textit{insularimontana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼芭蕉&T2_new_value=true&fr=y}}{蘭嶼芭蕉}\index{蘭嶼芭蕉}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+itinerans+var.+chiumei}{\textit{M. itinerans} Cheesman var. \textit{chiumei} H.L.Chiu, C.T.Shii \& T.Y.A.Yang}  \index{Musa@\textit{Musa}!itinerans@\textit{itinerans}!var. chiumei@\textbf{var. \textit{chiumei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泰雅芭蕉&T2_new_value=true&fr=y}}{泰雅芭蕉}\index{泰雅芭蕉@{\Song{泰雅芭蕉}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+itinerans+var.+kavalanensis}{\textit{M. itinerans} Cheesman var. \textit{kavalanensis} H.L.Chiu, C.T.Shii \& T.Y.A.Yang}  \index{Musa@\textit{Musa}!itinerans@\textit{itinerans}!var. kavalanensis@\textbf{var. \textit{kavalanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葛瑪蘭芭蕉&T2_new_value=true&fr=y}}{葛瑪蘭芭蕉}\index{葛瑪蘭芭蕉@{\Song{葛瑪蘭芭蕉}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Musa+yamiensis}{\textit{M. yamiensis} C.L.Yeh \& J.H.Chen}  \index{Musa@\textit{Musa}!yamiensis@\textit{yamiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雅美芭蕉&T2_new_value=true&fr=y}}{雅美芭蕉}\index{雅美芭蕉} EW
  \end{itemize}
  \end{itemize}
