
  \begin{itemize}
 \item[] \textit{Decaspermum} 十子木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Decaspermum+gracilentum}{\textit{D. gracilentum} (Hance) Merr. \& L.M.Perry}  \index{Decaspermum@\textit{Decaspermum}!gracilentum@\textit{gracilentum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=十子木&T2_new_value=true&fr=y}}{十子木}\index{十子木} LC
  \end{itemize}
 \item[] \textit{Psidium} 番石榴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psidium+guajava}{\textit{P. guajava} L.}  \index{Psidium@\textit{Psidium}!guajava@\textit{guajava}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=番石榴&T2_new_value=true&fr=y}}{番石榴}\index{番石榴} NA$^n$
  \end{itemize}
 \item[] \textit{Rhodomyrtus} 桃金孃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhodomyrtus+tomentosa}{\textit{R. tomentosa} (Aiton) Hassk.}  \index{Rhodomyrtus@\textit{Rhodomyrtus}!tomentosa@\textit{tomentosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桃金孃&T2_new_value=true&fr=y}}{桃金孃}\index{桃金孃} LC
  \end{itemize}
 \item[] \textit{Syzygium} 赤楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+acuminatissimum}{\textit{S. acuminatissimum} (Blume) DC.}  \index{Syzygium@\textit{Syzygium}!acuminatissimum@\textit{acuminatissimum}}  \index{Acmena@\textit{Acmena}!acuminatissima@\textit{acuminatissima}{\\\noindent(= \textit{Syzygium acuminatissimum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賽赤楠&T2_new_value=true&fr=y}}{賽赤楠}\index{賽赤楠} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+buxifolium}{\textit{S. buxifolium} Hook. \& Arn.}  \index{Syzygium@\textit{Syzygium}!buxifolium@\textit{buxifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉赤楠&T2_new_value=true&fr=y}}{小葉赤楠}\index{小葉赤楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+densinervium+var.+insulare}{\textit{S. densinervium} Merr. var. \textit{insulare} Chang}  \index{Syzygium@\textit{Syzygium}!densinervium@\textit{densinervium}!var. insulare@var. \textit{insulare}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密脈赤楠&T2_new_value=true&fr=y}}{密脈赤楠}\index{密脈赤楠}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+euphlebium}{\textit{S. euphlebium} (Hayata) Mori}  \index{Syzygium@\textit{Syzygium}!euphlebium@\textit{euphlebium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細脈赤楠&T2_new_value=true&fr=y}}{細脈赤楠}\index{細脈赤楠}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+formosanum}{\textit{S. formosanum} (Hayata) Mori}  \index{Syzygium@\textit{Syzygium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣赤楠&T2_new_value=true&fr=y}}{臺灣赤楠}\index{臺灣赤楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+jambos}{\textit{S. jambos} (L.) Alston}  \index{Syzygium@\textit{Syzygium}!jambos@\textit{jambos}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蒲桃&T2_new_value=true&fr=y}}{蒲桃}\index{蒲桃} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+kusukusense}{\textit{S. kusukusense} (Hayata) Mori}  \index{Syzygium@\textit{Syzygium}!kusukusense@\textit{kusukusense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛赤楠&T2_new_value=true&fr=y}}{高士佛赤楠}\index{高士佛赤楠}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+paucivenium}{\textit{S. paucivenium} (Robins.) Merr.}  \index{Syzygium@\textit{Syzygium}!paucivenium@\textbf{\textit{paucivenium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏脈赤楠&T2_new_value=true&fr=y}}{疏脈赤楠}\index{疏脈赤楠@{\Song{疏脈赤楠}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+simile}{\textit{S. simile} (Merr.) Merr.}  \index{Syzygium@\textit{Syzygium}!simile@\textit{simile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼赤楠&T2_new_value=true&fr=y}}{蘭嶼赤楠}\index{蘭嶼赤楠} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+taiwanicum}{\textit{S. taiwanicum} Hung T.Chang \& R.H.Miao}  \index{Syzygium@\textit{Syzygium}!taiwanicum@\textbf{\textit{taiwanicum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣棒花蒲桃&T2_new_value=true&fr=y}}{臺灣棒花蒲桃}\index{臺灣棒花蒲桃@{\Song{臺灣棒花蒲桃}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Syzygium+tripinnatum}{\textit{S. tripinnatum} (Blanco) Merr.}  \index{Syzygium@\textit{Syzygium}!tripinnatum@\textit{tripinnatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花赤楠&T2_new_value=true&fr=y}}{大花赤楠}\index{大花赤楠} NT
  \end{itemize}
  \end{itemize}
