
  \begin{itemize}
 \item[] \textit{Circaea} 露珠草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Circaea+alpina+subsp.+imaicola}{\textit{C. alpina} L. subsp. \textit{imaicola} (Asch. \& Mag.) Kitam.}  \index{Circaea@\textit{Circaea}!alpina@\textit{alpina}!subsp. imaicola@subsp. \textit{imaicola}} 高山露珠草 \index{高山露珠草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Circaea+cordata}{\textit{C. cordata} Royle}  \index{Circaea@\textit{Circaea}!cordata@\textit{cordata}} 心葉露珠草 \index{心葉露珠草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Circaea+erubescens}{\textit{C. erubescens} Franch. \& Sav.}  \index{Circaea@\textit{Circaea}!erubescens@\textit{erubescens}} 臺灣露珠草 \index{臺灣露珠草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Circaea+glabrescens}{\textit{C. glabrescens} (Pamp.) Hand.-Mazz.}  \index{Circaea@\textit{Circaea}!glabrescens@\textit{glabrescens}} 禿梗露珠草 \index{禿梗露珠草}  RE
  \end{itemize}
 \item[] \textit{Epilobium} 柳葉菜屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+amurense}{\textit{E. amurense} Hausskn.}  \index{Epilobium@\textit{Epilobium}!amurense@\textit{amurense}} 黑龍江柳葉菜 \index{黑龍江柳葉菜}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+brevifolium+subsp.+trichoneurum}{\textit{E. brevifolium} D.Don subsp. \textit{trichoneurum} (Hausskn.) P.H.Raven}  \index{Epilobium@\textit{Epilobium}!brevifolium@\textit{brevifolium}!subsp. trichoneurum@subsp. \textit{trichoneurum}} 短葉柳葉菜 \index{短葉柳葉菜}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+hohuanense}{\textit{E. hohuanense} S.S.Ying ex C.J.Chen, Hoch \& P.H.Raven}  \index{Epilobium@\textit{Epilobium}!hohuanense@\textit{hohuanense}} 合歡柳葉菜 \index{合歡柳葉菜} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+nankotaizanense}{\textit{E. nankotaizanense} Yamam.}  \index{Epilobium@\textit{Epilobium}!nankotaizanense@\textit{nankotaizanense}} 南湖柳葉菜 \index{南湖柳葉菜} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+pengii}{\textit{E. pengii} C.J.Chen, Hoch \& P.H.Raven}  \index{Epilobium@\textit{Epilobium}!pengii@\textit{pengii}} 彭氏柳葉菜 \index{彭氏柳葉菜} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+platystigmatosum}{\textit{E. platystigmatosum} C.B.Rob.}  \index{Epilobium@\textit{Epilobium}!platystigmatosum@\textit{platystigmatosum}} 闊柱柳葉菜 \index{闊柱柳葉菜}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epilobium+taiwanianum}{\textit{E. taiwanianum} C.J.Chen, Hoch \& P.H.Raven}  \index{Epilobium@\textit{Epilobium}!taiwanianum@\textit{taiwanianum}} 臺灣柳葉菜 \index{臺灣柳葉菜} \# VU
  \end{itemize}
 \item[] \textit{Ludwigia} 水丁香屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+adscendens}{\textit{L. adscendens} (L.) H.Hara}  \index{Ludwigia@\textit{Ludwigia}!adscendens@\textit{adscendens}} 白花水龍 \index{白花水龍}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+decurrens}{\textit{L. decurrens} Walt.}  \index{Ludwigia@\textit{Ludwigia}!decurrens@\textit{decurrens}} 翼莖水丁香 \index{翼莖水丁香}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+epilobioides}{\textit{L. epilobioides} Maxim.}  \index{Ludwigia@\textit{Ludwigia}!epilobioides@\textit{epilobioides}} 假柳葉菜 \index{假柳葉菜}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+erecta}{\textit{L. erecta} (L.) H.Hara}  \index{Ludwigia@\textit{Ludwigia}!erecta@\textit{erecta}} 美洲水丁香 \index{美洲水丁香}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+hyssopifolia}{\textit{L. hyssopifolia} (G.Don) Exell}  \index{Ludwigia@\textit{Ludwigia}!hyssopifolia@\textit{hyssopifolia}} 細葉水丁香 \index{細葉水丁香}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+octovalvis}{\textit{L. octovalvis} (Jacq.) P.H.Raven}  \index{Ludwigia@\textit{Ludwigia}!octovalvis@\textit{octovalvis}} 水丁香 \index{水丁香}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+ovalis}{\textit{L. ovalis} Miq.}  \index{Ludwigia@\textit{Ludwigia}!ovalis@\textit{ovalis}} 卵葉水丁香 \index{卵葉水丁香}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+palustris}{\textit{L. palustris} (L.) Elliott}  \index{Ludwigia@\textit{Ludwigia}!palustris@\textit{palustris}} 沼生水丁香 \index{沼生水丁香}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+perennis}{\textit{L. perennis} L.}  \index{Ludwigia@\textit{Ludwigia}!perennis@\textit{perennis}} 小花水丁香 \index{小花水丁香}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ludwigia+×taiwanensis}{\textit{L. ×taiwanensis} Peng}  \index{Ludwigia@\textit{Ludwigia}!×taiwanensis@\textit{×taiwanensis}} 臺灣水龍 \index{臺灣水龍} \# NA (H)
  \end{itemize}
 \item[] \textit{Oenothera} 待宵草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenothera+biennis}{\textit{O. biennis} L.}  \index{Oenothera@\textit{Oenothera}!biennis@\textit{biennis}} 月見草 \index{月見草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenothera+glazioviana}{\textit{O. glazioviana} Micheli}  \index{Oenothera@\textit{Oenothera}!glazioviana@\textit{glazioviana}} 黃花月見草 \index{黃花月見草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenothera+laciniata}{\textit{O. laciniata} J.Hill}  \index{Oenothera@\textit{Oenothera}!laciniata@\textit{laciniata}} 裂葉月見草 \index{裂葉月見草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenothera+stricta}{\textit{O. stricta} Ledeb. ex Link}  \index{Oenothera@\textit{Oenothera}!stricta@\textit{stricta}} 待宵草 \index{待宵草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oenothera+tetraptera}{\textit{O. tetraptera} Cav.}  \index{Oenothera@\textit{Oenothera}!tetraptera@\textit{tetraptera}} 四翅月見草 \index{四翅月見草}  NA (N)
  \end{itemize}
  \end{itemize}
