
  \begin{itemize}
 \item[] \textit{Botrychium} 陰地蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Botrychium+daucifolium}{\textit{B. daucifolium} Wall. ex Hook. \& Grev.}  \index{Botrychium@\textit{Botrychium}!daucifolium@\textit{daucifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉大陰地蕨&T2_new_value=true&fr=y}}{薄葉大陰地蕨}\index{薄葉大陰地蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Botrychium+lanuginosum}{\textit{B. lanuginosum} Wall. ex Hook. \& Grev}  \index{Botrychium@\textit{Botrychium}!lanuginosum@\textbf{\textit{lanuginosum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山蕨萁&T2_new_value=true&fr=y}}{阿里山蕨萁}\index{阿里山蕨萁@{\Song{阿里山蕨萁}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Botrychium+lunaria}{\textit{B. lunaria} (L.) Sw.}  \index{Botrychium@\textit{Botrychium}!lunaria@\textit{lunaria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=扇羽陰地蕨&T2_new_value=true&fr=y}}{扇羽陰地蕨}\index{扇羽陰地蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Botrychium+ternatum}{\textit{B. ternatum} (Thunb.) Sw.}  \index{Botrychium@\textit{Botrychium}!ternatum@\textbf{\textit{ternatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大陰地蕨&T2_new_value=true&fr=y}}{大陰地蕨}\index{大陰地蕨@{\Song{大陰地蕨}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Botrychium+virginianum}{\textit{B. virginianum} (L.) Sw.}  \index{Botrychium@\textit{Botrychium}!virginianum@\textbf{\textit{virginianum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蕨萁&T2_new_value=true&fr=y}}{蕨萁}\index{蕨萁@{\Song{蕨萁}}} EN
  \end{itemize}
 \item[] \textit{Helminthostachys} 七指蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Helminthostachys+zeylanica}{\textit{H. zeylanica} (L.) Hook.}  \index{Helminthostachys@\textit{Helminthostachys}!zeylanica@\textbf{\textit{zeylanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錫蘭七指蕨&T2_new_value=true&fr=y}}{錫蘭七指蕨}\index{錫蘭七指蕨@{\Song{錫蘭七指蕨}}} CR
  \end{itemize}
 \item[] \textit{Ophioderma} 帶狀瓶爾小草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioderma+pendula}{\textit{O. pendula} (L.) C.Presl}  \index{Ophioderma@\textit{Ophioderma}!pendula@\textit{pendula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=帶狀瓶爾小草&T2_new_value=true&fr=y}}{帶狀瓶爾小草}\index{帶狀瓶爾小草} LC
  \end{itemize}
 \item[] \textit{Ophioglossum} 瓶爾小草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioglossum+austroasiaticum}{\textit{O. austroasiaticum} M.Nishida}  \index{Ophioglossum@\textit{Ophioglossum}!austroasiaticum@\textit{austroasiaticum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山瓶爾小草&T2_new_value=true&fr=y}}{高山瓶爾小草}\index{高山瓶爾小草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioglossum+parvum}{\textit{O. parvum} M.Nishida \& Kurita}  \index{Ophioglossum@\textit{Ophioglossum}!parvum@\textit{parvum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小瓶爾小草&T2_new_value=true&fr=y}}{小瓶爾小草}\index{小瓶爾小草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioglossum+petiolatum}{\textit{O. petiolatum} Hook.}  \index{Ophioglossum@\textit{Ophioglossum}!petiolatum@\textit{petiolatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍頭瓶爾小草&T2_new_value=true&fr=y}}{鈍頭瓶爾小草}\index{鈍頭瓶爾小草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioglossum+reticulatum}{\textit{O. reticulatum} L.}  \index{Ophioglossum@\textit{Ophioglossum}!reticulatum@\textit{reticulatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=網脈瓶爾小草&T2_new_value=true&fr=y}}{網脈瓶爾小草}\index{網脈瓶爾小草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophioglossum+thermale}{\textit{O. thermale} Kom.}  \index{Ophioglossum@\textit{Ophioglossum}!thermale@\textit{thermale}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹葉瓶爾小草&T2_new_value=true&fr=y}}{狹葉瓶爾小草}\index{狹葉瓶爾小草} NT
  \end{itemize}
  \end{itemize}
