
  \begin{itemize}
 \item[] \textit{Acampe} 脆蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acampe+hayatae}{\textit{A. hayatae} Schltr.}  \index{Acampe@\textit{Acampe}!hayatae@\textit{hayatae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣肉蘭&T2_new_value=true&fr=y}}{臺灣肉蘭}\index{臺灣肉蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acampe+rigida}{\textit{A. rigida} (Buch.-Ham ex Sm.) Hunt}  \index{Acampe@\textit{Acampe}!rigida@\textit{rigida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蕉蘭&T2_new_value=true&fr=y}}{蕉蘭}\index{蕉蘭} LC
  \end{itemize}
 \item[] \textit{Acanthephippium} 罈花蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acanthephippium+pictum}{\textit{A. pictum} Fukuyama}  \index{Acanthephippium@\textit{Acanthephippium}!pictum@\textbf{\textit{pictum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=延齡罈花蘭&T2_new_value=true&fr=y}}{延齡罈花蘭}\index{延齡罈花蘭@{\Song{延齡罈花蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acanthephippium+striatum}{\textit{A. striatum} Lindl.}  \index{Acanthephippium@\textit{Acanthephippium}!striatum@\textit{striatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=一葉罈花蘭&T2_new_value=true&fr=y}}{一葉罈花蘭}\index{一葉罈花蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acanthephippium+sylhetense}{\textit{A. sylhetense} Lindl.}  \index{Acanthephippium@\textit{Acanthephippium}!sylhetense@\textit{sylhetense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=罈花蘭&T2_new_value=true&fr=y}}{罈花蘭}\index{罈花蘭} LC
  \end{itemize}
 \item[] \textit{Aeridostachya} 絨蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeridostachya+robusta}{\textit{A. robusta} (Blume) Brieger}  \index{Aeridostachya@\textit{Aeridostachya}!robusta@\textbf{\textit{robusta}}}  \index{Eria@\textit{Eria}!robusta@\textit{robusta}{\\\noindent(= \textit{Aeridostachya robusta})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細花絨蘭&T2_new_value=true&fr=y}}{細花絨蘭}\index{細花絨蘭@{\Song{細花絨蘭}}} CR
  \end{itemize}
 \item[] \textit{Agrostophyllum} 糠穗蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agrostophyllum+formosanum}{\textit{A. formosanum} Rolfe}  \index{Agrostophyllum@\textit{Agrostophyllum}!formosanum@\textbf{\textit{formosanum}}}  \index{Agrostophyllum@\textit{Agrostophyllum}!inocephalum@\textit{inocephalum}{\\\noindent(= \textit{Agrostophyllum formosanum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣禾葉蘭&T2_new_value=true&fr=y}}{臺灣禾葉蘭}\index{臺灣禾葉蘭@{\Song{臺灣禾葉蘭}}} CR
  \end{itemize}
 \item[] \textit{Amitostigma} 雛蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amitostigma+alpestre}{\textit{A. alpestre} Fukuy.}  \index{Amitostigma@\textit{Amitostigma}!alpestre@\textit{alpestre}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖雛蘭&T2_new_value=true&fr=y}}{南湖雛蘭}\index{南湖雛蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Amitostigma+gracile}{\textit{A. gracile} (Blume) Schltr.}  \index{Amitostigma@\textit{Amitostigma}!gracile@\textit{gracile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小雛蘭&T2_new_value=true&fr=y}}{小雛蘭}\index{小雛蘭} NT
  \end{itemize}
 \item[] \textit{Androcorys} 兜蕊蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Androcorys+pusillus}{\textit{A. pusillus} (Ohwi \& Fukuy.) Masam.}  \index{Androcorys@\textit{Androcorys}!pusillus@\textit{pusillus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小兜蕊蘭&T2_new_value=true&fr=y}}{小兜蕊蘭}\index{小兜蕊蘭} LC
  \end{itemize}
 \item[] \textit{Ania} 安蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ania+penangiana}{\textit{A. penangiana} (Hook.f.) Summerh.}  \index{Ania@\textit{Ania}!penangiana@\textit{penangiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠花安蘭&T2_new_value=true&fr=y}}{綠花安蘭}\index{綠花安蘭} NT
  \end{itemize}
 \item[] \textit{Anoectochilus} 金線蓮屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anoectochilus+formosanus}{\textit{A. formosanus} Hayata}  \index{Anoectochilus@\textit{Anoectochilus}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣金線蓮&T2_new_value=true&fr=y}}{臺灣金線蓮}\index{臺灣金線蓮}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anoectochilus+koshunensis}{\textit{A. koshunensis} Hayata}  \index{Anoectochilus@\textit{Anoectochilus}!koshunensis@\textit{koshunensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春金線蓮&T2_new_value=true&fr=y}}{恆春金線蓮}\index{恆春金線蓮}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anoectochilus+semiresupinata}{\textit{A. semiresupinata} T.C.Hsu \& S.W.Chung}  \index{Anoectochilus@\textit{Anoectochilus}!semiresupinata@\textit{semiresupinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=半轉位金線蓮&T2_new_value=true&fr=y}}{半轉位金線蓮}\index{半轉位金線蓮} LC
  \end{itemize}
 \item[] \textit{Aphyllorchis} 無葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aphyllorchis+montana}{\textit{A. montana} (Thw.) Rchb.f.}  \index{Aphyllorchis@\textit{Aphyllorchis}!montana@\textit{montana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山林無葉蘭&T2_new_value=true&fr=y}}{山林無葉蘭}\index{山林無葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aphyllorchis+montana+var.+membranacea}{\textit{A. montana} Rchb.f. var. \textit{membranacea} T.C.Hsu}  \index{Aphyllorchis@\textit{Aphyllorchis}!montana@\textit{montana}!var. membranacea@var. \textit{membranacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄唇無葉蘭&T2_new_value=true&fr=y}}{薄唇無葉蘭}\index{薄唇無葉蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aphyllorchis+simplex}{\textit{A. simplex} Tang \& F.T.Wang}  \index{Aphyllorchis@\textit{Aphyllorchis}!simplex@\textit{simplex}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓瓣無葉蘭&T2_new_value=true&fr=y}}{圓瓣無葉蘭}\index{圓瓣無葉蘭} DD
  \end{itemize}
 \item[] \textit{Appendicula} 竹節蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Appendicula+fenixii}{\textit{A. fenixii} (Ames) Schltr.}  \index{Appendicula@\textit{Appendicula}!fenixii@\textit{fenixii}}  \index{Appendicula@\textit{Appendicula}!terrestris@\textit{terrestris}{\\\noindent(= \textit{Appendicula fenixii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉竹節蘭&T2_new_value=true&fr=y}}{長葉竹節蘭}\index{長葉竹節蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Appendicula+kotoensis}{\textit{A. kotoensis} Hayata}  \index{Appendicula@\textit{Appendicula}!kotoensis@\textbf{\textit{kotoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼竹節蘭&T2_new_value=true&fr=y}}{蘭嶼竹節蘭}\index{蘭嶼竹節蘭@{\Song{蘭嶼竹節蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Appendicula+lucbanensis}{\textit{A. lucbanensis} (Ames) Ames}  \index{Appendicula@\textit{Appendicula}!lucbanensis@\textbf{\textit{lucbanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多枝竹節蘭&T2_new_value=true&fr=y}}{多枝竹節蘭}\index{多枝竹節蘭@{\Song{多枝竹節蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Appendicula+reflexa}{\textit{A. reflexa} Blume}  \index{Appendicula@\textit{Appendicula}!reflexa@\textit{reflexa}}  \index{Appendicula@\textit{Appendicula}!formosana@\textit{formosana}{\\\noindent(= \textit{Appendicula reflexa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣竹葉蘭&T2_new_value=true&fr=y}}{臺灣竹葉蘭}\index{臺灣竹葉蘭}\# LC
  \end{itemize}
 \item[] \textit{Arachnis} 龍爪蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arachnis+labrosa}{\textit{A. labrosa} (Lindl. \& Paxt.) Rchb.f.}  \index{Arachnis@\textit{Arachnis}!labrosa@\textit{labrosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=龍爪蘭&T2_new_value=true&fr=y}}{龍爪蘭}\index{龍爪蘭} LC
  \end{itemize}
 \item[] \textit{Arundina} 竹葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Arundina+graminifolia}{\textit{A. graminifolia} (D.Don) Hochr.}  \index{Arundina@\textit{Arundina}!graminifolia@\textbf{\textit{graminifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葦草蘭&T2_new_value=true&fr=y}}{葦草蘭}\index{葦草蘭@{\Song{葦草蘭}}} CR
  \end{itemize}
 \item[] \textit{Bletilla} 白及屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bletilla+formosana}{\textit{B. formosana} (Hayata) Schltr.}  \index{Bletilla@\textit{Bletilla}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣白及&T2_new_value=true&fr=y}}{臺灣白及}\index{臺灣白及} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bletilla+formosana+ f. +kotoensis}{\textit{B. formosana} (Hayata) Schltr.  f.  \textit{kotoensis} (Hayata) T.P.Lin}  \index{Bletilla@\textit{Bletilla}!formosana@\textit{formosana}!f. kotoensis@f. \textit{kotoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼白及&T2_new_value=true&fr=y}}{蘭嶼白及}\index{蘭嶼白及} NA$^f$
  \end{itemize}
 \item[] \textit{Brachycorythis} 苞葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Brachycorythis+galeandra}{\textit{B. galeandra} (Rchb.f.) Summerh.}  \index{Brachycorythis@\textit{Brachycorythis}!galeandra@\textbf{\textit{galeandra}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬唇苞葉蘭&T2_new_value=true&fr=y}}{寬唇苞葉蘭}\index{寬唇苞葉蘭@{\Song{寬唇苞葉蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Brachycorythis+peitawuensis}{\textit{B. peitawuensis} T.P.Lin \& W.M.Lin}  \index{Brachycorythis@\textit{Brachycorythis}!peitawuensis@\textit{peitawuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=北大武苞葉蘭&T2_new_value=true&fr=y}}{北大武苞葉蘭}\index{北大武苞葉蘭}\# DD
  \end{itemize}
 \item[] \textit{Bulbophyllum} 豆蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+affine}{\textit{B. affine} Lindl.}  \index{Bulbophyllum@\textit{Bulbophyllum}!affine@\textit{affine}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紋星蘭&T2_new_value=true&fr=y}}{紋星蘭}\index{紋星蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+albociliatum+var.+albociliatum}{\textit{B. albociliatum} (T.S.Liu \& H.J.Su) K.Nakaj. var. \textit{albociliatum}}  \index{Bulbophyllum@\textit{Bulbophyllum}!albociliatum@\textit{albociliatum}!var. albociliatum@var. \textit{albociliatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白毛捲瓣蘭&T2_new_value=true&fr=y}}{白毛捲瓣蘭}\index{白毛捲瓣蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+albociliatum+var.+shanlinshiense}{\textit{B. albociliatum} (T.S.Liu \& H.J.Su) K.Nakaj. var. \textit{shanlinshiense} T.P.Lin \& Y.N.Chang}  \index{Bulbophyllum@\textit{Bulbophyllum}!albociliatum@\textit{albociliatum}!var. shanlinshiense@var. \textit{shanlinshiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杉林溪捲瓣蘭&T2_new_value=true&fr=y}}{杉林溪捲瓣蘭}\index{杉林溪捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+aureolabellum}{\textit{B. aureolabellum} T.P.Lin}  \index{Bulbophyllum@\textit{Bulbophyllum}!aureolabellum@\textit{aureolabellum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小豆蘭&T2_new_value=true&fr=y}}{小豆蘭}\index{小豆蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+brevipedunculatum}{\textit{B. brevipedunculatum} T.C.Hsu \& S.W.Chung}  \index{Bulbophyllum@\textit{Bulbophyllum}!brevipedunculatum@\textbf{\textit{brevipedunculatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短梗豆蘭&T2_new_value=true&fr=y}}{短梗豆蘭}\index{短梗豆蘭@{\Song{短梗豆蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+ciliisepalum}{\textit{B. ciliisepalum} T.C.Hsu \& S.W.Chung}  \index{Bulbophyllum@\textit{Bulbophyllum}!ciliisepalum@\textbf{\textit{ciliisepalum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛緣萼豆蘭&T2_new_value=true&fr=y}}{毛緣萼豆蘭}\index{毛緣萼豆蘭@{\Song{毛緣萼豆蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+confragosum}{\textit{B. confragosum} T.P.Lin \& Y.N.Chang}  \index{Bulbophyllum@\textit{Bulbophyllum}!confragosum@\textit{confragosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斷尾捲瓣蘭&T2_new_value=true&fr=y}}{斷尾捲瓣蘭}\index{斷尾捲瓣蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+drymoglossum}{\textit{B. drymoglossum} Maxim. ex Okubo}  \index{Bulbophyllum@\textit{Bulbophyllum}!drymoglossum@\textit{drymoglossum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹萼豆蘭&T2_new_value=true&fr=y}}{狹萼豆蘭}\index{狹萼豆蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+electrinum+var.+calvum}{\textit{B. electrinum} Seidenf. var. \textit{calvum} T.P.Lin \& W.M.Lin}  \index{Bulbophyllum@\textit{Bulbophyllum}!electrinum@\textit{electrinum}!var. calvum@var. \textit{calvum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無毛捲瓣蘭&T2_new_value=true&fr=y}}{無毛捲瓣蘭}\index{無毛捲瓣蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+fimbriperianthium}{\textit{B. fimbriperianthium} W.M.Lin, T.P.Lin \& Kuo Huang}  \index{Bulbophyllum@\textit{Bulbophyllum}!fimbriperianthium@\textbf{\textit{fimbriperianthium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=流蘇豆蘭&T2_new_value=true&fr=y}}{流蘇豆蘭}\index{流蘇豆蘭@{\Song{流蘇豆蘭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+flaviflorum}{\textit{B. flaviflorum} (T.S.Liu \& H.J.Su) Seidenf.}  \index{Bulbophyllum@\textit{Bulbophyllum}!flaviflorum@\textit{flaviflorum}}  \index{Bulbophyllum@\textit{Bulbophyllum}!pectenveneris@\textit{pectenveneris}{\\\noindent(= \textit{Bulbophyllum flaviflorum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花捲瓣蘭&T2_new_value=true&fr=y}}{黃花捲瓣蘭}\index{黃花捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+griffithii}{\textit{B. griffithii} (Lindl.) Rchb.f.}  \index{Bulbophyllum@\textit{Bulbophyllum}!griffithii@\textbf{\textit{griffithii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=溪頭豆蘭&T2_new_value=true&fr=y}}{溪頭豆蘭}\index{溪頭豆蘭@{\Song{溪頭豆蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+hymenanthum}{\textit{B. hymenanthum} Hook.f.}  \index{Bulbophyllum@\textit{Bulbophyllum}!hymenanthum@\textit{hymenanthum}}  \index{Bulbophyllum@\textit{Bulbophyllum}!tenuislinguae@\textit{tenuislinguae}{\\\noindent(= \textit{Bulbophyllum hymenanthum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓唇雙花豆蘭&T2_new_value=true&fr=y}}{圓唇雙花豆蘭(金枝雙花豆蘭)} \index{圓唇雙花豆蘭} \index{金枝雙花豆蘭@{金枝雙花豆蘭(=圓唇雙花豆蘭)}} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+insulsoides}{\textit{B. insulsoides} Seidenf.}  \index{Bulbophyllum@\textit{Bulbophyllum}!insulsoides@\textit{insulsoides}}  \index{Bulbophyllum@\textit{Bulbophyllum}!insulsum@\textit{insulsum}{\\\noindent(= \textit{Bulbophyllum insulsoides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=穗花捲瓣蘭&T2_new_value=true&fr=y}}{穗花捲瓣蘭}\index{穗花捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+japonicum}{\textit{B. japonicum} (Makino) Makino}  \index{Bulbophyllum@\textit{Bulbophyllum}!japonicum@\textit{japonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本捲瓣蘭&T2_new_value=true&fr=y}}{日本捲瓣蘭}\index{日本捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+karenkoense}{\textit{B. karenkoense} T.P.Lin}  \index{Bulbophyllum@\textit{Bulbophyllum}!karenkoense@\textit{karenkoense}}  \index{Bulbophyllum@\textit{Bulbophyllum}!hirundinis@\textit{hirundinis}!var. puniceum@var. \textit{puniceum}{\\\noindent(=\textit{Bulbophyllum karenkoense})}}   \index{Bulbophyllum@\textit{Bulbophyllum}!hirundinis@\textit{hirundinis}{\\\noindent(= \textit{Bulbophyllum karenkoense})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=花蓮捲瓣蘭&T2_new_value=true&fr=y}}{花蓮捲瓣蘭(張氏捲瓣蘭)} \index{花蓮捲瓣蘭} \index{張氏捲瓣蘭@{張氏捲瓣蘭(=花蓮捲瓣蘭)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+kuanwuense+var.+kuanwuense}{\textit{B. kuanwuense} S.W.Chung \& T.C.Hsu var. \textit{kuanwuense}}  \index{Bulbophyllum@\textit{Bulbophyllum}!kuanwuense@\textit{kuanwuense}!var. kuanwuense@\textbf{var. \textit{kuanwuense}}}  \index{Bulbophyllum@\textit{Bulbophyllum}!kuanwuensis@\textit{kuanwuensis}!var. luchuensis@var. \textit{luchuensis}{\\\noindent(=\textit{Bulbophyllum kuanwuense} var. \textit{kuanwuense})}}   \index{Bulbophyllum@\textit{Bulbophyllum}!kuanwuensis@\textit{kuanwuensis}!var. rutilum@var. \textit{rutilum}{\\\noindent(=\textit{Bulbophyllum kuanwuense} var. \textit{kuanwuense})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=觀霧豆蘭&T2_new_value=true&fr=y}}{觀霧豆蘭(克森豆蘭、石仙桃豆蘭)} \index{觀霧豆蘭@{\Song{觀霧豆蘭}}} \index{克森豆蘭@{\Song{克森豆蘭(=觀霧豆蘭)}}} \index{石仙桃豆蘭@{\Song{石仙桃豆蘭(=觀霧豆蘭)}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+kuanwuense+var.+peitawuense}{\textit{B. kuanwuense} S.W.Chung \& T.C.Hsu var. \textit{peitawuense} T.C.Hsu}  \index{Bulbophyllum@\textit{Bulbophyllum}!kuanwuense@\textit{kuanwuense}!var. peitawuense@var. \textit{peitawuense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=北大武豆蘭&T2_new_value=true&fr=y}}{北大武豆蘭}\index{北大武豆蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+macraei}{\textit{B. macraei} (Lindl.) Rchb.f.}  \index{Bulbophyllum@\textit{Bulbophyllum}!macraei@\textit{macraei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來捲瓣蘭&T2_new_value=true&fr=y}}{烏來捲瓣蘭}\index{烏來捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+melanoglossum}{\textit{B. melanoglossum} Hayata}  \index{Bulbophyllum@\textit{Bulbophyllum}!melanoglossum@\textit{melanoglossum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫紋捲瓣蘭&T2_new_value=true&fr=y}}{紫紋捲瓣蘭}\index{紫紋捲瓣蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+omerandrum}{\textit{B. omerandrum} Hayata}  \index{Bulbophyllum@\textit{Bulbophyllum}!omerandrum@\textit{omerandrum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛藥捲瓣蘭&T2_new_value=true&fr=y}}{毛藥捲瓣蘭}\index{毛藥捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+pauciflorum}{\textit{B. pauciflorum} Anes}  \index{Bulbophyllum@\textit{Bulbophyllum}!pauciflorum@\textbf{\textit{pauciflorum}}}  \index{Bulbophyllum@\textit{Bulbophyllum}!riyanum@\textit{riyanum}{\\\noindent(= \textit{Bulbophyllum pauciflorum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花豆蘭&T2_new_value=true&fr=y}}{白花豆蘭}\index{白花豆蘭@{\Song{白花豆蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+pectinatum}{\textit{B. pectinatum} Finet}  \index{Bulbophyllum@\textit{Bulbophyllum}!pectinatum@\textit{pectinatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山豆蘭&T2_new_value=true&fr=y}}{阿里山豆蘭}\index{阿里山豆蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+pingtungensis}{\textit{B. pingtungensis} S.S.Ying}  \index{Bulbophyllum@\textit{Bulbophyllum}!pingtungensis@\textbf{\textit{pingtungensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花豆蘭&T2_new_value=true&fr=y}}{大花豆蘭}\index{大花豆蘭@{\Song{大花豆蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+remotifolium}{\textit{B. remotifolium} (Fukuy.) K.Nakaj.}  \index{Bulbophyllum@\textit{Bulbophyllum}!remotifolium@\textit{remotifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=間距捲瓣蘭&T2_new_value=true&fr=y}}{間距捲瓣蘭}\index{間距捲瓣蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+retusiusculum}{\textit{B. retusiusculum} Rchb.f.}  \index{Bulbophyllum@\textit{Bulbophyllum}!retusiusculum@\textit{retusiusculum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃萼捲瓣蘭&T2_new_value=true&fr=y}}{黃萼捲瓣蘭}\index{黃萼捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+rubrolabellum}{\textit{B. rubrolabellum} T.P.Lin}  \index{Bulbophyllum@\textit{Bulbophyllum}!rubrolabellum@\textbf{\textit{rubrolabellum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅心豆蘭&T2_new_value=true&fr=y}}{紅心豆蘭}\index{紅心豆蘭@{\Song{紅心豆蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+sasakii}{\textit{B. sasakii} (Hayata) J.J.Verm., A.Schuit. \& de Vogel}  \index{Bulbophyllum@\textit{Bulbophyllum}!sasakii@\textit{sasakii}}  \index{Sunipia@\textit{Sunipia}!andersonii@\textit{andersonii}{\\\noindent(= \textit{Bulbophyllum sasakii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠花寶石蘭&T2_new_value=true&fr=y}}{綠花寶石蘭}\index{綠花寶石蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+setaceum+var.+pilusiense}{\textit{B. setaceum} T.P.Lin var. \textit{pilusiense} T.C.Hsu}  \index{Bulbophyllum@\textit{Bulbophyllum}!setaceum@\textit{setaceum}!var. pilusiense@var. \textit{pilusiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=畢祿溪豆蘭&T2_new_value=true&fr=y}}{畢祿溪豆蘭}\index{畢祿溪豆蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+setaceum+var.+setaceum}{\textit{B. setaceum} T.P.Lin var. \textit{setaceum}}  \index{Bulbophyllum@\textit{Bulbophyllum}!setaceum@\textit{setaceum}!var. setaceum@var. \textit{setaceum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鸛冠蘭&T2_new_value=true&fr=y}}{鸛冠蘭}\index{鸛冠蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+sui}{\textit{B. sui} (T.P.Lin \& W.M.Lin) T.C.Hsu}  \index{Bulbophyllum@\textit{Bulbophyllum}!sui@\textbf{\textit{sui}}}  \index{Bulbophyllum@\textit{Bulbophyllum}!electrinum@\textit{electrinum}!var. sui@var. \textit{sui}{\\\noindent(=\textit{Bulbophyllum sui})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長軸捲瓣蘭&T2_new_value=true&fr=y}}{長軸捲瓣蘭}\index{長軸捲瓣蘭@{\Song{長軸捲瓣蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+taiwanense}{\textit{B. taiwanense} (Fukuy.) K.Nakaj.}  \index{Bulbophyllum@\textit{Bulbophyllum}!taiwanense@\textit{taiwanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣捲瓣蘭&T2_new_value=true&fr=y}}{臺灣捲瓣蘭}\index{臺灣捲瓣蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+tokioi}{\textit{B. tokioi} Fukuy.}  \index{Bulbophyllum@\textit{Bulbophyllum}!tokioi@\textit{tokioi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉豆蘭&T2_new_value=true&fr=y}}{小葉豆蘭}\index{小葉豆蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+umbellatum}{\textit{B. umbellatum} Lindl.}  \index{Bulbophyllum@\textit{Bulbophyllum}!umbellatum@\textit{umbellatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=傘花捲瓣蘭&T2_new_value=true&fr=y}}{傘花捲瓣蘭}\index{傘花捲瓣蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bulbophyllum+weiminianum}{\textit{B. weiminianum} (T.P.Lin \& Kuo Huang) T.C.Hsu}  \index{Bulbophyllum@\textit{Bulbophyllum}!weiminianum@\textbf{\textit{weiminianum}}}  \index{Bulbophyllum@\textit{Bulbophyllum}!albociliatum@\textit{albociliatum}!var. weiminianum@var. \textit{weiminianum}{\\\noindent(=\textit{Bulbophyllum weiminianum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=維明豆蘭&T2_new_value=true&fr=y}}{維明豆蘭}\index{維明豆蘭@{\Song{維明豆蘭}}}\# VU
  \end{itemize}
 \item[] \textit{Calanthe} 根節蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+alismifolia}{\textit{C. alismifolia} Lindl.}  \index{Calanthe@\textit{Calanthe}!alismifolia@\textit{alismifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細點根節蘭&T2_new_value=true&fr=y}}{細點根節蘭}\index{細點根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+alpina}{\textit{C. alpina} Hook.f. ex Lindl.}  \index{Calanthe@\textit{Calanthe}!alpina@\textbf{\textit{alpina}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽唇根節蘭&T2_new_value=true&fr=y}}{羽唇根節蘭}\index{羽唇根節蘭@{\Song{羽唇根節蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+arcuata}{\textit{C. arcuata} Rolfe}  \index{Calanthe@\textit{Calanthe}!arcuata@\textit{arcuata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾唇根節蘭&T2_new_value=true&fr=y}}{尾唇根節蘭}\index{尾唇根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+arisanensis}{\textit{C. arisanensis} Hayata}  \index{Calanthe@\textit{Calanthe}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山根節蘭&T2_new_value=true&fr=y}}{阿里山根節蘭}\index{阿里山根節蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+aristullifera}{\textit{C. aristullifera} Rchb.f.}  \index{Calanthe@\textit{Calanthe}!aristullifera@\textit{aristullifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翹距根節蘭&T2_new_value=true&fr=y}}{翹距根節蘭}\index{翹距根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+brevicolumna}{\textit{C. brevicolumna} Hayata}  \index{Calanthe@\textit{Calanthe}!brevicolumna@\textit{brevicolumna}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短柱根節蘭&T2_new_value=true&fr=y}}{短柱根節蘭}\index{短柱根節蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+clavata}{\textit{C. clavata} Lindl.}  \index{Calanthe@\textit{Calanthe}!clavata@\textit{clavata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=棒距根節蘭&T2_new_value=true&fr=y}}{棒距根節蘭}\index{棒距根節蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+davidii+var.+davidii}{\textit{C. davidii} Franch. var. \textit{davidii}}  \index{Calanthe@\textit{Calanthe}!davidii@\textit{davidii}!var. davidii@var. \textit{davidii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉根節蘭&T2_new_value=true&fr=y}}{長葉根節蘭}\index{長葉根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+davidii+var.+matsudae}{\textit{C. davidii} Franch. var. \textit{matsudae} (Hayata) T.C.Hsu}  \index{Calanthe@\textit{Calanthe}!davidii@\textit{davidii}!var. matsudae@var. \textit{matsudae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=松田氏根節蘭&T2_new_value=true&fr=y}}{松田氏根節蘭}\index{松田氏根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+graciliflora}{\textit{C. graciliflora} Hayata}  \index{Calanthe@\textit{Calanthe}!graciliflora@\textit{graciliflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細花根節蘭&T2_new_value=true&fr=y}}{細花根節蘭}\index{細花根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+kinabaluensis}{\textit{C. kinabaluensis} Rolfe}  \index{Calanthe@\textit{Calanthe}!kinabaluensis@\textit{kinabaluensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃翹距根節蘭&T2_new_value=true&fr=y}}{黃翹距根節蘭}\index{黃翹距根節蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+masuca}{\textit{C. masuca} (D.Don) Lindl.}  \index{Calanthe@\textit{Calanthe}!masuca@\textit{masuca}}  \index{Calanthe@\textit{Calanthe}!sylvatica@\textit{sylvatica}{\\\noindent(= \textit{Calanthe masuca})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長距根節蘭&T2_new_value=true&fr=y}}{長距根節蘭}\index{長距根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+puberula}{\textit{C. puberula} Lindl.}  \index{Calanthe@\textit{Calanthe}!puberula@\textit{puberula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=反捲根節蘭&T2_new_value=true&fr=y}}{反捲根節蘭}\index{反捲根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+striata}{\textit{C. striata} R.Br. ex Lindl.}  \index{Calanthe@\textit{Calanthe}!striata@\textit{striata}}  \index{Calanthe@\textit{Calanthe}!sieboldii@\textit{sieboldii}{\\\noindent(= \textit{Calanthe striata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃根節蘭&T2_new_value=true&fr=y}}{黃根節蘭}\index{黃根節蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+tricarinata}{\textit{C. tricarinata} Lindl.}  \index{Calanthe@\textit{Calanthe}!tricarinata@\textit{tricarinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三板根節蘭&T2_new_value=true&fr=y}}{三板根節蘭}\index{三板根節蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+triplicata}{\textit{C. triplicata} (Willem.) Ames}  \index{Calanthe@\textit{Calanthe}!triplicata@\textit{triplicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白鶴蘭&T2_new_value=true&fr=y}}{白鶴蘭}\index{白鶴蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+×dominii}{\textit{C. ×dominii} Lindl.}  \index{Calanthe@\textit{Calanthe}!×dominii@\textit{×dominii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長距白鶴蘭&T2_new_value=true&fr=y}}{長距白鶴蘭}\index{長距白鶴蘭} NA$^h$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calanthe+×hsinchuensis}{\textit{C. ×hsinchuensis} Y.I Lee}  \index{Calanthe@\textit{Calanthe}!×hsinchuensis@\textit{×hsinchuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=新竹根節蘭&T2_new_value=true&fr=y}}{新竹根節蘭}\index{新竹根節蘭} NA$^h$
  \end{itemize}
 \item[] \textit{Cephalanthera} 金蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalanthera+alpicola}{\textit{C. alpicola} Fukuy.}  \index{Cephalanthera@\textit{Cephalanthera}!alpicola@\textit{alpicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山頭蕊蘭&T2_new_value=true&fr=y}}{高山頭蕊蘭}\index{高山頭蕊蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalanthera+erecta}{\textit{C. erecta} (Thunb.) Blume}  \index{Cephalanthera@\textit{Cephalanthera}!erecta@\textbf{\textit{erecta}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀蘭&T2_new_value=true&fr=y}}{銀蘭}\index{銀蘭@{\Song{銀蘭}}} VU
  \end{itemize}
 \item[] \textit{Cephalantheropsis} 肖頭蕊蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalantheropsis+dolichopoda}{\textit{C. dolichopoda} (Fukuy.) T.P.Lin.}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!dolichopoda@\textit{dolichopoda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花肖頭蕊蘭&T2_new_value=true&fr=y}}{白花肖頭蕊蘭}\index{白花肖頭蕊蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalantheropsis+halconensis}{\textit{C. halconensis} (Ames) S.S.Ying}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!halconensis@\textbf{\textit{halconensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉肖頭蕊蘭&T2_new_value=true&fr=y}}{細葉肖頭蕊蘭}\index{細葉肖頭蕊蘭@{\Song{細葉肖頭蕊蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalantheropsis+longipes}{\textit{C. longipes} (Hook.f.) Ormd.}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!longipes@\textit{longipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三伯肖頭蕊蘭&T2_new_value=true&fr=y}}{三伯肖頭蕊蘭}\index{三伯肖頭蕊蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalantheropsis+obcordata+var.+alboflavescens}{\textit{C. obcordata} (Lindl.) Ormerod var. \textit{alboflavescens} T.C.Hsu}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!obcordata@\textit{obcordata}!var. alboflavescens@var. \textit{alboflavescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=淺黃肖頭蕊蘭&T2_new_value=true&fr=y}}{淺黃肖頭蕊蘭}\index{淺黃肖頭蕊蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalantheropsis+obcordata+var.+obcordata}{\textit{C. obcordata} (Lindl.) Ormerod var. \textit{obcordata}}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!obcordata@\textit{obcordata}!var. obcordata@var. \textit{obcordata}}  \index{Cephalantheropsis@\textit{Cephalantheropsis}!gracilis@\textit{gracilis}{\\\noindent(= \textit{Cephalantheropsis obcordata} var. \textit{obcordata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠花肖頭蕊蘭&T2_new_value=true&fr=y}}{綠花肖頭蕊蘭}\index{綠花肖頭蕊蘭} LC
  \end{itemize}
 \item[] \textit{Cheirostylis} 指柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+chinensis}{\textit{C. chinensis} Rolfe}  \index{Cheirostylis@\textit{Cheirostylis}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中國指柱蘭&T2_new_value=true&fr=y}}{中國指柱蘭}\index{中國指柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+clibborndyeri}{\textit{C. clibborndyeri} S.Y.Hu \& Barretto}  \index{Cheirostylis@\textit{Cheirostylis}!clibborndyeri@\textit{clibborndyeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斑葉指柱蘭&T2_new_value=true&fr=y}}{斑葉指柱蘭}\index{斑葉指柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+cochinchinensis}{\textit{C. cochinchinensis} Blume}  \index{Cheirostylis@\textit{Cheirostylis}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雉尾指柱蘭&T2_new_value=true&fr=y}}{雉尾指柱蘭}\index{雉尾指柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+derchiensis}{\textit{C. derchiensis} S.S.Ying}  \index{Cheirostylis@\textit{Cheirostylis}!derchiensis@\textit{derchiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=德基指柱蘭&T2_new_value=true&fr=y}}{德基指柱蘭}\index{德基指柱蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+liukiuensis}{\textit{C. liukiuensis} Masam.}  \index{Cheirostylis@\textit{Cheirostylis}!liukiuensis@\textit{liukiuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球指柱蘭&T2_new_value=true&fr=y}}{琉球指柱蘭}\index{琉球指柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+nantouensis}{\textit{C. nantouensis} T.P.Lin}  \index{Cheirostylis@\textit{Cheirostylis}!nantouensis@\textit{nantouensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投指柱蘭&T2_new_value=true&fr=y}}{南投指柱蘭}\index{南投指柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+octodactyla}{\textit{C. octodactyla} Ames}  \index{Cheirostylis@\textit{Cheirostylis}!octodactyla@\textit{octodactyla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽唇指柱蘭&T2_new_value=true&fr=y}}{羽唇指柱蘭}\index{羽唇指柱蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+pusilla+var.+simplex}{\textit{C. pusilla} Lindl. var. \textit{simplex} T.P. Lin}  \index{Cheirostylis@\textit{Cheirostylis}!pusilla@\textit{pusilla}!var. simplex@\textbf{var. \textit{simplex}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=沈氏指柱蘭&T2_new_value=true&fr=y}}{沈氏指柱蘭}\index{沈氏指柱蘭@{\Song{沈氏指柱蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+rubrifolius}{\textit{C. rubrifolius} T.P.Lin \& W.M.Lin}  \index{Cheirostylis@\textit{Cheirostylis}!rubrifolius@\textit{rubrifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅衣指柱蘭&T2_new_value=true&fr=y}}{紅衣指柱蘭}\index{紅衣指柱蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+takeoi}{\textit{C. takeoi} (Hayata) Schltr.}  \index{Cheirostylis@\textit{Cheirostylis}!takeoi@\textit{takeoi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山指柱蘭&T2_new_value=true&fr=y}}{阿里山指柱蘭}\index{阿里山指柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheirostylis+tortilacinia}{\textit{C. tortilacinia} C.S.Leou}  \index{Cheirostylis@\textit{Cheirostylis}!tortilacinia@\textit{tortilacinia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=和社指柱蘭&T2_new_value=true&fr=y}}{和社指柱蘭}\index{和社指柱蘭}\# NT
  \end{itemize}
 \item[] \textit{Chiloschista} 大蜘蛛蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chiloschista+parishii}{\textit{C. parishii} Seidenf.}  \index{Chiloschista@\textit{Chiloschista}!parishii@\textbf{\textit{parishii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬囊大蜘蛛蘭&T2_new_value=true&fr=y}}{寬囊大蜘蛛蘭}\index{寬囊大蜘蛛蘭@{\Song{寬囊大蜘蛛蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chiloschista+segawae}{\textit{C. segawae} (Masam.) Masam. \& Fukuy.}  \index{Chiloschista@\textit{Chiloschista}!segawae@\textit{segawae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大蜘蛛蘭&T2_new_value=true&fr=y}}{大蜘蛛蘭}\index{大蜘蛛蘭}\# NT
  \end{itemize}
 \item[] \textit{Chrysoglossum} 金蟬蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chrysoglossum+formosanum}{\textit{C. formosanum} Hayata}  \index{Chrysoglossum@\textit{Chrysoglossum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃唇蘭&T2_new_value=true&fr=y}}{臺灣黃唇蘭}\index{臺灣黃唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chrysoglossum+ornatum}{\textit{C. ornatum} Blume}  \index{Chrysoglossum@\textit{Chrysoglossum}!ornatum@\textit{ornatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃唇蘭&T2_new_value=true&fr=y}}{黃唇蘭}\index{黃唇蘭} LC
  \end{itemize}
 \item[] \textit{Cleisostoma} 隔距蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleisostoma+paniculatum}{\textit{C. paniculatum} (Ker Gawl.) Garay}  \index{Cleisostoma@\textit{Cleisostoma}!paniculatum@\textit{paniculatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虎紋蘭&T2_new_value=true&fr=y}}{虎紋蘭}\index{虎紋蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleisostoma+uraiensis}{\textit{C. uraiensis} (Hayata) Garay \& Sweet}  \index{Cleisostoma@\textit{Cleisostoma}!uraiensis@\textbf{\textit{uraiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來閉口蘭&T2_new_value=true&fr=y}}{烏來閉口蘭}\index{烏來閉口蘭@{\Song{烏來閉口蘭}}} EN
  \end{itemize}
 \item[] \textit{Collabium} 吻蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Collabium+chinense}{\textit{C. chinense} (Rolfe) T.Tang \& F.T.Wang}  \index{Collabium@\textit{Collabium}!chinense@\textbf{\textit{chinense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柯麗白蘭&T2_new_value=true&fr=y}}{柯麗白蘭}\index{柯麗白蘭@{\Song{柯麗白蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Collabium+formosanum}{\textit{C. formosanum} Hayata}  \index{Collabium@\textit{Collabium}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣柯麗白蘭&T2_new_value=true&fr=y}}{臺灣柯麗白蘭}\index{臺灣柯麗白蘭} LC
  \end{itemize}
 \item[] \textit{Corybas} 鎧蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corybas+himalaicus}{\textit{C. himalaicus} (King \& Pantl.) Schltr.}  \index{Corybas@\textit{Corybas}!himalaicus@\textbf{\textit{himalaicus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=喜馬拉雅盔蘭&T2_new_value=true&fr=y}}{喜馬拉雅盔蘭}\index{喜馬拉雅盔蘭@{\Song{喜馬拉雅盔蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corybas+puniceus}{\textit{C. puniceus} T.P.Lin \& W.M.Lin}  \index{Corybas@\textit{Corybas}!puniceus@\textbf{\textit{puniceus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=艷紫盔蘭&T2_new_value=true&fr=y}}{艷紫盔蘭}\index{艷紫盔蘭@{\Song{艷紫盔蘭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corybas+shanlinshiensis}{\textit{C. shanlinshiensis} W.M.Lin, T.C.Hsu \& T.P.Lin}  \index{Corybas@\textit{Corybas}!shanlinshiensis@\textbf{\textit{shanlinshiensis}}}  \index{Corybas@\textit{Corybas}!taliensis@\textit{taliensis}{\\\noindent(= \textit{Corybas shanlinshiensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杉林溪盔蘭&T2_new_value=true&fr=y}}{杉林溪盔蘭}\index{杉林溪盔蘭@{\Song{杉林溪盔蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corybas+sinii}{\textit{C. sinii} T.Tang \& F.T.Wang}  \index{Corybas@\textit{Corybas}!sinii@\textbf{\textit{sinii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=辛氏盔蘭&T2_new_value=true&fr=y}}{辛氏盔蘭}\index{辛氏盔蘭@{\Song{辛氏盔蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corybas+taiwanesis}{\textit{C. taiwanesis} T.P.Lin \& S. Y. Leu}  \index{Corybas@\textit{Corybas}!taiwanesis@\textbf{\textit{taiwanesis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅盔蘭&T2_new_value=true&fr=y}}{紅盔蘭}\index{紅盔蘭@{\Song{紅盔蘭}}}\# EN
  \end{itemize}
 \item[] \textit{Corymborkis} 管花蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corymborkis+veratrifolia}{\textit{C. veratrifolia} (Reinw.) Bl.}  \index{Corymborkis@\textit{Corymborkis}!veratrifolia@\textbf{\textit{veratrifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=管花蘭&T2_new_value=true&fr=y}}{管花蘭}\index{管花蘭@{\Song{管花蘭}}} EN
  \end{itemize}
 \item[] \textit{Cremastra} 馬鞭蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cremastra+appendiculata}{\textit{C. appendiculata} (D.Don) Makino}  \index{Cremastra@\textit{Cremastra}!appendiculata@\textit{appendiculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬鞭蘭&T2_new_value=true&fr=y}}{馬鞭蘭}\index{馬鞭蘭} LC
  \end{itemize}
 \item[] \textit{Crepidium} 沼蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidium+bancanoides}{\textit{C. bancanoides} (Ames) Szlach.}  \index{Crepidium@\textit{Crepidium}!bancanoides@\textit{bancanoides}}  \index{Malaxis@\textit{Malaxis}!bancanoides@\textit{bancanoides}{\\\noindent(= \textit{Crepidium bancanoides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂唇軟葉蘭&T2_new_value=true&fr=y}}{裂唇軟葉蘭}\index{裂唇軟葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidium+matsudae}{\textit{C. matsudae} (Yamam.) Szlach.}  \index{Crepidium@\textit{Crepidium}!matsudae@\textit{matsudae}}  \index{Malaxis@\textit{Malaxis}!matsudae@\textit{matsudae}{\\\noindent(= \textit{Crepidium matsudae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹唇軟葉蘭&T2_new_value=true&fr=y}}{凹唇軟葉蘭}\index{凹唇軟葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidium+purpureum}{\textit{C. purpureum} (Lindl.) Szlach.}  \index{Crepidium@\textit{Crepidium}!purpureum@\textbf{\textit{purpureum}}}  \index{Malaxis@\textit{Malaxis}!purpurea@\textit{purpurea}{\\\noindent(= \textit{Crepidium purpureum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花軟葉蘭&T2_new_value=true&fr=y}}{紫花軟葉蘭}\index{紫花軟葉蘭@{\Song{紫花軟葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Crepidium+roohutuensis}{\textit{C. roohutuensis} (Fukuy.) T.C.Hsu}  \index{Crepidium@\textit{Crepidium}!roohutuensis@\textit{roohutuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫背小柱蘭&T2_new_value=true&fr=y}}{紫背小柱蘭}\index{紫背小柱蘭}\# LC
  \end{itemize}
 \item[] \textit{Cryptostylis} 隱柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptostylis+arachnites}{\textit{C. arachnites} (Blume) Hassk.}  \index{Cryptostylis@\textit{Cryptostylis}!arachnites@\textit{arachnites}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=滿綠隱柱蘭&T2_new_value=true&fr=y}}{滿綠隱柱蘭}\index{滿綠隱柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptostylis+taiwaniana}{\textit{C. taiwaniana} Masam.}  \index{Cryptostylis@\textit{Cryptostylis}!taiwaniana@\textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊隱柱蘭&T2_new_value=true&fr=y}}{蓬萊隱柱蘭}\index{蓬萊隱柱蘭} LC
  \end{itemize}
 \item[] \textit{Cymbidium} 蕙蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+cochleare}{\textit{C. cochleare} Lindl.}  \index{Cymbidium@\textit{Cymbidium}!cochleare@\textbf{\textit{cochleare}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香莎草蘭&T2_new_value=true&fr=y}}{香莎草蘭}\index{香莎草蘭@{\Song{香莎草蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+dayanum}{\textit{C. dayanum} Rchb.f.}  \index{Cymbidium@\textit{Cymbidium}!dayanum@\textit{dayanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鳳蘭&T2_new_value=true&fr=y}}{鳳蘭}\index{鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+ensifolium+var.+ensifolium}{\textit{C. ensifolium} (L.) Sw. var. \textit{ensifolium}}  \index{Cymbidium@\textit{Cymbidium}!ensifolium@\textit{ensifolium}!var. ensifolium@var. \textit{ensifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=建蘭&T2_new_value=true&fr=y}}{建蘭}\index{建蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+faberi}{\textit{C. faberi} Rolfe}  \index{Cymbidium@\textit{Cymbidium}!faberi@\textbf{\textit{faberi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=九華蘭&T2_new_value=true&fr=y}}{九華蘭}\index{九華蘭@{\Song{九華蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+floribundum}{\textit{C. floribundum} Lindl.}  \index{Cymbidium@\textit{Cymbidium}!floribundum@\textit{floribundum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金稜邊蘭&T2_new_value=true&fr=y}}{金稜邊蘭}\index{金稜邊蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+formosanum+var.+formosanum}{\textit{C. formosanum} Hayata var. \textit{formosanum}}  \index{Cymbidium@\textit{Cymbidium}!formosanum@\textit{formosanum}!var. formosanum@var. \textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=朵朵香&T2_new_value=true&fr=y}}{朵朵香}\index{朵朵香} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+formosanum+var.+gracillimum}{\textit{C. formosanum} Hayata var. \textit{gracillimum} (Fukuy.) T.S.Liu \& H.J.Su}  \index{Cymbidium@\textit{Cymbidium}!formosanum@\textit{formosanum}!var. gracillimum@var. \textit{gracillimum}}  \index{Cymbidium@\textit{Cymbidium}!goeringii@\textit{goeringii}!var. serratum@var. \textit{serratum}{\\\noindent(=\textit{Cymbidium formosanum} var. \textit{gracillimum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉春蘭&T2_new_value=true&fr=y}}{細葉春蘭}\index{細葉春蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+kanran}{\textit{C. kanran} Makino}  \index{Cymbidium@\textit{Cymbidium}!kanran@\textbf{\textit{kanran}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寒蘭&T2_new_value=true&fr=y}}{寒蘭}\index{寒蘭@{\Song{寒蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+lancifolium+var.+aspidistrifolium}{\textit{C. lancifolium} Hook.f. var. \textit{aspidistrifolium} (Fukuy.) S.S.Ying}  \index{Cymbidium@\textit{Cymbidium}!lancifolium@\textit{lancifolium}!var. aspidistrifolium@var. \textit{aspidistrifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠花竹柏蘭&T2_new_value=true&fr=y}}{綠花竹柏蘭}\index{綠花竹柏蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+lancifolium+var.+lancifolium}{\textit{C. lancifolium} Hook.f. var. \textit{lancifolium}}  \index{Cymbidium@\textit{Cymbidium}!lancifolium@\textit{lancifolium}!var. lancifolium@var. \textit{lancifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=竹柏蘭&T2_new_value=true&fr=y}}{竹柏蘭}\index{竹柏蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+lancifolium+var.+syunitianum}{\textit{C. lancifolium} Hook.f. var. \textit{syunitianum} (Fukuy.) S.S.Ying}  \index{Cymbidium@\textit{Cymbidium}!lancifolium@\textit{lancifolium}!var. syunitianum@var. \textit{syunitianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大竹柏蘭&T2_new_value=true&fr=y}}{大竹柏蘭}\index{大竹柏蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+macrorhizon}{\textit{C. macrorhizon} Lindl.}  \index{Cymbidium@\textit{Cymbidium}!macrorhizon@\textit{macrorhizon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大根蘭&T2_new_value=true&fr=y}}{大根蘭}\index{大根蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+sinense}{\textit{C. sinense} (Jackson ex Andr.) Willd.}  \index{Cymbidium@\textit{Cymbidium}!sinense@\textit{sinense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=報歲蘭&T2_new_value=true&fr=y}}{報歲蘭}\index{報歲蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+sinense+ f. +albo-jucundissimum}{\textit{C. sinense} (Jackson ex Andr.) Willd.  f.  \textit{albo-jucundissimum} (Hayata) Fukuy.}  \index{Cymbidium@\textit{Cymbidium}!sinense@\textit{sinense}!f. albo-jucundissimum@f. \textit{albo-jucundissimum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花報歲蘭&T2_new_value=true&fr=y}}{白花報歲蘭}\index{白花報歲蘭} NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cymbidium+tortisepalum}{\textit{C. tortisepalum} Fukuy.}  \index{Cymbidium@\textit{Cymbidium}!tortisepalum@\textit{tortisepalum}}  \index{Cymbidium@\textit{Cymbidium}!goeringii@\textit{goeringii}!var. tortisepalum@var. \textit{tortisepalum}{\\\noindent(=\textit{Cymbidium tortisepalum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菅草蘭&T2_new_value=true&fr=y}}{菅草蘭}\index{菅草蘭}\# NT
  \end{itemize}
 \item[] \textit{Cynorchis} 非洲紅蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cynorchis+fastigiata}{\textit{C. fastigiata} Thouars}  \index{Cynorchis@\textit{Cynorchis}!fastigiata@\textit{fastigiata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=非洲紅蘭&T2_new_value=true&fr=y}}{非洲紅蘭}\index{非洲紅蘭} NA$^n$
  \end{itemize}
 \item[] \textit{Cypripedium} 蘭花雙葉草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cypripedium+debile}{\textit{C. debile} Rchb.f.}  \index{Cypripedium@\textit{Cypripedium}!debile@\textit{debile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小喜普鞋蘭&T2_new_value=true&fr=y}}{小喜普鞋蘭}\index{小喜普鞋蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cypripedium+formosanum}{\textit{C. formosanum} Hayata}  \index{Cypripedium@\textit{Cypripedium}!formosanum@\textbf{\textit{formosanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣喜普鞋蘭&T2_new_value=true&fr=y}}{臺灣喜普鞋蘭}\index{臺灣喜普鞋蘭@{\Song{臺灣喜普鞋蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cypripedium+macranthos}{\textit{C. macranthos} Sw.}  \index{Cypripedium@\textit{Cypripedium}!macranthos@\textbf{\textit{macranthos}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奇萊喜普鞋蘭&T2_new_value=true&fr=y}}{奇萊喜普鞋蘭}\index{奇萊喜普鞋蘭@{\Song{奇萊喜普鞋蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cypripedium+segawae}{\textit{C. segawae} Masam.}  \index{Cypripedium@\textit{Cypripedium}!segawae@\textbf{\textit{segawae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寶島喜普鞋蘭&T2_new_value=true&fr=y}}{寶島喜普鞋蘭}\index{寶島喜普鞋蘭@{\Song{寶島喜普鞋蘭}}}\# CR
  \end{itemize}
 \item[] \textit{Cyrtosia} 肉果蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyrtosia+javanica}{\textit{C. javanica} Blume}  \index{Cyrtosia@\textit{Cyrtosia}!javanica@\textbf{\textit{javanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=肉果蘭&T2_new_value=true&fr=y}}{肉果蘭}\index{肉果蘭@{\Song{肉果蘭}}} EN
  \end{itemize}
 \item[] \textit{Dactylorhiza} 凹舌蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dactylorhiza+viridis}{\textit{D. viridis} (L.) R.M.Bateman, Pridgeon \& M.W.Chase}  \index{Dactylorhiza@\textit{Dactylorhiza}!viridis@\textit{viridis}}  \index{Coeloglossum@\textit{Coeloglossum}!viride@\textit{viride}{\\\noindent(= \textit{Dactylorhiza viridis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠花凹舌蘭&T2_new_value=true&fr=y}}{綠花凹舌蘭}\index{綠花凹舌蘭} LC
  \end{itemize}
 \item[] \textit{Dendrobium} 石斛屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+catenatum}{\textit{D. catenatum} Lindl.}  \index{Dendrobium@\textit{Dendrobium}!catenatum@\textbf{\textit{catenatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花石斛&T2_new_value=true&fr=y}}{黃花石斛}\index{黃花石斛@{\Song{黃花石斛}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+chameleon}{\textit{D. chameleon} Ames}  \index{Dendrobium@\textit{Dendrobium}!chameleon@\textit{chameleon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長距石斛&T2_new_value=true&fr=y}}{長距石斛}\index{長距石斛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+chryseum}{\textit{D. chryseum} Rolfe}  \index{Dendrobium@\textit{Dendrobium}!chryseum@\textit{chryseum}}  \index{Dendrobium@\textit{Dendrobium}!aurantiacum@\textit{aurantiacum}{\\\noindent(= \textit{Dendrobium chryseum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金草蘭&T2_new_value=true&fr=y}}{金草蘭}\index{金草蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+comatum}{\textit{D. comatum} (Blume) Lindl.}  \index{Dendrobium@\textit{Dendrobium}!comatum@\textit{comatum}}  \index{Flickingeria@\textit{Flickingeria}!comata@\textit{comata}{\\\noindent(= \textit{Dendrobium comatum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=木槲&T2_new_value=true&fr=y}}{木槲}\index{木槲} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+crumenatum}{\textit{D. crumenatum} Sw.}  \index{Dendrobium@\textit{Dendrobium}!crumenatum@\textbf{\textit{crumenatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鴿石斛&T2_new_value=true&fr=y}}{鴿石斛}\index{鴿石斛@{\Song{鴿石斛}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+equitans}{\textit{D. equitans} Kranzl.}  \index{Dendrobium@\textit{Dendrobium}!equitans@\textit{equitans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=燕子石斛&T2_new_value=true&fr=y}}{燕子石斛}\index{燕子石斛} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+falconeri}{\textit{D. falconeri} Hook.}  \index{Dendrobium@\textit{Dendrobium}!falconeri@\textit{falconeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=新竹石斛&T2_new_value=true&fr=y}}{新竹石斛}\index{新竹石斛} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+furcatopedicellatum}{\textit{D. furcatopedicellatum} Hayata}  \index{Dendrobium@\textit{Dendrobium}!furcatopedicellatum@\textbf{\textit{furcatopedicellatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙花石斛&T2_new_value=true&fr=y}}{雙花石斛}\index{雙花石斛@{\Song{雙花石斛}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+goldschmidtianum}{\textit{D. goldschmidtianum} Kranzl}  \index{Dendrobium@\textit{Dendrobium}!goldschmidtianum@\textit{goldschmidtianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花石斛&T2_new_value=true&fr=y}}{紅花石斛}\index{紅花石斛} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+leptocladum}{\textit{D. leptocladum} Hayata}  \index{Dendrobium@\textit{Dendrobium}!leptocladum@\textit{leptocladum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細莖石斛&T2_new_value=true&fr=y}}{細莖石斛}\index{細莖石斛}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+linawianum}{\textit{D. linawianum} Rchb.f.}  \index{Dendrobium@\textit{Dendrobium}!linawianum@\textbf{\textit{linawianum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=櫻石斛&T2_new_value=true&fr=y}}{櫻石斛}\index{櫻石斛@{\Song{櫻石斛}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+luzonense}{\textit{D. luzonense} Lindl.}  \index{Dendrobium@\textit{Dendrobium}!luzonense@\textbf{\textit{luzonense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=呂宋石斛&T2_new_value=true&fr=y}}{呂宋石斛}\index{呂宋石斛@{\Song{呂宋石斛}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+moniliforme}{\textit{D. moniliforme} (L.) Sw.}  \index{Dendrobium@\textit{Dendrobium}!moniliforme@\textit{moniliforme}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石斛&T2_new_value=true&fr=y}}{石斛}\index{石斛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+nakaharae}{\textit{D. nakaharae} Schltr.}  \index{Dendrobium@\textit{Dendrobium}!nakaharae@\textit{nakaharae}}  \index{Epigeneium@\textit{Epigeneium}!nakaharae@\textit{nakaharae}{\\\noindent(= \textit{Dendrobium nakaharae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蠟著頦蘭&T2_new_value=true&fr=y}}{蠟著頦蘭}\index{蠟著頦蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+nobile+var.+formosanaum}{\textit{D. nobile} Lindl. var. \textit{formosanaum} Rchb.f.}  \index{Dendrobium@\textit{Dendrobium}!nobile@\textit{nobile}!var. formosanaum@var. \textit{formosanaum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣石斛&T2_new_value=true&fr=y}}{臺灣石斛}\index{臺灣石斛}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+okinawense}{\textit{D. okinawense} Hatusima \& Ida}  \index{Dendrobium@\textit{Dendrobium}!okinawense@\textit{okinawense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球石斛&T2_new_value=true&fr=y}}{琉球石斛}\index{琉球石斛} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+parietiforme}{\textit{D. parietiforme} J.J.Sm.}  \index{Dendrobium@\textit{Dendrobium}!parietiforme@\textit{parietiforme}}  \index{Flickingeria@\textit{Flickingeria}!parietiformis@\textit{parietiformis}{\\\noindent(= \textit{Dendrobium parietiforme})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=世富暫花蘭&T2_new_value=true&fr=y}}{世富暫花蘭}\index{世富暫花蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+sanseiense}{\textit{D. sanseiense} Hayata}  \index{Dendrobium@\textit{Dendrobium}!sanseiense@\textit{sanseiense}}  \index{Epigeneium@\textit{Epigeneium}!fargesii@\textit{fargesii}{\\\noindent(= \textit{Dendrobium sanseiense})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=著頦蘭&T2_new_value=true&fr=y}}{著頦蘭}\index{著頦蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+somae}{\textit{D. somae} Hayata}  \index{Dendrobium@\textit{Dendrobium}!somae@\textbf{\textit{somae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小雙花石斛&T2_new_value=true&fr=y}}{小雙花石斛}\index{小雙花石斛@{\Song{小雙花石斛}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrobium+xantholeucum}{\textit{D. xantholeucum} Rchb.f.}  \index{Dendrobium@\textit{Dendrobium}!xantholeucum@\textit{xantholeucum}}  \index{Flickingeria@\textit{Flickingeria}!xantholeuca@\textit{xantholeuca}{\\\noindent(= \textit{Dendrobium xantholeucum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=淺黃暫花蘭&T2_new_value=true&fr=y}}{淺黃暫花蘭}\index{淺黃暫花蘭} NT
  \end{itemize}
 \item[] \textit{Dendrochilum} 穗花蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrochilum+uncatum}{\textit{D. uncatum} Rchb.f.}  \index{Dendrochilum@\textit{Dendrochilum}!uncatum@\textbf{\textit{uncatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃穗蘭&T2_new_value=true&fr=y}}{黃穗蘭}\index{黃穗蘭@{\Song{黃穗蘭}}} VU
  \end{itemize}
 \item[] \textit{Didymoplexiella} 錨柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoplexiella+siamensis}{\textit{D. siamensis} (Rolfe ex Downie) Seidenf.}  \index{Didymoplexiella@\textit{Didymoplexiella}!siamensis@\textit{siamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錨柱蘭&T2_new_value=true&fr=y}}{錨柱蘭}\index{錨柱蘭} NT
  \end{itemize}
 \item[] \textit{Didymoplexis} 雙唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoplexis+micradenia}{\textit{D. micradenia} (Rchb.f.) Hemsl.}  \index{Didymoplexis@\textit{Didymoplexis}!micradenia@\textit{micradenia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小鬼蘭&T2_new_value=true&fr=y}}{小鬼蘭}\index{小鬼蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoplexis+pallens+var.+nantouensis}{\textit{D. pallens} Griff. var. \textit{nantouensis} T.C.Hsu}  \index{Didymoplexis@\textit{Didymoplexis}!pallens@\textit{pallens}!var. nantouensis@var. \textit{nantouensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投鬼蘭&T2_new_value=true&fr=y}}{南投鬼蘭}\index{南投鬼蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Didymoplexis+pallens+var.+pallens}{\textit{D. pallens} Griff. var. \textit{pallens}}  \index{Didymoplexis@\textit{Didymoplexis}!pallens@\textit{pallens}!var. pallens@var. \textit{pallens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=吊鐘鬼蘭&T2_new_value=true&fr=y}}{吊鐘鬼蘭}\index{吊鐘鬼蘭} LC
  \end{itemize}
 \item[] \textit{Dienia} 小柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dienia+ophrydis}{\textit{D. ophrydis} (J.Koenig) Ormerod \& Seidenf.}  \index{Dienia@\textit{Dienia}!ophrydis@\textit{ophrydis}}  \index{Malaxis@\textit{Malaxis}!ophrydis@\textit{ophrydis}{\\\noindent(= \textit{Dienia ophrydis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=廣葉軟葉蘭&T2_new_value=true&fr=y}}{廣葉軟葉蘭}\index{廣葉軟葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dienia+shuicae}{\textit{D. shuicae} (S.S.Ying) T.P.Lin}  \index{Dienia@\textit{Dienia}!shuicae@\textit{shuicae}}  \index{Malaxis@\textit{Malaxis}!shampoae@\textit{shampoae}{\\\noindent(= \textit{Dienia shuicae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=壽卡小柱蘭&T2_new_value=true&fr=y}}{壽卡小柱蘭(三伯花柱蘭)} \index{壽卡小柱蘭} \index{三伯花柱蘭@{三伯花柱蘭(=壽卡小柱蘭)}} LC
  \end{itemize}
 \item[] \textit{Diploprora} 蛇舌蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diploprora+championii}{\textit{D. championii} (Lindl.) Hook.f.}  \index{Diploprora@\textit{Diploprora}!championii@\textit{championii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=倒吊蘭&T2_new_value=true&fr=y}}{倒吊蘭}\index{倒吊蘭} LC
  \end{itemize}
 \item[] \textit{Disperis} 鴛鴦蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Disperis+neilgherrensis}{\textit{D. neilgherrensis} Wight}  \index{Disperis@\textit{Disperis}!neilgherrensis@\textbf{\textit{neilgherrensis}}}  \index{Disperis@\textit{Disperis}!siamensis@\textit{siamensis}{\\\noindent(= \textit{Disperis neilgherrensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙袋蘭&T2_new_value=true&fr=y}}{雙袋蘭}\index{雙袋蘭@{\Song{雙袋蘭}}} EN
  \end{itemize}
 \item[] \textit{Epidendrum} 樹蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epidendrum+×obrienianum}{\textit{E. ×obrienianum} Rolfe}  \index{Epidendrum@\textit{Epidendrum}!×obrienianum@\textit{×obrienianum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雜交樹蘭&T2_new_value=true&fr=y}}{雜交樹蘭}\index{雜交樹蘭} NA$^h$
  \end{itemize}
 \item[] \textit{Epipactis} 鈴蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipactis+helleborine+subsp.+helleborine}{\textit{E. helleborine} (L.) Crantz subsp. \textit{helleborine}}  \index{Epipactis@\textit{Epipactis}!helleborine@\textit{helleborine}!subsp. helleborine@subsp. \textit{helleborine}}  \index{Epipactis@\textit{Epipactis}!fascicularis@\textit{fascicularis}{\\\noindent(= \textit{Epipactis helleborine} subsp. \textit{helleborine})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=余氏鈴蘭&T2_new_value=true&fr=y}}{余氏鈴蘭}\index{余氏鈴蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipactis+ohwii}{\textit{E. ohwii} Fukuy.}  \index{Epipactis@\textit{Epipactis}!ohwii@\textit{ohwii}}  \index{Epipactis@\textit{Epipactis}!helleborine@\textit{helleborine}!subsp. ohwii@subsp. \textit{ohwii}{\\\noindent(=\textit{Epipactis ohwii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鈴蘭&T2_new_value=true&fr=y}}{臺灣鈴蘭}\index{臺灣鈴蘭}\# LC
  \end{itemize}
 \item[] \textit{Epipogium} 上鬚蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipogium+aphyllum}{\textit{E. aphyllum} (F.W.Schmidt) Sw.}  \index{Epipogium@\textit{Epipogium}!aphyllum@\textit{aphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無葉上鬚蘭&T2_new_value=true&fr=y}}{無葉上鬚蘭}\index{無葉上鬚蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipogium+japonicum}{\textit{E. japonicum} Makino}  \index{Epipogium@\textit{Epipogium}!japonicum@\textit{japonicum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本上鬚蘭&T2_new_value=true&fr=y}}{日本上鬚蘭}\index{日本上鬚蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipogium+kentingensis}{\textit{E. kentingensis} T.P.Lin \& S.H.Wu}  \index{Epipogium@\textit{Epipogium}!kentingensis@\textit{kentingensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=墾丁上鬚蘭&T2_new_value=true&fr=y}}{墾丁上鬚蘭}\index{墾丁上鬚蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipogium+roseum}{\textit{E. roseum} (D.Don) Lindl.}  \index{Epipogium@\textit{Epipogium}!roseum@\textit{roseum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛上鬚蘭&T2_new_value=true&fr=y}}{高士佛上鬚蘭}\index{高士佛上鬚蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Epipogium+taiwanense}{\textit{E. taiwanense} T.C.Hsu}  \index{Epipogium@\textit{Epipogium}!taiwanense@\textit{taiwanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣上鬚蘭&T2_new_value=true&fr=y}}{臺灣上鬚蘭}\index{臺灣上鬚蘭} NT
  \end{itemize}
 \item[] \textit{Eria} 絨蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eria+corneri}{\textit{E. corneri} Rchb.f.}  \index{Eria@\textit{Eria}!corneri@\textit{corneri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃絨蘭&T2_new_value=true&fr=y}}{黃絨蘭}\index{黃絨蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eria+herklotsii}{\textit{E. herklotsii} P.J.Cribb}  \index{Eria@\textit{Eria}!herklotsii@\textbf{\textit{herklotsii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香港毛蘭&T2_new_value=true&fr=y}}{香港毛蘭}\index{香港毛蘭@{\Song{香港毛蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eria+javanica}{\textit{E. javanica} (Sw.) Blume}  \index{Eria@\textit{Eria}!javanica@\textbf{\textit{javanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉絨蘭&T2_new_value=true&fr=y}}{大葉絨蘭}\index{大葉絨蘭@{\Song{大葉絨蘭}}} CR
  \end{itemize}
 \item[] \textit{Erythrodes} 小唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrodes+blumei+var.+aggregatus}{\textit{E. blumei} (Lindl.) Schltr. var. \textit{aggregatus} T.P.Lin \& W.M.Lin}  \index{Erythrodes@\textit{Erythrodes}!blumei@\textit{blumei}!var. aggregatus@var. \textit{aggregatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花小唇蘭&T2_new_value=true&fr=y}}{密花小唇蘭}\index{密花小唇蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrodes+chinensis}{\textit{E. chinensis} (Rolfe) Schltr.}  \index{Erythrodes@\textit{Erythrodes}!chinensis@\textit{chinensis}}  \index{Erythrodes@\textit{Erythrodes}!blumei@\textit{blumei}!var. blumei@var. \textit{blumei}{\\\noindent(=\textit{Erythrodes chinensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小唇蘭&T2_new_value=true&fr=y}}{小唇蘭}\index{小唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrodes+triantherae+var.+ecalcarata}{\textit{E. triantherae} C.L.Yeh \& C.S.Leou var. \textit{ecalcarata} T.C.Hsu}  \index{Erythrodes@\textit{Erythrodes}!triantherae@\textit{triantherae}!var. ecalcarata@var. \textit{ecalcarata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無距細筆蘭&T2_new_value=true&fr=y}}{無距細筆蘭}\index{無距細筆蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrodes+triantherae+var.+triantherae}{\textit{E. triantherae} C.L.Yeh \& C.S.Leou var. \textit{triantherae}}  \index{Erythrodes@\textit{Erythrodes}!triantherae@\textit{triantherae}!var. triantherae@\textbf{var. \textit{triantherae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葯細筆蘭&T2_new_value=true&fr=y}}{三葯細筆蘭}\index{三葯細筆蘭@{\Song{三葯細筆蘭}}}\# EN
  \end{itemize}
 \item[] \textit{Erythrorchis} 倒吊蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Erythrorchis+altissima}{\textit{E. altissima} (Blume) Blume}  \index{Erythrorchis@\textit{Erythrorchis}!altissima@\textit{altissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓莖山珊瑚&T2_new_value=true&fr=y}}{蔓莖山珊瑚}\index{蔓莖山珊瑚} LC
  \end{itemize}
 \item[] \textit{Eucosia} 哥綠懷蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eucosia+cordata}{\textit{E. cordata} (Lindl.) T.C.Hsu}  \index{Eucosia@\textit{Eucosia}!cordata@\textit{cordata}}  \index{Goodyera@\textit{Goodyera}!carnea@\textit{carnea}{\\\noindent(= \textit{Eucosia cordata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=淡紅歌綠懷蘭&T2_new_value=true&fr=y}}{淡紅歌綠懷蘭(淡紅花斑葉蘭)} \index{淡紅歌綠懷蘭} \index{淡紅花斑葉蘭@{淡紅花斑葉蘭(=淡紅歌綠懷蘭)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eucosia+hengchunensis}{\textit{E. hengchunensis} T.C.Hsu}  \index{Eucosia@\textit{Eucosia}!hengchunensis@\textbf{\textit{hengchunensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春歌綠懷蘭&T2_new_value=true&fr=y}}{恆春歌綠懷蘭}\index{恆春歌綠懷蘭@{\Song{恆春歌綠懷蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eucosia+longirostrata}{\textit{E. longirostrata} (Hayata) T.C.Hsu}  \index{Eucosia@\textit{Eucosia}!longirostrata@\textit{longirostrata}}  \index{Goodyera@\textit{Goodyera}!seikoomontana@\textit{seikoomontana}{\\\noindent(= \textit{Eucosia longirostrata})}}   \index{Goodyera@\textit{Goodyera}!viridiflora@\textit{viridiflora}{\\\noindent(= \textit{Eucosia longirostrata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=歌綠懷蘭&T2_new_value=true&fr=y}}{歌綠懷蘭(綠花斑葉蘭)} \index{歌綠懷蘭} \index{綠花斑葉蘭@{綠花斑葉蘭(=歌綠懷蘭)}}\# LC
  \end{itemize}
 \item[] \textit{Eulophia} 芋蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+bicallosa}{\textit{E. bicallosa} (D.Don) P.F.Hunt \& Summerh.}  \index{Eulophia@\textit{Eulophia}!bicallosa@\textit{bicallosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寶島芋蘭&T2_new_value=true&fr=y}}{寶島芋蘭}\index{寶島芋蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+bicarinata}{\textit{E. bicarinata} (Lindl.) Hook.f.}  \index{Eulophia@\textit{Eulophia}!bicarinata@\textit{bicarinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉芋蘭&T2_new_value=true&fr=y}}{闊葉芋蘭}\index{闊葉芋蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+brachycentra}{\textit{E. brachycentra} Hayata}  \index{Eulophia@\textit{Eulophia}!brachycentra@\textit{brachycentra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短裂芋蘭&T2_new_value=true&fr=y}}{短裂芋蘭}\index{短裂芋蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+dentata}{\textit{E. dentata} Ames}  \index{Eulophia@\textit{Eulophia}!dentata@\textit{dentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫芋蘭&T2_new_value=true&fr=y}}{紫芋蘭}\index{紫芋蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+graminea}{\textit{E. graminea} Lindl.}  \index{Eulophia@\textit{Eulophia}!graminea@\textit{graminea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=禾草芋蘭&T2_new_value=true&fr=y}}{禾草芋蘭}\index{禾草芋蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+pelorica}{\textit{E. pelorica} Jones \& Clem.}  \index{Eulophia@\textit{Eulophia}!pelorica@\textit{pelorica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=輻射芋蘭&T2_new_value=true&fr=y}}{輻射芋蘭}\index{輻射芋蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+segawae}{\textit{E. segawae} Fukuy.}  \index{Eulophia@\textit{Eulophia}!segawae@\textit{segawae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瀨川氏芋蘭&T2_new_value=true&fr=y}}{瀨川氏芋蘭}\index{瀨川氏芋蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eulophia+zollingeri}{\textit{E. zollingeri} (Rchb.f.) J.J.Sm.}  \index{Eulophia@\textit{Eulophia}!zollingeri@\textit{zollingeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山芋蘭&T2_new_value=true&fr=y}}{山芋蘭}\index{山芋蘭} LC
  \end{itemize}
 \item[] \textit{Flickingeria} 暫花蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flickingeria+tairukounia}{\textit{F. tairukounia} (S.S.Ying) T.P.Lin}  \index{Flickingeria@\textit{Flickingeria}!tairukounia@\textit{tairukounia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=輻射暫花蘭&T2_new_value=true&fr=y}}{輻射暫花蘭}\index{輻射暫花蘭}\# DD
  \end{itemize}
 \item[] \textit{Galeola} 山珊瑚屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galeola+falconeri}{\textit{G. falconeri} Hook.f.}  \index{Galeola@\textit{Galeola}!falconeri@\textit{falconeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小囊山珊瑚&T2_new_value=true&fr=y}}{小囊山珊瑚}\index{小囊山珊瑚} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galeola+lindleyana}{\textit{G. lindleyana} (Hook.f. \& Thoms.) Rchb.f.}  \index{Galeola@\textit{Galeola}!lindleyana@\textit{lindleyana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山珊瑚&T2_new_value=true&fr=y}}{山珊瑚}\index{山珊瑚} LC
  \end{itemize}
 \item[] \textit{Gastrochilus} 松蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+ciliaris}{\textit{G. ciliaris} F.Maek.}  \index{Gastrochilus@\textit{Gastrochilus}!ciliaris@\textit{ciliaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=緣毛松蘭&T2_new_value=true&fr=y}}{緣毛松蘭}\index{緣毛松蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+formosanus}{\textit{G. formosanus} (Hayata) Hayata}  \index{Gastrochilus@\textit{Gastrochilus}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣松蘭&T2_new_value=true&fr=y}}{臺灣松蘭}\index{臺灣松蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+fuscopunctatus}{\textit{G. fuscopunctatus} (Hayata) Hayata}  \index{Gastrochilus@\textit{Gastrochilus}!fuscopunctatus@\textit{fuscopunctatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅斑松蘭&T2_new_value=true&fr=y}}{紅斑松蘭}\index{紅斑松蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+hoii}{\textit{G. hoii} T.P.Lin}  \index{Gastrochilus@\textit{Gastrochilus}!hoii@\textit{hoii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=何氏松蘭&T2_new_value=true&fr=y}}{何氏松蘭}\index{何氏松蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+linii}{\textit{G. linii} Ormerod}  \index{Gastrochilus@\textit{Gastrochilus}!linii@\textit{linii}}  \index{Gastrochilus@\textit{Gastrochilus}!flavus@\textit{flavus}{\\\noindent(= \textit{Gastrochilus linii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金松蘭&T2_new_value=true&fr=y}}{金松蘭}\index{金松蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+matsudae}{\textit{G. matsudae} Hayata}  \index{Gastrochilus@\textit{Gastrochilus}!matsudae@\textit{matsudae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬唇松蘭&T2_new_value=true&fr=y}}{寬唇松蘭}\index{寬唇松蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+rantabunensis}{\textit{G. rantabunensis} C.Chow. ex T.P.Lin}  \index{Gastrochilus@\textit{Gastrochilus}!rantabunensis@\textbf{\textit{rantabunensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=合歡松蘭&T2_new_value=true&fr=y}}{合歡松蘭}\index{合歡松蘭@{\Song{合歡松蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+raraensis}{\textit{G. raraensis} Fukuy.}  \index{Gastrochilus@\textit{Gastrochilus}!raraensis@\textit{raraensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅檜松蘭&T2_new_value=true&fr=y}}{紅檜松蘭}\index{紅檜松蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrochilus+somae}{\textit{G. somae} Hayata}  \index{Gastrochilus@\textit{Gastrochilus}!somae@\textit{somae}}  \index{Gastrochilus@\textit{Gastrochilus}!japonicus@\textit{japonicus}{\\\noindent(= \textit{Gastrochilus somae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃松蘭&T2_new_value=true&fr=y}}{黃松蘭}\index{黃松蘭} LC
  \end{itemize}
 \item[] \textit{Gastrodia} 赤箭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+albida}{\textit{G. albida} T.C.Hsu \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!albida@\textit{albida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白赤箭&T2_new_value=true&fr=y}}{白赤箭}\index{白赤箭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+appendiculata}{\textit{G. appendiculata} C.S.Leou \& N.J.Chung}  \index{Gastrodia@\textit{Gastrodia}!appendiculata@\textit{appendiculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無蕊喙赤箭&T2_new_value=true&fr=y}}{無蕊喙赤箭}\index{無蕊喙赤箭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+callosa}{\textit{G. callosa} J. J. Sm.}  \index{Gastrodia@\textit{Gastrodia}!callosa@\textit{callosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=緋赤箭&T2_new_value=true&fr=y}}{緋赤箭}\index{緋赤箭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+clausa}{\textit{G. clausa} T.C.Hsu, S.W.Chung \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!clausa@\textit{clausa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=閉花赤箭&T2_new_value=true&fr=y}}{閉花赤箭}\index{閉花赤箭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+confusoides+var.+confusoides}{\textit{G. confusoides} T.C.Hsu, S.W.Chung \& C.M.Kuo var. \textit{confusoides}}  \index{Gastrodia@\textit{Gastrodia}!confusoides@\textit{confusoides}!var. confusoides@var. \textit{confusoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬八代赤箭&T2_new_value=true&fr=y}}{擬八代赤箭}\index{擬八代赤箭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+confusoides+var.+taitungensis}{\textit{G. confusoides} T.C.Hsu, S.W.Chung \& C.M.Kuo var. \textit{taitungensis} T.C.Hsu \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!confusoides@\textit{confusoides}!var. taitungensis@var. \textit{taitungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東赤箭&T2_new_value=true&fr=y}}{臺東赤箭}\index{臺東赤箭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+elata}{\textit{G. elata} Blume}  \index{Gastrodia@\textit{Gastrodia}!elata@\textbf{\textit{elata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高赤箭&T2_new_value=true&fr=y}}{高赤箭}\index{高赤箭@{\Song{高赤箭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+flabilabella}{\textit{G. flabilabella} S.S.Ying}  \index{Gastrodia@\textit{Gastrodia}!flabilabella@\textbf{\textit{flabilabella}}}  \index{Gastrodia@\textit{Gastrodia}!flavilabella@\textit{flavilabella}{\\\noindent(= \textit{Gastrodia flabilabella})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=夏赤箭&T2_new_value=true&fr=y}}{夏赤箭}\index{夏赤箭@{\Song{夏赤箭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+flexistyla}{\textit{G. flexistyla} T.C.Hsu \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!flexistyla@\textbf{\textit{flexistyla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=摺柱赤箭&T2_new_value=true&fr=y}}{摺柱赤箭}\index{摺柱赤箭@{\Song{摺柱赤箭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+fontinalis+var.+fontinalis}{\textit{G. fontinalis} T.P.Lin var. \textit{fontinalis}}  \index{Gastrodia@\textit{Gastrodia}!fontinalis@\textit{fontinalis}!var. fontinalis@\textbf{var. \textit{fontinalis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=春赤箭&T2_new_value=true&fr=y}}{春赤箭}\index{春赤箭@{\Song{春赤箭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+fontinalis+var.+suburceolata}{\textit{G. fontinalis} T.P.Lin var. \textit{suburceolata} T.C.Hsu}  \index{Gastrodia@\textit{Gastrodia}!fontinalis@\textit{fontinalis}!var. suburceolata@\textbf{var. \textit{suburceolata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=壺花赤箭&T2_new_value=true&fr=y}}{壺花赤箭}\index{壺花赤箭@{\Song{壺花赤箭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+gracillis}{\textit{G. gracillis} Blume}  \index{Gastrodia@\textit{Gastrodia}!gracillis@\textit{gracillis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細赤箭&T2_new_value=true&fr=y}}{細赤箭}\index{細赤箭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+javanica}{\textit{G. javanica} (Blume) Lindl.}  \index{Gastrodia@\textit{Gastrodia}!javanica@\textbf{\textit{javanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=爪哇赤箭&T2_new_value=true&fr=y}}{爪哇赤箭}\index{爪哇赤箭@{\Song{爪哇赤箭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+leoui}{\textit{G. leoui} T.C.Hsu \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!leoui@\textit{leoui}}  \index{Gastrodia@\textit{Gastrodia}!confusa@\textit{confusa}{\\\noindent(= \textit{Gastrodia leoui})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柳氏赤箭&T2_new_value=true&fr=y}}{柳氏赤箭(八代赤箭)} \index{柳氏赤箭} \index{八代赤箭@{八代赤箭(=柳氏赤箭)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+leucochila}{\textit{G. leucochila} T.C.Hsu \& Z.H.Chen}  \index{Gastrodia@\textit{Gastrodia}!leucochila@\textit{leucochila}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白唇赤箭&T2_new_value=true&fr=y}}{白唇赤箭}\index{白唇赤箭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+nantoensis}{\textit{G. nantoensis} T.C.Hsu \& C.M.Kuo ex T.P.Lin}  \index{Gastrodia@\textit{Gastrodia}!nantoensis@\textit{nantoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投赤箭&T2_new_value=true&fr=y}}{南投赤箭}\index{南投赤箭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+nipponica}{\textit{G. nipponica} (Honda) Tuyama}  \index{Gastrodia@\textit{Gastrodia}!nipponica@\textit{nipponica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本赤箭&T2_new_value=true&fr=y}}{日本赤箭}\index{日本赤箭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+peichatieniana}{\textit{G. peichatieniana} S.S.Ying}  \index{Gastrodia@\textit{Gastrodia}!peichatieniana@\textit{peichatieniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=秋赤箭&T2_new_value=true&fr=y}}{秋赤箭}\index{秋赤箭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+pubilabiata}{\textit{G. pubilabiata} Sawa}  \index{Gastrodia@\textit{Gastrodia}!pubilabiata@\textbf{\textit{pubilabiata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冬赤箭&T2_new_value=true&fr=y}}{冬赤箭}\index{冬赤箭@{\Song{冬赤箭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+shimizuana}{\textit{G. shimizuana} Tuyama}  \index{Gastrodia@\textit{Gastrodia}!shimizuana@\textbf{\textit{shimizuana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水氏赤箭&T2_new_value=true&fr=y}}{清水氏赤箭}\index{清水氏赤箭@{\Song{清水氏赤箭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+sui}{\textit{G. sui} C.S.Leou, T.C.Hsu \& C.L.Yeh}  \index{Gastrodia@\textit{Gastrodia}!sui@\textbf{\textit{sui}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘇氏赤箭&T2_new_value=true&fr=y}}{蘇氏赤箭}\index{蘇氏赤箭@{\Song{蘇氏赤箭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+theana}{\textit{G. theana} Aver.}  \index{Gastrodia@\textit{Gastrodia}!theana@\textit{theana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短柱赤箭&T2_new_value=true&fr=y}}{短柱赤箭}\index{短柱赤箭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gastrodia+uraiensis}{\textit{G. uraiensis} T.C.Hsu \& C.M.Kuo}  \index{Gastrodia@\textit{Gastrodia}!uraiensis@\textit{uraiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來赤箭&T2_new_value=true&fr=y}}{烏來赤箭}\index{烏來赤箭}\# NT
  \end{itemize}
 \item[] \textit{Geodorum} 地寶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Geodorum+densiflorum}{\textit{G. densiflorum} (Lam.) Schltr.}  \index{Geodorum@\textit{Geodorum}!densiflorum@\textit{densiflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂頭地寶蘭&T2_new_value=true&fr=y}}{垂頭地寶蘭}\index{垂頭地寶蘭} LC
  \end{itemize}
 \item[] \textit{Goodyera} 斑葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+biflora}{\textit{G. biflora} (Lindl.) Hook.f.}  \index{Goodyera@\textit{Goodyera}!biflora@\textbf{\textit{biflora}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花斑葉蘭&T2_new_value=true&fr=y}}{大花斑葉蘭}\index{大花斑葉蘭@{\Song{大花斑葉蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+bilamellata}{\textit{G. bilamellata} Hayata}  \index{Goodyera@\textit{Goodyera}!bilamellata@\textit{bilamellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙板斑葉蘭&T2_new_value=true&fr=y}}{雙板斑葉蘭}\index{雙板斑葉蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+bomiensis}{\textit{G. bomiensis} K.Y.Lang}  \index{Goodyera@\textit{Goodyera}!bomiensis@\textbf{\textit{bomiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=波密斑葉蘭&T2_new_value=true&fr=y}}{波密斑葉蘭}\index{波密斑葉蘭@{\Song{波密斑葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+daibuzanensis}{\textit{G. daibuzanensis} Yamam.}  \index{Goodyera@\textit{Goodyera}!daibuzanensis@\textit{daibuzanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大武斑葉蘭&T2_new_value=true&fr=y}}{大武斑葉蘭}\index{大武斑葉蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+foliosa}{\textit{G. foliosa} (Lindl.) Benth. ex C.B.Clarke}  \index{Goodyera@\textit{Goodyera}!foliosa@\textit{foliosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚唇斑葉蘭&T2_new_value=true&fr=y}}{厚唇斑葉蘭}\index{厚唇斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+foliosa+var.+taoana}{\textit{G. foliosa} (Lindl.) Benth. ex C.B.Clarke var. \textit{taoana} T.C.Hsu}  \index{Goodyera@\textit{Goodyera}!foliosa@\textit{foliosa}!var. taoana@var. \textit{taoana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=達悟斑葉蘭&T2_new_value=true&fr=y}}{達悟斑葉蘭}\index{達悟斑葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+fumata}{\textit{G. fumata} Thwaites}  \index{Goodyera@\textit{Goodyera}!fumata@\textit{fumata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾唇斑葉蘭&T2_new_value=true&fr=y}}{尾唇斑葉蘭}\index{尾唇斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+henryi}{\textit{G. henryi} Rolfe}  \index{Goodyera@\textit{Goodyera}!henryi@\textit{henryi}}  \index{Goodyera@\textit{Goodyera}!maximowicziana@\textit{maximowicziana}{\\\noindent(= \textit{Goodyera henryi})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短穗斑葉蘭&T2_new_value=true&fr=y}}{短穗斑葉蘭}\index{短穗斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+kwangtungensis}{\textit{G. kwangtungensis} C.L.Tso}  \index{Goodyera@\textit{Goodyera}!kwangtungensis@\textit{kwangtungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=花格斑葉蘭&T2_new_value=true&fr=y}}{花格斑葉蘭}\index{花格斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+matsumurana}{\textit{G. matsumurana} Schltr.}  \index{Goodyera@\textit{Goodyera}!matsumurana@\textit{matsumurana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銀線蓮&T2_new_value=true&fr=y}}{銀線蓮}\index{銀線蓮} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+nankoensis}{\textit{G. nankoensis} Fukuy.}  \index{Goodyera@\textit{Goodyera}!nankoensis@\textit{nankoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖斑葉蘭&T2_new_value=true&fr=y}}{南湖斑葉蘭}\index{南湖斑葉蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+nantoensis}{\textit{G. nantoensis} Hayata}  \index{Goodyera@\textit{Goodyera}!nantoensis@\textbf{\textit{nantoensis}}}  \index{Goodyera@\textit{Goodyera}!arisanensis@\textit{arisanensis}{\\\noindent(= \textit{Goodyera nantoensis})}}   \index{Goodyera@\textit{Goodyera}!repens@\textit{repens}{\\\noindent(= \textit{Goodyera nantoensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投斑葉蘭&T2_new_value=true&fr=y}}{南投斑葉蘭(阿里山斑葉蘭)} \index{南投斑葉蘭@{\Song{南投斑葉蘭}}} \index{阿里山斑葉蘭@{\Song{阿里山斑葉蘭(=南投斑葉蘭)}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+pendula}{\textit{G. pendula} Maxim.}  \index{Goodyera@\textit{Goodyera}!pendula@\textbf{\textit{pendula}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂葉斑葉蘭&T2_new_value=true&fr=y}}{垂葉斑葉蘭}\index{垂葉斑葉蘭@{\Song{垂葉斑葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+procera}{\textit{G. procera} (Ker Gawl.) Hook.f.}  \index{Goodyera@\textit{Goodyera}!procera@\textit{procera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=穗花斑葉蘭&T2_new_value=true&fr=y}}{穗花斑葉蘭}\index{穗花斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+pusilla}{\textit{G. pusilla} Blume}  \index{Goodyera@\textit{Goodyera}!pusilla@\textit{pusilla}}  \index{Goodyera@\textit{Goodyera}!yangmeishanensis@\textit{yangmeishanensis}{\\\noindent(= \textit{Goodyera pusilla})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小小斑葉蘭&T2_new_value=true&fr=y}}{小小斑葉蘭}\index{小小斑葉蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+rubicunda}{\textit{G. rubicunda} (Blume) Lindl.}  \index{Goodyera@\textit{Goodyera}!rubicunda@\textit{rubicunda}}  \index{Goodyera@\textit{Goodyera}!grandis@\textit{grandis}{\\\noindent(= \textit{Goodyera rubicunda})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛苞斑葉蘭&T2_new_value=true&fr=y}}{毛苞斑葉蘭}\index{毛苞斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+schlechtendaliana}{\textit{G. schlechtendaliana} Rchb.f.}  \index{Goodyera@\textit{Goodyera}!schlechtendaliana@\textit{schlechtendaliana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斑葉蘭&T2_new_value=true&fr=y}}{斑葉蘭}\index{斑葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+similis}{\textit{G. similis} Blume}  \index{Goodyera@\textit{Goodyera}!similis@\textit{similis}}  \index{Goodyera@\textit{Goodyera}!velutina@\textit{velutina}{\\\noindent(= \textit{Goodyera similis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鳥嘴蓮&T2_new_value=true&fr=y}}{鳥嘴蓮}\index{鳥嘴蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+velutina+var.+albo-nervosa}{\textit{G. velutina} Maxim. var. \textit{albo-nervosa} T.P.Lin \& Y.N.Chang}  \index{Goodyera@\textit{Goodyera}!velutina@\textit{velutina}!var. albo-nervosa@var. \textit{albo-nervosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斑紋鳥嘴蓮&T2_new_value=true&fr=y}}{斑紋鳥嘴蓮}\index{斑紋鳥嘴蓮} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Goodyera+yamiana}{\textit{G. yamiana} Fukuy.}  \index{Goodyera@\textit{Goodyera}!yamiana@\textbf{\textit{yamiana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼金銀草&T2_new_value=true&fr=y}}{蘭嶼金銀草}\index{蘭嶼金銀草@{\Song{蘭嶼金銀草}}}\# VU
  \end{itemize}
 \item[] \textit{Habenaria} 玉鳳蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+alishanensis}{\textit{H. alishanensis} T.P.Lin \& D.M.Huang}  \index{Habenaria@\textit{Habenaria}!alishanensis@\textit{alishanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樂氏玉鳳蘭&T2_new_value=true&fr=y}}{樂氏玉鳳蘭}\index{樂氏玉鳳蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+ciliolaris}{\textit{H. ciliolaris} Kranzl.}  \index{Habenaria@\textit{Habenaria}!ciliolaris@\textit{ciliolaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉蜂蘭&T2_new_value=true&fr=y}}{玉蜂蘭}\index{玉蜂蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+dentata}{\textit{H. dentata} (Sw.) Schltr.}  \index{Habenaria@\textit{Habenaria}!dentata@\textit{dentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白鳳蘭&T2_new_value=true&fr=y}}{白鳳蘭}\index{白鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+iyoensis}{\textit{H. iyoensis} Ohwi}  \index{Habenaria@\textit{Habenaria}!iyoensis@\textit{iyoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=岩坡玉鳳蘭&T2_new_value=true&fr=y}}{岩坡玉鳳蘭}\index{岩坡玉鳳蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+longiracema}{\textit{H. longiracema} Fukuy.}  \index{Habenaria@\textit{Habenaria}!longiracema@\textit{longiracema}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長穗玉鳳蘭&T2_new_value=true&fr=y}}{長穗玉鳳蘭}\index{長穗玉鳳蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+pantlingiana}{\textit{H. pantlingiana} Kraenzl.}  \index{Habenaria@\textit{Habenaria}!pantlingiana@\textit{pantlingiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=叉瓣玉鳳蘭&T2_new_value=true&fr=y}}{叉瓣玉鳳蘭}\index{叉瓣玉鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+petelotii}{\textit{H. petelotii} Gagnep.}  \index{Habenaria@\textit{Habenaria}!petelotii@\textit{petelotii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛唇玉鳳蘭&T2_new_value=true&fr=y}}{毛唇玉鳳蘭}\index{毛唇玉鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+polytricha}{\textit{H. polytricha} Rolfe}  \index{Habenaria@\textit{Habenaria}!polytricha@\textit{polytricha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂瓣玉鳳蘭&T2_new_value=true&fr=y}}{裂瓣玉鳳蘭}\index{裂瓣玉鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+stenopetala}{\textit{H. stenopetala} Lindl.}  \index{Habenaria@\textit{Habenaria}!stenopetala@\textit{stenopetala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹瓣玉鳳蘭&T2_new_value=true&fr=y}}{狹瓣玉鳳蘭}\index{狹瓣玉鳳蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Habenaria+tsaiana}{\textit{H. tsaiana} T.P.Lin}  \index{Habenaria@\textit{Habenaria}!tsaiana@\textit{tsaiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔡氏玉鳳蘭&T2_new_value=true&fr=y}}{蔡氏玉鳳蘭}\index{蔡氏玉鳳蘭}\# DD
  \end{itemize}
 \item[] \textit{Hancockia} 漢考克蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hancockia+uniflora}{\textit{H. uniflora} Rolfe}  \index{Hancockia@\textit{Hancockia}!uniflora@\textbf{\textit{uniflora}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=漢考克蘭&T2_new_value=true&fr=y}}{漢考克蘭}\index{漢考克蘭@{\Song{漢考克蘭}}} CR
  \end{itemize}
 \item[] \textit{Haraella} 香蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haraella+retrocalla}{\textit{H. retrocalla} (Hayata) Kudo}  \index{Haraella@\textit{Haraella}!retrocalla@\textit{retrocalla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香蘭&T2_new_value=true&fr=y}}{香蘭}\index{香蘭}\# NT
  \end{itemize}
 \item[] \textit{Hayata} 早田蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hayata+merrillii}{\textit{H. merrillii} (Ames \& Quisumb.) T.C.Hsu \& S.W.Chung}  \index{Hayata@\textit{Hayata}!merrillii@\textit{merrillii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全唇早田蘭&T2_new_value=true&fr=y}}{全唇早田蘭}\index{全唇早田蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hayata+tabiyahanensis}{\textit{H. tabiyahanensis} (H.) Aver.}  \index{Hayata@\textit{Hayata}!tabiyahanensis@\textit{tabiyahanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂唇早田蘭&T2_new_value=true&fr=y}}{裂唇早田蘭}\index{裂唇早田蘭}\# NT
  \end{itemize}
 \item[] \textit{Hemipilia} 玉山一葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemipilia+cordifolia}{\textit{H. cordifolia} Lindl.}  \index{Hemipilia@\textit{Hemipilia}!cordifolia@\textbf{\textit{cordifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山一葉蘭&T2_new_value=true&fr=y}}{玉山一葉蘭}\index{玉山一葉蘭@{\Song{玉山一葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemipilia+×alpestroides}{\textit{H. ×alpestroides} T.C.Hsu}  \index{Hemipilia@\textit{Hemipilia}!×alpestroides@\textit{×alpestroides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雛蝶蘭&T2_new_value=true&fr=y}}{雛蝶蘭}\index{雛蝶蘭} NA$^h$
  \end{itemize}
 \item[] \textit{Herminium} 腳根蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Herminium+lanceum}{\textit{H. lanceum} (Thunb. ex Sw.) Vuijk}  \index{Herminium@\textit{Herminium}!lanceum@\textit{lanceum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉零餘子草&T2_new_value=true&fr=y}}{細葉零餘子草}\index{細葉零餘子草} LC
  \end{itemize}
 \item[] \textit{Hetaeria} 角唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hetaeria+anomala}{\textit{H. anomala} (Lindl.) Rchb.f.}  \index{Hetaeria@\textit{Hetaeria}!anomala@\textit{anomala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓唇伴蘭&T2_new_value=true&fr=y}}{圓唇伴蘭}\index{圓唇伴蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hetaeria+oblongifolia}{\textit{H. oblongifolia} (Blume) Blume}  \index{Hetaeria@\textit{Hetaeria}!oblongifolia@\textbf{\textit{oblongifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長橢圓葉伴蘭&T2_new_value=true&fr=y}}{長橢圓葉伴蘭}\index{長橢圓葉伴蘭@{\Song{長橢圓葉伴蘭}}} VU
  \end{itemize}
 \item[] \textit{Holcoglossum} 撬唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Holcoglossum+pumilum}{\textit{H. pumilum} (Hayata) X.H.Jin}  \index{Holcoglossum@\textit{Holcoglossum}!pumilum@\textit{pumilum}}  \index{Ascocentrum@\textit{Ascocentrum}!pumilum@\textit{pumilum}{\\\noindent(= \textit{Holcoglossum pumilum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鹿角蘭&T2_new_value=true&fr=y}}{鹿角蘭}\index{鹿角蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Holcoglossum+quasipinifolium}{\textit{H. quasipinifolium} (Hayata) Schltr.}  \index{Holcoglossum@\textit{Holcoglossum}!quasipinifolium@\textit{quasipinifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=撬唇蘭&T2_new_value=true&fr=y}}{撬唇蘭}\index{撬唇蘭} NT
  \end{itemize}
 \item[] \textit{Hylophila} 光唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hylophila+nipponica}{\textit{H. nipponica} (Fukuy.) S.S.Ying}  \index{Hylophila@\textit{Hylophila}!nipponica@\textit{nipponica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼袋唇蘭&T2_new_value=true&fr=y}}{蘭嶼袋唇蘭}\index{蘭嶼袋唇蘭}\# NT
  \end{itemize}
 \item[] \textit{Lecanorchis} 皿柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+bihuensis}{\textit{L. bihuensis} T.P.Lin \& S.H.Wu}  \index{Lecanorchis@\textit{Lecanorchis}!bihuensis@\textit{bihuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全唇皿柱蘭&T2_new_value=true&fr=y}}{全唇皿柱蘭}\index{全唇皿柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+cerina}{\textit{L. cerina} Fukuy.}  \index{Lecanorchis@\textit{Lecanorchis}!cerina@\textit{cerina}}  \index{Lecanorchis@\textit{Lecanorchis}!japonica@\textit{japonica}{\\\noindent(= \textit{Lecanorchis cerina})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫皿蘭&T2_new_value=true&fr=y}}{紫皿蘭(日本皿柱蘭)} \index{紫皿蘭} \index{日本皿柱蘭@{日本皿柱蘭(=紫皿蘭)}}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+latens}{\textit{L. latens} T.P.Lin \& W.M.Lin}  \index{Lecanorchis@\textit{Lecanorchis}!latens@\textit{latens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=士賢皿柱蘭&T2_new_value=true&fr=y}}{士賢皿柱蘭}\index{士賢皿柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+nigricans+var.+nigricans}{\textit{L. nigricans} Honda var. \textit{nigricans}}  \index{Lecanorchis@\textit{Lecanorchis}!nigricans@\textit{nigricans}!var. nigricans@var. \textit{nigricans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全唇皿柱蘭&T2_new_value=true&fr=y}}{全唇皿柱蘭}\index{全唇皿柱蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+nigricans+var.+yakushimensis}{\textit{L. nigricans} Honda var. \textit{yakushimensis} T.Hashim}  \index{Lecanorchis@\textit{Lecanorchis}!nigricans@\textit{nigricans}!var. yakushimensis@var. \textit{yakushimensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屋久全唇皿蘭&T2_new_value=true&fr=y}}{屋久全唇皿蘭}\index{屋久全唇皿蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+ohwii}{\textit{L. ohwii} Masam.}  \index{Lecanorchis@\textit{Lecanorchis}!ohwii@\textit{ohwii}}  \index{Lecanorchis@\textit{Lecanorchis}!kiusiana@\textit{kiusiana}{\\\noindent(= \textit{Lecanorchis ohwii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白皿蘭&T2_new_value=true&fr=y}}{白皿蘭}\index{白皿蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+subpelorica}{\textit{L. subpelorica} T.C.Hsu \& S.W.Chung}  \index{Lecanorchis@\textit{Lecanorchis}!subpelorica@\textit{subpelorica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亞輻射皿蘭&T2_new_value=true&fr=y}}{亞輻射皿蘭}\index{亞輻射皿蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+suginoana}{\textit{L. suginoana} (Tuyama) Serizawa}  \index{Lecanorchis@\textit{Lecanorchis}!suginoana@\textit{suginoana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=杉野氏皿蘭&T2_new_value=true&fr=y}}{杉野氏皿蘭}\index{杉野氏皿蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+taiwaniana}{\textit{L. taiwaniana} S.S.Ying}  \index{Lecanorchis@\textit{Lecanorchis}!taiwaniana@\textbf{\textit{taiwaniana}}}  \index{Lecanorchis@\textit{Lecanorchis}!amethystea@\textit{amethystea}{\\\noindent(= \textit{Lecanorchis taiwaniana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫晶皿蘭&T2_new_value=true&fr=y}}{紫晶皿蘭}\index{紫晶皿蘭@{\Song{紫晶皿蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+thalassica}{\textit{L. thalassica} T.P.Lin}  \index{Lecanorchis@\textit{Lecanorchis}!thalassica@\textbf{\textit{thalassica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紋皿柱蘭&T2_new_value=true&fr=y}}{紋皿柱蘭}\index{紋皿柱蘭@{\Song{紋皿柱蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+trachycaula}{\textit{L. trachycaula} Ohwi}  \index{Lecanorchis@\textit{Lecanorchis}!trachycaula@\textit{trachycaula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=糙莖皿蘭&T2_new_value=true&fr=y}}{糙莖皿蘭}\index{糙莖皿蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+triloba}{\textit{L. triloba} J.J.Sm.}  \index{Lecanorchis@\textit{Lecanorchis}!triloba@\textbf{\textit{triloba}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三裂皿蘭&T2_new_value=true&fr=y}}{三裂皿蘭}\index{三裂皿蘭@{\Song{三裂皿蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+vietnamica}{\textit{L. vietnamica} Aver.}  \index{Lecanorchis@\textit{Lecanorchis}!vietnamica@\textit{vietnamica}}  \index{Lecanorchis@\textit{Lecanorchis}!flavicans@\textit{flavicans}!var. acutiloba@var. \textit{acutiloba}{\\\noindent(=\textit{Lecanorchis vietnamica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白髭皿蘭&T2_new_value=true&fr=y}}{白髭皿蘭}\index{白髭皿蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanorchis+virella}{\textit{L. virella} T.Hashim.}  \index{Lecanorchis@\textit{Lecanorchis}!virella@\textbf{\textit{virella}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠皿蘭&T2_new_value=true&fr=y}}{綠皿蘭}\index{綠皿蘭@{\Song{綠皿蘭}}} CR
  \end{itemize}
 \item[] \textit{Liparis} 羊耳蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+amabilis}{\textit{L. amabilis} Fukuy.}  \index{Liparis@\textit{Liparis}!amabilis@\textbf{\textit{amabilis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花羊耳蒜&T2_new_value=true&fr=y}}{白花羊耳蒜}\index{白花羊耳蒜@{\Song{白花羊耳蒜}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+barbata}{\textit{L. barbata} Lindl.}  \index{Liparis@\textit{Liparis}!barbata@\textit{barbata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬚唇羊耳蒜&T2_new_value=true&fr=y}}{鬚唇羊耳蒜}\index{鬚唇羊耳蒜} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+bootanensis}{\textit{L. bootanensis} Griff.}  \index{Liparis@\textit{Liparis}!bootanensis@\textit{bootanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=一葉羊耳蒜&T2_new_value=true&fr=y}}{一葉羊耳蒜}\index{一葉羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+caespitosa}{\textit{L. caespitosa} (Thouars) Lindl.}  \index{Liparis@\textit{Liparis}!caespitosa@\textbf{\textit{caespitosa}}}  \index{Liparis@\textit{Liparis}!cespitosa@\textit{cespitosa}{\\\noindent(= \textit{Liparis caespitosa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花羊耳蒜&T2_new_value=true&fr=y}}{小花羊耳蒜}\index{小花羊耳蒜@{\Song{小花羊耳蒜}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+campylostalix}{\textit{L. campylostalix} Rchb.f.}  \index{Liparis@\textit{Liparis}!campylostalix@\textbf{\textit{campylostalix}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=彎柱羊耳蒜&T2_new_value=true&fr=y}}{彎柱羊耳蒜}\index{彎柱羊耳蒜@{\Song{彎柱羊耳蒜}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+condylobulbon}{\textit{L. condylobulbon} Rchb.f.}  \index{Liparis@\textit{Liparis}!condylobulbon@\textit{condylobulbon}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長腳羊耳蒜&T2_new_value=true&fr=y}}{長腳羊耳蒜}\index{長腳羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+cordifolia}{\textit{L. cordifolia} Hook f.}  \index{Liparis@\textit{Liparis}!cordifolia@\textit{cordifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=心葉羊耳蒜&T2_new_value=true&fr=y}}{心葉羊耳蒜}\index{心葉羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+derchiensis}{\textit{L. derchiensis} S.S.Ying}  \index{Liparis@\textit{Liparis}!derchiensis@\textbf{\textit{derchiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=德基羊耳蒜&T2_new_value=true&fr=y}}{德基羊耳蒜}\index{德基羊耳蒜@{\Song{德基羊耳蒜}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+elliptica}{\textit{L. elliptica} Wight}  \index{Liparis@\textit{Liparis}!elliptica@\textit{elliptica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=扁球羊耳蒜&T2_new_value=true&fr=y}}{扁球羊耳蒜}\index{扁球羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+elongata}{\textit{L. elongata} Fukuy.}  \index{Liparis@\textit{Liparis}!elongata@\textbf{\textit{elongata}}}  \index{Liparis@\textit{Liparis}!japonica@\textit{japonica}{\\\noindent(= \textit{Liparis elongata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長穗羊耳蒜&T2_new_value=true&fr=y}}{長穗羊耳蒜}\index{長穗羊耳蒜@{\Song{長穗羊耳蒜}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+ferruginea}{\textit{L. ferruginea} Lindl.}  \index{Liparis@\textit{Liparis}!ferruginea@\textit{ferruginea}}  \index{Liparis@\textit{Liparis}!hensoaensis@\textit{hensoaensis}{\\\noindent(= \textit{Liparis ferruginea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=明潭羊耳蒜&T2_new_value=true&fr=y}}{明潭羊耳蒜}\index{明潭羊耳蒜} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+formosana}{\textit{L. formosana} Rchb.f.}  \index{Liparis@\textit{Liparis}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寶島羊耳蒜&T2_new_value=true&fr=y}}{寶島羊耳蒜}\index{寶島羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+gigantea}{\textit{L. gigantea} C.L.Tso}  \index{Liparis@\textit{Liparis}!gigantea@\textit{gigantea}}  \index{Liparis@\textit{Liparis}!nigra@\textit{nigra}{\\\noindent(= \textit{Liparis gigantea})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花羊耳蒜&T2_new_value=true&fr=y}}{大花羊耳蒜}\index{大花羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+grossa}{\textit{L. grossa} Rchb.f.}  \index{Liparis@\textit{Liparis}!grossa@\textit{grossa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春羊耳蒜&T2_new_value=true&fr=y}}{恆春羊耳蒜}\index{恆春羊耳蒜} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+henryi}{\textit{L. henryi} Rolfe}  \index{Liparis@\textit{Liparis}!henryi@\textit{henryi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=齒唇羊耳蒜&T2_new_value=true&fr=y}}{齒唇羊耳蒜}\index{齒唇羊耳蒜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+kawakamii}{\textit{L. kawakamii} Hayata}  \index{Liparis@\textit{Liparis}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=川上氏羊耳蘭&T2_new_value=true&fr=y}}{川上氏羊耳蘭}\index{川上氏羊耳蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+laurisilvatica}{\textit{L. laurisilvatica} Fukuy.}  \index{Liparis@\textit{Liparis}!laurisilvatica@\textit{laurisilvatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花羊耳蘭&T2_new_value=true&fr=y}}{小花羊耳蘭}\index{小花羊耳蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+liangzuensis}{\textit{L. liangzuensis} T.P.Lin \& W.M.Lin}  \index{Liparis@\textit{Liparis}!liangzuensis@\textit{liangzuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=良如羊耳蘭&T2_new_value=true&fr=y}}{良如羊耳蘭}\index{良如羊耳蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+nakaharai}{\textit{L. nakaharai} Hayata}  \index{Liparis@\textit{Liparis}!nakaharai@\textit{nakaharai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉羊耳蒜&T2_new_value=true&fr=y}}{長葉羊耳蒜}\index{長葉羊耳蒜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+nervosa}{\textit{L. nervosa} (Thunb.) Lindl.}  \index{Liparis@\textit{Liparis}!nervosa@\textit{nervosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅花羊耳蒜&T2_new_value=true&fr=y}}{紅花羊耳蒜}\index{紅花羊耳蒜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+nokoensis}{\textit{L. nokoensis} Fukuy.}  \index{Liparis@\textit{Liparis}!nokoensis@\textit{nokoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=能高羊耳蘭&T2_new_value=true&fr=y}}{能高羊耳蘭}\index{能高羊耳蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+odorata}{\textit{L. odorata} (Willd.) Lindl.}  \index{Liparis@\textit{Liparis}!odorata@\textit{odorata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香花羊耳蒜&T2_new_value=true&fr=y}}{香花羊耳蒜}\index{香花羊耳蒜} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+petiolata}{\textit{L. petiolata} (D.Don) P.F.Hunt \& Summerh.}  \index{Liparis@\textit{Liparis}!petiolata@\textbf{\textit{petiolata}}}  \index{Liparis@\textit{Liparis}!auriculata@\textit{auriculata}{\\\noindent(= \textit{Liparis petiolata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙葉羊耳蒜&T2_new_value=true&fr=y}}{雙葉羊耳蒜}\index{雙葉羊耳蒜@{\Song{雙葉羊耳蒜}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+reckoniana}{\textit{L. reckoniana} T.C.Hsu }  \index{Liparis@\textit{Liparis}!reckoniana@\textbf{\textit{reckoniana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雲頂羊耳蒜&T2_new_value=true&fr=y}}{雲頂羊耳蒜}\index{雲頂羊耳蒜@{\Song{雲頂羊耳蒜}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+rubrotincta}{\textit{L. rubrotincta} T.C.Hsu }  \index{Liparis@\textit{Liparis}!rubrotincta@\textbf{\textit{rubrotincta}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絳唇羊耳蒜&T2_new_value=true&fr=y}}{絳唇羊耳蒜}\index{絳唇羊耳蒜@{\Song{絳唇羊耳蒜}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+sasakii}{\textit{L. sasakii} Hayata}  \index{Liparis@\textit{Liparis}!sasakii@\textbf{\textit{sasakii}}}  \index{Liparis@\textit{Liparis}!krameri@\textit{krameri}!var. sasakii@var. \textit{sasakii}{\\\noindent(=\textit{Liparis sasakii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾唇羊耳蒜&T2_new_value=true&fr=y}}{尾唇羊耳蒜}\index{尾唇羊耳蒜@{\Song{尾唇羊耳蒜}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+somai}{\textit{L. somai} Hayata}  \index{Liparis@\textit{Liparis}!somai@\textbf{\textit{somai}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛羊耳蒜&T2_new_value=true&fr=y}}{高士佛羊耳蒜}\index{高士佛羊耳蒜@{\Song{高士佛羊耳蒜}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+sootenzanensis}{\textit{L. sootenzanensis} Fukuy.}  \index{Liparis@\textit{Liparis}!sootenzanensis@\textit{sootenzanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=插天山羊耳蒜&T2_new_value=true&fr=y}}{插天山羊耳蒜}\index{插天山羊耳蒜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Liparis+viridiflora}{\textit{L. viridiflora} (Blume) Lindl.}  \index{Liparis@\textit{Liparis}!viridiflora@\textit{viridiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=淡綠羊耳蒜&T2_new_value=true&fr=y}}{淡綠羊耳蒜}\index{淡綠羊耳蒜} LC
  \end{itemize}
 \item[] \textit{Luisia} 釵子股屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Luisia+cordata}{\textit{L. cordata} Fukuy.}  \index{Luisia@\textit{Luisia}!cordata@\textbf{\textit{cordata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=心唇金釵蘭&T2_new_value=true&fr=y}}{心唇金釵蘭}\index{心唇金釵蘭@{\Song{心唇金釵蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Luisia+lui}{\textit{L. lui} T.C.Hsu \& S.W.Chung}  \index{Luisia@\textit{Luisia}!lui@\textit{lui}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=呂氏金釵蘭&T2_new_value=true&fr=y}}{呂氏金釵蘭}\index{呂氏金釵蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Luisia+megasepala}{\textit{L. megasepala} Hayata}  \index{Luisia@\textit{Luisia}!megasepala@\textit{megasepala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣金釵蘭&T2_new_value=true&fr=y}}{臺灣金釵蘭}\index{臺灣金釵蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Luisia+teres}{\textit{L. teres} (Thunb.) Blume}  \index{Luisia@\textit{Luisia}!teres@\textit{teres}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金釵蘭&T2_new_value=true&fr=y}}{金釵蘭}\index{金釵蘭} LC
  \end{itemize}
 \item[] \textit{Malaxis} 小柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malaxis+monophyllos}{\textit{M. monophyllos} (L.) Sw.}  \index{Malaxis@\textit{Malaxis}!monophyllos@\textit{monophyllos}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單葉軟葉蘭&T2_new_value=true&fr=y}}{單葉軟葉蘭}\index{單葉軟葉蘭} LC
  \end{itemize}
 \item[] \textit{Microtis} 韭葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microtis+unifolia}{\textit{M. unifolia} (Forst.) Rchb.f.}  \index{Microtis@\textit{Microtis}!unifolia@\textit{unifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=韭葉蘭&T2_new_value=true&fr=y}}{韭葉蘭}\index{韭葉蘭} LC
  \end{itemize}
 \item[] \textit{Neottia} 鳥巢蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+acuminata}{\textit{N. acuminata} Schltr.}  \index{Neottia@\textit{Neottia}!acuminata@\textit{acuminata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鳥巢蘭&T2_new_value=true&fr=y}}{鳥巢蘭}\index{鳥巢蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+atayalica}{\textit{N. atayalica} T.C.Hsu}  \index{Neottia@\textit{Neottia}!atayalica@\textit{atayalica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泰雅雙葉蘭&T2_new_value=true&fr=y}}{泰雅雙葉蘭}\index{泰雅雙葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+breviscapa}{\textit{N. breviscapa} T.C.Hsu}  \index{Neottia@\textit{Neottia}!breviscapa@\textbf{\textit{breviscapa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短葶雙葉蘭&T2_new_value=true&fr=y}}{短葶雙葉蘭}\index{短葶雙葉蘭@{\Song{短葶雙葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+fukuyamae}{\textit{N. fukuyamae} T.C.Hsu \& S.W.Chung}  \index{Neottia@\textit{Neottia}!fukuyamae@\textit{fukuyamae}}  \index{Listera@\textit{Listera}!macrantha@\textit{macrantha}{\\\noindent(= \textit{Neottia fukuyamae})}}   \index{Neottia@\textit{Neottia}!formosana@\textit{formosana}{\\\noindent(= \textit{Neottia fukuyamae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花雙葉蘭&T2_new_value=true&fr=y}}{大花雙葉蘭}\index{大花雙葉蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+fukuyamae+var.+chilaiensis}{\textit{N. fukuyamae} T.C.Hsu \& S.W.Chung var. \textit{chilaiensis} T.C.Hsu}  \index{Neottia@\textit{Neottia}!fukuyamae@\textit{fukuyamae}!var. chilaiensis@var. \textit{chilaiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奇萊雙葉蘭&T2_new_value=true&fr=y}}{奇萊雙葉蘭}\index{奇萊雙葉蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+hohuanshanensis}{\textit{N. hohuanshanensis} T.P.Lin \& S.H.Wu}  \index{Neottia@\textit{Neottia}!hohuanshanensis@\textit{hohuanshanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=合歡山雙葉蘭&T2_new_value=true&fr=y}}{合歡山雙葉蘭}\index{合歡山雙葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+japonica}{\textit{N. japonica} (Blume) Szlach.}  \index{Neottia@\textit{Neottia}!japonica@\textit{japonica}}  \index{Listera@\textit{Listera}!japonica@\textit{japonica}{\\\noindent(= \textit{Neottia japonica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本雙葉蘭&T2_new_value=true&fr=y}}{日本雙葉蘭}\index{日本雙葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+kuanshanensis}{\textit{N. kuanshanensis} (H.J.Su) T.C.Hsu \& S.W.Chung}  \index{Neottia@\textit{Neottia}!kuanshanensis@\textbf{\textit{kuanshanensis}}}  \index{Listera@\textit{Listera}!kuanshanensis@\textit{kuanshanensis}{\\\noindent(= \textit{Neottia kuanshanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山雙葉蘭&T2_new_value=true&fr=y}}{關山雙葉蘭}\index{關山雙葉蘭@{\Song{關山雙葉蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+meifongensis}{\textit{N. meifongensis} (H.J.Su \& C.Y.Hu) T.C.Hsu \& S.W.Chung}  \index{Neottia@\textit{Neottia}!meifongensis@\textbf{\textit{meifongensis}}}  \index{Listera@\textit{Listera}!meifongensis@\textit{meifongensis}{\\\noindent(= \textit{Neottia meifongensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梅峰雙葉蘭&T2_new_value=true&fr=y}}{梅峰雙葉蘭}\index{梅峰雙葉蘭@{\Song{梅峰雙葉蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+microauriculata}{\textit{N. microauriculata} T.C.Hsu}  \index{Neottia@\textit{Neottia}!microauriculata@\textbf{\textit{microauriculata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=微耳雙葉蘭&T2_new_value=true&fr=y}}{微耳雙葉蘭}\index{微耳雙葉蘭@{\Song{微耳雙葉蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+morrisonicola}{\textit{N. morrisonicola} (Hayata) Szlach.}  \index{Neottia@\textit{Neottia}!morrisonicola@\textit{morrisonicola}}  \index{Listera@\textit{Listera}!morrisonicola@\textit{morrisonicola}{\\\noindent(= \textit{Neottia morrisonicola})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山雙葉蘭&T2_new_value=true&fr=y}}{玉山雙葉蘭}\index{玉山雙葉蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+nankomontana}{\textit{N. nankomontana} (Fukuy.) Szlach.}  \index{Neottia@\textit{Neottia}!nankomontana@\textbf{\textit{nankomontana}}}  \index{Listera@\textit{Listera}!nankomontana@\textit{nankomontana}{\\\noindent(= \textit{Neottia nankomontana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖雙葉蘭&T2_new_value=true&fr=y}}{南湖雙葉蘭}\index{南湖雙葉蘭@{\Song{南湖雙葉蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+piluchiensis}{\textit{N. piluchiensis} T.P.Lin}  \index{Neottia@\textit{Neottia}!piluchiensis@\textit{piluchiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=碧綠溪雙葉蘭&T2_new_value=true&fr=y}}{碧綠溪雙葉蘭}\index{碧綠溪雙葉蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+pseudonipponica}{\textit{N. pseudonipponica} (Fukuy.) Szlach.}  \index{Neottia@\textit{Neottia}!pseudonipponica@\textbf{\textit{pseudonipponica}}}  \index{Listera@\textit{Listera}!pseudonipponica@\textit{pseudonipponica}{\\\noindent(= \textit{Neottia pseudonipponica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假日本雙葉蘭&T2_new_value=true&fr=y}}{假日本雙葉蘭}\index{假日本雙葉蘭@{\Song{假日本雙葉蘭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+shenlengiana}{\textit{N. shenlengiana} T.C.Hsu}  \index{Neottia@\textit{Neottia}!shenlengiana@\textit{shenlengiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=聖稜雙葉蘭&T2_new_value=true&fr=y}}{聖稜雙葉蘭}\index{聖稜雙葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+suzukii}{\textit{N. suzukii} (Masam.) Szlach.}  \index{Neottia@\textit{Neottia}!suzukii@\textit{suzukii}}  \index{Listera@\textit{Listera}!suzukii@\textit{suzukii}{\\\noindent(= \textit{Neottia suzukii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈴木氏雙葉蘭&T2_new_value=true&fr=y}}{鈴木氏雙葉蘭}\index{鈴木氏雙葉蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+taizanensis}{\textit{N. taizanensis} (Fukuy.) Szlach.}  \index{Neottia@\textit{Neottia}!taizanensis@\textbf{\textit{taizanensis}}}  \index{Listera@\textit{Listera}!taizanensis@\textit{taizanensis}{\\\noindent(= \textit{Neottia taizanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大山雙葉蘭&T2_new_value=true&fr=y}}{大山雙葉蘭}\index{大山雙葉蘭@{\Song{大山雙葉蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neottia+tatakaensis}{\textit{N. tatakaensis} T.C.Hsu \& H.C.Hung}  \index{Neottia@\textit{Neottia}!tatakaensis@\textbf{\textit{tatakaensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=塔塔加雙葉蘭&T2_new_value=true&fr=y}}{塔塔加雙葉蘭}\index{塔塔加雙葉蘭@{\Song{塔塔加雙葉蘭}}} VU
  \end{itemize}
 \item[] \textit{Nephelaphyllum} 雲葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nephelaphyllum+tenuiflorum}{\textit{N. tenuiflorum} Blume}  \index{Nephelaphyllum@\textit{Nephelaphyllum}!tenuiflorum@\textbf{\textit{tenuiflorum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雲葉蘭&T2_new_value=true&fr=y}}{雲葉蘭}\index{雲葉蘭@{\Song{雲葉蘭}}} EN
  \end{itemize}
 \item[] \textit{Nervilia} 脈葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+alishanensis}{\textit{N. alishanensis} T.C.Hsu, S.W.Chung \& C.M.Kuo}  \index{Nervilia@\textit{Nervilia}!alishanensis@\textit{alishanensis}}  \index{Nervilia@\textit{Nervilia}!brevilobata@\textit{brevilobata}{\\\noindent(= \textit{Nervilia alishanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山脈葉蘭&T2_new_value=true&fr=y}}{阿里山脈葉蘭(短梗脈葉蘭)} \index{阿里山脈葉蘭} \index{短梗脈葉蘭@{短梗脈葉蘭(=阿里山脈葉蘭)}} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+aragoana}{\textit{N. aragoana} Gaud.}  \index{Nervilia@\textit{Nervilia}!aragoana@\textit{aragoana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=東亞脈葉蘭&T2_new_value=true&fr=y}}{東亞脈葉蘭}\index{東亞脈葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+crociformis}{\textit{N. crociformis} (Zoll. \& Moritzi) Seidenf.}  \index{Nervilia@\textit{Nervilia}!crociformis@\textit{crociformis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=四重溪脈葉蘭&T2_new_value=true&fr=y}}{四重溪脈葉蘭}\index{四重溪脈葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+cumberlegei}{\textit{N. cumberlegei} Seidenf. \& Smitin.}  \index{Nervilia@\textit{Nervilia}!cumberlegei@\textbf{\textit{cumberlegei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=古氏脈葉蘭&T2_new_value=true&fr=y}}{古氏脈葉蘭}\index{古氏脈葉蘭@{\Song{古氏脈葉蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+hungii}{\textit{N. hungii} T.C.Hsu}  \index{Nervilia@\textit{Nervilia}!hungii@\textbf{\textit{hungii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐮唇脈葉蘭&T2_new_value=true&fr=y}}{鐮唇脈葉蘭}\index{鐮唇脈葉蘭@{\Song{鐮唇脈葉蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+lanyuensis}{\textit{N. lanyuensis} S.S.Ying}  \index{Nervilia@\textit{Nervilia}!lanyuensis@\textit{lanyuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼脈葉蘭&T2_new_value=true&fr=y}}{蘭嶼脈葉蘭}\index{蘭嶼脈葉蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+linearilabia}{\textit{N. linearilabia} T.-P.Lin}  \index{Nervilia@\textit{Nervilia}!linearilabia@\textit{linearilabia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小麥脈葉蘭&T2_new_value=true&fr=y}}{小麥脈葉蘭}\index{小麥脈葉蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+plicata}{\textit{N. plicata} (Andr.) Schltr.}  \index{Nervilia@\textit{Nervilia}!plicata@\textit{plicata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花脈葉蘭&T2_new_value=true&fr=y}}{紫花脈葉蘭}\index{紫花脈葉蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+purpureotincta}{\textit{N. purpureotincta} T.C.Hsu}  \index{Nervilia@\textit{Nervilia}!purpureotincta@\textit{purpureotincta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寬唇脈葉蘭&T2_new_value=true&fr=y}}{寬唇脈葉蘭}\index{寬唇脈葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+ratis}{\textit{N. ratis} T.P.Lin \& Y.N.Chang}  \index{Nervilia@\textit{Nervilia}!ratis@\textit{ratis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三伯脈葉蘭&T2_new_value=true&fr=y}}{三伯脈葉蘭}\index{三伯脈葉蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+tahanshanensis}{\textit{N. tahanshanensis} T.P.Lin \& W.M.Lin}  \index{Nervilia@\textit{Nervilia}!tahanshanensis@\textit{tahanshanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大漢山脈葉蘭&T2_new_value=true&fr=y}}{大漢山脈葉蘭}\index{大漢山脈葉蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+taitoensis}{\textit{N. taitoensis} (Hayata) Schltr.}  \index{Nervilia@\textit{Nervilia}!taitoensis@\textit{taitoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=台東脈葉蘭&T2_new_value=true&fr=y}}{台東脈葉蘭}\index{台東脈葉蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nervilia+taiwaniana}{\textit{N. taiwaniana} S.S.Ying}  \index{Nervilia@\textit{Nervilia}!taiwaniana@\textit{taiwaniana}}  \index{Nervilia@\textit{Nervilia}!nipponica@\textit{nipponica}{\\\noindent(= \textit{Nervilia taiwaniana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單花脈葉蘭&T2_new_value=true&fr=y}}{單花脈葉蘭}\index{單花脈葉蘭} LC
  \end{itemize}
 \item[] \textit{Oberonia} 莪白蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+arisanensis}{\textit{O. arisanensis} Hayata}  \index{Oberonia@\textit{Oberonia}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山莪白蘭&T2_new_value=true&fr=y}}{阿里山莪白蘭}\index{阿里山莪白蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+caulescens}{\textit{O. caulescens} Lindl. ex Wall.}  \index{Oberonia@\textit{Oberonia}!caulescens@\textit{caulescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二裂唇莪白蘭&T2_new_value=true&fr=y}}{二裂唇莪白蘭}\index{二裂唇莪白蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+formosana}{\textit{O. formosana} Hayata}  \index{Oberonia@\textit{Oberonia}!formosana@\textit{formosana}}  \index{Oberonia@\textit{Oberonia}!japonica@\textit{japonica}{\\\noindent(= \textit{Oberonia formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣莪白蘭&T2_new_value=true&fr=y}}{臺灣莪白蘭}\index{臺灣莪白蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+gigantea}{\textit{O. gigantea} Fukuy.}  \index{Oberonia@\textit{Oberonia}!gigantea@\textbf{\textit{gigantea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大莪白蘭&T2_new_value=true&fr=y}}{大莪白蘭}\index{大莪白蘭@{\Song{大莪白蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+insularis}{\textit{O. insularis} Hayata}  \index{Oberonia@\textit{Oberonia}!insularis@\textbf{\textit{insularis}}}  \index{Oberonia@\textit{Oberonia}!pumila@\textit{pumila}{\\\noindent(= \textit{Oberonia insularis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小騎士蘭&T2_new_value=true&fr=y}}{小騎士蘭}\index{小騎士蘭@{\Song{小騎士蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+kusukusensis}{\textit{O. kusukusensis} Hayata}  \index{Oberonia@\textit{Oberonia}!kusukusensis@\textit{kusukusensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛莪白蘭&T2_new_value=true&fr=y}}{高士佛莪白蘭}\index{高士佛莪白蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+linguae}{\textit{O. linguae} T.P.Lin \& Y.N.Chang}  \index{Oberonia@\textit{Oberonia}!linguae@\textit{linguae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓唇莪白蘭&T2_new_value=true&fr=y}}{圓唇莪白蘭}\index{圓唇莪白蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+pumila+var.+rotundum}{\textit{O. pumila} (Fukuy. ex S.C.Chen \& K.Y.Lang) S.S.Ying ex Ormerod var. \textit{rotundum} T.P.Lin \& W.M.Lin}  \index{Oberonia@\textit{Oberonia}!pumila@\textit{pumila}!var. rotundum@var. \textit{rotundum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓唇小騎士蘭&T2_new_value=true&fr=y}}{圓唇小騎士蘭}\index{圓唇小騎士蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+rosea}{\textit{O. rosea} Hook.f.}  \index{Oberonia@\textit{Oberonia}!rosea@\textbf{\textit{rosea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂瓣莪白蘭&T2_new_value=true&fr=y}}{裂瓣莪白蘭}\index{裂瓣莪白蘭@{\Song{裂瓣莪白蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+segawae}{\textit{O. segawae} T.C.Hsu \& S.W.Chung}  \index{Oberonia@\textit{Oberonia}!segawae@\textbf{\textit{segawae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=齒唇莪白蘭&T2_new_value=true&fr=y}}{齒唇莪白蘭}\index{齒唇莪白蘭@{\Song{齒唇莪白蘭}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonia+seidenfadenii}{\textit{O. seidenfadenii} (H.J.Su) Ormerod}  \index{Oberonia@\textit{Oberonia}!seidenfadenii@\textbf{\textit{seidenfadenii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花小騎士蘭&T2_new_value=true&fr=y}}{密花小騎士蘭}\index{密花小騎士蘭@{\Song{密花小騎士蘭}}}\# EN
  \end{itemize}
 \item[] \textit{Oberonioides} 小柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oberonioides+pusillus}{\textit{O. pusillus} (Rolfe) H.B.Marg. \& D.L.Szlach.}  \index{Oberonioides@\textit{Oberonioides}!pusillus@\textbf{\textit{pusillus}}}  \index{Malaxis@\textit{Malaxis}!microtatantha@\textit{microtatantha}{\\\noindent(= \textit{Oberonioides pusillus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小軟葉蘭&T2_new_value=true&fr=y}}{小軟葉蘭}\index{小軟葉蘭@{\Song{小軟葉蘭}}} VU
  \end{itemize}
 \item[] \textit{Odontochilus} 齒唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+brevistylus}{\textit{O. brevistylus} Hook.f.}  \index{Odontochilus@\textit{Odontochilus}!brevistylus@\textit{brevistylus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短柱齒唇蘭&T2_new_value=true&fr=y}}{短柱齒唇蘭}\index{短柱齒唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+drymoglossifolius}{\textit{O. drymoglossifolius} (Hayata) T.Yukawa}  \index{Odontochilus@\textit{Odontochilus}!drymoglossifolius@\textit{drymoglossifolius}}  \index{Myrmechis@\textit{Myrmechis}!drymoglossifolia@\textit{drymoglossifolia}{\\\noindent(= \textit{Odontochilus drymoglossifolius})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花金唇蘭&T2_new_value=true&fr=y}}{白花金唇蘭}\index{白花金唇蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+elwesii}{\textit{O. elwesii} Clarke ex Hook.f.}  \index{Odontochilus@\textit{Odontochilus}!elwesii@\textbf{\textit{elwesii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫葉齒唇蘭&T2_new_value=true&fr=y}}{紫葉齒唇蘭}\index{紫葉齒唇蘭@{\Song{紫葉齒唇蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+formosanus}{\textit{O. formosanus} T.C.Hsu}  \index{Odontochilus@\textit{Odontochilus}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣全唇蘭&T2_new_value=true&fr=y}}{臺灣全唇蘭}\index{臺灣全唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+inabai}{\textit{O. inabai} (Hayata) Hayata ex T.P.Lin}  \index{Odontochilus@\textit{Odontochilus}!inabai@\textit{inabai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單囊齒唇蘭&T2_new_value=true&fr=y}}{單囊齒唇蘭}\index{單囊齒唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+integrus}{\textit{O. integrus} (Fukuy.) T.Yukawa}  \index{Odontochilus@\textit{Odontochilus}!integrus@\textbf{\textit{integrus}}}  \index{Vexillabium@\textit{Vexillabium}!integrum@\textit{integrum}{\\\noindent(= \textit{Odontochilus integrus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綠葉旗唇蘭&T2_new_value=true&fr=y}}{綠葉旗唇蘭}\index{綠葉旗唇蘭@{\Song{綠葉旗唇蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+lanceolatus}{\textit{O. lanceolatus} (Lindl.) Blume}  \index{Odontochilus@\textit{Odontochilus}!lanceolatus@\textit{lanceolatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙囊齒唇蘭&T2_new_value=true&fr=y}}{雙囊齒唇蘭}\index{雙囊齒唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+nanlingensis}{\textit{O. nanlingensis} (L.P.Siu \& K.Y.Lang) Ormerod}  \index{Odontochilus@\textit{Odontochilus}!nanlingensis@\textit{nanlingensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南嶺齒唇蘭&T2_new_value=true&fr=y}}{南嶺齒唇蘭}\index{南嶺齒唇蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+poilanei}{\textit{O. poilanei} (Gagnep.) Ormerod}  \index{Odontochilus@\textit{Odontochilus}!poilanei@\textbf{\textit{poilanei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=齒爪齒唇蘭&T2_new_value=true&fr=y}}{齒爪齒唇蘭}\index{齒爪齒唇蘭@{\Song{齒爪齒唇蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Odontochilus+yakushimensis}{\textit{O. yakushimensis} (Yamam.) T.Yukawa}  \index{Odontochilus@\textit{Odontochilus}!yakushimensis@\textit{yakushimensis}}  \index{Vexillabium@\textit{Vexillabium}!yakushimense@\textit{yakushimense}{\\\noindent(= \textit{Odontochilus yakushimensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫葉旗唇蘭&T2_new_value=true&fr=y}}{紫葉旗唇蘭}\index{紫葉旗唇蘭} LC
  \end{itemize}
 \item[] \textit{Oeceoclades} 芋蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oeceoclades+pulchra}{\textit{O. pulchra} (Thouars) M.A.Clem. \& P.J.Cribb}  \index{Oeceoclades@\textit{Oeceoclades}!pulchra@\textit{pulchra}}  \index{Eulophia@\textit{Eulophia}!pulchra@\textit{pulchra}{\\\noindent(= \textit{Oeceoclades pulchra})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南洋芋蘭&T2_new_value=true&fr=y}}{南洋芋蘭}\index{南洋芋蘭} NT
  \end{itemize}
 \item[] \textit{Oreorchis} 山蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreorchis+bilamellata}{\textit{O. bilamellata} Fukuy.}  \index{Oreorchis@\textit{Oreorchis}!bilamellata@\textbf{\textit{bilamellata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙板山蘭&T2_new_value=true&fr=y}}{雙板山蘭}\index{雙板山蘭@{\Song{雙板山蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreorchis+fargesii}{\textit{O. fargesii} Finet}  \index{Oreorchis@\textit{Oreorchis}!fargesii@\textbf{\textit{fargesii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花山蘭&T2_new_value=true&fr=y}}{密花山蘭}\index{密花山蘭@{\Song{密花山蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreorchis+indica}{\textit{O. indica} (Lindl.) Hook.f.}  \index{Oreorchis@\textit{Oreorchis}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=印度山蘭&T2_new_value=true&fr=y}}{印度山蘭}\index{印度山蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreorchis+micrantha}{\textit{O. micrantha} Lindl.}  \index{Oreorchis@\textit{Oreorchis}!micrantha@\textbf{\textit{micrantha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖山蘭&T2_new_value=true&fr=y}}{南湖山蘭}\index{南湖山蘭@{\Song{南湖山蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreorchis+patens}{\textit{O. patens} (Lindl) Lindl.}  \index{Oreorchis@\textit{Oreorchis}!patens@\textit{patens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細花山蘭&T2_new_value=true&fr=y}}{細花山蘭}\index{細花山蘭} NT
  \end{itemize}
 \item[] \textit{Pachystoma} 粉口蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pachystoma+pubesens}{\textit{P. pubesens} Blume}  \index{Pachystoma@\textit{Pachystoma}!pubesens@\textbf{\textit{pubesens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粉口蘭&T2_new_value=true&fr=y}}{粉口蘭}\index{粉口蘭@{\Song{粉口蘭}}} CR
  \end{itemize}
 \item[] \textit{Papilionanthe} 鳳蝶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Papilionanthe+pseudotaiwaniana}{\textit{P. pseudotaiwaniana} T.C.Hsu}  \index{Papilionanthe@\textit{Papilionanthe}!pseudotaiwaniana@\textit{pseudotaiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬臺灣鳳蝶蘭&T2_new_value=true&fr=y}}{擬臺灣鳳蝶蘭}\index{擬臺灣鳳蝶蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Papilionanthe+taiwaniana}{\textit{P. taiwaniana} (S.S.Ying) Ormerod}  \index{Papilionanthe@\textit{Papilionanthe}!taiwaniana@\textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣萬代蘭&T2_new_value=true&fr=y}}{臺灣萬代蘭}\index{臺灣萬代蘭} DD
  \end{itemize}
 \item[] \textit{Paraphaius} 鶴頂蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraphaius+flavus}{\textit{P. flavus} (Blume) J.W.Zhai, Z.J.Liu \& F.W.Xing}  \index{Paraphaius@\textit{Paraphaius}!flavus@\textit{flavus}}  \index{Phaius@\textit{Phaius}!flavus@\textit{flavus}{\\\noindent(= \textit{Paraphaius flavus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃鶴頂蘭&T2_new_value=true&fr=y}}{黃鶴頂蘭}\index{黃鶴頂蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paraphaius+takeoi}{\textit{P. takeoi} (Hayata) J.W.Zhai, Z.J.Liu \& F.W.Xing}  \index{Paraphaius@\textit{Paraphaius}!takeoi@\textbf{\textit{takeoi}}}  \index{Phaius@\textit{Phaius}!takeoi@\textit{takeoi}{\\\noindent(= \textit{Paraphaius takeoi})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗莖鶴頂蘭&T2_new_value=true&fr=y}}{粗莖鶴頂蘭}\index{粗莖鶴頂蘭@{\Song{粗莖鶴頂蘭}}} EN
  \end{itemize}
 \item[] \textit{Peristylus} 闊蕊蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+calcaratus}{\textit{P. calcaratus} (Rolfe) S.Y.Hu}  \index{Peristylus@\textit{Peristylus}!calcaratus@\textit{calcaratus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貓鬚蘭&T2_new_value=true&fr=y}}{貓鬚蘭}\index{貓鬚蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+formosanus}{\textit{P. formosanus} (Schltr.) T.P.Lin}  \index{Peristylus@\textit{Peristylus}!formosanus@\textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鷺草&T2_new_value=true&fr=y}}{臺灣鷺草}\index{臺灣鷺草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+goodyeroides}{\textit{P. goodyeroides} (D.Don) Lindl.}  \index{Peristylus@\textit{Peristylus}!goodyeroides@\textit{goodyeroides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投闊蕊蘭&T2_new_value=true&fr=y}}{南投闊蕊蘭}\index{南投闊蕊蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+gracilis}{\textit{P. gracilis} Blume}  \index{Peristylus@\textit{Peristylus}!gracilis@\textbf{\textit{gracilis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=纖細闊蕊蘭&T2_new_value=true&fr=y}}{纖細闊蕊蘭}\index{纖細闊蕊蘭@{\Song{纖細闊蕊蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+intrudens}{\textit{P. intrudens} (Ames) Ormerod}  \index{Peristylus@\textit{Peristylus}!intrudens@\textbf{\textit{intrudens}}}  \index{Peristylus@\textit{Peristylus}!lacertifer@\textit{lacertifer}!var. taipoensis@var. \textit{taipoensis}{\\\noindent(=\textit{Peristylus intrudens})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短裂闊蕊蘭&T2_new_value=true&fr=y}}{短裂闊蕊蘭}\index{短裂闊蕊蘭@{\Song{短裂闊蕊蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+lacertifer+var.+lacertifer}{\textit{P. lacertifer} (Lindl.) J.J.Sm. var. \textit{lacertifer}}  \index{Peristylus@\textit{Peristylus}!lacertifer@\textit{lacertifer}!var. lacertifer@var. \textit{lacertifer}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂唇闊蕊蘭&T2_new_value=true&fr=y}}{裂唇闊蕊蘭}\index{裂唇闊蕊蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peristylus+monticola}{\textit{P. monticola} (Ridl.) Seidenf.}  \index{Peristylus@\textit{Peristylus}!monticola@\textit{monticola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=深山闊蕊蘭&T2_new_value=true&fr=y}}{深山闊蕊蘭}\index{深山闊蕊蘭} DD
  \end{itemize}
 \item[] \textit{Phaius} 鶴頂蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phaius+mishmensis}{\textit{P. mishmensis} (Lindl. \& Paxt.) Rchb.f.}  \index{Phaius@\textit{Phaius}!mishmensis@\textit{mishmensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細莖鶴頂蘭&T2_new_value=true&fr=y}}{細莖鶴頂蘭}\index{細莖鶴頂蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phaius+tankervilleae}{\textit{P. tankervilleae} (Banks ex L'Her.) Blume}  \index{Phaius@\textit{Phaius}!tankervilleae@\textit{tankervilleae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅鶴頂蘭&T2_new_value=true&fr=y}}{紅鶴頂蘭}\index{紅鶴頂蘭} NT
  \end{itemize}
 \item[] \textit{Phalaenopsis} 蝴蝶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phalaenopsis+aphrodite+subsp.+formosana}{\textit{P. aphrodite} Rchb.f. subsp. \textit{formosana} Christenson}  \index{Phalaenopsis@\textit{Phalaenopsis}!aphrodite@\textit{aphrodite}!subsp. formosana@\textbf{subsp. \textit{formosana}}}  \index{Phalaenopsis@\textit{Phalaenopsis}!aphrodite@\textit{aphrodite}{\\\noindent(= \textit{Phalaenopsis aphrodite} subsp. \textit{formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白蝴蝶蘭&T2_new_value=true&fr=y}}{白蝴蝶蘭}\index{白蝴蝶蘭@{\Song{白蝴蝶蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phalaenopsis+equestris}{\textit{P. equestris} (Schauer) Rchb.f.}  \index{Phalaenopsis@\textit{Phalaenopsis}!equestris@\textbf{\textit{equestris}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桃紅蝴蝶蘭&T2_new_value=true&fr=y}}{桃紅蝴蝶蘭}\index{桃紅蝴蝶蘭@{\Song{桃紅蝴蝶蘭}}} CR
  \end{itemize}
 \item[] \textit{Pholidota} 石山桃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pholidota+cantonensis}{\textit{P. cantonensis} Rolfe}  \index{Pholidota@\textit{Pholidota}!cantonensis@\textit{cantonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏來石山桃&T2_new_value=true&fr=y}}{烏來石山桃}\index{烏來石山桃} LC
  \end{itemize}
 \item[] \textit{Phreatia} 芙樂蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phreatia+caulescens}{\textit{P. caulescens} Ames}  \index{Phreatia@\textit{Phreatia}!caulescens@\textbf{\textit{caulescens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=垂莖芙樂蘭&T2_new_value=true&fr=y}}{垂莖芙樂蘭}\index{垂莖芙樂蘭@{\Song{垂莖芙樂蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phreatia+formosana}{\textit{P. formosana} Rolfe}  \index{Phreatia@\textit{Phreatia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寶島芙樂蘭&T2_new_value=true&fr=y}}{寶島芙樂蘭}\index{寶島芙樂蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phreatia+morii}{\textit{P. morii} Hayata}  \index{Phreatia@\textit{Phreatia}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大芙樂蘭&T2_new_value=true&fr=y}}{大芙樂蘭}\index{大芙樂蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phreatia+taiwaniana}{\textit{P. taiwaniana} Fukuy.}  \index{Phreatia@\textit{Phreatia}!taiwaniana@\textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣芙樂蘭&T2_new_value=true&fr=y}}{臺灣芙樂蘭}\index{臺灣芙樂蘭}\# NT
  \end{itemize}
 \item[] \textit{Pinalia} 絨蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinalia+amica}{\textit{P. amica} (Rchb.f.) Kuntze}  \index{Pinalia@\textit{Pinalia}!amica@\textit{amica}}  \index{Eria@\textit{Eria}!amica@\textit{amica}{\\\noindent(= \textit{Pinalia amica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小腳筒蘭&T2_new_value=true&fr=y}}{小腳筒蘭}\index{小腳筒蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinalia+formosana}{\textit{P. formosana} (Rolfe) Ormerod}  \index{Pinalia@\textit{Pinalia}!formosana@\textit{formosana}}  \index{Eria@\textit{Eria}!tomentosiflora@\textit{tomentosiflora}{\\\noindent(= \textit{Pinalia formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樹絨蘭&T2_new_value=true&fr=y}}{樹絨蘭}\index{樹絨蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinalia+japonica}{\textit{P. japonica} (Maxim.) Ormerod}  \index{Pinalia@\textit{Pinalia}!japonica@\textit{japonica}}  \index{Eria@\textit{Eria}!japonica@\textit{japonica}{\\\noindent(= \textit{Pinalia japonica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=連珠絨蘭&T2_new_value=true&fr=y}}{連珠絨蘭}\index{連珠絨蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinalia+ovata}{\textit{P. ovata} (Lindl.) W.Suarez \& Cootes}  \index{Pinalia@\textit{Pinalia}!ovata@\textit{ovata}}  \index{Eria@\textit{Eria}!ovata@\textit{ovata}{\\\noindent(= \textit{Pinalia ovata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大腳筒蘭&T2_new_value=true&fr=y}}{大腳筒蘭}\index{大腳筒蘭} LC
  \end{itemize}
 \item[] \textit{Platanthera} 粉蝶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+brevicalcarata}{\textit{P. brevicalcarata} Hayata}  \index{Platanthera@\textit{Platanthera}!brevicalcarata@\textit{brevicalcarata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短距粉蝶蘭&T2_new_value=true&fr=y}}{短距粉蝶蘭}\index{短距粉蝶蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+devolii}{\textit{P. devolii} (T.P.Lin \& T.W.Hu) T.P.Lin \& K.Inoue}  \index{Platanthera@\textit{Platanthera}!devolii@\textit{devolii}}  \index{Tulotis@\textit{Tulotis}!devolii@\textit{devolii}{\\\noindent(= \textit{Platanthera devolii})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉蜻蜓蘭&T2_new_value=true&fr=y}}{長葉蜻蜓蘭}\index{長葉蜻蜓蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+formosana}{\textit{P. formosana} (T.P.Lin \& K.Inoue) Efimov}  \index{Platanthera@\textit{Platanthera}!formosana@\textit{formosana}}  \index{Platanthera@\textit{Platanthera}!mandarinorum@\textit{mandarinorum}!subsp. formosana@subsp. \textit{formosana}{\\\noindent(=\textit{Platanthera formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=惠粉蝶蘭&T2_new_value=true&fr=y}}{惠粉蝶蘭}\index{惠粉蝶蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+longibracteata}{\textit{P. longibracteata} Hayata}  \index{Platanthera@\textit{Platanthera}!longibracteata@\textit{longibracteata}}  \index{Platanthera@\textit{Platanthera}!sachalinensis@\textit{sachalinensis}{\\\noindent(= \textit{Platanthera longibracteata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山粉蝶蘭&T2_new_value=true&fr=y}}{高山粉蝶蘭}\index{高山粉蝶蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+longicalcarata}{\textit{P. longicalcarata} Hayata}  \index{Platanthera@\textit{Platanthera}!longicalcarata@\textbf{\textit{longicalcarata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長距粉蝶蘭&T2_new_value=true&fr=y}}{長距粉蝶蘭}\index{長距粉蝶蘭@{\Song{長距粉蝶蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+minor}{\textit{P. minor} (Miq.) Rchb.f.}  \index{Platanthera@\textit{Platanthera}!minor@\textit{minor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=卵唇粉蝶蘭&T2_new_value=true&fr=y}}{卵唇粉蝶蘭}\index{卵唇粉蝶蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+ophrydioides}{\textit{P. ophrydioides} F.Schmidt}  \index{Platanthera@\textit{Platanthera}!ophrydioides@\textit{ophrydioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=千鳥粉蝶蘭&T2_new_value=true&fr=y}}{千鳥粉蝶蘭}\index{千鳥粉蝶蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+pachyglossa}{\textit{P. pachyglossa} Hayata}  \index{Platanthera@\textit{Platanthera}!pachyglossa@\textit{pachyglossa}}  \index{Platanthera@\textit{Platanthera}!mandarinorum@\textit{mandarinorum}!subsp. pachyglossa@subsp. \textit{pachyglossa}{\\\noindent(=\textit{Platanthera pachyglossa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚唇粉蝶蘭&T2_new_value=true&fr=y}}{厚唇粉蝶蘭}\index{厚唇粉蝶蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+sonoharae}{\textit{P. sonoharae} Masam.}  \index{Platanthera@\textit{Platanthera}!sonoharae@\textbf{\textit{sonoharae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球蜻蛉蘭&T2_new_value=true&fr=y}}{琉球蜻蛉蘭}\index{琉球蜻蛉蘭@{\Song{琉球蜻蛉蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+stenoglossa}{\textit{P. stenoglossa} Hayata}  \index{Platanthera@\textit{Platanthera}!stenoglossa@\textit{stenoglossa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狹唇粉蝶蘭&T2_new_value=true&fr=y}}{狹唇粉蝶蘭}\index{狹唇粉蝶蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+taiwanensis}{\textit{P. taiwanensis} (S.S.Ying) S.C.Chen, S.W.Gale \& P.J.Cribb}  \index{Platanthera@\textit{Platanthera}!taiwanensis@\textit{taiwanensis}}  \index{Platanthera@\textit{Platanthera}!nantousylvatica@\textit{nantousylvatica}{\\\noindent(= \textit{Platanthera taiwanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蜻蛉蘭&T2_new_value=true&fr=y}}{臺灣蜻蛉蘭(南投蜻蛉蘭)} \index{臺灣蜻蛉蘭} \index{南投蜻蛉蘭@{南投蜻蛉蘭(=臺灣蜻蛉蘭)}} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Platanthera+yangmeiensis}{\textit{P. yangmeiensis} T.P.Lin}  \index{Platanthera@\textit{Platanthera}!yangmeiensis@\textit{yangmeiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=陰粉蝶蘭&T2_new_value=true&fr=y}}{陰粉蝶蘭}\index{陰粉蝶蘭}\# NT
  \end{itemize}
 \item[] \textit{Pleione} 一葉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pleione+bulbocodioides}{\textit{P. bulbocodioides} (Franch.) Rolfe}  \index{Pleione@\textit{Pleione}!bulbocodioides@\textit{bulbocodioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣一葉蘭&T2_new_value=true&fr=y}}{臺灣一葉蘭}\index{臺灣一葉蘭} NT
  \end{itemize}
 \item[] \textit{Pogonia} 鬚唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pogonia+minor}{\textit{P. minor} (Makino) Makino}  \index{Pogonia@\textit{Pogonia}!minor@\textbf{\textit{minor}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小鬚唇蘭&T2_new_value=true&fr=y}}{小鬚唇蘭}\index{小鬚唇蘭@{\Song{小鬚唇蘭}}} EN
  \end{itemize}
 \item[] \textit{Pomatocalpa} 繡球蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pomatocalpa+acuminatum}{\textit{P. acuminatum} (Rolfe) Schltr.}  \index{Pomatocalpa@\textit{Pomatocalpa}!acuminatum@\textit{acuminatum}}  \index{Pomatocalpa@\textit{Pomatocalpa}!acuminata@\textit{acuminata}{\\\noindent(= \textit{Pomatocalpa acuminatum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃繡球蘭&T2_new_value=true&fr=y}}{黃繡球蘭}\index{黃繡球蘭}\# NT
  \end{itemize}
 \item[] \textit{Ponerorchis} 小蝶蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ponerorchis+kiraishiensis}{\textit{P. kiraishiensis} (Hayata) Ohwi}  \index{Ponerorchis@\textit{Ponerorchis}!kiraishiensis@\textit{kiraishiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅小蝶蘭&T2_new_value=true&fr=y}}{紅小蝶蘭}\index{紅小蝶蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ponerorchis+taiwanensis}{\textit{P. taiwanensis} (Fukuy.) Ohwi}  \index{Ponerorchis@\textit{Ponerorchis}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣小蝶蘭&T2_new_value=true&fr=y}}{臺灣小蝶蘭}\index{臺灣小蝶蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ponerorchis+takasago-montana}{\textit{P. takasago-montana} (Masam.) Ohwi}  \index{Ponerorchis@\textit{Ponerorchis}!takasago-montana@\textbf{\textit{takasago-montana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山小蝶蘭&T2_new_value=true&fr=y}}{高山小蝶蘭}\index{高山小蝶蘭@{\Song{高山小蝶蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ponerorchis+tominagae}{\textit{P. tominagae} (Hayata) H.J. Su \& J.J. Chen}  \index{Ponerorchis@\textit{Ponerorchis}!tominagae@\textbf{\textit{tominagae}}}  \index{Orchis@\textit{Orchis}!kunihikoana@\textit{kunihikoana}{\\\noindent(= \textit{Ponerorchis tominagae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅斑蘭&T2_new_value=true&fr=y}}{紅斑蘭(大水窟紅蘭)} \index{紅斑蘭@{\Song{紅斑蘭}}} \index{大水窟紅蘭@{\Song{大水窟紅蘭(=紅斑蘭)}}}\# VU
  \end{itemize}
 \item[] \textit{Pseudoliparis} 小柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pseudoliparis+moluccana}{\textit{P. moluccana} (J.J.Sm.) H.B.Marg.}  \index{Pseudoliparis@\textit{Pseudoliparis}!moluccana@\textbf{\textit{moluccana}}}  \index{Malaxis@\textit{Malaxis}!ramosii@\textit{ramosii}{\\\noindent(= \textit{Pseudoliparis moluccana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓唇軟葉蘭&T2_new_value=true&fr=y}}{圓唇軟葉蘭}\index{圓唇軟葉蘭@{\Song{圓唇軟葉蘭}}} VU
  \end{itemize}
 \item[] \textit{Rhomboda} 白點伴蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhomboda+tokioi}{\textit{R. tokioi} (Fukuy.) Ormerod}  \index{Rhomboda@\textit{Rhomboda}!tokioi@\textit{tokioi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白點伴蘭&T2_new_value=true&fr=y}}{白點伴蘭}\index{白點伴蘭} LC
  \end{itemize}
 \item[] \textit{Saccolabiopsis} 假囊唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Saccolabiopsis+viridiflora+subsp.+taiwaniana}{\textit{S. viridiflora} Aver. subsp. \textit{taiwaniana} (S.W.Chung, T.C.Hsu \& T.Yukawa) T.C.Hsu}  \index{Saccolabiopsis@\textit{Saccolabiopsis}!viridiflora@\textit{viridiflora}!subsp. taiwaniana@\textbf{subsp. \textit{taiwaniana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣擬囊唇蘭&T2_new_value=true&fr=y}}{臺灣擬囊唇蘭}\index{臺灣擬囊唇蘭@{\Song{臺灣擬囊唇蘭}}}\# EN
  \end{itemize}
 \item[] \textit{Schoenorchis} 羞花蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schoenorchis+vanoverberghii}{\textit{S. vanoverberghii} Ames}  \index{Schoenorchis@\textit{Schoenorchis}!vanoverberghii@\textbf{\textit{vanoverberghii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘆蘭&T2_new_value=true&fr=y}}{蘆蘭}\index{蘆蘭@{\Song{蘆蘭}}} VU
  \end{itemize}
 \item[] \textit{Spathoglottis} 苞舌蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spathoglottis+plicata}{\textit{S. plicata} Blume}  \index{Spathoglottis@\textit{Spathoglottis}!plicata@\textbf{\textit{plicata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫苞舌蘭&T2_new_value=true&fr=y}}{紫苞舌蘭}\index{紫苞舌蘭@{\Song{紫苞舌蘭}}} CR
  \end{itemize}
 \item[] \textit{Spiranthes} 綬草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiranthes+hongkongensis}{\textit{S. hongkongensis} S.Y.Hu \& Barretto}  \index{Spiranthes@\textit{Spiranthes}!hongkongensis@\textit{hongkongensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香港綬草&T2_new_value=true&fr=y}}{香港綬草}\index{香港綬草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiranthes+sinensis}{\textit{S. sinensis} (Pers.) Ames}  \index{Spiranthes@\textit{Spiranthes}!sinensis@\textit{sinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=綬草&T2_new_value=true&fr=y}}{綬草}\index{綬草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiranthes+suishaensis}{\textit{S. suishaensis} (Hayata) Schltr.}  \index{Spiranthes@\textit{Spiranthes}!suishaensis@\textit{suishaensis}}  \index{Spiranthes@\textit{Spiranthes}!nivea@\textit{nivea}{\\\noindent(= \textit{Spiranthes suishaensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水社綬草&T2_new_value=true&fr=y}}{水社綬草(義富綬草)} \index{水社綬草} \index{義富綬草@{義富綬草(=水社綬草)}}\# NT
  \end{itemize}
 \item[] \textit{Stereosandra} 堅葯蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stereosandra+javanica}{\textit{S. javanica} Blume}  \index{Stereosandra@\textit{Stereosandra}!javanica@\textbf{\textit{javanica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=肉葯蘭&T2_new_value=true&fr=y}}{肉葯蘭}\index{肉葯蘭@{\Song{肉葯蘭}}} EN
  \end{itemize}
 \item[] \textit{Stigmatodactylus} 絲柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stigmatodactylus+shikokiana}{\textit{S. shikokiana} Maxim. ex Makino}  \index{Stigmatodactylus@\textit{Stigmatodactylus}!shikokiana@\textbf{\textit{shikokiana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=絲柱蘭&T2_new_value=true&fr=y}}{絲柱蘭}\index{絲柱蘭@{\Song{絲柱蘭}}} VU
  \end{itemize}
 \item[] \textit{Styloglossum} 落苞蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styloglossum+actinomorphum}{\textit{S. actinomorphum} (Fukuy.) T.C.Hsu}  \index{Styloglossum@\textit{Styloglossum}!actinomorphum@\textit{actinomorphum}}  \index{Calanthe@\textit{Calanthe}!actinomorpha@\textit{actinomorpha}{\\\noindent(= \textit{Styloglossum actinomorphum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=輻形根節蘭&T2_new_value=true&fr=y}}{輻形根節蘭}\index{輻形根節蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styloglossum+densiflorum}{\textit{S. densiflorum} (Lindl.) T.Yukawa \& P.J.Cribb}  \index{Styloglossum@\textit{Styloglossum}!densiflorum@\textit{densiflorum}}  \index{Calanthe@\textit{Calanthe}!densiflora@\textit{densiflora}{\\\noindent(= \textit{Styloglossum densiflorum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=竹葉根節蘭&T2_new_value=true&fr=y}}{竹葉根節蘭}\index{竹葉根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styloglossum+formosanum}{\textit{S. formosanum} (Rolfe) T.P.Lin}  \index{Styloglossum@\textit{Styloglossum}!formosanum@\textit{formosanum}}  \index{Calanthe@\textit{Calanthe}!speciosa@\textit{speciosa}{\\\noindent(= \textit{Styloglossum formosanum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣根節蘭&T2_new_value=true&fr=y}}{臺灣根節蘭}\index{臺灣根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styloglossum+lyroglossum}{\textit{S. lyroglossum} (Rchb.f.) T.Yukawa \& P.J.Cribb}  \index{Styloglossum@\textit{Styloglossum}!lyroglossum@\textit{lyroglossum}}  \index{Calanthe@\textit{Calanthe}!lyroglossa@\textit{lyroglossa}{\\\noindent(= \textit{Styloglossum lyroglossum})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=連翹根節蘭&T2_new_value=true&fr=y}}{連翹根節蘭}\index{連翹根節蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styloglossum+pseudodensiflorum}{\textit{S. pseudodensiflorum} T.C.Hsu}  \index{Styloglossum@\textit{Styloglossum}!pseudodensiflorum@\textit{pseudodensiflorum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬竹葉根節蘭&T2_new_value=true&fr=y}}{擬竹葉根節蘭}\index{擬竹葉根節蘭} DD
  \end{itemize}
 \item[] \textit{Taeniophyllum} 小蜘蛛蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+aphyllum}{\textit{T. aphyllum} (Makino) Makino}  \index{Taeniophyllum@\textit{Taeniophyllum}!aphyllum@\textit{aphyllum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小蜘蛛蘭&T2_new_value=true&fr=y}}{小蜘蛛蘭}\index{小蜘蛛蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+compacta}{\textit{T. compacta} Ames}  \index{Taeniophyllum@\textit{Taeniophyllum}!compacta@\textit{compacta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假蜘蛛蘭&T2_new_value=true&fr=y}}{假蜘蛛蘭}\index{假蜘蛛蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+complanatum}{\textit{T. complanatum} Fukuy.}  \index{Taeniophyllum@\textit{Taeniophyllum}!complanatum@\textit{complanatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=扁蜘蛛蘭&T2_new_value=true&fr=y}}{扁蜘蛛蘭}\index{扁蜘蛛蘭}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+crassipes}{\textit{T. crassipes} Fukuy.}  \index{Taeniophyllum@\textit{Taeniophyllum}!crassipes@\textit{crassipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚蜘蛛蘭&T2_new_value=true&fr=y}}{厚蜘蛛蘭}\index{厚蜘蛛蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+glandulosum}{\textit{T. glandulosum} Blume}  \index{Taeniophyllum@\textit{Taeniophyllum}!glandulosum@\textit{glandulosum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蜘蛛蘭&T2_new_value=true&fr=y}}{蜘蛛蘭}\index{蜘蛛蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Taeniophyllum+radiatum}{\textit{T. radiatum} J.J.Sm.}  \index{Taeniophyllum@\textit{Taeniophyllum}!radiatum@\textit{radiatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大扁根蜘蛛蘭&T2_new_value=true&fr=y}}{大扁根蜘蛛蘭}\index{大扁根蜘蛛蘭} DD
  \end{itemize}
 \item[] \textit{Tainia} 小杜鵑蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tainia+caterva}{\textit{T. caterva} T.P.Lin \& W.M.Lin}  \index{Tainia@\textit{Tainia}!caterva@\textit{caterva}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花杜鵑蘭&T2_new_value=true&fr=y}}{密花杜鵑蘭}\index{密花杜鵑蘭}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tainia+cordifolia}{\textit{T. cordifolia} Hook.f.}  \index{Tainia@\textit{Tainia}!cordifolia@\textit{cordifolia}}  \index{Mischobulbum@\textit{Mischobulbum}!cordifolium@\textit{cordifolium}{\\\noindent(= \textit{Tainia cordifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=心葉葵蘭&T2_new_value=true&fr=y}}{心葉葵蘭}\index{心葉葵蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tainia+dunnii}{\textit{T. dunnii} Rolfe}  \index{Tainia@\textit{Tainia}!dunnii@\textit{dunnii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉杜鵑蘭&T2_new_value=true&fr=y}}{長葉杜鵑蘭}\index{長葉杜鵑蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tainia+hualienia}{\textit{T. hualienia} S.S.Ying}  \index{Tainia@\textit{Tainia}!hualienia@\textit{hualienia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃花小杜鵑蘭&T2_new_value=true&fr=y}}{黃花小杜鵑蘭}\index{黃花小杜鵑蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tainia+latifolia}{\textit{T. latifolia} (Lindl.) Rchb.f.}  \index{Tainia@\textit{Tainia}!latifolia@\textbf{\textit{latifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉杜鵑蘭&T2_new_value=true&fr=y}}{闊葉杜鵑蘭}\index{闊葉杜鵑蘭@{\Song{闊葉杜鵑蘭}}} VU
  \end{itemize}
 \item[] \textit{Thelasis} 八粉蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thelasis+pygmaea}{\textit{T. pygmaea} (Griff.) Blume}  \index{Thelasis@\textit{Thelasis}!pygmaea@\textbf{\textit{pygmaea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=閉花八粉蘭&T2_new_value=true&fr=y}}{閉花八粉蘭}\index{閉花八粉蘭@{\Song{閉花八粉蘭}}} EN
  \end{itemize}
 \item[] \textit{Thrixspermum} 風鈴蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+annamense}{\textit{T. annamense} (Guill.) Garay}  \index{Thrixspermum@\textit{Thrixspermum}!annamense@\textbf{\textit{annamense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白毛風蘭&T2_new_value=true&fr=y}}{白毛風蘭}\index{白毛風蘭@{\Song{白毛風蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+eximium}{\textit{T. eximium} L.O.Williams}  \index{Thrixspermum@\textit{Thrixspermum}!eximium@\textbf{\textit{eximium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=異色風蘭&T2_new_value=true&fr=y}}{異色風蘭}\index{異色風蘭@{\Song{異色風蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+fantasticum}{\textit{T. fantasticum} L.O.Williams}  \index{Thrixspermum@\textit{Thrixspermum}!fantasticum@\textit{fantasticum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金唇風蘭&T2_new_value=true&fr=y}}{金唇風蘭}\index{金唇風蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+formosanum}{\textit{T. formosanum} (Hayata) Schltr.}  \index{Thrixspermum@\textit{Thrixspermum}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣風蘭&T2_new_value=true&fr=y}}{臺灣風蘭}\index{臺灣風蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+laurisilvaticum}{\textit{T. laurisilvaticum} (Fukuy.) Garay}  \index{Thrixspermum@\textit{Thrixspermum}!laurisilvaticum@\textit{laurisilvaticum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃蛾蘭&T2_new_value=true&fr=y}}{黃蛾蘭}\index{黃蛾蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+merguense}{\textit{T. merguense} (Hook.f.) Kuntze}  \index{Thrixspermum@\textit{Thrixspermum}!merguense@\textbf{\textit{merguense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛風蘭&T2_new_value=true&fr=y}}{高士佛風蘭}\index{高士佛風蘭@{\Song{高士佛風蘭}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+pensile}{\textit{T. pensile} Schltr.}  \index{Thrixspermum@\textit{Thrixspermum}!pensile@\textbf{\textit{pensile}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=倒垂風蘭&T2_new_value=true&fr=y}}{倒垂風蘭}\index{倒垂風蘭@{\Song{倒垂風蘭}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+saruwatarii}{\textit{T. saruwatarii} (Hayata) Schltr.}  \index{Thrixspermum@\textit{Thrixspermum}!saruwatarii@\textit{saruwatarii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小白蛾蘭&T2_new_value=true&fr=y}}{小白蛾蘭}\index{小白蛾蘭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thrixspermum+subulatum}{\textit{T. subulatum} Rchb.f.}  \index{Thrixspermum@\textit{Thrixspermum}!subulatum@\textbf{\textit{subulatum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉風蘭&T2_new_value=true&fr=y}}{厚葉風蘭}\index{厚葉風蘭@{\Song{厚葉風蘭}}} VU
  \end{itemize}
 \item[] \textit{Tipularia} 飛鶴蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tipularia+cunninghamii}{\textit{T. cunninghamii} (King \& Prain) S.C.Chen, S.W.Gale \& P.J.Cribb}  \index{Tipularia@\textit{Tipularia}!cunninghamii@\textit{cunninghamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細花軟葉蘭&T2_new_value=true&fr=y}}{細花軟葉蘭}\index{細花軟葉蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tipularia+odorata}{\textit{T. odorata} Fukuy.}  \index{Tipularia@\textit{Tipularia}!odorata@\textit{odorata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖蠅蘭&T2_new_value=true&fr=y}}{南湖蠅蘭}\index{南湖蠅蘭}\# NT
  \end{itemize}
 \item[] \textit{Trichoglottis} 鳳尾蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trichoglottis+luchuensis}{\textit{T. luchuensis} (Rolfe) Garay \& H.R.Sweet}  \index{Trichoglottis@\textit{Trichoglottis}!luchuensis@\textit{luchuensis}}  \index{Staurochilus@\textit{Staurochilus}!luchuensis@\textit{luchuensis}{\\\noindent(= \textit{Trichoglottis luchuensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豹紋蘭&T2_new_value=true&fr=y}}{豹紋蘭}\index{豹紋蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trichoglottis+rosea}{\textit{T. rosea} (Lindl.) Ames}  \index{Trichoglottis@\textit{Trichoglottis}!rosea@\textit{rosea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短穗毛舌蘭&T2_new_value=true&fr=y}}{短穗毛舌蘭}\index{短穗毛舌蘭} NT
  \end{itemize}
 \item[] \textit{Tropidia} 摺唇蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+curculigoides}{\textit{T. curculigoides} Lindl.}  \index{Tropidia@\textit{Tropidia}!curculigoides@\textit{curculigoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=仙茅摺唇蘭&T2_new_value=true&fr=y}}{仙茅摺唇蘭}\index{仙茅摺唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+formosana}{\textit{T. formosana} Rolfe}  \index{Tropidia@\textit{Tropidia}!formosana@\textbf{\textit{formosana}}}  \index{Tropidia@\textit{Tropidia}!nanhuae@\textit{nanhuae}{\\\noindent(= \textit{Tropidia formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南化摺唇蘭&T2_new_value=true&fr=y}}{南化摺唇蘭}\index{南化摺唇蘭@{\Song{南化摺唇蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+namasiae}{\textit{T. namasiae} C.K.Liao, T.P.Lin \& M.S.Tang}  \index{Tropidia@\textit{Tropidia}!namasiae@\textbf{\textit{namasiae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=那瑪夏摺唇蘭&T2_new_value=true&fr=y}}{那瑪夏摺唇蘭}\index{那瑪夏摺唇蘭@{\Song{那瑪夏摺唇蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+nipponica}{\textit{T. nipponica} Masam.}  \index{Tropidia@\textit{Tropidia}!nipponica@\textit{nipponica}}  \index{Tropidia@\textit{Tropidia}!angustifolia@\textit{angustifolia}{\\\noindent(= \textit{Tropidia nipponica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本摺唇蘭&T2_new_value=true&fr=y}}{日本摺唇蘭}\index{日本摺唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+somae}{\textit{T. somae} Hayata}  \index{Tropidia@\textit{Tropidia}!somae@\textit{somae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=相馬氏摺唇蘭&T2_new_value=true&fr=y}}{相馬氏摺唇蘭}\index{相馬氏摺唇蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tropidia+sui}{\textit{T. sui} T.C.Hsu}  \index{Tropidia@\textit{Tropidia}!sui@\textit{sui}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘇氏摺唇蘭&T2_new_value=true&fr=y}}{蘇氏摺唇蘭}\index{蘇氏摺唇蘭} LC
  \end{itemize}
 \item[] \textit{Tuberolabium} 紅頭蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tuberolabium+kotoense}{\textit{T. kotoense} Yamam.}  \index{Tuberolabium@\textit{Tuberolabium}!kotoense@\textbf{\textit{kotoense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=管唇蘭&T2_new_value=true&fr=y}}{管唇蘭}\index{管唇蘭@{\Song{管唇蘭}}}\# VU
  \end{itemize}
 \item[] \textit{Vanda} 萬代蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vanda+lamellata}{\textit{V. lamellata} Lindl.}  \index{Vanda@\textit{Vanda}!lamellata@\textbf{\textit{lamellata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雅美萬代蘭&T2_new_value=true&fr=y}}{雅美萬代蘭}\index{雅美萬代蘭@{\Song{雅美萬代蘭}}} VU
  \end{itemize}
 \item[] \textit{Vanilla} 梵尼蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vanilla+somae}{\textit{V. somae} Hayata}  \index{Vanilla@\textit{Vanilla}!somae@\textit{somae}}  \index{Vanilla@\textit{Vanilla}!albida@\textit{albida}{\\\noindent(= \textit{Vanilla somae})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣凡尼蘭&T2_new_value=true&fr=y}}{臺灣凡尼蘭}\index{臺灣凡尼蘭} LC
  \end{itemize}
 \item[] \textit{Vrydagzynea} 二尾蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vrydagzynea+formosana}{\textit{V. formosana} Hayata}  \index{Vrydagzynea@\textit{Vrydagzynea}!formosana@\textit{formosana}}  \index{Vrydagzynea@\textit{Vrydagzynea}!nuda@\textit{nuda}{\\\noindent(= \textit{Vrydagzynea formosana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=二尾蘭&T2_new_value=true&fr=y}}{二尾蘭}\index{二尾蘭} LC
  \end{itemize}
 \item[] \textit{Yoania} 長花柄蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Yoania+amagiensis+var.+squamipes}{\textit{Y. amagiensis} Nakai \& F.Maek. var. \textit{squamipes} (Fukuy.) C.S.Leou \& C.L.Yeh}  \index{Yoania@\textit{Yoania}!amagiensis@\textit{amagiensis}!var. squamipes@\textbf{var. \textit{squamipes}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密鱗長花柄蘭&T2_new_value=true&fr=y}}{密鱗長花柄蘭}\index{密鱗長花柄蘭@{\Song{密鱗長花柄蘭}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Yoania+japonica}{\textit{Y. japonica} Maxim.}  \index{Yoania@\textit{Yoania}!japonica@\textbf{\textit{japonica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長花柄蘭&T2_new_value=true&fr=y}}{長花柄蘭}\index{長花柄蘭@{\Song{長花柄蘭}}} EN
  \end{itemize}
 \item[] \textit{Zeuxine} 線柱蘭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+affinis}{\textit{Z. affinis} (Lindl.) Benth. ex Hook.f.}  \index{Zeuxine@\textit{Zeuxine}!affinis@\textit{affinis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花線柱蘭&T2_new_value=true&fr=y}}{白花線柱蘭}\index{白花線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+agyokuana}{\textit{Z. agyokuana} Fukuy.}  \index{Zeuxine@\textit{Zeuxine}!agyokuana@\textit{agyokuana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿玉線柱蘭&T2_new_value=true&fr=y}}{阿玉線柱蘭}\index{阿玉線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+arisanensis}{\textit{Z. arisanensis} Hayata}  \index{Zeuxine@\textit{Zeuxine}!arisanensis@\textit{arisanensis}}  \index{Zeuxine@\textit{Zeuxine}!reflexa@\textit{reflexa}{\\\noindent(= \textit{Zeuxine arisanensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山線柱蘭&T2_new_value=true&fr=y}}{阿里山線柱蘭}\index{阿里山線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+integrilabella}{\textit{Z. integrilabella} C.S.Leou}  \index{Zeuxine@\textit{Zeuxine}!integrilabella@\textbf{\textit{integrilabella}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全唇線柱蘭&T2_new_value=true&fr=y}}{全唇線柱蘭}\index{全唇線柱蘭@{\Song{全唇線柱蘭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+kantokeiense}{\textit{Z. kantokeiense} Tatew. \& Masam.}  \index{Zeuxine@\textit{Zeuxine}!kantokeiense@\textit{kantokeiense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關刀溪線柱蘭&T2_new_value=true&fr=y}}{關刀溪線柱蘭}\index{關刀溪線柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+nervosa}{\textit{Z. nervosa} (Wall. ex Lindl.) Benth. ex C.B.Clarke}  \index{Zeuxine@\textit{Zeuxine}!nervosa@\textit{nervosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣線柱蘭&T2_new_value=true&fr=y}}{臺灣線柱蘭}\index{臺灣線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+niijimae}{\textit{Z. niijimae} Tatew. \& Masam.}  \index{Zeuxine@\textit{Zeuxine}!niijimae@\textit{niijimae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=眉原線柱蘭&T2_new_value=true&fr=y}}{眉原線柱蘭}\index{眉原線柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+odorate}{\textit{Z. odorate} Fukuy.}  \index{Zeuxine@\textit{Zeuxine}!odorate@\textit{odorate}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=香線柱蘭&T2_new_value=true&fr=y}}{香線柱蘭}\index{香線柱蘭} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+philippinensis}{\textit{Z. philippinensis} (Ames) Ames}  \index{Zeuxine@\textit{Zeuxine}!philippinensis@\textbf{\textit{philippinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲律賓線柱蘭&T2_new_value=true&fr=y}}{菲律賓線柱蘭}\index{菲律賓線柱蘭@{\Song{菲律賓線柱蘭}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+pingtungensis}{\textit{Z. pingtungensis} T.C.Hsu}  \index{Zeuxine@\textit{Zeuxine}!pingtungensis@\textit{pingtungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東線柱蘭&T2_new_value=true&fr=y}}{屏東線柱蘭}\index{屏東線柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+sakagutii}{\textit{Z. sakagutii} Tuyama}  \index{Zeuxine@\textit{Zeuxine}!sakagutii@\textit{sakagutii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃唇線柱蘭&T2_new_value=true&fr=y}}{黃唇線柱蘭}\index{黃唇線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+strateumatica+var.+rupicola}{\textit{Z. strateumatica} (L.) Schltr. var. \textit{rupicola} (Fukuy.) S.S.Ying}  \index{Zeuxine@\textit{Zeuxine}!strateumatica@\textit{strateumatica}!var. rupicola@var. \textit{rupicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=岩線柱蘭&T2_new_value=true&fr=y}}{岩線柱蘭}\index{岩線柱蘭} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+strateumatica+var.+strateumatica}{\textit{Z. strateumatica} (L.) Schltr. var. \textit{strateumatica}}  \index{Zeuxine@\textit{Zeuxine}!strateumatica@\textit{strateumatica}!var. strateumatica@var. \textit{strateumatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=線柱蘭&T2_new_value=true&fr=y}}{線柱蘭}\index{線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+tenuifolia}{\textit{Z. tenuifolia} Tuyama}  \index{Zeuxine@\textit{Zeuxine}!tenuifolia@\textit{tenuifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛鞘線柱蘭&T2_new_value=true&fr=y}}{毛鞘線柱蘭}\index{毛鞘線柱蘭} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zeuxine+yehii}{\textit{Z. yehii} T.C.Hsu}  \index{Zeuxine@\textit{Zeuxine}!yehii@\textbf{\textit{yehii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼線柱蘭&T2_new_value=true&fr=y}}{蘭嶼線柱蘭}\index{蘭嶼線柱蘭@{\Song{蘭嶼線柱蘭}}} VU
  \end{itemize}
  \end{itemize}
