
  \begin{itemize}
 \item[] \textit{Aeginetia} 野菰屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aeginetia+indica}{\textit{A. indica} L.}  \index{Aeginetia@\textit{Aeginetia}!indica@\textit{indica}} 野菰\index{野菰} LC
  \end{itemize}
 \item[] \textit{Alectra} 黑蒴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alectra+arvensis}{\textit{A. arvensis} (Benth.) Merr.}  \index{Alectra@\textit{Alectra}!arvensis@\textit{arvensis}} 黑蒴\index{黑蒴} LC
  \end{itemize}
 \item[] \textit{Boschniakia} 草蓯容屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boschniakia+himalaica}{\textit{B. himalaica} Hook.f. \& Thomson}  \index{Boschniakia@\textit{Boschniakia}!himalaica@\textit{himalaica}} 丁座草\index{丁座草} LC
  \end{itemize}
 \item[] \textit{Centranthera} 胡麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Centranthera+cochinchinensis}{\textit{C. cochinchinensis} (Lour.) Merr.}  \index{Centranthera@\textit{Centranthera}!cochinchinensis@\textit{cochinchinensis}} 胡麻草\index{胡麻草} NT
  \end{itemize}
 \item[] \textit{Christisonia} 假野菰屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Christisonia+hookeri}{\textit{C. hookeri} C.B.Clarke}  \index{Christisonia@\textit{Christisonia}!hookeri@\textit{hookeri}} 假野菰\index{假野菰} VU
  \end{itemize}
 \item[] \textit{Euphrasia} 碎雪草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphrasia+nankotaizanensis}{\textit{E. nankotaizanensis} Yamam.}  \index{Euphrasia@\textit{Euphrasia}!nankotaizanensis@\textit{nankotaizanensis}} 南湖碎雪草\index{南湖碎雪草}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphrasia+tarokoana}{\textit{E. tarokoana} Ohwi}  \index{Euphrasia@\textit{Euphrasia}!tarokoana@\textit{tarokoana}} 太魯閣小米草\index{太魯閣小米草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphrasia+transmorrisonensis+var.+durietziana}{\textit{E. transmorrisonensis} Hayata var. \textit{durietziana} (Ohwi) T.C.Huang \& M.J.Wu}  \index{Euphrasia@\textit{Euphrasia}!transmorrisonensis@\textit{transmorrisonensis}!var. durietziana@var. \textit{durietziana}} 臺灣碎雪草\index{臺灣碎雪草}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphrasia+transmorrisonensis+var.+transmorrisonensis}{\textit{E. transmorrisonensis} Hayata var. \textit{transmorrisonensis}}  \index{Euphrasia@\textit{Euphrasia}!transmorrisonensis@\textit{transmorrisonensis}!var. transmorrisonensis@var. \textit{transmorrisonensis}} 玉山小米草\index{玉山小米草}\# LC
  \end{itemize}
 \item[] \textit{Lathraea} 齒鱗草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lathraea+purpurea}{\textit{L. purpurea} Cummins}  \index{Lathraea@\textit{Lathraea}!purpurea@\textit{purpurea}} 紫花齒鱗草\index{紫花齒鱗草} NT
  \end{itemize}
 \item[] \textit{Melampyrum} 山羅花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melampyrum+roseum}{\textit{M. roseum} Maxim.}  \index{Melampyrum@\textit{Melampyrum}!roseum@\textit{roseum}} 山蘿花\index{山蘿花} EN
  \end{itemize}
 \item[] \textit{Orobanche} 列當屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Orobanche+coerulescens}{\textit{O. coerulescens} Stephan}  \index{Orobanche@\textit{Orobanche}!coerulescens@\textit{coerulescens}} 列當\index{列當} EN
  \end{itemize}
 \item[] \textit{Pedicularis} 馬先蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pedicularis+ikomae}{\textit{P. ikomae} Sasaki}  \index{Pedicularis@\textit{Pedicularis}!ikomae@\textit{ikomae}} 高山馬先蒿\index{高山馬先蒿}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pedicularis+verticillata}{\textit{P. verticillata} L.}  \index{Pedicularis@\textit{Pedicularis}!verticillata@\textit{verticillata}} 馬先蒿\index{馬先蒿} LC
  \end{itemize}
 \item[] \textit{Phacellanthus} 黃筒花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phacellanthus+tubiflorus}{\textit{P. tubiflorus} Siebold \& Zucc}  \index{Phacellanthus@\textit{Phacellanthus}!tubiflorus@\textit{tubiflorus}} 黃筒花\index{黃筒花} CR
  \end{itemize}
 \item[] \textit{Phtheirospermum} 松蒿屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phtheirospermum+japonicum}{\textit{P. japonicum} (Thunb.) Kanitz}  \index{Phtheirospermum@\textit{Phtheirospermum}!japonicum@\textit{japonicum}} 日本松蒿\index{日本松蒿} NT
  \end{itemize}
 \item[] \textit{Siphonostegia} 陰行草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Siphonostegia+chinensis}{\textit{S. chinensis} Benth.}  \index{Siphonostegia@\textit{Siphonostegia}!chinensis@\textit{chinensis}} 陰行草\index{陰行草} EN
  \end{itemize}
 \item[] \textit{Striga} 獨腳金屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Striga+lutea}{\textit{S. lutea} Lour.}  \index{Striga@\textit{Striga}!lutea@\textit{lutea}} 獨腳金\index{獨腳金} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Striga+masuria}{\textit{S. masuria} (Buch.-Ham. ex Benth.) Benth.}  \index{Striga@\textit{Striga}!masuria@\textit{masuria}} 高雄獨腳金\index{高雄獨腳金} EN
  \end{itemize}
  \end{itemize}
