
  \begin{itemize}
 \item[] \textit{Biophytum} 羞禮花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Biophytum+sensitivum}{\textit{B. sensitivum} DC.}  \index{Biophytum@\textit{Biophytum}!sensitivum@\textit{sensitivum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羞禮花&T2_new_value=true&fr=y}}{羞禮花}\index{羞禮花} LC
  \end{itemize}
 \item[] \textit{Oxalis} 酢漿草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oxalis+acetosella+subsp.+griffithii+var.+formosana}{\textit{O. acetosella} L. subsp. \textit{griffithii} (Edgew. \& Hook f.) H.Hara var. \textit{formosana} S.F.Huang \& T.C.Huang}  \index{Oxalis@\textit{Oxalis}!acetosella@\textit{acetosella}!subsp. griffithii var. formosana@subsp. \textit{griffithii} var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山酢漿草&T2_new_value=true&fr=y}}{臺灣山酢漿草}\index{臺灣山酢漿草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oxalis+acetosella+subsp.+taemoni}{\textit{O. acetosella} L. subsp. \textit{taemoni} (Yamam.) S.F.Huang \& T.C.Huang}  \index{Oxalis@\textit{Oxalis}!acetosella@\textit{acetosella}!subsp. taemoni@\textbf{subsp. \textit{taemoni}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大霸尖山酢漿草&T2_new_value=true&fr=y}}{大霸尖山酢漿草}\index{大霸尖山酢漿草@{\Song{大霸尖山酢漿草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oxalis+corniculata}{\textit{O. corniculata} L.}  \index{Oxalis@\textit{Oxalis}!corniculata@\textit{corniculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=酢漿草&T2_new_value=true&fr=y}}{酢漿草}\index{酢漿草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oxalis+corymbosa}{\textit{O. corymbosa} DC.}  \index{Oxalis@\textit{Oxalis}!corymbosa@\textit{corymbosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫花酢漿草&T2_new_value=true&fr=y}}{紫花酢漿草}\index{紫花酢漿草} NA$^n$
  \end{itemize}
  \end{itemize}
