
  \begin{itemize}
 \item[] \textit{Argemone} 薊罌粟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argemone+mexicana}{\textit{A. mexicana} L.}  \index{Argemone@\textit{Argemone}!mexicana@\textit{mexicana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薊罌粟&T2_new_value=true&fr=y}}{薊罌粟}\index{薊罌粟} NA$^n$
  \end{itemize}
 \item[] \textit{Corydalis} 紫菫屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+decumbens}{\textit{C. decumbens} (Thunb.) Pers.}  \index{Corydalis@\textit{Corydalis}!decumbens@\textit{decumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=伏莖紫菫&T2_new_value=true&fr=y}}{伏莖紫菫}\index{伏莖紫菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+incisa}{\textit{C. incisa} (Thunb.) Pers.}  \index{Corydalis@\textit{Corydalis}!incisa@\textit{incisa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刻葉紫菫&T2_new_value=true&fr=y}}{刻葉紫菫}\index{刻葉紫菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+koidzumiana}{\textit{C. koidzumiana} Ohwi}  \index{Corydalis@\textit{Corydalis}!koidzumiana@\textit{koidzumiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密花黃菫&T2_new_value=true&fr=y}}{密花黃菫}\index{密花黃菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+ochotensis}{\textit{C. ochotensis} Turcz.}  \index{Corydalis@\textit{Corydalis}!ochotensis@\textit{ochotensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏花黃菫&T2_new_value=true&fr=y}}{疏花黃菫}\index{疏花黃菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+ophiocarpa}{\textit{C. ophiocarpa} Hook.f. \& Thomsson}  \index{Corydalis@\textit{Corydalis}!ophiocarpa@\textit{ophiocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=彎果黃菫&T2_new_value=true&fr=y}}{彎果黃菫}\index{彎果黃菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+pallida+var.+pallida}{\textit{C. pallida} (Thunb.) Pers. var. \textit{pallida}}  \index{Corydalis@\textit{Corydalis}!pallida@\textit{pallida}!var. pallida@var. \textit{pallida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃菫&T2_new_value=true&fr=y}}{黃菫}\index{黃菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+pallida+var.+sparsimamma}{\textit{C. pallida} (Thunb.) Pers. var. \textit{sparsimamma} (Ohwi) Ohwi}  \index{Corydalis@\textit{Corydalis}!pallida@\textit{pallida}!var. sparsimamma@var. \textit{sparsimamma}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹子黃菫&T2_new_value=true&fr=y}}{凹子黃菫}\index{凹子黃菫}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+racemosa}{\textit{C. racemosa} (Thunb.) Pers.}  \index{Corydalis@\textit{Corydalis}!racemosa@\textit{racemosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花黃菫&T2_new_value=true&fr=y}}{小花黃菫}\index{小花黃菫} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Corydalis+tashiroi}{\textit{C. tashiroi} Makino}  \index{Corydalis@\textit{Corydalis}!tashiroi@\textit{tashiroi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃菫&T2_new_value=true&fr=y}}{臺灣黃菫}\index{臺灣黃菫} LC
  \end{itemize}
 \item[] \textit{Fumaria} 球果紫菫屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fumaria+officinalis}{\textit{F. officinalis} L.}  \index{Fumaria@\textit{Fumaria}!officinalis@\textit{officinalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=球果紫菫&T2_new_value=true&fr=y}}{球果紫菫}\index{球果紫菫} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fumaria+parviflora}{\textit{F. parviflora} Lam.}  \index{Fumaria@\textit{Fumaria}!parviflora@\textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花球果紫菫&T2_new_value=true&fr=y}}{小花球果紫菫}\index{小花球果紫菫} NA$^n$
  \end{itemize}
 \item[] \textit{Macleaya} 博落迴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Macleaya+cordata}{\textit{M. cordata} (Willd.) R.Br.}  \index{Macleaya@\textit{Macleaya}!cordata@\textit{cordata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=博落迴&T2_new_value=true&fr=y}}{博落迴}\index{博落迴} NT
  \end{itemize}
 \item[] \textit{Papaver} 罌粟屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Papaver+rhoeas}{\textit{P. rhoeas} L.}  \index{Papaver@\textit{Papaver}!rhoeas@\textit{rhoeas}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虞美人&T2_new_value=true&fr=y}}{虞美人}\index{虞美人} NA$^n$
  \end{itemize}
  \end{itemize}
