
  \begin{itemize}
 \item[] \textit{Adinandra} 楊桐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adinandra+formosana+var.+fomosana}{\textit{A. formosana} Hayata var. \textit{fomosana} }  \index{Adinandra@\textit{Adinandra}!formosana@\textit{formosana}!var. fomosana@var. \textit{fomosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣楊桐&T2_new_value=true&fr=y}}{臺灣楊桐}\index{臺灣楊桐}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adinandra+formosana+var.+obtusissima}{\textit{A. formosana} Hayata var. \textit{obtusissima} (Hayata) H.Keng}  \index{Adinandra@\textit{Adinandra}!formosana@\textit{formosana}!var. obtusissima@var. \textit{obtusissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍葉楊桐&T2_new_value=true&fr=y}}{鈍葉楊桐}\index{鈍葉楊桐}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adinandra+lasiostyla}{\textit{A. lasiostyla} Hayata}  \index{Adinandra@\textit{Adinandra}!lasiostyla@\textit{lasiostyla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛柱楊桐&T2_new_value=true&fr=y}}{毛柱楊桐}\index{毛柱楊桐}\# LC
  \end{itemize}
 \item[] \textit{Anneslea} 茶梨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anneslea+lanceolata}{\textit{A. lanceolata} (Hayata) Kaneh.}  \index{Anneslea@\textit{Anneslea}!lanceolata@\textbf{\textit{lanceolata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉茶梨&T2_new_value=true&fr=y}}{細葉茶梨}\index{細葉茶梨@{\Song{細葉茶梨}}}\# VU
  \end{itemize}
 \item[] \textit{Cleyera} 紅淡比屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleyera+japonica+var.+japonica}{\textit{C. japonica} Thunb. var. \textit{japonica}}  \index{Cleyera@\textit{Cleyera}!japonica@\textit{japonica}!var. japonica@var. \textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅淡比&T2_new_value=true&fr=y}}{紅淡比}\index{紅淡比} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleyera+japonica+var.+longicarpa}{\textit{C. japonica} Thunb. var. \textit{longicarpa} (Yamam.) L.K.Ling \& C.F.Hsieh}  \index{Cleyera@\textit{Cleyera}!japonica@\textit{japonica}!var. longicarpa@var. \textit{longicarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長果紅淡比&T2_new_value=true&fr=y}}{長果紅淡比}\index{長果紅淡比}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleyera+japonica+var.+morii}{\textit{C. japonica} Thunb. var. \textit{morii} (Yamam.) Masam.}  \index{Cleyera@\textit{Cleyera}!japonica@\textit{japonica}!var. morii@var. \textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏紅淡比&T2_new_value=true&fr=y}}{森氏紅淡比}\index{森氏紅淡比}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cleyera+japonica+var.+taipinensis}{\textit{C. japonica} Thunb. var. \textit{taipinensis} H.Keng}  \index{Cleyera@\textit{Cleyera}!japonica@\textit{japonica}!var. taipinensis@var. \textit{taipinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太平紅淡比&T2_new_value=true&fr=y}}{太平紅淡比}\index{太平紅淡比}\# LC
  \end{itemize}
 \item[] \textit{Eurya} 柃木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+chinensis}{\textit{E. chinensis} R.Br.}  \index{Eurya@\textit{Eurya}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=米碎柃木&T2_new_value=true&fr=y}}{米碎柃木}\index{米碎柃木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+crenatifolia}{\textit{E. crenatifolia} (Yamam.) Kobuski}  \index{Eurya@\textit{Eurya}!crenatifolia@\textit{crenatifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假柃木&T2_new_value=true&fr=y}}{假柃木}\index{假柃木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+emarginata}{\textit{E. emarginata} (Thunb.) Makino}  \index{Eurya@\textit{Eurya}!emarginata@\textit{emarginata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=凹葉柃木&T2_new_value=true&fr=y}}{凹葉柃木}\index{凹葉柃木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+glaberrima}{\textit{E. glaberrima} Hayata}  \index{Eurya@\textit{Eurya}!glaberrima@\textit{glaberrima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉柃木&T2_new_value=true&fr=y}}{厚葉柃木}\index{厚葉柃木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+gnaphalocarpa}{\textit{E. gnaphalocarpa} Hayata}  \index{Eurya@\textit{Eurya}!gnaphalocarpa@\textit{gnaphalocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果柃木&T2_new_value=true&fr=y}}{毛果柃木}\index{毛果柃木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+hayatae}{\textit{E. hayatae} Yamam.}  \index{Eurya@\textit{Eurya}!hayatae@\textit{hayatae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏柃木&T2_new_value=true&fr=y}}{早田氏柃木}\index{早田氏柃木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+japonica}{\textit{E. japonica} Thunb.}  \index{Eurya@\textit{Eurya}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本柃木&T2_new_value=true&fr=y}}{日本柃木}\index{日本柃木} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+leptophylla}{\textit{E. leptophylla} Hayata}  \index{Eurya@\textit{Eurya}!leptophylla@\textit{leptophylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉柃木&T2_new_value=true&fr=y}}{薄葉柃木}\index{薄葉柃木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+loquaiana}{\textit{E. loquaiana} Dunn}  \index{Eurya@\textit{Eurya}!loquaiana@\textit{loquaiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細枝柃木&T2_new_value=true&fr=y}}{細枝柃木}\index{細枝柃木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+nitida+var.+nanjenshanensis}{\textit{E. nitida} Korthals var. \textit{nanjenshanensis} C.F.Hsieh, L.K.Ling \& Sheng Z.Yang}  \index{Eurya@\textit{Eurya}!nitida@\textit{nitida}!var. nanjenshanensis@var. \textit{nanjenshanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南仁山柃木&T2_new_value=true&fr=y}}{南仁山柃木}\index{南仁山柃木}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+nitida+var.+nitida}{\textit{E. nitida} Korthals var. \textit{nitida}}  \index{Eurya@\textit{Eurya}!nitida@\textit{nitida}!var. nitida@var. \textit{nitida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉柃木&T2_new_value=true&fr=y}}{光葉柃木}\index{光葉柃木} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+rengechiensis}{\textit{E. rengechiensis} Yamam.}  \index{Eurya@\textit{Eurya}!rengechiensis@\textbf{\textit{rengechiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓮華池柃木&T2_new_value=true&fr=y}}{蓮華池柃木}\index{蓮華池柃木@{\Song{蓮華池柃木}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+septata}{\textit{E. septata} Chi C.Wu, Z.F.Hsu \& C.H.Tsou}  \index{Eurya@\textit{Eurya}!septata@\textit{septata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣格柃&T2_new_value=true&fr=y}}{臺灣格柃}\index{臺灣格柃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+strigillosa}{\textit{E. strigillosa} Hayata}  \index{Eurya@\textit{Eurya}!strigillosa@\textit{strigillosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛柃木&T2_new_value=true&fr=y}}{粗毛柃木}\index{粗毛柃木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurya+taitungensis}{\textit{E. taitungensis} C.E.Chang}  \index{Eurya@\textit{Eurya}!taitungensis@\textit{taitungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水山柃木&T2_new_value=true&fr=y}}{清水山柃木}\index{清水山柃木}\# DD
  \end{itemize}
 \item[] \textit{Ternstroemia} 厚皮香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ternstroemia+gymnanthera}{\textit{T. gymnanthera} (Wight \& Arn.) Sprague}  \index{Ternstroemia@\textit{Ternstroemia}!gymnanthera@\textit{gymnanthera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚皮香&T2_new_value=true&fr=y}}{厚皮香}\index{厚皮香} LC
  \end{itemize}
  \end{itemize}
