
  \begin{itemize}
 \item[] \textit{Antidesma} 五月茶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antidesma+hiiranense}{\textit{A. hiiranense} Hayata}  \index{Antidesma@\textit{Antidesma}!hiiranense@\textit{hiiranense}} 南仁五月茶\index{南仁五月茶}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antidesma+japonicum+var.+acutisepalum}{\textit{A. japonicum} Siebold \& Zucc. var. \textit{acutisepalum} (Hayata) Hurus.}  \index{Antidesma@\textit{Antidesma}!japonicum@\textit{japonicum}!var. acutisepalum@var. \textit{acutisepalum}} 南投五月茶\index{南投五月茶}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antidesma+japonicum+var.+densiflorum}{\textit{A. japonicum} Siebold \& Zucc. var. \textit{densiflorum} Hurus.}  \index{Antidesma@\textit{Antidesma}!japonicum@\textit{japonicum}!var. densiflorum@var. \textit{densiflorum}} 密花五月茶\index{密花五月茶}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antidesma+pentandrum+var.+barbatum}{\textit{A. pentandrum} (Blanco) Merr. var. \textit{barbatum} (C.Presl) Merr.}  \index{Antidesma@\textit{Antidesma}!pentandrum@\textit{pentandrum}!var. barbatum@var. \textit{barbatum}} 枯里珍\index{枯里珍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antidesma+pleuricum}{\textit{A. pleuricum} Tul.}  \index{Antidesma@\textit{Antidesma}!pleuricum@\textit{pleuricum}} 蘭嶼枯里珍\index{蘭嶼枯里珍} VU
  \end{itemize}
 \item[] \textit{Bischofia} 重陽木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bischofia+javanica}{\textit{B. javanica} Blume}  \index{Bischofia@\textit{Bischofia}!javanica@\textit{javanica}} 茄冬\index{茄冬} LC
  \end{itemize}
 \item[] \textit{Breynia} 山漆莖屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Breynia+officinalis+var.+accrescens}{\textit{B. officinalis} Hemsl. var. \textit{accrescens} (Hayata) M.J.Deng \& J.C.Wang}  \index{Breynia@\textit{Breynia}!officinalis@\textit{officinalis}!var. accrescens@var. \textit{accrescens}} 小紅仔珠\index{小紅仔珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Breynia+officinalis+var.+officinalis}{\textit{B. officinalis} Hemsl. var. \textit{officinalis}}  \index{Breynia@\textit{Breynia}!officinalis@\textit{officinalis}!var. officinalis@var. \textit{officinalis}} 紅仔珠\index{紅仔珠} LC
  \end{itemize}
 \item[] \textit{Bridelia} 土密樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bridelia+balansae}{\textit{B. balansae} Tutcher}  \index{Bridelia@\textit{Bridelia}!balansae@\textit{balansae}} 刺杜密\index{刺杜密} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bridelia+tomentosa}{\textit{B. tomentosa} Blume}  \index{Bridelia@\textit{Bridelia}!tomentosa@\textit{tomentosa}} 土密樹\index{土密樹} LC
  \end{itemize}
 \item[] \textit{Flueggea} 白飯樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flueggea+suffruticosa}{\textit{F. suffruticosa} (Pall.) Baill.}  \index{Flueggea@\textit{Flueggea}!suffruticosa@\textit{suffruticosa}} 白飯樹\index{白飯樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flueggea+virosa}{\textit{F. virosa} (Roxb. ex Willd.) Voigt}  \index{Flueggea@\textit{Flueggea}!virosa@\textit{virosa}} 密花白飯樹\index{密花白飯樹} LC
  \end{itemize}
 \item[] \textit{Glochidion} 饅頭果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+acuminatum}{\textit{G. acuminatum} Müll.Arg.}  \index{Glochidion@\textit{Glochidion}!acuminatum@\textit{acuminatum}} 裏白饅頭果\index{裏白饅頭果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+kusukusense}{\textit{G. kusukusense} Hay.}  \index{Glochidion@\textit{Glochidion}!kusukusense@\textit{kusukusense}} 高士佛饅頭果\index{高士佛饅頭果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+ovalifolium}{\textit{G. ovalifolium} F.Y.Lu \& Y.S.Hsu}  \index{Glochidion@\textit{Glochidion}!ovalifolium@\textit{ovalifolium}} 卵葉饅頭果\index{卵葉饅頭果}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+philippicum}{\textit{G. philippicum} (Cavan.) C.B.Rob.}  \index{Glochidion@\textit{Glochidion}!philippicum@\textit{philippicum}} 菲律賓饅頭果\index{菲律賓饅頭果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+puber}{\textit{G. puber} (L.) Hutch.}  \index{Glochidion@\textit{Glochidion}!puber@\textit{puber}}  \index{Glochidion@\textit{Glochidion}!puberum@\textit{puberum}{\\\noindent(= \textit{Glochidion puber})}} 紅毛饅頭果\index{紅毛饅頭果} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+rubrum}{\textit{G. rubrum} Blume}  \index{Glochidion@\textit{Glochidion}!rubrum@\textit{rubrum}} 細葉饅頭果\index{細葉饅頭果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+zeylanicum+var.+lanceolatum}{\textit{G. zeylanicum} (Gaertn.) A.Juss. var. \textit{lanceolatum} (Hayata) M.J.Deng \& J.C.Wang}  \index{Glochidion@\textit{Glochidion}!zeylanicum@\textit{zeylanicum}!var. lanceolatum@var. \textit{lanceolatum}} 披針葉饅頭果\index{披針葉饅頭果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+zeylanicum+var.+tomentosum}{\textit{G. zeylanicum} (Gaertn.) A.Juss. var. \textit{tomentosum} Trimem}  \index{Glochidion@\textit{Glochidion}!zeylanicum@\textit{zeylanicum}!var. tomentosum@var. \textit{tomentosum}} 赤血仔\index{赤血仔} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glochidion+zeylanicum+var.+zeylanicum}{\textit{G. zeylanicum} (Gaertn.) A.Juss. var. \textit{zeylanicum}}  \index{Glochidion@\textit{Glochidion}!zeylanicum@\textit{zeylanicum}!var. zeylanicum@var. \textit{zeylanicum}} 錫蘭饅頭果\index{錫蘭饅頭果} LC
  \end{itemize}
 \item[] \textit{Margaritaria} 紫黃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Margaritaria+indica}{\textit{M. indica} (Daiz.) Airy Shaw}  \index{Margaritaria@\textit{Margaritaria}!indica@\textit{indica}} 紫黃\index{紫黃} VU
  \end{itemize}
 \item[] \textit{Phyllanthus} 油柑屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+amarus}{\textit{P. amarus} Schum. \& Thonn.}  \index{Phyllanthus@\textit{Phyllanthus}!amarus@\textit{amarus}} 小返魂\index{小返魂} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+debilis}{\textit{P. debilis} Klen ex Willd.}  \index{Phyllanthus@\textit{Phyllanthus}!debilis@\textit{debilis}} 銳葉小返魂\index{銳葉小返魂} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+embergeri}{\textit{P. embergeri} Haic. \& Rossign.}  \index{Phyllanthus@\textit{Phyllanthus}!embergeri@\textit{embergeri}} 擬葉下珠\index{擬葉下珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+hookeri}{\textit{P. hookeri} Müll.Arg.}  \index{Phyllanthus@\textit{Phyllanthus}!hookeri@\textit{hookeri}} 疣果葉下珠\index{疣果葉下珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+multiflorus}{\textit{P. multiflorus} Willd.}  \index{Phyllanthus@\textit{Phyllanthus}!multiflorus@\textit{multiflorus}} 多花油柑\index{多花油柑} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+oligospermus}{\textit{P. oligospermus} Hayata}  \index{Phyllanthus@\textit{Phyllanthus}!oligospermus@\textit{oligospermus}} 新竹油柑\index{新竹油柑}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+tenellus}{\textit{P. tenellus} Roxb.}  \index{Phyllanthus@\textit{Phyllanthus}!tenellus@\textit{tenellus}} 五蕊油柑\index{五蕊油柑} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+urinaria+subsp.+nudicarpus}{\textit{P. urinaria} L. subsp. \textit{nudicarpus} Rossign. \& Haic.}  \index{Phyllanthus@\textit{Phyllanthus}!urinaria@\textit{urinaria}!subsp. nudicarpus@subsp. \textit{nudicarpus}} 光果葉下珠\index{光果葉下珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+ussuriensis}{\textit{P. ussuriensis} Rupr. \& Maxim.}  \index{Phyllanthus@\textit{Phyllanthus}!ussuriensis@\textit{ussuriensis}} 蜜甘草\index{蜜甘草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phyllanthus+virgatus}{\textit{P. virgatus} Forst.f.}  \index{Phyllanthus@\textit{Phyllanthus}!virgatus@\textit{virgatus}} 黃珠子草\index{黃珠子草} LC
  \end{itemize}
 \item[] \textit{Sauropus} 假葉下珠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sauropus+bacciformis}{\textit{S. bacciformis} (L.) Airy Shaw}  \index{Sauropus@\textit{Sauropus}!bacciformis@\textit{bacciformis}}  \index{Synostemon@\textit{Synostemon}!bacciformis@\textit{bacciformis}{\\\noindent(= \textit{Sauropus bacciformis})}} 假葉下珠\index{假葉下珠} LC
  \end{itemize}
  \end{itemize}
