
  \begin{itemize}
 \item[] \textit{Abies} 冷杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Abies+kawakamii}{\textit{A. kawakamii} (Hayata) T.Itô}  \index{Abies@\textit{Abies}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣冷杉&T2_new_value=true&fr=y}}{臺灣冷杉}\index{臺灣冷杉}\# LC
  \end{itemize}
 \item[] \textit{Keteleeria} 油杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Keteleeria+davidiana+var.+formosana}{\textit{K. davidiana} (Franchet) Beissner var. \textit{formosana} (Hayata) Hayata}  \index{Keteleeria@\textit{Keteleeria}!davidiana@\textit{davidiana}!var. formosana@\textbf{var. \textit{formosana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣油杉&T2_new_value=true&fr=y}}{臺灣油杉}\index{臺灣油杉@{\Song{臺灣油杉}}}\# CR
  \end{itemize}
 \item[] \textit{Picea} 雲杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Picea+morrisonicola}{\textit{P. morrisonicola} Hayata}  \index{Picea@\textit{Picea}!morrisonicola@\textit{morrisonicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣雲杉&T2_new_value=true&fr=y}}{臺灣雲杉}\index{臺灣雲杉}\# LC
  \end{itemize}
 \item[] \textit{Pinus} 松屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+armandii+var.+mastersiana}{\textit{P. armandii} Franch. var. \textit{mastersiana} (Hayata) Hayata}  \index{Pinus@\textit{Pinus}!armandii@\textit{armandii}!var. mastersiana@var. \textit{mastersiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣華山松&T2_new_value=true&fr=y}}{臺灣華山松}\index{臺灣華山松}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+fragilissima}{\textit{P. fragilissima} Businský}  \index{Pinus@\textit{Pinus}!fragilissima@\textit{fragilissima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天龍二葉松&T2_new_value=true&fr=y}}{天龍二葉松}\index{天龍二葉松} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+massoniana}{\textit{P. massoniana} Lamb.}  \index{Pinus@\textit{Pinus}!massoniana@\textit{massoniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬尾松&T2_new_value=true&fr=y}}{馬尾松}\index{馬尾松} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+morrisonicola}{\textit{P. morrisonicola} Hayata}  \index{Pinus@\textit{Pinus}!morrisonicola@\textit{morrisonicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣五葉松&T2_new_value=true&fr=y}}{臺灣五葉松}\index{臺灣五葉松}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+taiwanensis}{\textit{P. taiwanensis} Hayata}  \index{Pinus@\textit{Pinus}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣二葉松&T2_new_value=true&fr=y}}{臺灣二葉松}\index{臺灣二葉松}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pinus+×hayatana}{\textit{P. ×hayatana} Businský}  \index{Pinus@\textit{Pinus}!×hayatana@\textit{×hayatana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏松&T2_new_value=true&fr=y}}{早田氏松}\index{早田氏松} NA$^h$
  \end{itemize}
 \item[] \textit{Pseudotsuga} 黃杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pseudotsuga+wilsoniana}{\textit{P. wilsoniana} Hayata}  \index{Pseudotsuga@\textit{Pseudotsuga}!wilsoniana@\textit{wilsoniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃杉&T2_new_value=true&fr=y}}{臺灣黃杉}\index{臺灣黃杉}\# LC
  \end{itemize}
 \item[] \textit{Tsuga} 鐵杉屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tsuga+chinensis+var.+formosana}{\textit{T. chinensis} (Franch.) Pritz. ex Diels var. \textit{formosana} (Hayata) H.L.Li \& H.Keng}  \index{Tsuga@\textit{Tsuga}!chinensis@\textit{chinensis}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鐵杉&T2_new_value=true&fr=y}}{臺灣鐵杉}\index{臺灣鐵杉}\# LC
  \end{itemize}
  \end{itemize}
