
  \begin{itemize}
 \item[] \textit{Peperomia} 椒草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+japonica}{\textit{P. japonica} Makino}  \index{Peperomia@\textit{Peperomia}!japonica@\textit{japonica}} 椒草 \index{椒草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+nakaharai}{\textit{P. nakaharai} Hayata}  \index{Peperomia@\textit{Peperomia}!nakaharai@\textit{nakaharai}} 山椒草 \index{山椒草} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+pellucida}{\textit{P. pellucida} Kunth}  \index{Peperomia@\textit{Peperomia}!pellucida@\textit{pellucida}} 草胡椒 \index{草胡椒}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+reflexa}{\textit{P. reflexa} (L.f.) A.Dietr.}  \index{Peperomia@\textit{Peperomia}!reflexa@\textit{reflexa}} 小椒草 \index{小椒草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+rubrivenosa}{\textit{P. rubrivenosa} C.DC.}  \index{Peperomia@\textit{Peperomia}!rubrivenosa@\textit{rubrivenosa}} 蘭嶼椒草 \index{蘭嶼椒草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Peperomia+sui}{\textit{P. sui} T.T.Lin \& S.Y.Lu}  \index{Peperomia@\textit{Peperomia}!sui@\textit{sui}} 紅莖椒草 \index{紅莖椒草} \# LC
  \end{itemize}
 \item[] \textit{Piper} 胡椒屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+arborescens}{\textit{P. arborescens} Roxb.}  \index{Piper@\textit{Piper}!arborescens@\textit{arborescens}} 蘭嶼風藤 \index{蘭嶼風藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+betle}{\textit{P. betle} L.}  \index{Piper@\textit{Piper}!betle@\textit{betle}} 荖藤 \index{荖藤}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+interruptum+var.+multinervum}{\textit{P. interruptum} Opiz var. \textit{multinervum} C.DC.}  \index{Piper@\textit{Piper}!interruptum@\textit{interruptum}!var. multinervum@var. \textit{multinervum}} 多脈風藤 \index{多脈風藤}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+kadsura}{\textit{P. kadsura} (Choisy) Ohwi}  \index{Piper@\textit{Piper}!kadsura@\textit{kadsura}} 風藤 \index{風藤}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+kawakamii}{\textit{P. kawakamii} Hayata}  \index{Piper@\textit{Piper}!kawakamii@\textit{kawakamii}} 恆春風藤 \index{恆春風藤} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+kwashoense}{\textit{P. kwashoense} Hayata}  \index{Piper@\textit{Piper}!kwashoense@\textit{kwashoense}} 綠島風藤 \index{綠島風藤} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+sarmentosum}{\textit{P. sarmentosum} Roxb.}  \index{Piper@\textit{Piper}!sarmentosum@\textit{sarmentosum}} 假蒟 \index{假蒟}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+sintenense}{\textit{P. sintenense} Hatus.}  \index{Piper@\textit{Piper}!sintenense@\textit{sintenense}} 薄葉風藤 \index{薄葉風藤} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+taiwanense}{\textit{P. taiwanense} T.T.Lin \& S.Y.Lu}  \index{Piper@\textit{Piper}!taiwanense@\textit{taiwanense}} 臺灣荖藤 \index{臺灣荖藤} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Piper+umbellatum}{\textit{P. umbellatum} L.}  \index{Piper@\textit{Piper}!umbellatum@\textit{umbellatum}} 臺灣胡椒 \index{臺灣胡椒}  LC
  \end{itemize}
  \end{itemize}
