
  \begin{itemize}
 \item[] \textit{Pittosporum} 海桐屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+daphniphylloides}{\textit{P. daphniphylloides} Hayata}  \index{Pittosporum@\textit{Pittosporum}!daphniphylloides@\textit{daphniphylloides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉海桐&T2_new_value=true&fr=y}}{大葉海桐}\index{大葉海桐}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+illicioides+var.+angustifolium}{\textit{P. illicioides} Makino var. \textit{angustifolium} T.C.Huang ex S.Y.Lu}  \index{Pittosporum@\textit{Pittosporum}!illicioides@\textit{illicioides}!var. angustifolium@\textbf{var. \textit{angustifolium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉疏果海桐&T2_new_value=true&fr=y}}{細葉疏果海桐}\index{細葉疏果海桐@{\Song{細葉疏果海桐}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+illicioides+var.+illicioides}{\textit{P. illicioides} Makino var. \textit{illicioides}}  \index{Pittosporum@\textit{Pittosporum}!illicioides@\textit{illicioides}!var. illicioides@var. \textit{illicioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏果海桐&T2_new_value=true&fr=y}}{疏果海桐}\index{疏果海桐} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+moluccanum}{\textit{P. moluccanum} Miq.}  \index{Pittosporum@\textit{Pittosporum}!moluccanum@\textit{moluccanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼海桐&T2_new_value=true&fr=y}}{蘭嶼海桐}\index{蘭嶼海桐} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+pentandrum}{\textit{P. pentandrum} (Blanco) Merr.}  \index{Pittosporum@\textit{Pittosporum}!pentandrum@\textit{pentandrum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=七里香&T2_new_value=true&fr=y}}{七里香}\index{七里香} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pittosporum+tobira}{\textit{P. tobira} W.T.Aiton}  \index{Pittosporum@\textit{Pittosporum}!tobira@\textit{tobira}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海桐&T2_new_value=true&fr=y}}{海桐}\index{海桐} LC
  \end{itemize}
  \end{itemize}
