
  \begin{itemize}
 \item[] \textit{Bacopa} 過長沙屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bacopa+carolineana}{\textit{B. carolineana} Robinson}  \index{Bacopa@\textit{Bacopa}!carolineana@\textit{carolineana}} 卡羅萊納過長沙 \index{卡羅萊納過長沙}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Bacopa+monnieri}{\textit{B. monnieri} (L.) Wettst.}  \index{Bacopa@\textit{Bacopa}!monnieri@\textit{monnieri}} 過長沙 \index{過長沙}  LC
  \end{itemize}
 \item[] \textit{Callitriche} 水馬齒屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+japonica}{\textit{C. japonica} Engelm. ex Hegelm.}  \index{Callitriche@\textit{Callitriche}!japonica@\textit{japonica}} 日本水馬齒 \index{日本水馬齒}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+palustris+var.+oryzetorum}{\textit{C. palustris} L. var. \textit{oryzetorum} (Petrov) Lansdown}  \index{Callitriche@\textit{Callitriche}!palustris@\textit{palustris}!var. oryzetorum@var. \textit{oryzetorum}} 廣東水馬齒 \index{廣東水馬齒}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+palustris+var.+palustris}{\textit{C. palustris} L. var. \textit{palustris}}  \index{Callitriche@\textit{Callitriche}!palustris@\textit{palustris}!var. palustris@var. \textit{palustris}} 水馬齒 \index{水馬齒}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+peploides}{\textit{C. peploides} Nutt.}  \index{Callitriche@\textit{Callitriche}!peploides@\textit{peploides}} 凹果水馬齒 \index{凹果水馬齒}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+raveniana}{\textit{C. raveniana} Lansdown}  \index{Callitriche@\textit{Callitriche}!raveniana@\textit{raveniana}} 雷文氏水馬齒(細苞水馬齒) \index{雷文氏水馬齒(細苞水馬齒)}  DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Callitriche+verna}{\textit{C. verna} L.}  \index{Callitriche@\textit{Callitriche}!verna@\textit{verna}} 水馬齒 \index{水馬齒}  LC
  \end{itemize}
 \item[] \textit{Deinostema} 澤番椒屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deinostema+adenocaulon}{\textit{D. adenocaulon} (Maxim.) T.Yamaz.}  \index{Deinostema@\textit{Deinostema}!adenocaulon@\textit{adenocaulon}} 毛澤番椒 \index{毛澤番椒}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Deinostema+violaceum}{\textit{D. violaceum} (Maxim.) T.Yamaz.}  \index{Deinostema@\textit{Deinostema}!violaceum@\textit{violaceum}} 澤番椒 \index{澤番椒}  DD
  \end{itemize}
 \item[] \textit{Digitalis} 毛地黃屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Digitalis+lutea}{\textit{D. lutea} L.}  \index{Digitalis@\textit{Digitalis}!lutea@\textit{lutea}} 黃花毛地黃 \index{黃花毛地黃}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Digitalis+purpurea}{\textit{D. purpurea} L.}  \index{Digitalis@\textit{Digitalis}!purpurea@\textit{purpurea}} 毛地黃 \index{毛地黃}  NA (N)
  \end{itemize}
 \item[] \textit{Dopatrium} 虻眼草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dopatrium+junceum}{\textit{D. junceum} (Roxb.) Buch.-Ham. ex Benth.}  \index{Dopatrium@\textit{Dopatrium}!junceum@\textit{junceum}} 虻眼草 \index{虻眼草}  NT
  \end{itemize}
 \item[] \textit{Ellisiophyllum} 海螺菊屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ellisiophyllum+pinnatum}{\textit{E. pinnatum} (Wall. ex Benth.) Makino}  \index{Ellisiophyllum@\textit{Ellisiophyllum}!pinnatum@\textit{pinnatum}} 海螺菊 \index{海螺菊}  LC
  \end{itemize}
 \item[] \textit{Hemiphragma} 腰只花屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hemiphragma+heterophyllum}{\textit{H. heterophyllum} Wall.}  \index{Hemiphragma@\textit{Hemiphragma}!heterophyllum@\textit{heterophyllum}} 腰只花 \index{腰只花}  LC
  \end{itemize}
 \item[] \textit{Limnophila} 石龍尾屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+aromatica}{\textit{L. aromatica} (Lam.) Merr.}  \index{Limnophila@\textit{Limnophila}!aromatica@\textit{aromatica}} 紫蘇草 \index{紫蘇草}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+aromaticoides}{\textit{L. aromaticoides} Yuen P.Yang \& S.H.Yen}  \index{Limnophila@\textit{Limnophila}!aromaticoides@\textit{aromaticoides}} 擬紫蘇草 \index{擬紫蘇草}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+fragrans}{\textit{L. fragrans} (G.Forst.) Seem.}  \index{Limnophila@\textit{Limnophila}!fragrans@\textit{fragrans}} 無柄田香草 \index{無柄田香草}  B2ac(iii)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+heterophylla}{\textit{L. heterophylla} (Roxb.) Benth.}  \index{Limnophila@\textit{Limnophila}!heterophylla@\textit{heterophylla}} 異葉石龍尾 \index{異葉石龍尾}  EW
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+rugosa}{\textit{L. rugosa} (Roth) Merr.}  \index{Limnophila@\textit{Limnophila}!rugosa@\textit{rugosa}} 大葉石龍尾 \index{大葉石龍尾}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+sessiliflora}{\textit{L. sessiliflora} Blume}  \index{Limnophila@\textit{Limnophila}!sessiliflora@\textit{sessiliflora}} 無柄花石龍尾 \index{無柄花石龍尾}  EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+taoyuanensis}{\textit{L. taoyuanensis} Yuen P.Yang \& S.H.Yen}  \index{Limnophila@\textit{Limnophila}!taoyuanensis@\textit{taoyuanensis}} 桃園石龍尾 \index{桃園石龍尾} \# EW
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Limnophila+trichophylla}{\textit{L. trichophylla} Kom.}  \index{Limnophila@\textit{Limnophila}!trichophylla@\textit{trichophylla}} 石龍尾 \index{石龍尾}  EN
  \end{itemize}
 \item[] \textit{Mecardonia} 過長沙舅屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mecardonia+procumbens}{\textit{M. procumbens} (Mill.) Small}  \index{Mecardonia@\textit{Mecardonia}!procumbens@\textit{procumbens}} 黃花過長沙舅 \index{黃花過長沙舅}  NA (N)
  \end{itemize}
 \item[] \textit{Microcarpaea} 微果草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Microcarpaea+minima}{\textit{M. minima} (K.D.Koenig ex Retz.) Merr.}  \index{Microcarpaea@\textit{Microcarpaea}!minima@\textit{minima}} 微果草 \index{微果草}  NT
  \end{itemize}
 \item[] \textit{Plantago} 車前屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Plantago+asiatica}{\textit{P. asiatica} L.}  \index{Plantago@\textit{Plantago}!asiatica@\textit{asiatica}} 車前草 \index{車前草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Plantago+lanceolata}{\textit{P. lanceolata} L.}  \index{Plantago@\textit{Plantago}!lanceolata@\textit{lanceolata}} 長葉車前草 \index{長葉車前草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Plantago+macronipponica}{\textit{P. macronipponica} Yamam.}  \index{Plantago@\textit{Plantago}!macronipponica@\textit{macronipponica}} 巨葉車前草 \index{巨葉車前草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Plantago+major}{\textit{P. major} L.}  \index{Plantago@\textit{Plantago}!major@\textit{major}} 大車前草 \index{大車前草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Plantago+virginica}{\textit{P. virginica} L.}  \index{Plantago@\textit{Plantago}!virginica@\textit{virginica}} 毛車前草 \index{毛車前草}  NA (N)
  \end{itemize}
 \item[] \textit{Scoparia} 野甘草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scoparia+dulcis}{\textit{S. dulcis} L.}  \index{Scoparia@\textit{Scoparia}!dulcis@\textit{dulcis}} 野甘草 \index{野甘草}  NA (N)
  \end{itemize}
 \item[] \textit{Stemodia} 孿生花屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stemodia+verticillata}{\textit{S. verticillata} (Mill.) Hassl.}  \index{Stemodia@\textit{Stemodia}!verticillata@\textit{verticillata}} 輪葉孿生花 \index{輪葉孿生花}  NA (N)
  \end{itemize}
 \item[] \textit{Veronica} 婆婆納屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+arvensis}{\textit{V. arvensis} L.}  \index{Veronica@\textit{Veronica}!arvensis@\textit{arvensis}} 直立婆婆納 \index{直立婆婆納}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+didyma}{\textit{V. didyma} Tenore}  \index{Veronica@\textit{Veronica}!didyma@\textit{didyma}} 婆婆納 \index{婆婆納}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+hederifolia}{\textit{V. hederifolia} L.}  \index{Veronica@\textit{Veronica}!hederifolia@\textit{hederifolia}} 睫毛婆婆納 \index{睫毛婆婆納}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+javanica}{\textit{V. javanica} Blume}  \index{Veronica@\textit{Veronica}!javanica@\textit{javanica}} 爪哇水苦藚 \index{爪哇水苦藚}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+linariifolia}{\textit{V. linariifolia} Pallas ex Link}  \index{Veronica@\textit{Veronica}!linariifolia@\textit{linariifolia}} 追風草 \index{追風草}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+morrisonicola}{\textit{V. morrisonicola} Hayata}  \index{Veronica@\textit{Veronica}!morrisonicola@\textit{morrisonicola}} 玉山水苦藚 \index{玉山水苦藚} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+oligosperma}{\textit{V. oligosperma} Hayata}  \index{Veronica@\textit{Veronica}!oligosperma@\textit{oligosperma}} 貧子水苦藚 \index{貧子水苦藚} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+peregrina}{\textit{V. peregrina} L.}  \index{Veronica@\textit{Veronica}!peregrina@\textit{peregrina}} 毛蟲婆婆納 \index{毛蟲婆婆納}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+persica}{\textit{V. persica} Poir.}  \index{Veronica@\textit{Veronica}!persica@\textit{persica}} 阿拉伯婆婆納 \index{阿拉伯婆婆納}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+taiwanica}{\textit{V. taiwanica} T.Yamaz.}  \index{Veronica@\textit{Veronica}!taiwanica@\textit{taiwanica}} 臺灣水苦藚 \index{臺灣水苦藚} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronica+undulata}{\textit{V. undulata} Wall.}  \index{Veronica@\textit{Veronica}!undulata@\textit{undulata}} 水苦藚 \index{水苦藚}  LC
  \end{itemize}
 \item[] \textit{Veronicastrum} 腹水草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronicastrum+axillare+var.+simadai}{\textit{V. axillare} (Siebold \& Zucc.) T.Yamaz. var. \textit{simadai} (Masam.) H.Y.Liu}  \index{Veronicastrum@\textit{Veronicastrum}!axillare@\textit{axillare}!var. simadai@var. \textit{simadai}} 新竹腹水草 \index{新竹腹水草} \# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronicastrum+formosanum}{\textit{V. formosanum} (Masam.) T.Yamaz.}  \index{Veronicastrum@\textit{Veronicastrum}!formosanum@\textit{formosanum}} 臺灣腹水草 \index{臺灣腹水草} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronicastrum+kitamurae}{\textit{V. kitamurae} (Ohwi) T.Yamaz.}  \index{Veronicastrum@\textit{Veronicastrum}!kitamurae@\textit{kitamurae}} 高山腹水草 \index{高山腹水草} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Veronicastrum+loshanense}{\textit{V. loshanense} Tien T.Chen \& F.S.Chou}  \index{Veronicastrum@\textit{Veronicastrum}!loshanense@\textit{loshanense}} 羅山腹水草 \index{羅山腹水草} \# CR
  \end{itemize}
  \end{itemize}
