
  \begin{itemize}
 \item[] \textit{Nageia} 竹柏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nageia+nagi}{\textit{N. nagi} (Thunb.) O.Ktze.}  \index{Nageia@\textit{Nageia}!nagi@\textbf{\textit{nagi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=竹柏&T2_new_value=true&fr=y}}{竹柏}\index{竹柏@{\Song{竹柏}}} EN
  \end{itemize}
 \item[] \textit{Podocarpus} 羅漢松屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+costalis}{\textit{P. costalis} C.Presl}  \index{Podocarpus@\textit{Podocarpus}!costalis@\textbf{\textit{costalis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼羅漢松&T2_new_value=true&fr=y}}{蘭嶼羅漢松}\index{蘭嶼羅漢松@{\Song{蘭嶼羅漢松}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+fasciculus}{\textit{P. fasciculus} de Laub.}  \index{Podocarpus@\textit{Podocarpus}!fasciculus@\textbf{\textit{fasciculus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=叢花百日青&T2_new_value=true&fr=y}}{叢花百日青}\index{叢花百日青@{\Song{叢花百日青}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+macrophyllus+var.+macrophyllus}{\textit{P. macrophyllus} (Thunb.) Sweet var. \textit{macrophyllus}}  \index{Podocarpus@\textit{Podocarpus}!macrophyllus@\textit{macrophyllus}!var. macrophyllus@\textbf{var. \textit{macrophyllus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉羅漢松&T2_new_value=true&fr=y}}{大葉羅漢松}\index{大葉羅漢松@{\Song{大葉羅漢松}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+macrophyllus+var.+maki}{\textit{P. macrophyllus} (Thunb.) Sweet var. \textit{maki} Siebold \& Zucc.}  \index{Podocarpus@\textit{Podocarpus}!macrophyllus@\textit{macrophyllus}!var. maki@\textbf{var. \textit{maki}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉羅漢松&T2_new_value=true&fr=y}}{小葉羅漢松}\index{小葉羅漢松@{\Song{小葉羅漢松}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+nakaii}{\textit{P. nakaii} Hayata}  \index{Podocarpus@\textit{Podocarpus}!nakaii@\textbf{\textit{nakaii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桃實百日青&T2_new_value=true&fr=y}}{桃實百日青}\index{桃實百日青@{\Song{桃實百日青}}}\# EN
  \end{itemize}
  \end{itemize}
