
  \begin{itemize}
 \item[] \textit{Antigonon} 珊瑚藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antigonon+leptopus}{\textit{A. leptopus} Hook. \& Arn.}  \index{Antigonon@\textit{Antigonon}!leptopus@\textit{leptopus}} 珊瑚藤\index{珊瑚藤} NA $^n$
  \end{itemize}
 \item[] \textit{Fagopyrum} 蕎麥屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fagopyrum+cymosum}{\textit{F. cymosum} (Trev.) Meisn.}  \index{Fagopyrum@\textit{Fagopyrum}!cymosum@\textit{cymosum}} 赤地利\index{赤地利} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fagopyrum+esculentum}{\textit{F. esculentum} Moench.}  \index{Fagopyrum@\textit{Fagopyrum}!esculentum@\textit{esculentum}} 蕎麥\index{蕎麥} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fagopyrum+tataricum}{\textit{F. tataricum} Gaertn.}  \index{Fagopyrum@\textit{Fagopyrum}!tataricum@\textit{tataricum}} 印度蕎麥\index{印度蕎麥} NA $^n$
  \end{itemize}
 \item[] \textit{Fallopia} 蔓蓼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fallopia+multiflora}{\textit{F. multiflora} (Thunb.) Haraldson}  \index{Fallopia@\textit{Fallopia}!multiflora@\textit{multiflora}}  \index{Polygonum@\textit{Polygonum}!multiflorum@\textit{multiflorum}!var. hypoleucum@var. \textit{hypoleucum}{\\\noindent(=\textit{Fallopia multiflora})}} 臺灣何首烏\index{臺灣何首烏}\# LC
  \end{itemize}
 \item[] \textit{Koenigia} 高山蓼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Koenigia+delicatula}{\textit{K. delicatula} (Meisn.) H.Hara*}  \index{Koenigia@\textit{Koenigia}!delicatula@\textit{delicatula}} 小葉蓼\index{小葉蓼} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Koenigia+nepalensis}{\textit{K. nepalensis} D.Don}  \index{Koenigia@\textit{Koenigia}!nepalensis@\textit{nepalensis}}  \index{Polygonum@\textit{Polygonum}!filicaule@\textit{filicaule}{\\\noindent(= \textit{Koenigia nepalensis})}} 高山蓼\index{高山蓼} NT
  \end{itemize}
 \item[] \textit{Persicaria} 春蓼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+barbata+var.+barbata}{\textit{P. barbata} (L.) H.Hara var. \textit{barbata}}  \index{Persicaria@\textit{Persicaria}!barbata@\textit{barbata}!var. barbata@var. \textit{barbata}}  \index{Polygonum@\textit{Polygonum}!barbatum@\textit{barbatum}{\\\noindent(= \textit{Persicaria barbata} var. \textit{barbata})}} 毛蓼\index{毛蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+barbata+var.+gracilis}{\textit{P. barbata} (L.) H.Hara var. \textit{gracilis} (Danser) H.Hara}  \index{Persicaria@\textit{Persicaria}!barbata@\textit{barbata}!var. gracilis@var. \textit{gracilis}}  \index{Polygonum@\textit{Polygonum}!barbatum@\textit{barbatum}!var. gracilis@var. \textit{gracilis}{\\\noindent(=\textit{Persicaria barbata} var. \textit{gracilis})}} 細刺毛蓼\index{細刺毛蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+capitata}{\textit{P. capitata} (Buch.-Ham. ex D.Don) H.Gross}  \index{Persicaria@\textit{Persicaria}!capitata@\textit{capitata}}  \index{Polygonum@\textit{Polygonum}!capitatum@\textit{capitatum}{\\\noindent(= \textit{Persicaria capitata})}} 頭花蓼\index{頭花蓼} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+chinensis}{\textit{P. chinensis} (L.) H.Gross}  \index{Persicaria@\textit{Persicaria}!chinensis@\textit{chinensis}}  \index{Polygonum@\textit{Polygonum}!chinense@\textit{chinense}{\\\noindent(= \textit{Persicaria chinensis})}} 火炭母草\index{火炭母草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+conspicua}{\textit{P. conspicua} (Nakai) Nakai ex T.Mori}  \index{Persicaria@\textit{Persicaria}!conspicua@\textit{conspicua}}  \index{Polygonum@\textit{Polygonum}!conspicuum@\textit{conspicuum}{\\\noindent(= \textit{Persicaria conspicua})}} 櫻蓼\index{櫻蓼} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+dichotoma}{\textit{P. dichotoma} (Blume) Masam.}  \index{Persicaria@\textit{Persicaria}!dichotoma@\textit{dichotoma}}  \index{Polygonum@\textit{Polygonum}!dichotomum@\textit{dichotomum}{\\\noindent(= \textit{Persicaria dichotoma})}} 水紅骨蛇\index{水紅骨蛇} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+filiformis}{\textit{P. filiformis} (Thunb.) Nakai}  \index{Persicaria@\textit{Persicaria}!filiformis@\textit{filiformis}}  \index{Polygonum@\textit{Polygonum}!virginatum@\textit{virginatum}!var. filiforme@var. \textit{filiforme}{\\\noindent(=\textit{Persicaria filiformis})}} 金線草\index{金線草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+foliosa}{\textit{P. foliosa} (H.Lindb.) Kitag.}  \index{Persicaria@\textit{Persicaria}!foliosa@\textit{foliosa}}  \index{Polygonum@\textit{Polygonum}!foliosum@\textit{foliosum}{\\\noindent(= \textit{Persicaria foliosa})}} 宜蘭蓼\index{宜蘭蓼} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+glabra}{\textit{P. glabra} (Willd.) M.Gómez}  \index{Persicaria@\textit{Persicaria}!glabra@\textit{glabra}}  \index{Polygonum@\textit{Polygonum}!glabrum@\textit{glabrum}{\\\noindent(= \textit{Persicaria glabra})}} 紅辣蓼\index{紅辣蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+hastatosagittata}{\textit{P. hastatosagittata} (Makino) Nakai ex T.Mori}  \index{Persicaria@\textit{Persicaria}!hastatosagittata@\textit{hastatosagittata}}  \index{Polygonum@\textit{Polygonum}!hastatosagittatum@\textit{hastatosagittatum}{\\\noindent(= \textit{Persicaria hastatosagittata})}} 長箭葉蓼\index{長箭葉蓼} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+hydropiper}{\textit{P. hydropiper} (L.) Delarbre}  \index{Persicaria@\textit{Persicaria}!hydropiper@\textit{hydropiper}}  \index{Polygonum@\textit{Polygonum}!hydropiper@\textit{hydropiper}{\\\noindent(= \textit{Persicaria hydropiper})}} 水蓼\index{水蓼} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+japonica}{\textit{P. japonica} (Meisn.) H.Gross ex Nakai}  \index{Persicaria@\textit{Persicaria}!japonica@\textit{japonica}}  \index{Polygonum@\textit{Polygonum}!japonicum@\textit{japonicum}{\\\noindent(= \textit{Persicaria japonica})}} 蠶繭草\index{蠶繭草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+kawagoeana}{\textit{P. kawagoeana} (Makino) Nakai}  \index{Persicaria@\textit{Persicaria}!kawagoeana@\textit{kawagoeana}}  \index{Polygonum@\textit{Polygonum}!micranthum@\textit{micranthum}{\\\noindent(= \textit{Persicaria kawagoeana})}} 盤腺蓼\index{盤腺蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+lanata}{\textit{P. lanata} (Roxb.) Tzvelev}  \index{Persicaria@\textit{Persicaria}!lanata@\textit{lanata}}  \index{Polygonum@\textit{Polygonum}!lanatum@\textit{lanatum}{\\\noindent(= \textit{Persicaria lanata})}} 白苦柱\index{白苦柱} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+lapathifolia}{\textit{P. lapathifolia} (L.) Delarbre}  \index{Persicaria@\textit{Persicaria}!lapathifolia@\textit{lapathifolia}}  \index{Polygonum@\textit{Polygonum}!lapathifolium@\textit{lapathifolium}{\\\noindent(= \textit{Persicaria lapathifolia})}} 早苗蓼\index{早苗蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+longiseta}{\textit{P. longiseta} (Bruijn) Kitag.}  \index{Persicaria@\textit{Persicaria}!longiseta@\textit{longiseta}}  \index{Polygonum@\textit{Polygonum}!longisetum@\textit{longisetum}{\\\noindent(= \textit{Persicaria longiseta})}} 睫穗蓼\index{睫穗蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+maackiana}{\textit{P. maackiana} (Regel) Nakai ex T.Mori}  \index{Persicaria@\textit{Persicaria}!maackiana@\textit{maackiana}}  \index{Polygonum@\textit{Polygonum}!maackianum@\textit{maackianum}{\\\noindent(= \textit{Persicaria maackiana})}} 長戟葉蓼\index{長戟葉蓼} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+maculosa}{\textit{P. maculosa} Gray}  \index{Persicaria@\textit{Persicaria}!maculosa@\textit{maculosa}}  \index{Polygonum@\textit{Polygonum}!persicaria@\textit{persicaria}{\\\noindent(= \textit{Persicaria maculosa})}} 春蓼\index{春蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+muricata}{\textit{P. muricata} (Meisn.) Nemoto}  \index{Persicaria@\textit{Persicaria}!muricata@\textit{muricata}}  \index{Polygonum@\textit{Polygonum}!muricatum@\textit{muricatum}{\\\noindent(= \textit{Persicaria muricata})}} 小花蓼\index{小花蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+nepalensis}{\textit{P. nepalensis} (Meisn.) Miyabe}  \index{Persicaria@\textit{Persicaria}!nepalensis@\textit{nepalensis}}  \index{Polygonum@\textit{Polygonum}!nepalense@\textit{nepalense}{\\\noindent(= \textit{Persicaria nepalensis})}} 野蕎麥\index{野蕎麥} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+orientalis}{\textit{P. orientalis} (L.) Spach}  \index{Persicaria@\textit{Persicaria}!orientalis@\textit{orientalis}}  \index{Polygonum@\textit{Polygonum}!orientale@\textit{orientale}{\\\noindent(= \textit{Persicaria orientalis})}} 紅蓼\index{紅蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+perfoliata}{\textit{P. perfoliata} (L.) H.Gross}  \index{Persicaria@\textit{Persicaria}!perfoliata@\textit{perfoliata}}  \index{Polygonum@\textit{Polygonum}!perfoliatum@\textit{perfoliatum}{\\\noindent(= \textit{Persicaria perfoliata})}} 扛板歸\index{扛板歸} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+posumbu}{\textit{P. posumbu} (Buch.-Ham. ex D.Don) H.Gross}  \index{Persicaria@\textit{Persicaria}!posumbu@\textit{posumbu}}  \index{Polygonum@\textit{Polygonum}!posumbu@\textit{posumbu}{\\\noindent(= \textit{Persicaria posumbu})}} 花蓼\index{花蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+praetermissa}{\textit{P. praetermissa} (Hook.f.) H.Hara}  \index{Persicaria@\textit{Persicaria}!praetermissa@\textit{praetermissa}}  \index{Polygonum@\textit{Polygonum}!praetermissum@\textit{praetermissum}{\\\noindent(= \textit{Persicaria praetermissa})}} 細葉雀翹\index{細葉雀翹} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+pubescens}{\textit{P. pubescens} (Blume) H.Hara}  \index{Persicaria@\textit{Persicaria}!pubescens@\textit{pubescens}}  \index{Polygonum@\textit{Polygonum}!pubescens@\textit{pubescens}{\\\noindent(= \textit{Persicaria pubescens})}} 腺花毛蓼\index{腺花毛蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+pulchra}{\textit{P. pulchra} (Blume) Soják}  \index{Persicaria@\textit{Persicaria}!pulchra@\textit{pulchra}}  \index{Polygonum@\textit{Polygonum}!pulchrum@\textit{pulchrum}{\\\noindent(= \textit{Persicaria pulchra})}} 絨毛蓼\index{絨毛蓼} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+runcinata}{\textit{P. runcinata} (Buch.-Ham. ex D.Don) H.Gross}  \index{Persicaria@\textit{Persicaria}!runcinata@\textit{runcinata}}  \index{Polygonum@\textit{Polygonum}!runcinatum@\textit{runcinatum}{\\\noindent(= \textit{Persicaria runcinata})}} 玉山蓼\index{玉山蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+sagittata}{\textit{P. sagittata} (L.) H.Gross}  \index{Persicaria@\textit{Persicaria}!sagittata@\textit{sagittata}}  \index{Polygonum@\textit{Polygonum}!sagittatum@\textit{sagittatum}{\\\noindent(= \textit{Persicaria sagittata})}} 箭葉蓼\index{箭葉蓼} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+scabra}{\textit{P. scabra} (Moench) Moldenke}  \index{Persicaria@\textit{Persicaria}!scabra@\textit{scabra}}  \index{Polygonum@\textit{Polygonum}!scabrum@\textit{scabrum}{\\\noindent(= \textit{Persicaria scabra})}} 糙葉蓼\index{糙葉蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+senticosa}{\textit{P. senticosa} (Meisn.) H.Gross ex Nakai}  \index{Persicaria@\textit{Persicaria}!senticosa@\textit{senticosa}}  \index{Polygonum@\textit{Polygonum}!senticosum@\textit{senticosum}{\\\noindent(= \textit{Persicaria senticosa})}} 刺蓼\index{刺蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+thunbergii}{\textit{P. thunbergii} (Siebold \& Zucc.) H.Gross}  \index{Persicaria@\textit{Persicaria}!thunbergii@\textit{thunbergii}}  \index{Polygonum@\textit{Polygonum}!thunbergii@\textit{thunbergii}{\\\noindent(= \textit{Persicaria thunbergii})}} 戟葉蓼\index{戟葉蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+tripterocarpa}{\textit{P. tripterocarpa} (A.Gray ex Rothr.) Ronse Decr.}  \index{Persicaria@\textit{Persicaria}!tripterocarpa@\textit{tripterocarpa}}  \index{Polygonum@\textit{Polygonum}!trigonocarpum@\textit{trigonocarpum}{\\\noindent(= \textit{Persicaria tripterocarpa})}} 細葉蓼\index{細葉蓼} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Persicaria+viscosa}{\textit{P. viscosa} (Buch.-Ham. ex D.Don) H.Gross ex Nakai}  \index{Persicaria@\textit{Persicaria}!viscosa@\textit{viscosa}}  \index{Polygonum@\textit{Polygonum}!viscosum@\textit{viscosum}{\\\noindent(= \textit{Persicaria viscosa})}} 粘毛蓼\index{粘毛蓼} VU
  \end{itemize}
 \item[] \textit{Polygonum} 蓼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polygonum+aviculare}{\textit{P. aviculare} L.}  \index{Polygonum@\textit{Polygonum}!aviculare@\textit{aviculare}} 扁蓄\index{扁蓄} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polygonum+pilushanense}{\textit{P. pilushanense} Y.C.Liu \& C.S.Ou*}  \index{Polygonum@\textit{Polygonum}!pilushanense@\textit{pilushanense}} 畢祿山蓼\index{畢祿山蓼}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Polygonum+plebeium}{\textit{P. plebeium} R.Br.}  \index{Polygonum@\textit{Polygonum}!plebeium@\textit{plebeium}} 假扁蓄\index{假扁蓄} NA $^n$
  \end{itemize}
 \item[] \textit{Reynoutria} 虎杖屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Reynoutria+japonica}{\textit{R. japonica} Houtt.}  \index{Reynoutria@\textit{Reynoutria}!japonica@\textit{japonica}}  \index{Polygonum@\textit{Polygonum}!cuspidatum@\textit{cuspidatum}{\\\noindent(= \textit{Reynoutria japonica})}} 虎杖\index{虎杖} LC
  \end{itemize}
 \item[] \textit{Rumex} 酸模屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+acetosa}{\textit{R. acetosa} L.}  \index{Rumex@\textit{Rumex}!acetosa@\textit{acetosa}} 酸模\index{酸模} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+acetosella}{\textit{R. acetosella} L.}  \index{Rumex@\textit{Rumex}!acetosella@\textit{acetosella}} 小酸模\index{小酸模} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+crispus+var.+crispus}{\textit{R. crispus} L. var. \textit{crispus}}  \index{Rumex@\textit{Rumex}!crispus@\textit{crispus}!var. crispus@var. \textit{crispus}} 皺葉酸模\index{皺葉酸模} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+crispus+var.+japonicus}{\textit{R. crispus} L. var. \textit{japonicus} (Houtt.) Makino}  \index{Rumex@\textit{Rumex}!crispus@\textit{crispus}!var. japonicus@var. \textit{japonicus}} 羊蹄\index{羊蹄} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+maritimus}{\textit{R. maritimus} L.}  \index{Rumex@\textit{Rumex}!maritimus@\textit{maritimus}} 連明子\index{連明子} NA $^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+nipponicus}{\textit{R. nipponicus} Franch. \& Sav.}  \index{Rumex@\textit{Rumex}!nipponicus@\textit{nipponicus}} 小羊蹄\index{小羊蹄} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rumex+obtusifolius}{\textit{R. obtusifolius} L.}  \index{Rumex@\textit{Rumex}!obtusifolius@\textit{obtusifolius}} 大羊蹄\index{大羊蹄} NA $^n$
  \end{itemize}
  \end{itemize}
