
  \begin{itemize}
 \item[] \textit{Aglaomorpha}\index{Aglaomorpha@\textit{Aglaomorpha}} 連珠蕨屬
                                
  \begin{itemize}
        \item[] \textit{A. coronans} (Wall. ex Mett.) Copel. \index{Aglaomorpha@\textit{Aglaomorpha}!coronans@\textit{coronans}} 崖薑蕨 \index{崖薑蕨}  LC
        \item[] \textit{A. fortunei} (Kunze ex Mett.) Hovenkamp \& S.Linds. \index{Aglaomorpha@\textit{Aglaomorpha}!fortunei@\textit{fortunei}} 槲蕨 \index{槲蕨}  LC
        \item[] \textit{A. meyeniana} Schott \index{Aglaomorpha@\textit{Aglaomorpha}!meyeniana@\textit{meyeniana}} 連珠蕨　 \index{連珠蕨　}  NT
  \end{itemize}
 \item[] \textit{Arthromeris}\index{Arthromeris@\textit{Arthromeris}} 節肢蕨屬
                                
  \begin{itemize}
        \item[] \textit{A. lehmanni} (Mett.) Ching \index{Arthromeris@\textit{Arthromeris}!lehmanni@\textit{lehmanni}} 肢節蕨 \index{肢節蕨}  LC
  \end{itemize}
 \item[] \textit{Calymmodon}\index{Calymmodon@\textit{Calymmodon}} 荷包蕨屬
                                
  \begin{itemize}
        \item[] \textit{C. gracilis} (Fée) Copel. \index{Calymmodon@\textit{Calymmodon}!gracilis@\textit{gracilis}} 疏毛荷包蕨 \index{疏毛荷包蕨}  LC
        \item[] \textit{C. oligotrichus} T.C.Hsu \index{Calymmodon@\textit{Calymmodon}!oligotrichus@\textit{oligotrichus}} 寡毛荷包蕨 \index{寡毛荷包蕨}  NT
        \item[] \textit{C. ordinatus} Copel. \index{Calymmodon@\textit{Calymmodon}!ordinatus@\textit{ordinatus}} 姬荷包蕨 \index{姬荷包蕨}  VU
  \end{itemize}
 \item[] \textit{Chrysogrammitis}\index{Chrysogrammitis@\textit{Chrysogrammitis}} Chrysogrammitis屬
                                
  \begin{itemize}
        \item[] \textit{C. glandulosa} (J.Sm.) Parris \index{Chrysogrammitis@\textit{Chrysogrammitis}!glandulosa@\textit{glandulosa}} 擬虎尾蒿蕨 \index{擬虎尾蒿蕨}  EN
  \end{itemize}
 \item[] \textit{Dasygrammitis}\index{Dasygrammitis@\textit{Dasygrammitis}} Dasygrammitis屬
                                
  \begin{itemize}
        \item[] \textit{D. mollicoma} (Nees \& Blume) Parris \index{Dasygrammitis@\textit{Dasygrammitis}!mollicoma@\textit{mollicoma}} 南洋蒿蕨 \index{南洋蒿蕨}  EN
  \end{itemize}
 \item[] \textit{Goniophlebium}\index{Goniophlebium@\textit{Goniophlebium}} Goniophlebium屬
                                
  \begin{itemize}
        \item[] \textit{G. argutum} (Wall. ex Hook.) J.Sm. \index{Goniophlebium@\textit{Goniophlebium}!argutum@\textit{argutum}} 箭葉水龍骨 \index{箭葉水龍骨}  LC
  \end{itemize}
 \item[] \textit{Grammitis}\index{Grammitis@\textit{Grammitis}} 禾葉蕨屬
                                
  \begin{itemize}
        \item[] \textit{G. intromissa} (H.Christ) Parris \index{Grammitis@\textit{Grammitis}!intromissa@\textit{intromissa}} 大禾葉蕨 \index{大禾葉蕨}  DD
  \end{itemize}
 \item[] \textit{Lemmaphyllum}\index{Lemmaphyllum@\textit{Lemmaphyllum}} 伏石蕨屬
                                
  \begin{itemize}
        \item[] \textit{L. diversum} (Rosenst.) Tagawa \index{Lemmaphyllum@\textit{Lemmaphyllum}!diversum@\textit{diversum}} 骨牌蕨 \index{骨牌蕨}  LC
        \item[] \textit{L. microphyllum} var. \textit{microphyllum}  \index{Lemmaphyllum@\textit{Lemmaphyllum}!microphyllum@\textit{microphyllum}!var. microphyllum@var. \textit{microphyllum}}
                                        伏石蕨 \index{伏石蕨}  LC
        \item[] \textit{L. microphyllum} var. \textit{obovatum} (Harrington) C.Chr. \index{Lemmaphyllum@\textit{Lemmaphyllum}!microphyllum@\textit{microphyllum}!var. obovatum@var. \textit{obovatum}}
                                        倒卵伏石蕨 \index{倒卵伏石蕨}  ?
  \end{itemize}
 \item[] \textit{Lepisorus}\index{Lepisorus@\textit{Lepisorus}} 瓦韋屬
                                
  \begin{itemize}
        \item[] \textit{L. clathratus} (C.B.Clarke) Ching \index{Lepisorus@\textit{Lepisorus}!clathratus@\textit{clathratus}} 網眼瓦葦 \index{網眼瓦葦}  LC
        \item[] \textit{L. kawakamii} (Hayata) Tagawa \index{Lepisorus@\textit{Lepisorus}!kawakamii@\textit{kawakamii}} 鱗瓦葦 \index{鱗瓦葦} \# LC
        \item[] \textit{L. kuchenensis} (Y.C.Wu) Ching \index{Lepisorus@\textit{Lepisorus}!kuchenensis@\textit{kuchenensis}} 猺山瓦葦 \index{猺山瓦葦}  DD
        \item[] \textit{L. megasorus} (C.Chr.) Ching \index{Lepisorus@\textit{Lepisorus}!megasorus@\textit{megasorus}} 長柄瓦葦 \index{長柄瓦葦} \# LC
        \item[] \textit{L. miyoshianus} (Makino) Fraser-Jenk. \& Subh.Chandra \index{Lepisorus@\textit{Lepisorus}!miyoshianus@\textit{miyoshianus}} 二條線蕨 \index{二條線蕨}  NT
        \item[] \textit{L. monilisorus} (Hayata) Tagawa \index{Lepisorus@\textit{Lepisorus}!monilisorus@\textit{monilisorus}} 擬笈瓦葦 \index{擬笈瓦葦} \# LC
        \item[] \textit{L. morrisonensis} (Hayata) H.Ito \index{Lepisorus@\textit{Lepisorus}!morrisonensis@\textit{morrisonensis}} 玉山瓦葦 \index{玉山瓦葦}  LC
        \item[] \textit{L. mucronatus} (Fée) Li Wang \index{Lepisorus@\textit{Lepisorus}!mucronatus@\textit{mucronatus}} 尖嘴蕨 \index{尖嘴蕨}  CR
        \item[] \textit{L. obscurevenulosus} (Hayata) Ching \index{Lepisorus@\textit{Lepisorus}!obscurevenulosus@\textit{obscurevenulosus}} 粵瓦葦 \index{粵瓦葦}  LC
        \item[] \textit{L. pseudoussuriensis} Tagawa \index{Lepisorus@\textit{Lepisorus}!pseudoussuriensis@\textit{pseudoussuriensis}} 擬烏蘇里瓦葦 \index{擬烏蘇里瓦葦} \# LC
        \item[] \textit{L. suboligolepidus} Ching \index{Lepisorus@\textit{Lepisorus}!suboligolepidus@\textit{suboligolepidus}} 擬鱗瓦葦 \index{擬鱗瓦葦}  LC
        \item[] \textit{L. thunbergianus} (Kaulf.) Ching \index{Lepisorus@\textit{Lepisorus}!thunbergianus@\textit{thunbergianus}} 瓦葦 \index{瓦葦}  LC
        \item[] \textit{L. tosaensis} (Makino) H.Ito \index{Lepisorus@\textit{Lepisorus}!tosaensis@\textit{tosaensis}} 擬瓦葦 \index{擬瓦葦}  LC
  \end{itemize}
 \item[] \textit{Leptochilus}\index{Leptochilus@\textit{Leptochilus}} 薄唇蕨屬
                                
  \begin{itemize}
        \item[] \textit{L. decurrens} Blume \index{Leptochilus@\textit{Leptochilus}!decurrens@\textit{decurrens}} 萊蕨 \index{萊蕨}  LC
        \item[] \textit{L. ellipticus} (Thunb.) Noot. \index{Leptochilus@\textit{Leptochilus}!ellipticus@\textit{ellipticus}} 橢圓線蕨 \index{橢圓線蕨}  LC
        \item[] \textit{L. hemionitideus} (C.Presl) Noot. \index{Leptochilus@\textit{Leptochilus}!hemionitideus@\textit{hemionitideus}} 斷線蕨 \index{斷線蕨}  LC
        \item[] \textit{L. henryi} (Baker) X.C.Zhang \index{Leptochilus@\textit{Leptochilus}!henryi@\textit{henryi}} 亨利氏線蕨 \index{亨利氏線蕨}  DD-T
        \item[] \textit{L. insignis} (Blume) Fraser-Jenk. \index{Leptochilus@\textit{Leptochilus}!insignis@\textit{insignis}} 箭葉星蕨 \index{箭葉星蕨}  LC
        \item[] \textit{L. pothifolius} (Buch.-Ham. ex D.Don) Fraser-Jenk. \index{Leptochilus@\textit{Leptochilus}!pothifolius@\textit{pothifolius}} 大線蕨 \index{大線蕨}  LC
        \item[] \textit{L. pteropus} (Blume) Fraser-Jenk. \index{Leptochilus@\textit{Leptochilus}!pteropus@\textit{pteropus}} 三叉葉星蕨 \index{三叉葉星蕨}  LC
        \item[] \textit{L. wrightii} (Hook.) X.C.Zhang \index{Leptochilus@\textit{Leptochilus}!wrightii@\textit{wrightii}} 萊氏線蕨 \index{萊氏線蕨}  LC
        \item[] \textit{L. ×} shintenensis \textit{} (Hayata) Nakaike \index{Leptochilus@\textit{Leptochilus}!×@\textit{×}!shintenensis @shintenensis \textit{}}
                                        新店線蕨 \index{新店線蕨}  NA
  \end{itemize}
 \item[] \textit{Loxogramme}\index{Loxogramme@\textit{Loxogramme}} 劍蕨屬
                                
  \begin{itemize}
        \item[] \textit{L. biformis} Tagawa \index{Loxogramme@\textit{Loxogramme}!biformis@\textit{biformis}} 二形劍蕨 \index{二形劍蕨} \# EN
        \item[] \textit{L. chinensis} Ching \index{Loxogramme@\textit{Loxogramme}!chinensis@\textit{chinensis}} 中國劍蕨 \index{中國劍蕨} \# DD
        \item[] \textit{L. confertifolia} Tagawa \index{Loxogramme@\textit{Loxogramme}!confertifolia@\textit{confertifolia}} 密葉劍蕨 \index{密葉劍蕨} \# DD
        \item[] \textit{L. formosana} Nakai \index{Loxogramme@\textit{Loxogramme}!formosana@\textit{formosana}} 臺灣劍蕨 \index{臺灣劍蕨}  LC
        \item[] \textit{L. grammitoides} (Baker) C.Chr. \index{Loxogramme@\textit{Loxogramme}!grammitoides@\textit{grammitoides}} 小葉劍蕨 \index{小葉劍蕨}  NT
        \item[] \textit{L. remotefrondigera} Hayata \index{Loxogramme@\textit{Loxogramme}!remotefrondigera@\textit{remotefrondigera}} 長柄劍蕨 \index{長柄劍蕨} \# LC
        \item[] \textit{L. salicifolia} (Makino) Makino \index{Loxogramme@\textit{Loxogramme}!salicifolia@\textit{salicifolia}} 柳葉劍蕨 \index{柳葉劍蕨}  LC
  \end{itemize}
 \item[] \textit{Microsorum}\index{Microsorum@\textit{Microsorum}} 星蕨屬
                                
  \begin{itemize}
        \item[] \textit{M. membranaceum} (D.Don) Ching \index{Microsorum@\textit{Microsorum}!membranaceum@\textit{membranaceum}} 膜葉星蕨 \index{膜葉星蕨}  LC
        \item[] \textit{M. punctatum} (L.) Copel. \index{Microsorum@\textit{Microsorum}!punctatum@\textit{punctatum}} 星蕨 \index{星蕨}  LC
        \item[] \textit{M. steerei} (Harr.) Ching \index{Microsorum@\textit{Microsorum}!steerei@\textit{steerei}} 廣葉星蕨 \index{廣葉星蕨}  EN
  \end{itemize}
 \item[] \textit{Neocheiropteris}\index{Neocheiropteris@\textit{Neocheiropteris}} 扇蕨屬
                                
  \begin{itemize}
        \item[] \textit{N. ensata} (Thunb.) Ching \index{Neocheiropteris@\textit{Neocheiropteris}!ensata@\textit{ensata}} 扇蕨 \index{扇蕨}  LC
        \item[] \textit{N. fortunei} (T.Moore) Fraser-Jenkins, Pariyar \& Kandel \index{Neocheiropteris@\textit{Neocheiropteris}!fortunei@\textit{fortunei}} 大星蕨 \index{大星蕨}  LC
  \end{itemize}
 \item[] \textit{Oreogrammitis}\index{Oreogrammitis@\textit{Oreogrammitis}} Oreogrammitis屬
                                
  \begin{itemize}
        \item[] \textit{O. adspersa} (Blume) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!adspersa@\textit{adspersa}} 無毛禾葉蕨 \index{無毛禾葉蕨}  VU
        \item[] \textit{O. caespitosa} (Blume) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!caespitosa@\textit{caespitosa}} 穴孢濱禾蕨 \index{穴孢濱禾蕨}  CR
        \item[] \textit{O. congener} (Blume) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!congener@\textit{congener}} 大武禾葉蕨 \index{大武禾葉蕨}  LC
        \item[] \textit{O. congener} var. \textit{polytricha} T.C.Hsu \index{Oreogrammitis@\textit{Oreogrammitis}!congener@\textit{congener}!var. polytricha@var. \textit{polytricha}}
                                        多毛禾葉蕨 \index{多毛禾葉蕨}  EN
        \item[] \textit{O. marivelesensis} (Copel.) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!marivelesensis@\textit{marivelesensis}} 弼昭禾葉蕨 \index{弼昭禾葉蕨}  CR
        \item[] \textit{O. nuda} (Tagawa) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!nuda@\textit{nuda}} 長孢禾葉蕨 \index{長孢禾葉蕨} \# EN
        \item[] \textit{O. orientalis} T.C.Hsu \index{Oreogrammitis@\textit{Oreogrammitis}!orientalis@\textit{orientalis}} 東亞禾葉蕨 \index{東亞禾葉蕨}  CR
        \item[] \textit{O. reinwardtii} (Blume) Parris \index{Oreogrammitis@\textit{Oreogrammitis}!reinwardtii@\textit{reinwardtii}} 毛禾葉蕨 \index{毛禾葉蕨}  NT
  \end{itemize}
 \item[] \textit{Phymatosorus}\index{Phymatosorus@\textit{Phymatosorus}} 瘤蕨屬
                                
  \begin{itemize}
        \item[] \textit{P. longissimus} (Blume) Pic.Serm. \index{Phymatosorus@\textit{Phymatosorus}!longissimus@\textit{longissimus}} 水社擬茀蕨 \index{水社擬茀蕨}  EN
        \item[] \textit{P. membranifolius} (R.Br.) S.G.Lu \index{Phymatosorus@\textit{Phymatosorus}!membranifolius@\textit{membranifolius}} 薄葉擬茀蕨 \index{薄葉擬茀蕨}  VU
        \item[] \textit{P. scolopendria} (Burm.f.) Pic.Serm. \index{Phymatosorus@\textit{Phymatosorus}!scolopendria@\textit{scolopendria}} 海岸星蕨 \index{海岸星蕨}  LC
  \end{itemize}
 \item[] \textit{Pichisermollodes}\index{Pichisermollodes@\textit{Pichisermollodes}} Pichisermollodes屬
                                
  \begin{itemize}
        \item[] \textit{P. quasidivaricata} (Hayata) Fraser-Jenk. \index{Pichisermollodes@\textit{Pichisermollodes}!quasidivaricata@\textit{quasidivaricata}} 玉山茀蕨 \index{玉山茀蕨}  LC
  \end{itemize}
 \item[] \textit{Platycerium}\index{Platycerium@\textit{Platycerium}} Platycerium屬
                                
  \begin{itemize}
        \item[] \textit{P. bifurcatum} (Cav.) C.Chr. \index{Platycerium@\textit{Platycerium}!bifurcatum@\textit{bifurcatum}} 鹿角蕨 \index{鹿角蕨}  NA
  \end{itemize}
 \item[] \textit{Polypodiodes}\index{Polypodiodes@\textit{Polypodiodes}} Polypodiodes屬
                                
  \begin{itemize}
        \item[] \textit{P. amoena} (Wall. ex Mett.) Ching \index{Polypodiodes@\textit{Polypodiodes}!amoena@\textit{amoena}} 阿里山水龍骨 \index{阿里山水龍骨}  LC
        \item[] \textit{P. fieldingiana} (Kunze ex Mett.) Fraser-Jenk., Kandel \& Pariyar \index{Polypodiodes@\textit{Polypodiodes}!fieldingiana@\textit{fieldingiana}} 栗柄水龍骨 \index{栗柄水龍骨}  VU
        \item[] \textit{P. formosana} (Baker) Ching \index{Polypodiodes@\textit{Polypodiodes}!formosana@\textit{formosana}} 臺灣水龍骨 \index{臺灣水龍骨}  LC
        \item[] \textit{P. raishaensis} (Rosenst.) S.G.Lu \index{Polypodiodes@\textit{Polypodiodes}!raishaensis@\textit{raishaensis}} 大葉水龍骨 \index{大葉水龍骨} \# LC
        \item[] \textit{P. transpianensis} (Yamam.) Saiki \index{Polypodiodes@\textit{Polypodiodes}!transpianensis@\textit{transpianensis}} 疏毛水龍骨 \index{疏毛水龍骨} \# LC
  \end{itemize}
 \item[] \textit{Prosaptia}\index{Prosaptia@\textit{Prosaptia}} 穴子蕨屬
                                
  \begin{itemize}
        \item[] \textit{P. contigua} (G.Forst.) C.Presl \index{Prosaptia@\textit{Prosaptia}!contigua@\textit{contigua}} 穴子蕨 \index{穴子蕨}  LC
        \item[] \textit{P. formosana} (Hayata) T.C.Hsu \index{Prosaptia@\textit{Prosaptia}!formosana@\textit{formosana}} 寶島穴子蕨 \index{寶島穴子蕨}  LC
        \item[] \textit{P. nutans} (Blume) Mett. \index{Prosaptia@\textit{Prosaptia}!nutans@\textit{nutans}} 俯垂穴子蕨 \index{俯垂穴子蕨}  EN
        \item[] \textit{P. obliquata} (Blume) Mett. \index{Prosaptia@\textit{Prosaptia}!obliquata@\textit{obliquata}} 密毛蒿蕨 \index{密毛蒿蕨}  LC
        \item[] \textit{P. pectinata} T.Moore \index{Prosaptia@\textit{Prosaptia}!pectinata@\textit{pectinata}} 篦齒穴子蕨 \index{篦齒穴子蕨}  CR
        \item[] \textit{P. urceolaris} (Hayata) Copel. \index{Prosaptia@\textit{Prosaptia}!urceolaris@\textit{urceolaris}} 臺灣穴子蕨 \index{臺灣穴子蕨}  NT
  \end{itemize}
 \item[] \textit{Pyrrosia}\index{Pyrrosia@\textit{Pyrrosia}} 石韋屬
                                
  \begin{itemize}
        \item[] \textit{P. adnascens} (Sw.) Ching \index{Pyrrosia@\textit{Pyrrosia}!adnascens@\textit{adnascens}} 抱樹石葦 \index{抱樹石葦}  LC
        \item[] \textit{P. angustissima} (Giesenh. ex Diels) Tagawa \& K.Iwats. \index{Pyrrosia@\textit{Pyrrosia}!angustissima@\textit{angustissima}} 石蕨 \index{石蕨}  VU
        \item[] \textit{P. assimilis} (Baker) Ching \index{Pyrrosia@\textit{Pyrrosia}!assimilis@\textit{assimilis}} 相似石葦 \index{相似石葦}  EN
        \item[] \textit{P. davidii} (Bak.) Ching \index{Pyrrosia@\textit{Pyrrosia}!davidii@\textit{davidii}} 中國石葦 \index{中國石葦}  DD
        \item[] \textit{P. linearifolia} (Hook.) Ching \index{Pyrrosia@\textit{Pyrrosia}!linearifolia@\textit{linearifolia}} 絨毛石葦 \index{絨毛石葦}  LC
        \item[] \textit{P. lingua} (Thunb.) Farw. \index{Pyrrosia@\textit{Pyrrosia}!lingua@\textit{lingua}} 石葦 \index{石葦}  LC
        \item[] \textit{P. matsudae} (Hayata) Tagawa \index{Pyrrosia@\textit{Pyrrosia}!matsudae@\textit{matsudae}} 松田氏石葦 \index{松田氏石葦} \# DD
        \item[] \textit{P. polydactyla} (Hance) Ching \index{Pyrrosia@\textit{Pyrrosia}!polydactyla@\textit{polydactyla}} 槭葉石葦 \index{槭葉石葦} \# LC
        \item[] \textit{P. sheareri} (Baker) Ching \index{Pyrrosia@\textit{Pyrrosia}!sheareri@\textit{sheareri}} 盧山石葦 \index{盧山石葦}  LC
        \item[] \textit{P. transmorrisonensis} (Hayata) Ching \index{Pyrrosia@\textit{Pyrrosia}!transmorrisonensis@\textit{transmorrisonensis}} 玉山石葦 \index{玉山石葦} \# DD
  \end{itemize}
 \item[] \textit{Radiogrammitis}\index{Radiogrammitis@\textit{Radiogrammitis}} 幅禾蕨屬
                                
  \begin{itemize}
        \item[] \textit{R. beddomeana} (Alderw.) Parris \index{Radiogrammitis@\textit{Radiogrammitis}!beddomeana@\textit{beddomeana}} 無鱗禾葉蕨 \index{無鱗禾葉蕨}  NT
        \item[] \textit{R. ilanensis} T.C.Hsu \index{Radiogrammitis@\textit{Radiogrammitis}!ilanensis@\textit{ilanensis}} 宜蘭禾葉蕨 \index{宜蘭禾葉蕨}  CR
        \item[] \textit{R. moorei} Parris \& R. Knapp \index{Radiogrammitis@\textit{Radiogrammitis}!moorei@\textit{moorei}} 牟氏輻禾蕨 \index{牟氏輻禾蕨}  CR
        \item[] \textit{R. setigera} (Blume) Parris \index{Radiogrammitis@\textit{Radiogrammitis}!setigera@\textit{setigera}} 剛毛輻禾蕨 \index{剛毛輻禾蕨}  VU
        \item[] \textit{R. subnervosa} T.C.Hsu \index{Radiogrammitis@\textit{Radiogrammitis}!subnervosa@\textit{subnervosa}} 亞顯脈禾葉蕨 \index{亞顯脈禾葉蕨}  NT
        \item[] \textit{R. taiwanensis} Parris \& R. Knapp \index{Radiogrammitis@\textit{Radiogrammitis}!taiwanensis@\textit{taiwanensis}} 台灣輻禾蕨 \index{台灣輻禾蕨}  NT
  \end{itemize}
 \item[] \textit{Schellolepis}\index{Schellolepis@\textit{Schellolepis}} 棱脈蕨屬
                                
  \begin{itemize}
        \item[] \textit{S. persicifolia} (Desv.) Pic.Serm. \index{Schellolepis@\textit{Schellolepis}!persicifolia@\textit{persicifolia}} 棱脈蕨 \index{棱脈蕨}  DD
  \end{itemize}
 \item[] \textit{Scleroglossum}\index{Scleroglossum@\textit{Scleroglossum}} 革舌蕨屬
                                
  \begin{itemize}
        \item[] \textit{S. sulcatum} (Mett. ex Kuhn) Alderw. \index{Scleroglossum@\textit{Scleroglossum}!sulcatum@\textit{sulcatum}} 革舌蕨 \index{革舌蕨}  NT
  \end{itemize}
 \item[] \textit{Selliguea}\index{Selliguea@\textit{Selliguea}} Selliguea屬
                                
  \begin{itemize}
        \item[] \textit{S. echinospora} (Tagawa) Fraser-Jenk. \index{Selliguea@\textit{Selliguea}!echinospora@\textit{echinospora}} 大葉玉山茀蕨 \index{大葉玉山茀蕨} \# LC
        \item[] \textit{S. engleri} (Luerss.) Fraser-Jenk. \index{Selliguea@\textit{Selliguea}!engleri@\textit{engleri}} 恩氏茀蕨 \index{恩氏茀蕨}  LC
        \item[] \textit{S. hastata} (Thunb.) Fraser-Jenk. \index{Selliguea@\textit{Selliguea}!hastata@\textit{hastata}} 三葉茀蕨 \index{三葉茀蕨}  LC
        \item[] \textit{S. okamotoi} (Tagawa) Ralf Knapp \index{Selliguea@\textit{Selliguea}!okamotoi@\textit{okamotoi}} 岡本氏茀蕨 \index{岡本氏茀蕨} \# DD
        \item[] \textit{S. taeniata} (Sw.) Parris \index{Selliguea@\textit{Selliguea}!taeniata@\textit{taeniata}} 掌葉茀蕨 \index{掌葉茀蕨}  VU
        \item[] \textit{S. taiwanensis} (Tagawa) H.Ohashi \& K.Ohashi \index{Selliguea@\textit{Selliguea}!taiwanensis@\textit{taiwanensis}} 臺灣茀蕨 \index{臺灣茀蕨} \# DD
        \item[] \textit{S. yakushimensis} (Makino) Fraser-Jenk. \index{Selliguea@\textit{Selliguea}!yakushimensis@\textit{yakushimensis}} 姬茀蕨 \index{姬茀蕨}  NT
  \end{itemize}
 \item[] \textit{Themelium}\index{Themelium@\textit{Themelium}} Themelium屬
                                
  \begin{itemize}
        \item[] \textit{T. curtisii} (Baker) Parris \index{Themelium@\textit{Themelium}!curtisii@\textit{curtisii}} 蒿蕨 \index{蒿蕨}  LC
        \item[] \textit{T. tenuisectum} (Blume) Parris \index{Themelium@\textit{Themelium}!tenuisectum@\textit{tenuisectum}} 細葉蒿蕨 \index{細葉蒿蕨}  VU
  \end{itemize}
 \item[] \textit{Tomophyllum}\index{Tomophyllum@\textit{Tomophyllum}} Tomophyllum屬
                                
  \begin{itemize}
        \item[] \textit{T. subfalcatum} (Blume) Parris \index{Tomophyllum@\textit{Tomophyllum}!subfalcatum@\textit{subfalcatum}} 虎尾蒿蕨 \index{虎尾蒿蕨}  NT
  \end{itemize}
 \item[] \textit{Tricholepidium}\index{Tricholepidium@\textit{Tricholepidium}} Tricholepidium屬
                                
  \begin{itemize}
        \item[] \textit{T. buergerianum} (Miq.) Fraser-Jenk. \index{Tricholepidium@\textit{Tricholepidium}!buergerianum@\textit{buergerianum}} 波氏星蕨 \index{波氏星蕨}  LC
  \end{itemize}
 \item[] \textit{Xiphopterella}\index{Xiphopterella@\textit{Xiphopterella}} Xiphopterella屬
                                
  \begin{itemize}
        \item[] \textit{X. devolii} S.J.Moore, Parris \& W.L.Chiou \index{Xiphopterella@\textit{Xiphopterella}!devolii@\textit{devolii}} 梳葉蕨 \index{梳葉蕨}  LC
  \end{itemize}
  \end{itemize}
