
  \begin{itemize}
 \item[] \textit{Anagallis} 琉璃繁縷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anagallis+arvensis}{\textit{A. arvensis} L.}  \index{Anagallis@\textit{Anagallis}!arvensis@\textit{arvensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉璃繁縷&T2_new_value=true&fr=y}}{琉璃繁縷}\index{琉璃繁縷} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anagallis+minima}{\textit{A. minima} (L.) E.H.L.Krause}  \index{Anagallis@\textit{Anagallis}!minima@\textit{minima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小海綠&T2_new_value=true&fr=y}}{小海綠}\index{小海綠} NA$^n$
  \end{itemize}
 \item[] \textit{Androsace} 點地梅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Androsace+umbellata}{\textit{A. umbellata} (Lour.) Merr.}  \index{Androsace@\textit{Androsace}!umbellata@\textit{umbellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=地錢草&T2_new_value=true&fr=y}}{地錢草}\index{地錢草} LC
  \end{itemize}
 \item[] \textit{Ardisia} 紫金牛屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+brevicaulis}{\textit{A. brevicaulis} Diels}  \index{Ardisia@\textit{Ardisia}!brevicaulis@\textit{brevicaulis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屯鹿紫金牛&T2_new_value=true&fr=y}}{屯鹿紫金牛}\index{屯鹿紫金牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+chinensis}{\textit{A. chinensis} Benth.}  \index{Ardisia@\textit{Ardisia}!chinensis@\textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華紫金牛&T2_new_value=true&fr=y}}{華紫金牛}\index{華紫金牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+cornudentata+subsp.+cornudentata}{\textit{A. cornudentata} Mez subsp. \textit{cornudentata}}  \index{Ardisia@\textit{Ardisia}!cornudentata@\textit{cornudentata}!subsp. cornudentata@subsp. \textit{cornudentata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雨傘仔&T2_new_value=true&fr=y}}{雨傘仔}\index{雨傘仔}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+cornudentata+subsp.+morrisonensis}{\textit{A. cornudentata} Mez subsp. \textit{morrisonensis} (Hayata) Yuen P.Yang}  \index{Ardisia@\textit{Ardisia}!cornudentata@\textit{cornudentata}!subsp. morrisonensis@subsp. \textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山紫金牛&T2_new_value=true&fr=y}}{玉山紫金牛}\index{玉山紫金牛}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+cornudentata+subsp.+morrisonensis+var.+stenosepala}{\textit{A. cornudentata} Mez subsp. \textit{morrisonensis} (Hayata) Yuen P.Yang var. \textit{stenosepala} (Hayata) Yuen P.Yang}  \index{Ardisia@\textit{Ardisia}!cornudentata@\textit{cornudentata}!subsp. morrisonensis var. stenosepala@subsp. \textit{morrisonensis} var. \textit{stenosepala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山紫金牛&T2_new_value=true&fr=y}}{阿里山紫金牛}\index{阿里山紫金牛}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+crenata}{\textit{A. crenata} Sims}  \index{Ardisia@\textit{Ardisia}!crenata@\textit{crenata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=珠砂根&T2_new_value=true&fr=y}}{珠砂根}\index{珠砂根} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+crispa}{\textit{A. crispa} (Thunb.) A.DC.}  \index{Ardisia@\textit{Ardisia}!crispa@\textit{crispa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=百兩金&T2_new_value=true&fr=y}}{百兩金}\index{百兩金} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+elliptica}{\textit{A. elliptica} Thunb.}  \index{Ardisia@\textit{Ardisia}!elliptica@\textit{elliptica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼紫金牛&T2_new_value=true&fr=y}}{蘭嶼紫金牛}\index{蘭嶼紫金牛} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+japonica}{\textit{A. japonica} (Hornsted) Blume}  \index{Ardisia@\textit{Ardisia}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紫金牛&T2_new_value=true&fr=y}}{紫金牛}\index{紫金牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+kusukusensis}{\textit{A. kusukusensis} Hayata}  \index{Ardisia@\textit{Ardisia}!kusukusensis@\textbf{\textit{kusukusensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高士佛紫金牛&T2_new_value=true&fr=y}}{高士佛紫金牛}\index{高士佛紫金牛@{\Song{高士佛紫金牛}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+maclurei}{\textit{A. maclurei} Merr.}  \index{Ardisia@\textit{Ardisia}!maclurei@\textbf{\textit{maclurei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=麥氏紫金牛&T2_new_value=true&fr=y}}{麥氏紫金牛}\index{麥氏紫金牛@{\Song{麥氏紫金牛}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+miaoliensis}{\textit{A. miaoliensis} S.Y.Lu}  \index{Ardisia@\textit{Ardisia}!miaoliensis@\textit{miaoliensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苗栗紫金牛&T2_new_value=true&fr=y}}{苗栗紫金牛}\index{苗栗紫金牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+pusilla}{\textit{A. pusilla} A.DC.}  \index{Ardisia@\textit{Ardisia}!pusilla@\textit{pusilla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=輪葉紫金牛&T2_new_value=true&fr=y}}{輪葉紫金牛}\index{輪葉紫金牛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+quinquegona}{\textit{A. quinquegona} Blume}  \index{Ardisia@\textit{Ardisia}!quinquegona@\textit{quinquegona}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉樹杞&T2_new_value=true&fr=y}}{小葉樹杞}\index{小葉樹杞} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+sieboldii}{\textit{A. sieboldii} Miq.}  \index{Ardisia@\textit{Ardisia}!sieboldii@\textit{sieboldii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樹杞&T2_new_value=true&fr=y}}{樹杞}\index{樹杞} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+squamulosa}{\textit{A. squamulosa} Presl}  \index{Ardisia@\textit{Ardisia}!squamulosa@\textit{squamulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=春不老&T2_new_value=true&fr=y}}{春不老}\index{春不老} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+villosa}{\textit{A. villosa} Roxb.}  \index{Ardisia@\textit{Ardisia}!villosa@\textbf{\textit{villosa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪下紅&T2_new_value=true&fr=y}}{雪下紅}\index{雪下紅@{\Song{雪下紅}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+violacea}{\textit{A. violacea} (T.Suzuki) W.Z.Fang \& K.Yao}  \index{Ardisia@\textit{Ardisia}!violacea@\textit{violacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裡菫紫金牛&T2_new_value=true&fr=y}}{裡菫紫金牛}\index{裡菫紫金牛}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ardisia+virens}{\textit{A. virens} Kurz}  \index{Ardisia@\textit{Ardisia}!virens@\textit{virens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑星紫金牛&T2_new_value=true&fr=y}}{黑星紫金牛}\index{黑星紫金牛} LC
  \end{itemize}
 \item[] \textit{Embelia} 藤木檞屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Embelia+laeta+var.+papilligera}{\textit{E. laeta} (L.) Mez var. \textit{papilligera} (Nakai) Walker}  \index{Embelia@\textit{Embelia}!laeta@\textit{laeta}!var. papilligera@var. \textit{papilligera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藤毛木檞&T2_new_value=true&fr=y}}{藤毛木檞}\index{藤毛木檞}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Embelia+lenticellata}{\textit{E. lenticellata} Hayata}  \index{Embelia@\textit{Embelia}!lenticellata@\textit{lenticellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賽山椒&T2_new_value=true&fr=y}}{賽山椒}\index{賽山椒}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Embelia+rudis}{\textit{E. rudis} Hand.-Mazz.}  \index{Embelia@\textit{Embelia}!rudis@\textit{rudis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=野山椒&T2_new_value=true&fr=y}}{野山椒}\index{野山椒} LC
  \end{itemize}
 \item[] \textit{Lysimachia} 珍珠菜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+ardisioides}{\textit{L. ardisioides} Masam.}  \index{Lysimachia@\textit{Lysimachia}!ardisioides@\textit{ardisioides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣排香&T2_new_value=true&fr=y}}{臺灣排香}\index{臺灣排香}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+candida}{\textit{L. candida} Lindl.}  \index{Lysimachia@\textit{Lysimachia}!candida@\textit{candida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=澤珍珠菜&T2_new_value=true&fr=y}}{澤珍珠菜}\index{澤珍珠菜} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+capillipes}{\textit{L. capillipes} Hemsl.}  \index{Lysimachia@\textit{Lysimachia}!capillipes@\textit{capillipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=排香草&T2_new_value=true&fr=y}}{排香草}\index{排香草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+chingshuiensis}{\textit{L. chingshuiensis} C.I Peng \& C.M.Hu}  \index{Lysimachia@\textit{Lysimachia}!chingshuiensis@\textbf{\textit{chingshuiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水山過路黃&T2_new_value=true&fr=y}}{清水山過路黃}\index{清水山過路黃@{\Song{清水山過路黃}}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+congestiflora}{\textit{L. congestiflora} Hemsl.}  \index{Lysimachia@\textit{Lysimachia}!congestiflora@\textit{congestiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣珍珠菜&T2_new_value=true&fr=y}}{臺灣珍珠菜}\index{臺灣珍珠菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+decurrens}{\textit{L. decurrens} G.Forst.}  \index{Lysimachia@\textit{Lysimachia}!decurrens@\textit{decurrens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=異葉珍珠菜&T2_new_value=true&fr=y}}{異葉珍珠菜}\index{異葉珍珠菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+fortunei}{\textit{L. fortunei} Maxim.}  \index{Lysimachia@\textit{Lysimachia}!fortunei@\textit{fortunei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=星宿菜&T2_new_value=true&fr=y}}{星宿菜}\index{星宿菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+japonica}{\textit{L. japonica} Thunb.}  \index{Lysimachia@\textit{Lysimachia}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小茄&T2_new_value=true&fr=y}}{小茄}\index{小茄} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+mauritiana}{\textit{L. mauritiana} Lam.}  \index{Lysimachia@\textit{Lysimachia}!mauritiana@\textit{mauritiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茅毛珍珠菜&T2_new_value=true&fr=y}}{茅毛珍珠菜}\index{茅毛珍珠菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+nigropunctata}{\textit{L. nigropunctata} Masam.}  \index{Lysimachia@\textit{Lysimachia}!nigropunctata@\textit{nigropunctata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑點珍珠菜&T2_new_value=true&fr=y}}{黑點珍珠菜}\index{黑點珍珠菜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lysimachia+remota}{\textit{L. remota} Petitm.}  \index{Lysimachia@\textit{Lysimachia}!remota@\textit{remota}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊珍珠菜&T2_new_value=true&fr=y}}{蓬萊珍珠菜}\index{蓬萊珍珠菜} LC
  \end{itemize}
 \item[] \textit{Maesa} 山桂花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maesa+japonica}{\textit{M. japonica} (Thunb.) Moritzi ex Zoll.}  \index{Maesa@\textit{Maesa}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山桂花&T2_new_value=true&fr=y}}{山桂花}\index{山桂花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maesa+lanyuensis}{\textit{M. lanyuensis} Yuen P.Yang}  \index{Maesa@\textit{Maesa}!lanyuensis@\textit{lanyuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼山桂花&T2_new_value=true&fr=y}}{蘭嶼山桂花}\index{蘭嶼山桂花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maesa+perlaria+var.+formosana}{\textit{M. perlaria} (Lour.) Merr. var. \textit{formosana} (Mez) Yuen P.Yang}  \index{Maesa@\textit{Maesa}!perlaria@\textit{perlaria}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山桂花&T2_new_value=true&fr=y}}{臺灣山桂花}\index{臺灣山桂花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maesa+perlaria+var.+perlaria}{\textit{M. perlaria} (Lour.) Merr. var. \textit{perlaria}}  \index{Maesa@\textit{Maesa}!perlaria@\textit{perlaria}!var. perlaria@var. \textit{perlaria}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鯽魚膽&T2_new_value=true&fr=y}}{鯽魚膽}\index{鯽魚膽} DD
  \end{itemize}
 \item[] \textit{Myrsine} 竹杞屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Myrsine+africana}{\textit{M. africana} L.}  \index{Myrsine@\textit{Myrsine}!africana@\textit{africana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉鐵仔&T2_new_value=true&fr=y}}{小葉鐵仔}\index{小葉鐵仔} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Myrsine+seguinii}{\textit{M. seguinii} H.Lév.}  \index{Myrsine@\textit{Myrsine}!seguinii@\textit{seguinii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大明橘&T2_new_value=true&fr=y}}{大明橘}\index{大明橘} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Myrsine+stolonifera}{\textit{M. stolonifera} (Koidz.) Walker}  \index{Myrsine@\textit{Myrsine}!stolonifera@\textit{stolonifera}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓竹杞&T2_new_value=true&fr=y}}{蔓竹杞}\index{蔓竹杞} LC
  \end{itemize}
 \item[] \textit{Primula} 櫻草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Primula+miyabeana}{\textit{P. miyabeana} T.Itô \& Kawak.}  \index{Primula@\textit{Primula}!miyabeana@\textit{miyabeana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山櫻草&T2_new_value=true&fr=y}}{玉山櫻草}\index{玉山櫻草}\# LC
  \end{itemize}
 \item[] \textit{Stimpsonia} 施丁草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stimpsonia+chamaedryoides}{\textit{S. chamaedryoides} C.Wright ex A.Gray}  \index{Stimpsonia@\textit{Stimpsonia}!chamaedryoides@\textbf{\textit{chamaedryoides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=施丁草&T2_new_value=true&fr=y}}{施丁草}\index{施丁草@{\Song{施丁草}}} EN
  \end{itemize}
  \end{itemize}
