
  \begin{itemize}
 \item[] \textit{Acrostichum} 鹵蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acrostichum+aureum}{\textit{A. aureum} L.}  \index{Acrostichum@\textit{Acrostichum}!aureum@\textit{aureum}} 鹵蕨\index{鹵蕨} VU
  \end{itemize}
 \item[] \textit{Adiantum} 鐵線蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+capillus-junonis}{\textit{A. capillus-junonis} Rupr.}  \index{Adiantum@\textit{Adiantum}!capillus-junonis@\textit{capillus-junonis}} 團羽鐵線蕨\index{團羽鐵線蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+capillus-veneris}{\textit{A. capillus-veneris} L.}  \index{Adiantum@\textit{Adiantum}!capillus-veneris@\textit{capillus-veneris}} 鐵線蕨\index{鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+capillus-veneris+ f. +lanyuanum}{\textit{A. capillus-veneris} L.  f.  \textit{lanyuanum} W.C.Shieh}  \index{Adiantum@\textit{Adiantum}!capillus-veneris@\textit{capillus-veneris}!f. lanyuanum@f. \textit{lanyuanum}} 蘭嶼鐵線蕨\index{蘭嶼鐵線蕨}\# NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+caudatum}{\textit{A. caudatum} L.}  \index{Adiantum@\textit{Adiantum}!caudatum@\textit{caudatum}} 鞭葉鐵線蕨\index{鞭葉鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+ciliatum}{\textit{A. ciliatum} Blume}  \index{Adiantum@\textit{Adiantum}!ciliatum@\textit{ciliatum}}  \index{Adiantum@\textit{Adiantum}!malesianum@\textit{malesianum}{\\\noindent(= \textit{Adiantum ciliatum})}} 馬來鐵線蕨\index{馬來鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+diaphanum}{\textit{A. diaphanum} Blume}  \index{Adiantum@\textit{Adiantum}!diaphanum@\textit{diaphanum}} 長尾鐵線蕨\index{長尾鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+edgeworthii}{\textit{A. edgeworthii} Hook.}  \index{Adiantum@\textit{Adiantum}!edgeworthii@\textit{edgeworthii}} 愛氏鐵線蕨\index{愛氏鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+flabellulatum}{\textit{A. flabellulatum} L.}  \index{Adiantum@\textit{Adiantum}!flabellulatum@\textit{flabellulatum}} 扇葉鐵線蕨\index{扇葉鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+formosanum}{\textit{A. formosanum} Tagawa}  \index{Adiantum@\textit{Adiantum}!formosanum@\textit{formosanum}} 深山鐵線蕨\index{深山鐵線蕨}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+hispidulum}{\textit{A. hispidulum} Sw.}  \index{Adiantum@\textit{Adiantum}!hispidulum@\textit{hispidulum}} 毛葉鐵線蕨\index{毛葉鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+meishanianum}{\textit{A. meishanianum} F.S.Hsu ex Yea C.Liu \& W.L.Chiou}  \index{Adiantum@\textit{Adiantum}!meishanianum@\textit{meishanianum}} 梅山口鐵線蕨\index{梅山口鐵線蕨}\# NA$^h$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+menglianense}{\textit{A. menglianense} Y.Y.Qian}  \index{Adiantum@\textit{Adiantum}!menglianense@\textit{menglianense}} 孟連鐵線蕨\index{孟連鐵線蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+monochlamys}{\textit{A. monochlamys} Eaton}  \index{Adiantum@\textit{Adiantum}!monochlamys@\textit{monochlamys}} 石長生\index{石長生} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+myriosorum}{\textit{A. myriosorum} Baker}  \index{Adiantum@\textit{Adiantum}!myriosorum@\textit{myriosorum}} 灰背鐵線蕨\index{灰背鐵線蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+philippense}{\textit{A. philippense} L.}  \index{Adiantum@\textit{Adiantum}!philippense@\textit{philippense}} 半月鐵線蕨\index{半月鐵線蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+roborowskii+var.+taiwanianum}{\textit{A. roborowskii} Maxim. var. \textit{taiwanianum} (Tagawa) W.C.Shieh}  \index{Adiantum@\textit{Adiantum}!roborowskii@\textit{roborowskii}!var. taiwanianum@var. \textit{taiwanianum}} 臺灣高山鐵線蕨\index{臺灣高山鐵線蕨}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Adiantum+soboliferum}{\textit{A. soboliferum} Wall. ex Hook.}  \index{Adiantum@\textit{Adiantum}!soboliferum@\textit{soboliferum}} 翅柄鐵線蕨\index{翅柄鐵線蕨} VU
  \end{itemize}
 \item[] \textit{Anogramma} 翠蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anogramma+leptophylla}{\textit{A. leptophylla} (L.) Link}  \index{Anogramma@\textit{Anogramma}!leptophylla@\textit{leptophylla}} 翠蕨\index{翠蕨} NT
  \end{itemize}
 \item[] \textit{Antrophyum} 車前蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+castaneum}{\textit{A. castaneum} H.Ito}  \index{Antrophyum@\textit{Antrophyum}!castaneum@\textit{castaneum}} 阿里山車前蕨\index{阿里山車前蕨}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+formosanum}{\textit{A. formosanum} Hieron.}  \index{Antrophyum@\textit{Antrophyum}!formosanum@\textit{formosanum}} 臺灣車前蕨\index{臺灣車前蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+henryi}{\textit{A. henryi} Hieron.}  \index{Antrophyum@\textit{Antrophyum}!henryi@\textit{henryi}} 亨利氏車前蕨\index{亨利氏車前蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+obovatum}{\textit{A. obovatum} Baker}  \index{Antrophyum@\textit{Antrophyum}!obovatum@\textit{obovatum}} 車前蕨\index{車前蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+parvulum}{\textit{A. parvulum} Blume}  \index{Antrophyum@\textit{Antrophyum}!parvulum@\textit{parvulum}} 無柄車前蕨\index{無柄車前蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Antrophyum+sessilifolium}{\textit{A. sessilifolium} (Cav.) Spreng.}  \index{Antrophyum@\textit{Antrophyum}!sessilifolium@\textit{sessilifolium}} 蘭嶼車前蕨\index{蘭嶼車前蕨} NT
  \end{itemize}
 \item[] \textit{Ceratopteris} 水蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ceratopteris+gaudichaudii+var.+vulgaris}{\textit{C. gaudichaudii} Brongn. var. \textit{vulgaris} Masuyama \& Watano}  \index{Ceratopteris@\textit{Ceratopteris}!gaudichaudii@\textit{gaudichaudii}!var. vulgaris@var. \textit{vulgaris}} 姬水蕨\index{姬水蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ceratopteris+thalictroides}{\textit{C. thalictroides} (L.) Brongn.}  \index{Ceratopteris@\textit{Ceratopteris}!thalictroides@\textit{thalictroides}} 水蕨\index{水蕨} LC
  \end{itemize}
 \item[] \textit{Cheilanthes} 碎米蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+argentea}{\textit{C. argentea} (S.G.Gmel.) Kunze}  \index{Cheilanthes@\textit{Cheilanthes}!argentea@\textit{argentea}} 長柄粉背蕨\index{長柄粉背蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+chusana}{\textit{C. chusana} Hook.}  \index{Cheilanthes@\textit{Cheilanthes}!chusana@\textit{chusana}} 細葉碎米蕨\index{細葉碎米蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+formosana}{\textit{C. formosana} Hayata}  \index{Cheilanthes@\textit{Cheilanthes}!formosana@\textit{formosana}}  \index{Cheilanthes@\textit{Cheilanthes}!dealbata@\textit{dealbata}{\\\noindent(= \textit{Cheilanthes formosana})}}   \index{Cheilanthes@\textit{Cheilanthes}!farinosa@\textit{farinosa}{\\\noindent(= \textit{Cheilanthes formosana})}} 深山粉背蕨(臺灣粉背蕨) \index{深山粉背蕨} \index{臺灣粉背蕨@{臺灣粉背蕨(=深山粉背蕨)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+hirsuta}{\textit{C. hirsuta} (Poir.) Mett.}  \index{Cheilanthes@\textit{Cheilanthes}!hirsuta@\textit{hirsuta}} 毛碎米蕨\index{毛碎米蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+mexicana}{\textit{C. mexicana} Fee}  \index{Cheilanthes@\textit{Cheilanthes}!mexicana@\textit{mexicana}} 粉背蕨\index{粉背蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+subargentea}{\textit{C. subargentea} (Ching) C.M.Kuo}  \index{Cheilanthes@\textit{Cheilanthes}!subargentea@\textit{subargentea}} 擬長柄粉背蕨\index{擬長柄粉背蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cheilanthes+tenuifolia}{\textit{C. tenuifolia} (Burm.f.) Sw.}  \index{Cheilanthes@\textit{Cheilanthes}!tenuifolia@\textit{tenuifolia}} 薄葉碎米蕨\index{薄葉碎米蕨} LC
  \end{itemize}
 \item[] \textit{Coniogramme} 鳳了蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coniogramme+fraxinea}{\textit{C. fraxinea} (D.Don) Diels}  \index{Coniogramme@\textit{Coniogramme}!fraxinea@\textit{fraxinea}} 全緣鳳了蕨\index{全緣鳳了蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coniogramme+intermedia}{\textit{C. intermedia} Heiron.}  \index{Coniogramme@\textit{Coniogramme}!intermedia@\textit{intermedia}} 華鳳了蕨\index{華鳳了蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coniogramme+japonica}{\textit{C. japonica} (Thunb.) Diels}  \index{Coniogramme@\textit{Coniogramme}!japonica@\textit{japonica}} 日本鳳了蕨\index{日本鳳了蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coniogramme+procera}{\textit{C. procera} Fée}  \index{Coniogramme@\textit{Coniogramme}!procera@\textit{procera}} 高山鳳了蕨\index{高山鳳了蕨} LC
  \end{itemize}
 \item[] \textit{Cryptogramma} 珠蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptogramma+brunoniana}{\textit{C. brunoniana} Wall. ex Hook. \& Grev.}  \index{Cryptogramma@\textit{Cryptogramma}!brunoniana@\textit{brunoniana}} 高山珠蕨\index{高山珠蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cryptogramma+stelleri}{\textit{C. stelleri} (S.G.Gmel.) Prantl}  \index{Cryptogramma@\textit{Cryptogramma}!stelleri@\textit{stelleri}} 疏葉珠蕨\index{疏葉珠蕨} NT
  \end{itemize}
 \item[] \textit{Doryopteris} 黑心蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Doryopteris+concolor}{\textit{D. concolor} (Langsd. \& Fisch.) Kuhn}  \index{Doryopteris@\textit{Doryopteris}!concolor@\textit{concolor}} 黑心蕨\index{黑心蕨} LC
  \end{itemize}
 \item[] \textit{Haplopteris} 書帶蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+anguste-elongata}{\textit{H. anguste-elongata} (Hayata) E.H.Crane}  \index{Haplopteris@\textit{Haplopteris}!anguste-elongata@\textit{anguste-elongata}}  \index{Vittaria@\textit{Vittaria}!anguste-elongata@\textit{anguste-elongata}{\\\noindent(= \textit{Haplopteris anguste-elongata})}} 姬書帶蕨\index{姬書帶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+elongata}{\textit{H. elongata} (Sw.) E.H.Crane}  \index{Haplopteris@\textit{Haplopteris}!elongata@\textit{elongata}}  \index{Vittaria@\textit{Vittaria}!zosterifolia@\textit{zosterifolia}{\\\noindent(= \textit{Haplopteris elongata})}} 垂葉書帶蕨\index{垂葉書帶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+flexuosa}{\textit{H. flexuosa} (Fée) E.H.Crane}  \index{Haplopteris@\textit{Haplopteris}!flexuosa@\textit{flexuosa}}  \index{Vittaria@\textit{Vittaria}!flexuosa@\textit{flexuosa}{\\\noindent(= \textit{Haplopteris flexuosa})}} 書帶蕨\index{書帶蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+heterophylla}{\textit{H. heterophylla} C.W.Chen, Y.H.Chang \& Yea C.Liu}  \index{Haplopteris@\textit{Haplopteris}!heterophylla@\textit{heterophylla}} 異葉書帶蕨\index{異葉書帶蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+mediosora}{\textit{H. mediosora} (Hayata) X.C.Zhang}  \index{Haplopteris@\textit{Haplopteris}!mediosora@\textit{mediosora}} 細葉書帶蕨\index{細葉書帶蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Haplopteris+taeniophylla}{\textit{H. taeniophylla} (Copel.) E.H.Crane}  \index{Haplopteris@\textit{Haplopteris}!taeniophylla@\textit{taeniophylla}}  \index{Vittaria@\textit{Vittaria}!taeniophylla@\textit{taeniophylla}{\\\noindent(= \textit{Haplopteris taeniophylla})}} 廣葉書帶蕨\index{廣葉書帶蕨} LC
  \end{itemize}
 \item[] \textit{Mildella} 擬旱蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mildella+henryi}{\textit{M. henryi} (Christ) C.C.Hall \& Lellinger}  \index{Mildella@\textit{Mildella}!henryi@\textit{henryi}} 亨氏擬旱蕨\index{亨氏擬旱蕨} LC
  \end{itemize}
 \item[] \textit{Onychium} 金粉蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Onychium+japonicum}{\textit{O. japonicum} (Thunb.) Kunze}  \index{Onychium@\textit{Onychium}!japonicum@\textit{japonicum}} 日本金粉蕨\index{日本金粉蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Onychium+lucidum}{\textit{O. lucidum} (D.Don) Spreng.}  \index{Onychium@\textit{Onychium}!lucidum@\textit{lucidum}}  \index{Onychium@\textit{Onychium}!contiguum@\textit{contiguum}{\\\noindent(= \textit{Onychium lucidum})}} 高山金粉蕨\index{高山金粉蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Onychium+siliculosum}{\textit{O. siliculosum} (Desv.) C.Chr.}  \index{Onychium@\textit{Onychium}!siliculosum@\textit{siliculosum}} 金粉蕨\index{金粉蕨} NT
  \end{itemize}
 \item[] \textit{Paragymnopteris} 金毛裸蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paragymnopteris+vestita}{\textit{P. vestita} (Wall. ex C.Presl) K.H.Shing}  \index{Paragymnopteris@\textit{Paragymnopteris}!vestita@\textit{vestita}} 金毛裸蕨\index{金毛裸蕨} EN
  \end{itemize}
 \item[] \textit{Parahemionitis} 擬澤瀉蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parahemionitis+arifolia}{\textit{P. arifolia} (Burm.f.) Panigrahi}  \index{Parahemionitis@\textit{Parahemionitis}!arifolia@\textit{arifolia}} 澤瀉蕨\index{澤瀉蕨} VU
  \end{itemize}
 \item[] \textit{Pityrogramma} 粉葉蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pityrogramma+calomelanos}{\textit{P. calomelanos} (L.) Link}  \index{Pityrogramma@\textit{Pityrogramma}!calomelanos@\textit{calomelanos}} 粉葉蕨\index{粉葉蕨} NA$^n$
  \end{itemize}
 \item[] \textit{Pteris} 鳳尾蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+alata}{\textit{P. alata} Lam.}  \index{Pteris@\textit{Pteris}!alata@\textit{alata}} 半邊羽裂鳳尾蕨\index{半邊羽裂鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+amoena}{\textit{P. amoena} Blume}  \index{Pteris@\textit{Pteris}!amoena@\textit{amoena}}  \index{Pteris@\textit{Pteris}!tokioi@\textit{tokioi}{\\\noindent(= \textit{Pteris amoena})}} 鈴木氏鳳尾蕨\index{鈴木氏鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+angustipinna}{\textit{P. angustipinna} Tagawa}  \index{Pteris@\textit{Pteris}!angustipinna@\textit{angustipinna}} 細葉鳳尾蕨\index{細葉鳳尾蕨}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+arisanensis}{\textit{P. arisanensis} Tagawa}  \index{Pteris@\textit{Pteris}!arisanensis@\textit{arisanensis}}  \index{Pteris@\textit{Pteris}!linearis@\textit{linearis}{\\\noindent(= \textit{Pteris arisanensis})}} 阿里山鳳尾蕨(三角脈鳳尾蕨) \index{阿里山鳳尾蕨} \index{三角脈鳳尾蕨@{三角脈鳳尾蕨(=阿里山鳳尾蕨)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+aspericaulis}{\textit{P. aspericaulis} Wall. ex J.Agardh}  \index{Pteris@\textit{Pteris}!aspericaulis@\textit{aspericaulis}}  \index{Pteris@\textit{Pteris}!scabristipes@\textit{scabristipes}{\\\noindent(= \textit{Pteris aspericaulis})}} 紅柄鳳尾蕨\index{紅柄鳳尾蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+bella}{\textit{P. bella} Tagawa}  \index{Pteris@\textit{Pteris}!bella@\textit{bella}} 長柄鳳尾蕨\index{長柄鳳尾蕨}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+biaurita}{\textit{P. biaurita} L.}  \index{Pteris@\textit{Pteris}!biaurita@\textit{biaurita}} 弧脈鳳尾蕨\index{弧脈鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+cadieri}{\textit{P. cadieri} H.Christ}  \index{Pteris@\textit{Pteris}!cadieri@\textit{cadieri}}  \index{Pteris@\textit{Pteris}!plumbea@\textit{plumbea}{\\\noindent(= \textit{Pteris cadieri})}} 卡氏鳳尾蕨(廣東鳳尾蕨) \index{卡氏鳳尾蕨} \index{廣東鳳尾蕨@{廣東鳳尾蕨(=卡氏鳳尾蕨)}} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+cretica+subsp.+cretica}{\textit{P. cretica} L. subsp. \textit{cretica}}  \index{Pteris@\textit{Pteris}!cretica@\textit{cretica}!subsp. cretica@subsp. \textit{cretica}} 大葉鳳尾蕨\index{大葉鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+cretica+subsp.+laeta}{\textit{P. cretica} L. subsp. \textit{laeta} (Wall. ex Ettingsh.) Fraser-Jenk.}  \index{Pteris@\textit{Pteris}!cretica@\textit{cretica}!subsp. laeta@subsp. \textit{laeta}} 粗糙鳳尾蕨\index{粗糙鳳尾蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+dactylina}{\textit{P. dactylina} Hook.}  \index{Pteris@\textit{Pteris}!dactylina@\textit{dactylina}} 掌鳳尾蕨\index{掌鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+deltodon}{\textit{P. deltodon} Baker}  \index{Pteris@\textit{Pteris}!deltodon@\textit{deltodon}} 岩鳳尾蕨\index{岩鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+dimorpha+var.+dimorpha}{\textit{P. dimorpha} Copel. var. \textit{dimorpha}}  \index{Pteris@\textit{Pteris}!dimorpha@\textit{dimorpha}!var. dimorpha@var. \textit{dimorpha}} 二形鳳尾蕨\index{二形鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+dimorpha+var.+metagrevilleana}{\textit{P. dimorpha} Copel. var. \textit{metagrevilleana} Y.S.Chao, H.Y.Liu \& W.L.Chiou}  \index{Pteris@\textit{Pteris}!dimorpha@\textit{dimorpha}!var. metagrevilleana@var. \textit{metagrevilleana}} 擬翅柄鳳尾蕨\index{擬翅柄鳳尾蕨} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+dimorpha+var.+prolongata}{\textit{P. dimorpha} Copel. var. \textit{prolongata} Y.S.Chao, H.Y.Liu \& W.L.Chiou}  \index{Pteris@\textit{Pteris}!dimorpha@\textit{dimorpha}!var. prolongata@var. \textit{prolongata}} 尾葉鳳尾蕨\index{尾葉鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+ensiformis}{\textit{P. ensiformis} Burm.}  \index{Pteris@\textit{Pteris}!ensiformis@\textit{ensiformis}} 箭葉鳳尾蕨\index{箭葉鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+fauriei}{\textit{P. fauriei} Hieron.}  \index{Pteris@\textit{Pteris}!fauriei@\textit{fauriei}} 傅氏鳳尾蕨\index{傅氏鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+formosana}{\textit{P. formosana} Baker}  \index{Pteris@\textit{Pteris}!formosana@\textit{formosana}} 臺灣鳳尾蕨\index{臺灣鳳尾蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+grevilleana+var.+grevilleana}{\textit{P. grevilleana} Wall. ex J.Agardh var. \textit{grevilleana}}  \index{Pteris@\textit{Pteris}!grevilleana@\textit{grevilleana}!var. grevilleana@var. \textit{grevilleana}} 翅柄鳳尾蕨\index{翅柄鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+grevilleana+var.+ornata}{\textit{P. grevilleana} Wall. ex J.Agardh var. \textit{ornata} Alderw.}  \index{Pteris@\textit{Pteris}!grevilleana@\textit{grevilleana}!var. ornata@var. \textit{ornata}} 白斑翅柄鳳尾蕨\index{白斑翅柄鳳尾蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+incurvata}{\textit{P. incurvata} Y.S.Chao, H.Y.Liu \& W.L.Chiou}  \index{Pteris@\textit{Pteris}!incurvata@\textit{incurvata}} 彎羽鳳尾蕨\index{彎羽鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+kawabatae}{\textit{P. kawabatae} Sa.Kurata}  \index{Pteris@\textit{Pteris}!kawabatae@\textit{kawabatae}} 無柄鳳尾蕨\index{無柄鳳尾蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+kidoi}{\textit{P. kidoi} Sa.Kurata}  \index{Pteris@\textit{Pteris}!kidoi@\textit{kidoi}} 城戶氏鳳尾蕨\index{城戶氏鳳尾蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+latipinna}{\textit{P. latipinna} Y.S.Chao \& W.L.Chiou}  \index{Pteris@\textit{Pteris}!latipinna@\textit{latipinna}} 寬羽鳳尾蕨\index{寬羽鳳尾蕨} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+longipes}{\textit{P. longipes} D.Don}  \index{Pteris@\textit{Pteris}!longipes@\textit{longipes}} 蓬萊鳳尾蕨\index{蓬萊鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+longipinna}{\textit{P. longipinna} Hayata}  \index{Pteris@\textit{Pteris}!longipinna@\textit{longipinna}} 長葉鳳尾蕨\index{長葉鳳尾蕨}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+multifida}{\textit{P. multifida} Poir.}  \index{Pteris@\textit{Pteris}!multifida@\textit{multifida}} 鳳尾蕨\index{鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+nipponica}{\textit{P. nipponica} W.C.Shieh}  \index{Pteris@\textit{Pteris}!nipponica@\textit{nipponica}} 日本鳳尾蕨\index{日本鳳尾蕨} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+pellucida}{\textit{P. pellucida} C.Presl}  \index{Pteris@\textit{Pteris}!pellucida@\textit{pellucida}}  \index{Pteris@\textit{Pteris}!venusta@\textit{venusta}{\\\noindent(= \textit{Pteris pellucida})}} 爪哇鳳尾蕨\index{爪哇鳳尾蕨} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+pellucidifolia}{\textit{P. pellucidifolia} Hayata}  \index{Pteris@\textit{Pteris}!pellucidifolia@\textit{pellucidifolia}} 闊葉鳳尾蕨\index{闊葉鳳尾蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+perplexa}{\textit{P. perplexa} Y.S.Chao, H.Y.Liu \& W.L.Chiou}  \index{Pteris@\textit{Pteris}!perplexa@\textit{perplexa}} 變葉鳳尾蕨\index{變葉鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+ryukyuensis}{\textit{P. ryukyuensis} Tagawa}  \index{Pteris@\textit{Pteris}!ryukyuensis@\textit{ryukyuensis}} 琉球鳳尾蕨\index{琉球鳳尾蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+semipinnata}{\textit{P. semipinnata} L.}  \index{Pteris@\textit{Pteris}!semipinnata@\textit{semipinnata}}  \index{Pteris@\textit{Pteris}!dispar@\textit{dispar}{\\\noindent(= \textit{Pteris semipinnata})}} 天草鳳尾蕨\index{天草鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+setulosocostulata}{\textit{P. setulosocostulata} Hayata}  \index{Pteris@\textit{Pteris}!setulosocostulata@\textit{setulosocostulata}} 有刺鳳尾蕨\index{有刺鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+terminalis}{\textit{P. terminalis} Wall. ex J.Agardh}  \index{Pteris@\textit{Pteris}!terminalis@\textit{terminalis}}  \index{Pteris@\textit{Pteris}!excelsa@\textit{excelsa}{\\\noindent(= \textit{Pteris terminalis})}} 溪鳳尾蕨\index{溪鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+tripartita}{\textit{P. tripartita} Sw.}  \index{Pteris@\textit{Pteris}!tripartita@\textit{tripartita}} 三腳鳳尾蕨\index{三腳鳳尾蕨} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+vittata}{\textit{P. vittata} L.}  \index{Pteris@\textit{Pteris}!vittata@\textit{vittata}} 鱗蓋鳳尾蕨\index{鱗蓋鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+wallichiana}{\textit{P. wallichiana} J.Agardh}  \index{Pteris@\textit{Pteris}!wallichiana@\textit{wallichiana}} 瓦氏鳳尾蕨\index{瓦氏鳳尾蕨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pteris+wulaiensis}{\textit{P. wulaiensis} C.M.Kuo}  \index{Pteris@\textit{Pteris}!wulaiensis@\textit{wulaiensis}} 烏來鳳尾蕨\index{烏來鳳尾蕨}\# CR
  \end{itemize}
 \item[] \textit{Vaginularia} 針葉蕨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaginularia+junghuhnii}{\textit{V. junghuhnii} Mett.}  \index{Vaginularia@\textit{Vaginularia}!junghuhnii@\textit{junghuhnii}}  \index{Vaginularia@\textit{Vaginularia}!paradoxa@\textit{paradoxa}{\\\noindent(= \textit{Vaginularia junghuhnii})}} 連孢一條線蕨\index{連孢一條線蕨} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vaginularia+trichoidea}{\textit{V. trichoidea} Fée}  \index{Vaginularia@\textit{Vaginularia}!trichoidea@\textit{trichoidea}} 一條線蕨\index{一條線蕨} CR
  \end{itemize}
  \end{itemize}
