
  \begin{itemize}
 \item[] \textit{Aconitum} 烏頭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aconitum+fukutomei+var.+formosanum}{\textit{A. fukutomei} Hayata var. \textit{formosanum} (Tamura) T.Y.A.Yang \& T.C.Huang}  \index{Aconitum@\textit{Aconitum}!fukutomei@\textit{fukutomei}!var. formosanum@\textbf{var. \textit{formosanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓烏頭&T2_new_value=true&fr=y}}{蔓烏頭}\index{蔓烏頭@{\Song{蔓烏頭}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aconitum+fukutomei+var.+fukutomei}{\textit{A. fukutomei} Hayata var. \textit{fukutomei}}  \index{Aconitum@\textit{Aconitum}!fukutomei@\textit{fukutomei}!var. fukutomei@var. \textit{fukutomei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣烏頭&T2_new_value=true&fr=y}}{臺灣烏頭}\index{臺灣烏頭}\# NT
  \end{itemize}
 \item[] \textit{Anemone} 銀蓮花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anemone+stolonifera}{\textit{A. stolonifera} Maxim.}  \index{Anemone@\textit{Anemone}!stolonifera@\textbf{\textit{stolonifera}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匍枝銀蓮花&T2_new_value=true&fr=y}}{匍枝銀蓮花}\index{匍枝銀蓮花@{\Song{匍枝銀蓮花}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Anemone+vitifolia}{\textit{A. vitifolia} Buch.-Ham. ex DC.}  \index{Anemone@\textit{Anemone}!vitifolia@\textit{vitifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小白頭翁&T2_new_value=true&fr=y}}{小白頭翁}\index{小白頭翁} LC
  \end{itemize}
 \item[] \textit{Calathodes} 雞爪草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Calathodes+polycarpa}{\textit{C. polycarpa} Ohwi}  \index{Calathodes@\textit{Calathodes}!polycarpa@\textbf{\textit{polycarpa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=多果雞爪草&T2_new_value=true&fr=y}}{多果雞爪草}\index{多果雞爪草@{\Song{多果雞爪草}}} EN
  \end{itemize}
 \item[] \textit{Cimicifuga} 升麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cimicifuga+simplex}{\textit{C. simplex} (DC.) Wormsk. ex Turcz.}  \index{Cimicifuga@\textit{Cimicifuga}!simplex@\textit{simplex}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=單穗升麻&T2_new_value=true&fr=y}}{單穗升麻}\index{單穗升麻}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cimicifuga+taiwanensis}{\textit{C. taiwanensis} (J.Compton, Hedd. \& T.Y.A.Yang) Luferov}  \index{Cimicifuga@\textit{Cimicifuga}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣升麻&T2_new_value=true&fr=y}}{臺灣升麻}\index{臺灣升麻} NT
  \end{itemize}
 \item[] \textit{Clematis} 鐵線蓮屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+akoensis}{\textit{C. akoensis} Hayata}  \index{Clematis@\textit{Clematis}!akoensis@\textit{akoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東鐵線蓮&T2_new_value=true&fr=y}}{屏東鐵線蓮}\index{屏東鐵線蓮}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+chinensis+var.+chinensis}{\textit{C. chinensis} Osbeck var. \textit{chinensis}}  \index{Clematis@\textit{Clematis}!chinensis@\textit{chinensis}!var. chinensis@var. \textit{chinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=威靈仙&T2_new_value=true&fr=y}}{威靈仙}\index{威靈仙} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+chinensis+var.+tatushanensis}{\textit{C. chinensis} Osbeck var. \textit{tatushanensis} T.Y.A.Yang}  \index{Clematis@\textit{Clematis}!chinensis@\textit{chinensis}!var. tatushanensis@var. \textit{tatushanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大肚山威靈仙&T2_new_value=true&fr=y}}{大肚山威靈仙}\index{大肚山威靈仙} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+crassifolia}{\textit{C. crassifolia} Benth.}  \index{Clematis@\textit{Clematis}!crassifolia@\textit{crassifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉鐵線蓮&T2_new_value=true&fr=y}}{厚葉鐵線蓮}\index{厚葉鐵線蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+formosana}{\textit{C. formosana} Kuntze}  \index{Clematis@\textit{Clematis}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鐵線蓮&T2_new_value=true&fr=y}}{臺灣鐵線蓮}\index{臺灣鐵線蓮}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+gouriana+subsp.+lishanensis}{\textit{C. gouriana} Roxb. ex DC. subsp. \textit{lishanensis} T.Y.A.Yang \& T.C.Huang}  \index{Clematis@\textit{Clematis}!gouriana@\textit{gouriana}!subsp. lishanensis@subsp. \textit{lishanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梨山小蓑衣藤&T2_new_value=true&fr=y}}{梨山小蓑衣藤}\index{梨山小蓑衣藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+grata}{\textit{C. grata} Wall.}  \index{Clematis@\textit{Clematis}!grata@\textit{grata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=串鼻龍&T2_new_value=true&fr=y}}{串鼻龍}\index{串鼻龍} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+henryi+var.+henryi}{\textit{C. henryi} Oliv. var. \textit{henryi}}  \index{Clematis@\textit{Clematis}!henryi@\textit{henryi}!var. henryi@var. \textit{henryi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亨利氏鐵線蓮&T2_new_value=true&fr=y}}{亨利氏鐵線蓮}\index{亨利氏鐵線蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+henryi+var.+morii}{\textit{C. henryi} Oliv. var. \textit{morii} (Hayata) T.Y.A.Yang \& T.C.Huang}  \index{Clematis@\textit{Clematis}!henryi@\textit{henryi}!var. morii@var. \textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏鐵線蓮&T2_new_value=true&fr=y}}{森氏鐵線蓮}\index{森氏鐵線蓮}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+lasiandra}{\textit{C. lasiandra} Maxim.}  \index{Clematis@\textit{Clematis}!lasiandra@\textit{lasiandra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小木通&T2_new_value=true&fr=y}}{小木通}\index{小木通} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+leschenaultiana}{\textit{C. leschenaultiana} DC.}  \index{Clematis@\textit{Clematis}!leschenaultiana@\textit{leschenaultiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=銹毛鐵線蓮&T2_new_value=true&fr=y}}{銹毛鐵線蓮}\index{銹毛鐵線蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+meyeniana}{\textit{C. meyeniana} Walp.}  \index{Clematis@\textit{Clematis}!meyeniana@\textit{meyeniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=麥氏鐵線蓮&T2_new_value=true&fr=y}}{麥氏鐵線蓮}\index{麥氏鐵線蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+montana}{\textit{C. montana} Buch.-Ham. ex DC.}  \index{Clematis@\textit{Clematis}!montana@\textit{montana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繡球藤&T2_new_value=true&fr=y}}{繡球藤}\index{繡球藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+parviloba+subsp.+bartlettii}{\textit{C. parviloba} Gard. ex Champ. subsp. \textit{bartlettii} (Yamam.) T.Y.A.Yang \& T.C.Huang}  \index{Clematis@\textit{Clematis}!parviloba@\textit{parviloba}!subsp. bartlettii@subsp. \textit{bartlettii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巴氏鐵線蓮&T2_new_value=true&fr=y}}{巴氏鐵線蓮}\index{巴氏鐵線蓮}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+pseudootophora}{\textit{C. pseudootophora} M.Y.Fang}  \index{Clematis@\textit{Clematis}!pseudootophora@\textit{pseudootophora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華中鐵線蓮&T2_new_value=true&fr=y}}{華中鐵線蓮}\index{華中鐵線蓮} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+psilandra}{\textit{C. psilandra} Kitag.}  \index{Clematis@\textit{Clematis}!psilandra@\textbf{\textit{psilandra}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣牡丹藤&T2_new_value=true&fr=y}}{臺灣牡丹藤}\index{臺灣牡丹藤@{\Song{臺灣牡丹藤}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+tamurae}{\textit{C. tamurae} T.Y.A.Yang \& T.C.Huang}  \index{Clematis@\textit{Clematis}!tamurae@\textit{tamurae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田村氏鐵線蓮&T2_new_value=true&fr=y}}{田村氏鐵線蓮}\index{田村氏鐵線蓮}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+tashiroi+var.+huangii}{\textit{C. tashiroi} Maxim. var. \textit{huangii} T.Y.A.Yang}  \index{Clematis@\textit{Clematis}!tashiroi@\textit{tashiroi}!var. huangii@\textbf{var. \textit{huangii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃氏鐵線蓮&T2_new_value=true&fr=y}}{黃氏鐵線蓮}\index{黃氏鐵線蓮@{\Song{黃氏鐵線蓮}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+tashiroi+var.+tashiroi}{\textit{C. tashiroi} Maxim. var. \textit{tashiroi}}  \index{Clematis@\textit{Clematis}!tashiroi@\textit{tashiroi}!var. tashiroi@var. \textit{tashiroi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=田代氏鐵線蓮&T2_new_value=true&fr=y}}{田代氏鐵線蓮}\index{田代氏鐵線蓮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+terniflora+var.+garanbiensis}{\textit{C. terniflora} DC. var. \textit{garanbiensis} (Hayata) M.C.Chang}  \index{Clematis@\textit{Clematis}!terniflora@\textit{terniflora}!var. garanbiensis@\textbf{var. \textit{garanbiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鵝鑾鼻鐵線蓮&T2_new_value=true&fr=y}}{鵝鑾鼻鐵線蓮}\index{鵝鑾鼻鐵線蓮@{\Song{鵝鑾鼻鐵線蓮}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+tsugetorum}{\textit{C. tsugetorum} Ohwi}  \index{Clematis@\textit{Clematis}!tsugetorum@\textbf{\textit{tsugetorum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山鐵線蓮&T2_new_value=true&fr=y}}{高山鐵線蓮}\index{高山鐵線蓮@{\Song{高山鐵線蓮}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+uncinata+var.+okinawensis}{\textit{C. uncinata} Champ. ex Benth. var. \textit{okinawensis} (Ohwi) Ohwi}  \index{Clematis@\textit{Clematis}!uncinata@\textit{uncinata}!var. okinawensis@\textbf{var. \textit{okinawensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛果鐵線蓮&T2_new_value=true&fr=y}}{毛果鐵線蓮}\index{毛果鐵線蓮@{\Song{毛果鐵線蓮}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clematis+uncinata+var.+uncinata}{\textit{C. uncinata} Champ. ex Benth. var. \textit{uncinata}}  \index{Clematis@\textit{Clematis}!uncinata@\textit{uncinata}!var. uncinata@var. \textit{uncinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柱果鐵線蓮&T2_new_value=true&fr=y}}{柱果鐵線蓮}\index{柱果鐵線蓮} LC
  \end{itemize}
 \item[] \textit{Coptis} 黃連屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coptis+quinquefolia}{\textit{C. quinquefolia} Miq.}  \index{Coptis@\textit{Coptis}!quinquefolia@\textit{quinquefolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=五葉黃連&T2_new_value=true&fr=y}}{五葉黃連}\index{五葉黃連} LC
  \end{itemize}
 \item[] \textit{Dichocarpum} 人字果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dichocarpum+adiantifolium}{\textit{D. adiantifolium} (Hook.f. \& Thoms.) W.T.Wang \& Hsiao}  \index{Dichocarpum@\textit{Dichocarpum}!adiantifolium@\textit{adiantifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鐵線蕨葉人字果&T2_new_value=true&fr=y}}{鐵線蕨葉人字果}\index{鐵線蕨葉人字果}\# NT
  \end{itemize}
 \item[] \textit{Ranunculus} 毛茛屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+cantoniensis}{\textit{R. cantoniensis} DC.}  \index{Ranunculus@\textit{Ranunculus}!cantoniensis@\textit{cantoniensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水辣菜&T2_new_value=true&fr=y}}{水辣菜}\index{水辣菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+cheirophyllus}{\textit{R. cheirophyllus} Hayata}  \index{Ranunculus@\textit{Ranunculus}!cheirophyllus@\textit{cheirophyllus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=掌葉毛茛&T2_new_value=true&fr=y}}{掌葉毛茛}\index{掌葉毛茛}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+chinensis}{\textit{R. chinensis} Bunge}  \index{Ranunculus@\textit{Ranunculus}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茴茴蒜&T2_new_value=true&fr=y}}{茴茴蒜}\index{茴茴蒜@{\Song{茴茴蒜}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+formosa-montanus}{\textit{R. formosa-montanus} Ohwi}  \index{Ranunculus@\textit{Ranunculus}!formosa-montanus@\textit{formosa-montanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓬萊毛茛&T2_new_value=true&fr=y}}{蓬萊毛茛}\index{蓬萊毛茛}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+japonicus}{\textit{R. japonicus} Thunb.}  \index{Ranunculus@\textit{Ranunculus}!japonicus@\textit{japonicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛茛&T2_new_value=true&fr=y}}{毛茛}\index{毛茛} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+junipericola}{\textit{R. junipericola} Ohwi}  \index{Ranunculus@\textit{Ranunculus}!junipericola@\textit{junipericola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=檜林毛茛&T2_new_value=true&fr=y}}{檜林毛茛}\index{檜林毛茛}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+morii}{\textit{R. morii} (Yamam.) Ohwi}  \index{Ranunculus@\textit{Ranunculus}!morii@\textbf{\textit{morii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏毛茛&T2_new_value=true&fr=y}}{森氏毛茛}\index{森氏毛茛@{\Song{森氏毛茛}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+nankotaizanus}{\textit{R. nankotaizanus} Ohwi}  \index{Ranunculus@\textit{Ranunculus}!nankotaizanus@\textbf{\textit{nankotaizanus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖毛茛&T2_new_value=true&fr=y}}{南湖毛茛}\index{南湖毛茛@{\Song{南湖毛茛}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+sceleratus}{\textit{R. sceleratus} L.}  \index{Ranunculus@\textit{Ranunculus}!sceleratus@\textit{sceleratus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石龍芮&T2_new_value=true&fr=y}}{石龍芮}\index{石龍芮} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+sieboldii}{\textit{R. sieboldii} Miq.}  \index{Ranunculus@\textit{Ranunculus}!sieboldii@\textit{sieboldii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=辣子草&T2_new_value=true&fr=y}}{辣子草}\index{辣子草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+silerifolius}{\textit{R. silerifolius} Lev.}  \index{Ranunculus@\textit{Ranunculus}!silerifolius@\textit{silerifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鉤柱毛茛&T2_new_value=true&fr=y}}{鉤柱毛茛}\index{鉤柱毛茛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+taisanensis}{\textit{R. taisanensis} Hayata}  \index{Ranunculus@\textit{Ranunculus}!taisanensis@\textit{taisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鹿場毛茛&T2_new_value=true&fr=y}}{鹿場毛茛}\index{鹿場毛茛}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ranunculus+ternatus}{\textit{R. ternatus} Thunb.}  \index{Ranunculus@\textit{Ranunculus}!ternatus@\textbf{\textit{ternatus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小毛茛&T2_new_value=true&fr=y}}{小毛茛}\index{小毛茛@{\Song{小毛茛}}} VU
  \end{itemize}
 \item[] \textit{Semiaquilegia} 天葵屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Semiaquilegia+adoxoides}{\textit{S. adoxoides} (DC.) Makino}  \index{Semiaquilegia@\textit{Semiaquilegia}!adoxoides@\textit{adoxoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天葵&T2_new_value=true&fr=y}}{天葵}\index{天葵} NA$^n$
  \end{itemize}
 \item[] \textit{Thalictrum} 唐松草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+javanicum+var.+puberulum}{\textit{T. javanicum} Blume var. \textit{puberulum} W.T.Wang}  \index{Thalictrum@\textit{Thalictrum}!javanicum@\textit{javanicum}!var. puberulum@var. \textit{puberulum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=微毛爪哇唐松草&T2_new_value=true&fr=y}}{微毛爪哇唐松草}\index{微毛爪哇唐松草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+myriophyllum}{\textit{T. myriophyllum} Ohwi}  \index{Thalictrum@\textit{Thalictrum}!myriophyllum@\textbf{\textit{myriophyllum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密葉唐松草&T2_new_value=true&fr=y}}{密葉唐松草}\index{密葉唐松草@{\Song{密葉唐松草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+rubescens}{\textit{T. rubescens} Ohwi}  \index{Thalictrum@\textit{Thalictrum}!rubescens@\textbf{\textit{rubescens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖唐松草&T2_new_value=true&fr=y}}{南湖唐松草}\index{南湖唐松草@{\Song{南湖唐松草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+sessile}{\textit{T. sessile} Hayata}  \index{Thalictrum@\textit{Thalictrum}!sessile@\textit{sessile}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山唐松草&T2_new_value=true&fr=y}}{玉山唐松草}\index{玉山唐松草}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+urbaini+var.+majus}{\textit{T. urbaini} Hayata var. \textit{majus} T.Shimizu}  \index{Thalictrum@\textit{Thalictrum}!urbaini@\textit{urbaini}!var. majus@\textbf{var. \textit{majus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大花傅氏唐松草&T2_new_value=true&fr=y}}{大花傅氏唐松草}\index{大花傅氏唐松草@{\Song{大花傅氏唐松草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Thalictrum+urbaini+var.+urbaini}{\textit{T. urbaini} Hayata var. \textit{urbaini}}  \index{Thalictrum@\textit{Thalictrum}!urbaini@\textit{urbaini}!var. urbaini@var. \textit{urbaini}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=傅氏唐松草&T2_new_value=true&fr=y}}{傅氏唐松草}\index{傅氏唐松草}\# LC
  \end{itemize}
 \item[] \textit{Trollius} 金蓮花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Trollius+taihasenzanensis}{\textit{T. taihasenzanensis} Masam.}  \index{Trollius@\textit{Trollius}!taihasenzanensis@\textbf{\textit{taihasenzanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣金蓮花&T2_new_value=true&fr=y}}{臺灣金蓮花}\index{臺灣金蓮花@{\Song{臺灣金蓮花}}}\# VU
  \end{itemize}
  \end{itemize}
