
  \begin{itemize}
 \item[] \textit{Berchemia} 黃鱔藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berchemia+arisanensis}{\textit{B. arisanensis} Y.C.Liu \& F.Y.Lu}  \index{Berchemia@\textit{Berchemia}!arisanensis@\textbf{\textit{arisanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山黃鱔藤&T2_new_value=true&fr=y}}{阿里山黃鱔藤}\index{阿里山黃鱔藤@{\Song{阿里山黃鱔藤}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berchemia+fenchifuensis}{\textit{B. fenchifuensis} C.M.Wang \& F.Y.Lu}  \index{Berchemia@\textit{Berchemia}!fenchifuensis@\textbf{\textit{fenchifuensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=奮起湖黃鱔藤&T2_new_value=true&fr=y}}{奮起湖黃鱔藤}\index{奮起湖黃鱔藤@{\Song{奮起湖黃鱔藤}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berchemia+formosana}{\textit{B. formosana} C.K.Schneid.}  \index{Berchemia@\textit{Berchemia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃鱔藤&T2_new_value=true&fr=y}}{臺灣黃鱔藤}\index{臺灣黃鱔藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berchemia+lineata}{\textit{B. lineata} (L.) DC.}  \index{Berchemia@\textit{Berchemia}!lineata@\textit{lineata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉黃鱔藤&T2_new_value=true&fr=y}}{小葉黃鱔藤}\index{小葉黃鱔藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Berchemia+racemosa+var.+magna}{\textit{B. racemosa} Siebold \& Zucc. var. \textit{magna} Makino}  \index{Berchemia@\textit{Berchemia}!racemosa@\textit{racemosa}!var. magna@var. \textit{magna}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大黃鱔藤&T2_new_value=true&fr=y}}{大黃鱔藤}\index{大黃鱔藤} LC
  \end{itemize}
 \item[] \textit{Colubrina} 濱棗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Colubrina+asiatica}{\textit{C. asiatica} (L.) Brongn.}  \index{Colubrina@\textit{Colubrina}!asiatica@\textbf{\textit{asiatica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=亞洲濱棗&T2_new_value=true&fr=y}}{亞洲濱棗}\index{亞洲濱棗@{\Song{亞洲濱棗}}} EN
  \end{itemize}
 \item[] \textit{Paliurus} 馬甲子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paliurus+ramosissimus}{\textit{P. ramosissimus} (Lour.) Poir.}  \index{Paliurus@\textit{Paliurus}!ramosissimus@\textbf{\textit{ramosissimus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=馬甲子&T2_new_value=true&fr=y}}{馬甲子}\index{馬甲子@{\Song{馬甲子}}} EN
  \end{itemize}
 \item[] \textit{Rhamnus} 鼠李屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+chingshuiensis+var.+chingshuiensis}{\textit{R. chingshuiensis} T.Shimizu var. \textit{chingshuiensis}}  \index{Rhamnus@\textit{Rhamnus}!chingshuiensis@\textit{chingshuiensis}!var. chingshuiensis@\textbf{var. \textit{chingshuiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水鼠李&T2_new_value=true&fr=y}}{清水鼠李}\index{清水鼠李@{\Song{清水鼠李}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+chingshuiensis+var.+tashanensis}{\textit{R. chingshuiensis} T.Shimizu var. \textit{tashanensis} Y.C.Liu \& C.M.Wang}  \index{Rhamnus@\textit{Rhamnus}!chingshuiensis@\textit{chingshuiensis}!var. tashanensis@var. \textit{tashanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=塔山鼠李&T2_new_value=true&fr=y}}{塔山鼠李}\index{塔山鼠李}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+crenata}{\textit{R. crenata} Siebold \& Zucc.}  \index{Rhamnus@\textit{Rhamnus}!crenata@\textit{crenata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鈍齒鼠李&T2_new_value=true&fr=y}}{鈍齒鼠李}\index{鈍齒鼠李} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+formosana}{\textit{R. formosana} Matsum.}  \index{Rhamnus@\textit{Rhamnus}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桶鉤藤&T2_new_value=true&fr=y}}{桶鉤藤}\index{桶鉤藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+kanagusuki}{\textit{R. kanagusuki} Makino}  \index{Rhamnus@\textit{Rhamnus}!kanagusuki@\textit{kanagusuki}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉鼠李&T2_new_value=true&fr=y}}{變葉鼠李}\index{變葉鼠李} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+nakaharae}{\textit{R. nakaharae} (Hayata) Hayata}  \index{Rhamnus@\textit{Rhamnus}!nakaharae@\textit{nakaharae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=中原氏鼠李&T2_new_value=true&fr=y}}{中原氏鼠李}\index{中原氏鼠李}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+parvifolia}{\textit{R. parvifolia} Bunge}  \index{Rhamnus@\textit{Rhamnus}!parvifolia@\textit{parvifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉鼠李&T2_new_value=true&fr=y}}{小葉鼠李}\index{小葉鼠李} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhamnus+pilushanensis}{\textit{R. pilushanensis} Y.C.Liu \& C.M.Wang}  \index{Rhamnus@\textit{Rhamnus}!pilushanensis@\textit{pilushanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=畢祿山鼠李&T2_new_value=true&fr=y}}{畢祿山鼠李}\index{畢祿山鼠李}\# LC
  \end{itemize}
 \item[] \textit{Sageretia} 雀梅藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sageretia+randaiensis}{\textit{S. randaiensis} Hayata}  \index{Sageretia@\textit{Sageretia}!randaiensis@\textit{randaiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巒大雀梅藤&T2_new_value=true&fr=y}}{巒大雀梅藤}\index{巒大雀梅藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sageretia+thea+var.+taiwaniana}{\textit{S. thea} (Osbeck) Johnst. var. \textit{taiwaniana} (Masam.) Y.C.Liu \& C.M.Wang}  \index{Sageretia@\textit{Sageretia}!thea@\textit{thea}!var. taiwaniana@var. \textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣雀梅藤&T2_new_value=true&fr=y}}{臺灣雀梅藤}\index{臺灣雀梅藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sageretia+thea+var.+thea}{\textit{S. thea} (Osbeck) Johnst. var. \textit{thea}}  \index{Sageretia@\textit{Sageretia}!thea@\textit{thea}!var. thea@var. \textit{thea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雀梅藤&T2_new_value=true&fr=y}}{雀梅藤}\index{雀梅藤} LC
  \end{itemize}
 \item[] \textit{Ventilago} 翼核木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ventilago+elegans}{\textit{V. elegans} Hemsl.}  \index{Ventilago@\textit{Ventilago}!elegans@\textit{elegans}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼核木&T2_new_value=true&fr=y}}{翼核木}\index{翼核木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ventilago+leiocarpa}{\textit{V. leiocarpa} Benth.}  \index{Ventilago@\textit{Ventilago}!leiocarpa@\textit{leiocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光果翼核木&T2_new_value=true&fr=y}}{光果翼核木}\index{光果翼核木} LC
  \end{itemize}
  \end{itemize}
