
  \begin{itemize}
 \item[] \textit{Agrimonia} 龍牙草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Agrimonia+pilosa}{\textit{A. pilosa} Ledeb.}  \index{Agrimonia@\textit{Agrimonia}!pilosa@\textit{pilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=龍牙草&T2_new_value=true&fr=y}}{龍牙草}\index{龍牙草} LC
  \end{itemize}
 \item[] \textit{Aria} 赤楊葉梨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Aria+alnifolia}{\textit{A. alnifolia} (Siebold \& Zucc.) Decne.}  \index{Aria@\textit{Aria}!alnifolia@\textbf{\textit{alnifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=赤楊葉梨&T2_new_value=true&fr=y}}{赤楊葉梨}\index{赤楊葉梨@{\Song{赤楊葉梨}}} EN
  \end{itemize}
 \item[] \textit{Cotoneaster} 舖地蜈蚣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+apiculatus}{\textit{C. apiculatus} Rehd. \& Wils.}  \index{Cotoneaster@\textit{Cotoneaster}!apiculatus@\textit{apiculatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細尖栒子&T2_new_value=true&fr=y}}{細尖栒子}\index{細尖栒子} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+bullatus}{\textit{C. bullatus} Bois}  \index{Cotoneaster@\textit{Cotoneaster}!bullatus@\textbf{\textit{bullatus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=泡葉栒子&T2_new_value=true&fr=y}}{泡葉栒子}\index{泡葉栒子@{\Song{泡葉栒子}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+chingshuiensis}{\textit{C. chingshuiensis} Kun C.Chang \& Chih C.Wang}  \index{Cotoneaster@\textit{Cotoneaster}!chingshuiensis@\textbf{\textit{chingshuiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水山栒子&T2_new_value=true&fr=y}}{清水山栒子}\index{清水山栒子@{\Song{清水山栒子}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+dammeri}{\textit{C. dammeri} C.K.Schneid.}  \index{Cotoneaster@\textit{Cotoneaster}!dammeri@\textit{dammeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=矮生栒子&T2_new_value=true&fr=y}}{矮生栒子}\index{矮生栒子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+horizontalis}{\textit{C. horizontalis} Dcne.}  \index{Cotoneaster@\textit{Cotoneaster}!horizontalis@\textit{horizontalis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=平枝舖地蜈蚣&T2_new_value=true&fr=y}}{平枝舖地蜈蚣}\index{平枝舖地蜈蚣} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+konishii}{\textit{C. konishii} Hayata}  \index{Cotoneaster@\textit{Cotoneaster}!konishii@\textit{konishii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣舖地蜈蚣&T2_new_value=true&fr=y}}{臺灣舖地蜈蚣}\index{臺灣舖地蜈蚣}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+morrisonensis}{\textit{C. morrisonensis} Hayata}  \index{Cotoneaster@\textit{Cotoneaster}!morrisonensis@\textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山舖地蜈蚣&T2_new_value=true&fr=y}}{玉山舖地蜈蚣}\index{玉山舖地蜈蚣}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+rokujodaisanensis}{\textit{C. rokujodaisanensis} Hayata}  \index{Cotoneaster@\textit{Cotoneaster}!rokujodaisanensis@\textit{rokujodaisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=樂山舖地蜈蚣&T2_new_value=true&fr=y}}{樂山舖地蜈蚣}\index{樂山舖地蜈蚣}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+rosiflorus}{\textit{C. rosiflorus} K.C.Chang \& F.Y.Lu}  \index{Cotoneaster@\textit{Cotoneaster}!rosiflorus@\textit{rosiflorus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粉紅花舖地蜈蚣&T2_new_value=true&fr=y}}{粉紅花舖地蜈蚣}\index{粉紅花舖地蜈蚣}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cotoneaster+subadpressus}{\textit{C. subadpressus} T.T.Yu}  \index{Cotoneaster@\textit{Cotoneaster}!subadpressus@\textbf{\textit{subadpressus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山栒子&T2_new_value=true&fr=y}}{高山栒子}\index{高山栒子@{\Song{高山栒子}}} VU
  \end{itemize}
 \item[] \textit{Duchesnea} 蛇莓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Duchesnea+chrysantha}{\textit{D. chrysantha} (Zoll. \& Mor.) Miq.}  \index{Duchesnea@\textit{Duchesnea}!chrysantha@\textit{chrysantha}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蛇莓&T2_new_value=true&fr=y}}{臺灣蛇莓}\index{臺灣蛇莓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Duchesnea+indica}{\textit{D. indica} (Andr.) Focke}  \index{Duchesnea@\textit{Duchesnea}!indica@\textit{indica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蛇莓&T2_new_value=true&fr=y}}{蛇莓}\index{蛇莓} LC
  \end{itemize}
 \item[] \textit{Eriobotrya} 枇杷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eriobotrya+deflexa}{\textit{E. deflexa} (Hemsl.) Nakai}  \index{Eriobotrya@\textit{Eriobotrya}!deflexa@\textit{deflexa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山枇杷&T2_new_value=true&fr=y}}{山枇杷}\index{山枇杷}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eriobotrya+deflexa+ f. +buisanensis}{\textit{E. deflexa} (Hemsl.) Nakai  f.  \textit{buisanensis} (Hayata) Nakai}  \index{Eriobotrya@\textit{Eriobotrya}!deflexa@\textit{deflexa}!f. buisanensis@f. \textit{buisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=武威山枇杷&T2_new_value=true&fr=y}}{武威山枇杷}\index{武威山枇杷}\# NA$^f$
  \end{itemize}
 \item[] \textit{Filipendula} 蚊子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Filipendula+kiraishiensis}{\textit{F. kiraishiensis} Hayata}  \index{Filipendula@\textit{Filipendula}!kiraishiensis@\textbf{\textit{kiraishiensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蚊子草&T2_new_value=true&fr=y}}{臺灣蚊子草}\index{臺灣蚊子草@{\Song{臺灣蚊子草}}}\# VU
  \end{itemize}
 \item[] \textit{Fragaria} 草莓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Fragaria+hayatai}{\textit{F. hayatai} Makino}  \index{Fragaria@\textit{Fragaria}!hayatai@\textit{hayatai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣草莓&T2_new_value=true&fr=y}}{臺灣草莓}\index{臺灣草莓}\# LC
  \end{itemize}
 \item[] \textit{Geum} 水楊梅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Geum+japonicum}{\textit{G. japonicum} Thunb.}  \index{Geum@\textit{Geum}!japonicum@\textbf{\textit{japonicum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本水楊梅&T2_new_value=true&fr=y}}{日本水楊梅}\index{日本水楊梅@{\Song{日本水楊梅}}} VU
  \end{itemize}
 \item[] \textit{Malus} 蘋果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malus+doumeri}{\textit{M. doumeri} (Bois.) Chev.}  \index{Malus@\textit{Malus}!doumeri@\textit{doumeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣蘋果&T2_new_value=true&fr=y}}{臺灣蘋果}\index{臺灣蘋果} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Malus+hupehensis}{\textit{M. hupehensis} (Pamp.) Rehder}  \index{Malus@\textit{Malus}!hupehensis@\textbf{\textit{hupehensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=湖北海棠&T2_new_value=true&fr=y}}{湖北海棠}\index{湖北海棠@{\Song{湖北海棠}}} CR
  \end{itemize}
 \item[] \textit{Osteomeles} 小石積屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osteomeles+anthyllidifolia+var.+subrotunda}{\textit{O. anthyllidifolia} Lindl. var. \textit{subrotunda} (C.Koch) Masam.}  \index{Osteomeles@\textit{Osteomeles}!anthyllidifolia@\textit{anthyllidifolia}!var. subrotunda@\textbf{var. \textit{subrotunda}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小石積&T2_new_value=true&fr=y}}{小石積}\index{小石積@{\Song{小石積}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Osteomeles+schwerinae}{\textit{O. schwerinae} C.K.Schneid.}  \index{Osteomeles@\textit{Osteomeles}!schwerinae@\textbf{\textit{schwerinae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華西小石積&T2_new_value=true&fr=y}}{華西小石積}\index{華西小石積@{\Song{華西小石積}}} CR
  \end{itemize}
 \item[] \textit{Photinia} 石楠屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+beauverdiana}{\textit{P. beauverdiana} C.K.Schneid.}  \index{Photinia@\textit{Photinia}!beauverdiana@\textit{beauverdiana}}  \index{Pourthiaea@\textit{Pourthiaea}!beauverdiana@\textit{beauverdiana}!var. notabilis@var. \textit{notabilis}{\\\noindent(=\textit{Photinia beauverdiana})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣老葉兒樹&T2_new_value=true&fr=y}}{臺灣老葉兒樹}\index{臺灣老葉兒樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+chingshuiensis}{\textit{P. chingshuiensis} (T.Shimizu) T.S.Liu \& H.J.Su}  \index{Photinia@\textit{Photinia}!chingshuiensis@\textit{chingshuiensis}}  \index{Pourthiaea@\textit{Pourthiaea}!villosa@\textit{villosa}!var. chingshuiensis@var. \textit{chingshuiensis}{\\\noindent(=\textit{Photinia chingshuiensis})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水石楠&T2_new_value=true&fr=y}}{清水石楠}\index{清水石楠}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+lucida}{\textit{P. lucida} (Decne.) C.K.Schneid.}  \index{Photinia@\textit{Photinia}!lucida@\textit{lucida}}  \index{Pourthiaea@\textit{Pourthiaea}!lucida@\textit{lucida}{\\\noindent(= \textit{Photinia lucida})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣石楠&T2_new_value=true&fr=y}}{臺灣石楠}\index{臺灣石楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+niitakayamensis}{\textit{P. niitakayamensis} Hayata}  \index{Photinia@\textit{Photinia}!niitakayamensis@\textit{niitakayamensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山假沙梨&T2_new_value=true&fr=y}}{玉山假沙梨}\index{玉山假沙梨} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+parvifolia}{\textit{P. parvifolia} (E.Pritz.) C.K.Schneid.}  \index{Photinia@\textit{Photinia}!parvifolia@\textit{parvifolia}}  \index{Pourthiaea@\textit{Pourthiaea}!villosa@\textit{villosa}!var. parvifolia@var. \textit{parvifolia}{\\\noindent(=\textit{Photinia parvifolia})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉石楠&T2_new_value=true&fr=y}}{小葉石楠}\index{小葉石楠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+serratifolia+var.+ardisiifolia}{\textit{P. serratifolia} (Desf.) Kalkman var. \textit{ardisiifolia} (Hayata) H.Ohashi}  \index{Photinia@\textit{Photinia}!serratifolia@\textit{serratifolia}!var. ardisiifolia@var. \textit{ardisiifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東石楠&T2_new_value=true&fr=y}}{臺東石楠}\index{臺東石楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+serratifolia+var.+lasiopetala}{\textit{P. serratifolia} (Desf.) Kalkman var. \textit{lasiopetala} (Hayata) H.Ohashi}  \index{Photinia@\textit{Photinia}!serratifolia@\textit{serratifolia}!var. lasiopetala@var. \textit{lasiopetala}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛瓣石楠&T2_new_value=true&fr=y}}{毛瓣石楠}\index{毛瓣石楠}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Photinia+serratifolia+var.+serratifolia}{\textit{P. serratifolia} (Desf.) Kalkman var. \textit{serratifolia}}  \index{Photinia@\textit{Photinia}!serratifolia@\textit{serratifolia}!var. serratifolia@var. \textit{serratifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石楠&T2_new_value=true&fr=y}}{石楠}\index{石楠} LC
  \end{itemize}
 \item[] \textit{Potentilla} 翻白草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+amurensis}{\textit{P. amurensis} Maxim.}  \index{Potentilla@\textit{Potentilla}!amurensis@\textit{amurensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花金梅&T2_new_value=true&fr=y}}{小花金梅}\index{小花金梅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+chinensis}{\textit{P. chinensis} Ser.}  \index{Potentilla@\textit{Potentilla}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=委陵菜&T2_new_value=true&fr=y}}{委陵菜}\index{委陵菜@{\Song{委陵菜}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+discolor}{\textit{P. discolor} Bunge}  \index{Potentilla@\textit{Potentilla}!discolor@\textit{discolor}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翻白草&T2_new_value=true&fr=y}}{翻白草}\index{翻白草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+leuconota}{\textit{P. leuconota} D.Don}  \index{Potentilla@\textit{Potentilla}!leuconota@\textit{leuconota}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山金梅&T2_new_value=true&fr=y}}{玉山金梅}\index{玉山金梅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+matsumurae+var.+pilosa}{\textit{P. matsumurae} Th.Wolf. var. \textit{pilosa} Koidz.}  \index{Potentilla@\textit{Potentilla}!matsumurae@\textit{matsumurae}!var. pilosa@var. \textit{pilosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山翻白草&T2_new_value=true&fr=y}}{高山翻白草}\index{高山翻白草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+nipponica}{\textit{P. nipponica} Th.Wolf.}  \index{Potentilla@\textit{Potentilla}!nipponica@\textbf{\textit{nipponica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本翻白草&T2_new_value=true&fr=y}}{日本翻白草}\index{日本翻白草@{\Song{日本翻白草}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Potentilla+tugitakensis}{\textit{P. tugitakensis} Masam.}  \index{Potentilla@\textit{Potentilla}!tugitakensis@\textbf{\textit{tugitakensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪山翻白草&T2_new_value=true&fr=y}}{雪山翻白草}\index{雪山翻白草@{\Song{雪山翻白草}}}\# EN
  \end{itemize}
 \item[] \textit{Prinsepia} 假皂莢屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prinsepia+scandens}{\textit{P. scandens} Hayata}  \index{Prinsepia@\textit{Prinsepia}!scandens@\textit{scandens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假皂莢&T2_new_value=true&fr=y}}{假皂莢}\index{假皂莢}\# LC
  \end{itemize}
 \item[] \textit{Prunus} 梅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+buergeriana}{\textit{P. buergeriana} Miq.}  \index{Prunus@\textit{Prunus}!buergeriana@\textit{buergeriana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=布氏稠李&T2_new_value=true&fr=y}}{布氏稠李}\index{布氏稠李} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+campanulata}{\textit{P. campanulata} Maxim.}  \index{Prunus@\textit{Prunus}!campanulata@\textit{campanulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山櫻花&T2_new_value=true&fr=y}}{山櫻花}\index{山櫻花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+grisea}{\textit{P. grisea} (C.Muell.) Kalkman}  \index{Prunus@\textit{Prunus}!grisea@\textbf{\textit{grisea}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼野櫻花&T2_new_value=true&fr=y}}{蘭嶼野櫻花}\index{蘭嶼野櫻花@{\Song{蘭嶼野櫻花}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+japonica}{\textit{P. japonica} Thunb.}  \index{Prunus@\textit{Prunus}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=郁李&T2_new_value=true&fr=y}}{郁李}\index{郁李} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+matuurai}{\textit{P. matuurai} Sasaki}  \index{Prunus@\textit{Prunus}!matuurai@\textit{matuurai}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太平山櫻花&T2_new_value=true&fr=y}}{太平山櫻花}\index{太平山櫻花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+mume}{\textit{P. mume} (Siebold) Siebold \& Zucc.}  \index{Prunus@\textit{Prunus}!mume@\textit{mume}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梅&T2_new_value=true&fr=y}}{梅}\index{梅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+obtusata}{\textit{P. obtusata} Koehne}  \index{Prunus@\textit{Prunus}!obtusata@\textbf{\textit{obtusata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣稠李&T2_new_value=true&fr=y}}{臺灣稠李}\index{臺灣稠李@{\Song{臺灣稠李}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+phaeosticta+var.+ilicifolia}{\textit{P. phaeosticta} (Hance) Maxim. var. \textit{ilicifolia} Yamam.}  \index{Prunus@\textit{Prunus}!phaeosticta@\textit{phaeosticta}!var. ilicifolia@\textbf{var. \textit{ilicifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冬青葉桃仁&T2_new_value=true&fr=y}}{冬青葉桃仁}\index{冬青葉桃仁@{\Song{冬青葉桃仁}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+phaeosticta+var.+phaeosticta}{\textit{P. phaeosticta} (Hance) Maxim. var. \textit{phaeosticta}}  \index{Prunus@\textit{Prunus}!phaeosticta@\textit{phaeosticta}!var. phaeosticta@var. \textit{phaeosticta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=墨點櫻桃&T2_new_value=true&fr=y}}{墨點櫻桃}\index{墨點櫻桃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+pogonostyla}{\textit{P. pogonostyla} Maxim.}  \index{Prunus@\textit{Prunus}!pogonostyla@\textbf{\textit{pogonostyla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=庭梅&T2_new_value=true&fr=y}}{庭梅}\index{庭梅@{\Song{庭梅}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+spinulosa}{\textit{P. spinulosa} Siebold \& Zucc.}  \index{Prunus@\textit{Prunus}!spinulosa@\textit{spinulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺葉桂櫻&T2_new_value=true&fr=y}}{刺葉桂櫻}\index{刺葉桂櫻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+taiwaniana}{\textit{P. taiwaniana} Hayata}  \index{Prunus@\textit{Prunus}!taiwaniana@\textit{taiwaniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=霧社山櫻花&T2_new_value=true&fr=y}}{霧社山櫻花}\index{霧社山櫻花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+takasagomontana}{\textit{P. takasagomontana} Sasaki}  \index{Prunus@\textit{Prunus}!takasagomontana@\textit{takasagomontana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山白櫻&T2_new_value=true&fr=y}}{山白櫻}\index{山白櫻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+transarisanensis}{\textit{P. transarisanensis} Hayata}  \index{Prunus@\textit{Prunus}!transarisanensis@\textit{transarisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山櫻花&T2_new_value=true&fr=y}}{阿里山櫻花}\index{阿里山櫻花}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Prunus+zippeliana}{\textit{P. zippeliana} Miq.}  \index{Prunus@\textit{Prunus}!zippeliana@\textit{zippeliana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黃土樹&T2_new_value=true&fr=y}}{黃土樹}\index{黃土樹} LC
  \end{itemize}
 \item[] \textit{Pyracantha} 火刺木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyracantha+koidzumii}{\textit{P. koidzumii} (Hayata) Rehder}  \index{Pyracantha@\textit{Pyracantha}!koidzumii@\textbf{\textit{koidzumii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣火刺木&T2_new_value=true&fr=y}}{臺灣火刺木}\index{臺灣火刺木@{\Song{臺灣火刺木}}}\# VU
  \end{itemize}
 \item[] \textit{Pyrus} 梨屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrus+calleryana}{\textit{P. calleryana} Decne.}  \index{Pyrus@\textit{Pyrus}!calleryana@\textbf{\textit{calleryana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豆梨&T2_new_value=true&fr=y}}{豆梨}\index{豆梨@{\Song{豆梨}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrus+taiwanensis}{\textit{P. taiwanensis} Iketani \& H.Ohashi}  \index{Pyrus@\textit{Pyrus}!taiwanensis@\textbf{\textit{taiwanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣野梨&T2_new_value=true&fr=y}}{臺灣野梨}\index{臺灣野梨@{\Song{臺灣野梨}}}\# CR
  \end{itemize}
 \item[] \textit{Rhaphiolepis} 石斑木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhaphiolepis+indica+var.+hiiranensis}{\textit{R. indica} (L.) Lindl. ex Ker var. \textit{hiiranensis} (Kaneh.) H.L.Li}  \index{Rhaphiolepis@\textit{Rhaphiolepis}!indica@\textit{indica}!var. hiiranensis@var. \textit{hiiranensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春石斑木&T2_new_value=true&fr=y}}{恆春石斑木}\index{恆春石斑木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhaphiolepis+indica+var.+tashiroi}{\textit{R. indica} (L.) Lindl. ex Ker var. \textit{tashiroi} Hayata ex Matsum. \& Hayata}  \index{Rhaphiolepis@\textit{Rhaphiolepis}!indica@\textit{indica}!var. tashiroi@var. \textit{tashiroi}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石斑木&T2_new_value=true&fr=y}}{石斑木}\index{石斑木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rhaphiolepis+indica+var.+umbellata}{\textit{R. indica} (L.) Lindl. ex Ker var. \textit{umbellata} (Thunb.) H.Ohashi}  \index{Rhaphiolepis@\textit{Rhaphiolepis}!indica@\textit{indica}!var. umbellata@var. \textit{umbellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=厚葉石斑木&T2_new_value=true&fr=y}}{厚葉石斑木}\index{厚葉石斑木} NT
  \end{itemize}
 \item[] \textit{Rosa} 薔薇屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+bracteata+var.+bracteata}{\textit{R. bracteata} Wendl. var. \textit{bracteata}}  \index{Rosa@\textit{Rosa}!bracteata@\textit{bracteata}!var. bracteata@\textbf{var. \textit{bracteata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球野薔薇&T2_new_value=true&fr=y}}{琉球野薔薇}\index{琉球野薔薇@{\Song{琉球野薔薇}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+bracteata+var.+scabricaulis}{\textit{R. bracteata} Wendl. var. \textit{scabricaulis} Lindl. ex Koidz.}  \index{Rosa@\textit{Rosa}!bracteata@\textit{bracteata}!var. scabricaulis@var. \textit{scabricaulis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=濱野薔薇&T2_new_value=true&fr=y}}{濱野薔薇}\index{濱野薔薇} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+cymosa}{\textit{R. cymosa} Tratt.}  \index{Rosa@\textit{Rosa}!cymosa@\textbf{\textit{cymosa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小果薔薇&T2_new_value=true&fr=y}}{小果薔薇}\index{小果薔薇@{\Song{小果薔薇}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+laevigata}{\textit{R. laevigata} Michx.}  \index{Rosa@\textit{Rosa}!laevigata@\textbf{\textit{laevigata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金櫻子&T2_new_value=true&fr=y}}{金櫻子}\index{金櫻子@{\Song{金櫻子}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+luciae+var.+luciae}{\textit{R. luciae} Franch. \& Rochebr. ex Crepin var. \textit{luciae}}  \index{Rosa@\textit{Rosa}!luciae@\textit{luciae}!var. luciae@var. \textit{luciae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉薔薇&T2_new_value=true&fr=y}}{光葉薔薇}\index{光葉薔薇}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+luciae+var.+rosea}{\textit{R. luciae} Franch. \& Rochebr. ex Crepin var. \textit{rosea} H.L.Li}  \index{Rosa@\textit{Rosa}!luciae@\textit{luciae}!var. rosea@var. \textit{rosea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣光葉薔薇&T2_new_value=true&fr=y}}{臺灣光葉薔薇}\index{臺灣光葉薔薇}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+multiflora+var.+formosana}{\textit{R. multiflora} Thunb. var. \textit{formosana} Cardot}  \index{Rosa@\textit{Rosa}!multiflora@\textit{multiflora}!var. formosana@var. \textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣野薔薇&T2_new_value=true&fr=y}}{臺灣野薔薇}\index{臺灣野薔薇} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+pricei}{\textit{R. pricei} Hayata}  \index{Rosa@\textit{Rosa}!pricei@\textit{pricei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣薔薇&T2_new_value=true&fr=y}}{太魯閣薔薇}\index{太魯閣薔薇}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+sambucina}{\textit{R. sambucina} Koidz.}  \index{Rosa@\textit{Rosa}!sambucina@\textit{sambucina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山薔薇&T2_new_value=true&fr=y}}{山薔薇}\index{山薔薇} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+sericea+var.+morrisonensis}{\textit{R. sericea} Lindl. var. \textit{morrisonensis} (Hayata) Masam.}  \index{Rosa@\textit{Rosa}!sericea@\textit{sericea}!var. morrisonensis@var. \textit{morrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山野薔薇&T2_new_value=true&fr=y}}{玉山野薔薇}\index{玉山野薔薇}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+taiwanensis}{\textit{R. taiwanensis} Nakai}  \index{Rosa@\textit{Rosa}!taiwanensis@\textit{taiwanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小金櫻&T2_new_value=true&fr=y}}{小金櫻}\index{小金櫻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rosa+transmorrisonensis}{\textit{R. transmorrisonensis} Hayata}  \index{Rosa@\textit{Rosa}!transmorrisonensis@\textit{transmorrisonensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山薔薇&T2_new_value=true&fr=y}}{高山薔薇}\index{高山薔薇} LC
  \end{itemize}
 \item[] \textit{Rubus} 懸鉤子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+alceifolius}{\textit{R. alceifolius} Poir.}  \index{Rubus@\textit{Rubus}!alceifolius@\textit{alceifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羽萼懸鉤子&T2_new_value=true&fr=y}}{羽萼懸鉤子}\index{羽萼懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+alnifoliolatus}{\textit{R. alnifoliolatus} H.Lév.}  \index{Rubus@\textit{Rubus}!alnifoliolatus@\textit{alnifoliolatus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=榿葉懸鉤子&T2_new_value=true&fr=y}}{榿葉懸鉤子}\index{榿葉懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+amphidasys}{\textit{R. amphidasys} Focke}  \index{Rubus@\textit{Rubus}!amphidasys@\textit{amphidasys}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=周毛懸鉤子&T2_new_value=true&fr=y}}{周毛懸鉤子}\index{周毛懸鉤子} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+buergeri}{\textit{R. buergeri} Miq.}  \index{Rubus@\textit{Rubus}!buergeri@\textit{buergeri}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=寒莓&T2_new_value=true&fr=y}}{寒莓}\index{寒莓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+corchorifolius}{\textit{R. corchorifolius} L.f.}  \index{Rubus@\textit{Rubus}!corchorifolius@\textit{corchorifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=變葉懸鉤子&T2_new_value=true&fr=y}}{變葉懸鉤子}\index{變葉懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+croceacanthus+var.+croceacanthus}{\textit{R. croceacanthus} H.Lév. var. \textit{croceacanthus}}  \index{Rubus@\textit{Rubus}!croceacanthus@\textit{croceacanthus}!var. croceacanthus@var. \textit{croceacanthus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虎婆刺&T2_new_value=true&fr=y}}{虎婆刺}\index{虎婆刺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+croceacanthus+var.+glaber}{\textit{R. croceacanthus} H.Lév. var. \textit{glaber} Koidz.}  \index{Rubus@\textit{Rubus}!croceacanthus@\textit{croceacanthus}!var. glaber@var. \textit{glaber}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=禿懸鉤子&T2_new_value=true&fr=y}}{禿懸鉤子}\index{禿懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+flagelliflorus}{\textit{R. flagelliflorus} Focke}  \index{Rubus@\textit{Rubus}!flagelliflorus@\textbf{\textit{flagelliflorus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂緣苞懸鉤子&T2_new_value=true&fr=y}}{裂緣苞懸鉤子}\index{裂緣苞懸鉤子@{\Song{裂緣苞懸鉤子}}} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+formosensis}{\textit{R. formosensis} Kuntze}  \index{Rubus@\textit{Rubus}!formosensis@\textit{formosensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣懸鉤子&T2_new_value=true&fr=y}}{臺灣懸鉤子}\index{臺灣懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+fraxinifoliolus}{\textit{R. fraxinifoliolus} Hayata}  \index{Rubus@\textit{Rubus}!fraxinifoliolus@\textit{fraxinifoliolus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梣葉懸鉤子&T2_new_value=true&fr=y}}{梣葉懸鉤子}\index{梣葉懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+fraxinifolius}{\textit{R. fraxinifolius} Poir.}  \index{Rubus@\textit{Rubus}!fraxinifolius@\textit{fraxinifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼榿葉懸鉤子&T2_new_value=true&fr=y}}{蘭嶼榿葉懸鉤子}\index{蘭嶼榿葉懸鉤子} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+howii}{\textit{R. howii} Merr. \& Chun.}  \index{Rubus@\textit{Rubus}!howii@\textit{howii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裂葉懸鉤子&T2_new_value=true&fr=y}}{裂葉懸鉤子}\index{裂葉懸鉤子} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+hui}{\textit{R. hui} Diels}  \index{Rubus@\textit{Rubus}!hui@\textit{hui}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=胡氏懸鉤子&T2_new_value=true&fr=y}}{胡氏懸鉤子}\index{胡氏懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+kawakamii}{\textit{R. kawakamii} Hayata}  \index{Rubus@\textit{Rubus}!kawakamii@\textit{kawakamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=桑葉懸鉤子&T2_new_value=true&fr=y}}{桑葉懸鉤子}\index{桑葉懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+lambertianus}{\textit{R. lambertianus} Ser. ex DC.}  \index{Rubus@\textit{Rubus}!lambertianus@\textit{lambertianus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高梁泡&T2_new_value=true&fr=y}}{高梁泡}\index{高梁泡} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+lanyuensis}{\textit{R. lanyuensis} C.E.Chang}  \index{Rubus@\textit{Rubus}!lanyuensis@\textit{lanyuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼懸鉤子&T2_new_value=true&fr=y}}{蘭嶼懸鉤子}\index{蘭嶼懸鉤子}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+linearifoliolus}{\textit{R. linearifoliolus} Hayata}  \index{Rubus@\textit{Rubus}!linearifoliolus@\textit{linearifoliolus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細葉懸鉤子&T2_new_value=true&fr=y}}{細葉懸鉤子}\index{細葉懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+liuiYuen}{\textit{R. liuiYuen} P.Yang \& S.Y.Lu}  \index{Rubus@\textit{Rubus}!liuiYuen@\textit{liuiYuen}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柳氏懸鉤子&T2_new_value=true&fr=y}}{柳氏懸鉤子}\index{柳氏懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+mesogaeus}{\textit{R. mesogaeus} Focke}  \index{Rubus@\textit{Rubus}!mesogaeus@\textit{mesogaeus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=裏白懸鉤子&T2_new_value=true&fr=y}}{裏白懸鉤子}\index{裏白懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+morii}{\textit{R. morii} Hayata}  \index{Rubus@\textit{Rubus}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=尾葉懸鉤子&T2_new_value=true&fr=y}}{尾葉懸鉤子}\index{尾葉懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+nagasawanus+var.+arachnoideus}{\textit{R. nagasawanus} Koidz. var. \textit{arachnoideus} (Y.C.Liu \& F.Y.Lu) S.S.Ying}  \index{Rubus@\textit{Rubus}!nagasawanus@\textit{nagasawanus}!var. arachnoideus@\textbf{var. \textit{arachnoideus}}}  \index{Rubus@\textit{Rubus}!arachnoideus@\textit{arachnoideus}{\\\noindent(= \textit{Rubus nagasawanus} var. \textit{arachnoideus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=灰葉懸鉤子&T2_new_value=true&fr=y}}{灰葉懸鉤子}\index{灰葉懸鉤子@{\Song{灰葉懸鉤子}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+nagasawanus+var.+nagasawanus}{\textit{R. nagasawanus} Koidz. var. \textit{nagasawanus}}  \index{Rubus@\textit{Rubus}!nagasawanus@\textit{nagasawanus}!var. nagasawanus@\textbf{var. \textit{nagasawanus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛懸鉤子&T2_new_value=true&fr=y}}{粗毛懸鉤子}\index{粗毛懸鉤子@{\Song{粗毛懸鉤子}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+niveus}{\textit{R. niveus} Thunb.}  \index{Rubus@\textit{Rubus}!niveus@\textit{niveus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白絨懸鉤子&T2_new_value=true&fr=y}}{白絨懸鉤子}\index{白絨懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+parviaraliifolius}{\textit{R. parviaraliifolius} Hayata}  \index{Rubus@\textit{Rubus}!parviaraliifolius@\textit{parviaraliifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小楤葉懸鉤子&T2_new_value=true&fr=y}}{小楤葉懸鉤子}\index{小楤葉懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+parvifolius+var.+parvifolius}{\textit{R. parvifolius} L. var. \textit{parvifolius}}  \index{Rubus@\textit{Rubus}!parvifolius@\textit{parvifolius}!var. parvifolius@var. \textit{parvifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅梅消&T2_new_value=true&fr=y}}{紅梅消}\index{紅梅消} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+parvifolius+var.+toapiensis}{\textit{R. parvifolius} L. var. \textit{toapiensis} (Yamam.) Hosok.}  \index{Rubus@\textit{Rubus}!parvifolius@\textit{parvifolius}!var. toapiensis@var. \textit{toapiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東紅梅消&T2_new_value=true&fr=y}}{臺東紅梅消}\index{臺東紅梅消}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+pectinellus}{\textit{R. pectinellus} Maxim.}  \index{Rubus@\textit{Rubus}!pectinellus@\textit{pectinellus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺萼寒莓&T2_new_value=true&fr=y}}{刺萼寒莓}\index{刺萼寒莓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+pseudoacer+subsp.+flexuosus}{\textit{R. pseudoacer} Makino subsp. \textit{flexuosus} (Y.C.Liu \& F.Y.Lu) H.Ohashi \& C.F.Hsieh}  \index{Rubus@\textit{Rubus}!pseudoacer@\textit{pseudoacer}!subsp. flexuosus@subsp. \textit{flexuosus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水懸鉤子&T2_new_value=true&fr=y}}{清水懸鉤子}\index{清水懸鉤子}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+pungens+var.+oldhamii}{\textit{R. pungens} Camb. var. \textit{oldhamii} (Miq.) Maxim.}  \index{Rubus@\textit{Rubus}!pungens@\textit{pungens}!var. oldhamii@var. \textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛刺懸鉤子&T2_new_value=true&fr=y}}{毛刺懸鉤子}\index{毛刺懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+pungens+var.+pungens}{\textit{R. pungens} Camb. var. \textit{pungens}}  \index{Rubus@\textit{Rubus}!pungens@\textit{pungens}!var. pungens@var. \textit{pungens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺懸鉤子&T2_new_value=true&fr=y}}{刺懸鉤子}\index{刺懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+pyrifolius}{\textit{R. pyrifolius} Sm.}  \index{Rubus@\textit{Rubus}!pyrifolius@\textit{pyrifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=梨葉懸鉤子&T2_new_value=true&fr=y}}{梨葉懸鉤子}\index{梨葉懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+ritozanensis}{\textit{R. ritozanensis} Sasaki}  \index{Rubus@\textit{Rubus}!ritozanensis@\textit{ritozanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=李棟山懸鉤子&T2_new_value=true&fr=y}}{李棟山懸鉤子}\index{李棟山懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+rolfei}{\textit{R. rolfei} Vidal}  \index{Rubus@\textit{Rubus}!rolfei@\textit{rolfei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山懸鉤子&T2_new_value=true&fr=y}}{高山懸鉤子}\index{高山懸鉤子} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+rosifolius}{\textit{R. rosifolius} Sm.}  \index{Rubus@\textit{Rubus}!rosifolius@\textit{rosifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺莓&T2_new_value=true&fr=y}}{刺莓}\index{刺莓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+rufus}{\textit{R. rufus} Focke}  \index{Rubus@\textit{Rubus}!rufus@\textit{rufus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=棕紅懸鉤子&T2_new_value=true&fr=y}}{棕紅懸鉤子}\index{棕紅懸鉤子} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+sumatranus}{\textit{R. sumatranus} Miq.}  \index{Rubus@\textit{Rubus}!sumatranus@\textbf{\textit{sumatranus}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅腺懸鉤子&T2_new_value=true&fr=y}}{紅腺懸鉤子}\index{紅腺懸鉤子@{\Song{紅腺懸鉤子}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+swinhoei}{\textit{R. swinhoei} Hance}  \index{Rubus@\textit{Rubus}!swinhoei@\textit{swinhoei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=斯氏懸鉤子&T2_new_value=true&fr=y}}{斯氏懸鉤子}\index{斯氏懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+taitoensis+var.+aculeatiflorus}{\textit{R. taitoensis} Hayata var. \textit{aculeatiflorus} (Hayata) H.Ohashi \& C.F.Hsieh}  \index{Rubus@\textit{Rubus}!taitoensis@\textit{taitoensis}!var. aculeatiflorus@var. \textit{aculeatiflorus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺花懸鉤子&T2_new_value=true&fr=y}}{刺花懸鉤子}\index{刺花懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+taitoensis+var.+taitoensis}{\textit{R. taitoensis} Hayata var. \textit{taitoensis}}  \index{Rubus@\textit{Rubus}!taitoensis@\textit{taitoensis}!var. taitoensis@var. \textit{taitoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東刺花懸鉤子&T2_new_value=true&fr=y}}{臺東刺花懸鉤子}\index{臺東刺花懸鉤子}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+taiwanicolus}{\textit{R. taiwanicolus} Koidz. \& Ohwi}  \index{Rubus@\textit{Rubus}!taiwanicolus@\textit{taiwanicolus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣莓&T2_new_value=true&fr=y}}{臺灣莓}\index{臺灣莓}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+trianthus}{\textit{R. trianthus} Focke}  \index{Rubus@\textit{Rubus}!trianthus@\textit{trianthus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苦懸鉤子&T2_new_value=true&fr=y}}{苦懸鉤子}\index{苦懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+wallichianus}{\textit{R. wallichianus} Wight \& Arnott}  \index{Rubus@\textit{Rubus}!wallichianus@\textit{wallichianus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鬼懸鉤子&T2_new_value=true&fr=y}}{鬼懸鉤子}\index{鬼懸鉤子} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+yuliensis}{\textit{R. yuliensis} Y.C.Liu \& F.Y.Lu}  \index{Rubus@\textit{Rubus}!yuliensis@\textit{yuliensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉里懸鉤子&T2_new_value=true&fr=y}}{玉里懸鉤子}\index{玉里懸鉤子} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubus+×parvifraxinifolius}{\textit{R. ×parvifraxinifolius} Hayata}  \index{Rubus@\textit{Rubus}!×parvifraxinifolius@\textit{×parvifraxinifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小梣葉懸鉤子&T2_new_value=true&fr=y}}{小梣葉懸鉤子}\index{小梣葉懸鉤子} NA$^h$
  \end{itemize}
 \item[] \textit{Sanguisorba} 地榆屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sanguisorba+officinalis+var.+longifolia}{\textit{S. officinalis} L. var. \textit{longifolia} (Bertol.) T.T.Yu \& C.L.Li}  \index{Sanguisorba@\textit{Sanguisorba}!officinalis@\textit{officinalis}!var. longifolia@\textbf{var. \textit{longifolia}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣地榆&T2_new_value=true&fr=y}}{臺灣地榆}\index{臺灣地榆@{\Song{臺灣地榆}}} CR
  \end{itemize}
 \item[] \textit{Sibbaldia} 五蕊莓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sibbaldia+procumbens}{\textit{S. procumbens} L.}  \index{Sibbaldia@\textit{Sibbaldia}!procumbens@\textit{procumbens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=五蕊莓&T2_new_value=true&fr=y}}{五蕊莓}\index{五蕊莓} LC
  \end{itemize}
 \item[] \textit{Sorbus} 花楸屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sorbus+randaiensis}{\textit{S. randaiensis} (Hayata) Koidz.}  \index{Sorbus@\textit{Sorbus}!randaiensis@\textit{randaiensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巒大花楸&T2_new_value=true&fr=y}}{巒大花楸}\index{巒大花楸}\# LC
  \end{itemize}
 \item[] \textit{Spiraea} 繡線菊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+formosana}{\textit{S. formosana} Hayata}  \index{Spiraea@\textit{Spiraea}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣繡線菊&T2_new_value=true&fr=y}}{臺灣繡線菊}\index{臺灣繡線菊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+hayatana}{\textit{S. hayatana} H.L.Li}  \index{Spiraea@\textit{Spiraea}!hayatana@\textit{hayatana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假繡線菊&T2_new_value=true&fr=y}}{假繡線菊}\index{假繡線菊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+morrisonicola}{\textit{S. morrisonicola} Hayata}  \index{Spiraea@\textit{Spiraea}!morrisonicola@\textit{morrisonicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山繡線菊&T2_new_value=true&fr=y}}{玉山繡線菊}\index{玉山繡線菊}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+prunifolia+var.+pseudoprunifolia}{\textit{S. prunifolia} Siebold \& Zucc. var. \textit{pseudoprunifolia} (Hayata) H.L.Li}  \index{Spiraea@\textit{Spiraea}!prunifolia@\textit{prunifolia}!var. pseudoprunifolia@var. \textit{pseudoprunifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=笑靨花&T2_new_value=true&fr=y}}{笑靨花}\index{笑靨花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+tarokoensis}{\textit{S. tarokoensis} Hayata}  \index{Spiraea@\textit{Spiraea}!tarokoensis@\textbf{\textit{tarokoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣繡線菊&T2_new_value=true&fr=y}}{太魯閣繡線菊}\index{太魯閣繡線菊@{\Song{太魯閣繡線菊}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spiraea+tatakaensis}{\textit{S. tatakaensis} I.S.Chen}  \index{Spiraea@\textit{Spiraea}!tatakaensis@\textbf{\textit{tatakaensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=塔塔加繡線菊&T2_new_value=true&fr=y}}{塔塔加繡線菊}\index{塔塔加繡線菊@{\Song{塔塔加繡線菊}}}\# VU
  \end{itemize}
 \item[] \textit{Stephanandra} 冠蕊木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Stephanandra+incisa}{\textit{S. incisa} (Thunb.) Zabel}  \index{Stephanandra@\textit{Stephanandra}!incisa@\textbf{\textit{incisa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=冠蕊木&T2_new_value=true&fr=y}}{冠蕊木}\index{冠蕊木@{\Song{冠蕊木}}} VU
  \end{itemize}
  \end{itemize}
