
  \begin{itemize}
 \item[] \textit{Argostemma} 水冠草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Argostemma+solaniflorum}{\textit{A. solaniflorum} Elmer}  \index{Argostemma@\textit{Argostemma}!solaniflorum@\textbf{\textit{solaniflorum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水冠草&T2_new_value=true&fr=y}}{水冠草}\index{水冠草@{\Song{水冠草}}} VU
  \end{itemize}
 \item[] \textit{Borreria} 豐花草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Borreria+laevis}{\textit{B. laevis} (Lamk.) Grieseb.}  \index{Borreria@\textit{Borreria}!laevis@\textit{laevis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小破得力&T2_new_value=true&fr=y}}{小破得力}\index{小破得力} NA$^n$
  \end{itemize}
 \item[] \textit{Canthium} 朴萊木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Canthium+gynochodes}{\textit{C. gynochodes} Baill.}  \index{Canthium@\textit{Canthium}!gynochodes@\textit{gynochodes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=朴萊木&T2_new_value=true&fr=y}}{朴萊木}\index{朴萊木} NT
  \end{itemize}
 \item[] \textit{Cephalanthus} 風箱樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalanthus+tetrandrus}{\textit{C. tetrandrus} (Roxb.) Ridsdale \& Bakh. f.}  \index{Cephalanthus@\textit{Cephalanthus}!tetrandrus@\textbf{\textit{tetrandrus}}}  \index{Cephalanthus@\textit{Cephalanthus}!naucleoides@\textit{naucleoides}{\\\noindent(= \textit{Cephalanthus tetrandrus})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=風箱樹&T2_new_value=true&fr=y}}{風箱樹}\index{風箱樹@{\Song{風箱樹}}} CR
  \end{itemize}
 \item[] \textit{Coptosapelta} 瓢簞藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Coptosapelta+diffusa}{\textit{C. diffusa} (Champ. ex Benth.) Steenis}  \index{Coptosapelta@\textit{Coptosapelta}!diffusa@\textit{diffusa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=瓢簞藤&T2_new_value=true&fr=y}}{瓢簞藤}\index{瓢簞藤} LC
  \end{itemize}
 \item[] \textit{Damnacanthus} 伏牛花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Damnacanthus+angustifolius}{\textit{D. angustifolius} Hayata}  \index{Damnacanthus@\textit{Damnacanthus}!angustifolius@\textit{angustifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=無刺伏牛花&T2_new_value=true&fr=y}}{無刺伏牛花}\index{無刺伏牛花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Damnacanthus+indicus}{\textit{D. indicus} Gaertn.}  \index{Damnacanthus@\textit{Damnacanthus}!indicus@\textit{indicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=伏牛花&T2_new_value=true&fr=y}}{伏牛花}\index{伏牛花} LC
  \end{itemize}
 \item[] \textit{Dentella} 小牙草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dentella+repens}{\textit{D. repens} (L.) J.R.Forst. \& G.Forst.}  \index{Dentella@\textit{Dentella}!repens@\textit{repens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小牙草&T2_new_value=true&fr=y}}{小牙草}\index{小牙草} LC
  \end{itemize}
 \item[] \textit{Diodia} 鈕扣草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diodia+teres}{\textit{D. teres} Walt.}  \index{Diodia@\textit{Diodia}!teres@\textit{teres}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓莖鈕釦草&T2_new_value=true&fr=y}}{圓莖鈕釦草}\index{圓莖鈕釦草} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Diodia+virginiana}{\textit{D. virginiana} L.}  \index{Diodia@\textit{Diodia}!virginiana@\textit{virginiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=維州鈕釦草&T2_new_value=true&fr=y}}{維州鈕釦草}\index{維州鈕釦草} NA$^n$
  \end{itemize}
 \item[] \textit{Galium} 豬殃殃屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+echinocarpum}{\textit{G. echinocarpum} Hayata}  \index{Galium@\textit{Galium}!echinocarpum@\textit{echinocarpum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺果豬殃殃&T2_new_value=true&fr=y}}{刺果豬殃殃}\index{刺果豬殃殃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+formosense}{\textit{G. formosense} Ohwi}  \index{Galium@\textit{Galium}!formosense@\textit{formosense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉豬殃殃&T2_new_value=true&fr=y}}{圓葉豬殃殃}\index{圓葉豬殃殃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+fukuyamai}{\textit{G. fukuyamai} Masam.}  \index{Galium@\textit{Galium}!fukuyamai@\textbf{\textit{fukuyamai}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=福山氏豬殃殃&T2_new_value=true&fr=y}}{福山氏豬殃殃}\index{福山氏豬殃殃@{\Song{福山氏豬殃殃}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+gracilens}{\textit{G. gracilens} (A.Gray) Makino}  \index{Galium@\textit{Galium}!gracilens@\textit{gracilens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球豬殃殃&T2_new_value=true&fr=y}}{琉球豬殃殃}\index{琉球豬殃殃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+morii}{\textit{G. morii} Hayata}  \index{Galium@\textit{Galium}!morii@\textbf{\textit{morii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏豬殃殃&T2_new_value=true&fr=y}}{森氏豬殃殃}\index{森氏豬殃殃@{\Song{森氏豬殃殃}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+nankotaizanum}{\textit{G. nankotaizanum} Ohwi}  \index{Galium@\textit{Galium}!nankotaizanum@\textbf{\textit{nankotaizanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南湖大山豬殃殃&T2_new_value=true&fr=y}}{南湖大山豬殃殃}\index{南湖大山豬殃殃@{\Song{南湖大山豬殃殃}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+paradoxum}{\textit{G. paradoxum} Maxim.}  \index{Galium@\textit{Galium}!paradoxum@\textit{paradoxum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=林猪殃殃&T2_new_value=true&fr=y}}{林猪殃殃}\index{林猪殃殃} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+spurium}{\textit{G. spurium} L.}  \index{Galium@\textit{Galium}!spurium@\textit{spurium}}  \index{Galium@\textit{Galium}!spurium@\textit{spurium}{\\\noindent(= \textit{Galium spurium})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=豬殃殃&T2_new_value=true&fr=y}}{豬殃殃}\index{豬殃殃} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+taiwanense}{\textit{G. taiwanense} Masam.}  \index{Galium@\textit{Galium}!taiwanense@\textit{taiwanense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣豬殃殃&T2_new_value=true&fr=y}}{臺灣豬殃殃}\index{臺灣豬殃殃}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+tarokoense}{\textit{G. tarokoense} Hayata}  \index{Galium@\textit{Galium}!tarokoense@\textbf{\textit{tarokoense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=太魯閣豬殃殃&T2_new_value=true&fr=y}}{太魯閣豬殃殃}\index{太魯閣豬殃殃@{\Song{太魯閣豬殃殃}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Galium+trifidum}{\textit{G. trifidum} L.}  \index{Galium@\textit{Galium}!trifidum@\textit{trifidum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉四葉葎&T2_new_value=true&fr=y}}{小葉四葉葎}\index{小葉四葉葎} NT
  \end{itemize}
 \item[] \textit{Gardenia} 黃梔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gardenia+jasminoides}{\textit{G. jasminoides} Ellis}  \index{Gardenia@\textit{Gardenia}!jasminoides@\textit{jasminoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山黃梔&T2_new_value=true&fr=y}}{山黃梔}\index{山黃梔} LC
  \end{itemize}
 \item[] \textit{Geophila} 苞花蔓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Geophila+repens}{\textit{G. repens} (L.) I.M. Johnst.}  \index{Geophila@\textit{Geophila}!repens@\textit{repens}}  \index{Geophila@\textit{Geophila}!herbacea@\textit{herbacea}{\\\noindent(= \textit{Geophila repens})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=苞花蔓&T2_new_value=true&fr=y}}{苞花蔓}\index{苞花蔓} LC
  \end{itemize}
 \item[] \textit{Guettarda} 葛塔德木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Guettarda+speciosa}{\textit{G. speciosa} L.}  \index{Guettarda@\textit{Guettarda}!speciosa@\textit{speciosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=葛塔德木&T2_new_value=true&fr=y}}{葛塔德木}\index{葛塔德木} LC
  \end{itemize}
 \item[] \textit{Hedyotis} 耳草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+biflora}{\textit{H. biflora} (L.) Lam.}  \index{Hedyotis@\textit{Hedyotis}!biflora@\textit{biflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙花耳草&T2_new_value=true&fr=y}}{雙花耳草}\index{雙花耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+brachypoda}{\textit{H. brachypoda} (DC.) Sivar. \& Biju}  \index{Hedyotis@\textit{Hedyotis}!brachypoda@\textit{brachypoda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬定經草&T2_new_value=true&fr=y}}{擬定經草}\index{擬定經草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+butensis}{\textit{H. butensis} Masam.}  \index{Hedyotis@\textit{Hedyotis}!butensis@\textit{butensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭涼喉茶&T2_new_value=true&fr=y}}{臭涼喉茶}\index{臭涼喉茶}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+chrysotricha}{\textit{H. chrysotricha} (Palib.) Merr.}  \index{Hedyotis@\textit{Hedyotis}!chrysotricha@\textbf{\textit{chrysotricha}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金毛耳草&T2_new_value=true&fr=y}}{金毛耳草}\index{金毛耳草@{\Song{金毛耳草}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+corymbosa}{\textit{H. corymbosa} (L.) Lam.}  \index{Hedyotis@\textit{Hedyotis}!corymbosa@\textit{corymbosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=繖花龍吐珠&T2_new_value=true&fr=y}}{繖花龍吐珠}\index{繖花龍吐珠} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+diffusa}{\textit{H. diffusa} Willd.}  \index{Hedyotis@\textit{Hedyotis}!diffusa@\textit{diffusa}}  \index{Hedyotis@\textit{Hedyotis}!diffusa@\textit{diffusa}{\\\noindent(= \textit{Hedyotis diffusa})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=定經草&T2_new_value=true&fr=y}}{定經草}\index{定經草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+hedyotidea}{\textit{H. hedyotidea} (DC.) Merr.}  \index{Hedyotis@\textit{Hedyotis}!hedyotidea@\textit{hedyotidea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南投涼喉茶&T2_new_value=true&fr=y}}{南投涼喉茶}\index{南投涼喉茶} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+koana}{\textit{H. koana} R.J.Wang}  \index{Hedyotis@\textit{Hedyotis}!koana@\textit{koana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘊璋耳草&T2_new_value=true&fr=y}}{蘊璋耳草}\index{蘊璋耳草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+pinifolia}{\textit{H. pinifolia} Wall. ex G.Don}  \index{Hedyotis@\textit{Hedyotis}!pinifolia@\textit{pinifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=松葉耳草&T2_new_value=true&fr=y}}{松葉耳草}\index{松葉耳草} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+strigulosa+var.+parvifolia}{\textit{H. strigulosa} Bartl. ex DC. var. \textit{parvifolia} (Hook. \& Arn.) T.Yamaz.}  \index{Hedyotis@\textit{Hedyotis}!strigulosa@\textit{strigulosa}!var. parvifolia@var. \textit{parvifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=脈耳草&T2_new_value=true&fr=y}}{脈耳草}\index{脈耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+tenelliflora}{\textit{H. tenelliflora} Blume}  \index{Hedyotis@\textit{Hedyotis}!tenelliflora@\textit{tenelliflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=纖花耳草&T2_new_value=true&fr=y}}{纖花耳草}\index{纖花耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+uncinella}{\textit{H. uncinella} Hook. \& Arn.}  \index{Hedyotis@\textit{Hedyotis}!uncinella@\textit{uncinella}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長節耳草&T2_new_value=true&fr=y}}{長節耳草}\index{長節耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedyotis+verticillata}{\textit{H. verticillata} (L.) Lam.}  \index{Hedyotis@\textit{Hedyotis}!verticillata@\textit{verticillata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗葉耳草&T2_new_value=true&fr=y}}{粗葉耳草}\index{粗葉耳草} NT
  \end{itemize}
 \item[] \textit{Ixora} 仙丹花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ixora+philippinensis}{\textit{I. philippinensis} Merr.}  \index{Ixora@\textit{Ixora}!philippinensis@\textbf{\textit{philippinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小仙丹花&T2_new_value=true&fr=y}}{小仙丹花}\index{小仙丹花@{\Song{小仙丹花}}} EN
  \end{itemize}
 \item[] \textit{Knoxia} 諾氏草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Knoxia+corymbosa}{\textit{K. corymbosa} Willd.}  \index{Knoxia@\textit{Knoxia}!corymbosa@\textit{corymbosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=諾氏草&T2_new_value=true&fr=y}}{諾氏草}\index{諾氏草} NT
  \end{itemize}
 \item[] \textit{Lasianthus} 雞屎樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+appressihirtus+var.+appressihirtus}{\textit{L. appressihirtus} Simizu var. \textit{appressihirtus}}  \index{Lasianthus@\textit{Lasianthus}!appressihirtus@\textit{appressihirtus}!var. appressihirtus@var. \textit{appressihirtus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密毛雞屎樹&T2_new_value=true&fr=y}}{密毛雞屎樹}\index{密毛雞屎樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+appressihirtus+var.+maximus}{\textit{L. appressihirtus} Simizu var. \textit{maximus} Simizu ex T.S.Liu \& J.M.Chao}  \index{Lasianthus@\textit{Lasianthus}!appressihirtus@\textit{appressihirtus}!var. maximus@var. \textit{maximus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉密毛雞屎樹&T2_new_value=true&fr=y}}{大葉密毛雞屎樹}\index{大葉密毛雞屎樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+bunzanensis}{\textit{L. bunzanensis} Simizu}  \index{Lasianthus@\textit{Lasianthus}!bunzanensis@\textit{bunzanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=文山雞屎樹&T2_new_value=true&fr=y}}{文山雞屎樹}\index{文山雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+chinensis}{\textit{L. chinensis} (Champ. ex Benth.) Benth.}  \index{Lasianthus@\textit{Lasianthus}!chinensis@\textbf{\textit{chinensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白果雞屎樹&T2_new_value=true&fr=y}}{白果雞屎樹}\index{白果雞屎樹@{\Song{白果雞屎樹}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+curtisii}{\textit{L. curtisii} King \& Gamble}  \index{Lasianthus@\textit{Lasianthus}!curtisii@\textit{curtisii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柯氏雞屎樹&T2_new_value=true&fr=y}}{柯氏雞屎樹}\index{柯氏雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+cyanocarpus}{\textit{L. cyanocarpus} Jack}  \index{Lasianthus@\textit{Lasianthus}!cyanocarpus@\textit{cyanocarpus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛雞屎樹&T2_new_value=true&fr=y}}{毛雞屎樹}\index{毛雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+fordii}{\textit{L. fordii} Hance}  \index{Lasianthus@\textit{Lasianthus}!fordii@\textit{fordii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球雞屎樹&T2_new_value=true&fr=y}}{琉球雞屎樹}\index{琉球雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+formosensis}{\textit{L. formosensis} Matsum.}  \index{Lasianthus@\textit{Lasianthus}!formosensis@\textit{formosensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣雞屎樹&T2_new_value=true&fr=y}}{臺灣雞屎樹}\index{臺灣雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+hiiranensis}{\textit{L. hiiranensis} Hayata}  \index{Lasianthus@\textit{Lasianthus}!hiiranensis@\textbf{\textit{hiiranensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=棲蘭山雞屎樹&T2_new_value=true&fr=y}}{棲蘭山雞屎樹}\index{棲蘭山雞屎樹@{\Song{棲蘭山雞屎樹}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+japonicus+var.+japonicus}{\textit{L. japonicus} Miq. var. \textit{japonicus}}  \index{Lasianthus@\textit{Lasianthus}!japonicus@\textit{japonicus}!var. japonicus@var. \textit{japonicus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本雞屎樹&T2_new_value=true&fr=y}}{日本雞屎樹}\index{日本雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+japonicus+var.+satsumensis}{\textit{L. japonicus} Miq. var. \textit{satsumensis} (Matsum.) Makino}  \index{Lasianthus@\textit{Lasianthus}!japonicus@\textit{japonicus}!var. satsumensis@var. \textit{satsumensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗毛日本雞屎樹&T2_new_value=true&fr=y}}{粗毛日本雞屎樹}\index{粗毛日本雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+microphyllus}{\textit{L. microphyllus} Elmer}  \index{Lasianthus@\textit{Lasianthus}!microphyllus@\textit{microphyllus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉雞屎樹&T2_new_value=true&fr=y}}{小葉雞屎樹}\index{小葉雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+microstachys}{\textit{L. microstachys} Hayata}  \index{Lasianthus@\textit{Lasianthus}!microstachys@\textit{microstachys}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉雞屎樹&T2_new_value=true&fr=y}}{薄葉雞屎樹}\index{薄葉雞屎樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+obliquinervis+var.+obliquinervis}{\textit{L. obliquinervis} Merr. var. \textit{obliquinervis}}  \index{Lasianthus@\textit{Lasianthus}!obliquinervis@\textit{obliquinervis}!var. obliquinervis@var. \textit{obliquinervis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞屎樹&T2_new_value=true&fr=y}}{雞屎樹}\index{雞屎樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+obliquinervis+var.+simizui}{\textit{L. obliquinervis} Merr. var. \textit{simizui} T.S.Liu \& J.M.Chao}  \index{Lasianthus@\textit{Lasianthus}!obliquinervis@\textit{obliquinervis}!var. simizui@\textbf{var. \textit{simizui}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=清水氏雞屎樹&T2_new_value=true&fr=y}}{清水氏雞屎樹}\index{清水氏雞屎樹@{\Song{清水氏雞屎樹}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+obliquinervis+var.+taitoensis}{\textit{L. obliquinervis} Merr. var. \textit{taitoensis} (Simizu) T.S.Liu \& J.M.Chao}  \index{Lasianthus@\textit{Lasianthus}!obliquinervis@\textit{obliquinervis}!var. taitoensis@var. \textit{taitoensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺東雞屎樹&T2_new_value=true&fr=y}}{臺東雞屎樹}\index{臺東雞屎樹}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+tsangii}{\textit{L. tsangii} Merr. ex H.L.Li}  \index{Lasianthus@\textit{Lasianthus}!tsangii@\textbf{\textit{tsangii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長苞雞屎樹&T2_new_value=true&fr=y}}{長苞雞屎樹}\index{長苞雞屎樹@{\Song{長苞雞屎樹}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lasianthus+wallichii}{\textit{L. wallichii} Wight}  \index{Lasianthus@\textit{Lasianthus}!wallichii@\textit{wallichii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=圓葉雞屎樹&T2_new_value=true&fr=y}}{圓葉雞屎樹}\index{圓葉雞屎樹} LC
  \end{itemize}
 \item[] \textit{Litosanthes} 壺冠木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Litosanthes+biflora}{\textit{L. biflora} Blume}  \index{Litosanthes@\textit{Litosanthes}!biflora@\textit{biflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=壺冠木&T2_new_value=true&fr=y}}{壺冠木}\index{壺冠木} LC
  \end{itemize}
 \item[] \textit{Mitchella} 蔓虎刺屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mitchella+undulata}{\textit{M. undulata} Siebold \& Zucc.}  \index{Mitchella@\textit{Mitchella}!undulata@\textbf{\textit{undulata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓虎刺&T2_new_value=true&fr=y}}{蔓虎刺}\index{蔓虎刺@{\Song{蔓虎刺}}} VU
  \end{itemize}
 \item[] \textit{Mitracarpus} 蓋裂果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mitracarpus+hirtus}{\textit{M. hirtus} (L.) DC.}  \index{Mitracarpus@\textit{Mitracarpus}!hirtus@\textit{hirtus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蓋裂果&T2_new_value=true&fr=y}}{蓋裂果}\index{蓋裂果} NA$^n$
  \end{itemize}
 \item[] \textit{Morinda} 羊角藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Morinda+citrifolia}{\textit{M. citrifolia} L.}  \index{Morinda@\textit{Morinda}!citrifolia@\textit{citrifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=檄樹&T2_new_value=true&fr=y}}{檄樹}\index{檄樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Morinda+parvifolia}{\textit{M. parvifolia} Bartl.}  \index{Morinda@\textit{Morinda}!parvifolia@\textit{parvifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅珠藤&T2_new_value=true&fr=y}}{紅珠藤}\index{紅珠藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Morinda+umbellata}{\textit{M. umbellata} L.}  \index{Morinda@\textit{Morinda}!umbellata@\textit{umbellata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羊角藤&T2_new_value=true&fr=y}}{羊角藤}\index{羊角藤} LC
  \end{itemize}
 \item[] \textit{Mussaenda} 玉葉金花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+albiflora}{\textit{M. albiflora} Hayata}  \index{Mussaenda@\textit{Mussaenda}!albiflora@\textbf{\textit{albiflora}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水社玉葉金花&T2_new_value=true&fr=y}}{水社玉葉金花}\index{水社玉葉金花@{\Song{水社玉葉金花}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+macrophylla}{\textit{M. macrophylla} Wall.}  \index{Mussaenda@\textit{Mussaenda}!macrophylla@\textit{macrophylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉玉葉金花&T2_new_value=true&fr=y}}{大葉玉葉金花}\index{大葉玉葉金花}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+parviflora}{\textit{M. parviflora} Miq.}  \index{Mussaenda@\textit{Mussaenda}!parviflora@\textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉葉金花&T2_new_value=true&fr=y}}{玉葉金花}\index{玉葉金花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+pubescens}{\textit{M. pubescens} W.T.Aiton}  \index{Mussaenda@\textit{Mussaenda}!pubescens@\textit{pubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛玉葉金花&T2_new_value=true&fr=y}}{毛玉葉金花}\index{毛玉葉金花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+taihokuensis}{\textit{M. taihokuensis} Masam.}  \index{Mussaenda@\textit{Mussaenda}!taihokuensis@\textit{taihokuensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺北玉葉金花&T2_new_value=true&fr=y}}{臺北玉葉金花}\index{臺北玉葉金花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Mussaenda+taiwanensis}{\textit{M. taiwanensis} Kaneh.}  \index{Mussaenda@\textit{Mussaenda}!taiwanensis@\textbf{\textit{taiwanensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣玉葉金花&T2_new_value=true&fr=y}}{臺灣玉葉金花}\index{臺灣玉葉金花@{\Song{臺灣玉葉金花}}}\# VU
  \end{itemize}
 \item[] \textit{Neanotis} 新耳草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neanotis+formosana}{\textit{N. formosana} (Hayata) W.H.Lewis}  \index{Neanotis@\textit{Neanotis}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣新耳草&T2_new_value=true&fr=y}}{臺灣新耳草}\index{臺灣新耳草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neanotis+hirsuta}{\textit{N. hirsuta} (L.f.) W.H.Lewis}  \index{Neanotis@\textit{Neanotis}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=涼喉茶&T2_new_value=true&fr=y}}{涼喉茶}\index{涼喉茶} LC
  \end{itemize}
 \item[] \textit{Neonauclea} 欖仁舅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Neonauclea+reticulata}{\textit{N. reticulata} (Havil.) Merr.}  \index{Neonauclea@\textit{Neonauclea}!reticulata@\textit{reticulata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=欖仁舅&T2_new_value=true&fr=y}}{欖仁舅}\index{欖仁舅} LC
  \end{itemize}
 \item[] \textit{Nertera} 深柱夢草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nertera+granadense}{\textit{N. granadense} (Mutis ex L.f.) Druce}  \index{Nertera@\textit{Nertera}!granadense@\textit{granadense}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅果深柱夢草&T2_new_value=true&fr=y}}{紅果深柱夢草}\index{紅果深柱夢草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nertera+nigricarpa}{\textit{N. nigricarpa} Hayata}  \index{Nertera@\textit{Nertera}!nigricarpa@\textit{nigricarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=黑果深柱夢草&T2_new_value=true&fr=y}}{黑果深柱夢草}\index{黑果深柱夢草}\# LC
  \end{itemize}
 \item[] \textit{Oldenlandiopsis} 微耳草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oldenlandiopsis+callitrichoides}{\textit{O. callitrichoides} (Griseb.) Terrell \& W.H.Lewis.}  \index{Oldenlandiopsis@\textit{Oldenlandiopsis}!callitrichoides@\textit{callitrichoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=匍匐微耳草&T2_new_value=true&fr=y}}{匍匐微耳草}\index{匍匐微耳草} NA$^n$
  \end{itemize}
 \item[] \textit{Ophiorrhiza} 蛇根草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiorrhiza+hayatana}{\textit{O. hayatana} Ohwi}  \index{Ophiorrhiza@\textit{Ophiorrhiza}!hayatana@\textit{hayatana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=早田氏蛇根草&T2_new_value=true&fr=y}}{早田氏蛇根草}\index{早田氏蛇根草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiorrhiza+japonica}{\textit{O. japonica} Blume}  \index{Ophiorrhiza@\textit{Ophiorrhiza}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蛇根草&T2_new_value=true&fr=y}}{蛇根草}\index{蛇根草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiorrhiza+kuroiwae}{\textit{O. kuroiwae} Makino}  \index{Ophiorrhiza@\textit{Ophiorrhiza}!kuroiwae@\textit{kuroiwae}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小花蛇根草&T2_new_value=true&fr=y}}{小花蛇根草}\index{小花蛇根草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiorrhiza+mitchelloides}{\textit{O. mitchelloides} (Masam.) H.S.Lo}  \index{Ophiorrhiza@\textit{Ophiorrhiza}!mitchelloides@\textbf{\textit{mitchelloides}}}  \index{Hayataella@\textit{Hayataella}!michelloides@\textit{michelloides}{\\\noindent(= \textit{Ophiorrhiza mitchelloides})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉蘭草&T2_new_value=true&fr=y}}{玉蘭草}\index{玉蘭草@{\Song{玉蘭草}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ophiorrhiza+pumila}{\textit{O. pumila} Champ. ex Benth.}  \index{Ophiorrhiza@\textit{Ophiorrhiza}!pumila@\textit{pumila}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白花蛇根草&T2_new_value=true&fr=y}}{白花蛇根草}\index{白花蛇根草} LC
  \end{itemize}
 \item[] \textit{Paederia} 雞屎藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paederia+cavaleriei}{\textit{P. cavaleriei} H.Lév.}  \index{Paederia@\textit{Paederia}!cavaleriei@\textit{cavaleriei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛雞屎藤&T2_new_value=true&fr=y}}{毛雞屎藤}\index{毛雞屎藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Paederia+foetida}{\textit{P. foetida} L.}  \index{Paederia@\textit{Paederia}!foetida@\textit{foetida}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雞屎藤&T2_new_value=true&fr=y}}{雞屎藤}\index{雞屎藤} LC
  \end{itemize}
 \item[] \textit{Pavetta} 茜木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pavetta+indica}{\textit{P. indica} L.}  \index{Pavetta@\textit{Pavetta}!indica@\textbf{\textit{indica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茜木&T2_new_value=true&fr=y}}{茜木}\index{茜木@{\Song{茜木}}} CR
  \end{itemize}
 \item[] \textit{Psychotria} 九節木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psychotria+cephalophora}{\textit{P. cephalophora} Merr.}  \index{Psychotria@\textit{Psychotria}!cephalophora@\textit{cephalophora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼九節木&T2_new_value=true&fr=y}}{蘭嶼九節木}\index{蘭嶼九節木} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psychotria+manillensis}{\textit{P. manillensis} Bartl. ex DC.}  \index{Psychotria@\textit{Psychotria}!manillensis@\textit{manillensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球九節木&T2_new_value=true&fr=y}}{琉球九節木}\index{琉球九節木} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psychotria+rubra}{\textit{P. rubra} (Lour.) Poir.}  \index{Psychotria@\textit{Psychotria}!rubra@\textit{rubra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=九節木&T2_new_value=true&fr=y}}{九節木}\index{九節木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Psychotria+serpens}{\textit{P. serpens} L.}  \index{Psychotria@\textit{Psychotria}!serpens@\textit{serpens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=拎壁龍&T2_new_value=true&fr=y}}{拎壁龍}\index{拎壁龍} LC
  \end{itemize}
 \item[] \textit{Randia} 茜草樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Randia+canthioides}{\textit{R. canthioides} Champ. ex Benth.}  \index{Randia@\textit{Randia}!canthioides@\textbf{\textit{canthioides}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺北茜草樹&T2_new_value=true&fr=y}}{臺北茜草樹}\index{臺北茜草樹@{\Song{臺北茜草樹}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Randia+cochinchinensis}{\textit{R. cochinchinensis} (Lour.) Merr.}  \index{Randia@\textit{Randia}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=茜草樹&T2_new_value=true&fr=y}}{茜草樹}\index{茜草樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Randia+sinensis}{\textit{R. sinensis} (Lour.) Roem. \& Schult.}  \index{Randia@\textit{Randia}!sinensis@\textit{sinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=華茜草樹&T2_new_value=true&fr=y}}{華茜草樹}\index{華茜草樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Randia+spinosa}{\textit{R. spinosa} (Thunb.) Poir.}  \index{Randia@\textit{Randia}!spinosa@\textit{spinosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=對面花&T2_new_value=true&fr=y}}{對面花}\index{對面花} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Randia+wallichii}{\textit{R. wallichii} Hook.f.}  \index{Randia@\textit{Randia}!wallichii@\textbf{\textit{wallichii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大果玉心花&T2_new_value=true&fr=y}}{大果玉心花}\index{大果玉心花@{\Song{大果玉心花}}} VU
  \end{itemize}
 \item[] \textit{Richardia} 擬鴨舌廣屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Richardia+brasiliensis}{\textit{R. brasiliensis} Gomez}  \index{Richardia@\textit{Richardia}!brasiliensis@\textit{brasiliensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=巴西擬鴨舌癀&T2_new_value=true&fr=y}}{巴西擬鴨舌癀}\index{巴西擬鴨舌癀} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Richardia+scabra}{\textit{R. scabra} L.}  \index{Richardia@\textit{Richardia}!scabra@\textit{scabra}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬鴨舌癀&T2_new_value=true&fr=y}}{擬鴨舌癀}\index{擬鴨舌癀} NA$^n$
  \end{itemize}
 \item[] \textit{Rubia} 茜草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubia+akane+var.+akane}{\textit{R. akane} Nakai var. \textit{akane}}  \index{Rubia@\textit{Rubia}!akane@\textit{akane}!var. akane@var. \textit{akane}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅藤仔草&T2_new_value=true&fr=y}}{紅藤仔草}\index{紅藤仔草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubia+akane+var.+erecta}{\textit{R. akane} Nakai var. \textit{erecta} Masam.}  \index{Rubia@\textit{Rubia}!akane@\textit{akane}!var. erecta@var. \textit{erecta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=直立紅藤草&T2_new_value=true&fr=y}}{直立紅藤草}\index{直立紅藤草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubia+lanceolata}{\textit{R. lanceolata} Hayata}  \index{Rubia@\textit{Rubia}!lanceolata@\textit{lanceolata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=金劍草&T2_new_value=true&fr=y}}{金劍草}\index{金劍草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Rubia+linii}{\textit{R. linii} C.Y.Chao}  \index{Rubia@\textit{Rubia}!linii@\textit{linii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=林氏茜草&T2_new_value=true&fr=y}}{林氏茜草}\index{林氏茜草}\# LC
  \end{itemize}
 \item[] \textit{Serissa} 六月雪屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Serissa+serissoides}{\textit{S. serissoides} (DC.) Druce}  \index{Serissa@\textit{Serissa}!serissoides@\textit{serissoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=六月雪&T2_new_value=true&fr=y}}{六月雪}\index{六月雪} NT
  \end{itemize}
 \item[] \textit{Sherardia} 雪亞迪草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sherardia+arvensis}{\textit{S. arvensis} L.}  \index{Sherardia@\textit{Sherardia}!arvensis@\textit{arvensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雪亞迪草&T2_new_value=true&fr=y}}{雪亞迪草}\index{雪亞迪草} NA$^n$
  \end{itemize}
 \item[] \textit{Sinoadina} 水冬瓜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sinoadina+racemosa}{\textit{S. racemosa} (Siebold \& Zucc.) Ridsdale}  \index{Sinoadina@\textit{Sinoadina}!racemosa@\textit{racemosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水團花&T2_new_value=true&fr=y}}{水團花}\index{水團花} NT
  \end{itemize}
 \item[] \textit{Spermacoce} 擬鴨舌廣舅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+articularis}{\textit{S. articularis} L.f.}  \index{Spermacoce@\textit{Spermacoce}!articularis@\textit{articularis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=鴨舌癀舅&T2_new_value=true&fr=y}}{鴨舌癀舅}\index{鴨舌癀舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+assurgens}{\textit{S. assurgens} Ruiz \& Pavon}  \index{Spermacoce@\textit{Spermacoce}!assurgens@\textit{assurgens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉鴨舌癀舅&T2_new_value=true&fr=y}}{光葉鴨舌癀舅}\index{光葉鴨舌癀舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+latifolia}{\textit{S. latifolia} Aubl.}  \index{Spermacoce@\textit{Spermacoce}!latifolia@\textit{latifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=闊葉鴨舌癀舅&T2_new_value=true&fr=y}}{闊葉鴨舌癀舅}\index{闊葉鴨舌癀舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+mauritiana}{\textit{S. mauritiana} Gideon}  \index{Spermacoce@\textit{Spermacoce}!mauritiana@\textit{mauritiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蔓鴨舌癀舅&T2_new_value=true&fr=y}}{蔓鴨舌癀舅}\index{蔓鴨舌癀舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+ocymifolia}{\textit{S. ocymifolia} Willd. ex Roem. \& Schult.}  \index{Spermacoce@\textit{Spermacoce}!ocymifolia@\textit{ocymifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬鴨舌癀舅&T2_new_value=true&fr=y}}{擬鴨舌癀舅}\index{擬鴨舌癀舅} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+pusilla}{\textit{S. pusilla} Wall.}  \index{Spermacoce@\textit{Spermacoce}!pusilla@\textit{pusilla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小鴨舌癀舅&T2_new_value=true&fr=y}}{小鴨舌癀舅}\index{小鴨舌癀舅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Spermacoce+verticillata}{\textit{S. verticillata} L.}  \index{Spermacoce@\textit{Spermacoce}!verticillata@\textit{verticillata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長葉鴨舌癀&T2_new_value=true&fr=y}}{長葉鴨舌癀}\index{長葉鴨舌癀} LC
  \end{itemize}
 \item[] \textit{Tarenna} 玉心花屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tarenna+gracilipes}{\textit{T. gracilipes} (Hayata) Ohwi}  \index{Tarenna@\textit{Tarenna}!gracilipes@\textit{gracilipes}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉玉心花&T2_new_value=true&fr=y}}{薄葉玉心花}\index{薄葉玉心花}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tarenna+zeylanica}{\textit{T. zeylanica} Gaertn.}  \index{Tarenna@\textit{Tarenna}!zeylanica@\textit{zeylanica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錫蘭玉心花&T2_new_value=true&fr=y}}{錫蘭玉心花}\index{錫蘭玉心花} LC
  \end{itemize}
 \item[] \textit{Theligonum} 纖花草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Theligonum+formosanum}{\textit{T. formosanum} (Ohwi) Ohwi \& T.S.Liu}  \index{Theligonum@\textit{Theligonum}!formosanum@\textbf{\textit{formosanum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣纖花草&T2_new_value=true&fr=y}}{臺灣纖花草}\index{臺灣纖花草@{\Song{臺灣纖花草}}}\# EN
  \end{itemize}
 \item[] \textit{Timonius} 貝木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Timonius+arboreus}{\textit{T. arboreus} Elmer}  \index{Timonius@\textit{Timonius}!arboreus@\textit{arboreus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=貝木&T2_new_value=true&fr=y}}{貝木}\index{貝木} LC
  \end{itemize}
 \item[] \textit{Tricalysia} 狗骨仔屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tricalysia+dubia}{\textit{T. dubia} (Lindl.) Ohwi}  \index{Tricalysia@\textit{Tricalysia}!dubia@\textit{dubia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狗骨仔&T2_new_value=true&fr=y}}{狗骨仔}\index{狗骨仔} LC
  \end{itemize}
 \item[] \textit{Uncaria} 鉤藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uncaria+hirsuta}{\textit{U. hirsuta} Havil.}  \index{Uncaria@\textit{Uncaria}!hirsuta@\textit{hirsuta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣鉤藤&T2_new_value=true&fr=y}}{臺灣鉤藤}\index{臺灣鉤藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uncaria+lanosa+var.+appendiculata}{\textit{U. lanosa} Wall. var. \textit{appendiculata} Ridsdale}  \index{Uncaria@\textit{Uncaria}!lanosa@\textit{lanosa}!var. appendiculata@var. \textit{appendiculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春鉤藤&T2_new_value=true&fr=y}}{恆春鉤藤}\index{恆春鉤藤} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Uncaria+rhynchophylla}{\textit{U. rhynchophylla} (Miq.) Miq. ex Havil.}  \index{Uncaria@\textit{Uncaria}!rhynchophylla@\textbf{\textit{rhynchophylla}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=嘴葉鉤藤&T2_new_value=true&fr=y}}{嘴葉鉤藤}\index{嘴葉鉤藤@{\Song{嘴葉鉤藤}}} VU
  \end{itemize}
 \item[] \textit{Wendlandia} 水錦樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wendlandia+formosana}{\textit{W. formosana} Cowan}  \index{Wendlandia@\textit{Wendlandia}!formosana@\textit{formosana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水金京&T2_new_value=true&fr=y}}{水金京}\index{水金京} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wendlandia+luzoniensis}{\textit{W. luzoniensis} DC.}  \index{Wendlandia@\textit{Wendlandia}!luzoniensis@\textit{luzoniensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=呂宋水錦樹&T2_new_value=true&fr=y}}{呂宋水錦樹}\index{呂宋水錦樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Wendlandia+uvariifolia}{\textit{W. uvariifolia} Hance}  \index{Wendlandia@\textit{Wendlandia}!uvariifolia@\textit{uvariifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水錦樹&T2_new_value=true&fr=y}}{水錦樹}\index{水錦樹} LC
  \end{itemize}
  \end{itemize}
