
  \begin{itemize}
 \item[] \textit{Acronychia} 降真香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acronychia+pedunculata}{\textit{A. pedunculata} (L.) Miq.}  \index{Acronychia@\textit{Acronychia}!pedunculata@\textit{pedunculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=降真香&T2_new_value=true&fr=y}}{降真香}\index{降真香} DD
  \end{itemize}
 \item[] \textit{Boenninghausenia} 臭節草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boenninghausenia+albiflora}{\textit{B. albiflora} Rchb.}  \index{Boenninghausenia@\textit{Boenninghausenia}!albiflora@\textit{albiflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臭節草&T2_new_value=true&fr=y}}{臭節草}\index{臭節草} LC
  \end{itemize}
 \item[] \textit{Citrus} 柑橘屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Citrus+aurantium}{\textit{C. aurantium} L.}  \index{Citrus@\textit{Citrus}!aurantium@\textbf{\textit{aurantium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=來母&T2_new_value=true&fr=y}}{來母}\index{來母@{\Song{來母}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Citrus+depressa}{\textit{C. depressa} Hayata}  \index{Citrus@\textit{Citrus}!depressa@\textbf{\textit{depressa}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣香檬&T2_new_value=true&fr=y}}{臺灣香檬}\index{臺灣香檬@{\Song{臺灣香檬}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Citrus+tachibana}{\textit{C. tachibana} (Makino) Tanaka}  \index{Citrus@\textit{Citrus}!tachibana@\textit{tachibana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=橘柑&T2_new_value=true&fr=y}}{橘柑}\index{橘柑} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Citrus+taiwanica}{\textit{C. taiwanica} Tanaka \& Shimada}  \index{Citrus@\textit{Citrus}!taiwanica@\textit{taiwanica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=南庄橙&T2_new_value=true&fr=y}}{南庄橙}\index{南庄橙}\# DD
  \end{itemize}
 \item[] \textit{Clausena} 黃皮屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clausena+anisum-olens}{\textit{C. anisum-olens} (Blanco) Merr.}  \index{Clausena@\textit{Clausena}!anisum-olens@\textbf{\textit{anisum-olens}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=短柱黃皮&T2_new_value=true&fr=y}}{短柱黃皮}\index{短柱黃皮@{\Song{短柱黃皮}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Clausena+excavata}{\textit{C. excavata} Burm.f.}  \index{Clausena@\textit{Clausena}!excavata@\textit{excavata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=過山香&T2_new_value=true&fr=y}}{過山香}\index{過山香} LC
  \end{itemize}
 \item[] \textit{Glycosmis} 石苓舅屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycosmis+citrifolia}{\textit{G. citrifolia} (Willd.) Lindl.}  \index{Glycosmis@\textit{Glycosmis}!citrifolia@\textit{citrifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=石苓舅&T2_new_value=true&fr=y}}{石苓舅}\index{石苓舅} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycosmis+parviflora+var.+erythrocarpa}{\textit{G. parviflora} (Sims) Kurz. var. \textit{erythrocarpa} (Hayata) T.C.Ho}  \index{Glycosmis@\textit{Glycosmis}!parviflora@\textit{parviflora}!var. erythrocarpa@var. \textit{erythrocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長果山桔&T2_new_value=true&fr=y}}{長果山桔}\index{長果山桔} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Glycosmis+parviflora+var.+parviflora}{\textit{G. parviflora} (Sims) Kurz. var. \textit{parviflora}}  \index{Glycosmis@\textit{Glycosmis}!parviflora@\textit{parviflora}!var. parviflora@var. \textit{parviflora}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山桔&T2_new_value=true&fr=y}}{山桔}\index{山桔} NT
  \end{itemize}
 \item[] \textit{Melicope} 三腳虌屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melicope+pteleifolia}{\textit{M. pteleifolia} (Champ. ex Benth.) T.Hartley}  \index{Melicope@\textit{Melicope}!pteleifolia@\textit{pteleifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三腳虌&T2_new_value=true&fr=y}}{三腳虌}\index{三腳虌} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melicope+semecarpifolia}{\textit{M. semecarpifolia} (Merr.) T.Hartley}  \index{Melicope@\textit{Melicope}!semecarpifolia@\textit{semecarpifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山刈葉&T2_new_value=true&fr=y}}{山刈葉}\index{山刈葉} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Melicope+triphylla}{\textit{M. triphylla} (Lam.) Merr.}  \index{Melicope@\textit{Melicope}!triphylla@\textit{triphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假三腳虌&T2_new_value=true&fr=y}}{假三腳虌}\index{假三腳虌} LC
  \end{itemize}
 \item[] \textit{Murraya} 月橘屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Murraya+crenulata}{\textit{M. crenulata} (Turcz.) Oliv.}  \index{Murraya@\textit{Murraya}!crenulata@\textbf{\textit{crenulata}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼月橘&T2_new_value=true&fr=y}}{蘭嶼月橘}\index{蘭嶼月橘@{\Song{蘭嶼月橘}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Murraya+euchrestifolia}{\textit{M. euchrestifolia} Hayata}  \index{Murraya@\textit{Murraya}!euchrestifolia@\textit{euchrestifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山黃皮&T2_new_value=true&fr=y}}{山黃皮}\index{山黃皮}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Murraya+exotica}{\textit{M. exotica} L.}  \index{Murraya@\textit{Murraya}!exotica@\textit{exotica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=月橘&T2_new_value=true&fr=y}}{月橘}\index{月橘} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Murraya+paniculata+var.+omphalocarpa}{\textit{M. paniculata} (L.) Jack. var. \textit{omphalocarpa} (Hayata) Swingle}  \index{Murraya@\textit{Murraya}!paniculata@\textit{paniculata}!var. omphalocarpa@var. \textit{omphalocarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=長果月橘&T2_new_value=true&fr=y}}{長果月橘}\index{長果月橘}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Murraya+paniculata+var.+paniculata}{\textit{M. paniculata} (L.) Jack. var. \textit{paniculata}}  \index{Murraya@\textit{Murraya}!paniculata@\textit{paniculata}!var. paniculata@var. \textit{paniculata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=千里香&T2_new_value=true&fr=y}}{千里香}\index{千里香} LC
  \end{itemize}
 \item[] \textit{Phellodendron} 黃蘗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Phellodendron+amurense+var.+wilsonii}{\textit{P. amurense} Rupr. var. \textit{wilsonii} (Hayata \& Kaneh.) C.E.Chang}  \index{Phellodendron@\textit{Phellodendron}!amurense@\textit{amurense}!var. wilsonii@\textbf{var. \textit{wilsonii}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣黃蘗&T2_new_value=true&fr=y}}{臺灣黃蘗}\index{臺灣黃蘗@{\Song{臺灣黃蘗}}}\# CR
  \end{itemize}
 \item[] \textit{Severinia} 烏柑屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Severinia+buxifolia}{\textit{S. buxifolia} (Poir.) Tenore}  \index{Severinia@\textit{Severinia}!buxifolia@\textit{buxifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏柑仔&T2_new_value=true&fr=y}}{烏柑仔}\index{烏柑仔} LC
  \end{itemize}
 \item[] \textit{Skimmia} 茵芋屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Skimmia+arisanensis}{\textit{S. arisanensis} Hayata}  \index{Skimmia@\textit{Skimmia}!arisanensis@\textit{arisanensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿里山茵芋&T2_new_value=true&fr=y}}{阿里山茵芋}\index{阿里山茵芋}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Skimmia+japonica+subsp.+distincte-venulosa+var.+distincte-venulosa}{\textit{S. japonica} Thunb. subsp. \textit{distincte-venulosa} (Hayata) T.C.Ho var. \textit{distincte-venulosa} }  \index{Skimmia@\textit{Skimmia}!japonica@\textit{japonica}!subsp. distincte-venulosa var. distincte-venulosa@subsp. \textit{distincte-venulosa} var. \textit{distincte-venulosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=顯脈茵芋&T2_new_value=true&fr=y}}{顯脈茵芋}\index{顯脈茵芋}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Skimmia+japonica+subsp.+distincte-venulosa+var.+orthoclada}{\textit{S. japonica} Thunb. subsp. \textit{distincte-venulosa} (Hayata) T.C.Ho var. \textit{orthoclada} (Hayata) T.C.Ho}  \index{Skimmia@\textit{Skimmia}!japonica@\textit{japonica}!subsp. distincte-venulosa var. orthoclada@subsp. \textit{distincte-venulosa} var. \textit{orthoclada}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣茵芋&T2_new_value=true&fr=y}}{臺灣茵芋}\index{臺灣茵芋} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Skimmia+reevesiana}{\textit{S. reevesiana} Fortune}  \index{Skimmia@\textit{Skimmia}!reevesiana@\textit{reevesiana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=深紅茵芋&T2_new_value=true&fr=y}}{深紅茵芋}\index{深紅茵芋} LC
  \end{itemize}
 \item[] \textit{Tetradium} 賊仔樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetradium+glabrifolium}{\textit{T. glabrifolium} (Champ. ex Benth.) T.Hartley}  \index{Tetradium@\textit{Tetradium}!glabrifolium@\textit{glabrifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=賊仔樹&T2_new_value=true&fr=y}}{賊仔樹}\index{賊仔樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetradium+ruticarpum}{\textit{T. ruticarpum} (A.Juss.) T.Hartley}  \index{Tetradium@\textit{Tetradium}!ruticarpum@\textit{ruticarpum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=吳茱萸&T2_new_value=true&fr=y}}{吳茱萸}\index{吳茱萸} LC
  \end{itemize}
 \item[] \textit{Toddalia} 飛龍掌血屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Toddalia+asiatica}{\textit{T. asiatica} (L.) Lam.}  \index{Toddalia@\textit{Toddalia}!asiatica@\textit{asiatica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=飛龍掌血&T2_new_value=true&fr=y}}{飛龍掌血}\index{飛龍掌血} LC
  \end{itemize}
 \item[] \textit{Zanthoxylum} 花椒屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+acanthopodium}{\textit{Z. acanthopodium} DC.}  \index{Zanthoxylum@\textit{Zanthoxylum}!acanthopodium@\textbf{\textit{acanthopodium}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=岩花椒&T2_new_value=true&fr=y}}{岩花椒}\index{岩花椒@{\Song{岩花椒}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+ailanthoides+var.+ailanthoides}{\textit{Z. ailanthoides} Siebold \& Zucc. var. \textit{ailanthoides}}  \index{Zanthoxylum@\textit{Zanthoxylum}!ailanthoides@\textit{ailanthoides}!var. ailanthoides@var. \textit{ailanthoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=食茱萸&T2_new_value=true&fr=y}}{食茱萸}\index{食茱萸} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+ailanthoides+var.+pubescens}{\textit{Z. ailanthoides} Siebold \& Zucc. var. \textit{pubescens} Hatusima}  \index{Zanthoxylum@\textit{Zanthoxylum}!ailanthoides@\textit{ailanthoides}!var. pubescens@var. \textit{pubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛茱萸&T2_new_value=true&fr=y}}{毛茱萸}\index{毛茱萸} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+armatum}{\textit{Z. armatum} DC.}  \index{Zanthoxylum@\textit{Zanthoxylum}!armatum@\textit{armatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=秦椒&T2_new_value=true&fr=y}}{秦椒}\index{秦椒} RE
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+avicennae}{\textit{Z. avicennae} (Lam.) DC.}  \index{Zanthoxylum@\textit{Zanthoxylum}!avicennae@\textbf{\textit{avicennae}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=狗花椒&T2_new_value=true&fr=y}}{狗花椒}\index{狗花椒@{\Song{狗花椒}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+integrifoliolum}{\textit{Z. integrifoliolum} (Merr.) Merr.}  \index{Zanthoxylum@\textit{Zanthoxylum}!integrifoliolum@\textbf{\textit{integrifoliolum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼花椒&T2_new_value=true&fr=y}}{蘭嶼花椒}\index{蘭嶼花椒@{\Song{蘭嶼花椒}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+nitidum}{\textit{Z. nitidum} (Roxb.) DC.}  \index{Zanthoxylum@\textit{Zanthoxylum}!nitidum@\textit{nitidum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=雙面刺&T2_new_value=true&fr=y}}{雙面刺}\index{雙面刺} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+pistaciiflorum}{\textit{Z. pistaciiflorum} Hayata}  \index{Zanthoxylum@\textit{Zanthoxylum}!pistaciiflorum@\textbf{\textit{pistaciiflorum}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葉花椒&T2_new_value=true&fr=y}}{三葉花椒}\index{三葉花椒@{\Song{三葉花椒}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+scandens}{\textit{Z. scandens} Blume}  \index{Zanthoxylum@\textit{Zanthoxylum}!scandens@\textit{scandens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藤花椒&T2_new_value=true&fr=y}}{藤花椒}\index{藤花椒} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+schinifolium}{\textit{Z. schinifolium} Siebold \& Zucc.}  \index{Zanthoxylum@\textit{Zanthoxylum}!schinifolium@\textit{schinifolium}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼柄花椒&T2_new_value=true&fr=y}}{翼柄花椒}\index{翼柄花椒} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+simulans}{\textit{Z. simulans} Hance}  \index{Zanthoxylum@\textit{Zanthoxylum}!simulans@\textbf{\textit{simulans}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=刺花椒&T2_new_value=true&fr=y}}{刺花椒}\index{刺花椒@{\Song{刺花椒}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zanthoxylum+wutaiense}{\textit{Z. wutaiense} I.S.Chen}  \index{Zanthoxylum@\textit{Zanthoxylum}!wutaiense@\textbf{\textit{wutaiense}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=屏東花椒&T2_new_value=true&fr=y}}{屏東花椒}\index{屏東花椒@{\Song{屏東花椒}}}\# EN
  \end{itemize}
  \end{itemize}
