
  \begin{itemize}
 \item[] \textit{Casearia} 嘉賜木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Casearia+membranacea}{\textit{C. membranacea} Hance}  \index{Casearia@\textit{Casearia}!membranacea@\textit{membranacea}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉嘉賜木&T2_new_value=true&fr=y}}{薄葉嘉賜木}\index{薄葉嘉賜木} LC
  \end{itemize}
 \item[] \textit{Flacourtia} 羅庚果屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Flacourtia+rukam}{\textit{F. rukam} Zoll. \& Merr.}  \index{Flacourtia@\textit{Flacourtia}!rukam@\textit{rukam}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=羅庚果&T2_new_value=true&fr=y}}{羅庚果}\index{羅庚果} NT
  \end{itemize}
 \item[] \textit{Homalium} 天料木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Homalium+cochinchinensis}{\textit{H. cochinchinensis} (Lour.) Druce}  \index{Homalium@\textit{Homalium}!cochinchinensis@\textit{cochinchinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=天料木&T2_new_value=true&fr=y}}{天料木}\index{天料木} NT
  \end{itemize}
 \item[] \textit{Idesia} 山桐子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Idesia+polycarpa}{\textit{I. polycarpa} Maxim.}  \index{Idesia@\textit{Idesia}!polycarpa@\textit{polycarpa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=山桐子&T2_new_value=true&fr=y}}{山桐子}\index{山桐子} LC
  \end{itemize}
 \item[] \textit{Salix} 柳屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+fulvopubescens+var.+doii}{\textit{S. fulvopubescens} Hayata var. \textit{doii} (Hayata) K.C.Yang \& T.C.Huang}  \index{Salix@\textit{Salix}!fulvopubescens@\textit{fulvopubescens}!var. doii@var. \textit{doii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=薄葉柳&T2_new_value=true&fr=y}}{薄葉柳}\index{薄葉柳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+fulvopubescens+var.+fulvopubescens}{\textit{S. fulvopubescens} Hayata var. \textit{fulvopubescens}}  \index{Salix@\textit{Salix}!fulvopubescens@\textit{fulvopubescens}!var. fulvopubescens@var. \textit{fulvopubescens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=褐毛柳&T2_new_value=true&fr=y}}{褐毛柳}\index{褐毛柳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+fulvopubescens+var.+tagawana}{\textit{S. fulvopubescens} Hayata var. \textit{tagawana} (Koidz.) K.C.Yang \& T.C.Huang}  \index{Salix@\textit{Salix}!fulvopubescens@\textit{fulvopubescens}!var. tagawana@var. \textit{tagawana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=白毛柳&T2_new_value=true&fr=y}}{白毛柳}\index{白毛柳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+kusanoi}{\textit{S. kusanoi} (Hayata) C.K.Schneid.}  \index{Salix@\textit{Salix}!kusanoi@\textbf{\textit{kusanoi}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水社柳&T2_new_value=true&fr=y}}{水社柳}\index{水社柳@{\Song{水社柳}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+morii}{\textit{S. morii} Hayata}  \index{Salix@\textit{Salix}!morii@\textit{morii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=森氏柳&T2_new_value=true&fr=y}}{森氏柳}\index{森氏柳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+okamotoana}{\textit{S. okamotoana} Koidz.}  \index{Salix@\textit{Salix}!okamotoana@\textbf{\textit{okamotoana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=關山嶺柳&T2_new_value=true&fr=y}}{關山嶺柳}\index{關山嶺柳@{\Song{關山嶺柳}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+taiwanalpina+var.+morrisonicola}{\textit{S. taiwanalpina} Kimura var. \textit{morrisonicola} (Kimura) K.C.Yang \& T.C.Huang}  \index{Salix@\textit{Salix}!taiwanalpina@\textit{taiwanalpina}!var. morrisonicola@var. \textit{morrisonicola}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山柳&T2_new_value=true&fr=y}}{玉山柳}\index{玉山柳}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+taiwanalpina+var.+taiwanalpina}{\textit{S. taiwanalpina} Kimura var. \textit{taiwanalpina}}  \index{Salix@\textit{Salix}!taiwanalpina@\textit{taiwanalpina}!var. taiwanalpina@var. \textit{taiwanalpina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣山柳&T2_new_value=true&fr=y}}{臺灣山柳}\index{臺灣山柳}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+taiwanalpina+var.+takasagoalpina}{\textit{S. taiwanalpina} Kimura var. \textit{takasagoalpina} (Koidz.) S.S.Ying}  \index{Salix@\textit{Salix}!taiwanalpina@\textit{taiwanalpina}!var. takasagoalpina@var. \textit{takasagoalpina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山柳&T2_new_value=true&fr=y}}{高山柳}\index{高山柳}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Salix+warburgii}{\textit{S. warburgii} Seemen}  \index{Salix@\textit{Salix}!warburgii@\textit{warburgii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=水柳&T2_new_value=true&fr=y}}{水柳}\index{水柳}\# LC
  \end{itemize}
 \item[] \textit{Scolopia} 魯花樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Scolopia+oldhamii}{\textit{S. oldhamii} Hance}  \index{Scolopia@\textit{Scolopia}!oldhamii@\textit{oldhamii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=魯花樹&T2_new_value=true&fr=y}}{魯花樹}\index{魯花樹} LC
  \end{itemize}
 \item[] \textit{Xylosma} 柞木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Xylosma+congesta}{\textit{X. congesta} (Lour.) Merr.}  \index{Xylosma@\textit{Xylosma}!congesta@\textit{congesta}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=柞木&T2_new_value=true&fr=y}}{柞木}\index{柞木} LC
  \end{itemize}
  \end{itemize}
