
  \begin{itemize}
 \item[] \textit{Acer} 槭屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+albopurpurascens}{\textit{A. albopurpurascens} Hayata}  \index{Acer@\textit{Acer}!albopurpurascens@\textit{albopurpurascens}} 樟葉槭\index{樟葉槭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+buergerianum+var.+formosanum}{\textit{A. buergerianum} Miq. var. \textit{formosanum} (Hayata) Sasaki}  \index{Acer@\textit{Acer}!buergerianum@\textit{buergerianum}!var. formosanum@var. \textit{formosanum}} 臺灣三角楓\index{臺灣三角楓}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+kawakamii}{\textit{A. kawakamii} Koidz.}  \index{Acer@\textit{Acer}!kawakamii@\textit{kawakamii}} 尖葉槭\index{尖葉槭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+morrisonense}{\textit{A. morrisonense} Hayata}  \index{Acer@\textit{Acer}!morrisonense@\textit{morrisonense}} 臺灣紅榨槭\index{臺灣紅榨槭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+palmatum+var.+pubescens}{\textit{A. palmatum} Thunb. var. \textit{pubescens} H.L.Li}  \index{Acer@\textit{Acer}!palmatum@\textit{palmatum}!var. pubescens@var. \textit{pubescens}} 臺灣掌葉槭\index{臺灣掌葉槭}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Acer+serrulatum}{\textit{A. serrulatum} Hayata}  \index{Acer@\textit{Acer}!serrulatum@\textit{serrulatum}} 青楓\index{青楓}\# LC
  \end{itemize}
 \item[] \textit{Allophylus} 止宮樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Allophylus+timorensis}{\textit{A. timorensis} (DC.) Blume}  \index{Allophylus@\textit{Allophylus}!timorensis@\textit{timorensis}} 止宮樹\index{止宮樹} LC
  \end{itemize}
 \item[] \textit{Cardiospermum} 倒地鈴屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardiospermum+grandiflorum}{\textit{C. grandiflorum} Sw. }  \index{Cardiospermum@\textit{Cardiospermum}!grandiflorum@\textit{grandiflorum}} 大花倒地鈴\index{大花倒地鈴} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cardiospermum+halicacabum}{\textit{C. halicacabum} L.}  \index{Cardiospermum@\textit{Cardiospermum}!halicacabum@\textit{halicacabum}} 倒地鈴\index{倒地鈴} NA$^n$
  \end{itemize}
 \item[] \textit{Dodonaea} 車桑子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dodonaea+viscosa}{\textit{D. viscosa} (L.) Jacq.}  \index{Dodonaea@\textit{Dodonaea}!viscosa@\textit{viscosa}} 車桑子\index{車桑子} LC
  \end{itemize}
 \item[] \textit{Euphoria} 龍眼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Euphoria+longana}{\textit{E. longana} Lam.}  \index{Euphoria@\textit{Euphoria}!longana@\textit{longana}} 龍眼\index{龍眼} NA$^n$
  \end{itemize}
 \item[] \textit{Eurycorymbus} 賽欒華屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Eurycorymbus+cavaleriei}{\textit{E. cavaleriei} (H.Lév.) Rehder \& Hand.-Mazz}  \index{Eurycorymbus@\textit{Eurycorymbus}!cavaleriei@\textit{cavaleriei}} 賽欒華\index{賽欒華} LC
  \end{itemize}
 \item[] \textit{Koelreuteria} 欒樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Koelreuteria+henryi}{\textit{K. henryi} Dummer}  \index{Koelreuteria@\textit{Koelreuteria}!henryi@\textit{henryi}} 臺灣欒樹\index{臺灣欒樹}\# LC
  \end{itemize}
 \item[] \textit{Pometia} 番龍眼屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pometia+pinnata}{\textit{P. pinnata} J.R.Forst. \& G.Forst.}  \index{Pometia@\textit{Pometia}!pinnata@\textit{pinnata}} 番龍眼\index{番龍眼} LC
  \end{itemize}
 \item[] \textit{Sapindus} 無患子屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Sapindus+mukorossii}{\textit{S. mukorossii} Gaertn.}  \index{Sapindus@\textit{Sapindus}!mukorossii@\textit{mukorossii}} 無患子\index{無患子} LC
  \end{itemize}
  \end{itemize}
