
  \begin{itemize}
 \item[] \textit{Selaginella} 卷柏屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+aristata}{\textit{S. aristata} Spring}  \index{Selaginella@\textit{Selaginella}!aristata@\textit{aristata}}  \index{Selaginella@\textit{Selaginella}!leptophylla@\textit{leptophylla}{\\\noindent(= \textit{Selaginella aristata})}}   \index{Selaginella@\textit{Selaginella}!satakeana@\textit{satakeana}{\\\noindent(= \textit{Selaginella aristata})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=膜葉卷柏&T2_new_value=true&fr=y}}{膜葉卷柏}\index{膜葉卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+boninensis}{\textit{S. boninensis} Baker}  \index{Selaginella@\textit{Selaginella}!boninensis@\textit{boninensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小笠原卷柏&T2_new_value=true&fr=y}}{小笠原卷柏}\index{小笠原卷柏} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+ciliaris}{\textit{S. ciliaris} (Retz.) Spring}  \index{Selaginella@\textit{Selaginella}!ciliaris@\textit{ciliaris}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=緣毛卷柏&T2_new_value=true&fr=y}}{緣毛卷柏}\index{緣毛卷柏} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+delicatula}{\textit{S. delicatula} (Desv.) Alston}  \index{Selaginella@\textit{Selaginella}!delicatula@\textit{delicatula}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=全緣卷柏&T2_new_value=true&fr=y}}{全緣卷柏}\index{全緣卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+devolii}{\textit{S. devolii} H.M.Chang, P.F.Lu \& W.L.Chiou}  \index{Selaginella@\textit{Selaginella}!devolii@\textit{devolii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=棣氏卷柏&T2_new_value=true&fr=y}}{棣氏卷柏}\index{棣氏卷柏} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+doederleinii+subsp.+doederleinii}{\textit{S. doederleinii} Hieron. subsp. \textit{doederleinii}}  \index{Selaginella@\textit{Selaginella}!doederleinii@\textit{doederleinii}!subsp. doederleinii@subsp. \textit{doederleinii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=生根卷柏&T2_new_value=true&fr=y}}{生根卷柏}\index{生根卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+doederleinii+subsp.+trachyphylla}{\textit{S. doederleinii} Hieron. subsp. \textit{trachyphylla} (Warb.) X.C.Zhang}  \index{Selaginella@\textit{Selaginella}!doederleinii@\textit{doederleinii}!subsp. trachyphylla@subsp. \textit{trachyphylla}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粗葉卷柏&T2_new_value=true&fr=y}}{粗葉卷柏}\index{粗葉卷柏} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+helvetica+subsp.+pseudonipponica}{\textit{S. helvetica} (L.) Spring subsp. \textit{pseudonipponica} (Tagawa) H.M.Chang, W.L.Chiou \& J.C.Wang}  \index{Selaginella@\textit{Selaginella}!helvetica@\textit{helvetica}!subsp. pseudonipponica@subsp. \textit{pseudonipponica}}  \index{Selaginella@\textit{Selaginella}!pseudonipponica@\textit{pseudonipponica}{\\\noindent(= \textit{Selaginella helvetica} subsp. \textit{pseudonipponica})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬日本卷柏&T2_new_value=true&fr=y}}{擬日本卷柏}\index{擬日本卷柏}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+heterostachys}{\textit{S. heterostachys} Baker}  \index{Selaginella@\textit{Selaginella}!heterostachys@\textit{heterostachys}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=姬卷柏&T2_new_value=true&fr=y}}{姬卷柏}\index{姬卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+involvens}{\textit{S. involvens} (Sw.) Spring}  \index{Selaginella@\textit{Selaginella}!involvens@\textit{involvens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=密葉卷柏&T2_new_value=true&fr=y}}{密葉卷柏}\index{密葉卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+labordei}{\textit{S. labordei} Hieron. ex H.Christ}  \index{Selaginella@\textit{Selaginella}!labordei@\textit{labordei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=玉山卷柏&T2_new_value=true&fr=y}}{玉山卷柏}\index{玉山卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+lutchuensis}{\textit{S. lutchuensis} Koidz.}  \index{Selaginella@\textit{Selaginella}!lutchuensis@\textbf{\textit{lutchuensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=琉球卷柏&T2_new_value=true&fr=y}}{琉球卷柏}\index{琉球卷柏@{\Song{琉球卷柏}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+moellendorffii}{\textit{S. moellendorffii} Hieron.}  \index{Selaginella@\textit{Selaginella}!moellendorffii@\textit{moellendorffii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=異葉卷柏&T2_new_value=true&fr=y}}{異葉卷柏}\index{異葉卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+nipponica}{\textit{S. nipponica} Franch. \& Sav.}  \index{Selaginella@\textit{Selaginella}!nipponica@\textbf{\textit{nipponica}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=日本卷柏&T2_new_value=true&fr=y}}{日本卷柏}\index{日本卷柏@{\Song{日本卷柏}}} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+remotifolia}{\textit{S. remotifolia} Spring}  \index{Selaginella@\textit{Selaginella}!remotifolia@\textit{remotifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=疏葉卷柏&T2_new_value=true&fr=y}}{疏葉卷柏}\index{疏葉卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+repanda}{\textit{S. repanda} (Desv. ex Poir.) Spring}  \index{Selaginella@\textit{Selaginella}!repanda@\textit{repanda}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高雄卷柏&T2_new_value=true&fr=y}}{高雄卷柏}\index{高雄卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+stauntoniana}{\textit{S. stauntoniana} Spring}  \index{Selaginella@\textit{Selaginella}!stauntoniana@\textit{stauntoniana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=擬密葉卷柏&T2_new_value=true&fr=y}}{擬密葉卷柏}\index{擬密葉卷柏} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+tama-montana}{\textit{S. tama-montana} Seriz.}  \index{Selaginella@\textit{Selaginella}!tama-montana@\textit{tama-montana}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=高山卷柏&T2_new_value=true&fr=y}}{高山卷柏}\index{高山卷柏} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+tamariscina}{\textit{S. tamariscina} (P.Beauv.) Spring}  \index{Selaginella@\textit{Selaginella}!tamariscina@\textit{tamariscina}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=萬年松&T2_new_value=true&fr=y}}{萬年松}\index{萬年松} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Selaginella+uncinata}{\textit{S. uncinata} (Desv. ex Poir.) Spring}  \index{Selaginella@\textit{Selaginella}!uncinata@\textit{uncinata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=藍地柏&T2_new_value=true&fr=y}}{藍地柏}\index{藍地柏} NA$^n$
  \end{itemize}
  \end{itemize}
