
  \begin{itemize}
 \item[] \textit{Heterosmilax} 土茯苓屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Heterosmilax+septemnervia}{\textit{H. septemnervia} F.T.Wang \& T.Tang*}  \index{Heterosmilax@\textit{Heterosmilax}!septemnervia@\textit{septemnervia}} 短柱土茯苓\index{短柱土茯苓} DD
  \end{itemize}
 \item[] \textit{Smilax} 菝葜屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+arisanensis}{\textit{S. arisanensis} Hayata}  \index{Smilax@\textit{Smilax}!arisanensis@\textit{arisanensis}} 阿里山菝葜\index{阿里山菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+bockii}{\textit{S. bockii} Warb.}  \index{Smilax@\textit{Smilax}!bockii@\textit{bockii}}  \index{Heterosmilax@\textit{Heterosmilax}!indica@\textit{indica}{\\\noindent(= \textit{Smilax bockii})}}   \index{Heterosmilax@\textit{Heterosmilax}!japonica@\textit{japonica}{\\\noindent(= \textit{Smilax bockii})}} 平柄菝葜(土茯苓) \index{平柄菝葜} \index{土茯苓@{土茯苓(=平柄菝葜)}} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+bracteata+var.+bracteata}{\textit{S. bracteata} C.Presl var. \textit{bracteata}}  \index{Smilax@\textit{Smilax}!bracteata@\textit{bracteata}!var. bracteata@var. \textit{bracteata}} 假菝葜\index{假菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+bracteata+var.+verruculosa}{\textit{S. bracteata} C.Presl var. \textit{verruculosa} (Merr.) T.Koyama}  \index{Smilax@\textit{Smilax}!bracteata@\textit{bracteata}!var. verruculosa@var. \textit{verruculosa}} 糙莖菝葜\index{糙莖菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+china}{\textit{S. china} L.}  \index{Smilax@\textit{Smilax}!china@\textit{china}} 菝葜\index{菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+corbularia}{\textit{S. corbularia} Kunth}  \index{Smilax@\textit{Smilax}!corbularia@\textit{corbularia}} 裏白菝葜\index{裏白菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+discotis}{\textit{S. discotis} Warb.}  \index{Smilax@\textit{Smilax}!discotis@\textit{discotis}} 宜蘭菝葜\index{宜蘭菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+elongato-umbellata}{\textit{S. elongato-umbellata} Hayata}  \index{Smilax@\textit{Smilax}!elongato-umbellata@\textit{elongato-umbellata}} 細葉菝葜\index{細葉菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+glabra}{\textit{S. glabra} Wright}  \index{Smilax@\textit{Smilax}!glabra@\textit{glabra}} 禹餘糧\index{禹餘糧} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+hayatae}{\textit{S. hayatae} T.Koyama}  \index{Smilax@\textit{Smilax}!hayatae@\textit{hayatae}} 早田氏菝葜\index{早田氏菝葜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+horridiramula}{\textit{S. horridiramula} Hayata}  \index{Smilax@\textit{Smilax}!horridiramula@\textit{horridiramula}} 密刺菝葜\index{密刺菝葜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+insularis}{\textit{S. insularis} T.C.Hsu \& S.W.Chung}  \index{Smilax@\textit{Smilax}!insularis@\textit{insularis}} 海島土茯苓\index{海島土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+koyamae}{\textit{S. koyamae} T.C.Hsu \& S.W.Chung}  \index{Smilax@\textit{Smilax}!koyamae@\textit{koyamae}} 阿里山土茯苓\index{阿里山土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+lanceifolia}{\textit{S. lanceifolia} Roxb.}  \index{Smilax@\textit{Smilax}!lanceifolia@\textit{lanceifolia}} 臺灣土茯苓\index{臺灣土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+luei}{\textit{S. luei} T.Koyama}  \index{Smilax@\textit{Smilax}!luei@\textit{luei}} 呂氏菝葜\index{呂氏菝葜}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+menispermoidea}{\textit{S. menispermoidea} A.DC.}  \index{Smilax@\textit{Smilax}!menispermoidea@\textit{menispermoidea}} 巒大菝葜\index{巒大菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+nantoensis}{\textit{S. nantoensis} T.Koyama}  \index{Smilax@\textit{Smilax}!nantoensis@\textit{nantoensis}} 南投菝葜\index{南投菝葜}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+nipponica}{\textit{S. nipponica} Miq.}  \index{Smilax@\textit{Smilax}!nipponica@\textit{nipponica}} 日本菝葜\index{日本菝葜} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+ocreata}{\textit{S. ocreata} A.DC.}  \index{Smilax@\textit{Smilax}!ocreata@\textit{ocreata}} 耳葉菝葜\index{耳葉菝葜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+planipedunculata+var.+plenipedunculata}{\textit{S. planipedunculata} Hayata var. \textit{plenipedunculata} }  \index{Smilax@\textit{Smilax}!planipedunculata@\textit{planipedunculata}!var. plenipedunculata@var. \textit{plenipedunculata}} 平柄土茯苓\index{平柄土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+planipedunculata+var.+raishaensis}{\textit{S. planipedunculata} Hayata var. \textit{raishaensis} (Hayata) T.C.Hsu \& S.W.Chung}  \index{Smilax@\textit{Smilax}!planipedunculata@\textit{planipedunculata}!var. raishaensis@var. \textit{raishaensis}} 來社土茯苓\index{來社土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+riparia}{\textit{S. riparia} A.DC.}  \index{Smilax@\textit{Smilax}!riparia@\textit{riparia}} 大武牛尾菜\index{大武牛尾菜} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+seisuiensis}{\textit{S. seisuiensis} (Hayata) T.C.Hsu \& S.W.Chung}  \index{Smilax@\textit{Smilax}!seisuiensis@\textit{seisuiensis}}  \index{Heterosmilax@\textit{Heterosmilax}!seisuiensis@\textit{seisuiensis}{\\\noindent(= \textit{Smilax seisuiensis})}} 臺中土茯苓(臺中假土茯苓) \index{臺中土茯苓} \index{臺中假土茯苓@{臺中假土茯苓(=臺中土茯苓)}}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+sieboldii}{\textit{S. sieboldii} Miq.}  \index{Smilax@\textit{Smilax}!sieboldii@\textit{sieboldii}} 臺灣山馬薯\index{臺灣山馬薯} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+taipeiensis}{\textit{S. taipeiensis} T.C.Hsu \& S.W.Chung}  \index{Smilax@\textit{Smilax}!taipeiensis@\textit{taipeiensis}} 臺北土茯苓\index{臺北土茯苓} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Smilax+vaginata}{\textit{S. vaginata} Decne.}  \index{Smilax@\textit{Smilax}!vaginata@\textit{vaginata}} 玉山菝葜\index{玉山菝葜} LC
  \end{itemize}
  \end{itemize}
