
  \begin{itemize}
 \item[] \textit{Brugmansia} 曼陀羅木屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Brugmansia+suaveolens}{\textit{B. suaveolens} (Willd.) Bercht. \& C.Presl}  \index{Brugmansia@\textit{Brugmansia}!suaveolens@\textit{suaveolens}} 大花曼陀羅 \index{大花曼陀羅}  NA (N)
  \end{itemize}
 \item[] \textit{Capsicum} 辣椒屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Capsicum+annuum+var.+annuum}{\textit{C. annuum} L. var. \textit{annuum}}  \index{Capsicum@\textit{Capsicum}!annuum@\textit{annuum}!var. annuum@var. \textit{annuum}} 辣椒 \index{辣椒}  NA (N)
  \end{itemize}
 \item[] \textit{Cyphomandra} 樹茄屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cyphomandra+betacea}{\textit{C. betacea} (Cav.) Stendt.}  \index{Cyphomandra@\textit{Cyphomandra}!betacea@\textit{betacea}} 樹番茄 \index{樹番茄}  NA (N)
  \end{itemize}
 \item[] \textit{Datura} 曼陀羅屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Datura+innoxia}{\textit{D. innoxia} Mill.}  \index{Datura@\textit{Datura}!innoxia@\textit{innoxia}} 毛曼陀羅 \index{毛曼陀羅}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Datura+metel}{\textit{D. metel} L.}  \index{Datura@\textit{Datura}!metel@\textit{metel}} 曼陀羅 \index{曼陀羅}  NA (N)
  \end{itemize}
 \item[] \textit{Lycianthes} 紅絲線屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lycianthes+biflora}{\textit{L. biflora} (Lour.) Bitter}  \index{Lycianthes@\textit{Lycianthes}!biflora@\textit{biflora}} 雙花龍葵 \index{雙花龍葵}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lycianthes+lysimachioides}{\textit{L. lysimachioides} (Wall.) Bitter}  \index{Lycianthes@\textit{Lycianthes}!lysimachioides@\textit{lysimachioides}} 蔓茄 \index{蔓茄}  LC
  \end{itemize}
 \item[] \textit{Lycium} 枸杞屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lycium+chinense}{\textit{L. chinense} Mill.}  \index{Lycium@\textit{Lycium}!chinense@\textit{chinense}} 枸杞 \index{枸杞}  NA (N)
  \end{itemize}
 \item[] \textit{Lycopersicon} 番茄屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lycopersicon+esculentum+var.+cerasiforme}{\textit{L. esculentum} Mill. var. \textit{cerasiforme} (Dunal) A.Gray}  \index{Lycopersicon@\textit{Lycopersicon}!esculentum@\textit{esculentum}!var. cerasiforme@var. \textit{cerasiforme}} 櫻桃小番茄 \index{櫻桃小番茄}  NA (N)
  \end{itemize}
 \item[] \textit{Nicandra} 假酸漿屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nicandra+physalodes}{\textit{N. physalodes} (L.) Gaertn.}  \index{Nicandra@\textit{Nicandra}!physalodes@\textit{physalodes}} 大本炮仔草 \index{大本炮仔草}  NA (N)
  \end{itemize}
 \item[] \textit{Nicotiana} 煙草屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nicotiana+alata}{\textit{N. alata} Link \& Otto}  \index{Nicotiana@\textit{Nicotiana}!alata@\textit{alata}} 翼柄煙草 \index{翼柄煙草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nicotiana+longiflora}{\textit{N. longiflora} Cav.}  \index{Nicotiana@\textit{Nicotiana}!longiflora@\textit{longiflora}} 長花煙草 \index{長花煙草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nicotiana+plumbaginifolia}{\textit{N. plumbaginifolia} Viviani}  \index{Nicotiana@\textit{Nicotiana}!plumbaginifolia@\textit{plumbaginifolia}} 皺葉煙草 \index{皺葉煙草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nicotiana+tabacum}{\textit{N. tabacum} L.}  \index{Nicotiana@\textit{Nicotiana}!tabacum@\textit{tabacum}} 煙草 \index{煙草}  NA (N)
  \end{itemize}
 \item[] \textit{Physaliastrum} 散血丹屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Physaliastrum+chamaesarachoides}{\textit{P. chamaesarachoides} (Makino) Makino}  \index{Physaliastrum@\textit{Physaliastrum}!chamaesarachoides@\textit{chamaesarachoides}} 林氏燈籠草 \index{林氏燈籠草}  EN
  \end{itemize}
 \item[] \textit{Physalis} 酸漿屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Physalis+angulata}{\textit{P. angulata} L.}  \index{Physalis@\textit{Physalis}!angulata@\textit{angulata}} 燈籠草 \index{燈籠草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Physalis+peruviana}{\textit{P. peruviana} L.}  \index{Physalis@\textit{Physalis}!peruviana@\textit{peruviana}} 秘魯苦蘵 \index{秘魯苦蘵}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Physalis+pubescens}{\textit{P. pubescens} L.}  \index{Physalis@\textit{Physalis}!pubescens@\textit{pubescens}} 毛酸漿 \index{毛酸漿}  NA (N)
  \end{itemize}
 \item[] \textit{Solanum} 茄屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+americanum}{\textit{S. americanum} Miller}  \index{Solanum@\textit{Solanum}!americanum@\textit{americanum}} 光果龍葵 \index{光果龍葵}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+capsicoides}{\textit{S. capsicoides} All.}  \index{Solanum@\textit{Solanum}!capsicoides@\textit{capsicoides}} 刺茄 \index{刺茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+diphyllum}{\textit{S. diphyllum} L.}  \index{Solanum@\textit{Solanum}!diphyllum@\textit{diphyllum}} 瑪瑙珠 \index{瑪瑙珠}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+elaeagnifolium}{\textit{S. elaeagnifolium} Cav.}  \index{Solanum@\textit{Solanum}!elaeagnifolium@\textit{elaeagnifolium}} 銀葉茄 \index{銀葉茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+erianthum}{\textit{S. erianthum} D.Don}  \index{Solanum@\textit{Solanum}!erianthum@\textit{erianthum}} 山煙草 \index{山煙草}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+lasiocarpum}{\textit{S. lasiocarpum} Dunal}  \index{Solanum@\textit{Solanum}!lasiocarpum@\textit{lasiocarpum}} 羊不食 \index{羊不食}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+luzoniense}{\textit{S. luzoniense} Merr.}  \index{Solanum@\textit{Solanum}!luzoniense@\textit{luzoniense}} 呂宋茄 \index{呂宋茄}  CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+lyratum}{\textit{S. lyratum} Thunb.}  \index{Solanum@\textit{Solanum}!lyratum@\textit{lyratum}} 白英 \index{白英}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+macaonense}{\textit{S. macaonense} Dunal}  \index{Solanum@\textit{Solanum}!macaonense@\textit{macaonense}} 毛柱萬桃花 \index{毛柱萬桃花}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+mammosum}{\textit{S. mammosum} L.}  \index{Solanum@\textit{Solanum}!mammosum@\textit{mammosum}} 五指茄 \index{五指茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+mauritianum}{\textit{S. mauritianum} Scop.}  \index{Solanum@\textit{Solanum}!mauritianum@\textit{mauritianum}} 野煙樹 \index{野煙樹}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+miyakojimense}{\textit{S. miyakojimense} H.Yamaz. \& Takushi}  \index{Solanum@\textit{Solanum}!miyakojimense@\textit{miyakojimense}} 宮古茄 \index{宮古茄}  NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+nigrum}{\textit{S. nigrum} L.}  \index{Solanum@\textit{Solanum}!nigrum@\textit{nigrum}} 龍葵 \index{龍葵}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+peikuoensis}{\textit{S. peikuoensis} S.S.Ying}  \index{Solanum@\textit{Solanum}!peikuoensis@\textit{peikuoensis}} 白狗大山茄 \index{白狗大山茄} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+pittosporifolium}{\textit{S. pittosporifolium} Hemsl.}  \index{Solanum@\textit{Solanum}!pittosporifolium@\textit{pittosporifolium}} 玉山茄 \index{玉山茄}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+pseudocapsicum}{\textit{S. pseudocapsicum} L.}  \index{Solanum@\textit{Solanum}!pseudocapsicum@\textit{pseudocapsicum}} 珊瑚櫻 \index{珊瑚櫻}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+rostratum}{\textit{S. rostratum} Dunal}  \index{Solanum@\textit{Solanum}!rostratum@\textit{rostratum}} 壼萼刺茄 \index{壼萼刺茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+scabrum}{\textit{S. scabrum} Mill.}  \index{Solanum@\textit{Solanum}!scabrum@\textit{scabrum}} 木龍葵 \index{木龍葵}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+seaforthianum}{\textit{S. seaforthianum} Andrews}  \index{Solanum@\textit{Solanum}!seaforthianum@\textit{seaforthianum}} 星茄 \index{星茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+sisymbriifolium}{\textit{S. sisymbriifolium} Lam.}  \index{Solanum@\textit{Solanum}!sisymbriifolium@\textit{sisymbriifolium}} 擬刺茄 \index{擬刺茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+torvum}{\textit{S. torvum} Sw.}  \index{Solanum@\textit{Solanum}!torvum@\textit{torvum}} 萬桃花 \index{萬桃花}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+tuberosum}{\textit{S. tuberosum} L.}  \index{Solanum@\textit{Solanum}!tuberosum@\textit{tuberosum}} 馬鈴薯 \index{馬鈴薯}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+undatum}{\textit{S. undatum} Lam.}  \index{Solanum@\textit{Solanum}!undatum@\textit{undatum}} 黃水茄 \index{黃水茄}  VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+viarum}{\textit{S. viarum} Dunal }  \index{Solanum@\textit{Solanum}!viarum@\textit{viarum}} 毛果茄 \index{毛果茄}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Solanum+violaceum}{\textit{S. violaceum} Ortega}  \index{Solanum@\textit{Solanum}!violaceum@\textit{violaceum}} 印度茄 \index{印度茄}  LC
  \end{itemize}
 \item[] \textit{Tubocapsicum} 龍珠屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tubocapsicum+anomalum}{\textit{T. anomalum} (Franch. \& Sav.) Makino}  \index{Tubocapsicum@\textit{Tubocapsicum}!anomalum@\textit{anomalum}} 龍珠 \index{龍珠}  LC
  \end{itemize}
  \end{itemize}
