
  \begin{itemize}
 \item[] \textit{Alniphyllum} 假赤楊屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alniphyllum+pterospermum}{\textit{A. pterospermum} Matsum.}  \index{Alniphyllum@\textit{Alniphyllum}!pterospermum@\textit{pterospermum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=假赤楊&T2_new_value=true&fr=y}}{假赤楊}\index{假赤楊} LC
  \end{itemize}
 \item[] \textit{Styrax} 安息香屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styrax+formosanus+var.+formosanus}{\textit{S. formosanus} Matsum. var. \textit{formosanus}}  \index{Styrax@\textit{Styrax}!formosanus@\textit{formosanus}!var. formosanus@var. \textit{formosanus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=烏皮九芎&T2_new_value=true&fr=y}}{烏皮九芎}\index{烏皮九芎}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styrax+formosanus+var.+hayataianus}{\textit{S. formosanus} Matsum. var. \textit{hayataianus} (Perkins) H.L.Li}  \index{Styrax@\textit{Styrax}!formosanus@\textit{formosanus}!var. hayataianus@var. \textit{hayataianus}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=恆春野茉莉&T2_new_value=true&fr=y}}{恆春野茉莉}\index{恆春野茉莉}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styrax+japonicus+var.+kotoensis}{\textit{S. japonicus} Siebold \& Zucc. var. \textit{kotoensis} (Hayata) Masam. ＆ Suzuki}  \index{Styrax@\textit{Styrax}!japonicus@\textit{japonicus}!var. kotoensis@\textbf{var. \textit{kotoensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼野茉莉&T2_new_value=true&fr=y}}{蘭嶼野茉莉}\index{蘭嶼野茉莉@{\Song{蘭嶼野茉莉}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styrax+matsumuraei}{\textit{S. matsumuraei} Perkins}  \index{Styrax@\textit{Styrax}!matsumuraei@\textbf{\textit{matsumuraei}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣野茉莉&T2_new_value=true&fr=y}}{臺灣野茉莉}\index{臺灣野茉莉@{\Song{臺灣野茉莉}}}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Styrax+suberifolius}{\textit{S. suberifolius} Hook. \& Arn.}  \index{Styrax@\textit{Styrax}!suberifolius@\textit{suberifolius}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅皮&T2_new_value=true&fr=y}}{紅皮}\index{紅皮} LC
  \end{itemize}
  \end{itemize}
