
  \begin{itemize}
 \item[] \textit{Symplocos} 灰木屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+acuminata}{\textit{S. acuminata} (Blume) Miq.}  \index{Symplocos@\textit{Symplocos}!acuminata@\textit{acuminata}} 大里力灰木\index{大里力灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+arisanensis}{\textit{S. arisanensis} Hayata}  \index{Symplocos@\textit{Symplocos}!arisanensis@\textit{arisanensis}} 阿里山灰木\index{阿里山灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+caudata}{\textit{S. caudata} Wall. ex G.Don}  \index{Symplocos@\textit{Symplocos}!caudata@\textit{caudata}} 尾葉灰木\index{尾葉灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+chinensis}{\textit{S. chinensis} (Lour.) Druce}  \index{Symplocos@\textit{Symplocos}!chinensis@\textit{chinensis}} 灰木\index{灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+cochinchinensis+var.+cochinchinensis}{\textit{S. cochinchinensis} (Lour.) S.Moore var. \textit{cochinchinensis}}  \index{Symplocos@\textit{Symplocos}!cochinchinensis@\textit{cochinchinensis}!var. cochinchinensis@var. \textit{cochinchinensis}} 銹葉灰木\index{銹葉灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+cochinchinensis+var.+philippinensis}{\textit{S. cochinchinensis} (Lour.) S.Moore var. \textit{philippinensis} (Brand) Noot.}  \index{Symplocos@\textit{Symplocos}!cochinchinensis@\textit{cochinchinensis}!var. philippinensis@var. \textit{philippinensis}} 蘭嶼銹葉灰木\index{蘭嶼銹葉灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+congesta}{\textit{S. congesta} Benth.}  \index{Symplocos@\textit{Symplocos}!congesta@\textit{congesta}} 楊桐葉灰木\index{楊桐葉灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+decora}{\textit{S. decora} Hance}  \index{Symplocos@\textit{Symplocos}!decora@\textit{decora}} 小泉氏灰木\index{小泉氏灰木} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+eriostroma}{\textit{S. eriostroma} Hayata}  \index{Symplocos@\textit{Symplocos}!eriostroma@\textit{eriostroma}} 薄葉灰木\index{薄葉灰木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+formosana}{\textit{S. formosana} Brand}  \index{Symplocos@\textit{Symplocos}!formosana@\textit{formosana}} 臺灣灰木\index{臺灣灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+glauca}{\textit{S. glauca} (Thunb.) Koidz.}  \index{Symplocos@\textit{Symplocos}!glauca@\textit{glauca}} 山羊耳\index{山羊耳} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+grandis}{\textit{S. grandis} Hand.-Mazz.}  \index{Symplocos@\textit{Symplocos}!grandis@\textit{grandis}} 大葉灰木\index{大葉灰木} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+heishanensis}{\textit{S. heishanensis} Hayata}  \index{Symplocos@\textit{Symplocos}!heishanensis@\textit{heishanensis}} 平遮那灰木\index{平遮那灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+juiyenensis}{\textit{S. juiyenensis} C.C.Wang \& C.H.Ou}  \index{Symplocos@\textit{Symplocos}!juiyenensis@\textit{juiyenensis}} 瑞岩灰木\index{瑞岩灰木} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+konishii}{\textit{S. konishii} Hayata}  \index{Symplocos@\textit{Symplocos}!konishii@\textit{konishii}} 小西氏灰木\index{小西氏灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+koshunensis}{\textit{S. koshunensis} Kaneh.}  \index{Symplocos@\textit{Symplocos}!koshunensis@\textit{koshunensis}} 恆春灰木\index{恆春灰木}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+macrostroma}{\textit{S. macrostroma} Hayata}  \index{Symplocos@\textit{Symplocos}!macrostroma@\textit{macrostroma}} 大花灰木\index{大花灰木} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+migoi}{\textit{S. migoi} Nagam.}  \index{Symplocos@\textit{Symplocos}!migoi@\textit{migoi}} 擬日本灰木\index{擬日本灰木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+modesta}{\textit{S. modesta} Brand}  \index{Symplocos@\textit{Symplocos}!modesta@\textit{modesta}} 小葉白筆\index{小葉白筆}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+morrisonicola}{\textit{S. morrisonicola} Hayata}  \index{Symplocos@\textit{Symplocos}!morrisonicola@\textit{morrisonicola}} 玉山灰木\index{玉山灰木}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+nokoensis}{\textit{S. nokoensis} (Hayata) Kaneh.}  \index{Symplocos@\textit{Symplocos}!nokoensis@\textit{nokoensis}} 能高山灰木\index{能高山灰木}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+sasakii}{\textit{S. sasakii} Hayata}  \index{Symplocos@\textit{Symplocos}!sasakii@\textit{sasakii}} 佐佐木氏灰木\index{佐佐木氏灰木}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+setchuensis}{\textit{S. setchuensis} Brand}  \index{Symplocos@\textit{Symplocos}!setchuensis@\textit{setchuensis}} 四川灰木\index{四川灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+shilanensis}{\textit{S. shilanensis} Y.C.Liu \& F.Y.Lu.}  \index{Symplocos@\textit{Symplocos}!shilanensis@\textit{shilanensis}} 希蘭灰木\index{希蘭灰木}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+sonoharae}{\textit{S. sonoharae} Koidz.}  \index{Symplocos@\textit{Symplocos}!sonoharae@\textit{sonoharae}} 南嶺灰木\index{南嶺灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+stellaris}{\textit{S. stellaris} Brand}  \index{Symplocos@\textit{Symplocos}!stellaris@\textit{stellaris}} 枇杷葉灰木\index{枇杷葉灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+theophrastifolia}{\textit{S. theophrastifolia} Siebold \& Zucc.}  \index{Symplocos@\textit{Symplocos}!theophrastifolia@\textit{theophrastifolia}} 山豬肝\index{山豬肝} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+trichoclada}{\textit{S. trichoclada} Hayata}  \index{Symplocos@\textit{Symplocos}!trichoclada@\textit{trichoclada}} 褐毛灰木\index{褐毛灰木} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Symplocos+wikstroemiifolia}{\textit{S. wikstroemiifolia} Hayata}  \index{Symplocos@\textit{Symplocos}!wikstroemiifolia@\textit{wikstroemiifolia}} 月桂葉灰木\index{月桂葉灰木} LC
  \end{itemize}
  \end{itemize}
