
  \begin{itemize}
 \item[] \textit{Arthropteris}\index{Arthropteris@\textit{Arthropteris}} 爬樹蕨屬
                                
  \begin{itemize}
        \item[] \textit{A. palisotii} (Desv.) Alston \index{Arthropteris@\textit{Arthropteris}!palisotii@\textit{palisotii}} 藤蕨 \index{藤蕨}  LC
  \end{itemize}
 \item[] \textit{Pleocnemia}\index{Pleocnemia@\textit{Pleocnemia}} 黃腺羽蕨屬
                                
  \begin{itemize}
        \item[] \textit{P. rufinervis} (Hayata) Nakai \index{Pleocnemia@\textit{Pleocnemia}!rufinervis@\textit{rufinervis}} 網脈突齒蕨 \index{網脈突齒蕨}  LC
        \item[] \textit{P. winitii} Holttum \index{Pleocnemia@\textit{Pleocnemia}!winitii@\textit{winitii}} 黃腺羽蕨 \index{黃腺羽蕨}  LC
  \end{itemize}
 \item[] \textit{Pteridrys}\index{Pteridrys@\textit{Pteridrys}} 牙蕨屬
                                
  \begin{itemize}
        \item[] \textit{P. cnemidaria} (H.Christ) C.Chr. \& Ching \index{Pteridrys@\textit{Pteridrys}!cnemidaria@\textit{cnemidaria}} 長柄牙蕨 \index{長柄牙蕨}  VU
  \end{itemize}
 \item[] \textit{Tectaria}\index{Tectaria@\textit{Tectaria}} 叉蕨屬
                                
  \begin{itemize}
        \item[] \textit{T. coadunata} (Wall. ex Hook. \& Grev.) C.Chr. \index{Tectaria@\textit{Tectaria}!coadunata@\textit{coadunata}} 陰地三叉蕨 \index{陰地三叉蕨}  LC
        \item[] \textit{T. decurrens} (C.Presl) Copel. \index{Tectaria@\textit{Tectaria}!decurrens@\textit{decurrens}} 翅柄三叉蕨 \index{翅柄三叉蕨}  LC
        \item[] \textit{T. devexa} (Kunze) Copel. \index{Tectaria@\textit{Tectaria}!devexa@\textit{devexa}} 薄葉三叉蕨 \index{薄葉三叉蕨}  LC
        \item[] \textit{T. dissecta} (G.Forst.) Lellinger \index{Tectaria@\textit{Tectaria}!dissecta@\textit{dissecta}} 薄葉擬肋毛蕨 \index{薄葉擬肋毛蕨}  LC
        \item[] \textit{T. dubia} (C.B.Clarke \& Baker) Ching \index{Tectaria@\textit{Tectaria}!dubia@\textit{dubia}} 大葉三叉蕨 \index{大葉三叉蕨}  LC
        \item[] \textit{T. fauriei} Tagawa \index{Tectaria@\textit{Tectaria}!fauriei@\textit{fauriei}} 傅氏三叉蕨 \index{傅氏三叉蕨}  LC
        \item[] \textit{T. fuscipes} (Wall. ex Bedd.) C.Chr. \index{Tectaria@\textit{Tectaria}!fuscipes@\textit{fuscipes}} 屏東擬肋毛蕨 \index{屏東擬肋毛蕨}  LC
        \item[] \textit{T. griffithii} (Baker) C.Chr. \index{Tectaria@\textit{Tectaria}!griffithii@\textit{griffithii}} 葛氏三叉蕨 \index{葛氏三叉蕨}  LC
        \item[] \textit{T. harlandii} (Hook.) C.M.Kuo \index{Tectaria@\textit{Tectaria}!harlandii@\textit{harlandii}} 沙皮蕨 \index{沙皮蕨}  LC
        \item[] \textit{T. impressa} (Fée) Holtt. \index{Tectaria@\textit{Tectaria}!impressa@\textit{impressa}} 變葉三叉蕨 \index{變葉三叉蕨}  LC
        \item[] \textit{T. kusukusensis} (Hayata) Lellinger \index{Tectaria@\textit{Tectaria}!kusukusensis@\textit{kusukusensis}} 高士佛擬肋毛蕨 \index{高士佛擬肋毛蕨}  LC
        \item[] \textit{T. multicaudata} Ching \index{Tectaria@\textit{Tectaria}!multicaudata@\textit{multicaudata}} 鱗柄三叉蕨 \index{鱗柄三叉蕨}  NT
        \item[] \textit{T. phaeocaulis} (Rosenst.) C.Chr. \index{Tectaria@\textit{Tectaria}!phaeocaulis@\textit{phaeocaulis}} 蛇脈三叉蕨 \index{蛇脈三叉蕨}  LC
        \item[] \textit{T. polymorpha} (Wall. ex Hook.) Copel. \index{Tectaria@\textit{Tectaria}!polymorpha@\textit{polymorpha}} 南投三叉蕨 \index{南投三叉蕨}  LC
        \item[] \textit{T. rockii} C.Chr. \index{Tectaria@\textit{Tectaria}!rockii@\textit{rockii}} 毛三叉蕨 \index{毛三叉蕨}  DD
        \item[] \textit{T. simonsii} (Baker) Ching \index{Tectaria@\textit{Tectaria}!simonsii@\textit{simonsii}} 花蓮三叉蕨 \index{花蓮三叉蕨}  LC
        \item[] \textit{T. subfuscipes} (Tagawa) C.M.Kuo \index{Tectaria@\textit{Tectaria}!subfuscipes@\textit{subfuscipes}} 排灣三叉蕨 \index{排灣三叉蕨}  LC
        \item[] \textit{T. subtriphylla} (Hook. \& Arn.) Copel. \index{Tectaria@\textit{Tectaria}!subtriphylla@\textit{subtriphylla}} 三叉蕨 \index{三叉蕨}  LC
        \item[] \textit{T. sulitii} Copel. \index{Tectaria@\textit{Tectaria}!sulitii@\textit{sulitii}} 多羽三叉蕨 \index{多羽三叉蕨}  VU
        \item[] \textit{T. zeylanica} (Houtt.) Sledge \index{Tectaria@\textit{Tectaria}!zeylanica@\textit{zeylanica}} 地耳蕨 \index{地耳蕨}  LC
  \end{itemize}
  \end{itemize}
