
  \begin{itemize}
 \item[] \textit{Camellia} 山茶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+brevistyla}{\textit{C. brevistyla} (Hayata) Cohen-Stuart}  \index{Camellia@\textit{Camellia}!brevistyla@\textit{brevistyla}} 短柱山茶\index{短柱山茶} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+caudata}{\textit{C. caudata} Wall.}  \index{Camellia@\textit{Camellia}!caudata@\textit{caudata}} 尾葉山茶\index{尾葉山茶} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+formosensis}{\textit{C. formosensis} (Masam. \& Suzuki) M.H.Su, C.F.Hsieh \& C.H.Tsou}  \index{Camellia@\textit{Camellia}!formosensis@\textit{formosensis}}  \index{Camellia@\textit{Camellia}!sinensis@\textit{sinensis}{\\\noindent(= \textit{Camellia formosensis})}} 臺灣山茶\index{臺灣山茶}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+furfuracea}{\textit{C. furfuracea} (Merr.) Cohen-Stuart}  \index{Camellia@\textit{Camellia}!furfuracea@\textit{furfuracea}} 垢果山茶\index{垢果山茶} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+hengchunensis}{\textit{C. hengchunensis} C.E.Chang}  \index{Camellia@\textit{Camellia}!hengchunensis@\textit{hengchunensis}} 恆春山茶\index{恆春山茶}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+japonica}{\textit{C. japonica} L.}  \index{Camellia@\textit{Camellia}!japonica@\textit{japonica}} 日本山茶\index{日本山茶} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+kissi}{\textit{C. kissi} Wallich}  \index{Camellia@\textit{Camellia}!kissi@\textit{kissi}} 落瓣油茶\index{落瓣油茶} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+nokoensis}{\textit{C. nokoensis} Hayata}  \index{Camellia@\textit{Camellia}!nokoensis@\textit{nokoensis}} 能高山茶\index{能高山茶}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+salicifolia}{\textit{C. salicifolia} Champ.}  \index{Camellia@\textit{Camellia}!salicifolia@\textit{salicifolia}} 柳葉山茶\index{柳葉山茶} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+tenuifolia}{\textit{C. tenuifolia} (Hayata) Cohen-Stuart}  \index{Camellia@\textit{Camellia}!tenuifolia@\textit{tenuifolia}} 細葉山茶\index{細葉山茶}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+transarisanensis}{\textit{C. transarisanensis} (Hayata) Cohen-Stuart}  \index{Camellia@\textit{Camellia}!transarisanensis@\textit{transarisanensis}} 阿里山茶\index{阿里山茶}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+transnokoensis}{\textit{C. transnokoensis} Hayata}  \index{Camellia@\textit{Camellia}!transnokoensis@\textit{transnokoensis}} 泛能高山茶\index{泛能高山茶}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Camellia+trichoclada}{\textit{C. trichoclada} (Rehder) S.S.Chien}  \index{Camellia@\textit{Camellia}!trichoclada@\textit{trichoclada}} 毛枝連蕊茶\index{毛枝連蕊茶} VU
  \end{itemize}
 \item[] \textit{Gordonia} 大頭茶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gordonia+axillaris}{\textit{G. axillaris} (Roxb.) Dietr.}  \index{Gordonia@\textit{Gordonia}!axillaris@\textit{axillaris}} 大頭茶\index{大頭茶} LC
  \end{itemize}
 \item[] \textit{Pyrenaria} 烏皮茶屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrenaria+buisanensis}{\textit{P. buisanensis} (Sasaki) C.F.Hsieh, Sheng Z.Yang \& M.H.Su}  \index{Pyrenaria@\textit{Pyrenaria}!buisanensis@\textit{buisanensis}}  \index{Camellia@\textit{Camellia}!buisanensis@\textit{buisanensis}{\\\noindent(= \textit{Pyrenaria buisanensis})}} 武威山烏皮茶(武威山茶) \index{武威山烏皮茶} \index{武威山茶@{武威山茶(=武威山烏皮茶)}}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pyrenaria+shinkoensis}{\textit{P. shinkoensis} (Hayata) H.Keng}  \index{Pyrenaria@\textit{Pyrenaria}!shinkoensis@\textit{shinkoensis}} 烏皮茶\index{烏皮茶}\# LC
  \end{itemize}
 \item[] \textit{Schima} 木荷屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schima+superba+var.+kankaoensis}{\textit{S. superba} Gard. \& Champ. var. \textit{kankaoensis} (Hayata) H.Keng}  \index{Schima@\textit{Schima}!superba@\textit{superba}!var. kankaoensis@var. \textit{kankaoensis}} 港口木荷\index{港口木荷}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Schima+superba+var.+superba}{\textit{S. superba} Gard. \& Champ. var. \textit{superba}}  \index{Schima@\textit{Schima}!superba@\textit{superba}!var. superba@var. \textit{superba}} 木荷\index{木荷} LC
  \end{itemize}
  \end{itemize}
