
  \begin{itemize}
 \item[] \textit{Boehmeria} 苧麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+blinii+var.+podocarpa}{\textit{B. blinii} H. Lev. var. \textit{podocarpa} W.T.Wang}  \index{Boehmeria@\textit{Boehmeria}!blinii@\textit{blinii}!var. podocarpa@var. \textit{podocarpa}} 柄果苧麻\index{柄果苧麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+clidemioides}{\textit{B. clidemioides} Miq.}  \index{Boehmeria@\textit{Boehmeria}!clidemioides@\textit{clidemioides}} 序葉苧麻\index{序葉苧麻} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+densiflora}{\textit{B. densiflora} Hook. \& Arn.}  \index{Boehmeria@\textit{Boehmeria}!densiflora@\textit{densiflora}} 密花苧麻\index{密花苧麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+formosana}{\textit{B. formosana} Hayata}  \index{Boehmeria@\textit{Boehmeria}!formosana@\textit{formosana}} 臺灣苧麻\index{臺灣苧麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+hwaliensis}{\textit{B. hwaliensis} Y.C.Liu \& F.Y.Lu}  \index{Boehmeria@\textit{Boehmeria}!hwaliensis@\textit{hwaliensis}} 花蓮苧麻\index{花蓮苧麻}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+longispica}{\textit{B. longispica} Steud.}  \index{Boehmeria@\textit{Boehmeria}!longispica@\textit{longispica}} 長穗苧麻\index{長穗苧麻} EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+nivea+var.+nivea}{\textit{B. nivea} (L.) Gaudich. var. \textit{nivea}}  \index{Boehmeria@\textit{Boehmeria}!nivea@\textit{nivea}!var. nivea@var. \textit{nivea}} 苧麻\index{苧麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+nivea+var.+tenacissima}{\textit{B. nivea} (L.) Gaudich. var. \textit{tenacissima} (Gaudich.) Miq.}  \index{Boehmeria@\textit{Boehmeria}!nivea@\textit{nivea}!var. tenacissima@var. \textit{tenacissima}} 青苧麻\index{青苧麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+pilosiuscula}{\textit{B. pilosiuscula} (Blume) Hassk.}  \index{Boehmeria@\textit{Boehmeria}!pilosiuscula@\textit{pilosiuscula}} 華南苧麻\index{華南苧麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+pilushanensis}{\textit{B. pilushanensis} Y.C.Liu \& F.Y.Lu}  \index{Boehmeria@\textit{Boehmeria}!pilushanensis@\textit{pilushanensis}} 畢祿山苧麻\index{畢祿山苧麻}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Boehmeria+wattersii}{\textit{B. wattersii} (Hance) B.L.Shih \& Yuen P.Yang}  \index{Boehmeria@\textit{Boehmeria}!wattersii@\textit{wattersii}} 長葉苧麻\index{長葉苧麻}\# LC
  \end{itemize}
 \item[] \textit{Chamabainia} 蟲蟻麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Chamabainia+cuspidata}{\textit{C. cuspidata} Wight}  \index{Chamabainia@\textit{Chamabainia}!cuspidata@\textit{cuspidata}} 蟲蟻麻\index{蟲蟻麻} LC
  \end{itemize}
 \item[] \textit{Cypholophus} 瘤冠麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cypholophus+moluccanus}{\textit{C. moluccanus} (Blume) Miq.}  \index{Cypholophus@\textit{Cypholophus}!moluccanus@\textit{moluccanus}} 瘤冠麻\index{瘤冠麻} NT
  \end{itemize}
 \item[] \textit{Debregeasia} 水麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Debregeasia+orientalis}{\textit{D. orientalis} C.J.Chen}  \index{Debregeasia@\textit{Debregeasia}!orientalis@\textit{orientalis}} 水麻\index{水麻} LC
  \end{itemize}
 \item[] \textit{Dendrocnide} 咬人狗屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrocnide+kotoensis}{\textit{D. kotoensis} (Hayata ex Yamam.) B.L.Shih \& Yuen P.Yang}  \index{Dendrocnide@\textit{Dendrocnide}!kotoensis@\textit{kotoensis}} 紅頭咬人狗\index{紅頭咬人狗}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Dendrocnide+meyeniana}{\textit{D. meyeniana} (Walp.) Chew}  \index{Dendrocnide@\textit{Dendrocnide}!meyeniana@\textit{meyeniana}} 咬人狗\index{咬人狗} LC
  \end{itemize}
 \item[] \textit{Droguetia} 單蕊麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Droguetia+iners+subsp.+urticoides}{\textit{D. iners} (Forssk.) Schweinf. subsp. \textit{urticoides} (Wight) Friis \& Wilmot-Dear}  \index{Droguetia@\textit{Droguetia}!iners@\textit{iners}!subsp. urticoides@subsp. \textit{urticoides}} 單蕊麻\index{單蕊麻} NT
  \end{itemize}
 \item[] \textit{Elatostema} 樓梯草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+acuteserratum}{\textit{E. acuteserratum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!acuteserratum@\textit{acuteserratum}} 銳齒樓梯草\index{銳齒樓梯草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+cyrtandrifolium}{\textit{E. cyrtandrifolium} (Zoll. \& Moritzi) Miq.}  \index{Elatostema@\textit{Elatostema}!cyrtandrifolium@\textit{cyrtandrifolium}}  \index{Elatostema@\textit{Elatostema}!herbaceifolium@\textit{herbaceifolium}{\\\noindent(= \textit{Elatostema cyrtandrifolium})}} 臺灣樓梯草\index{臺灣樓梯草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+edule}{\textit{E. edule} C.B.Rob.}  \index{Elatostema@\textit{Elatostema}!edule@\textit{edule}} 食用樓梯草\index{食用樓梯草} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+hirtellipedunculatum}{\textit{E. hirtellipedunculatum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!hirtellipedunculatum@\textit{hirtellipedunculatum}} 糙梗樓梯草\index{糙梗樓梯草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+hypoglaucum}{\textit{E. hypoglaucum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!hypoglaucum@\textit{hypoglaucum}} 白背樓梯草\index{白背樓梯草}\# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+lineolatum+var.+majus}{\textit{E. lineolatum} Wight var. \textit{majus} Wedd.}  \index{Elatostema@\textit{Elatostema}!lineolatum@\textit{lineolatum}!var. majus@var. \textit{majus}} 冷清草\index{冷清草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+microcephalanthum}{\textit{E. microcephalanthum} Hayata}  \index{Elatostema@\textit{Elatostema}!microcephalanthum@\textit{microcephalanthum}} 微頭花樓梯草\index{微頭花樓梯草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+multicanaliculatum}{\textit{E. multicanaliculatum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!multicanaliculatum@\textit{multicanaliculatum}} 多溝樓梯草\index{多溝樓梯草}\# CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+oblongifolium}{\textit{E. oblongifolium} Fu}  \index{Elatostema@\textit{Elatostema}!oblongifolium@\textit{oblongifolium}} 長圓樓梯草\index{長圓樓梯草} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+parvum}{\textit{E. parvum} (Blume) Miq.}  \index{Elatostema@\textit{Elatostema}!parvum@\textit{parvum}} 絨莖樓梯草\index{絨莖樓梯草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+platyphylloides}{\textit{E. platyphylloides} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!platyphylloides@\textit{platyphylloides}} 闊葉樓梯草\index{闊葉樓梯草} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+rivulare}{\textit{E. rivulare} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!rivulare@\textit{rivulare}} 溪澗樓梯草\index{溪澗樓梯草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+strigillosum}{\textit{E. strigillosum} B.L.Shih \&Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!strigillosum@\textit{strigillosum}} 微粗毛樓梯草\index{微粗毛樓梯草}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+subcoriaceum}{\textit{E. subcoriaceum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!subcoriaceum@\textit{subcoriaceum}} 近革葉樓梯草\index{近革葉樓梯草}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+trilobulatum}{\textit{E. trilobulatum} (Hayata) T.Yamaz.}  \index{Elatostema@\textit{Elatostema}!trilobulatum@\textit{trilobulatum}} 裂葉樓梯草\index{裂葉樓梯草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Elatostema+villosum}{\textit{E. villosum} B.L.Shih \& Yuen P.Yang}  \index{Elatostema@\textit{Elatostema}!villosum@\textit{villosum}} 柔毛樓梯草\index{柔毛樓梯草}\# VU
  \end{itemize}
 \item[] \textit{Girardinia} 蠍子草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Girardinia+diversifolia}{\textit{G. diversifolia} (Link) Friis}  \index{Girardinia@\textit{Girardinia}!diversifolia@\textit{diversifolia}} 蠍子草\index{蠍子草} LC
  \end{itemize}
 \item[] \textit{Gonostegia} 石薯屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gonostegia+hirta}{\textit{G. hirta} (Blume) Miq.}  \index{Gonostegia@\textit{Gonostegia}!hirta@\textit{hirta}} 糯米糰\index{糯米糰} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gonostegia+matsudae}{\textit{G. matsudae} (Yamam.) Yamam. \& Masam.}  \index{Gonostegia@\textit{Gonostegia}!matsudae@\textit{matsudae}} 小葉石薯\index{小葉石薯}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Gonostegia+pentandra}{\textit{G. pentandra} (Roxb.) Miq.}  \index{Gonostegia@\textit{Gonostegia}!pentandra@\textit{pentandra}} 五蕊石薯\index{五蕊石薯} VU
  \end{itemize}
 \item[] \textit{Laportea} 桑葉麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Laportea+aestuans}{\textit{L. aestuans} (L.) Chew}  \index{Laportea@\textit{Laportea}!aestuans@\textit{aestuans}} 火焰桑葉麻\index{火焰桑葉麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Laportea+bulbifera}{\textit{L. bulbifera} (Siebold \& Zucc.) Wedd.}  \index{Laportea@\textit{Laportea}!bulbifera@\textit{bulbifera}} 珠芽桑葉麻\index{珠芽桑葉麻} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Laportea+interrupta}{\textit{L. interrupta} (L.) Chew}  \index{Laportea@\textit{Laportea}!interrupta@\textit{interrupta}} 桑葉麻\index{桑葉麻} DD
  \end{itemize}
 \item[] \textit{Lecanthus} 盤花麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Lecanthus+peduncularis}{\textit{L. peduncularis} (Wall. ex Royle) Wedd.}  \index{Lecanthus@\textit{Lecanthus}!peduncularis@\textit{peduncularis}} 長梗盤花麻\index{長梗盤花麻} LC
  \end{itemize}
 \item[] \textit{Leucosyke} 四脈麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leucosyke+quadrinervia}{\textit{L. quadrinervia} C.B.Rob.}  \index{Leucosyke@\textit{Leucosyke}!quadrinervia@\textit{quadrinervia}} 四脈麻\index{四脈麻} LC
  \end{itemize}
 \item[] \textit{Maoutia} 水絲麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Maoutia+setosa}{\textit{M. setosa} Wedd.}  \index{Maoutia@\textit{Maoutia}!setosa@\textit{setosa}} 蘭嶼水絲麻\index{蘭嶼水絲麻} LC
  \end{itemize}
 \item[] \textit{Nanocnide} 花點草屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Nanocnide+japonica}{\textit{N. japonica} Blume}  \index{Nanocnide@\textit{Nanocnide}!japonica@\textit{japonica}} 花點草\index{花點草} LC
  \end{itemize}
 \item[] \textit{Oreocnide} 紫麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreocnide+pedunculata}{\textit{O. pedunculata} (Shirai) Masam.}  \index{Oreocnide@\textit{Oreocnide}!pedunculata@\textit{pedunculata}} 長梗紫麻\index{長梗紫麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Oreocnide+trinervis}{\textit{O. trinervis} (Wedd.) Miq.}  \index{Oreocnide@\textit{Oreocnide}!trinervis@\textit{trinervis}} 三脈紫麻\index{三脈紫麻} LC
  \end{itemize}
 \item[] \textit{Pellionia} 赤車使者屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pellionia+radicans}{\textit{P. radicans} (Siebold \& Zucc.) Wedd.}  \index{Pellionia@\textit{Pellionia}!radicans@\textit{radicans}} 赤車使者\index{赤車使者} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pellionia+scabra}{\textit{P. scabra} Benth.}  \index{Pellionia@\textit{Pellionia}!scabra@\textit{scabra}} 糙葉赤車使者\index{糙葉赤車使者} LC
  \end{itemize}
 \item[] \textit{Pilea} 冷水麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+angulata}{\textit{P. angulata} (Blume) Blume}  \index{Pilea@\textit{Pilea}!angulata@\textit{angulata}} 長柄冷水麻\index{長柄冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+aquarum+subsp.+brevicornuta}{\textit{P. aquarum} Dunn subsp. \textit{brevicornuta} (Hayata) C.J.Chen}  \index{Pilea@\textit{Pilea}!aquarum@\textit{aquarum}!subsp. brevicornuta@subsp. \textit{brevicornuta}} 短角冷水麻\index{短角冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+elliptifolia}{\textit{P. elliptifolia} B.L.Shih \& Yuen P.Yang}  \index{Pilea@\textit{Pilea}!elliptifolia@\textit{elliptifolia}} 橢圓葉冷水麻\index{橢圓葉冷水麻}\# VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+funkikensis}{\textit{P. funkikensis} Hayata}  \index{Pilea@\textit{Pilea}!funkikensis@\textit{funkikensis}} 奮起湖冷水麻\index{奮起湖冷水麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+japonica}{\textit{P. japonica} (Maxim.) Hand.-Mazz.}  \index{Pilea@\textit{Pilea}!japonica@\textit{japonica}} 日本冷水麻\index{日本冷水麻} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+matsudae}{\textit{P. matsudae} Yamam.}  \index{Pilea@\textit{Pilea}!matsudae@\textit{matsudae}} 細尾冷水麻\index{細尾冷水麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+melastomoides}{\textit{P. melastomoides} (Poir.) Wedd.}  \index{Pilea@\textit{Pilea}!melastomoides@\textit{melastomoides}} 大冷水麻\index{大冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+microphylla}{\textit{P. microphylla} (L.) Liebm.}  \index{Pilea@\textit{Pilea}!microphylla@\textit{microphylla}} 小葉冷水麻\index{小葉冷水麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+nummulariifolia}{\textit{P. nummulariifolia} (Swartz) Weddell.}  \index{Pilea@\textit{Pilea}!nummulariifolia@\textit{nummulariifolia}} 古錢冷水麻\index{古錢冷水麻} NA$^n$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+peploides+var.+major}{\textit{P. peploides} (Gaudich.) Hook. \& Arn. var. \textit{major} Wedd.}  \index{Pilea@\textit{Pilea}!peploides@\textit{peploides}!var. major@var. \textit{major}} 齒葉矮冷水麻\index{齒葉矮冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+peploides+var.+peploides}{\textit{P. peploides} (Gaudich.) Hook. \& Arn. var. \textit{peploides}}  \index{Pilea@\textit{Pilea}!peploides@\textit{peploides}!var. peploides@var. \textit{peploides}} 矮冷水麻\index{矮冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+plataniflora}{\textit{P. plataniflora} C.H.Wright}  \index{Pilea@\textit{Pilea}!plataniflora@\textit{plataniflora}} 西南冷水麻\index{西南冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+pumila}{\textit{P. pumila} (L.) A.Gray}  \index{Pilea@\textit{Pilea}!pumila@\textit{pumila}} 透莖冷水麻\index{透莖冷水麻} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+rotundinucula}{\textit{P. rotundinucula} Hayata}  \index{Pilea@\textit{Pilea}!rotundinucula@\textit{rotundinucula}} 圓果冷水麻\index{圓果冷水麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+somae}{\textit{P. somae} Hayata}  \index{Pilea@\textit{Pilea}!somae@\textit{somae}} 細葉冷水麻\index{細葉冷水麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pilea+swinglei}{\textit{P. swinglei} Merr.}  \index{Pilea@\textit{Pilea}!swinglei@\textit{swinglei}} 三角葉冷水麻\index{三角葉冷水麻} DD
  \end{itemize}
 \item[] \textit{Pipturus} 落尾麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pipturus+arborescens}{\textit{P. arborescens} (Link) C.B.Rob.}  \index{Pipturus@\textit{Pipturus}!arborescens@\textit{arborescens}} 落尾麻\index{落尾麻} LC
  \end{itemize}
 \item[] \textit{Poikilospermum} 錐頭麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Poikilospermum+acuminata}{\textit{P. acuminata} (Trécul) Merr.}  \index{Poikilospermum@\textit{Poikilospermum}!acuminata@\textit{acuminata}} 錐頭麻\index{錐頭麻} EN
  \end{itemize}
 \item[] \textit{Pouzolzia} 霧水葛屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pouzolzia+elegans}{\textit{P. elegans} Wedd.}  \index{Pouzolzia@\textit{Pouzolzia}!elegans@\textit{elegans}} 水雞油\index{水雞油} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pouzolzia+taiwaniana}{\textit{P. taiwaniana} C.I Peng \& S.W.Chung}  \index{Pouzolzia@\textit{Pouzolzia}!taiwaniana@\textit{taiwaniana}} 臺灣霧水葛\index{臺灣霧水葛} CR
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Pouzolzia+zeylanica}{\textit{P. zeylanica} (L.) Benn.}  \index{Pouzolzia@\textit{Pouzolzia}!zeylanica@\textit{zeylanica}} 霧水葛\index{霧水葛} LC
  \end{itemize}
 \item[] \textit{Procris} 烏來麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Procris+laevigata}{\textit{P. laevigata} Blume}  \index{Procris@\textit{Procris}!laevigata@\textit{laevigata}} 烏來麻\index{烏來麻} LC
  \end{itemize}
 \item[] \textit{Urtica} 蕁麻屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Urtica+taiwaniana}{\textit{U. taiwaniana} S.S.Ying}  \index{Urtica@\textit{Urtica}!taiwaniana@\textit{taiwaniana}} 臺灣蕁麻\index{臺灣蕁麻}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Urtica+thunbergiana}{\textit{U. thunbergiana} Siebold \& Zucc.}  \index{Urtica@\textit{Urtica}!thunbergiana@\textit{thunbergiana}} 咬人貓\index{咬人貓} LC
  \end{itemize}
  \end{itemize}
