
  \begin{itemize}
 \item[] \textit{Ampelopsis} 山葡萄屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ampelopsis+brevipedunculata+var.+ciliata}{\textit{A. brevipedunculata} (Maxim.) Trautv. var. \textit{ciliata} (Nakai) F.Y.Lu}  \index{Ampelopsis@\textit{Ampelopsis}!brevipedunculata@\textit{brevipedunculata}!var. ciliata@var. \textit{ciliata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=毛山葡萄&T2_new_value=true&fr=y}}{毛山葡萄}\index{毛山葡萄} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ampelopsis+brevipedunculata+var.+hancei}{\textit{A. brevipedunculata} (Maxim.) Trautv. var. \textit{hancei} (Planch.) Rehder}  \index{Ampelopsis@\textit{Ampelopsis}!brevipedunculata@\textit{brevipedunculata}!var. hancei@var. \textit{hancei}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=漢氏山葡萄&T2_new_value=true&fr=y}}{漢氏山葡萄}\index{漢氏山葡萄} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ampelopsis+cantoniensis+var.+cantoniensis}{\textit{A. cantoniensis} (Hook. \& Arn.) Planch. var. \textit{cantoniensis}}  \index{Ampelopsis@\textit{Ampelopsis}!cantoniensis@\textit{cantoniensis}!var. cantoniensis@var. \textit{cantoniensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=廣東山葡萄&T2_new_value=true&fr=y}}{廣東山葡萄}\index{廣東山葡萄} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Ampelopsis+cantoniensis+var.+leecoides}{\textit{A. cantoniensis} (Hook. \& Arn.) Planch. var. \textit{leecoides} (Maxim.) F.Y.Lu}  \index{Ampelopsis@\textit{Ampelopsis}!cantoniensis@\textit{cantoniensis}!var. leecoides@var. \textit{leecoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=大葉廣東山葡萄&T2_new_value=true&fr=y}}{大葉廣東山葡萄}\index{大葉廣東山葡萄} LC
  \end{itemize}
 \item[] \textit{Cayratia} 虎葛屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cayratia+japonica}{\textit{C. japonica} (Thunb.) Gagnep.}  \index{Cayratia@\textit{Cayratia}!japonica@\textit{japonica}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=虎葛&T2_new_value=true&fr=y}}{虎葛}\index{虎葛} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cayratia+maritima}{\textit{C. maritima} B.R.Jackes}  \index{Cayratia@\textit{Cayratia}!maritima@\textit{maritima}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=海岸烏斂莓&T2_new_value=true&fr=y}}{海岸烏斂莓}\index{海岸烏斂莓} NT
  \end{itemize}
 \item[] \textit{Cissus} 粉藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissus+adnata}{\textit{C. adnata} Roxb}  \index{Cissus@\textit{Cissus}!adnata@\textit{adnata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=紅毛粉藤&T2_new_value=true&fr=y}}{紅毛粉藤}\index{紅毛粉藤} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissus+elongata}{\textit{C. elongata} Roxb.}  \index{Cissus@\textit{Cissus}!elongata@\textit{elongata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=五葉粉藤&T2_new_value=true&fr=y}}{五葉粉藤}\index{五葉粉藤} DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissus+pteroclada}{\textit{C. pteroclada} Hayata}  \index{Cissus@\textit{Cissus}!pteroclada@\textit{pteroclada}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼莖粉藤&T2_new_value=true&fr=y}}{翼莖粉藤}\index{翼莖粉藤}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissus+repens}{\textit{C. repens} Lam.}  \index{Cissus@\textit{Cissus}!repens@\textit{repens}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=粉藤&T2_new_value=true&fr=y}}{粉藤}\index{粉藤} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Cissus+sicyoides}{\textit{C. sicyoides} L.}  \index{Cissus@\textit{Cissus}!sicyoides@\textit{sicyoides}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=錦屏粉藤&T2_new_value=true&fr=y}}{錦屏粉藤}\index{錦屏粉藤} NA$^n$
  \end{itemize}
 \item[] \textit{Leea} 火筒樹屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leea+guineensis}{\textit{L. guineensis} G.Don}  \index{Leea@\textit{Leea}!guineensis@\textit{guineensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=火筒樹&T2_new_value=true&fr=y}}{火筒樹}\index{火筒樹} LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Leea+philippinensis}{\textit{L. philippinensis} Merr.}  \index{Leea@\textit{Leea}!philippinensis@\textit{philippinensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=菲律賓火筒樹&T2_new_value=true&fr=y}}{菲律賓火筒樹}\index{菲律賓火筒樹} NT
  \end{itemize}
 \item[] \textit{Parthenocissus} 地錦屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Parthenocissus+tricuspidata}{\textit{P. tricuspidata} (Siebold \& Zucc.) Planch.}  \index{Parthenocissus@\textit{Parthenocissus}!tricuspidata@\textit{tricuspidata}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=地錦&T2_new_value=true&fr=y}}{地錦}\index{地錦} LC
  \end{itemize}
 \item[] \textit{Tetrastigma} 崖爬藤屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrastigma+alatum}{\textit{T. alatum} H.L.Li}  \index{Tetrastigma@\textit{Tetrastigma}!alatum@\textit{alatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=翼柄崖爬藤&T2_new_value=true&fr=y}}{翼柄崖爬藤}\index{翼柄崖爬藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrastigma+dentatum}{\textit{T. dentatum} (Hayata) H.L.Li}  \index{Tetrastigma@\textit{Tetrastigma}!dentatum@\textit{dentatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三腳虌草&T2_new_value=true&fr=y}}{三腳虌草}\index{三腳虌草}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrastigma+formosanum}{\textit{T. formosanum} (Hemsl.) Gagnep.}  \index{Tetrastigma@\textit{Tetrastigma}!formosanum@\textit{formosanum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=三葉崖爬藤&T2_new_value=true&fr=y}}{三葉崖爬藤}\index{三葉崖爬藤}\# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrastigma+lanyuense}{\textit{T. lanyuense} C.E.Chang}  \index{Tetrastigma@\textit{Tetrastigma}!lanyuense@\textit{lanyuense}}  \index{Cissus@\textit{Cissus}!lanyuensisi@\textit{lanyuensisi}{\\\noindent(= \textit{Tetrastigma lanyuense})}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=蘭嶼崖爬藤&T2_new_value=true&fr=y}}{蘭嶼崖爬藤}\index{蘭嶼崖爬藤}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Tetrastigma+umbellatum}{\textit{T. umbellatum} (Hemsl.) Nakai}  \index{Tetrastigma@\textit{Tetrastigma}!umbellatum@\textit{umbellatum}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=臺灣崖爬藤&T2_new_value=true&fr=y}}{臺灣崖爬藤}\index{臺灣崖爬藤}\# LC
  \end{itemize}
 \item[] \textit{Vitis} 葡萄屬
                    
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+amurenensis}{\textit{V. amurenensis} Rupr.}  \index{Vitis@\textit{Vitis}!amurenensis@\textbf{\textit{amurenensis}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=阿穆爾葡萄&T2_new_value=true&fr=y}}{阿穆爾葡萄}\index{阿穆爾葡萄@{\Song{阿穆爾葡萄}}} VU
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+flexuosa}{\textit{V. flexuosa} Thunb.}  \index{Vitis@\textit{Vitis}!flexuosa@\textit{flexuosa}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=光葉葡萄&T2_new_value=true&fr=y}}{光葉葡萄}\index{光葉葡萄} NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+flexuosa+ f. +parvifolia}{\textit{V. flexuosa} Thunb.  f.  \textit{parvifolia} (Roxb.) Planch.}  \index{Vitis@\textit{Vitis}!flexuosa@\textit{flexuosa}!f. parvifolia@f. \textit{parvifolia}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉葛藟&T2_new_value=true&fr=y}}{小葉葛藟}\index{小葉葛藟} NA$^f$
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+kelungensis}{\textit{V. kelungensis} Momiy.}  \index{Vitis@\textit{Vitis}!kelungensis@\textit{kelungensis}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=基隆葡萄&T2_new_value=true&fr=y}}{基隆葡萄}\index{基隆葡萄}\# NT
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+thunbergii+var.+taiwaniana}{\textit{V. thunbergii} Siebold \& Zucc. var. \textit{taiwaniana} F.Y.Lu}  \index{Vitis@\textit{Vitis}!thunbergii@\textit{thunbergii}!var. taiwaniana@\textbf{var. \textit{taiwaniana}}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=小葉葡萄&T2_new_value=true&fr=y}}{小葉葡萄}\index{小葉葡萄@{\Song{小葉葡萄}}}\# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vitis+thunbergii+var.+thunbergii}{\textit{V. thunbergii} Siebold \& Zucc. var. \textit{thunbergii}}  \index{Vitis@\textit{Vitis}!thunbergii@\textit{thunbergii}!var. thunbergii@var. \textit{thunbergii}} \href{\detokenize{http://taibnet.sinica.edu.tw/chi/taibnet_species_list.php?T2=細本葡萄&T2_new_value=true&fr=y}}{細本葡萄}\index{細本葡萄} NT
  \end{itemize}
  \end{itemize}
