
  \begin{itemize}
 \item[] \textit{Alpinia} 月桃屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+flabellata}{\textit{A. flabellata} Ridl.}  \index{Alpinia@\textit{Alpinia}!flabellata@\textit{flabellata}} 呂宋月桃 \index{呂宋月桃}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+galanga}{\textit{A. galanga} (L.) Sw.}  \index{Alpinia@\textit{Alpinia}!galanga@\textit{galanga}} 高良薑 \index{高良薑}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+ilanensis}{\textit{A. ilanensis} S.C.Liu \& J.C.Wang}  \index{Alpinia@\textit{Alpinia}!ilanensis@\textit{ilanensis}} 宜蘭月桃 \index{宜蘭月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+intermedia}{\textit{A. intermedia} Gagnep.}  \index{Alpinia@\textit{Alpinia}!intermedia@\textit{intermedia}} 山月桃 \index{山月桃}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+japonica}{\textit{A. japonica} (Thunb.) Miq.}  \index{Alpinia@\textit{Alpinia}!japonica@\textit{japonica}} 山薑 \index{山薑}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+koshunensis}{\textit{A. koshunensis} Hayata}  \index{Alpinia@\textit{Alpinia}!koshunensis@\textit{koshunensis}} 恆春月桃 \index{恆春月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+nantoensis}{\textit{A. nantoensis} F.Y.Lu \& Y.W.Kuo}  \index{Alpinia@\textit{Alpinia}!nantoensis@\textit{nantoensis}} 南投月桃 \index{南投月桃} \# DD
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+oui}{\textit{A. oui} Y.H.Tseng \& Chih C.Wang}  \index{Alpinia@\textit{Alpinia}!oui@\textit{oui}} 歐氏月桃 \index{歐氏月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+pricei+var.+pricei}{\textit{A. pricei} Hayata var. \textit{pricei}}  \index{Alpinia@\textit{Alpinia}!pricei@\textit{pricei}!var. pricei@var. \textit{pricei}} 普萊氏月桃 \index{普萊氏月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+pricei+var.+sessiliflora}{\textit{A. pricei} Hayata var. \textit{sessiliflora} (Kitam.) Jeng J.Yang \& J.C.Wang}  \index{Alpinia@\textit{Alpinia}!pricei@\textit{pricei}!var. sessiliflora@var. \textit{sessiliflora}} 阿里山月桃 \index{阿里山月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+shimadae+var.+kawakamii}{\textit{A. shimadae} Hayata var. \textit{kawakamii} (Hayata) Jeng J.Yang \& J.C.Wang}  \index{Alpinia@\textit{Alpinia}!shimadae@\textit{shimadae}!var. kawakamii@var. \textit{kawakamii}} 川上氏月桃 \index{川上氏月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+shimadae+var.+shimadae}{\textit{A. shimadae} Hayata var. \textit{shimadae}}  \index{Alpinia@\textit{Alpinia}!shimadae@\textit{shimadae}!var. shimadae@var. \textit{shimadae}} 島田氏月桃 \index{島田氏月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+uraiensis}{\textit{A. uraiensis} Hayata}  \index{Alpinia@\textit{Alpinia}!uraiensis@\textit{uraiensis}} 烏來月桃 \index{烏來月桃} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+zerumbet}{\textit{A. zerumbet} (Pers.) B.L.Burtt \& R.M.Sm.}  \index{Alpinia@\textit{Alpinia}!zerumbet@\textit{zerumbet}} 月桃 \index{月桃}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+×formosana}{\textit{A. ×formosana} K.Schum.}  \index{Alpinia@\textit{Alpinia}!×formosana@\textit{×formosana}} 臺灣月桃 \index{臺灣月桃}  NA (H)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+×kusshakuensis}{\textit{A. ×kusshakuensis} Hayata}  \index{Alpinia@\textit{Alpinia}!×kusshakuensis@\textit{×kusshakuensis}} 屈尺月桃 \index{屈尺月桃} \# NA (H)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+×mesanthera}{\textit{A. ×mesanthera} Hayata}  \index{Alpinia@\textit{Alpinia}!×mesanthera@\textit{×mesanthera}} 角板山月桃 \index{角板山月桃} \# NA (H)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Alpinia+×tonrokuensis}{\textit{A. ×tonrokuensis} Hayata}  \index{Alpinia@\textit{Alpinia}!×tonrokuensis@\textit{×tonrokuensis}} 屯鹿月桃 \index{屯鹿月桃} \# NA (H)
  \end{itemize}
 \item[] \textit{Curcuma} 薑黃屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Curcuma+longa}{\textit{C. longa} L.}  \index{Curcuma@\textit{Curcuma}!longa@\textit{longa}} 薑黃 \index{薑黃}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Curcuma+zedoaria}{\textit{C. zedoaria} (Christm.) Roscoe}  \index{Curcuma@\textit{Curcuma}!zedoaria@\textit{zedoaria}} 莪朮 \index{莪朮}  NA (N)
  \end{itemize}
 \item[] \textit{Hedychium} 蝴蝶薑屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Hedychium+coronarium}{\textit{H. coronarium} Koenig}  \index{Hedychium@\textit{Hedychium}!coronarium@\textit{coronarium}} 野薑花 \index{野薑花}  NA (N)
  \end{itemize}
 \item[] \textit{Vanoverberghia} 法氏薑屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Vanoverberghia+sasakiana}{\textit{V. sasakiana} Funakoshi \& H.Ohashi}  \index{Vanoverberghia@\textit{Vanoverberghia}!sasakiana@\textit{sasakiana}} 蘭嶼法氏薑 \index{蘭嶼法氏薑} \# VU
  \end{itemize}
 \item[] \textit{Zingiber} 薑屬
                                
  \begin{itemize}
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zingiber+kawagoii}{\textit{Z. kawagoii} Hayata}  \index{Zingiber@\textit{Zingiber}!kawagoii@\textit{kawagoii}} 三奈 \index{三奈} \# LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zingiber+officinale}{\textit{Z. officinale} Roscoe}  \index{Zingiber@\textit{Zingiber}!officinale@\textit{officinale}} 薑 \index{薑}  NA (N)
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zingiber+oligophyllum}{\textit{Z. oligophyllum} K.Schum.}  \index{Zingiber@\textit{Zingiber}!oligophyllum@\textit{oligophyllum}} 少葉薑 \index{少葉薑} \# EN
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zingiber+shuanglongensis}{\textit{Z. shuanglongensis} C.L.Yeh \& S.W.Chung}  \index{Zingiber@\textit{Zingiber}!shuanglongensis@\textit{shuanglongensis}} 雙龍薑 \index{雙龍薑}  LC
        \item[] \href{http://www.theplantlist.org/tpl1.1/search?q=Zingiber+zerumbet}{\textit{Z. zerumbet} (L.) Roscoe ex Sm.}  \index{Zingiber@\textit{Zingiber}!zerumbet@\textit{zerumbet}} 薑花 \index{薑花}  NA (N)
  \end{itemize}
  \end{itemize}
