\footnotesize\selectfont
%\begin{table}[!h]
        {\def\arraystretch{1.5}\tabcolsep=2pt
        \begin{longtable}{L{2.5cm}L{2cm}L{5cm}L{2.5cm}L{3cm}}
        \multicolumn{2}{l}{\large{Gymnosperms 裸子植物}} & & \\
        & & & &\\
        \toprule
          \color{red}{\textbf{科名}} & \color{red}{\textbf{科中名}} & \color{red}{\textbf{分類群學名}} & \color{red}{\textbf{分類群中名}} & \color{red}{\textbf{評估標準}} \\
        \midrule 
        \endfirsthead

        \multicolumn{5}{l}{\large\color{red}{\Kai{國家易危 (NVU) 類別維管束植物名錄(續)}}} \\
        \toprule
        \color{red}{\textbf{科名}} & \color{red}{\textbf{科中名}} & \color{red}{\textbf{分類群學名}} & \color{red}{\textbf{分類群中名}} & \color{red}{\textbf{評估標準}} \\
        \midrule
        \endhead
                Cupressaceae & 柏科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Calocedrus+macrolepis+var.+formosana}{\textit{Calocedrus macrolepis} var. \textit{formosana} } & 臺灣肖楠 & B2ab(ii,v) \index{Calocedrus@\textit{Calocedrus}!macrolepis@\textit{macrolepis}!var. formosana@\textbf{var. \textit{formosana}}}  \index{臺灣肖楠@{\Song{臺灣肖楠}}} \\
    Cupressaceae & 柏科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Cunninghamia+konishii}{\textit{Cunninghamia konishii} } & 巒大杉 & A1ad \index{Cunninghamia@\textit{Cunninghamia}!konishii@\textbf{\textit{konishii}}}  \index{巒大杉@{\Song{巒大杉}}} \\
    Cupressaceae & 柏科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Juniperus+chinensis+var.+taiwanensis}{\textit{Juniperus chinensis} var. \textit{taiwanensis} } & 清水圓柏 & D1+2 \index{Juniperus@\textit{Juniperus}!chinensis@\textit{chinensis}!var. taiwanensis@\textbf{var. \textit{taiwanensis}}}  \index{清水圓柏@{\Song{清水圓柏}}} \\
    Podocarpaceae & 羅漢松科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+fasciculus}{\textit{Podocarpus fasciculus} } & 叢花百日青 & B2ab(i,ii) \index{Podocarpus@\textit{Podocarpus}!fasciculus@\textbf{\textit{fasciculus}}}  \index{叢花百日青@{\Song{叢花百日青}}} \\
    Podocarpaceae & 羅漢松科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Podocarpus+macrophyllus+var.+maki}{\textit{Podocarpus macrophyllus} var. \textit{maki} } & 小葉羅漢松 & B2ab(ii) \index{Podocarpus@\textit{Podocarpus}!macrophyllus@\textit{macrophyllus}!var. maki@\textbf{var. \textit{maki}}}  \index{小葉羅漢松@{\Song{小葉羅漢松}}} \\
    Taxaceae & 紅豆杉科 & \href{http://www.theplantlist.org/tpl1.1/search?q=Cephalotaxus+wilsoniana}{\textit{Cephalotaxus wilsoniana} } & 臺灣粗榧 & C2a(i) \index{Cephalotaxus@\textit{Cephalotaxus}!wilsoniana@\textbf{\textit{wilsoniana}}}  \index{臺灣粗榧@{\Song{臺灣粗榧}}} \\
    \bottomrule
        \end{longtable}
    %%\end{table}
        }
    